### 2022-08-17 Latex/paper.tex
Add files via upload

\documentclass[a4paper,10pt]{article}
%\documentclass{svjour3}
\usepackage{a4wide}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}

%\usepackage{tcolorbox}
\usepackage{subcaption}
\usepackage{amsmath,amssymb}
\usepackage{amsthm}
%\usepackage{calrsfs} % nice cal fonts
\usepackage{enumerate} 
%\usepackage[toc,page]{appendix}

%\usepackage[auth-sc]{authblk}
\usepackage{authblk}
\renewcommand\Affilfont{\normalfont\small}

\usepackage[round]{natbib}
\bibpunct[, ]{(}{)}{;}{a}{}{,}
\let\bibfont\relax
\def\bibfont{\fontsize{8}{10}\selectfont}
\setlength{\bibsep}{0pt}

\usepackage[svgnames]{xcolor}
\usepackage[pdftex]{hyperref}
\hypersetup{
    colorlinks=true,
    colorlinks,
    linkcolor=Navy,
    citecolor=Navy,
    urlcolor=Navy
}
%\definecolor{highlightNEW}{named}{Navy} %To get all equation in black:
\definecolor{highlightNEW}{named}{black}

\usepackage{graphicx}
\graphicspath{{fig/}}
\usepackage{epstopdf}
\usepackage{booktabs}
\usepackage{multirow}

% custom macros and definitions
\newtheorem{theorem}{Theorem}[section] 
%%\newtheorem{acknowledgement}[theorem]{Acknowledgement} 
%%\newtheorem{algorithm}[theorem]{Algorithm} 
%%\newtheorem{axiom}[theorem]{Axiom} 
%%\newtheorem{case}[theorem]{Case} 
%%\newtheorem{claim}[theorem]{Claim} 
%%\newtheorem{conclusion}[theorem]{Conclusion} 
%%\newtheorem{condition}[theorem]{Condition} 
%%\newtheorem{conjecture}[theorem]{Conjecture} 
\newtheorem{corollary}[theorem]{Corollary} 
%%\newtheorem{criterion}[theorem]{Criterion} 
%%\newtheorem{defi}[theorem]{Definition} 
\newtheorem{example}[theorem]{Example} 
%%\newtheorem{exercise}[theorem]{Exercise} 
%%\newtheorem{hypothesis}[theorem]{Hypothesis} 
\newtheorem{lemma}[theorem]{Lemma} 
%%\newtheorem{notation}[theorem]{Notation} 
%%\newtheorem{problem}[theorem]{Problem} 
\newtheorem{proposition}[theorem]{Proposition} 
%%\newtheorem{question}[theorem]{Question} 
\newtheorem{remark}[theorem]{Remark} 
%%\newtheorem{solution}[theorem]{Solution} 
%%\newtheorem{summary}[theorem]{Summary} 
%%\newtheorem{Rem}[theorem]{Remark}

\newcommand{\TODO}[1]{\textbf{\color{red}TODO: {#1}}\PackageWarning{TODO:}{#1!}}
\newcommand{\doi}[1]{DOI~\href{\detokenize{http://dx.doi.org/#1}}{\detokenize{#1}}}

\renewcommand{\d}{\,\mathrm{d}}
\newcommand{\e}{\mathrm{e}}
\newcommand{\E}{\mathbb{E}}
\newcommand{\F}{\mathcal{F}}
\renewcommand{\H}{\mathcal{H}}
\newcommand{\K}{\mathfrak{K}}
\newcommand{\N}{\mathbb{N}}
\renewcommand{\P}{\mathbb{P}}
\newcommand{\R}{\mathbb{R}}
\newcommand{\Var}{\mathbb{V}ar}
\newcommand{\1}{\mathbf{1}}

\newcommand{\la}{\!\left\langle}
\newcommand{\ra}{\right\rangle}
\newcommand{\p}{\partial}

%\newcommand*{\Cdot}{\raisebox{-0.25ex}{\scalebox{1.2}{\ensuremath{\cdot}}}}
\newcommand*{\Cdot}[1][1.25]{%
  \mathpalette{\CdotAux{#1}}\cdot%
}
\newdimen\CdotAxis
\newcommand*{\CdotAux}[3]{%
  {%
    \settoheight\CdotAxis{$#2\vcenter{}$}%
    \sbox0{%
      \raisebox\CdotAxis{%
        \scalebox{#1}{%
          \raisebox{-\CdotAxis}{%
            $\mathsurround=0pt #2#3$%
          }%
        }%
      }%
    }%
    % Remove depth that arises from scaling.
    \dp0=0pt %
    % Decrease scaled height.
    \sbox2{$#2\bullet$}%
    \ifdim\ht2<\ht0 %
      \ht0=\ht2 %
    \fi
    % Use the same width as the original \cdot.
    \sbox2{$\mathsurround=0pt #2#3$}%
    \hbox to \wd2{\hss\usebox{0}\hss}%
  }%
}
\makeatletter
\def\mathcolor#1#{\@mathcolor{#1}}
\def\@mathcolor#1#2#3{%
  \protect\leavevmode
  \begingroup
    \color#1{#2}#3%
  \endgroup
}
\makeatother

\newcommand{\NEW}[1]{\mathcolor{highlightNEW}{#1}}
\let\oldalpha\alpha
\renewcommand{\alpha}{\mathcolor{highlightNEW}{\oldalpha}}
\newcommand{\ccode}[2]{\par
        \vspace*{8pt}
        {{\leftskip18pt\rightskip\leftskip
        \noindent{\it #1}\/: #2\par}}\par}
\newcommand{\keywords}[1]{\ccode{Keywords}{#1}}
\newcommand{\email}[1]{\href{mailto:#1}{#1}}

\title{\textcolor{Navy}{\textsc{Convexity adjustments with a bit of Malliavin}}}

\author[1,2]{David Garcia-Lorite\thanks{Corresponding author, \email{dddd@caixabank.es}}}
\author[3]{Ra\'{u}l Merino}

\affil[1]{CaixaBank,....}
\affil[2]{Facultat de Matem\`{a}tiques i Inform\`{a}tica, Universitat de Barcelona, \authorcr Gran Via 585, 08007 Barcelona, Spain,\vspace*{3pt}}
\affil[3]{VidaCaixa S.A., Market Risk Management Unit, \authorcr C/Juan Gris, 2-8, 08014 Barcelona, Spain.}

%\date{Received: date / Accepted: date}
\date{\normalfont\small\today}

% main document
\begin{document}

\maketitle
\begin{abstract}
AA
\end{abstract}
%\keywords{V--}
%\ccode{MSC classification}{--}
%\ccode{JEL classification}{--}

%\TODO{Remove ToC in final version}
%\tableofcontents
%\clearpage

\section{Introduction}
Mathematical finance aims to find a methodology to price consistently all the instruments quoted in the market. When working with fixed income derivatives, a classic research topic is the introduction of a price adjustment to achieve this. This adjustment is called convexity adjustment. It is non-linear and depends on the interest rate model.

There are several reasons to include this type of adjustment. One of them is to incorporate futures on the yield curve construction. Futures and other fixed-income instruments are quoted differently. The firsts are linear against the yield, but the others are not. Therefore, the changes in value and yield of different contracts are different. This difference will depend on the volatility and correlation of the yield curve.

But it is not the only one. The fixed-income market has several features changing the schedule of payments. For example, in a swap in arrears, the floating coupon fixing and payment are on the same date. Or in a CMS swap, the floating rate is linked to a rate longer than the floating length. Any customization of an interest rate product based on changing time, currency, margin, or collateral will require a convexity adjustment. Deep down, by making these changes, we are mixing the martingale measures.

Convexity adjustments have become popular again. Not only by the increase in volatility in the markets. In addition, as a consequence of the transition in risk-free rates from the IBOR (InterBank Offered Rates) indices to the ARR (Alternative Reference Rates) indices, also called RFR. Both indices try to represent the same thing, the risk-free rate, but they are fundamentally different. While the former represents the average rate at which Panel Banks believe they could borrow money, the latter is calculated backward based on transactions. Therefore, these new products need their corresponding convexity adjustment.

The first references on the convexity adjustment were \cite{RitchkenS}, \cite{Flesaker} and \cite{BrothertonIben}, published almost simultaneously. A convexity formula for averaging contracts was found in \cite{RitchkenS}. Flesaker derived a convexity adjustment for computing the expected Libor rate under the Ho-Lee model in a continuous and discrete setting in \cite{Flesaker}. \cite{BrothertonIben} used the Taylor expansion on the inverse function for calculating the convexity adjustment. In the following years, several improvements were made. For example, the convexity adjustment was extended to other payoffs in \cite{Hull06}. \cite{Hart} improved the Taylor expansion. \cite{KirikosNovak} derived the convexity adjustment for the Hull-White model. Afterwards, we can find papers that extend the convexity adjustment to different payoffs, see \cite{Benhamou00WC} or \cite{Hagan03}. Or by applying alternative techniques such as the change of measure in \cite{Pelsser}, a martingale approach in \cite{Benhamou00} or the effects of stochastic volatility in \cite{PiterbargRenedo} and \cite{HaganWoodward20}.

In the present paper, we find an alternative way to calculate the convexity adjustment for a general interest rate model. The idea is to use the It\^o representation theorem. Unfortunately, the theorem does not give an insight into how to calculate the elements therein. Therefore, it is necessary to introduce basic concepts of Malliavin calculus to apply the Clark-Occone representation formula.

The structure of the paper is as follows. In Section \ref{sec:Notation}, we give the basic preliminaries and our notation related to Interest Rates models. This notation will be used throughout the paper without being repeated in particular theorems unless we find it useful to do so in order to guide the reader through the results. In Section \ref{sec:Malliavin}, we make an introduction to Malliavin calculus. In Section \ref{sec:CA}, In Section \ref{sec:Numerical Results}, In Section \ref{sec:Conclusion}

\section{Preliminaries and notation}\label{sec:Notation}

\section{Malliavin}\label{sec:Malliavin}

\section{Convexity Adjustment}\label{sec:CA}

\section{Numerical Results}\label{sec:Numerical Results}

\section{Conclusion}\label{sec:Conclusion}

% TODO: Change bibliographystyle according to the journal style - it should know the online entry, see Matsuda04
\bibliographystyle{spbasic}
\bibliography{references/references,references/references-books,references/references-own,references/references-online}
%\bibliography{references-export}

\end{document}

### 2022-08-18 Latex/paper.tex
Cambios Malliavin
Se añade la sección de Malliavin al articulo.

@@
 %%\newtheorem{conjecture}[theorem]{Conjecture}
+\newtheorem{definition}[theorem]{Definition}
 \newtheorem{corollary}[theorem]{Corollary} 
@@
 In the present paper, we find an alternative way to calculate the convexity adjustment for a general interest rate model.
-The idea is to use the It\^o representation theorem.
+The idea is to use the It\^o's representation theorem.
 Unfortunately, the theorem does not give an insight into how to calculate the elements therein.
-Therefore, it is necessary to introduce basic concepts of Malliavin calculus to apply the Clark-Occone representation formula.
+Therefore, it is necessary to introduce basic concepts of Malliavin calculus to apply the Clark-Ocone representation formula.
 
@@
 
-\section{Malliavin}\label{sec:Malliavin}
+\section{Basic introduction to Malliavin calculus}\label{sec:Malliavin}
+Malliavin calculus is an infinite-dimensional calculus in a Gaussian space, that is, a stochastic calculus of variations.
+In other words, this is a theory that provides a way to calculate the derivatives of random variables defined in a Gaussian probability space with respect to the underlying noise.
+The initial objective of Malliavin was the study of the existence of densities of Wiener functionals such as solutions of stochastic differential equations.
+But, nowadays, it has become an important tool in stochastic analysis due to the increase in its applications.
+Some of these applications include stochastic calculus for fractional Brownian motion, central limit theorems for multiple stochastic integrals, and an extension of the Itô formula for anticipative processes, but especially mathematical finance.
+For example, we can apply Mallaivin calculus for computing hedging strategies, Greeks, or obtain price approximations.
+See, for example, \cite{AlosLorite} or \cite{Nualart} for more general content.\\
+
+In our case, we are interested in using the Malliavin calculus to apply the Clark–Ocone representation theorem. But, first of all, let's introduce some basic concepts.\\
+
+Now, we introduce the derivative operator in the Malliavin calculus sense and the divergence operator to establish the notation that we use in the remainder of the paper.\\
+
+Consider $W=\left\{W_{t}, t\in \left[0,T\right]\right\}$ a Brownian motion defined on a complete probability space $\left(\Omega, \mathcal{F}, \mathbb{P}\right)$.
+Let $H=L^{2}(\left[0,T\right])$ and denote by
+\begin{eqnarray*}
+W_{t} := \int^{T}_{0} t_{s} \d W_{s},
+\end{eqnarray*}
+the It\^o integral of a deterministic function $h \in H$, also known as Wiener integral. Let $\mathcal{S}$ be the set of smooth random variables of the form
+\begin{eqnarray*}
+F=f\left(W_{t_{1}}, \ldots, W{t_{n}}\right)
+\end{eqnarray*}
+with $t_{1}, \ldots, t_{n} \in \left[0,T\right]$ and $f$ is infinitely differentiable bounded function.
+
+\medbreak
+
+The derivative of a random variable $F$, $D_{s}F$, is defined as the stochastic process given by
+\begin{eqnarray*}
+D_{s}F = \sum^{n}_{i=1} \frac{\partial f}{\partial x_{i}}\left(W_{t_{1}}, \ldots, W_{t_{n}}\right)1_{\left[0, t_{j}\right]}(s), \hspace{0.4cm} s \in \left[0,T\right].
+\end{eqnarray*}
+
+The iterated derivative operator of a random variable $F$ is defined by
+\begin{eqnarray*}
+D^{m}_{s_{1}, \ldots, s_{m}} F = D_{s_{1}} \cdots D_{s_{m}}F, \hspace{0.4cm} s_{1}, \ldots, s_{m} \in \left[0,T\right].
+\end{eqnarray*}
+
+\cite{Nualart} stated that these operators are closable from $L^{p}(\Omega)$ into $L^{p}(\Omega; L^{2}\left[0,T\right])$ for any $p\geq1$, and we denote by $\mathbb{D}^{n,p}$ the closure of $\mathcal{S}$ with respect to the norm
+\begin{eqnarray*}
+\left\|F\right\|_{n,p} := \left(E\left[F\right]^{p} + \sum^{n}_{i=1} E\left\|D^{i} F\right\|^{p}_{L^{2}\left(\left[0,T\right]^{i}\right)} \right)^{\frac{1}{p}}.
+\end{eqnarray*}
+
+\medbreak
+
+We define $\delta$ as the adjoint of derivative operator $D$, also referred to as the Skorohod integral.
+The domain of $\delta$, denoted by $Dom\text{ }\delta$, is the set of elements $u \in L^{2}([0,T] \times \Omega)$ such that there exists $\delta(u) \in L^{2}(\Omega)$ satisfying the duality relation
+\begin{eqnarray*}
+E\left[\delta(u) F \right] = E\left[\int^{T}_{0} \left(D_{s} F\right) u_{s} \d s\right].
+\end{eqnarray*}
+
+The operator $\delta$ is an extension of the Itô integral in the sense that the set $L^{2}_{a}([0,T] \times \Omega)$ of square integrable and adapted processes is included in $Dom\text{ }\delta$ and the operator $\delta$ restricted to $L^{2}_{a}([0,T] \times \Omega)$ coincides with the Itô stochastic integral.
+
+\medbreak
+
+For any $u \in Dom\text{ }\delta$, we will use the following notation
+\begin{eqnarray*}
+\delta(u)=\int^{T}_{0}u_{s}\d W_{s}.
+\end{eqnarray*}
+
+\medbreak
+
+The representation of functionals of Brownian motion by stochastic integrals, also known as martingale representation, has been widely studied over the years.
+It states that if $F$ is a square-integrable random variable, there exists a unique adapted process $\varphi$ in $L^{2}(\Omega \times \left[0,T\right]; \mathbb{R}^{d})$ such that
+\begin{eqnarray*}
+F=E\left[F\right] + \sum^{n}_{i=1}\int^{T}_{0} \varphi^{i}_{s} dW^{i}_{s}.
+\end{eqnarray*}
+In other words, there exists a unique martingale representation or, more precisely, the integrand $\varphi$ in the representation exists and is unique in $L^{2}(\Omega \times \left[0,T\right]; \mathbb{R}^{d})$.
+
+\medbreak
+
+Unfortunately, it is not easy to find an analytic representation of the process $\varphi$.
+Here, the Malliavin calculus helps us to find a solution.
+When the random variable $F$ is Malliavin differentiable, the process $\varphi$ appearing in It\^o's representation theorem, is given by
+\begin{eqnarray*}
+\varphi^{i}=E\left[D^{W^{i}}_{t}F|\mathcal{F}^{W}_{s}\right].
+\end{eqnarray*}
+In fact,
+\begin{eqnarray}
+F=E\left[F\right] + \sum^{n}_{i=1}\int^{T}_{0} E\left[D^{W^{i}}_{t}F|\mathcal{F}^{W}_{s}\right] dW^{i}_{s}
+\end{eqnarray}
+is the Clark-Ocone representation formula.
 

### 2022-08-21 Latex/paper.tex
# convexity adjustment futures under single factor hjm separable

@@
 In fact,
-\begin{eqnarray}
+\begin{eqnarray}\label{clark-okone}
 F=E\left[F\right] + \sum^{n}_{i=1}\int^{T}_{0} E\left[D^{W^{i}}_{t}F|\mathcal{F}^{W}_{s}\right] dW^{i}_{s}
@@
 \section{Convexity Adjustment}\label{sec:CA}
+$\cdots$  tengo que pensar que poner aqui como intro
+\subsection{HJM framework}
+In order to compute the convexity adjustment, we need to assume some dynamic on the estimation curve and discount curve.
+In order to avoid problems with a stochastic basis between both curves, we will suppose a not stochastic basis i.e, we will suppose the next representation for the forward rate curve $f_{E}(t, T)$
+\begin{equation}\label{estimation_forward_rate_curve}
+f_{E}(t,T) = f_{ois}(t,T) + s(t,T).
+\end{equation}
+Where $s(t,T)= f_{E}(0,T) - f_{ois}(0,T)$ i.e we suppose the basis between curves that we get from the market in time $t=0$.
+On other hand, $f_ois(t, T)$ is the OIS forward rate curve and whose dynamic under the $\mathbb{Q}$-measure will be a single factor HJM dynamic i.e
+\begin{align}\label{ois_forward_rate_curve}
+df_{ois}(t,T) &= \sigma(t,T)\nu(t,T)dt + \sigma(t,T)dW^{\mathbb{Q}}_t \nonumber  \\
+f_{ois}(0,T) &= -\partial_T \log\left(P_{ois}(0,T)\right).
+\end{align}
+Where $\nu(t,T)=\int_{t}^{T}\sigma(t,s)ds$ and $\sigma(t, T)$ is a positive function for all $t,T > 0$ .
+In order to have a Markovian representation of the HJM model, It is usual to assume that volatility function in \ref{ois_forward_rate_curve} is separable, i.e
+\begin{equation}
+\sigma(t,T)= h(t)g(T).
+\end{equation}
+where g is a time-dependent positive function and h is a general non-negative process. It is easy to show (see Andreasen 2001), that in this case (\ref{ois_forward_rate_curve})
+\begin{equation}
+r_{ois}(t)=f_{ois}(t,t)= f_{ois}(0,t) + x_t,
+\end{equation}  
+where
+\begin{align}\label{short_rate_cheyette}
+dx_t &= (-k_t x_t + y_t)dt + \eta_t dW_t^{\mathbb{Q}}\\
+dy_t &= (\eta^{2}_t - 2 k_t y_t) dt,
+\end{align} 
+with 
+\begin{align*}
+\eta_t &= g(t)h(t,x_t,y_t)  \nonumber \\
+k_t &= - \frac{\partial_t g(t)}{g(t)}
+\end{align*}
+Then with a little bit of algebra and we use Itô formula we can show the next representation formula for $P_{ois}(t,T)$
+\begin{equation}
+P_{ois}(t,T) = \frac{P_{ois}(0,T)}{P_{ois}(0,t)} \exp\left(-G(t,T)x_t - \frac{1}{2} G^{2}(t,T) \right)
+\end{equation}
+with $G(t,T) = \int_{t}^{T} \exp\left(-\int_{t}^{u} k_s ds \right) du$.
+
+\subsection{FRAs Vs futures}
+The cashflows in FRAs and futures are computing under different measures and consequently we have to adjust the futures price quote to transform them to FRAs price quote.
+As usual, we will define the forward rate  in time $t_0$ between $t_1$ and $t_2$ under the forward curve $E$ as
+\begin{equation}\label{forward_rate}
+L_{E}(t_0, t_1, t_2) = \frac{\left(\frac{P_{E}(t_0,t_1)}{P_{E}(t_0,t_2)} - 1   \right)}{\delta_{t_1,t_2}},
+\end{equation} 
+Where $P_{E}(t,T)$ is the discount factor for the curve $E$ from t to T and $\delta_{t_1,t_2}$ is the year fraction between $t_1$ and $t_2$.
+We must observe that $L_{E}(t, t_1, t_2)$ is a martingale under the forward measure $\mathbb{Q}^{t_2}$.
+Let us define the future rate
+\begin{equation}\label{future}
+\hat{L}_{E}(t, t_1, t_2) = \mathbb{E}_t^{\mathbb{Q}}\left(L_{E}(t_0, t_1, t_2) \right), 
+\end{equation}
+where the measure $\mathbb{Q}$ is the measure associated to the numeraire $B_t=\exp\left(\int_{0}^{t} r_{ois, s} ds \right)$ with $ r_{ois, t}$ the risk free short rate.
+From (\ref{forward_rate}) and (\ref{future}), we can define the convexity adjusment the next way
+\begin{equation}
+CA(t, t_0, t_1, t_2) = \mathbb{E}_t^{\mathbb{Q}}\left(L_{E}(t_0, t_1, t_2) \right) - \mathbb{E}_t^{\mathbb{Q}^{t_2}}\left(L_{E}(t_0, t_1, t_2) \right) =  \mathbb{E}_t^{\mathbb{Q}}\left(L_{E}(t_0, t_1, t_2) \right) - L_{E}(t_0, t_1, t_2)
+\end{equation}\label{convexity_adjustment_future}
+With view to get a general representation formula of the convexity adjustment for the futures, we will use (\ref{clark-okone}) to 
+$L_{E}(t_0,t_1,t_2)$ i.e
+
+\begin{equation}
+L_{E}(t_0,t_1,t_2) = \mathbb{E}^{\mathbb{Q}}_t\left(L_{E}(t_0,t_1,t_2)\right) + \int_{0}^{t_0} \mathbb{E}_{s}\left(D_s L_{E}(t_0,t_1,t_2) \right) dW^{\mathbb{Q}}_s.
+\end{equation} 
+Now, if we take $\mathbb{E}^{\mathbb{Q}^{t2}}(\cdot)$ in the last equation, then we get
+\begin{equation}
+CA(t, t_0, t_1, t_2) = - \mathbb{E}^{\mathbb{Q}^{t2}}\left(\int_{0}^{t_0} \mathbb{E}_{s}\left(D_s L_{E}(t_0,t_1,t_2) \right) dW^{\mathbb{Q}}_s \right)
+\end{equation}
+Now under the framwork of the last section and if we apply Girsanov's theorem to switch to measure $\mathbb{Q}^{t_2}$, we get that
+\begin{equation}
+CA(t, t_0, t_1, t_2) = \mathbb{E}^{\mathbb{Q}^{t2}}\left(\int_{0}^{t_0} \mathbb{E}_{s}\left(D_s L_{E}(t_0,t_1,t_2) \right) \nu(s,t_2) ds \right)
+\end{equation}
+where $\nu(t,T)$ has been defined in (\ref{ois_forward_rate_curve}).
+
+\subsection{OIS futures}
+
+\subsection{CMSs}
 

### 2022-08-24 Latex/paper.tex
# Calculations for future convexity adjusment

--- 2022-08-18 Latex/paper.tex
@@
 \section{Convexity Adjustment}\label{sec:CA}
+$\cdots$  tengo que pensar que poner aqui como intro
+\subsection{HJM framework}
+In order to compute the convexity adjustment, we need to assume some dynamic on the estimation curve and discount curve.
+In order to avoid problems with a stochastic basis between both curves, we will suppose a not stochastic basis i.e, we will suppose the next representation for the forward rate curve $f_{E}(t, T)$
+\begin{equation}\label{estimation_forward_rate_curve}
+f_{E}(t,T) = f_{ois}(t,T) + s(t,T).
+\end{equation}
+Where $s(t,T)= f_{E}(0,T) - f_{ois}(0,T)$ i.e we suppose the basis between curves that we get from the market in time $t=0$.
+On other hand, $f_ois(t, T)$ is the OIS forward rate curve and whose dynamic under the $\mathbb{Q}$-measure will be a single factor HJM dynamic i.e
+\begin{align}\label{ois_forward_rate_curve}
+df_{ois}(t,T) &= \sigma(t,T)\nu(t,T)dt + \sigma(t,T)dW^{\mathbb{Q}}_t  \\
+f_{ois}(0,T) &= -\partial_T \log\left(P_{ois}(0,T)\right) \nonumber
+\end{align}
+where $\nu(t,T)=\int_{t}^{T}\sigma(t,s)ds$ and $\sigma(t, T)$ is a positive function for all $t,T > 0$ .
+In order to have a Markovian representation of the HJM model, It is usual to assume that volatility function is separable, i.e
+\begin{equation}
+\sigma(t,T)= h(t)g(T).
+\end{equation}
+with g is a time-dependent positive function and h is a general non-negative process. It is easy to show (see Andreasen 2001), that in this case (\ref{ois_forward_rate_curve})
+\begin{equation}
+r_{ois}(t)=f_{ois}(t,t)= f_{ois}(0,t) + x_t,
+\end{equation}  
+where
+\begin{align}\label{short_rate_cheyette}
+dx_t &= (-k_t x_t + y_t)dt + \eta_t dW_t^{\mathbb{Q}} \nonumber \\
+dy_t &= (\eta^{2}_t - 2 k_t y_t) dt ,
+\end{align} 
+with 
+\begin{align*}
+\eta_t &= g(t)h(t,x_t,y_t)  \nonumber \\
+k_t &= - \frac{\partial_t g(t)}{g(t)}
+\end{align*}
+Then with a little bit of algebra and we use Itô formula we can show the next representation formula for $P_{ois}(t,T)$
+\begin{equation}\label{bond_ois}
+P_{ois}(t,T) = \frac{P_{ois}(0,T)}{P_{ois}(0,t)} \exp\left(-G(t,T)x_t - \frac{1}{2} G^{2}(t,T)y_t \right)
+\end{equation}
+where $G(t,T) = \int_{t}^{T} \exp\left(-\int_{t}^{u} k_s ds \right) du$. We must observe, that under the representation (\ref{estimation_forward_rate_curve}) we have that
+\begin{equation}\label{bond_forward}
+P_{E}(t,T)=H(t,T)P_{ois}(t,T)
+\end{equation}
+where $H(t,T)=\exp\left(-\int_{t}^{T}s(t,u) du \right)$.
+
+\subsection{FRAs Vs futures}
+The cashflows in FRAs and futures are computing under different measures and consequently we have to adjust the futures price quote to transform them to FRAs price quote.
+As usual, we will define the forward rate  in time $t_0$ between $t_1$ and $t_2$ under the forward curve $E$ as
+\begin{equation}\label{forward_rate}
+L_{E}(t_0, t_1, t_2) = \frac{\left(\frac{P_{E}(t_0,t_1)}{P_{E}(t_0,t_2)} - 1 \right)}{\delta_{t_1,t_2}}
+\end{equation} 
+where $P_{E}(t,T)$ is the discount factor for the curve $E$ from t to T and $\delta_{t_1,t_2}$ is the year fraction between $t_1$ and $t_2$.
+We must observe that $L_{E}(t, t_1, t_2)$ is a martingale under the forward measure $\mathbb{Q}^{t_2}$.
+Let us define the future rate
+\begin{equation}\label{future}
+\hat{L}_{E}(t, t_1, t_2) = \mathbb{E}_t^{\mathbb{Q}}\left(L_{E}(t_0, t_1, t_2) \right), 
+\end{equation}
+where the measure $\mathbb{Q}$ is the measure associated to the numeraire $B_t=\exp\left(\int_{0}^{t} r_{ois, s} ds \right)$ with $ r_{ois, t}$ the risk free short rate.
+From (\ref{forward_rate}) and (\ref{future}), we will define the convexity adjusment as
+\begin{equation*}
+CA(t, t_0, t_1, t_2) = \mathbb{E}_t^{\mathbb{Q}}\left(L_{E}(t_0, t_1, t_2) \right) - \mathbb{E}_t^{\mathbb{Q}^{t_2}}\left(L_{E}(t_0, t_1, t_2) \right) =  \mathbb{E}_t^{\mathbb{Q}}\left(L_{E}(t_0, t_1, t_2) \right) - L_{E}(t_0, t_1, t_2)
+\end{equation*}
+With view to get a general representation formula of the convexity adjustment for the futures, we will use (\ref{clark-okone}) to 
+$L_{E}(t_0,t_1,t_2)$ i.e
+
+\begin{equation}
+L_{E}(t_0,t_1,t_2) = \mathbb{E}^{\mathbb{Q}}_t\left(L_{E}(t_0,t_1,t_2)\right) + \int_{0}^{t_0} \mathbb{E}_{s}\left(D_s L_{E}(t_0,t_1,t_2) \right) dW^{\mathbb{Q}}_s
+\end{equation} 
+therefore, if we take $\mathbb{E}^{\mathbb{Q}^{t2}}(\cdot)$ in the last equation, then we get
+\begin{equation*}
+CA(t, t_0, t_1, t_2) = - \mathbb{E}^{\mathbb{Q}^{t2}}\left(\int_{0}^{t_0} \mathbb{E}_{s}\left(D_s L_{E}(t_0,t_1,t_2) \right) dW^{\mathbb{Q}}_s \right).
+\end{equation*}
+From (\ref{ois_forward_rate_curve}) and since $f_{ois}(t,T)$ is a $\mathbb{Q}^{T}$ martingale, we have that
+\begin{equation*}
+dW^{\mathbb{Q}^{t_2}} = dW^{\mathbb{Q}} + \nu(t,T) dt. 
+\end{equation*}
+Therefore, if we apply Girsanov's theorem to switch to measure $\mathbb{Q}^{t_2}$, we get that
+\begin{equation}\label{ca_future}
+CA(t, t_0, t_1, t_2) = \mathbb{E}^{\mathbb{Q}^{t2}}\left(\int_{0}^{t_0} \mathbb{E}_{s}\left(D_s L_{E}(t_0,t_1,t_2) \right) \nu(s,t_2) ds \right)
+\end{equation}
+where $\nu(t,T)$ has been defined in (\ref{ois_forward_rate_curve}). Now, from the definition of $L_{E}(t,T)$ we have that
+\begin{equation*}
+D_s L_{E}(t_0,t_1,t_2) = \frac{H(t_0,t_1)}{\delta_{t_1,t_2}H(t_0,t_2)} D_s \left(\frac{P_{ois}(t_0,t_1)}{P_{ois}(t_0,t_2)}\right). 
+\end{equation*}
+If we use the representation formula (\ref{bond_ois}) we get that
+\begin{equation*}
+D_s \left(\frac{P_{ois}(t_0,t_1)}{P_{ois}(t_0,t_2)}\right) = \frac{\left(\partial_{x}P_{ois}(t_0,t_1)P_{ois}(t_0,t_2) - \partial_{x}P_{ois}(t_0,t_2) P_{ois}(t_0,t_1) \right)}{P^{2}_{ois}(t_0,t_2)} D_s x_{t_0}
+\end{equation*}
+therefore
+\begin{equation*}
+D_s L_{E}(t_0,t_1,t_2) = \frac{H(t_0,t_1)}{\delta_{t_1,t_2}H(t_0,t_2)}\frac{\left(\partial_{x}P_{ois}(t_0,t_1)P_{ois}(t_0,t_2) - \partial_{x}P_{ois}(t_0,t_2) P_{ois}(t_0,t_1) \right)}{P^{2}_{ois}(t_0,t_2)} D_s x_{t_0}.
+\end{equation*}
+From (\ref{short_rate_cheyette}) y we define $\beta(s,t, x, y) = \exp\left(-\int_{s}^{t} k_{u} \right) \eta(s, x, y)$ we have that
+\begin{equation*}
+D_s x_{t_0} = \beta(s,t_0, x_s, y_s)M(s,t_0)
+\end{equation*}
+where $M(s,t_0)=\exp\left(-\frac{\int_{s}^{t_0} \left(\partial_x \beta(u,t_0,x_s,y_s)\right)^{2} du}{2} + \int_{s}^{t_0} \partial_x \beta(u,t_0,x_s,y_s) dW^{\mathbb{Q}}_u \right)$. 
+Then, we have that
+\begin{align*}
+D_s L_{E}(t_0,t_1,t_2) &= \frac{H(t_0,t_1)}{\delta_{t_1,t_2}H(t_0,t_2)}\frac{\left(\partial_{x}P_{ois}(t_0,t_1)P_{ois}(t_0,t_2) - \partial_{x}P_{ois}(t_0,t_2) P_{ois}(t_0,t_1) \right)}{P^{2}_{ois}(t_0,t_2)} \beta(s,t_0, x_s, y_s)M(s,t_0) \nonumber \\
+=& \frac{P_{E}(0,t_1)}{\delta_{t_1,t_2} P_{E}(0,t_2)} \left(G(t_0,t_2) - G(t_0,t_1)\right)\beta(s,t_0, x_s, y_s)M(s,t_0).
+\end{align*}
+It is a common practice, freeze the state variables of the model to achieve some approximations. We can approximate $x_s$ and $y_s$ the next way
+\begin{align*}
+x_s &\approx x_0 \nonumber \\
+y_s &\approx y_0 + \int_{0}^{s} \exp\left(-2\int_{u}^{s} k_{u^{\prime}} du^{\prime} \right) \eta(u,x_0,y_0) du
+\end{align*}
+Therefore, 
+\begin{equation}\label{approximation_clarkocone}
+\mathbb{E}_s\left( D_s L_{E}(t_0,t_1,t_2) \right) = \frac{P_{E}(0,t_1)}{\delta_{t_1,t_2} P_{E}(0,t_2)} \left(G(t_0,t_2) - G(t_0,t_1)\right)\beta(s,t_0, x_0, \hat{y}_s)
+\end{equation}
+where $\hat{y}_s = y_0 + \int_{0}^{s} \exp\left(-2\int_{u}^{s} k_{u^{\prime}} du^{\prime} \right) \eta(u,x_0,y_0) du$.
+Now, from (\ref{ca_future}) and (\ref{approximation_clarkocone}) we have the next approximation for the convexity adjustmet for future
+
+\hspace{1cm}
+\fboxsep1em
+\fbox{\parbox{310pt}
+{
+\begin{equation}
+CA(t,t_0,t_1) \approx \frac{P_{E}(0,t_1)}{\delta_{t_1,t_2} P_{E}(0,t_2)} \left(G(t_0,t_2) - G(t_0,t_1)\right) \int_{0}^{t_0}  \beta(s,t_0, x_0, \hat{y}_s) ds. 
+\end{equation}
+}}
+\begin{example}
+Hull-White model
+\end{example}
+
+\begin{example}
+Ho-Lee model
+\end{example}
+\subsection{OIS futures}
+
+\subsection{CMSs}
 

### 2022-09-01 Latex/paper.tex
# ois futures

@@
 Therefore, if we apply Girsanov's theorem to switch to measure $\mathbb{Q}^{t_2}$, we get that
-\begin{equation}\label{ca_future}
+\begin{equation}\label{ca_general_future}
 CA(t, t_0, t_1, t_2) = \mathbb{E}^{\mathbb{Q}^{t2}}\left(\int_{0}^{t_0} \mathbb{E}_{s}\left(D_s L_{E}(t_0,t_1,t_2) \right) \nu(s,t_2) ds \right)
@@
 where $\hat{y}_s = y_0 + \int_{0}^{s} \exp\left(-2\int_{u}^{s} k_{u^{\prime}} du^{\prime} \right) \eta(u,x_0,y_0) du$.
-Now, from (\ref{ca_future}) and (\ref{approximation_clarkocone}) we have the next approximation for the convexity adjustmet for future
+Now, from (\ref{ca_general_future}) and (\ref{approximation_clarkocone}) we have the next approximation for the convexity adjustmet for future
 
@@
 \fboxsep1em
-\fbox{\parbox{310pt}
+\fbox{\parbox{350pt}
 {
-\begin{equation}
-CA(t,t_0,t_1) \approx \frac{P_{E}(0,t_1)}{\delta_{t_1,t_2} P_{E}(0,t_2)} \left(G(t_0,t_2) - G(t_0,t_1)\right) \int_{0}^{t_0}  \beta(s,t_0, x_0, \hat{y}_s) ds. 
+\begin{equation}\label{ca_approximation_futures}
+CA(t,t_0,t_1) \approx \frac{P_{E}(0,t_1)}{\delta_{t_1,t_2} P_{E}(0,t_2)} \left(G(t_0,t_2) - G(t_0,t_1)\right) \int_{0}^{t_0}  \beta(s,t_0, x_0, \hat{y}_s) \nu(s,t_2) ds. 
 \end{equation}
@@
 \begin{example}
-Hull-White model
+Let us to set 
+\begin{align*}
+g(T) &= \exp(-kT) \\
+h(t) &= \sigma
+\end{align*}
 \end{example}
+With this parametrization, the Cheyette model is equiavalent to Hull-White model. It is easy to show that under this parametrization, the convexity adjustment (\ref{ca_approximation_futures}) is
+\begin{align*}
+CA(t,t_0,t_1) & \approx \frac{P_{E}(0,t_1)}{\delta_{t_1,t_2} P_{E}(0,t_2)} \left(\exp(-k(t_1 - t_0)) - \exp(-k(t_1 - t_0)) \right) \sigma^{2} \exp(-k t_0)  \int_{0}^{t_0} \frac{\left(\exp(- k s) - \exp(- k t_2)   \right)}{k} ds.
+\end{align*}
+In the next figure, we can check the accuracy of the last formula versus montecarlo. The parameters that we have used are $\sigma=0.05$, $k=0.003$ and flat curve with level $r=0.01$.
 
-\begin{example}
-Ho-Lee model
-\end{example}
+$\cdots$
+
 \subsection{OIS futures}
+In this we will derive the covexity adjustment for overnight-indexed swap (OIS) under. We will define for $t_0 < t_1$
+\begin{align*}
+R(t_0,t_1) &= \frac{\mathbb{E}_t^{Q}\left(\exp\left(\int_{t_0}^{t_1}r_{ois,u} du\right)\right) - 1}{t_1 - t_0} \\
+R_{avg}(t_0,t_1) &= \frac{\int_{t_0}^{t_1}r_{ois,u} du}{t_1 - t_0}.
+\end{align*}
+We must observe, that both $R(\cdot,t_0,t_1)$ and $R_{avg}(\cdot,t_0,t_1)$  are not predictible and they are only observable in $t_1$. However, since
+$R(\cdot,t_0,t_1)$ and $R_{avg}(\cdot,t_0,t_1)$ are flows that will be payed in $t_1$, we can considerer the expected value under the measure $\mathbb{Q}^{t_1}$ that will observable during whole period $[t_0, t_1]$.
+Let us define the next $\mathbb{Q}^{t_1}$ martingales
+\begin{align*} 
+\bar{R}(t,t_0,t_1) &= \mathbb{E}^{\mathbb{Q}^{t_1}}\left( R(t_0,t_1)  \right) \\
+\bar{R}_{avg}(t,t_0,t_1) &= \mathbb{E}^{\mathbb{Q}^{t_1}}\left( R_{avg}(t_0,t_1)  \right).
+\end{align*}
+We must do several obeservations. The first observation is that
+\begin{align*}
+F(t,t_0,t_1)=\mathbb{E}_{t}^{\mathbb{Q}}\left(\exp\left(-\int_{t}^{t_0} r_{ois,u} du \right) R(t_0,t_1) \right) &= \frac{P_{ois}(t,t_0)- P_{ois}(t,t_1)}{t_1 - t_0}, \quad t \in [0,t_0] \\
+F(t,t_0,t_1)=\mathbb{E}_{t}^{\mathbb{Q}}\left(\exp\left(-\int_{t}^{t_0} r_{ois,u} du \right) R(t_0,t_1) \right) &= \frac{1}{t_1 - t_0} \left(\frac{\left( \exp\left(\int_{t}^{t_1}r_{ois,u} du\right)\right)}{P_{ois}(t_0,t)}-1\right), \quad  t \in  [t_0, t_1].
+\end{align*}
+The can define the convexity adjustment for $ R(t_0,t_1)$ the next way
+\begin{equation}\label{R_ois_ca}
+CA_{ois}(t,t_0,t_1) = F(t,t_0,t_1) - \bar{R}(t,t_0,t_1) 
+\end{equation}
+The second observation, we must do is that
+\begin{equation*}
+F_{avg}(t,t_0,t_1) = \mathbb{E}_{t}^{\mathbb{Q}}\left(\exp\left(-\int_{t}^{t_0} r_{ois,u} du \right) R_{avg}(t_0,t_1) \right) =  
+\end{equation*}
+
+\subsection{FRAs in arrears}
 
 \subsection{CMSs}
-
-\section{Numerical Results}\label{sec:Numerical Results}
 

### 2022-09-01 Latex/paper.tex
# New project test unitaries as examples

@@
 therefore
-\begin{equation*}
+\begin{equation}\label{malliavin_derive_L}
 D_s L_{E}(t_0,t_1,t_2) = \frac{H(t_0,t_1)}{\delta_{t_1,t_2}H(t_0,t_2)}\frac{\left(\partial_{x}P_{ois}(t_0,t_1)P_{ois}(t_0,t_2) - \partial_{x}P_{ois}(t_0,t_2) P_{ois}(t_0,t_1) \right)}{P^{2}_{ois}(t_0,t_2)} D_s x_{t_0}.
-\end{equation*}
+\end{equation}
 From (\ref{short_rate_cheyette}) y we define $\beta(s,t, x, y) = \exp\left(-\int_{s}^{t} k_{u} \right) \eta(s, x, y)$ we have that
-\begin{equation*}
+\begin{equation}\label{malliavin_derive_x}
 D_s x_{t_0} = \beta(s,t_0, x_s, y_s)M(s,t_0)
-\end{equation*}
+\end{equation}
 where $M(s,t_0)=\exp\left(-\frac{\int_{s}^{t_0} \left(\partial_x \beta(u,t_0,x_s,y_s)\right)^{2} du}{2} + \int_{s}^{t_0} \partial_x \beta(u,t_0,x_s,y_s) dW^{\mathbb{Q}}_u \right)$. 
@@
 }}
-\begin{example}
+\begin{example}\label{example_ca_future}
 Let us to set 
@@
 \end{equation}
-The second observation, we must do is that
+The second observation, is that under the dyam we must do is that
 \begin{equation*}
-F_{avg}(t,t_0,t_1) = \mathbb{E}_{t}^{\mathbb{Q}}\left(\exp\left(-\int_{t}^{t_0} r_{ois,u} du \right) R_{avg}(t_0,t_1) \right) =  
+\mathbb{E}_{t}^{\mathbb{Q}}\left(R_{avg}(t_0,t_1) \right) = \mathbb{E}_t^{\mathbb{Q}}\left( \frac{\log\left(1+(t_1 - t_0)R(t_0,t_1) \right)}{t_1 - t_0} \right).  
 \end{equation*}
+Then, we have two convexity effects, one of them is the convexity of $\log(1+x)$ and the other comes from $R(t_0,t_1)$.
+Therefore, we need only to compute convexity adjusment for $R(t_0,t_1)$ and apply
+\begin{equation}\label{log_approximation}
+\frac{\log(1 + (t_1 - t_0)(x +\epsilon))}{(t_1 - t_0)} \approx \log(1 + (t_1 - t_0)x) + \frac{1}{1 + (t_1 - t_0)x}   \epsilon - \frac{1}{(1 + (t_1 - t_0)x)^{2}} \epsilon^{2}
+\end{equation}
+to get the convexity adjustment for $R_{avg}(t_0,t_1)$. Now, if we use (\ref{clark-okone}) and (\ref{malliavin_derive_x}, we have the next representation for $R(t_0,t_1)$ 
+\begin{align*}
+R(t_0,t_1) &=   \mathbb{E}^{\mathbb{Q}}\left(R(t_0,t_1) \right) + \int_{0}^{t_1}\mathbb{E}^{\mathbb{Q}}_s\left(D_s R(t_0,t_1) \right) dW^{\mathbb{Q}}_s \\
+&= \mathbb{E}^{\mathbb{Q}}\left(R(t_0,t_1) \right) + \int_{0}^{t_1}\mathbb{E}^{\mathbb{Q}}_s\left(\int_{\max(s,t_0)}^{t1} D_s x_u du \right) dW^{\mathbb{Q}}_s \\
+&= \mathbb{E}^{\mathbb{Q}}\left(R(t_0,t_1) \right) + \int_{0}^{t_1}\int_{\max(s,t_0)}^{t1} \mathbb{E}^{\mathbb{Q}}_s\left(\beta(s,u, x_s, y_s)M(s,u)  \right) du  dW^{\mathbb{Q}}_s\\
+&\approx \mathbb{E}^{\mathbb{Q}}\left(R(t_0,t_1) \right) + \int_{0}^{t_1}\int_{\max(s,t_0)}^{t1} \mathbb{E}^{\mathbb{Q}}_s\left(\beta(s,u, x_s, y_s)M(s,u)  \right) du  dW^{\mathbb{Q}}_s
+\end{align*}
+Then, if we use Girsanov's theorem we have that
+\begin{align*}
+F(0,t_0,t_1) &\approx \mathbb{E}^{\mathbb{Q}}\left(R(t_0,t_1) \right) - \int_{0}^{t_1}\int_{\max(s,t_0)}^{t1} \mathbb{E}^{\mathbb{Q}}_s\left(\beta(s,u, x_s, y_s)M(s,u)  \right) \nu(s,t_1)  du ds \\
+&\approx \mathbb{E}^{\mathbb{Q}}\left(R(t_0,t_1) \right) - \int_{0}^{t_1}\int_{\max(s,t_0)}^{t1}  \beta(s,u, x_0, \hat{y}_s) \nu(s,t_1)  du ds  
+\end{align*}
+And therefore
+\begin{equation}\label{convexity_ois_future}
+ \mathbb{E}^{\mathbb{Q}}\left(R(t_0,t_1) \right) \approx F(0,t_0,t_1) + \int_{0}^{t_1}\int_{\max(s,t_0)}^{t1}  \beta(s,u, x_0, \hat{y}_s) \nu(s,t_1)  du ds.
+\end{equation}
+Now, if we use (\ref{log_approximation}) with 
+\begin{align*}
+x &= \mathbb{E}^{\mathbb{Q}}\left(R(t_0,t_1) \right)\\
+\epsilon &= \int_{0}^{t_1}\int_{\max(s,t_0)}^{t1}  \beta(s,u, x_0, \hat{y}_s) \nu(s,t_1)  du  dW^{\mathbb{Q}}_s
+\end{align*} 
+we can calculate the adjusment for $R_{avg}(t_0,t1)$
+\begin{align*}
+\mathbb{E}^{\mathbb{Q}}\left(R_{avg}(t_0,t_1) \right) &\approx \frac{\log\left(1+(t_1 - t_0)\mathbb{E}^{\mathbb{Q}}\left(R(t_0,t_1)\right)\right)}{t_1 - t_0} \\
+&-\frac{1}{2(1 + (t_1 - t_0)\mathbb{E}^{\mathbb{Q}}\left(R(t_0,t_1)\right))^{2}} \int_{0}^{t_1}\left(\int_{\max(s,t_0)}^{t1}  \beta(s,u, x_0, \hat{y}_s)  du\right)^{2} ds
+\end{align*}
+
+\begin{example}
+The same way that in the example (\ref{example_ca_future}), we will suppose a Hull-White model with constan mean reversion $k$ and constant volatility $\sigma$. Then
+\end{example}
 

### 2022-09-01 ConvexityAdjustment-Lib/ConvexityAdjusmentUnitTests/FraVsFuturesTests.cs

@@ -1,0 +1,64 @@
+using NUnit.Framework;
+using ql = QLNet;
+using System;
+
+namespace ConvexityAdjustment_UnitTest
+{
+
+    public class ConvexityAdjustmentHullWhite
+    {
+        [Test]
+        public void HullWhiteFraVsFutureConvexity()
+        {
+            
+            // settings
+            var calendar = new ql.TARGET();
+            
+            // Hull-White parameters
+            double k = 0.003;
+            double sigma = 0.05;
+            // double spreadBasis = 0.001;
+
+            // Curves
+            double flatRate = 0.01;
+            ql.Quote quoteRate = new ql.SimpleQuote(flatRate);
+            ql.DayCounter dc = new ql.Actual365Fixed();
+            ql.Date startDate = ql.Settings.evaluationDate();
+            ql.Handle<ql.YieldTermStructure> curve =  new ql.Handle<ql.YieldTermStructure>(new ql.FlatForward(startDate, quoteRate, dc));
+
+            // Model and process
+            ql.HullWhiteProcess process = new ql.HullWhiteProcess(curve, k, sigma);
+            ql.HullWhite model = new ql.HullWhite(curve, k, sigma);
+            
+            // Product
+            var t0 = calendar.advance(startDate, 12, ql.TimeUnit.Months);
+            var t1 = calendar.advance(t0, 12, ql.TimeUnit.Months);
+            
+            // MC
+            int numberOfSimulations = 10;
+            ulong seed = 123545;
+            double deltaTime = 0.1;
+            double length = dc.yearFraction(startDate, t1);
+            int timeSteps = (int)(length / deltaTime);
+            
+            var rsg = (ql.InverseCumulativeRsg<ql.RandomSequenceGenerator<ql.MersenneTwisterUniformRng>, 
+                       ql.InverseCumulativeNormal>)
+                       new ql.PseudoRandom().make_sequence_generator(timeSteps, seed);
+
+            ql.PathGenerator<ql.IRNG> generator = new ql.PathGenerator<ql.IRNG>(process, length, timeSteps, rsg, false);
+            
+            // Path generator
+            int i;
+            for (i = 0; i < numberOfSimulations; i++)
+                generator.next();
+            
+            ql.Sample<ql.IPath> sample = generator.next();
+            ql.Path value = sample.value as ql.Path;
+        }
+        
+    }
+    
+
+
+
+}

### 2022-09-06 Latex/paper.tex
# New function to compute future convexity and modification in .tex

@@
 \begin{equation}\label{future}
-\hat{L}_{E}(t, t_1, t_2) = \mathbb{E}_t^{\mathbb{Q}}\left(L_{E}(t_0, t_1, t_2) \right), 
+\hat{L}_{E}(t,t_0, t_1, t_2) = \mathbb{E}_t^{\mathbb{Q}}\left(L_{E}(t_0, t_1, t_2) \right), 
 \end{equation}
@@
 \begin{equation*}
-CA(t, t_0, t_1, t_2) = \mathbb{E}_t^{\mathbb{Q}}\left(L_{E}(t_0, t_1, t_2) \right) - \mathbb{E}_t^{\mathbb{Q}^{t_2}}\left(L_{E}(t_0, t_1, t_2) \right) =  \mathbb{E}_t^{\mathbb{Q}}\left(L_{E}(t_0, t_1, t_2) \right) - L_{E}(t_0, t_1, t_2)
+CA(t, t_0, t_1, t_2) = \hat{L}_{E}(t,t_0, t_1, t_2) - \mathbb{E}_t^{\mathbb{Q}^{t_2}}\left(L_{E}(t_0, t_1, t_2) \right)
 \end{equation*}
@@
 \begin{equation}
-L_{E}(t_0,t_1,t_2) = \mathbb{E}^{\mathbb{Q}}_t\left(L_{E}(t_0,t_1,t_2)\right) + \int_{0}^{t_0} \mathbb{E}_{s}\left(D_s L_{E}(t_0,t_1,t_2) \right) dW^{\mathbb{Q}}_s
+L_{E}(t_0,t_1,t_2) = \hat{L}_{E}(t,t_0, t_1, t_2) + \int_{0}^{t_0} \mathbb{E}_{s}\left(D_s L_{E}(t_0,t_1,t_2) \right) dW^{\mathbb{Q}}_s
 \end{equation} 
@@
 \begin{equation*}
-CA(t, t_0, t_1, t_2) = - \mathbb{E}^{\mathbb{Q}^{t2}}\left(\int_{0}^{t_0} \mathbb{E}_{s}\left(D_s L_{E}(t_0,t_1,t_2) \right) dW^{\mathbb{Q}}_s \right).
+CA(t, t_0, t_1, t_2) = - \mathbb{E}^{\mathbb{Q}^{t2}}\left(\int_{0}^{t_0} \mathbb{E}^{\mathbb{Q}}_{s}\left(D_s L_{E}(t_0,t_1,t_2) \right) dW^{\mathbb{Q}}_s \right).
 \end{equation*}
@@
 \begin{equation}\label{ca_general_future}
-CA(t, t_0, t_1, t_2) = \mathbb{E}^{\mathbb{Q}^{t2}}\left(\int_{0}^{t_0} \mathbb{E}_{s}\left(D_s L_{E}(t_0,t_1,t_2) \right) \nu(s,t_2) ds \right)
+CA(t, t_0, t_1, t_2) = \mathbb{E}^{\mathbb{Q}^{t2}}\left(\int_{0}^{t_0} \mathbb{E}^{\mathbb{Q}}_{s}\left(D_s L_{E}(t_0,t_1,t_2) \right) \nu(s,t_2) ds \right)
 \end{equation}
@@
 D_s L_{E}(t_0,t_1,t_2) &= \frac{H(t_0,t_1)}{\delta_{t_1,t_2}H(t_0,t_2)}\frac{\left(\partial_{x}P_{ois}(t_0,t_1)P_{ois}(t_0,t_2) - \partial_{x}P_{ois}(t_0,t_2) P_{ois}(t_0,t_1) \right)}{P^{2}_{ois}(t_0,t_2)} \beta(s,t_0, x_s, y_s)M(s,t_0) \nonumber \\
-=& \frac{P_{E}(0,t_1)}{\delta_{t_1,t_2} P_{E}(0,t_2)} \left(G(t_0,t_2) - G(t_0,t_1)\right)\beta(s,t_0, x_s, y_s)M(s,t_0).
+\approx& \frac{P_{E}(0,t_1)}{\delta_{t_1,t_2} P_{E}(0,t_2)} \left(G(t_0,t_2) \frac{P_{ois}(0,t_2)}{P_{ois}(0,t_0)} - G(t_0,t_1) \frac{P_{ois}(0,t_1)}{P_{ois}(0,t_0)} \right)\beta(s,t_0, x_s, y_s)M(s,t_0).
 \end{align*}
@@
 \begin{equation}\label{approximation_clarkocone}
-\mathbb{E}_s\left( D_s L_{E}(t_0,t_1,t_2) \right) = \frac{P_{E}(0,t_1)}{\delta_{t_1,t_2} P_{E}(0,t_2)} \left(G(t_0,t_2) - G(t_0,t_1)\right)\beta(s,t_0, x_0, \hat{y}_s)
+\mathbb{E}_s\left( D_s L_{E}(t_0,t_1,t_2) \right) = \frac{P_{E}(0,t_1)}{\delta_{t_1,t_2} P_{E}(0,t_2)} \left(G(t_0,t_2) \frac{P_{ois}(0,t_2)}{P_{ois}(0,t_0)} - G(t_0,t_1) \frac{P_{ois}(0,t_1)}{P_{ois}(0,t_0)}\right)\beta(s,t_0, x_0, \hat{y}_s)
 \end{equation}
@@
 \fboxsep1em
-\fbox{\parbox{350pt}
+\fbox{\parbox{435pt}
 {
 \begin{equation}\label{ca_approximation_futures}
-CA(t,t_0,t_1) \approx \frac{P_{E}(0,t_1)}{\delta_{t_1,t_2} P_{E}(0,t_2)} \left(G(t_0,t_2) - G(t_0,t_1)\right) \int_{0}^{t_0}  \beta(s,t_0, x_0, \hat{y}_s) \nu(s,t_2) ds. 
+CA(t,t_0,t_1) \approx \frac{P_{E}(0,t_1)}{\delta_{t_1,t_2} P_{E}(0,t_2)} \left(G(t_0,t_2) \frac{P_{ois}(0,t_2)}{P_{ois}(0,t_0)} - G(t_0,t_1) \frac{P_{ois}(0,t_1)}{P_{ois}(0,t_0)}\right) \int_{0}^{t_0}  \beta(s,t_0, x_0, \hat{y}_s) \nu(s,t_2) ds.
 \end{equation}
@@
 \begin{align*}
-CA(t,t_0,t_1) & \approx \frac{P_{E}(0,t_1)}{\delta_{t_1,t_2} P_{E}(0,t_2)} \left(\exp(-k(t_1 - t_0)) - \exp(-k(t_1 - t_0)) \right) \sigma^{2} \exp(-k t_0)  \int_{0}^{t_0} \frac{\left(\exp(- k s) - \exp(- k t_2)   \right)}{k} ds.
+CA(t,t_0,t_1) & \approx \frac{\sigma^{2} \exp(-k t_0)  P_{E}(0,t_1)}{\delta_{t_1,t_2} P_{E}(0,t_2)} \left(\frac{1 - \exp(- k t_0)}{k^{2}} - \frac{t_0 \exp(-k t_2)}{k} \right).   
 \end{align*}
@@
 
-$\cdots$
+\begin{figure}[h]
+	\begin{center}
+		\includegraphics[scale=0.3]{Figures/future_convexity.jpg}
+		\caption{Convexity Mc Vs Convexity Malliavin}
+	\end{center}
+\end{figure}
 

### 2022-09-06 ConvexityAdjustment-Lib/ConvexityAdjusmentUnitTests/FraVsFuturesTests.cs

@@ -1,10 +1,8 @@
 using NUnit.Framework;
 using ql = QLNet;
-using System;
 
-namespace ConvexityAdjustment_UnitTest
+namespace ConvexityAdjusmentUnitTests
 {
-
     public class ConvexityAdjustmentHullWhite
     {
         [Test]
@@ -15,8 +13,8 @@ namespace ConvexityAdjustment_UnitTest
             var calendar = new ql.TARGET();
             
             // Hull-White parameters
-            double k = 0.003;
-            double sigma = 0.05;
+            double k = 0.0003;
+            double sigma = 0.0115;
             // double spreadBasis = 0.001;
 
             // Curves
@@ -25,35 +23,85 @@ namespace ConvexityAdjustment_UnitTest
             ql.DayCounter dc = new ql.Actual365Fixed();
             ql.Date startDate = ql.Settings.evaluationDate();
             ql.Handle<ql.YieldTermStructure> curve =  new ql.Handle<ql.YieldTermStructure>(new ql.FlatForward(startDate, quoteRate, dc));
-
+            
             // Model and process
-            ql.HullWhiteProcess process = new ql.HullWhiteProcess(curve, k, sigma);
+            ql.OrnsteinUhlenbeckProcess process = new ql.OrnsteinUhlenbeckProcess(k, sigma, 0.0, 0.0);
             ql.HullWhite model = new ql.HullWhite(curve, k, sigma);
             
-            // Product
-            var t0 = calendar.advance(startDate, 12, ql.TimeUnit.Months);
-            var t1 = calendar.advance(t0, 12, ql.TimeUnit.Months);
-            
             // MC
-            int numberOfSimulations = 10;
+            int numberOfSimulations = 2000000;
             ulong seed = 123545;
-            double deltaTime = 0.1;
-            double length = dc.yearFraction(startDate, t1);
-            int timeSteps = (int)(length / deltaTime);
-            
-            var rsg = (ql.InverseCumulativeRsg<ql.RandomSequenceGenerator<ql.MersenneTwisterUniformRng>, 
-                       ql.InverseCumulativeNormal>)
-                       new ql.PseudoRandom().make_sequence_generator(timeSteps, seed);
+            // double deltaTime = 0.01;
+            // int timeSteps = (int)(length / deltaTime);
+            int timeSteps = 1;
+            var numberOfMonths = 48;
 
[…]

### 2022-09-06 ConvexityAdjustment-Lib/ConvexityAdjustment-Lib/HullWhite.cs

@@ -1,8 +1,35 @@
-﻿namespace ConvexityAdjustment_Lib;
+﻿using ql = QLNet;
 
-public class HullWhite
+namespace ConvexityAdjustment_Lib
 {
-    
-    
-    
+    public static class HullWhite
+    {
+        public static double ConvexityFuture(ql.Handle<ql.YieldTermStructure> curve,  double k, double sigma, double t0, double t1, double t2,
+            double basisSpread)
+        {
+            // df, year fracs, basis,....
+            double df00 = curve.currentLink().discount(t0, true);
+            double df01 = curve.currentLink().discount(t1, true);
+            double df02 = curve.currentLink().discount(t2, true);
+            double delta12 = (t2 - t1);
+            double delta02 = (t2 - t0);
+            double delta01 = (t1 - t0);
+            double h01 = Math.Exp(-basisSpread * delta01);
+            double h02 = Math.Exp(-basisSpread * delta02);
+            
+            // adjustment
+            double g01 = (1.0 - Math.Exp(-k * delta01)) / k;
+            double g02 = (1.0 - Math.Exp(-k * delta02)) / k;
+            
+            double m = sigma * sigma * Math.Exp(-k * t0);
+            double integral = (1.0 - Math.Exp(-k * t0)) / (k * k) - t0 * Math.Exp(-k * t2) / k;
+            double alpha = (h01 * df01) / (df00 * (h02 * df02) * delta12) * ( df02 * g02 - df01 * g01);
+
+            return alpha * m * integral;
+
+
+        }
+
+
+    }
 }

### 2022-09-09 Latex/paper.tex
# convexity adjustment sofr unit test

@@
 \begin{align*} 
-\bar{R}(t,t_0,t_1) &= \mathbb{E}^{\mathbb{Q}^{t_1}}\left( R(t_0,t_1)  \right) \\
-\bar{R}_{avg}(t,t_0,t_1) &= \mathbb{E}^{\mathbb{Q}^{t_1}}\left( R_{avg}(t_0,t_1)  \right).
+\bar{R}(t,t_0,t_1) &= \mathbb{E}^{\mathbb{Q}}\left( R(t_0,t_1)  \right) \\
+\bar{R}_{avg}(t,t_0,t_1) &= \mathbb{E}^{\mathbb{Q}}\left( R_{avg}(t_0,t_1)  \right).
 \end{align*}
@@
 \begin{align*}
-F(t,t_0,t_1)=\mathbb{E}_{t}^{\mathbb{Q}}\left(\exp\left(-\int_{t}^{t_0} r_{ois,u} du \right) R(t_0,t_1) \right) &= \frac{P_{ois}(t,t_0)- P_{ois}(t,t_1)}{t_1 - t_0}, \quad t \in [0,t_0] \\
+F(t,t_0,t_1)=\mathbb{E}_{t}^{\mathbb{Q}}\left(\exp\left(-\int_{t}^{t_0} r_{ois,u} du \right) R(t_0,t_1) \right) &= \frac{\frac{P_{ois}(t,t_0)}{P_{ois}(t,t_1)} - 1}{t_1 - t_0}, \quad t \in [0,t_0] \\
 F(t,t_0,t_1)=\mathbb{E}_{t}^{\mathbb{Q}}\left(\exp\left(-\int_{t}^{t_0} r_{ois,u} du \right) R(t_0,t_1) \right) &= \frac{1}{t_1 - t_0} \left(\frac{\left( \exp\left(\int_{t}^{t_1}r_{ois,u} du\right)\right)}{P_{ois}(t_0,t)}-1\right), \quad  t \in  [t_0, t_1].
@@
 \end{equation}
-to get the convexity adjustment for $R_{avg}(t_0,t_1)$. Now, if we use (\ref{clark-okone}) and (\ref{malliavin_derive_x}, we have the next representation for $R(t_0,t_1)$ 
+to get the convexity adjustment for $R_{avg}(t_0,t_1)$. Now, if we use (\ref{clark-okone}) and (\ref{malliavin_derive_x}), we have the next representation for $R(t_0,t_1)$ 
 \begin{align*}
 R(t_0,t_1) &=   \mathbb{E}^{\mathbb{Q}}\left(R(t_0,t_1) \right) + \int_{0}^{t_1}\mathbb{E}^{\mathbb{Q}}_s\left(D_s R(t_0,t_1) \right) dW^{\mathbb{Q}}_s \\
-&= \mathbb{E}^{\mathbb{Q}}\left(R(t_0,t_1) \right) + \int_{0}^{t_1}\mathbb{E}^{\mathbb{Q}}_s\left(\int_{\max(s,t_0)}^{t1} D_s x_u du \right) dW^{\mathbb{Q}}_s \\
-&= \mathbb{E}^{\mathbb{Q}}\left(R(t_0,t_1) \right) + \int_{0}^{t_1}\int_{\max(s,t_0)}^{t1} \mathbb{E}^{\mathbb{Q}}_s\left(\beta(s,u, x_s, y_s)M(s,u)  \right) du  dW^{\mathbb{Q}}_s\\
-&\approx \mathbb{E}^{\mathbb{Q}}\left(R(t_0,t_1) \right) + \int_{0}^{t_1}\int_{\max(s,t_0)}^{t1} \mathbb{E}^{\mathbb{Q}}_s\left(\beta(s,u, x_s, y_s)M(s,u)  \right) du  dW^{\mathbb{Q}}_s
+&= \mathbb{E}^{\mathbb{Q}}\left(R(t_0,t_1) \right) + \frac{1}{t_1- t_0} \int_{0}^{t_1}\mathbb{E}^{\mathbb{Q}}_s\left(\int_{\max(s,t_0)}^{t1} D_s x_u du \right) dW^{\mathbb{Q}}_s \\
+&= \mathbb{E}^{\mathbb{Q}}\left(R(t_0,t_1) \right) + \frac{1}{t_1- t_0}  \int_{0}^{t_1}\int_{\max(s,t_0)}^{t1} \mathbb{E}^{\mathbb{Q}}_s\left(\beta(s,u, x_s, y_s)M(s,u)  \right) du  dW^{\mathbb{Q}}_s\\
+&\approx \mathbb{E}^{\mathbb{Q}}\left(R(t_0,t_1) \right) +  \frac{1}{t_1- t_0}  \int_{0}^{t_1}\int_{\max(s,t_0)}^{t1} \mathbb{E}^{\mathbb{Q}}_s\left(\beta(s,u, x_s, y_s)M(s,u)  \right) du  dW^{\mathbb{Q}}_s
 \end{align*}
-Then, if we use Girsanov's theorem we have that
+Then, if we use Girsanov's theorem and we apply $\mathbb{E}^{\mathbb{Q}^{t_1}}(\cdot)$ we get
 \begin{align*}
-F(0,t_0,t_1) &\approx \mathbb{E}^{\mathbb{Q}}\left(R(t_0,t_1) \right) - \int_{0}^{t_1}\int_{\max(s,t_0)}^{t1} \mathbb{E}^{\mathbb{Q}}_s\left(\beta(s,u, x_s, y_s)M(s,u)  \right) \nu(s,t_1)  du ds \\
-&\approx \mathbb{E}^{\mathbb{Q}}\left(R(t_0,t_1) \right) - \int_{0}^{t_1}\int_{\max(s,t_0)}^{t1}  \beta(s,u, x_0, \hat{y}_s) \nu(s,t_1)  du ds  
+F(0,t_0,t_1) &\approx \mathbb{E}^{\mathbb{Q}}\left(R(t_0,t_1) \right) - \frac{1}{t_1- t_0}   \int_{0}^{t_1}\int_{\max(s,t_0)}^{t1}  \mathbb{E}^{\mathbb{Q}^{t_1}}\left(\mathbb{E}^{\mathbb{Q}}_s\left(\beta(s,u, x_s, y_s)M(s,u)  \right)  \right) \nu(s,t_1)  du ds \\
+&\approx  \mathbb{E}^{\mathbb{Q}}\left(R(t_0,t_1) \right) -  \frac{1}{t_1- t_0}  \int_{0}^{t_1}\int_{\max(s,t_0)}^{t1}  \beta(s,u, x_0, \hat{y}_s) \nu(s,t_1)  du ds  
 \end{align*}
@@
 \begin{equation}\label{convexity_ois_future}
- \mathbb{E}^{\mathbb{Q}}\left(R(t_0,t_1) \right) \approx F(0,t_0,t_1) + \int_{0}^{t_1}\int_{\max(s,t_0)}^{t1}  \beta(s,u, x_0, \hat{y}_s) \nu(s,t_1)  du ds.
+ \mathbb{E}^{\mathbb{Q}}\left(R(t_0,t_1) \right) \approx F(0,t_0,t_1) + \frac{1}{t_1- t_0}   \int_{0}^{t_1}\int_{\max(s,t_0)}^{t1}  \beta(s,u, x_0, \hat{y}_s)  \nu(s,t_1)  du ds.
 \end{equation}
-Now, if we use (\ref{log_approximation}) with 
+
+\begin{example}
+The same way that in the example (\ref{example_ca_future}), we will suppose a Hull-White model with constan mean reversion $k$ and constant volatility $\sigma$.
+It is easy to show in the case of the Hull-White model
+
+\begin{align*}
+\eta_s &= \sigma \exp(-ks)\\
+\beta(s,u, x_0, \hat{y}_s) &= \sigma \exp(-ku) \\
+\nu(s,t_1) &= \sigma \frac{\exp(-ks) - \exp(-kt_1)}{k}
+\end{align*}
+ Therefore, from the last equalities and (\ref{convexity_ois_future}), we have that
+\begin{equation}
+ \mathbb{E}^{\mathbb{Q}}\left(R(t_0,t_1) \right) \approx F(0,t_0,t_1) + \frac{\sigma^{2}}{t_1- t_0}   \int_{0}^{t_1}\int_{\max(s,t_0)}^{t1}  \exp(-ku)   \frac{\exp(-ks) - \exp(-kt_1)}{k} du ds
+\end{equation}
+\end{example}
+Now, in order to compute the convexity adjustmen for the average case, we  wil use (\ref{log_approximation}) with 
 \begin{align*}
 x &= \mathbb{E}^{\mathbb{Q}}\left(R(t_0,t_1) \right)\\
-\epsilon &= \int_{0}^{t_1}\int_{\max(s,t_0)}^{t1}  \beta(s,u, x_0, \hat{y}_s) \nu(s,t_1)  du  dW^{\mathbb{Q}}_s
+\epsilon &=  \frac{1}{t_1- t_0}  \int_{0}^{t_1}\int_{\max(s,t_0)}^{t1}  \beta(s,u, x_0, \hat{y}_s) \nu(s,t_1)  du  dW^{\mathbb{Q}}_s
 \end{align*} 
@@
 \end{align*}
-
-\begin{example}
-The same way that in the example (\ref{example_ca_future}), we will suppose a Hull-White model with constan mean reversion $k$ and constant volatility $\sigma$. Then
-\end{example}
 

### 2022-09-09 ConvexityAdjustment-Lib/ConvexityAdjusmentUnitTests/SofrCovexity.cs

@@ -1,12 +1,13 @@
-using NUnit.Framework;
+﻿using ConvexityAdjustment_Lib;
 using ql = QLNet;
+using NUnit.Framework;
 
 namespace ConvexityAdjusmentUnitTests
 {
-    public class ConvexityFutureFras
+    public class ConvexityAdjustmentSofr
     {
         [Test]
-        public void HullWhiteFraVsFutureConvexity()
+        public void HullWhiteSofrConvexity()
         {
             
             // settings
@@ -33,7 +34,7 @@ namespace ConvexityAdjusmentUnitTests
             ulong seed = 123545;
             // double deltaTime = 0.01;
             // int timeSteps = (int)(length / deltaTime);
-            int timeSteps = 1;
+            // int timeSteps = 1;
             var numberOfMonths = 48;
 
             List<double> t0s = new List<double>();
@@ -52,55 +53,46 @@ namespace ConvexityAdjusmentUnitTests
                 double delta01 = dc.yearFraction(startDate, t1);
                 double delta02 = dc.yearFraction(startDate, t2);
 
-                List<double> mandatoryPoints = new List<double> { delta00};
-                double length = dc.yearFraction(startDate, t2);
-                
-                var rsg = (ql.InverseCumulativeRsg<ql.RandomSequenceGenerator<ql.MersenneTwisterUniformRng>, 
+                var rsg = (ql.InverseCumulativeRsg<ql.RandomSequenceGenerator<ql.MersenneTwisterUniformRng>,
                         ql.InverseCumulativeNormal>)
-                    new ql.PseudoRandom().make_sequence_generator(timeSteps, seed);
+                    new ql.PseudoRandom().make_sequence_generator(numberOfSimulations, seed);
 
-                ql.PathGenerator<ql.IRNG> generator = new ql.PathGenerator<ql.IRNG>(process, length, timeSteps, rsg, true, mandatoryPoints);
-                double f0t = curve.currentLink().forwardRate(delta00, delta00, ql.Compounding.Simple, ql.Frequency.NoFrequency).rate();
-                double expat = (1.0 - Math.Exp(-k * delta00)) / k ;
-                double mt = (sigma * sigma) / (2.0 * k) * (expat - Math.Exp(-k * delta00) * expat); 
+                double p0t1 = curve.currentLink().discount(delta01, true);
+                double p0t2 = curve.currentLink().discount(delta02, true);
+                double r0t = -Math.Log(p0t2 / p0t1);
                 
                 // Path generator
                 int i;
[…]

### 2022-09-09 ConvexityAdjustment-Lib/ConvexityAdjustment-Lib/HullWhite.cs

@@ -26,9 +26,33 @@ namespace ConvexityAdjustment_Lib
             double alpha = (h01 * df01) / (df00 * (h02 * df02) * delta12) * ( df02 * g02 - df01 * g01);
 
             return alpha * m * integral;
+        }
 
+        
+        public static double GetExpectedIntegralRt(double k, double sigma, double t0, double t1)
+        {
+
+            var alpha = 0.5 * sigma*sigma / k;
+            var part1 = t1 - t0;
+            var part2 = 0.5 * (Math.Exp(-2.0 * k * t0) - Math.Exp(-2.0 * k * t1)) / k;
+            var part3 = (1.0 - Math.Exp(- k * (t1 - t0))) / k;
+            var part4 = (Math.Exp(-k * (t0 + t1)) - Math.Exp(-2.0 * k * t1)) / k;
+
+            return alpha * (part1 - part2 - part3 + part4);
 
         }
+        
+        public static double GetVarianceIntegralRt(double k, double sigma, double t0, double t1)
+        {
+            var alpha = sigma * sigma;
+            var part1 = t1 - t0;
+            var part2 = 0.5 * (1.0 - Math.Exp(-2.0 * k * (t1 - t0))) / k;
+            var part3 = (1.0 - Math.Exp(-k * (t1 - t0))) / k;
+
+            return alpha * (part1 + part2 - 2.0 * part3);
+        }
+
+      
 
 
     }

### 2022-09-09 Latex/paper.tex
# convexity sofr example (not end)

@@
  Therefore, from the last equalities and (\ref{convexity_ois_future}), we have that
-\begin{equation}
- \mathbb{E}^{\mathbb{Q}}\left(R(t_0,t_1) \right) \approx F(0,t_0,t_1) + \frac{\sigma^{2}}{t_1- t_0}   \int_{0}^{t_1}\int_{\max(s,t_0)}^{t1}  \exp(-ku)   \frac{\exp(-ks) - \exp(-kt_1)}{k} du ds
-\end{equation}
+\begin{align*}
+ \mathbb{E}^{\mathbb{Q}}\left(R(t_0,t_1) \right) &\approx F(0,t_0,t_1) + \frac{\sigma^{2}}{t_1- t_0}   \int_{0}^{t_1}\int_{\max(s,t_0)}^{t1}  \exp(-ku)   \frac{\exp(-ks) - \exp(-kt_1)}{k} du ds \\
+ &\approx  F(0,t_0,t_1) + \frac{\sigma^{2}}{k^{2}(t_1- t_0)}   \int_{0}^{t_1} (\exp(-ks) - \exp(-kt_1))(\exp(-k\max(s,t_0)) - \exp(-kt_1))) ds \\
+ &\approx  F(0,t_0,t_1) + \frac{\sigma^{2}}{k^{2}(t_1- t_0)}   \int_{0}^{t_0} (\exp(-ks) - \exp(-kt_1))(\exp(-kt_0) - \exp(-kt_1))) ds  \\
+ &+ \frac{\sigma^{2}}{k^{2}(t_1- t_0)}   \int_{t_0}^{t_1} (\exp(-ks) - \exp(-kt_1))^{2} ds
+\end{align*}
+It is easy to show with a little bit of algebra that
+(tengo que terminarlo)
 \end{example}

### 2022-09-15 ConvexityAdjustment-Lib/ConvexityAdjusmentUnitTests/FraVsFuturesTests.cs
# fix some bugs and modifications in .tex

@@ -1,7 +1,7 @@
 using NUnit.Framework;
 using ql = QLNet;
 
-namespace ConvexityAdjusmentUnitTests
+namespace ConvexityAdjustmentUnitTests
 {
     public class ConvexityFutureFras
     {

### 2022-09-15 ConvexityAdjustment-Lib/ConvexityAdjusmentUnitTests/SofrCovexity.cs

@@ -2,7 +2,7 @@
 using ql = QLNet;
 using NUnit.Framework;
 
-namespace ConvexityAdjusmentUnitTests
+namespace ConvexityAdjustmentUnitTests
 {
     public class ConvexityAdjustmentSofr
     {

### 2022-09-15 Latex/paper.tex

@@
 \section{Preliminaries and notation}\label{sec:Notation}
+Consider a continuous-time economy where zero-coupon bonds are traded for all maturities.
+The price at time $t$ of a zero-coupon bond with maturity $T$ is denoted by $P(t,T)$ where $0\leq t \leq T$.
+Clearly, $P(T,T)=1$.
+We define the compounded instantaneous forward rate forward rate as:
+\begin{eqnarray*}
+f(t,T)= -\partial_{T}\ln P(t,T)
+\end{eqnarray*}
+and the spot interest rates as:
+\begin{eqnarray*}
+r(t)=\lim_{T\longrightarrow t} -\partial_{T}\ln P(t,T).
+\end{eqnarray*}
+We have that the price of a zero-coupon bond is given by
+\begin{eqnarray*}
+P(t,T)=\exp\left(-\int^{T}_{t} f(t,u) du\right).
+\end{eqnarray*}
+
+Before the financial crisis, there was a single curve framework where there was a single curve for discounting and forecasting.
+Since then, the market has adopted a multi-curve approach with two different curves: the discounting curve and the estimation curve chosen based on the maturity of the underlying rate.
+The difference between these two curves is known as basis.
+In this paper, we will assume that the basis are not stochastic.
+Therefore can be directly obtained from the market at time $t=0$.
+In other words, the estimation forward curve $f_{E}(t, T)$ is given by
+\begin{equation}\label{estimation_forward_rate_curve}
+f_{E}(t,T) = f_{ois}(t,T) + s(t,T)
+\end{equation}
+where and $f_{ois}$ is the discount curve and $s(t,T)$ are the basis between the two curves, i.e. $s(t,T)= f_{E}(0,T) - f_{ois}(0,T)$.\\
+
+We will assume that the $f_{ois}$ dynamics follows a single factor Heath-Jarrow-Morton model under the $\mathbb{Q}$-measure.
+Therefore, let $T>0$ a fixed time horizon, $t>0$ the starting time, and $W$ a Brownian motion defined on a complete probability space $(\omega, \mathcal{F}, \mathbb{P})$.
+Then, under the HJM we have the following dynamics
+\begin{align}\label{ois_forward_rate_curve}
+df_{ois}(t,T) &= \sigma(t,T)\nu(t,T)dt + \sigma(t,T)dW^{\mathbb{Q}}_t
+\end{align}
+where $\nu(t,T)=\int_{t}^{T}\sigma(t,s)ds$ and $\sigma(t, T)$ are $\mathcal{F}_{t}$-adapted process that are positive functions for all $t,T$ . In particular, we have that
+\begin{eqnarray*}
+f_{ois}(t,T)= -\partial_{T}\ln P_{ois}(t,T).
+\end{eqnarray*}
+
+In order to have a Markovian representation of the HJM, we will assume that the volatility is separable, i.e.
+\begin{equation}
+\sigma(t,T)= h(t)g(T).
+\end{equation}
+with $g$ a positive time-dependent function a $h$ a non-negative process.
+This version of the HJM is also known as the Cheyette model, \cite{Cheyette}.
+It is easy to show (see \cite{Andreasen01}), that in this case (\ref{ois_forward_rate_curve})
+\begin{equation}
+r_{ois}(t)=f_{ois}(t,t)= f_{ois}(0,t) + x_t,
+\end{equation}  
+where
+\begin{align}\label{short_rate_cheyette}
+dx_t &= (-k_t x_t + y_t)dt + \eta_t dW_t^{\mathbb{Q}} \nonumber \\
+dy_t &= (\eta^{2}_t - 2 k_t y_t) dt ,
+\end{align} 
+with 
+\begin{align*}
+\eta_t &= g(t)h(t,x_t,y_t)  \nonumber \\
+k_t &= - \frac{\partial_t g(t)}{g(t)}.
+\end{align*}
+Then with a little bit of algebra and we use Itô formula we can show the next representation formula for $P_{ois}(t,T)$
+\begin{equation}\label{bond_ois}
+P_{ois}(t,T) = \frac{P_{ois}(0,T)}{P_{ois}(0,t)} \exp\left(-G(t,T)x_t - \frac{1}{2} G^{2}(t,T)y_t \right)
+\end{equation}
+where $G(t,T) = \int_{t}^{T} \exp\left(-\int_{t}^{u} k_s ds \right) du$. We must observe, that under the representation (\ref{estimation_forward_rate_curve}) we have that
+\begin{equation}\label{bond_forward}
+P_{E}(t,T)=H(t,T)P_{ois}(t,T)
+\end{equation}
+where $H(t,T)=\exp\left(-\int_{t}^{T}s(t,u) du \right)$.
 
@@
 $\cdots$  tengo que pensar que poner aqui como intro
-\subsection{HJM framework}
-In order to compute the convexity adjustment, we need to assume some dynamic on the estimation curve and discount curve.
-In order to avoid problems with a stochastic basis between both curves, we will suppose a not stochastic basis i.e, we will suppose the next representation for the forward rate curve $f_{E}(t, T)$
-\begin{equation}\label{estimation_forward_rate_curve}
-f_{E}(t,T) = f_{ois}(t,T) + s(t,T).
-\end{equation}
-Where $s(t,T)= f_{E}(0,T) - f_{ois}(0,T)$ i.e we suppose the basis between curves that we get from the market in time $t=0$.
-On other hand, $f_ois(t, T)$ is the OIS forward rate curve and whose dynamic under the $\mathbb{Q}$-measure will be a single factor HJM dynamic i.e
-\begin{align}\label{ois_forward_rate_curve}
-df_{ois}(t,T) &= \sigma(t,T)\nu(t,T)dt + \sigma(t,T)dW^{\mathbb{Q}}_t  \\
-f_{ois}(0,T) &= -\partial_T \log\left(P_{ois}(0,T)\right) \nonumber
-\end{align}
-where $\nu(t,T)=\int_{t}^{T}\sigma(t,s)ds$ and $\sigma(t, T)$ is a positive function for all $t,T > 0$ .
-In order to have a Markovian representation of the HJM model, It is usual to assume that volatility function is separable, i.e
-\begin{equation}
-\sigma(t,T)= h(t)g(T).
-\end{equation}
-with g is a time-dependent positive function and h is a general non-negative process. It is easy to show (see Andreasen 2001), that in this case (\ref{ois_forward_rate_curve})
-\begin{equation}
-r_{ois}(t)=f_{ois}(t,t)= f_{ois}(0,t) + x_t,
-\end{equation}  
-where
-\begin{align}\label{short_rate_cheyette}
-dx_t &= (-k_t x_t + y_t)dt + \eta_t dW_t^{\mathbb{Q}} \nonumber \\
-dy_t &= (\eta^{2}_t - 2 k_t y_t) dt ,
-\end{align} 
-with 
-\begin{align*}
-\eta_t &= g(t)h(t,x_t,y_t)  \nonumber \\
-k_t &= - \frac{\partial_t g(t)}{g(t)}
-\end{align*}
-Then with a little bit of algebra and we use Itô formula we can show the next representation formula for $P_{ois}(t,T)$
-\begin{equation}\label{bond_ois}
-P_{ois}(t,T) = \frac{P_{ois}(0,T)}{P_{ois}(0,t)} \exp\left(-G(t,T)x_t - \frac{1}{2} G^{2}(t,T)y_t \right)
-\end{equation}
-where $G(t,T) = \int_{t}^{T} \exp\left(-\int_{t}^{u} k_s ds \right) du$. We must observe, that under the representation (\ref{estimation_forward_rate_curve}) we have that
-\begin{equation}\label{bond_forward}
-P_{E}(t,T)=H(t,T)P_{ois}(t,T)
-\end{equation}
-where $H(t,T)=\exp\left(-\int_{t}^{T}s(t,u) du \right)$.
 

### 2022-09-15 Latex/paper.tex
# convexity adjustment for fra in arrears

@@
 \begin{align*}
-CA(t,t_0,t_1) & \approx \frac{\sigma^{2} \exp(-k t_0)  P_{E}(0,t_1)}{\delta_{t_1,t_2} P_{E}(0,t_2)} \left(\frac{1 - \exp(- k t_0)}{k^{2}} - \frac{t_0 \exp(-k t_2)}{k} \right).   
+CA(t_0,t_1) & \approx \frac{\sigma^{2} \exp(-k t_0)  P_{E}(0,t_1)}{\delta_{t_1,t_2} P_{E}(0,t_2)} \left(\frac{1 - \exp(- k t_0)}{k^{2}} - \frac{t_0 \exp(-k t_2)}{k} \right).   
 \end{align*}
@@
 \end{figure}
+
+\newpage
 
@@
 \subsection{FRAs in arrears}
+The cash flows associated to a FRAs in arrears is $L_{E}(t_1,t_1,t_2)$ in $t_1$. Therefore the payment will be
+\begin{equation}
+P_{E}(0,t_1)\mathbb{E}^{\mathbb{Q}^{t_1}}\left( L_{E}(t_1,t_1,t_2\right).
+\end{equation}
+The expected value is clearly taken with respect to the wrong martingale, because $L_{E}(t,t_1,t_2)$ is martingale under the measure $\mathbb{Q}^{t_2}$.
+In order to calculate, the convexity adjustment we will use as before Clark-Ocone to get a representation for $L_{E}(t_1,t_1,t_2)$ i.e
+\begin{equation}\label{general_convexity_fras}
+L_{E}(t_1,t_1,t_2) = \mathbb{E}^{\mathbb{Q}^{t_2}}\left(L_{E}(t_1,t_1,t_2) \right) + \int_{0}^{t_1} \mathbb{E}^{\mathbb{Q}^{t_2}}\left(D_s L_{E}(t_1,t_1,t_2) \right) dW^{\mathbb{Q}^{t_2}}_{s}
+\end{equation}
+The if we suppose the HJM dynamic (\ref{estimation_forward_rate_curve})and we take $\mathbb{E}^{^{\mathbb{Q}^{t_1}}}(\cdot)$ we get
+\begin{align*}
+\mathbb{E}^{\mathbb{Q}^{t_1}}\left(L_{E}(t_1,t_1,t_2) \right) &= L_{E}(0,t_1,t_2) + \mathbb{E}\left( \int_{0}^{t_1} \mathbb{E}^{\mathbb{Q}^{t_2}}\left(D_s L_{E}(t_1,t_1,t_2) \right) dW^{\mathbb{Q}^{t_2}}_{s}\right)\\
+&= L_{E}(0,t_1,t_2) + \mathbb{E}\left( \int_{0}^{t_1} \mathbb{E}^{\mathbb{Q}^{t_2}}\left(D_s L_{E}(t_1,t_1,t_2) \right) (\nu(s,t_2)-\nu(s,t_1)) ds \right)
+\end{align*}
+Where we have used that 
+\begin{equation*}
+dW^{\mathbb{Q}^{t_2}}_s = dW^{\mathbb{Q}^{t_1}}_s + (\nu(s,t_2) - \nu(s,t_1)) ds 
+\end{equation*}
+Now from (\ref{malliavin_derive_x}) we have that 
+\begin{equation*}
+D_s L(t_1,t_1,t_2) = \frac{G(t_1,t_2)}{\delta_{t_1,t_2}P_{E}(t_1,t_2)} D_s x_{t_1} \approx \frac{G(t_1,t_2)}{\delta_{t_1,t_2}P_{E}(0,t_1,t_2)} \beta(s,t_1, x_0, \hat{y}_s)M(s,t_1)
+\end{equation*}
+Therefore, if we define 
+\begin{equation*}
+CA(t_0,t_1) = \mathbb{E}^{\mathbb{Q}^{t_1}}\left( L_{E}\left(t_1,t_1,t_2\right)\right) - L_{E}\left(0,t_1,t_2\right)
+\end{equation*}
+and we use the last approximation and (\ref{general_convexity_fras}), we can get the next approximation for $CA(t_0,t_1)$ 
+\hspace{2cm}
+\fboxsep1em
+\fbox{\parbox{435pt}
+{
+\begin{equation}\label{ca_approximations_fra_arrears}
+CA(t_0,t_1) \approx  \frac{G(t_1,t_2)}{\delta_{t_1,t_2}P_{E}(0,t_1,t_2)} \int_{0}^{t_1} \beta(s,t_1, x_0, \hat{y}_s) (\nu(s,t_2) - \nu(s,t_1)) ds.
+\end{equation}
+}}
+\begin{example}
+To check how works the last approximation.
+We will restrict a Hull-White model with mean reversion and volatility constant.
+We will use are $\sigma=0.1$, $k=0.007$ for our model.
+The analytical approximation that we get from (\ref{ca_approximation_futures}) is
+\begin{equation*}
+CA(t_0,t_1) \approx \frac{G(t_1,t_2)}{\delta_{t_1,t_2}P_{E}(0,t_1,t_2)}  \frac{\sigma^{2}}{k} \int_{0}^{t_1} \exp(- k(t_1 + u)) -   \exp(- k(t_2 + u)) du 
+\end{equation*}
+We have checked the last approximation using MC method to compute the value of a FRA in arrears. We will show the result of the simulation in the next figure
+
+\begin{figure}[h]
+	\begin{center}
+		\includegraphics[scale=0.3]{Figures/fra_convexity.jpg}
+		\caption{Convexity Mc Vs Convexity Malliavin}
+	\end{center}
+\end{figure}
+
+\end{example}
+
+\newpage
 

### 2022-09-15 ConvexityAdjustment-Lib/ConvexityAdjusmentUnitTests/FraInArrears.cs

@@ -1,20 +1,21 @@
+﻿using ConvexityAdjustment_Lib;
 using NUnit.Framework;
 using ql = QLNet;
 
 namespace ConvexityAdjustmentUnitTests
 {
-    public class ConvexityFutureFras
+    public class ConvexityFraInArrears
     {
         [Test]
-        public void HullWhiteFraVsFutureConvexity()
+        public void HullWhiteFraInArrears()
         {
             
             // settings
             var calendar = new ql.TARGET();
             
             // Hull-White parameters
-            double k = 0.0003;
-            double sigma = 0.0115;
+            double k = 0.0007;
+            double sigma = 0.01;
             // double spreadBasis = 0.001;
 
             // Curves
@@ -31,8 +32,6 @@ namespace ConvexityAdjustmentUnitTests
             // MC
             int numberOfSimulations = 2000000;
             ulong seed = 123545;
-            // double deltaTime = 0.01;
-            // int timeSteps = (int)(length / deltaTime);
             int timeSteps = 1;
             var numberOfMonths = 48;
 
@@ -43,16 +42,14 @@ namespace ConvexityAdjustmentUnitTests
             for (var j = 1; j < numberOfMonths + 1; j++)
             {
                 // Product
-                var t0 = calendar.advance(startDate, j, ql.TimeUnit.Months);
                 var t1 = calendar.advance(startDate, j, ql.TimeUnit.Months);
                 var t2 = calendar.advance(t1, 12, ql.TimeUnit.Months);
                  
                 // Delta times
-                double delta00 = dc.yearFraction(startDate, t0);
                 double delta01 = dc.yearFraction(startDate, t1);
                 double delta02 = dc.yearFraction(startDate, t2);
 
-                List<double> mandatoryPoints = new List<double> { delta00};
+                List<double> mandatoryPoints = new List<double> { delta01};
                 double length = dc.yearFraction(startDate, t2);
                 
                 var rsg = (ql.InverseCumulativeRsg<ql.RandomSequenceGenerator<ql.MersenneTwisterUniformRng>, 
@@ -60,9 +57,12 @@ namespace ConvexityAdjustmentUnitTests
                     new ql.PseudoRandom().make_sequence_generator(timeSteps, seed);
 
                 ql.PathGenerator<ql.IRNG> generator = new ql.PathGenerator<ql.IRNG>(process, length, timeSteps, rsg, true, mandatoryPoints);
[…]

### 2022-09-15 ConvexityAdjustment-Lib/ConvexityAdjustment-Lib/HullWhite.cs

@@ -4,6 +4,26 @@ namespace ConvexityAdjustment_Lib
 {
     public static class HullWhite
     {
+
+        public static double ConvexityFraInArrears(ql.Handle<ql.YieldTermStructure> curve, double k, double sigma,
+            double t1, double t2,
+            double basisSpread)
+        {
+            // df, year fracs, basis,....
+            double df01 = curve.currentLink().discount(t1, true);
+            double df02 = curve.currentLink().discount(t2, true);
+            double delta12 = (t2 - t1);
+            double h01 = Math.Exp(-basisSpread * t1);
+            double h02 = Math.Exp(-basisSpread * t2);
+            double df12 = (df02 * h02) / (df01 * h01);
+
+            double m = sigma * sigma / (delta12 * df12 * k);
+            double integral = Beta(t1, 2.0 * t1, k) - Beta(t2, t1 + t2, k);
+
+            return m * integral;
+
+        }
+
         public static double ConvexityFuture(ql.Handle<ql.YieldTermStructure> curve,  double k, double sigma, double t0, double t1, double t2,
             double basisSpread)
         {
@@ -21,7 +41,7 @@ namespace ConvexityAdjustment_Lib
             double g01 = (1.0 - Math.Exp(-k * delta01)) / k;
             double g02 = (1.0 - Math.Exp(-k * delta02)) / k;
             
-            double m = sigma * sigma * Math.Exp(-k * t0);
+            double m = Beta(0.0, delta12, k) * sigma * sigma * Math.Exp(-k * t0);
             double integral = (1.0 - Math.Exp(-k * t0)) / (k * k) - t0 * Math.Exp(-k * t2) / k;
             double alpha = (h01 * df01) / (df00 * (h02 * df02) * delta12) * ( df02 * g02 - df01 * g01);
 
@@ -52,8 +72,16 @@ namespace ConvexityAdjustment_Lib
             return alpha * (part1 + part2 - 2.0 * part3);
         }
 
-      
+        public static double Beta(double t0, double t1, double alpha)
+        {
+            double delta = t1 - t0;
+            if (ql.Utils.close(alpha * delta, 0.0))
+            {
+                return Math.Exp(-alpha * t0) * delta;
+            }
 
+            return (Math.Exp(-alpha * t0) - Math.Exp(-alpha * t1)) / alpha;
+        }
 
     }
 }

### 2022-09-19 Latex/paper.tex
# Fix some calculations in ois convexity

@@
 \begin{align*}
-R(t_0,t_1) &= \frac{\mathbb{E}_t^{Q}\left(\exp\left(\int_{t_0}^{t_1}r_{ois,u} du\right)\right) - 1}{t_1 - t_0} \\
+R(t_0,t_1) &= \frac{\exp\left(\int_{t_0}^{t_1}r_{ois,u} du \right) - 1}{t_1 - t_0} \\
 R_{avg}(t_0,t_1) &= \frac{\int_{t_0}^{t_1}r_{ois,u} du}{t_1 - t_0}.
@@
 The second observation, is that under the dyam we must do is that
+\begin{equation}\label{R_ois_avg}
+\mathbb{E}_{t}^{\mathbb{Q}}\left(R_{avg}(t_0,t_1) \right) = \mathbb{E}_t^{\mathbb{Q}}\left( \frac{\log\left(1+ \delta_{t_0,t_1} R(t_0,t_1) \right)}{\delta_{t_0,t_1}} \right)  
+\end{equation}
+In order to compute $\mathbb{E}^{\mathbb{Q}}\left(R(t_0,t_1\right)$, we will define
 \begin{equation*}
-\mathbb{E}_{t}^{\mathbb{Q}}\left(R_{avg}(t_0,t_1) \right) = \mathbb{E}_t^{\mathbb{Q}}\left( \frac{\log\left(1+(t_1 - t_0)R(t_0,t_1) \right)}{t_1 - t_0} \right).  
+I(t_0,t_1) = \int_{t_0}^{t_1} r_s ds
 \end{equation*}
-Then, we have two convexity effects, one of them is the convexity of $\log(1+x)$ and the other comes from $R(t_0,t_1)$.
-Therefore, we need only to compute convexity adjusment for $R(t_0,t_1)$ and apply
-\begin{equation}\label{log_approximation}
-\frac{\log(1 + (t_1 - t_0)(x +\epsilon))}{(t_1 - t_0)} \approx \log(1 + (t_1 - t_0)x) + \frac{1}{1 + (t_1 - t_0)x}   \epsilon - \frac{1}{(1 + (t_1 - t_0)x)^{2}} \epsilon^{2}
+then for $t < t_0$ from (\ref{clark-okone}) and (\ref{malliavin_derive_x}), we have the next representation for $I(t_0,t_1)$
+\begin{align}\label{apprx_I_t0_t1}
+I(t_0,t_1) &= \mathbb{E}^{\mathbb{Q}}\left(I(t_0,t_1)\right) + \int_{0}^{t_1}\int_{\max(s, t_{0})}^{t_1}  \mathbb{E}_s^{\mathbb{Q}}\left(\beta(s,u,x_s,y_s) M(s,u) \right) du dW_s^{\mathbb{Q}} \nonumber \\
+&\approx \mathbb{E}^{\mathbb{Q}}\left(I(t_0,t_1)\right) + \int_{0}^{t_1}\int_{\max(s, t_{0})}^{t_1} \beta(s,u,x_0,\hat{y}_s) du dW_s^{\mathbb{Q}}\nonumber \\
+&= \mathbb{E}^{\mathbb{Q}}\left(I(t_0,t_1)\right) + \int_{0}^{t_1} g(s)h(s,x_0,\hat{y}_s)\int_{\max(s, t_{0})}^{t_1} \exp\left( -\int_{s}^{u} k_{s^{\prime}} ds^{\prime}\right) du dW_s^{\mathbb{Q}}.
+\end{align}
+Therefore, we can get the next approximation
+\begin{align*}
+1 + \delta_{t_0,t_1}\mathbb{E}^{\mathbb{Q}^{t_1}}\left(R(t_0,t_1)\right) &= \mathbb{E}^{\mathbb{Q}^{t_1}}\left( \exp(I(t_0,t_1)) \right)\\
+&= \exp\left(\mathbb{E}^{\mathbb{Q}}\left(I(t_0,t_1)\right)\right)  \mathbb{E}^{\mathbb{Q}^{t_1}}\left(\exp\left(\int_{0}^{t_1} \Gamma(s,t_0,t_1)dW_s^{\mathbb{Q}}\right)\right)
+\end{align*}
+where $\Gamma(s,t_0,t_1)= g(s)h(s,x_0,\hat{y}_s)\int_{\max(s, t_{0})}^{t_1} \exp\left( -\int_{s}^{u} k_{s^{\prime}} ds^{\prime}\right)du$. Now, from the Girsanov's theorem we get that
+\begin{equation*}
+1 + \delta_{t_0,t_1}\mathbb{E}^{\mathbb{Q}}\left(R(t_0,t_1)\right) \approx \exp\left(\mathbb{E}^{\mathbb{Q}}\left(I(t_0,t_1)\right)\right)\exp\left(\int_{0}^{t_1}\frac{\Gamma^{2}(s,t_0,t_1)}{2} ds\right)
+\end{equation*}
+Therefore we have that
+\begin{equation}\label{convexity_ois_future}
+\mathbb{E}^{\mathbb{Q}}\left(R(t_0,t_1)\right) \approx \frac{\exp\left(\mathbb{E}^{\mathbb{Q}}\left(I(t_0,t_1)\right)\right)\exp\left(\int_{0}^{t_1}\frac{\Gamma^{2}(s,t_0,t_1)}{2} ds\right) - 1}{\delta_{t_0,t_1}}
 \end{equation}
-to get the convexity adjustment for $R_{avg}(t_0,t_1)$. Now, if we use (\ref{clark-okone}) and (\ref{malliavin_derive_x}), we have the next representation for $R(t_0,t_1)$ 
+We must note, that from (\ref{apprx_I_t0_t1}) and (\ref{R_ois_avg}) we can get an approximation for $R_{avg}(t_0,t_1)$
+\begin{equation*}
+R_{avg}(t_0,t_1) = \frac{\mathbb{E}^{\mathbb{Q}}\left(I(t_0,t_1)\right) }{\delta_{t_0,t_1}} \approx \frac{\log\left(1+\delta_{t_0,t_1}  \mathbb{E}^{\mathbb{Q}}\left(R(t_0,t_1)\right) \right)}{\delta_{t_0,t_1}} + \frac{\int_{0}^{t_1}\Gamma^{2}(s,t_0,t_1) ds}{2\delta_{t_0,t_1}}
+\end{equation*}
+Therefore, since $\log(1+x)\approx x$ we have that
+\begin{equation*}
+R_{avg}(t_0,t_1) \approx  \mathbb{E}^{\mathbb{Q}}\left(R(t_0,t_1)\right) + \frac{\int_{0}^{t_1}\Gamma^{2}(s,t_0,t_1) ds}{2\delta_{t_0,t_1}}.
+\end{equation*}
+
+\begin{remark}
+We must observe that for the case $t_0 < t < t_1$ we can compute the convexity adjusment in a similar way when $t < t_0$, but in this case we have to define
+\begin{equation*}
+I(t,t_1)=\int_{t}^{t_1} r_s ds
+\end{equation*}
+and 
 \begin{align*}
-R(t_0,t_1) &=   \mathbb{E}^{\mathbb{Q}}\left(R(t_0,t_1) \right) + \int_{0}^{t_1}\mathbb{E}^{\mathbb{Q}}_s\left(D_s R(t_0,t_1) \right) dW^{\mathbb{Q}}_s \\
-&= \mathbb{E}^{\mathbb{Q}}\left(R(t_0,t_1) \right) + \frac{1}{t_1- t_0} \int_{0}^{t_1}\mathbb{E}^{\mathbb{Q}}_s\left(\int_{\max(s,t_0)}^{t1} D_s x_u du \right) dW^{\mathbb{Q}}_s \\
-&= \mathbb{E}^{\mathbb{Q}}\left(R(t_0,t_1) \right) + \frac{1}{t_1- t_0}  \int_{0}^{t_1}\int_{\max(s,t_0)}^{t1} \mathbb{E}^{\mathbb{Q}}_s\left(\beta(s,u, x_s, y_s)M(s,u)  \right) du  dW^{\mathbb{Q}}_s\\
-&\approx \mathbb{E}^{\mathbb{Q}}\left(R(t_0,t_1) \right) +  \frac{1}{t_1- t_0}  \int_{0}^{t_1}\int_{\max(s,t_0)}^{t1} \mathbb{E}^{\mathbb{Q}}_s\left(\beta(s,u, x_s, y_s)M(s,u)  \right) du  dW^{\mathbb{Q}}_s
+R(t_0,t_1) &= \frac{\frac{\exp(\int_{t}^{t_1} r_{ois,s} ds )}{P_{ois}(t_0,t)} - 1}{t_1 - t_0} \\
+R_{avg}(t_0,t_1) &= \frac{\int_{t_0}^{t} r_{ois,s} ds}{t_1-t_0} +  \frac{\int_{t}^{t_1} r_{ois,s} ds}{t_1-t_0}.   
 \end{align*}
-Then, if we use Girsanov's theorem and we apply $\mathbb{E}^{\mathbb{Q}^{t_1}}(\cdot)$ we get
-\begin{align*}
-F(0,t_0,t_1) &\approx \mathbb{E}^{\mathbb{Q}}\left(R(t_0,t_1) \right) - \frac{1}{t_1- t_0}   \int_{0}^{t_1}\int_{\max(s,t_0)}^{t1}  \mathbb{E}^{\mathbb{Q}^{t_1}}\left(\mathbb{E}^{\mathbb{Q}}_s\left(\beta(s,u, x_s, y_s)M(s,u)  \right)  \right) \nu(s,t_1)  du ds \\
-&\approx  \mathbb{E}^{\mathbb{Q}}\left(R(t_0,t_1) \right) -  \frac{1}{t_1- t_0}  \int_{0}^{t_1}\int_{\max(s,t_0)}^{t1}  \beta(s,u, x_0, \hat{y}_s) \nu(s,t_1)  du ds  
-\end{align*}
-And therefore
-\begin{equation}\label{convexity_ois_future}
- \mathbb{E}^{\mathbb{Q}}\left(R(t_0,t_1) \right) \approx F(0,t_0,t_1) + \frac{1}{t_1- t_0}   \int_{0}^{t_1}\int_{\max(s,t_0)}^{t1}  \beta(s,u, x_0, \hat{y}_s)  \nu(s,t_1)  du ds.
-\end{equation}
+\end{remark}
 
 \begin{example}
-The same way that in the example (\ref{example_ca_future}), we will suppose a Hull-White model with constan mean reversion $k$ and constant volatility $\sigma$.
+The same way that in the example (\ref{example_ca_future}), we will suppose a Hull-White model with constan mean reversion $k=0.003$ and volatility $\sigma=0.01$.
 It is easy to show in the case of the Hull-White model
-
 \begin{align*}
@@
 \beta(s,u, x_0, \hat{y}_s) &= \sigma \exp(-ku) \\
-\nu(s,t_1) &= \sigma \frac{\exp(-ks) - \exp(-kt_1)}{k}
+\nu(s,t_1) &= \sigma \frac{\exp(-ks) - \exp(-kt_1)}{k}\\
+\Gamma(s,t_0,t_1) &= \frac{\exp(-ks)\sigma}{k}\left(\exp(-k(\max(s,t_0) - s)) - \exp(-k(t_1-t_0))\right)\\
+\mathbb{E}^{\mathbb{Q}}\left(I(t_0,t_1)\right)&=-\log\left(\frac{P_{ois}(0,t_1)}{P_{ois}(0,t_0)}\right) + \frac{\sigma^{2}}{2k^{2}}\left(\delta_{t_0,t_1} - 2 \frac{\exp(-kt_0) - \exp(-kt_1)}{k} + \frac{\exp(-2kt_0) - \exp(-2kt_1)}{k}  \right).
 \end{align*}
- Therefore, from the last equalities and (\ref{convexity_ois_future}), we have that
+Therefore we have that
 \begin{align*}
- \mathbb{E}^{\mathbb{Q}}\left(R(t_0,t_1) \right) &\approx F(0,t_0,t_1) + \frac{\sigma^{2}}{t_1- t_0}   \int_{0}^{t_1}\int_{\max(s,t_0)}^{t1}  \exp(-ku)   \frac{\exp(-ks) - \exp(-kt_1)}{k} du ds \\
- &\approx  F(0,t_0,t_1) + \frac{\sigma^{2}}{k^{2}(t_1- t_0)}   \int_{0}^{t_1} (\exp(-ks) - \exp(-kt_1))(\exp(-k\max(s,t_0)) - \exp(-kt_1))) ds \\
- &\approx  F(0,t_0,t_1) + \frac{\sigma^{2}}{k^{2}(t_1- t_0)}   \int_{0}^{t_0} (\exp(-ks) - \exp(-kt_1))(\exp(-kt_0) - \exp(-kt_1))) ds  \\
- &+ \frac{\sigma^{2}}{k^{2}(t_1- t_0)}   \int_{t_0}^{t_1} (\exp(-ks) - \exp(-kt_1))^{2} ds
+\frac{\int_{0}^{t_1} \Gamma^{2}(s,t_0,t_1) ds}{2} &= \frac{\sigma^{2}}{2k^{2}} \int_{0}^{t_1}  \exp(-2ks)\left(\exp(-k(\max(s,t_0) - s)) - \exp(-k\delta_{t_0,t_1})\right)^{2} ds \\
+&= \frac{\sigma^{2}}{2k^{2}} \int_{0}^{t_0} \exp(-2ks)\left(\exp(-k(t_0 - s)) - \exp(-k\delta_{t_0,t_1})\right)^{2} ds\\
+&+ \frac{\sigma^{2}}{2k^{2}} \int_{t_0}^{t_1} \exp(-2ks)\left(1 - \exp(-k\delta_{t_0,t_1})\right)^{2} ds\\
+&= \frac{\sigma^{2}}{2k^{2}} \left(\delta_{t_0,t_1}+ \exp(-2k\delta_{t_0,t_1}) \frac{\exp(-2kt_0)- \exp(-2kt_1)}{2k} - 2\exp(-kt_1) \frac{\exp(-kt_0)- \exp(-kt_1)}{k}  \right) \\
+&+ \frac{\sigma^{2}}{2k^{2}} \left(1 - \exp(-k\delta_{t_0,t_1})\right)^{2} \left(\frac{\exp(-2kt_0) - \exp(-2kt_1)}{2k}\right)
 \end{align*}
-It is easy to show with a little bit of algebra that
-(tengo que terminarlo)
+
 \end{example}
-Now, in order to compute the convexity adjustmen for the average case, we  wil use (\ref{log_approximation}) with 
-\begin{align*}
-x &= \mathbb{E}^{\mathbb{Q}}\left(R(t_0,t_1) \right)\\
-\epsilon &=  \frac{1}{t_1- t_0}  \int_{0}^{t_1}\int_{\max(s,t_0)}^{t1}  \beta(s,u, x_0, \hat{y}_s) \nu(s,t_1)  du  dW^{\mathbb{Q}}_s
-\end{align*} 
-we can calculate the adjusment for $R_{avg}(t_0,t1)$
-\begin{align*}
-\mathbb{E}^{\mathbb{Q}}\left(R_{avg}(t_0,t_1) \right) &\approx \frac{\log\left(1+(t_1 - t_0)\mathbb{E}^{\mathbb{Q}}\left(R(t_0,t_1)\right)\right)}{t_1 - t_0} \\
-&-\frac{1}{2(1 + (t_1 - t_0)\mathbb{E}^{\mathbb{Q}}\left(R(t_0,t_1)\right))^{2}} \int_{0}^{t_1}\left(\int_{\max(s,t_0)}^{t1}  \beta(s,u, x_0, \hat{y}_s)  du\right)^{2} ds
-\end{align*}
 

### 2022-09-19 ConvexityAdjustment-Lib/ConvexityAdjusmentUnitTests/SofrCovexity.cs

@@ -87,12 +87,17 @@ namespace ConvexityAdjustmentUnitTests
                 var intervalConfidence = new double[]
                     { mean - stdMc / Math.Sqrt(numberOfSimulations), mean + stdMc / Math.Sqrt(numberOfSimulations) };
                 
-                var convexityMc = mcFuturePrice - curve.currentLink()
+                var forward =  curve.currentLink()
                     .forwardRate(delta01, delta02, ql.Compounding.Simple, ql.Frequency.NoFrequency).rate();
+
+                var convexityMc = mcFuturePrice - forward;
+
+                var convexityMalliavin = HullWhite.ConvexityOis(curve, k, sigma, delta01, delta02) - forward;
                 
                 // outputs
                 t0s.Add(delta00);
                 caMc.Add(convexityMc);
+                caMalliavin.Add(convexityMalliavin);
             }
            
         }

### 2022-09-19 ConvexityAdjustment-Lib/ConvexityAdjustment-Lib/HullWhite.cs

@@ -4,7 +4,8 @@ namespace ConvexityAdjustment_Lib
 {
     public static class HullWhite
     {
-
+        
+        #region Convexity
         public static double ConvexityFraInArrears(ql.Handle<ql.YieldTermStructure> curve, double k, double sigma,
             double t1, double t2,
             double basisSpread)
@@ -48,17 +49,33 @@ namespace ConvexityAdjustment_Lib
             return alpha * m * integral;
         }
 
+        public static double ConvexityOis(ql.Handle<ql.YieldTermStructure> curve, double k, double sigma, double t1,
+            double t2)
+        {
+            double b1 = Beta(t1, t2, k);
+            double b2 = Beta(t1, t2, 2.0 * k);
+            double delta12 = t2 - t1;
+
+            double df1 = curve.link.discount(t1, true);
+            double df2 = curve.link.discount(t2, true);
+            double m = 0.5 * Math.Pow(sigma / k, 2.0);
+            double expected = -Math.Log(df2 / df1) + m * (delta12 - 2.0 * b1 + b2);
+            double i1 = m * (delta12 * Math.Exp(-2.0 * k * t1) + Math.Exp(-2.0 * k * delta12) * b2 - 2.0 * Math.Exp(-k*t2) * b1);
+            double i2 = m * Math.Pow(1.0 - Math.Exp(-k * delta12), 2.0) * b2;
+
+            return (Math.Exp(expected + i1 + i2) - 1.0) / delta12;
+        }
+
+        #endregion
+
+        #region Tools
         
         public static double GetExpectedIntegralRt(double k, double sigma, double t0, double t1)
         {
 
-            var alpha = 0.5 * sigma*sigma / k;
-            var part1 = t1 - t0;
-            var part2 = 0.5 * (Math.Exp(-2.0 * k * t0) - Math.Exp(-2.0 * k * t1)) / k;
-            var part3 = (1.0 - Math.Exp(- k * (t1 - t0))) / k;
-            var part4 = (Math.Exp(-k * (t0 + t1)) - Math.Exp(-2.0 * k * t1)) / k;
-
-            return alpha * (part1 - part2 - part3 + part4);
+            var m = 0.5 * Math.Pow(sigma / k, 2.0);
+            var delta = t1 - t0;
+            return m * (delta - 2.0 * Beta(t0, t1, k) + Beta(t0, t1, 2.0 * k));
 
         }
         
[…]

### 2022-09-19 Latex/paper.tex
# Fix bug in ois convexity

@@
 \nu(s,t_1) &= \sigma \frac{\exp(-ks) - \exp(-kt_1)}{k}\\
-\Gamma(s,t_0,t_1) &= \frac{\exp(-ks)\sigma}{k}\left(\exp(-k(\max(s,t_0) - s)) - \exp(-k(t_1-t_0))\right)\\
+\Gamma(s,t_0,t_1) &= \frac{\sigma \exp(-ks)}{k}\left(\exp(-k(\max(s,t_0) - s)) - \exp(-k(t_1-s))\right)\\
 \mathbb{E}^{\mathbb{Q}}\left(I(t_0,t_1)\right)&=-\log\left(\frac{P_{ois}(0,t_1)}{P_{ois}(0,t_0)}\right) + \frac{\sigma^{2}}{2k^{2}}\left(\delta_{t_0,t_1} - 2 \frac{\exp(-kt_0) - \exp(-kt_1)}{k} + \frac{\exp(-2kt_0) - \exp(-2kt_1)}{k}  \right).
@@
 \begin{align*}
-\frac{\int_{0}^{t_1} \Gamma^{2}(s,t_0,t_1) ds}{2} &= \frac{\sigma^{2}}{2k^{2}} \int_{0}^{t_1}  \exp(-2ks)\left(\exp(-k(\max(s,t_0) - s)) - \exp(-k\delta_{t_0,t_1})\right)^{2} ds \\
-&= \frac{\sigma^{2}}{2k^{2}} \int_{0}^{t_0} \exp(-2ks)\left(\exp(-k(t_0 - s)) - \exp(-k\delta_{t_0,t_1})\right)^{2} ds\\
+\frac{\int_{0}^{t_1} \Gamma^{2}(s,t_0,t_1) ds}{2} &= \frac{\sigma^{2}}{2k^{2}} \int_{0}^{t_1}  \exp(-2ks)\left(\exp(-k(\max(s,t_0) - s)) - \exp(-k(t_1 - s))\right)^{2} ds \\
+&= \frac{\sigma^{2}}{2k^{2}} \int_{0}^{t_0} \exp(-2ks)\left(\exp(-k(t_0 - s)) - \exp(-k(t_1 - s))\right)^{2} ds\\
 &+ \frac{\sigma^{2}}{2k^{2}} \int_{t_0}^{t_1} \exp(-2ks)\left(1 - \exp(-k\delta_{t_0,t_1})\right)^{2} ds\\
-&= \frac{\sigma^{2}}{2k^{2}} \left(\delta_{t_0,t_1}+ \exp(-2k\delta_{t_0,t_1}) \frac{\exp(-2kt_0)- \exp(-2kt_1)}{2k} - 2\exp(-kt_1) \frac{\exp(-kt_0)- \exp(-kt_1)}{k}  \right) \\
+&= \frac{\sigma^{2}}{2k^{2}} \left(\delta_{t_0,t_1} \exp(-kt_0) + \exp(-2kt_1) \frac{\exp(-2kt_0)- \exp(-2kt_1)}{2k}\right)\\  
+&- \frac{\sigma^{2}}{k^{2}} \frac{\exp(-k(t_1-t_0))- \exp(-k(t_1+t_0))}{k}   \\
 &+ \frac{\sigma^{2}}{2k^{2}} \left(1 - \exp(-k\delta_{t_0,t_1})\right)^{2} \left(\frac{\exp(-2kt_0) - \exp(-2kt_1)}{2k}\right)
 \end{align*}
+Then if we substitute the last equality in (\ref{convexity_ois_future}) we get the convexity adjustment for OIS future.
+The next figure, show accuracy of (\ref{convexity_ois_future}) in the case of Hull-White
+
+\begin{figure}[h]
+	\begin{center}
+		\includegraphics[scale=0.3]{Figures/convexity_ois.jpg}
+		\caption{Convexity Mc Vs Convexity Malliavin}
+	\end{center}
+\end{figure}
 

### 2022-09-19 ConvexityAdjustment-Lib/ConvexityAdjusmentUnitTests/SofrCovexity.cs

@@ -14,8 +14,8 @@ namespace ConvexityAdjustmentUnitTests
             var calendar = new ql.TARGET();
             
             // Hull-White parameters
-            double k = 0.0003;
-            double sigma = 0.0115;
+            double k = 0.0001;
+            double sigma = 0.01;
             // double spreadBasis = 0.001;
 
             // Curves

### 2022-09-19 ConvexityAdjustment-Lib/ConvexityAdjustment-Lib/HullWhite.cs

@@ -60,8 +60,8 @@ namespace ConvexityAdjustment_Lib
             double df2 = curve.link.discount(t2, true);
             double m = 0.5 * Math.Pow(sigma / k, 2.0);
             double expected = -Math.Log(df2 / df1) + m * (delta12 - 2.0 * b1 + b2);
-            double i1 = m * (delta12 * Math.Exp(-2.0 * k * t1) + Math.Exp(-2.0 * k * delta12) * b2 - 2.0 * Math.Exp(-k*t2) * b1);
-            double i2 = m * Math.Pow(1.0 - Math.Exp(-k * delta12), 2.0) * b2;
+            double i1 = m * ( t1 * Math.Exp(- 2.0 * k * t1) + Math.Exp( - 2.0 * k * t2) * t1  - 2.0 * Math.Exp( - k * (t1 + t2)) * t1);
+            double i2 = m * (b2 + Math.Exp(-2.0 * k * t2) * delta12 - 2.0 * Beta(t1+t2, 2.0*t2, k));
 
             return (Math.Exp(expected + i1 + i2) - 1.0) / delta12;
         }
@@ -81,12 +81,13 @@ namespace ConvexityAdjustment_Lib
         
         public static double GetVarianceIntegralRt(double k, double sigma, double t0, double t1)
         {
-            var alpha = sigma * sigma;
-            var part1 = t1 - t0;
-            var part2 = 0.5 * (1.0 - Math.Exp(-2.0 * k * (t1 - t0))) / k;
-            var part3 = (1.0 - Math.Exp(-k * (t1 - t0))) / k;
 
-            return alpha * (part1 + part2 - 2.0 * part3);
+            double m = Math.Pow(sigma / k, 2.0);
+            double delta = t1 - t0;
+            double i1 = m * (Beta(0.0, t0, 2.0 * k) + Beta(delta, t1, 2.0 * k) - Beta(t1 - t0, t1 + t0, k));
+            double i2 = m * (delta + Beta(0.0,delta, 2.0 * k) - 2.0 * Beta(0.0, delta, k));
+
+            return i1 + i2;
         }
         
         public static double Beta(double t0, double t1, double alpha)

### 2022-09-19 Latex/paper.tex
Fixing some words and punctuation

@@
 \end{equation}
-with $g$ a positive time-dependent function a $h$ a non-negative process.
+with $g$ a positive time-dependent function and $h$ a non-negative process.
 This version of the HJM is also known as the Cheyette model, \cite{Cheyette}.
@@
 where the measure $\mathbb{Q}$ is the measure associated to the numeraire $B_t=\exp\left(\int_{0}^{t} r_{ois, s} ds \right)$ with $ r_{ois, t}$ the risk free short rate.
-From (\ref{forward_rate}) and (\ref{future}), we will define the convexity adjusment as
+From (\ref{forward_rate}) and (\ref{future}), we will define the convexity adjustment as
 \begin{equation*}
@@
 \begin{equation}
-L_{E}(t_0,t_1,t_2) = \hat{L}_{E}(t,t_0, t_1, t_2) + \int_{0}^{t_0} \mathbb{E}_{s}\left(D_s L_{E}(t_0,t_1,t_2) \right) dW^{\mathbb{Q}}_s
+L_{E}(t_0,t_1,t_2) = \hat{L}_{E}(t,t_0, t_1, t_2) + \int_{0}^{t_0} \mathbb{E}_{s}\left(D_s L_{E}(t_0,t_1,t_2) \right) dW^{\mathbb{Q}}_s.
 \end{equation} 
-therefore, if we take $\mathbb{E}^{\mathbb{Q}^{t2}}(\cdot)$ in the last equation, then we get
+Therefore, if we take $\mathbb{E}^{\mathbb{Q}^{t2}}(\cdot)$ in the last equation, then we get
 \begin{equation*}

### 2022-09-20 Latex/paper.tex
# avg sofr

@@
 Therefore we have that
+
+\hspace{2cm}
+\fboxsep1em
+\fbox{\parbox{335pt}
+{
 \begin{equation}\label{convexity_ois_future}
@@
 \end{equation}
+}}
+
 We must note, that from (\ref{apprx_I_t0_t1}) and (\ref{R_ois_avg}) we can get an approximation for $R_{avg}(t_0,t_1)$
+
+\hspace{2cm}
+\fboxsep1em
+\fbox{\parbox{335pt}
+{
+\begin{equation}\label{convexity_avg_ois_future}
+R_{avg}(t_0,t_1) = \frac{\mathbb{E}^{\mathbb{Q}}\left(I(t_0,t_1)\right) }{\delta_{t_0,t_1}} \approx \frac{\log\left(1+\delta_{t_0,t_1}  \mathbb{E}^{\mathbb{Q}}\left(R(t_0,t_1)\right) \right)}{\delta_{t_0,t_1}} - \frac{\int_{0}^{t_1}\Gamma^{2}(s,t_0,t_1) ds}{2\delta_{t_0,t_1}}
+\end{equation}
+}}
+
+Therefore, since $\log(1+x)\approx x$ we have that
+
 \begin{equation*}
-R_{avg}(t_0,t_1) = \frac{\mathbb{E}^{\mathbb{Q}}\left(I(t_0,t_1)\right) }{\delta_{t_0,t_1}} \approx \frac{\log\left(1+\delta_{t_0,t_1}  \mathbb{E}^{\mathbb{Q}}\left(R(t_0,t_1)\right) \right)}{\delta_{t_0,t_1}} + \frac{\int_{0}^{t_1}\Gamma^{2}(s,t_0,t_1) ds}{2\delta_{t_0,t_1}}
-\end{equation*}
-Therefore, since $\log(1+x)\approx x$ we have that
-\begin{equation*}
-R_{avg}(t_0,t_1) \approx  \mathbb{E}^{\mathbb{Q}}\left(R(t_0,t_1)\right) + \frac{\int_{0}^{t_1}\Gamma^{2}(s,t_0,t_1) ds}{2\delta_{t_0,t_1}}.
+R_{avg}(t_0,t_1) \approx  \mathbb{E}^{\mathbb{Q}}\left(R(t_0,t_1)\right) - \frac{\int_{0}^{t_1}\Gamma^{2}(s,t_0,t_1) ds}{2\delta_{t_0,t_1}}.
 \end{equation*}
@@
 &+ \frac{\sigma^{2}}{2k^{2}} \int_{t_0}^{t_1} \exp(-2ks)\left(1 - \exp(-k\delta_{t_0,t_1})\right)^{2} ds\\
-&= \frac{\sigma^{2}}{2k^{2}} \left(\delta_{t_0,t_1} \exp(-kt_0) + \exp(-2kt_1) \frac{\exp(-2kt_0)- \exp(-2kt_1)}{2k}\right)\\  
-&- \frac{\sigma^{2}}{k^{2}} \frac{\exp(-k(t_1-t_0))- \exp(-k(t_1+t_0))}{k}   \\
-&+ \frac{\sigma^{2}}{2k^{2}} \left(1 - \exp(-k\delta_{t_0,t_1})\right)^{2} \left(\frac{\exp(-2kt_0) - \exp(-2kt_1)}{2k}\right)
+&= \frac{\sigma^{2}t_0}{2k^{2}} \left( \exp(-kt_0) + \exp(-2kt_1) - 2 \exp(-k(t_1+t_0)) \right)\\  
+&+ \frac{\sigma^{2}}{2k^{2}} \left(\frac{\exp(-2kt_0) - \exp(-2kt_1)}{2k} + \exp(-2kt_1)\delta_{t_0,t_1} - 2\frac{\exp(-k(t_0 + t_1)) - \exp(-kt_1)}{k}  \right)
 \end{align*}

### 2022-09-20 ConvexityAdjustment-Lib/ConvexityAdjusmentUnitTests/SofrCovexity.cs

@@ -39,7 +39,9 @@ namespace ConvexityAdjustmentUnitTests
 
             List<double> t0s = new List<double>();
             List<double> caMc = new List<double>();
+            List<double> caAvgMc = new List<double>();
             List<double> caMalliavin = new List<double>();
+            List<double> caAvgMalliavin = new List<double>();
 
             for (var j = 1; j < numberOfMonths + 1; j++)
             {
@@ -64,6 +66,7 @@ namespace ConvexityAdjustmentUnitTests
                 // Path generator
                 int i;
                 var mean = 0.0;
+                var avgMean = 0.0;
                 var meanXt0 = 0.0;
                 var momentOrderTwoMean = 0.0;
 
@@ -75,7 +78,9 @@ namespace ConvexityAdjustmentUnitTests
                 {
                     var it0Tot1 = mu + std * zk.value[i] + r0t;
                     var libor = (Math.Exp(it0Tot1) - 1.0) / (delta02 - delta01);
+                    var avgLibor = it0Tot1 / (delta02 - delta01);
                     mean += (libor / numberOfSimulations);
+                    avgMean += (avgLibor / numberOfSimulations);
                     meanXt0 += it0Tot1 / numberOfSimulations;
                     momentOrderTwoMean += (libor * libor) / numberOfSimulations;
                 }
@@ -88,16 +93,20 @@ namespace ConvexityAdjustmentUnitTests
                     { mean - stdMc / Math.Sqrt(numberOfSimulations), mean + stdMc / Math.Sqrt(numberOfSimulations) };
                 
                 var forward =  curve.currentLink()
-                    .forwardRate(delta01, delta02, ql.Compounding.Simple, ql.Frequency.NoFrequency).rate();
+                    .forwardRate(delta01, delta02, ql.Compounding.Continuous, ql.Frequency.NoFrequency).rate();
 
                 var convexityMc = mcFuturePrice - forward;
-
+                var convexityAvgMc = avgMean - forward;
+                
                 var convexityMalliavin = HullWhite.ConvexityOis(curve, k, sigma, delta01, delta02) - forward;
+                var convexityAvgMalliavin = HullWhite.ConvexityAvgOis(curve, k, sigma, delta01, delta02) - forward;
                 
                 // outputs
                 t0s.Add(delta00);
                 caMc.Add(convexityMc);
+                caAvgMc.Add(convexityAvgMc);
                 caMalliavin.Add(convexityMalliavin);
[…]

### 2022-09-20 ConvexityAdjustment-Lib/ConvexityAdjustment-Lib/HullWhite.cs

@@ -65,6 +65,26 @@ namespace ConvexityAdjustment_Lib
 
             return (Math.Exp(expected + i1 + i2) - 1.0) / delta12;
         }
+        
+        public static double ConvexityAvgOis(ql.Handle<ql.YieldTermStructure> curve, double k, double sigma, double t1,
+            double t2)
+        {
+            double b1 = Beta(t1, t2, k);
+            double b2 = Beta(t1, t2, 2.0 * k);
+            double delta12 = t2 - t1;
+
+            double df1 = curve.link.discount(t1, true);
+            double df2 = curve.link.discount(t2, true);
+            double m = 0.5 * Math.Pow(sigma / k, 2.0);
+            double expected = -Math.Log(df2 / df1) + m * (delta12 - 2.0 * b1 + b2);
+            double i1 = m * ( t1 * Math.Exp(- 2.0 * k * t1) + Math.Exp( - 2.0 * k * t2) * t1  - 2.0 * Math.Exp( - k * (t1 + t2)) * t1);
+            double i2 = m * (b2 + Math.Exp(-2.0 * k * t2) * delta12 - 2.0 * Beta(t1+t2, 2.0*t2, k));
+
+            var r01 = ConvexityOis(curve, k, sigma, t1, t2);
+            var logR01 = Math.Log(1.0 + delta12 * r01) / delta12;
+            
+            return logR01 - (i1 + i2);
+        }
 
         #endregion
 

### 2022-10-02 ConvexityAdjustment-Lib/ConvexityAdjusmentUnitTests/CmsConvexity.cs
# first steps cms

@@ -1,0 +1,111 @@
+using NUnit.Framework;
+using ql = QLNet;
+
+namespace ConvexityAdjustmentUnitTests
+{
+    public class CmsConvexity
+    {
+        [Test]
+        public void HullWhiteCms()
+        {
+            // settings
+            var calendar = new ql.TARGET();
+            ql.DayCounter dc = new ql.Actual365Fixed();
+            ql.Date startDate = ql.Settings.evaluationDate();
+            
+            // Hull-White parameters
+            double k = 0.0007;
+            double sigma = 0.01;
+
+            // Curves
+            double discountFlatRate = 0.015;
+            double basisSpread = 0.01;
+            ql.Quote quoteDiscountRate = new ql.SimpleQuote(discountFlatRate);
+            ql.Quote quoteSpread = new ql.SimpleQuote(basisSpread);
+            
+            ql.Handle<ql.YieldTermStructure> discountCurve =  new ql.Handle<ql.YieldTermStructure>(new ql.FlatForward(startDate, quoteDiscountRate, dc));
+            ql.Handle<ql.YieldTermStructure> forwardCurve =new ql.Handle<ql.YieldTermStructure>(
+                new ql.ForwardSpreadedTermStructure(discountCurve,  new ql.Handle<ql.Quote>(quoteSpread)));
+            
+            // Model and process
+            ql.OrnsteinUhlenbeckProcess process = new ql.OrnsteinUhlenbeckProcess(k, sigma, 0.0, 0.0);
+            ql.HullWhite model = new ql.HullWhite(discountCurve, k, sigma);
+            
+            // Swap product
+            var floatingPeriod = new ql.Period(ql.Frequency.Semiannual);
+            var fixedPeriod = new ql.Period(ql.Frequency.Annual);
+            var index = new ql.Euribor6M(forwardCurve);
+            var forwardPeriod = new ql.Period(5, ql.TimeUnit.Years);
+            var tenorSwap = new ql.Period(5, ql.TimeUnit.Years);
+            
+       
+            // Convexity test
+            var periodToCompute = new ql.Period(1, ql.TimeUnit.Years);
+            int numberOftimes = 25;
+            
+            List<ql.Date> datesToCompute = new List<ql.Date>(){calendar.advance(startDate, periodToCompute)};
+            List<double> deltaTimes = new List<double>(){dc.yearFraction(startDate, datesToCompute[0])};
[…]

### 2022-10-02 ConvexityAdjustment-Lib/ConvexityAdjusmentUnitTests/FraInArrears.cs

@@ -1,5 +1,4 @@
-﻿using ConvexityAdjustment_Lib;
-using NUnit.Framework;
+﻿using NUnit.Framework;
 using ql = QLNet;
 
 namespace ConvexityAdjustmentUnitTests
@@ -60,9 +59,10 @@ namespace ConvexityAdjustmentUnitTests
                 double f0t = curve.currentLink().forwardRate(delta01, delta01, ql.Compounding.Simple, ql.Frequency.NoFrequency).rate();
                 double expat = (1.0 - Math.Exp(-k * delta01)) / k ;
                 double mt = (sigma * sigma) / (2.0 * k) * (expat - Math.Exp(-k * delta01) * expat);
+                
                 // Adjustment forward measure
                 double adjFwdMeasure =
-                    -(sigma * sigma / k) * (HullWhite.Beta(0.0, delta01, k) - Math.Exp(-k * delta01) * delta01);
+                    -(sigma * sigma / k) * (ConvexityAdjustment_Lib.HullWhite.Beta(0.0, delta01, k) - Math.Exp(-k * delta01) * delta01);
                 
                 // Path generator
                 int i;

### 2022-10-02 ConvexityAdjustment-Lib/ConvexityAdjusmentUnitTests/FraVsFuturesTests.cs

@@ -14,11 +14,11 @@ namespace ConvexityAdjustmentUnitTests
             
             // Hull-White parameters
             double k = 0.0003;
-            double sigma = 0.0115;
-            // double spreadBasis = 0.001;
+            double sigma = 0.015;
+            double spreadBasis = 0.001;
 
             // Curves
-            double flatRate = 0.01;
+            double flatRate = 0.025;
             ql.Quote quoteRate = new ql.SimpleQuote(flatRate);
             ql.DayCounter dc = new ql.Actual365Fixed();
             ql.Date startDate = ql.Settings.evaluationDate();
@@ -76,8 +76,8 @@ namespace ConvexityAdjustmentUnitTests
                     ql.Sample<ql.IPath> sample = generator.next();
                     var path = (ql.Path)sample.value;
                     var rt0 = path[path.length() - 1] + mt + f0t;
-                    var df01 = model.discountBond(delta00, delta01, rt0);
-                    var df02 = model.discountBond(delta00, delta02, rt0);
+                    var df01 = model.discountBond(delta00, delta01, rt0) * Math.Exp(- spreadBasis * (delta01 - delta00));
+                    var df02 = model.discountBond(delta00, delta02, rt0) *  Math.Exp(- spreadBasis * (delta02 - delta00));
                     var libor = ((df01 / df02) - 1.0) / (delta02 - delta01);
                     mean += (libor / numberOfSimulations);
                     meanXt0 += path[path.length() - 1] / numberOfSimulations;
@@ -93,9 +93,9 @@ namespace ConvexityAdjustmentUnitTests
                 var intervalConfidence = new double[]
                     { mean - stdMc / Math.Sqrt(numberOfSimulations), mean + stdMc / Math.Sqrt(numberOfSimulations) };
                 var convexityMc = mcFuturePrice - curve.currentLink()
-                    .forwardRate(delta01, delta02, ql.Compounding.Simple, ql.Frequency.NoFrequency).rate();
+                    .forwardRate(delta01, delta02, ql.Compounding.Simple, ql.Frequency.NoFrequency).rate() - spreadBasis;
                 var convexityMalliavin =
-                    ConvexityAdjustment_Lib.HullWhite.ConvexityFuture(curve, k, sigma, delta00, delta01, delta02, 0.0);
+                    ConvexityAdjustment_Lib.HullWhite.ConvexityFuture(curve, k, sigma, delta00, delta01, delta02, spreadBasis);
                 
                 // outputs
                 t0s.Add(delta00);

### 2022-10-02 ConvexityAdjustment-Lib/ConvexityAdjustment-Lib/HullWhite.cs

@@ -120,7 +120,13 @@ namespace ConvexityAdjustment_Lib
 
             return (Math.Exp(-alpha * t0) - Math.Exp(-alpha * t1)) / alpha;
         }
-        
+
+        public static double HjmAdjustment(double t0, double t1, double k, double sigma)
+        {
+            double m = 0.5 * sigma * sigma / k;
+            return m * (Beta(0, t1 - t0, k) - Beta(t1 - t0, t1 + t0, k));
+        }
+
         #endregion
 
     }

### 2022-10-06 Latex/paper.tex
# first steps cms
# cms convexity

@@
 \end{align*}
-In the next figure, we can check the accuracy of the last formula versus montecarlo. The parameters that we have used are $\sigma=0.05$, $k=0.003$ and flat curve with level $r=0.01$.
+In the next figure, we can check the accuracy of the last formula versus montecarlo. The parameters that we have used are $\sigma=0.015$, $k=0.003$ and flat curve with level $r=0.01$.
 
@@
 $R(\cdot,t_0,t_1)$ and $R_{avg}(\cdot,t_0,t_1)$ are flows that will be payed in $t_1$, we can considerer the expected value under the measure $\mathbb{Q}^{t_1}$ that will observable during whole period $[t_0, t_1]$.
-Let us define the next $\mathbb{Q}^{t_1}$ martingales
+Let us define the next $\mathbb{Q}$ martingales
 \begin{align*} 
@@
 \subsection{CMSs}
+We will define the swap rate from $T_a$ to $T_b$ at time $t$
+\begin{equation*}
+S_{a,b} = \frac{\sum_{i=1}^{n_E}\delta_{t^{E}_{i-1}, t^{E}_i} L^{E}(t,t^{E}_{i-1}, t^{E}_{i}) P_{ois}(t,t^{E}_{i})}{01(t,T_a,T_b)}
+\end{equation*}
+where
+\begin{align*}
+01(t,T_a,T_b) = \sum_{j=1}^{n_f} \delta_{t^{f}_{i-1}, t^{f}_i} P_{ois}(t,t^{f}_{j}) \\
+T_a=T^{E}_0 < T^{E}_i< \cdots < T^{E}_{n_E}=T_b \quad i=0,\cdots,n_E&  \\
+T_a=T^{f}_0 < T^{f}_j< \cdots < T^{f}_{n_f}=T_b \quad j=0,\cdots,n_f&
+\end{align*}
+We suppose, that we have a flow in $T_a < T_p < T_b$ with value $S_{a,b}(T_a)$. Then, the present value of this flow
+\begin{equation*}
+P_{ois}(0,T_a)\mathbb{E}^{\mathbb{Q}^{T_{a}}}\left(S_{a,b}(T_a) P_{ois}(T_a,T_p) \right) = 01(0,T_a,T_b) \mathbb{E}^{\mathbb{Q}^{01(a,b)}}\left(S_{a,b}(T_a) \frac{P_{ois}(T_a,T_p)}{01(T_a,T_a,T_b) }\right)
+\end{equation*}
+therefore, we have that
+\begin{align}\label{cms_expedted_value}
+\mathbb{E}^{\mathbb{Q}^{T_{a}}}\left(S_{a,b}(T_a) P_{ois}(T_a,T_p) \right) &=  \mathbb{E}^{\mathbb{Q}^{01(a,b)}}\left(S_{a,b}(T_a) \frac{M(T_a)}{M(0)}\right) \nonumber \\
+& = S_{a,b}(0) + \mathbb{E}^{\mathbb{Q}^{01(a,b)}}\left(S_{a,b}(T_a) \left(\frac{M(0, T_p)}{M(T_a, T_p)} - 1\right) \right)  
+\end{align} 
+where $M(t)= \frac{01(t,T_a,T_b)}{P_{ois}(t,T_p)} $. From (\ref{cms_expedted_value}), we will define the convexity adjusment for a CMS the next way
+\begin{equation}\label{cms_convexity}
+CA_{CMS}(T_a,T_b) = \mathbb{E}^{\mathbb{Q}^{01(a,b)}}\left(S_{a,b}(T_a) \left(\frac{M(0, T_p)}{M(T_a, T_p)} - 1\right) \right). 
+\end{equation}
+In order to reduce the complexity to explain the movement od the forward curve, it is a common pratice to asumme that
+\begin{equation*}
+M(t) = f(S_{a,b}(t))
+\end{equation*}
+where $f(\cdot)$ is known as mapping function.
+There is a extensive literature how to define this function (see Piterbarg Volume III).
+Then under this assumption and applying Clark-Ocone to $f(S_{a,b}(t))$ we get
+\begin{align*}
+f(S_{a,b}(T_a)) &= \mathbb{E}^{\mathbb{Q}^{01(a,b)}}\left(S_{a,b}(T_a)\right) + \int_{0}^{T_a} \mathbb{E}_s^{01(a,b)}\left( D_s (f(S_{a,b}(T_a))) \right) dW^{01(a,b)}_{s} \\
+&= 1 + \int_{0}^{T_a} \mathbb{E}_s^{01(a,b)}\left(f^{\prime}(S_{a,b}(T_a)) \partial_{x}S_{a,b}(T_a) D_s x_{T_a} \right) dW^{01(a,b)}_{s}. 
+\end{align*}
+Therefore, we have that
+\begin{equation*}
+CA_{CMS}(T_a,T_b) = \mathbb{E}^{\mathbb{Q}^{01(a,b)}}\left(S_{a,b}(T_a) \int_{0}^{T_a} \mathbb{E}_s^{01(a,b)}\left( f^{\prime}(S_{a,b}(T_a)) \partial_{x}S_{a,b}(T_a) D_s x_{T_a} \right) dW^{01(a,b)}_{s} \right).
+\end{equation*}
+Now if we apply the adjoint of the Malliavin derivative (see Elisa-David) we get
+
+\begin{align}
+CA_{CMS}(T_a,T_b) &= \mathbb{E}^{\mathbb{Q}^{01(a,b)}}\left( \int_{0}^{T_a} \partial_{x}S_{a,b}(T_a) D_s x_{T_a} \mathbb{E}_s^{01(a,b)}\left(f^{\prime}(S_{a,b}(T_a)) \partial_{x}S_{a,b}(T_a) D_s x_{T_a} \right) ds \right) \nonumber \\
+&\approx  \mathbb{E}^{\mathbb{Q}^{01(a,b)}}\left( \int_{0}^{T_a} \left(\partial_{x}S_{a,b}(0)\right)^{2} f^{\prime}(S_{a,b}(0))  D_s x_{T_a} \mathbb{E}_s^{01(a,b)}\left(D_s x_{T_a} \right) ds \right)
+\end{align}
 

### 2022-10-06 Latex/paper.tex
#cms convexity

@@
 CA_{CMS}(T_a,T_b) &= \mathbb{E}^{\mathbb{Q}^{01(a,b)}}\left( \int_{0}^{T_a} \partial_{x}S_{a,b}(T_a) D_s x_{T_a} \mathbb{E}_s^{01(a,b)}\left(f^{\prime}(S_{a,b}(T_a)) \partial_{x}S_{a,b}(T_a) D_s x_{T_a} \right) ds \right) \nonumber \\
-&\approx  \mathbb{E}^{\mathbb{Q}^{01(a,b)}}\left( \int_{0}^{T_a} \left(\partial_{x}S_{a,b}(0)\right)^{2} f^{\prime}(S_{a,b}(0))  D_s x_{T_a} \mathbb{E}_s^{01(a,b)}\left(D_s x_{T_a} \right) ds \right)
+&\approx  \mathbb{E}^{\mathbb{Q}^{01(a,b)}}\left( \int_{0}^{T_a} \left(\partial_{x}S_{a,b}(0)\right)^{2} f^{\prime}(S_{a,b}(0))  D_s x_{T_a} \mathbb{E}_s^{01(a,b)}\left(D_s x_{T_a} \right) ds \right) \nonumber \\
+& \approx \mathbb{E}^{\mathbb{Q}^{01(a,b)}}\left( \int_{0}^{T_a} \left(\partial_{x}S_{a,b}(0)\right)^{2} f^{\prime}(S_{a,b}(0)) \beta(s,T_a,x_0,\hat{y}_{s})  D_s x_{T_a}  ds \right)
 \end{align}

### 2022-10-06 Latex/paper.tex
# cms convexity II

@@
 
+\begin{remark}\label{drift_01_spot_measure}
+Before to continue, we must to calculate the Girsanov's measure change from $\mathbb{Q}$ to $\mathbb{Q}^{01(a,b)}$.
+In order to achieve this target, we will use a continuous version of $01(t,T_a,T_b)$ i.e
+\begin{equation*}
+01^{c}(t,T_a,T_b) = \int_{T_a}^{T_b} P_{ois}(t,u) du.
+\end{equation*}
+It is easy to see that if we define $z_t=\frac{01^{c}(t,T_a,T_b)}{\beta_t}$ and apply Itô's formula we get
+\begin{equation*}
+dW^{01(a,b)}_t = dW^{\mathbb{Q}}_t + \lambda_{t}dt 
+\end{equation*}
+where $\lambda_t = \frac{\int_{T_a}^{T_b} P_{ois}(t,u) \nu(t,u) du}{01^{c}(t,T_a,T_b)}$. Then we can do the next approximation for $\lambda_t$
+\begin{equation*}
+\hat{\lambda}_t \approx \frac{\int_{T_a}^{T_b} P_{ois}(t,u,x_0,\hat{y}_t) \nu(t,u) du}{01^{c}(t,T_a,T_b,x_0,\hat{y}_t)} 
+\end{equation*}
+\end{remark}
+Now, if we apply (\ref{drift_01_spot_measure}) we get that 
+\begin{equation*}
+\mathbb{E}^{\mathbb{Q}^{01(a,b)}}\left( D_s x_{T_a} \right) \approx \beta(s,T_a,x_0,\hat{y}_{s}) \exp\left(\int_{s}^{T_a} \frac{\int_{T_a}^{T_b} P_{ois}(u,u^{\prime},x_0,\hat{y}_u) \nu(t,u^{\prime}) du^{\prime}}{01^{c}(u,T_a,T_b,x_0,\hat{y}_u)} \partial_x \beta(u,t_0,x_s,y_s) du \right)
+\end{equation*}
+Therefore we have the next approximation for $CA_{CMS}(T_a,T_b)$
+
+\fboxsep1em
+\fbox{\parbox{465pt}
+{
+\begin{equation*}
+\int_{0}^{T_a} \left(\partial_{x}S_{a,b}(0)\right)^{2} f^{\prime}(S_{a,b}(0)) \beta^{2}(s,T_a,x_0,\hat{y}_{s})  \exp\left(\int_{s}^{T_a} \frac{\int_{T_a}^{T_b} P_{ois}(u,u^{\prime},x_0,\hat{y}_u) \nu(t,u^{\prime}) du^{\prime}}{01^{c}(u,T_a,T_b,x_0,\hat{y}_u)} \partial_x \beta(u,t_0,x_s,y_s) du \right)  ds
+\end{equation*}
+}}
+
 \section{Conclusion}\label{sec:Conclusion}

### 2022-10-09 Latex/paper.tex
# fix some typos in cms convexity adjustment

--- 2022-10-06 Latex/paper.tex
@@
 
-\begin{example}
+\begin{example}\label{example_convexity_hw_ois}
 The same way that in the example (\ref{example_ca_future}), we will suppose a Hull-White model with constan mean reversion $k=0.003$ and volatility $\sigma=0.01$.
@@
 We suppose, that we have a flow in $T_a < T_p < T_b$ with value $S_{a,b}(T_a)$. Then, the present value of this flow
-\begin{equation*}
-P_{ois}(0,T_a)\mathbb{E}^{\mathbb{Q}^{T_{a}}}\left(S_{a,b}(T_a) P_{ois}(T_a,T_p) \right) = 01(0,T_a,T_b) \mathbb{E}^{\mathbb{Q}^{01(a,b)}}\left(S_{a,b}(T_a) \frac{P_{ois}(T_a,T_p)}{01(T_a,T_a,T_b) }\right)
-\end{equation*}
-therefore, we have that
 \begin{align}\label{cms_expedted_value}
-\mathbb{E}^{\mathbb{Q}^{T_{a}}}\left(S_{a,b}(T_a) P_{ois}(T_a,T_p) \right) &=  \mathbb{E}^{\mathbb{Q}^{01(a,b)}}\left(S_{a,b}(T_a) \frac{M(T_a)}{M(0)}\right) \nonumber \\
-& = S_{a,b}(0) + \mathbb{E}^{\mathbb{Q}^{01(a,b)}}\left(S_{a,b}(T_a) \left(\frac{M(0, T_p)}{M(T_a, T_p)} - 1\right) \right)  
+P_{ois}(0,T_a)\mathbb{E}^{\mathbb{Q}^{T_{a}}}\left(S_{a,b}(T_a) P_{ois}(T_a,T_p) \right) &= 01(0,T_a,T_b) \mathbb{E}^{\mathbb{Q}^{01(a,b)}}\left(S_{a,b}(T_a) \frac{P_{ois}(T_a,T_p)}{01(T_a,T_a,T_b) }\right) \nonumber \\
+&= 01(0,T_a,T_b) \mathbb{E}^{\mathbb{Q}^{01(a,b)}}\left(S_{a,b}(T_a) M(T_a,T_p)\right)
 \end{align}
-where $M(t)= \frac{01(t,T_a,T_b)}{P_{ois}(t,T_p)} $. From (\ref{cms_expedted_value}), we will define the convexity adjusment for a CMS the next way
-\begin{equation}\label{cms_convexity}
-CA_{CMS}(T_a,T_b) = \mathbb{E}^{\mathbb{Q}^{01(a,b)}}\left(S_{a,b}(T_a) \left(\frac{M(0, T_p)}{M(T_a, T_p)} - 1\right) \right). 
-\end{equation}
-In order to reduce the complexity to explain the movement od the forward curve, it is a common pratice to asumme that
+where $M(t, T_p)= \frac{P_{ois}(t,T_p) }{01(t,T_a,T_b)} $. In order to reduce the complexity to explain the movement od the forward curve, it is a common pratice to asumme that
 \begin{equation*}
@@
 where $f(\cdot)$ is known as mapping function.
-There is a extensive literature how to define this function (see Piterbarg Volume III).
-Then under this assumption and applying Clark-Ocone to $f(S_{a,b}(t))$ we get
+There is a extensive literature how to define this function (see Piterbarg Volume III), in later we will see some particular examples.
+Under the last assumption and applying Clark-Ocone to $f(S_{a,b}(t))$ we get
 \begin{align*}
-f(S_{a,b}(T_a)) &= \mathbb{E}^{\mathbb{Q}^{01(a,b)}}\left(S_{a,b}(T_a)\right) + \int_{0}^{T_a} \mathbb{E}_s^{01(a,b)}\left( D_s (f(S_{a,b}(T_a))) \right) dW^{01(a,b)}_{s} \\
-&= 1 + \int_{0}^{T_a} \mathbb{E}_s^{01(a,b)}\left(f^{\prime}(S_{a,b}(T_a)) \partial_{x}S_{a,b}(T_a) D_s x_{T_a} \right) dW^{01(a,b)}_{s}. 
+f(S_{a,b}(T_a)) &= \mathbb{E}^{\mathbb{Q}^{01(a,b)}}\left(f(S_{a,b}(T_a))\right) + \int_{0}^{T_a} \mathbb{E}_s^{01(a,b)}\left( D_s (f(S_{a,b}(T_a))) \right) dW^{01(a,b)}_{s} \\
+&= \frac{P_{ois}(0,T_p) }{01(0,T_a,T_b)} + \int_{0}^{T_a} \mathbb{E}_s^{01(a,b)}\left(f^{\prime}(S_{a,b}(T_a)) \partial_{x}S_{a,b}(T_a) D_s x_{T_a} \right) dW^{01(a,b)}_{s}. 
 \end{align*}
-Therefore, we have that
+Therefore, we can define the convexity adjustment for a CMS the next way
 \begin{equation*}
-CA_{CMS}(T_a,T_b) = \mathbb{E}^{\mathbb{Q}^{01(a,b)}}\left(S_{a,b}(T_a) \int_{0}^{T_a} \mathbb{E}_s^{01(a,b)}\left( f^{\prime}(S_{a,b}(T_a)) \partial_{x}S_{a,b}(T_a) D_s x_{T_a} \right) dW^{01(a,b)}_{s} \right).
+CA_{CMS}(T_a,T_b) = 01(0,T_a,T_b) \mathbb{E}^{\mathbb{Q}^{01(a,b)}}\left(S_{a,b}(T_a) \int_{0}^{T_a} \mathbb{E}_s^{01(a,b)}\left( f^{\prime}(S_{a,b}(T_a)) \partial_{x}S_{a,b}(T_a) D_s x_{T_a} \right) dW^{01(a,b)}_{s} \right).
 \end{equation*}
@@
 \begin{align}
-CA_{CMS}(T_a,T_b) &= \mathbb{E}^{\mathbb{Q}^{01(a,b)}}\left( \int_{0}^{T_a} \partial_{x}S_{a,b}(T_a) D_s x_{T_a} \mathbb{E}_s^{01(a,b)}\left(f^{\prime}(S_{a,b}(T_a)) \partial_{x}S_{a,b}(T_a) D_s x_{T_a} \right) ds \right) \nonumber \\
-&\approx  \mathbb{E}^{\mathbb{Q}^{01(a,b)}}\left( \int_{0}^{T_a} \left(\partial_{x}S_{a,b}(0)\right)^{2} f^{\prime}(S_{a,b}(0))  D_s x_{T_a} \mathbb{E}_s^{01(a,b)}\left(D_s x_{T_a} \right) ds \right)
+CA_{CMS}(T_a,T_b) &= 01(0,T_a,T_b) \mathbb{E}^{\mathbb{Q}^{01(a,b)}}\left( \int_{0}^{T_a} \partial_{x}S_{a,b}(T_a) D_s x_{T_a} \mathbb{E}_s^{01(a,b)}\left(f^{\prime}(S_{a,b}(T_a)) \partial_{x}S_{a,b}(T_a) D_s x_{T_a} \right) ds \right) \nonumber \\
+&\approx 01(0,T_a,T_b)  \mathbb{E}^{\mathbb{Q}^{01(a,b)}}\left( \int_{0}^{T_a} \left(\partial_{x}S_{a,b}(0)\right)^{2} f^{\prime}(S_{a,b}(0))  D_s x_{T_a} \mathbb{E}_s^{01(a,b)}\left(D_s x_{T_a} \right) ds \right) \nonumber \\
+& \approx 01(0,T_a,T_b)  \mathbb{E}^{\mathbb{Q}^{01(a,b)}}\left( \int_{0}^{T_a} \left(\partial_{x}S_{a,b}(0)\right)^{2} f^{\prime}(S_{a,b}(0)) \beta(s,T_a,x_0,\hat{y}_{s})  D_s x_{T_a}  ds \right)
 \end{align}
+
+\begin{remark}\label{drift_01_spot_measure}
+Before to continue, we must to calculate the Girsanov's measure change from $\mathbb{Q}$ to $\mathbb{Q}^{01(a,b)}$.
+In order to achieve this target, we will use a continuous version of $01(t,T_a,T_b)$ i.e
+\begin{equation*}
+01^{c}(t,T_a,T_b) = \int_{T_a}^{T_b} P_{ois}(t,u) du.
+\end{equation*}
+It is easy to see that if we define $z_t=\frac{01^{c}(t,T_a,T_b)}{\beta_t}$ and apply Itô's formula we get
+\begin{equation*}
+dW^{01(a,b)}_t = dW^{\mathbb{Q}}_t + \lambda_{t}dt 
+\end{equation*}
+where $\lambda_t = \frac{\int_{T_a}^{T_b} P_{ois}(t,u) \nu(t,u) du}{01^{c}(t,T_a,T_b)}$. Then we can do the next approximation for $\lambda_t$
+\begin{equation*}
+\hat{\lambda}_t \approx \frac{\int_{T_a}^{T_b} P_{ois}(t,u,x_0,\hat{y}_t) \nu(t,u) du}{01^{c}(t,T_a,T_b,x_0,\hat{y}_t)} 
+\end{equation*}
+\end{remark}
+Now, if we apply (\ref{drift_01_spot_measure}) we get that 
+\begin{equation*}
+\mathbb{E}^{\mathbb{Q}^{01(a,b)}}\left( D_s x_{T_a} \right) \approx \beta(s,T_a,x_0,\hat{y}_{s}) \exp\left(-\int_{s}^{T_a} \frac{\int_{T_a}^{T_b} P_{ois}(u,u^{\prime},x_0,\hat{y}_u) \nu(t,u^{\prime}) du^{\prime}}{01^{c}(u,T_a,T_b,x_0,\hat{y}_u)} \partial_x \beta(u,t_0,x_0,\hat{y}_u) du \right)
+\end{equation*}
+Therefore we have the next for the convexity adjustment
+
+\fboxsep1em
+\fbox{\parbox{435pt}
+{
+
+\begin{equation}\label{cms_adjustment}
+CA_{CMS}(T_a,T_b) \approx 01(0,T_a,T_b) \int_{0}^{T_a} \left(\partial_{x}S_{a,b}(0)\right)^{2} f^{\prime}(S_{a,b}(0)) \beta^{2}(s,T_a,x_0,\hat{y}_{u}) \Omega(s, T_a)    ds
+\end{equation}
+with 
+$$\Omega(s, T_a) = \exp\left(-\int_{s}^{T_a} \frac{\int_{T_a}^{T_b} P_{ois}(u,u^{\prime},x_0,\hat{y}_u) \nu(t,u^{\prime}) du^{\prime}}{01^{c}(u,T_a,T_b,x_0,\hat{y}_u)} \partial_x \beta(u,t_0,x_0,\hat{y}_u) du \right)
+$$
+}}
+\begin{example}
+In ghe case of a Hull-White model, we showed in the example  (\ref{example_convexity_hw_ois}) that 
+$$
+\partial_x \beta(u,t_0,x_0,\hat{y}_u)=0
+$$
+\end{example}
+Therefore (\ref{cms_adjustment}) is reduced to
+$$
+01(0,T_a,T_b) \int_{0}^{T_a} \left(\partial_{x}S_{a,b}(0)\right)^{2} f^{\prime}(S_{a,b}(0)) \beta^{2}(s,T_a,x_0,\hat{y}_{u}) ds
+$$
 

### 2022-10-09 ConvexityAdjustment-Lib/ConvexityAdjusmentUnitTests/CmsConvexity.cs
# new test for cms convexity adjusment (not end)

@@ -24,21 +24,21 @@ namespace ConvexityAdjustmentUnitTests
             ql.Quote quoteSpread = new ql.SimpleQuote(basisSpread);
             
             ql.Handle<ql.YieldTermStructure> discountCurve =  new ql.Handle<ql.YieldTermStructure>(new ql.FlatForward(startDate, quoteDiscountRate, dc));
-            ql.Handle<ql.YieldTermStructure> forwardCurve =new ql.Handle<ql.YieldTermStructure>(
-                new ql.ForwardSpreadedTermStructure(discountCurve,  new ql.Handle<ql.Quote>(quoteSpread)));
             
             // Model and process
             ql.OrnsteinUhlenbeckProcess process = new ql.OrnsteinUhlenbeckProcess(k, sigma, 0.0, 0.0);
             ql.HullWhite model = new ql.HullWhite(discountCurve, k, sigma);
             
+            // Dynamics curve
+            ql.Handle<ql.YieldTermStructure> hullWhiteDiscountCurve = new ql.Handle<ql.YieldTermStructure>(new ql.ShortRate1FYieldStructure<ql.HullWhite>(model));
+            
             // Swap product
             var floatingPeriod = new ql.Period(ql.Frequency.Semiannual);
-            var fixedPeriod = new ql.Period(ql.Frequency.Annual);
-            var index = new ql.Euribor6M(forwardCurve);
-            var forwardPeriod = new ql.Period(5, ql.TimeUnit.Years);
+            var payPeriod = new ql.Period(ql.Frequency.Annual);
             var tenorSwap = new ql.Period(5, ql.TimeUnit.Years);
+
+            var discountEngine = new ql.DiscountingSwapEngine(discountCurve, null, startDate, startDate);
             
-       
             // Convexity test
             var periodToCompute = new ql.Period(1, ql.TimeUnit.Years);
             int numberOftimes = 25;
@@ -51,7 +51,7 @@ namespace ConvexityAdjustmentUnitTests
             for (int i = 1; i < numberOftimes; i++)
             {
                 datesToCompute.Add(calendar.advance(datesToCompute[i-1], periodToCompute));
-                deltaTimes.Add(dc.yearFraction(startDate, datesToCompute[i-1]));
+                deltaTimes.Add(dc.yearFraction(startDate, datesToCompute[i]));
[…]

### 2022-10-09 ConvexityAdjustment-Lib/ConvexityAdjusmentUnitTests/CmsConvexity.cs
# fix some bugs cms hull white test

@@ -29,8 +29,6 @@ namespace ConvexityAdjustmentUnitTests
             ql.OrnsteinUhlenbeckProcess process = new ql.OrnsteinUhlenbeckProcess(k, sigma, 0.0, 0.0);
             ql.HullWhite model = new ql.HullWhite(discountCurve, k, sigma);
             
-            // Dynamics curve
-            ql.Handle<ql.YieldTermStructure> hullWhiteDiscountCurve = new ql.Handle<ql.YieldTermStructure>(new ql.ShortRate1FYieldStructure<ql.HullWhite>(model));
             
             // Swap product
             var floatingPeriod = new ql.Period(ql.Frequency.Semiannual);
@@ -88,7 +86,8 @@ namespace ConvexityAdjustmentUnitTests
                     var tP = calendar.advance(datesToCompute[j - 1], payPeriod,
                         ql.BusinessDayConvention.ModifiedFollowing);
                     
-                    // Curves
+                    // Dynamics curve
+                    ql.Handle<ql.YieldTermStructure> hullWhiteDiscountCurve = new ql.Handle<ql.YieldTermStructure>(new ql.ShortRate1FYieldStructure<ql.HullWhite>(datesToCompute[j - 1], dc, calendar, model));
                     var dt = dc.yearFraction(startDate, datesToCompute[j - 1]);
                     ((ql.ShortRate1FYieldStructure<ql.HullWhite>)hullWhiteDiscountCurve.link).updateState(dt, ri);
                     

### 2022-10-14 ConvexityAdjustment-Lib/ConvexityAdjusmentUnitTests/CmsConvexity.cs
# fix bugs in test cms convexity

@@ -15,7 +15,7 @@ namespace ConvexityAdjustmentUnitTests
             
             // Hull-White parameters
             double k = 0.0007;
-            double sigma = 0.01;
+            double sigma = 0.015;
 
             // Curves
             double discountFlatRate = 0.015;
@@ -35,27 +35,25 @@ namespace ConvexityAdjustmentUnitTests
             var payPeriod = new ql.Period(ql.Frequency.Annual);
             var tenorSwap = new ql.Period(5, ql.TimeUnit.Years);
 
-            var discountEngine = new ql.DiscountingSwapEngine(discountCurve, null, startDate, startDate);
-            
             // Convexity test
             var periodToCompute = new ql.Period(1, ql.TimeUnit.Years);
             int numberOftimes = 25;
             
             List<ql.Date> datesToCompute = new List<ql.Date>(){calendar.advance(startDate, periodToCompute)};
             List<double> deltaTimes = new List<double>(){dc.yearFraction(startDate, datesToCompute[0])};
-            List<double> f0ts = new List<double>(){discountCurve.link.forwardRate(deltaTimes[0], deltaTimes[0], ql.Compounding.Continuous, ql.Frequency.NoFrequency).rate()};
+            List<double> f0ts = new List<double>(){discountCurve.link.forwardRate(deltaTimes[0], deltaTimes[0], ql.Compounding.Simple, ql.Frequency.NoFrequency).rate()};
             List<double> hjmAdjustment = new List<double>(){ConvexityAdjustment_Lib.HullWhite.HjmAdjustment(0, deltaTimes[0], k, sigma)};
             
             for (int i = 1; i < numberOftimes; i++)
             {
                 datesToCompute.Add(calendar.advance(datesToCompute[i-1], periodToCompute));
                 deltaTimes.Add(dc.yearFraction(startDate, datesToCompute[i]));
-                f0ts.Add(discountCurve.link.forwardRate(deltaTimes[i], deltaTimes[i], ql.Compounding.Continuous, ql.Frequency.NoFrequency).rate());
+                f0ts.Add(discountCurve.link.forwardRate(deltaTimes[i], deltaTimes[i], ql.Compounding.Simple, ql.Frequency.NoFrequency).rate());
                 hjmAdjustment.Add(ConvexityAdjustment_Lib.HullWhite.HjmAdjustment(deltaTimes[i-1], deltaTimes[i], k, sigma));
             }
             
             // MC
-            int numberOfSimulations = 10;
[…]

### 2022-10-14 ConvexityAdjustment-Lib/ConvexityAdjustment-Lib/HullWhite.cs

@@ -1,5 +1,5 @@
 ﻿using ql = QLNet;
-
+    
 namespace ConvexityAdjustment_Lib
 {
     public static class HullWhite
@@ -124,7 +124,7 @@ namespace ConvexityAdjustment_Lib
         public static double HjmAdjustment(double t0, double t1, double k, double sigma)
         {
             double m = 0.5 * sigma * sigma / k;
-            return m * (Beta(0, t1 - t0, k) - Beta(t1 - t0, t1 + t0, k));
+            return m * (Beta(0, t1 - t0, k) - Beta(t1 + t0, 2.0 * t1, k));
         }
 
         #endregion

### 2022-10-15 ConvexityAdjustment-Lib/ConvexityAdjusmentUnitTests/CmsConvexity.cs
# improve performance cms comvexity test

@@ -29,15 +29,14 @@ namespace ConvexityAdjustmentUnitTests
             ql.OrnsteinUhlenbeckProcess process = new ql.OrnsteinUhlenbeckProcess(k, sigma, 0.0, 0.0);
             ql.HullWhite model = new ql.HullWhite(discountCurve, k, sigma);
             
-            
             // Swap product
             var floatingPeriod = new ql.Period(ql.Frequency.Semiannual);
             var payPeriod = new ql.Period(ql.Frequency.Annual);
             var tenorSwap = new ql.Period(5, ql.TimeUnit.Years);
 
             // Convexity test
-            var periodToCompute = new ql.Period(1, ql.TimeUnit.Years);
-            int numberOftimes = 25;
+            var periodToCompute = new ql.Period(6, ql.TimeUnit.Months);
+            int numberOftimes = 50;
             
             List<ql.Date> datesToCompute = new List<ql.Date>(){calendar.advance(startDate, periodToCompute)};
             List<double> deltaTimes = new List<double>(){dc.yearFraction(startDate, datesToCompute[0])};
@@ -55,14 +54,8 @@ namespace ConvexityAdjustmentUnitTests
             // MC
             int numberOfSimulations = 500000;
             ulong seed = 123545;
-            int timeSteps = deltaTimes.Count;
+            // int timeSteps = deltaTimes.Count;
             
-            // Path Generator
-            var rsg = (ql.InverseCumulativeRsg<ql.RandomSequenceGenerator<ql.MersenneTwisterUniformRng>, 
-                    ql.InverseCumulativeNormal>)
-                new ql.PseudoRandom().make_sequence_generator(timeSteps, seed);
-            
-            ql.PathGenerator<ql.IRNG> generator = new ql.PathGenerator<ql.IRNG>(process, deltaTimes.Last(), timeSteps, rsg, true, deltaTimes);
             
             // outputs
             var rateCmsMc = new Dictionary<int, double>();
@@ -72,7 +65,6 @@ namespace ConvexityAdjustmentUnitTests
             var rateCmsForward = new List<double>();
             
             // Test
-            // Swap rate at t=0
             for (int j = 0; j < numberOftimes; j++)
             {
                 
@@ -97,45 +89,51 @@ namespace ConvexityAdjustmentUnitTests
                 rateCmsForward.Add(payoffDiscount);
             }
 
-            for (int i = 0; i < numberOfSimulations; i++)
+            for (int j = 0; j < numberOftimes; j++)
             {
[…]

### 2022-10-16 ConvexityAdjustment-Lib/ConvexityAdjusmentUnitTests/CmsConvexity.cs
# fix some bugs in cms convexity test

@@ -11,7 +11,7 @@ namespace ConvexityAdjustmentUnitTests
             // settings
             var calendar = new ql.TARGET();
             ql.DayCounter dc = new ql.Actual365Fixed();
-            ql.Date startDate = ql.Settings.evaluationDate();
+            ql.Date startDate =  calendar.adjust(ql.Settings.evaluationDate());
             
             // Hull-White parameters
             double k = 0.0007;
@@ -77,12 +77,13 @@ namespace ConvexityAdjustmentUnitTests
                         
                 var discountEngine = new ql.DiscountingSwapEngine(discountCurve, null, startDate, startDate);
                         
-                var staticSwap = new ql.MakeVanillaSwap(floatingPeriod, staticIndex, 0.0)
+                var staticSwap = new ql.MakeVanillaSwap(tenorSwap, staticIndex, 0.0)
                     .withEffectiveDate(datesToCompute[j])
                     .withFloatingLegTenor(staticIndex.tenor())
                     .withFixedLegTenor(new ql.Period(1, ql.TimeUnit.Years))
-                    .withTerminationDate(endDate)
-                    .withPricingEngine(discountEngine).value();
+                    .withPricingEngine(discountEngine)
+                    .withFixedLegRule(ql.DateGeneration.Rule.Forward)
+                    .withFloatingLegRule(ql.DateGeneration.Rule.Forward).value();
                         
                         
                 double payoffDiscount = discountCurve.link.discount(datesToCompute[j]) * staticSwap.fairRate();
@@ -116,12 +117,21 @@ namespace ConvexityAdjustmentUnitTests
                 
                 var index = new ql.Euribor6M(forwardCurve);
                 
-                var swap = new ql.MakeVanillaSwap(floatingPeriod, index, 0.0)
+                var swap = new ql.MakeVanillaSwap(tenorSwap, index, 0.0)
+                    .withSettlementDays(0)
                     .withEffectiveDate(datesToCompute[j])
                     .withFloatingLegTenor(index.tenor())
                     .withFixedLegTenor(new ql.Period(1, ql.TimeUnit.Years))
-                    .withTerminationDate(endDate)
-                    .withPricingEngine(discountEngineHullWhite).value();
+                    .withPricingEngine(discountEngineHullWhite) 
+                    .withFixedLegRule(ql.DateGeneration.Rule.Forward)
+                    .withFloatingLegRule(ql.DateGeneration.Rule.Forward).value();
+
[…]

### 2022-10-16 ConvexityAdjustment-Lib/ConvexityAdjustment-Lib/HullWhite.cs

@@ -126,7 +126,7 @@ namespace ConvexityAdjustment_Lib
             double m = 0.5 * sigma * sigma / k;
             return m * (Beta(0, t1 - t0, k) - Beta(t1 + t0, 2.0 * t1, k));
         }
-
+        
         #endregion
 
     }

### 2022-10-16 ConvexityAdjustment-Lib/ConvexityAdjusmentUnitTests/CmsConvexity.cs
# fix some bugs in counters and compounding type

@@ -10,7 +10,7 @@ namespace ConvexityAdjustmentUnitTests
         {
             // settings
             var calendar = new ql.TARGET();
-            ql.DayCounter dc = new ql.Actual365Fixed();
+            ql.DayCounter dc = new ql.Actual360();
             ql.Date startDate =  calendar.adjust(ql.Settings.evaluationDate());
             
             // Hull-White parameters
@@ -30,9 +30,8 @@ namespace ConvexityAdjustmentUnitTests
             ql.HullWhite model = new ql.HullWhite(discountCurve, k, sigma);
             
             // Swap product
-            var floatingPeriod = new ql.Period(ql.Frequency.Semiannual);
             var payPeriod = new ql.Period(ql.Frequency.Annual);
-            var tenorSwap = new ql.Period(5, ql.TimeUnit.Years);
+            var tenorSwap = new ql.Period(1, ql.TimeUnit.Years);
 
             // Convexity test
             var periodToCompute = new ql.Period(6, ql.TimeUnit.Months);
@@ -47,7 +46,7 @@ namespace ConvexityAdjustmentUnitTests
             {
                 datesToCompute.Add(calendar.advance(datesToCompute[i-1], periodToCompute));
                 deltaTimes.Add(dc.yearFraction(startDate, datesToCompute[i]));
-                f0ts.Add(discountCurve.link.forwardRate(deltaTimes[i], deltaTimes[i], ql.Compounding.Simple, ql.Frequency.NoFrequency).rate());
+                f0ts.Add(discountCurve.link.forwardRate(deltaTimes[i], deltaTimes[i], ql.Compounding.Continuous, ql.Frequency.NoFrequency).rate());
                 hjmAdjustment.Add(ConvexityAdjustment_Lib.HullWhite.HjmAdjustment(deltaTimes[i-1], deltaTimes[i], k, sigma));
             }
             
@@ -84,6 +83,13 @@ namespace ConvexityAdjustmentUnitTests
                     .withPricingEngine(discountEngine)
                     .withFixedLegRule(ql.DateGeneration.Rule.Forward)
                     .withFloatingLegRule(ql.DateGeneration.Rule.Forward).value();
+
+                var annuity = model.GetAnnuity(startDate, datesToCompute[j], f0ts[j], staticSwap.fixedSchedule(),
+                    staticSwap.fixedDayCount());
+
+                var swapDerivative = model.GetPartialDerivativeSwapRate(startDate, datesToCompute[j], f0ts[j],
[…]

### 2022-10-16 Latex/paper.tex
# some advanced in the HW cms convexity

@@
 \begin{align*}
-f(S_{a,b}(T_a)) &= \mathbb{E}^{\mathbb{Q}^{01(a,b)}}\left(f(S_{a,b}(T_a))\right) + \int_{0}^{T_a} \mathbb{E}_s^{01(a,b)}\left( D_s (f(S_{a,b}(T_a))) \right) dW^{01(a,b)}_{s} \\
-&= \frac{P_{ois}(0,T_p) }{01(0,T_a,T_b)} + \int_{0}^{T_a} \mathbb{E}_s^{01(a,b)}\left(f^{\prime}(S_{a,b}(T_a)) \partial_{x}S_{a,b}(T_a) D_s x_{T_a} \right) dW^{01(a,b)}_{s}. 
+f(S_{a,b}(T_a)) &= \mathbb{E}^{\mathbb{Q}^{01(a,b)}}\left(f(S_{a,b}(T_a, x_s, y_s)\right) + \int_{0}^{T_a} \mathbb{E}_s^{01(a,b)}\left( D_s (f(S_{a,b}(T_a, x_s, y_s)) \right) dW^{01(a,b)}_{s} \\
+&= \frac{P_{ois}(0,T_p) }{01(0,T_a,T_b)} + \int_{0}^{T_a} \mathbb{E}_s^{01(a,b)}\left(f^{\prime}(S_{a,b}(T_a, x_s, y_s) \partial_{x}S_{a,b}(T_a, x_s, y_s) D_s x_{T_a} \right) dW^{01(a,b)}_{s}. 
 \end{align*}
 Therefore, we can define the convexity adjustment for a CMS the next way
-\begin{equation*}
-CA_{CMS}(T_a,T_b) = 01(0,T_a,T_b) \mathbb{E}^{\mathbb{Q}^{01(a,b)}}\left(S_{a,b}(T_a) \int_{0}^{T_a} \mathbb{E}_s^{01(a,b)}\left( f^{\prime}(S_{a,b}(T_a)) \partial_{x}S_{a,b}(T_a) D_s x_{T_a} \right) dW^{01(a,b)}_{s} \right).
-\end{equation*}
+\begin{align*}
+CA_{CMS}(T_a,T_b) = \\
+01(0,T_a,T_b) \mathbb{E}^{\mathbb{Q}^{01(a,b)}}\left(S_{a,b}(T_a, x_s, y_s) \int_{0}^{T_a} \mathbb{E}_s^{01(a,b)}\left( f^{\prime}(S_{a,b}(T_a, x_s, y_s)) \partial_{x}S_{a,b}(T_a, x_s, y_s) D_s x_{T_a} \right) dW^{01(a,b)}_{s} \right).
+\end{align*}
 Now if we apply the adjoint of the Malliavin derivative (see Elisa-David) we get
@@
 \begin{align}
-CA_{CMS}(T_a,T_b) &= 01(0,T_a,T_b) \mathbb{E}^{\mathbb{Q}^{01(a,b)}}\left( \int_{0}^{T_a} \partial_{x}S_{a,b}(T_a) D_s x_{T_a} \mathbb{E}_s^{01(a,b)}\left(f^{\prime}(S_{a,b}(T_a)) \partial_{x}S_{a,b}(T_a) D_s x_{T_a} \right) ds \right) \nonumber \\
-&\approx 01(0,T_a,T_b)  \mathbb{E}^{\mathbb{Q}^{01(a,b)}}\left( \int_{0}^{T_a} \left(\partial_{x}S_{a,b}(0)\right)^{2} f^{\prime}(S_{a,b}(0))  D_s x_{T_a} \mathbb{E}_s^{01(a,b)}\left(D_s x_{T_a} \right) ds \right) \nonumber \\
-& \approx 01(0,T_a,T_b)  \mathbb{E}^{\mathbb{Q}^{01(a,b)}}\left( \int_{0}^{T_a} \left(\partial_{x}S_{a,b}(0)\right)^{2} f^{\prime}(S_{a,b}(0)) \beta(s,T_a,x_0,\hat{y}_{s})  D_s x_{T_a}  ds \right)
+CA_{CMS}(T_a,T_b) &= 01(0,T_a,T_b) \mathbb{E}^{\mathbb{Q}^{01(a,b)}}\left( \int_{0}^{T_a} \partial_{x}S_{a,b}(T_a, x_s, y_s) D_s x_{T_a} \mathbb{E}_s^{01(a,b)}\left(f^{\prime}(S_{a,b}(T_a, x_s, y_s)) \partial_{x}S_{a,b}(T_a, x_s, y_s) D_s x_{T_a} \right) ds \right) \nonumber \\
+&\approx 01(0,T_a,T_b)  \mathbb{E}^{\mathbb{Q}^{01(a,b)}}\left( \int_{0}^{T_a} \left(\partial_{x}S_{a,b}(T_a, x_0, y_0)\right)^{2} f^{\prime}(S_{a,b}(T_a, x_0, y_0)  D_s x_{T_a} \mathbb{E}_s^{01(a,b)}\left(D_s x_{T_a} \right) ds \right) \nonumber \\
+& \approx 01(0,T_a,T_b)  \mathbb{E}^{\mathbb{Q}^{01(a,b)}}\left( \int_{0}^{T_a} \left(\partial_{x}S_{a,b}(T_a, x_0, y_0)\right)^{2} f^{\prime}(S_{a,b}(T_a, x_0, y_0) \beta(s,T_a,x_0,\hat{y}_{s})  D_s x_{T_a}  ds \right)
 \end{align}
@@
 \begin{equation}\label{cms_adjustment}
-CA_{CMS}(T_a,T_b) \approx 01(0,T_a,T_b) \int_{0}^{T_a} \left(\partial_{x}S_{a,b}(0)\right)^{2} f^{\prime}(S_{a,b}(0)) \beta^{2}(s,T_a,x_0,\hat{y}_{u}) \Omega(s, T_a)    ds
+CA_{CMS}(T_a,T_b) \approx 01(0,T_a,T_b) \int_{0}^{T_a} \left(\partial_{x}S_{a,b}(T_a, x_0, y_0)\right)^{2} f^{\prime}(S_{a,b}(T_a, x_0, y_0)) \beta^{2}(s,T_a,x_0,\hat{y}_{u}) \Omega(s, T_a)    ds
 \end{equation}
@@
 $$
+A common practice in market, it is suppose that $f(x)=\alpha x + \beta$ (TSR model). It is easy to show using (\ref{bond_ois}) and that 
+\begin{equation*}
+\mathbb{E}^{01(a,b)}\left(\alpha S_{a,b}(T_a) + b \right) = \frac{P_ois(0,T_p)}{01(0,T_a,T_b)}
+\end{equation*}
+we have that
+\begin{align*}
+\alpha &= - \frac{\frac{P_ois(T_a,T_p,x_0,y_0)}{01(T_a,T_a,T_b,x_0,y_0)} \left(G(T_a,T_p) +\frac{\partial_x 01(T_a,T_a,T_b,x_0,y_0)}{01(T_a,T_a,T_b,x_0,y_0)}\right)}{\partial_x S_{a,b}(T_a,T_a,T_b,x_{T_a},y_{T_a})} \\
+\beta &= \frac{P_ois(0,T_p)}{01(0,T_a,T_b,x_0,y_0)} - \alpha S_{a,b}(T_a,T_a,T_b,x_0,y_0)
+\end{align*}
+Therefore, we can approximate the convexity adjustment of a CMS rate as
+\begin{align*}
+CA_{CMS}(T_a,T_b) \approx \\
+- P_{ois}(T_a,T_p,x_0,y_0) \left(G(T_a,T_p) +\frac{\partial_x 01(T_a,T_a,T_b,x_0,y_0)}{01(T_a,T_a,T_b,x_0,y_0)}\right) \partial_{x}S_{a,b}(T_a,x_0,y_0) \int_{0}^{T_a}  \beta^{2}(s,T_a,x_0,\hat{y}_{u}) ds
+\end{align*}
+In the next figure, we can see the convexity adjustment for a CMS where the tenor for the underlying swap is 5Y using the last approximation and Monte Carlo method
 

### 2022-10-17 ConvexityAdjustment-Lib/ConvexityAdjusmentUnitTests/CmsConvexity.cs
# cms covexity adjustment (not end)

@@ -31,45 +31,45 @@ namespace ConvexityAdjustmentUnitTests
             
             // Swap product
             var payPeriod = new ql.Period(ql.Frequency.Annual);
-            var tenorSwap = new ql.Period(1, ql.TimeUnit.Years);
+            var tenorSwap = new ql.Period(5, ql.TimeUnit.Years);
 
             // Convexity test
             var periodToCompute = new ql.Period(6, ql.TimeUnit.Months);
             int numberOftimes = 50;
             
-            List<ql.Date> datesToCompute = new List<ql.Date>(){calendar.advance(startDate, periodToCompute)};
-            List<double> deltaTimes = new List<double>(){dc.yearFraction(startDate, datesToCompute[0])};
-            List<double> f0ts = new List<double>(){discountCurve.link.forwardRate(deltaTimes[0], deltaTimes[0], ql.Compounding.Simple, ql.Frequency.NoFrequency).rate()};
-            List<double> hjmAdjustment = new List<double>(){ConvexityAdjustment_Lib.HullWhite.HjmAdjustment(0, deltaTimes[0], k, sigma)};
-            
+            List<ql.Date> datesToCompute = new List<ql.Date>{calendar.advance(startDate, periodToCompute)};
+            List<double> deltaTimes = new List<double>{dc.yearFraction(startDate, datesToCompute[0])};
+            List<double> f0ts = new List<double>{discountCurve.link.forwardRate(deltaTimes[0], deltaTimes[0], ql.Compounding.Simple, ql.Frequency.NoFrequency).rate()};
+            List<double> hjmAdjustment = new List<double>{ConvexityAdjustment_Lib.HullWhite.hjmAdjustment(0, deltaTimes[0], k, sigma)};
+            var drift = new List<double>{ConvexityAdjustment_Lib.HullWhite.forwardMeasureAdjustment(deltaTimes[0], k, sigma)};
+
             for (int i = 1; i < numberOftimes; i++)
             {
                 datesToCompute.Add(calendar.advance(datesToCompute[i-1], periodToCompute));
                 deltaTimes.Add(dc.yearFraction(startDate, datesToCompute[i]));
                 f0ts.Add(discountCurve.link.forwardRate(deltaTimes[i], deltaTimes[i], ql.Compounding.Continuous, ql.Frequency.NoFrequency).rate());
[…]

### 2022-10-17 ConvexityAdjustment-Lib/ConvexityAdjusmentUnitTests/FraInArrears.cs

@@ -62,7 +62,7 @@ namespace ConvexityAdjustmentUnitTests
                 
                 // Adjustment forward measure
                 double adjFwdMeasure =
-                    -(sigma * sigma / k) * (ConvexityAdjustment_Lib.HullWhite.Beta(0.0, delta01, k) - Math.Exp(-k * delta01) * delta01);
+                    -(sigma * sigma / k) * (ConvexityAdjustment_Lib.HullWhite.beta(0.0, delta01, k) - Math.Exp(-k * delta01) * delta01);
                 
                 // Path generator
                 int i;
@@ -94,7 +94,7 @@ namespace ConvexityAdjustmentUnitTests
                 var convexityMc = mcFraInArrears - curve.currentLink()
                     .forwardRate(delta01, delta02, ql.Compounding.Simple, ql.Frequency.NoFrequency).rate();
                 var convexityMalliavin =
-                    ConvexityAdjustment_Lib.HullWhite.ConvexityFraInArrears(curve, k, sigma, delta01, delta02, 0.0);
+                    ConvexityAdjustment_Lib.HullWhite.convexityFraInArrears(curve, k, sigma, delta01, delta02, 0.0);
                 
                 // outputs
                 t0s.Add(delta01);

### 2022-10-17 ConvexityAdjustment-Lib/ConvexityAdjusmentUnitTests/FraVsFuturesTests.cs

@@ -95,7 +95,7 @@ namespace ConvexityAdjustmentUnitTests
                 var convexityMc = mcFuturePrice - curve.currentLink()
                     .forwardRate(delta01, delta02, ql.Compounding.Simple, ql.Frequency.NoFrequency).rate() - spreadBasis;
                 var convexityMalliavin =
-                    ConvexityAdjustment_Lib.HullWhite.ConvexityFuture(curve, k, sigma, delta00, delta01, delta02, spreadBasis);
+                    ConvexityAdjustment_Lib.HullWhite.convexityFuture(curve, k, sigma, delta00, delta01, delta02, spreadBasis);
                 
                 // outputs
                 t0s.Add(delta00);

### 2022-10-17 ConvexityAdjustment-Lib/ConvexityAdjusmentUnitTests/SofrCovexity.cs

@@ -71,8 +71,8 @@ namespace ConvexityAdjustmentUnitTests
                 var momentOrderTwoMean = 0.0;
 
                 var zk = rsg.nextSequence();
-                var mu = HullWhite.GetExpectedIntegralRt(k, sigma, delta01, delta02);
-                var std = Math.Sqrt(HullWhite.GetVarianceIntegralRt(k, sigma, delta01, delta02));
+                var mu = HullWhite.getExpectedIntegralRt(k, sigma, delta01, delta02);
+                var std = Math.Sqrt(HullWhite.getVarianceIntegralRt(k, sigma, delta01, delta02));
                 
                 for (i = 0; i < numberOfSimulations; i++)
                 {
@@ -98,8 +98,8 @@ namespace ConvexityAdjustmentUnitTests
                 var convexityMc = mcFuturePrice - forward;
                 var convexityAvgMc = avgMean - forward;
                 
-                var convexityMalliavin = HullWhite.ConvexityOis(curve, k, sigma, delta01, delta02) - forward;
-                var convexityAvgMalliavin = HullWhite.ConvexityAvgOis(curve, k, sigma, delta01, delta02) - forward;
+                var convexityMalliavin = HullWhite.convexityOis(curve, k, sigma, delta01, delta02) - forward;
+                var convexityAvgMalliavin = HullWhite.convexityAvgOis(curve, k, sigma, delta01, delta02) - forward;
                 
                 // outputs
                 t0s.Add(delta00);

### 2022-10-17 ConvexityAdjustment-Lib/ConvexityAdjustment-Lib/HullWhite.cs

@@ -6,7 +6,7 @@ namespace ConvexityAdjustment_Lib
     {
         
         #region Convexity
-        public static double ConvexityFraInArrears(ql.Handle<ql.YieldTermStructure> curve, double k, double sigma,
+        public static double convexityFraInArrears(ql.Handle<ql.YieldTermStructure> curve, double k, double sigma,
             double t1, double t2,
             double basisSpread)
         {
@@ -19,13 +19,13 @@ namespace ConvexityAdjustment_Lib
             double df12 = (df02 * h02) / (df01 * h01);
 
             double m = sigma * sigma / (delta12 * df12 * k);
-            double integral = Beta(t1, 2.0 * t1, k) - Beta(t2, t1 + t2, k);
+            double integral = beta(t1, 2.0 * t1, k) - beta(t2, t1 + t2, k);
 
             return m * integral;
 
         }
 
-        public static double ConvexityFuture(ql.Handle<ql.YieldTermStructure> curve,  double k, double sigma, double t0, double t1, double t2,
+        public static double convexityFuture(ql.Handle<ql.YieldTermStructure> curve,  double k, double sigma, double t0, double t1, double t2,
             double basisSpread)
         {
             // df, year fracs, basis,....
@@ -42,18 +42,18 @@ namespace ConvexityAdjustment_Lib
             double g01 = (1.0 - Math.Exp(-k * delta01)) / k;
             double g02 = (1.0 - Math.Exp(-k * delta02)) / k;
             
-            double m = Beta(0.0, delta12, k) * sigma * sigma * Math.Exp(-k * t0);
+            double m = beta(0.0, delta12, k) * sigma * sigma * Math.Exp(-k * t0);
             double integral = (1.0 - Math.Exp(-k * t0)) / (k * k) - t0 * Math.Exp(-k * t2) / k;
             double alpha = (h01 * df01) / (df00 * (h02 * df02) * delta12) * ( df02 * g02 - df01 * g01);
 
             return alpha * m * integral;
         }
 
-        public static double ConvexityOis(ql.Handle<ql.YieldTermStructure> curve, double k, double sigma, double t1,
+        public static double convexityOis(ql.Handle<ql.YieldTermStructure> curve, double k, double sigma, double t1,
             double t2)
         {
[…]

### 2022-10-23 ConvexityAdjustment-Lib/ConvexityAdjusmentUnitTests/CmsConvexity.cs
# fix bugs in convexity cms (not end)

@@ -15,7 +15,7 @@ namespace ConvexityAdjustmentUnitTests
             
             // Hull-White parameters
             double k = 0.0007;
-            double sigma = 0.00000001;
+            double sigma = 0.015;
 
             // Curves
             double discountFlatRate = 0.015;
@@ -34,13 +34,13 @@ namespace ConvexityAdjustmentUnitTests
             var tenorSwap = new ql.Period(5, ql.TimeUnit.Years);
 
             // Convexity test
-            var periodToCompute = new ql.Period(6, ql.TimeUnit.Months);
-            int numberOftimes = 25;
+            var periodToCompute = new ql.Period(1, ql.TimeUnit.Years);
+            int numberOftimes = 1;
             
             List<ql.Date> datesToCompute = new List<ql.Date>{calendar.advance(startDate, periodToCompute)};
             List<double> deltaTimes = new List<double>{dc.yearFraction(startDate, datesToCompute[0])};
             List<double> f0ts = new List<double>{discountCurve.link.forwardRate(deltaTimes[0], deltaTimes[0], ql.Compounding.Simple, ql.Frequency.NoFrequency).rate()};
-            List<double> hjmAdjustment = new List<double>{ConvexityAdjustment_Lib.HullWhite.hjmAdjustment(0, deltaTimes[0], k, sigma)};
+            List<double> hjmAdjustment = new List<double>{ConvexityAdjustment_Lib.HullWhite.hjmAdjustment(deltaTimes[0], k, sigma)};
             var drift = new List<double>{ConvexityAdjustment_Lib.HullWhite.forwardMeasureAdjustment(deltaTimes[0], k, sigma)};
 
             for (int i = 1; i < numberOftimes; i++)
@@ -48,7 +48,7 @@ namespace ConvexityAdjustmentUnitTests
                 datesToCompute.Add(calendar.advance(datesToCompute[i-1], periodToCompute));
                 deltaTimes.Add(dc.yearFraction(startDate, datesToCompute[i]));
                 f0ts.Add(discountCurve.link.forwardRate(deltaTimes[i], deltaTimes[i], ql.Compounding.Simple, ql.Frequency.NoFrequency).rate());
-                hjmAdjustment.Add(ConvexityAdjustment_Lib.HullWhite.hjmAdjustment(0.0, deltaTimes[i], k, sigma));
[…]

### 2022-10-23 ConvexityAdjustment-Lib/ConvexityAdjustment-Lib/HullWhite.cs

@@ -86,14 +86,14 @@ namespace ConvexityAdjustment_Lib
         }
 
         public static double convexityCms(ql.Handle<ql.YieldTermStructure> discountCurve,  ql.Date valueDate, ql.Date ta, ql.Date tb, ql.Date tp, double partialSwap, double annuity,
-            double partialAnnuity, ql.DayCounter dc, double k, double sigma)
+            double partialOisAnnuity, double partialVanillaSwap, ql.DayCounter dc, double k, double sigma)
         {
             var d0 = dc.yearFraction(valueDate, ta);
             var dtp = dc.yearFraction(valueDate, tp);
             var dfOis = discountCurve.link.discount(tp);
             var m = sigma * sigma * beta(0.0, d0, 2.0 * k);
 
-            return -dfOis * (beta(d0, dtp, k) + partialAnnuity / annuity) * partialSwap * m; 
+            return -dfOis * (beta(d0, dtp, k) + partialOisAnnuity / annuity) * partialSwap * m; 
             
         }
 
@@ -132,10 +132,10 @@ namespace ConvexityAdjustment_Lib
             return (Math.Exp(-alpha * t0) - Math.Exp(-alpha * t1)) / alpha;
         }
 
-        public static double hjmAdjustment(double t0, double t1, double k, double sigma)
+        public static double hjmAdjustment(double t, double k, double sigma)
         {
             double m = 0.5 * sigma * sigma / k;
-            return m * (beta(0, t1 - t0, k) - beta(t1 + t0, 2.0 * t1, k));
+            return m * (beta(0, t, k) - beta(t, 2.0 * t, k));
         }
 
         public static double forwardMeasureAdjustment(double dtP, double k, double sigma)

### 2022-10-25 Latex/paper.tex
# cms covexity adjustment (not end)
# fix several bugs in cms example

--- 2022-10-09 Latex/paper.tex
@@
 \begin{equation*}
-S_{a,b} = \frac{\sum_{i=1}^{n_E}\delta_{t^{E}_{i-1}, t^{E}_i} L^{E}(t,t^{E}_{i-1}, t^{E}_{i}) P_{ois}(t,t^{E}_{i})}{01(t,T_a,T_b)}
+S_{a,b}(t) = \frac{\sum_{i=1}^{n_E}\delta_{t^{E}_{i-1}, t^{E}_i} L^{E}(t,t^{E}_{i-1}, t^{E}_{i}) P_{ois}(t,t^{E}_{i})}{01(t,T_a,T_b)}
 \end{equation*}
@@
 \end{align*}
+The same way, let us define
+\begin{equation*}
+S^{ois}_{a,b}(t) = \frac{P_{ois}(t,T^{E}_a) - P_{ois}(t,T^{E}_b)}{01(t,T_a,T_b)}. 
+\end{equation*}
+
 We suppose, that we have a flow in $T_a < T_p < T_b$ with value $S_{a,b}(T_a)$. Then, the present value of this flow
@@
 \begin{equation*}
-M(t) = f(S_{a,b}(t))
+M(t) = f(S^{ois}_{a,b}(t))
 \end{equation*}
@@
 \begin{align*}
-f(S_{a,b}(T_a)) &= \mathbb{E}^{\mathbb{Q}^{01(a,b)}}\left(f(S_{a,b}(T_a))\right) + \int_{0}^{T_a} \mathbb{E}_s^{01(a,b)}\left( D_s (f(S_{a,b}(T_a))) \right) dW^{01(a,b)}_{s} \\
-&= \frac{P_{ois}(0,T_p) }{01(0,T_a,T_b)} + \int_{0}^{T_a} \mathbb{E}_s^{01(a,b)}\left(f^{\prime}(S_{a,b}(T_a)) \partial_{x}S_{a,b}(T_a) D_s x_{T_a} \right) dW^{01(a,b)}_{s}. 
+f(S^{ois}_{a,b}(T_a)) &= \mathbb{E}^{\mathbb{Q}^{01(a,b)}}\left(f(S^{ois}_{a,b}(T_a)\right) + \int_{0}^{T_a} \mathbb{E}_s^{01(a,b)}\left( D_s (f(S^{ois}_{a,b}(T_a)) \right) dW^{01(a,b)}_{s} \\
+&= \frac{P_{ois}(0,T_p) }{01(0,T_a,T_b)} + \int_{0}^{T_a} \mathbb{E}_s^{01(a,b)}\left(f^{\prime}(S^{ois}_{a,b}(T_a) \partial_{x}S^{ois}_{a,b}(T_a) D_s x_{T_a} \right) dW^{01(a,b)}_{s}. 
 \end{align*}
 Therefore, we can define the convexity adjustment for a CMS the next way
-\begin{equation*}
-CA_{CMS}(T_a,T_b) = 01(0,T_a,T_b) \mathbb{E}^{\mathbb{Q}^{01(a,b)}}\left(S_{a,b}(T_a) \int_{0}^{T_a} \mathbb{E}_s^{01(a,b)}\left( f^{\prime}(S_{a,b}(T_a)) \partial_{x}S_{a,b}(T_a) D_s x_{T_a} \right) dW^{01(a,b)}_{s} \right).
-\end{equation*}
-Now if we apply the adjoint of the Malliavin derivative (see Elisa-David) we get
+\begin{align*}
+CA_{CMS}(T_a,T_b) = \\
+01(0,T_a,T_b) \mathbb{E}^{\mathbb{Q}^{01(a,b)}}\left(S_{a,b}(T_a) \int_{0}^{T_a} \mathbb{E}_s^{01(a,b)}\left( f^{\prime}(S^{ois}_{a,b}(T_a)) \partial_{x}S^{ois}_{a,b}(T_a) D_s x_{T_a} \right) dW^{01(a,b)}_{s} \right)
+\end{align*}
+Now if we apply the adjoint operator of the Malliavin derivative (see Elisa-David) we get
 
-\begin{align}
-CA_{CMS}(T_a,T_b) &= 01(0,T_a,T_b) \mathbb{E}^{\mathbb{Q}^{01(a,b)}}\left( \int_{0}^{T_a} \partial_{x}S_{a,b}(T_a) D_s x_{T_a} \mathbb{E}_s^{01(a,b)}\left(f^{\prime}(S_{a,b}(T_a)) \partial_{x}S_{a,b}(T_a) D_s x_{T_a} \right) ds \right) \nonumber \\
-&\approx 01(0,T_a,T_b)  \mathbb{E}^{\mathbb{Q}^{01(a,b)}}\left( \int_{0}^{T_a} \left(\partial_{x}S_{a,b}(0)\right)^{2} f^{\prime}(S_{a,b}(0))  D_s x_{T_a} \mathbb{E}_s^{01(a,b)}\left(D_s x_{T_a} \right) ds \right) \nonumber \\
-& \approx 01(0,T_a,T_b)  \mathbb{E}^{\mathbb{Q}^{01(a,b)}}\left( \int_{0}^{T_a} \left(\partial_{x}S_{a,b}(0)\right)^{2} f^{\prime}(S_{a,b}(0)) \beta(s,T_a,x_0,\hat{y}_{s})  D_s x_{T_a}  ds \right)
-\end{align}
+\begin{align*}
+&CA_{CMS}(T_a,T_b)  \\
+&=01(0,T_a,T_b) \mathbb{E}^{\mathbb{Q}^{01(a,b)}}\left( \int_{0}^{T_a} \partial_{x}S_{a,b}(T_a) D_s x_{T_a} \mathbb{E}_s^{01(a,b)}\left(f^{\prime}(S^{ois}_{a,b}(T_a)) \partial_{x}S^{ois}_{a,b}(T_a) D_s x_{T_a} \right) ds \right) \nonumber \\
+&\approx 01(0,T_a,T_b)  \mathbb{E}^{\mathbb{Q}^{01(a,b)}}\left( \int_{0}^{T_a} \partial_{x}S_{a,b}(T_a, x_0, y_0) \partial_{x}S^{ois}_{a,b}(T_a, x_0, y_0) f^{\prime}(S^{ois}_{a,b}(T_a, x_0, y_0)  D_s x_{T_a} \mathbb{E}_s^{01(a,b)}\left(D_s x_{T_a} \right) ds \right) \nonumber \\
+& \approx 01(0,T_a,T_b)  \mathbb{E}^{\mathbb{Q}^{01(a,b)}}\left( \int_{0}^{T_a} \partial_{x}S_{a,b}(T_a, x_0, y_0) \partial_{x}S^{ois}_{a,b}(T_a, x_0, y_0) f^{\prime}(S^{ois}_{a,b}(T_a, x_0, y_0) \beta(s,T_a,x_0,\hat{y}_{s})  D_s x_{T_a}  ds \right)
+\end{align*}
 
@@
 \begin{equation*}
-\mathbb{E}^{\mathbb{Q}^{01(a,b)}}\left( D_s x_{T_a} \right) \approx \beta(s,T_a,x_0,\hat{y}_{s}) \exp\left(-\int_{s}^{T_a} \frac{\int_{T_a}^{T_b} P_{ois}(u,u^{\prime},x_0,\hat{y}_u) \nu(t,u^{\prime}) du^{\prime}}{01^{c}(u,T_a,T_b,x_0,\hat{y}_u)} \partial_x \beta(u,t_0,x_0,\hat{y}_u) du \right)
+\mathbb{E}_s^{\mathbb{Q}^{01(a,b)}}\left( D_s x_{T_a} \right) \approx \beta(s,T_a,x_0,\hat{y}_{s}) \exp\left(-\int_{s}^{T_a} \frac{\int_{T_a}^{T_b} P_{ois}(u,u^{\prime},x_0,\hat{y}_u) \nu(t,u^{\prime}) du^{\prime}}{01^{c}(u,T_a,T_b,x_0,\hat{y}_u)} \partial_x \beta(u,t_0,x_0,\hat{y}_u) du \right)
 \end{equation*}
@@
 
-\begin{equation}\label{cms_adjustment}
-CA_{CMS}(T_a,T_b) \approx 01(0,T_a,T_b) \int_{0}^{T_a} \left(\partial_{x}S_{a,b}(0)\right)^{2} f^{\prime}(S_{a,b}(0)) \beta^{2}(s,T_a,x_0,\hat{y}_{u}) \Omega(s, T_a)    ds
-\end{equation}
+\begin{align}\label{cms_adjustment}
+&CA_{CMS}(T_a,T_b) \nonumber \\
+&\approx 01(0,T_a,T_b) \int_{0}^{T_a} \partial_{x}S_{a,b}(T_a, x_0, y_0) \partial_{x}S^{ois}_{a,b}(T_a, x_0, y_0)  f^{\prime}(S^{ois}_{a,b}(T_a, x_0, y_0)) \beta^{2}(s,T_a,x_0,\hat{y}_{s}) \Omega(s, T_a)    ds
+\end{align}
 with 
-$$\Omega(s, T_a) = \exp\left(-\int_{s}^{T_a} \frac{\int_{T_a}^{T_b} P_{ois}(u,u^{\prime},x_0,\hat{y}_u) \nu(t,u^{\prime}) du^{\prime}}{01^{c}(u,T_a,T_b,x_0,\hat{y}_u)} \partial_x \beta(u,t_0,x_0,\hat{y}_u) du \right)
+$$\Omega(s, T_a) = \exp\left(-2\int_{s}^{T_a} \frac{\int_{T_a}^{T_b} P_{ois}(u,u^{\prime},x_0,\hat{y}_u) \nu(t,u^{\prime}) du^{\prime}}{01^{c}(u,T_a,T_b,x_0,\hat{y}_u)} \partial_x \beta(u,t_0,x_0,\hat{y}_u) du \right)
 $$
@@
 Therefore (\ref{cms_adjustment}) is reduced to
-$$
-01(0,T_a,T_b) \int_{0}^{T_a} \left(\partial_{x}S_{a,b}(0)\right)^{2} f^{\prime}(S_{a,b}(0)) \beta^{2}(s,T_a,x_0,\hat{y}_{u}) ds
-$$
+\begin{equation}\label{cms_general_convexity}
+01(0,T_a,T_b) \int_{0}^{T_a} \partial_{x}S_{a,b}(T_a,x_0,y_0) \partial_{x}S^{ois}_{a,b}(T_a,x_0,y_0) f^{\prime}(S^{ois}_{a,b}(T_a,x_0,y_0)) \beta^{2}(s,T_a,x_0,\hat{y}_{s}) ds
+\end{equation}
+A common practice in market, it is suppose that $f(x)=\alpha x + \beta$ (TSR model).
+We must to impose two equations in order to get $\alpha$ and $\beta$.
+The first equation follows straightforward from the definition of $M(t,T_p)$.
+Since, $M(t,T_p)$ is a $01(a,b)-$martingale we must have that
+\begin{equation*}
+\mathbb{E}^{01(a,b)}\left(\alpha S^{ois}_{a,b}(T_a) + \beta \right) = \frac{P_{ois}(0,T_p)}{01(0,T_a,T_b)}.
+\end{equation*}
+Therefore
+\begin{equation*}
+\beta = \frac{P_ois(0,T_p)}{01(0,T_a,T_b,x_0,y_0)} - \alpha S^{ois}_{a,b}(0,x_0,y_0).
+\end{equation*}
+Under a separable HJM dynamic we must have that
+\begin{equation*}
+\alpha \partial_{x} S^{ois}_{a,b}(T_a,x_0,y_0) = - M(0,T_p)\left(G(T_a,T_p)+\frac{\partial_x 01(T_a,T_a,T_b,x_0,y_0)}{01(T_a,T_a,T_b,x_0,y_0)}\right).
+\end{equation*}
+Then
+\begin{equation*}
+\alpha = -\frac{M(T_a,T_p)\left(G(T_a,T_p)+\frac{\partial_x 01(T_a,T_a,T_b,x_0,y_0)}{01(T_a,T_a,T_b,x_0,y_0)}\right)}{\partial_{x} S^{ois}_{a,b}(T_a,x_0,y_0)}.
+\end{equation*}
+Then from the last equalities, we can approximate the convexity adjustment of a CMS rate as
+\begin{align*}
+CA_{CMS}(T_a,T_b)\\
+\approx - P_{ois}(0,T_p,x_0,y_0) \left(G(T_a,T_p) +\frac{\partial_x 01(T_a,T_a,T_b,x_0,y_0)}{01(T_a,T_a,T_b,x_0,y_0)}\right) \partial_{x}S_{a,b}(0,x_0,y_0) \int_{0}^{T_a}  \beta^{2}(s,T_a,x_0,\hat{y}_{u}) ds
+\end{align*}
+In the next figure, we can see the convexity adjustment for a CMS where the tenor for the underlying swap is 5Y using the last approximation and Monte Carlo method
 

### 2022-10-25 ConvexityAdjustment-Lib/ConvexityAdjusmentUnitTests/CmsConvexity.cs

@@ -1,3 +1,4 @@
+using System.Security.Cryptography.X509Certificates;
 using NUnit.Framework;
 using ql = QLNet;
 
@@ -34,15 +35,15 @@ namespace ConvexityAdjustmentUnitTests
             var tenorSwap = new ql.Period(5, ql.TimeUnit.Years);
 
             // Convexity test
-            var periodToCompute = new ql.Period(1, ql.TimeUnit.Years);
+            var periodToCompute = new ql.Period(20, ql.TimeUnit.Years);
             int numberOftimes = 1;
-            
+
             List<ql.Date> datesToCompute = new List<ql.Date>{calendar.advance(startDate, periodToCompute)};
             List<double> deltaTimes = new List<double>{dc.yearFraction(startDate, datesToCompute[0])};
             List<double> f0ts = new List<double>{discountCurve.link.forwardRate(deltaTimes[0], deltaTimes[0], ql.Compounding.Simple, ql.Frequency.NoFrequency).rate()};
             List<double> hjmAdjustment = new List<double>{ConvexityAdjustment_Lib.HullWhite.hjmAdjustment(deltaTimes[0], k, sigma)};
             var drift = new List<double>{ConvexityAdjustment_Lib.HullWhite.forwardMeasureAdjustment(deltaTimes[0], k, sigma)};
-
+            
             for (int i = 1; i < numberOftimes; i++)
             {
                 datesToCompute.Add(calendar.advance(datesToCompute[i-1], periodToCompute));
@@ -53,7 +54,7 @@ namespace ConvexityAdjustmentUnitTests
             }
             
             // MC
-            int numberOfSimulations = 200000;
+            int numberOfSimulations = 400000;
             ulong seed = 123545;
             
             // outputs
@@ -98,7 +99,7 @@ namespace ConvexityAdjustmentUnitTests
                 
                 partialOisSwap.Add(swapOisDerivative);
                 partialVanillaSwap.Add(swapVanillaDerivative);
-
+                
                 var payDate = calendar.advance(datesToCompute[j], payPeriod,
                     ql.BusinessDayConvention.ModifiedFollowing);
                 
@@ -115,8 +116,6 @@ namespace ConvexityAdjustmentUnitTests
             
                 ql.PathGenerator<ql.IRNG> generator = new ql.PathGenerator<ql.IRNG>(process, deltaTimes[j], 1, rsg, false);
 
-                // var endDate = calendar.advance(datesToCompute[j], tenorSwap,
[…]

### 2022-10-25 ConvexityAdjustment-Lib/ConvexityAdjustment-Lib/HullWhite.cs

@@ -85,15 +85,17 @@ namespace ConvexityAdjustment_Lib
             return logR01 - (i1 + i2);
         }
 
-        public static double convexityCms(ql.Handle<ql.YieldTermStructure> discountCurve,  ql.Date valueDate, ql.Date ta, ql.Date tb, ql.Date tp, double partialSwap, double annuity,
-            double partialOisAnnuity, double partialVanillaSwap, ql.DayCounter dc, double k, double sigma)
+        public static double convexityCms(ql.Handle<ql.YieldTermStructure> discountCurve,  ql.Date valueDate, ql.Date ta, ql.Date tb, ql.Date tp, double annuity,
+            double partialAnnuity, double partialVanillaSwap, ql.DayCounter dc, double k, double sigma)
         {
-            var d0 = dc.yearFraction(valueDate, ta);
+            var dta = dc.yearFraction(valueDate, ta);
             var dtp = dc.yearFraction(valueDate, tp);
-            var dfOis = discountCurve.link.discount(tp);
-            var m = sigma * sigma * beta(0.0, d0, 2.0 * k);
-
-            return -dfOis * (beta(d0, dtp, k) + partialOisAnnuity / annuity) * partialSwap * m; 
+            
+            var dFtp = discountCurve.link.discount(tp);
+            var m = - dFtp   * (beta(dta, dtp, k) + partialAnnuity / annuity);
+            
+            var alpha = sigma * sigma * beta(0.0, dta, 2.0 * k);
+            return m * alpha * partialVanillaSwap;
             
         }
 

### 2022-10-27 ConvexityAdjustment-Lib/ConvexityAdjusmentUnitTests/CmsConvexity.cs
# new way to compute cms convexity

@@ -20,7 +20,7 @@ namespace ConvexityAdjustmentUnitTests
 
             // Curves
             double discountFlatRate = 0.015;
-            double basisSpread = 0.01;
+            double basisSpread = 0.0;
             ql.Quote quoteDiscountRate = new ql.SimpleQuote(discountFlatRate);
             ql.Quote quoteSpread = new ql.SimpleQuote(basisSpread);
             
@@ -35,7 +35,7 @@ namespace ConvexityAdjustmentUnitTests
             var tenorSwap = new ql.Period(5, ql.TimeUnit.Years);
 
             // Convexity test
-            var periodToCompute = new ql.Period(20, ql.TimeUnit.Years);
+            var periodToCompute = new ql.Period(1, ql.TimeUnit.Years);
             int numberOftimes = 1;
 
             List<ql.Date> datesToCompute = new List<ql.Date>{calendar.advance(startDate, periodToCompute)};
@@ -67,6 +67,8 @@ namespace ConvexityAdjustmentUnitTests
             var annuity = new List<Tuple<double,double>>();
             var partialOisSwap = new List<double>();
             var partialVanillaSwap = new List<double>();
+            var swapRates = new List<double>();
+            var swapOisRates = new List<double>();
             
             // Test
             for (int j = 0; j < numberOftimes; j++)
@@ -99,6 +101,14 @@ namespace ConvexityAdjustmentUnitTests
                 
                 partialOisSwap.Add(swapOisDerivative);
                 partialVanillaSwap.Add(swapVanillaDerivative);
+                swapRates.Add(staticSwap.fairRate());
+                
+                // ois swap rate
+                var tb =  calendar.advance(datesToCompute[j], tenorSwap,
+                    ql.BusinessDayConvention.ModifiedFollowing);
+                var dfta = discountCurve.link.discount(datesToCompute[j]);
+                var oisSwapRate = (discountCurve.link.discount(datesToCompute[j]) - discountCurve.link.discount(tb)) / (dfta * annuity[j].Item1); 
+                swapOisRates.Add(oisSwapRate);
                 
                 var payDate = calendar.advance(datesToCompute[j], payPeriod,
                     ql.BusinessDayConvention.ModifiedFollowing);
@@ -176,9 +186,10 @@ namespace ConvexityAdjustmentUnitTests
                 var errorRi = rtaMc - f0ts[j] / discountCurve.link.discount(tP);
                 
                 // Analytic convexity adjustment
[…]

### 2022-10-27 ConvexityAdjustment-Lib/ConvexityAdjustment-Lib/HullWhite.cs

@@ -86,14 +86,15 @@ namespace ConvexityAdjustment_Lib
         }
 
         public static double convexityCms(ql.Handle<ql.YieldTermStructure> discountCurve,  ql.Date valueDate, ql.Date ta, ql.Date tb, ql.Date tp, double annuity,
-            double partialAnnuity, double partialVanillaSwap, ql.DayCounter dc, double k, double sigma)
+            double partialAnnuity, double partialVanillaSwap, double partialOisSwap, double swapRate, double swapOisRate, ql.DayCounter dc, double k, double sigma)
         {
             var dta = dc.yearFraction(valueDate, ta);
             var dtp = dc.yearFraction(valueDate, tp);
             
             var dFtp = discountCurve.link.discount(tp);
+            var dFta = discountCurve.link.discount(ta);
             var m = - dFtp   * (beta(dta, dtp, k) + partialAnnuity / annuity);
-            
+
             var alpha = sigma * sigma * beta(0.0, dta, 2.0 * k);
             return m * alpha * partialVanillaSwap;
             

### 2022-10-30 Latex/paper.tex
# new appendix

@@
 \end{align*}
-Now if we apply the adjoint operator of the Malliavin derivative (see Elisa-David) we get
-
+Now if we use again the Clark-Ocone representation, but in this case for $S_{a,b}(T_a)$, we can do the next approximation
 \begin{align*}
-&CA_{CMS}(T_a,T_b)  \\
-&=01(0,T_a,T_b) \mathbb{E}^{\mathbb{Q}^{01(a,b)}}\left( \int_{0}^{T_a} \partial_{x}S_{a,b}(T_a) D_s x_{T_a} \mathbb{E}_s^{01(a,b)}\left(f^{\prime}(S^{ois}_{a,b}(T_a)) \partial_{x}S^{ois}_{a,b}(T_a) D_s x_{T_a} \right) ds \right) \nonumber \\
-&\approx 01(0,T_a,T_b)  \mathbb{E}^{\mathbb{Q}^{01(a,b)}}\left( \int_{0}^{T_a} \partial_{x}S_{a,b}(T_a, x_0, y_0) \partial_{x}S^{ois}_{a,b}(T_a, x_0, y_0) f^{\prime}(S^{ois}_{a,b}(T_a, x_0, y_0)  D_s x_{T_a} \mathbb{E}_s^{01(a,b)}\left(D_s x_{T_a} \right) ds \right) \nonumber \\
-& \approx 01(0,T_a,T_b)  \mathbb{E}^{\mathbb{Q}^{01(a,b)}}\left( \int_{0}^{T_a} \partial_{x}S_{a,b}(T_a, x_0, y_0) \partial_{x}S^{ois}_{a,b}(T_a, x_0, y_0) f^{\prime}(S^{ois}_{a,b}(T_a, x_0, y_0) \beta(s,T_a,x_0,\hat{y}_{s})  D_s x_{T_a}  ds \right)
+CA_{CMS}(T_a,T_b) &\approx 01(0,T_a,T_b)  f^{\prime}(S^{ois}_{a,b}(0)) \mathbb{E}^{\mathbb{Q}^{01(a,b)}}\left(S_{a,b}(T_a) \left( S^{ois}_{a,b}(T_a) - S^{ois}_{a,b}(0)\right)\right) \\
+&= 01(0,T_a,T_b)  f^{\prime}(S^{ois}_{a,b}(0)) \mathbb{E}^{\mathbb{Q}^{01(a,b)}}\left(S^{ois}_{a,b}(T_a)S_{a,b}(T_a) -  S_{a,b}(0) S^{ois}_{a,b}(0)\right)
 \end{align*}
-
-\begin{remark}\label{drift_01_spot_measure}
-Before to continue, we must to calculate the Girsanov's measure change from $\mathbb{Q}$ to $\mathbb{Q}^{01(a,b)}$.
-In order to achieve this target, we will use a continuous version of $01(t,T_a,T_b)$ i.e
-\begin{equation*}
-01^{c}(t,T_a,T_b) = \int_{T_a}^{T_b} P_{ois}(t,u) du.
-\end{equation*}
-It is easy to see that if we define $z_t=\frac{01^{c}(t,T_a,T_b)}{\beta_t}$ and apply Itô's formula we get
-\begin{equation*}
-dW^{01(a,b)}_t = dW^{\mathbb{Q}}_t + \lambda_{t}dt 
-\end{equation*}
-where $\lambda_t = \frac{\int_{T_a}^{T_b} P_{ois}(t,u) \nu(t,u) du}{01^{c}(t,T_a,T_b)}$. Then we can do the next approximation for $\lambda_t$
-\begin{equation*}
-\hat{\lambda}_t \approx \frac{\int_{T_a}^{T_b} P_{ois}(t,u,x_0,\hat{y}_t) \nu(t,u) du}{01^{c}(t,T_a,T_b,x_0,\hat{y}_t)} 
-\end{equation*}
-\end{remark}
-Now, if we apply (\ref{drift_01_spot_measure}) we get that 
-\begin{equation*}
-\mathbb{E}_s^{\mathbb{Q}^{01(a,b)}}\left( D_s x_{T_a} \right) \approx \beta(s,T_a,x_0,\hat{y}_{s}) \exp\left(-\int_{s}^{T_a} \frac{\int_{T_a}^{T_b} P_{ois}(u,u^{\prime},x_0,\hat{y}_u) \nu(t,u^{\prime}) du^{\prime}}{01^{c}(u,T_a,T_b,x_0,\hat{y}_u)} \partial_x \beta(u,t_0,x_0,\hat{y}_u) du \right)
-\end{equation*}
-Therefore we have the next for the convexity adjustment
+Where we have used that $S_{a,b}(t)$ and $S^{ois}_{a,b}(T_a)$ are $01(a,b)$-martingale. Also, if we use Itô formula we get that
+\begin{align*}
+dS^{ois}_{a,b}(t,x_t,y_t) &= \partial_{x}S^{ois}_{a,b}(t,x_t,y_t)\eta(t,x_t,y_t)dW^{01(a,b)}  \\
+dS_{a,b}(t,x_t,y_t) &= \partial_{x}S_{a,b}(t,x_t,y_t)\eta(t,x_t,y_t)dW^{01(a,b)} 
+\end{align*}
+with initial condition respectivaly $S^{ois}_{a,b}(0)$ and $S_{a,b}(0)$. Then we have that
+\begin{align*}
+\mathbb{E}^{\mathbb{Q}^{01(a,b)}}\left(S^{ois}_{a,b}(T_a)S_{a,b}(T_a) \right) &= \mathbb{E}^{\mathbb{Q}^{01(a,b)}}\left(\int_0^{T_a} \partial_{x}S_{a,b}(u,x_u,y_u) \partial_{x}S^{ois}_{a,b}(u,x_u,y_u)  \eta^{2}(u,x_u,y_u)
+du \right)  + S_{a,b}(0) S^{ois}_{a,b}(0) \\
+&\approx  \partial_{x}S_{a,b}(0) \partial_{x}S^{ois}_{a,b}(0)\int_0^{T_a} \eta^{2}(u,x_0,\hat{y}_u) + S_{a,b}(0) S^{ois}_{a,b}(0).
+du
+\end{align*}
+Therefore, if se use the last equality we can approximate $CA_{CMS}(T_a,T_b)$ the next way
 
@@
 {
+\begin{equation}\label{cms_adjustment}
+CA_{CMS}(T_a,T_b) \approx 01(0,T_a,T_b)  f^{\prime}(S^{ois}_{a,b}(0)) \partial_{x}S_{a,b}(0) \partial_{x}S^{ois}_{a,b}(0)\int_0^{T_a} \eta^{2}(u,x_0,\hat{y}_u) du
+\end{equation}
+}}
 
-\begin{align}\label{cms_adjustment}
-&CA_{CMS}(T_a,T_b) \nonumber \\
-&\approx 01(0,T_a,T_b) \int_{0}^{T_a} \partial_{x}S_{a,b}(T_a, x_0, y_0) \partial_{x}S^{ois}_{a,b}(T_a, x_0, y_0)  f^{\prime}(S^{ois}_{a,b}(T_a, x_0, y_0)) \beta^{2}(s,T_a,x_0,\hat{y}_{s}) \Omega(s, T_a)    ds
-\end{align}
-with 
-$$\Omega(s, T_a) = \exp\left(-2\int_{s}^{T_a} \frac{\int_{T_a}^{T_b} P_{ois}(u,u^{\prime},x_0,\hat{y}_u) \nu(t,u^{\prime}) du^{\prime}}{01^{c}(u,T_a,T_b,x_0,\hat{y}_u)} \partial_x \beta(u,t_0,x_0,\hat{y}_u) du \right)
-$$
-}}
 \begin{example}
@@
 $$
-\partial_x \beta(u,t_0,x_0,\hat{y}_u)=0
+\eta(t,x_t, y_t) = \sigma\exp(-kt)
 $$
@@
 Therefore (\ref{cms_adjustment}) is reduced to
-\begin{equation}\label{cms_general_convexity}
-01(0,T_a,T_b) \int_{0}^{T_a} \partial_{x}S_{a,b}(T_a,x_0,y_0) \partial_{x}S^{ois}_{a,b}(T_a,x_0,y_0) f^{\prime}(S^{ois}_{a,b}(T_a,x_0,y_0)) \beta^{2}(s,T_a,x_0,\hat{y}_{s}) ds
+\begin{equation}\label{hullwhite_cms_convexity}
+01(0,T_a,T_b)  f^{\prime}(S^{ois}_{a,b}(0)) \partial_{x}S_{a,b}(T_a) \partial_{x}S^{ois}_{a,b}(T_a) \frac{ \sigma^2(1-\exp(-2kT_a))}{2k} 
 \end{equation}
@@
 \begin{equation*}
-\beta = \frac{P_ois(0,T_p)}{01(0,T_a,T_b,x_0,y_0)} - \alpha S^{ois}_{a,b}(0,x_0,y_0).
+\beta = \frac{P_{ois}(0,T_p)}{01(0,T_a,T_b,x_0,y_0)} - \alpha S^{ois}_{a,b}(0,x_0,y_0).
 \end{equation*}
@@
 \begin{equation*}
-\alpha \partial_{x} S^{ois}_{a,b}(T_a,x_0,y_0) = - M(0,T_p)\left(G(T_a,T_p)+\frac{\partial_x 01(T_a,T_a,T_b,x_0,y_0)}{01(T_a,T_a,T_b,x_0,y_0)}\right).
+\alpha \partial_{x} S^{ois}_{a,b}(0) = - M(0,T_p)\left(G(T_a,T_p)+\frac{\partial_x 01(0,T_a,T_b)}{01(0,T_a,T_b)}\right).
 \end{equation*}
@@
 \begin{equation*}
-\alpha = -\frac{M(T_a,T_p)\left(G(T_a,T_p)+\frac{\partial_x 01(T_a,T_a,T_b,x_0,y_0)}{01(T_a,T_a,T_b,x_0,y_0)}\right)}{\partial_{x} S^{ois}_{a,b}(T_a,x_0,y_0)}.
+\alpha = -\frac{M(0,T_p)\left(G(T_a,T_p)+\frac{\partial_x 01(0,T_a,T_b)}{01(0,T_a,T_b)}\right)}{\partial_{x} S^{ois}_{a,b}(0)}.
 \end{equation*}
@@
 \begin{align*}
-CA_{CMS}(T_a,T_b)\\
-\approx - P_{ois}(0,T_p,x_0,y_0) \left(G(T_a,T_p) +\frac{\partial_x 01(T_a,T_a,T_b,x_0,y_0)}{01(T_a,T_a,T_b,x_0,y_0)}\right) \partial_{x}S_{a,b}(0,x_0,y_0) \int_{0}^{T_a}  \beta^{2}(s,T_a,x_0,\hat{y}_{u}) ds
+CA_{CMS}(T_a,T_b) \\ 
+\approx 01(0,T_a,T_b) \alpha \partial_{x}S_{a,b}(0) \partial_{x}S^{ois}_{a,b}(0) \frac{ \sigma^2(1-\exp(-2kT_a))}{2k}  \\   
+= - P_{ois}(0,T_p) \left(G(T_a,T_p)+\frac{\partial_x 01(0,T_a,T_b)}{01(0,T_a,T_b)}\right) \partial_{x}S_{a,b}(0)  \frac{ \sigma^2(1-\exp(-2kT_a))}{2k}
 \end{align*}
@@
 
-\section{Conclusion}\label{sec:Conclusion}
+\section*{Appendix}
+\appendix
+\renewcommand{\thesection}{\Alph{section}.\arabic{section}}
+\section{Malliavin derivative calculations}
+
+\subsection{Approximation of $\mathbb{E}_s^{T_p}\left(D_s x_{T_a}\right)$}
+\label{expected_forward_measure_malliavin_derivative_x_t}
+From (\ref{short_rate_cheyette}) is easy to show that
+\begin{equation*}
+x_{T_a} = \int_{0}^{T_a} \exp\left(-\int_{s}^{T_a}k_u du\right) y_u du + \int_{0}^{T_a}  \exp\left(-\int_{s}^{T_a}k_u du \right) \eta(u,x_u,y_u) dW_u^{\mathbb{Q}}  
+\end{equation*}
+Therefore, we have that
 

### 2022-10-30 Latex/paper.tex
# Some modifications to estimate D_s_x_T_a

@@
 \begin{equation*}
-dW^{\mathbb{Q}^{t_2}} = dW^{\mathbb{Q}} + \nu(t,T) dt. 
+dW^{\mathbb{Q}^{t_2}} = dW^{\mathbb{Q}} + \nu(t,T_2) dt. 
 \end{equation*}
@@
 \end{equation}
-From (\ref{short_rate_cheyette}) y we define $\beta(s,t, x, y) = \exp\left(-\int_{s}^{t} k_{u} \right) \eta(s, x, y)$ we have that
-\begin{equation}\label{malliavin_derive_x}
-D_s x_{t_0} = \beta(s,t_0, x_s, y_s)M(s,t_0)
+Now from (\ref{approximation_D_s_x_t}) with $T_a=t_0$ and $\beta(t,t_0,x,y) = \exp\left(-\int_{s}^{T_a}k_u du \right) \eta(u,x,y)$ we have that
+\begin{align*}
+D_s L_{E}(t_0,t_1,t_2) &\approx \frac{H(t_0,t_1)}{\delta_{t_1,t_2}H(t_0,t_2)}\frac{\left(\partial_{x}P_{ois}(t_0,t_1)P_{ois}(t_0,t_2) - \partial_{x}P_{ois}(t_0,t_2) P_{ois}(t_0,t_1) \right)}{P^{2}_{ois}(t_0,t_2)} \beta(t,t_0,\bar{x}_s,\bar{y}_s)\bar{M}(s,t_0) \nonumber \\
+\approx& \frac{P_{E}(0,t_1)}{\delta_{t_1,t_2} P_{E}(0,t_2)} \left(G(t_0,t_2) \frac{P_{ois}(0,t_2)}{P_{ois}(0,t_0)} - G(t_0,t_1) \frac{P_{ois}(0,t_1)}{P_{ois}(0,t_0)} \right)\beta(t,t_0,\bar{x}_s,\bar{y}_s)\bar{M}(s,t_0)
+\end{align*}
+and therefore
+\begin{equation}\label{approximation_clarkocone}
+\mathbb{E}_s\left( D_s L_{E}(t_0,t_1,t_2) \right) = \frac{P_{E}(0,t_1)}{\delta_{t_1,t_2} P_{E}(0,t_2)} \left(G(t_0,t_2) \frac{P_{ois}(0,t_2)}{P_{ois}(0,t_0)} - G(t_0,t_1) \frac{P_{ois}(0,t_1)}{P_{ois}(0,t_0)}\right)\beta(t,t_0,x_0,\bar{y}_s)\bar{M}(s,t_0)
 \end{equation}
-where $M(s,t_0)=\exp\left(-\frac{\int_{s}^{t_0} \left(\partial_x \beta(u,t_0,x_s,y_s)\right)^{2} du}{2} + \int_{s}^{t_0} \partial_x \beta(u,t_0,x_s,y_s) dW^{\mathbb{Q}}_u \right)$. 
-Then, we have that
-\begin{align*}
-D_s L_{E}(t_0,t_1,t_2) &= \frac{H(t_0,t_1)}{\delta_{t_1,t_2}H(t_0,t_2)}\frac{\left(\partial_{x}P_{ois}(t_0,t_1)P_{ois}(t_0,t_2) - \partial_{x}P_{ois}(t_0,t_2) P_{ois}(t_0,t_1) \right)}{P^{2}_{ois}(t_0,t_2)} \beta(s,t_0, x_s, y_s)M(s,t_0) \nonumber \\
-\approx& \frac{P_{E}(0,t_1)}{\delta_{t_1,t_2} P_{E}(0,t_2)} \left(G(t_0,t_2) \frac{P_{ois}(0,t_2)}{P_{ois}(0,t_0)} - G(t_0,t_1) \frac{P_{ois}(0,t_1)}{P_{ois}(0,t_0)} \right)\beta(s,t_0, x_s, y_s)M(s,t_0).
-\end{align*}
-It is a common practice, freeze the state variables of the model to achieve some approximations. We can approximate $x_s$ and $y_s$ the next way
-\begin{align*}
-x_s &\approx x_0 \nonumber \\
-y_s &\approx y_0 + \int_{0}^{s} \exp\left(-2\int_{u}^{s} k_{u^{\prime}} du^{\prime} \right) \eta(u,x_0,y_0) du
-\end{align*}
-Therefore, 
-\begin{equation}\label{approximation_clarkocone}
-\mathbb{E}_s\left( D_s L_{E}(t_0,t_1,t_2) \right) = \frac{P_{E}(0,t_1)}{\delta_{t_1,t_2} P_{E}(0,t_2)} \left(G(t_0,t_2) \frac{P_{ois}(0,t_2)}{P_{ois}(0,t_0)} - G(t_0,t_1) \frac{P_{ois}(0,t_1)}{P_{ois}(0,t_0)}\right)\beta(s,t_0, x_0, \hat{y}_s)
-\end{equation}
-where $\hat{y}_s = y_0 + \int_{0}^{s} \exp\left(-2\int_{u}^{s} k_{u^{\prime}} du^{\prime} \right) \eta(u,x_0,y_0) du$.
 Now, from (\ref{ca_general_future}) and (\ref{approximation_clarkocone}) we have the next approximation for the convexity adjustmet for future
-
 \hspace{1cm}
@@
 {
-\begin{equation}\label{ca_approximation_futures}
-CA(t,t_0,t_1) \approx \frac{P_{E}(0,t_1)}{\delta_{t_1,t_2} P_{E}(0,t_2)} \left(G(t_0,t_2) \frac{P_{ois}(0,t_2)}{P_{ois}(0,t_0)} - G(t_0,t_1) \frac{P_{ois}(0,t_1)}{P_{ois}(0,t_0)}\right) \int_{0}^{t_0}  \beta(s,t_0, x_0, \hat{y}_s) \nu(s,t_2) ds.
-\end{equation}
+\begin{align}\label{ca_approximation_futures}
+CA(t,t_0,t_1)& \nonumber \\ 
+\approx& \frac{P_{E}(0,t_1)}{\delta_{t_1,t_2} P_{E}(0,t_2)} \left(G(t_0,t_2) \frac{P_{ois}(0,t_2)}{P_{ois}(0,t_0)} - G(t_0,t_1) \frac{P_{ois}(0,t_1)}{P_{ois}(0,t_0)}\right) \int_{0}^{t_0} \beta(s,t_0,x_0,\hat{y}_s) \nu(s,t_2) ds.
+\end{align}
 }}
+
 \begin{example}\label{example_ca_future}
@@
 \end{equation*}
-then for $t < t_0$ from (\ref{clark-okone}) and (\ref{malliavin_derive_x}), we have the next representation for $I(t_0,t_1)$
+then for $t < t_0$ from (\ref{clark-okone}) and (\ref{approximation_D_s_x_t}), we have the next representation for $I(t_0,t_1)$
 \begin{align}\label{apprx_I_t0_t1}
-I(t_0,t_1) &= \mathbb{E}^{\mathbb{Q}}\left(I(t_0,t_1)\right) + \int_{0}^{t_1}\int_{\max(s, t_{0})}^{t_1}  \mathbb{E}_s^{\mathbb{Q}}\left(\beta(s,u,x_s,y_s) M(s,u) \right) du dW_s^{\mathbb{Q}} \nonumber \\
+I(t_0,t_1) &= \mathbb{E}^{\mathbb{Q}}\left(I(t_0,t_1)\right) + \int_{0}^{t_1}\int_{\max(s, t_{0})}^{t_1}  \mathbb{E}_s^{\mathbb{Q}}\left(\beta(s,u,x_s,y_s) \bar{M}(s,u) \right) du dW_s^{\mathbb{Q}} \nonumber \\
 &\approx \mathbb{E}^{\mathbb{Q}}\left(I(t_0,t_1)\right) + \int_{0}^{t_1}\int_{\max(s, t_{0})}^{t_1} \beta(s,u,x_0,\hat{y}_s) du dW_s^{\mathbb{Q}}\nonumber \\
@@
 \end{equation*}
-Now from (\ref{malliavin_derive_x}) we have that 
+Now from (\ref{approximation_D_s_x_t}) we have that 
 \begin{equation*}
-D_s L(t_1,t_1,t_2) = \frac{G(t_1,t_2)}{\delta_{t_1,t_2}P_{E}(t_1,t_2)} D_s x_{t_1} \approx \frac{G(t_1,t_2)}{\delta_{t_1,t_2}P_{E}(0,t_1,t_2)} \beta(s,t_1, x_0, \hat{y}_s)M(s,t_1)
+D_s L(t_1,t_1,t_2) = \frac{G(t_1,t_2)}{\delta_{t_1,t_2}P_{E}(t_1,t_2)} D_s x_{t_1} \approx \frac{G(t_1,t_2)}{\delta_{t_1,t_2}P_{E}(0,t_1,t_2)} \beta(s,t_1, x_0, \bar{y}_s)\bar{M}(s,t_1)
 \end{equation*}
-Therefore, if we define 
+Therefore, if we define and we use (\ref{approsimation_E_s_x_t}) we have that
 \begin{equation*}
@@
 \fboxsep1em
-\fbox{\parbox{435pt}
+\fbox{\parbox{475pt}
 {
 \begin{equation}\label{ca_approximations_fra_arrears}
-CA(t_0,t_1) \approx  \frac{G(t_1,t_2)}{\delta_{t_1,t_2}P_{E}(0,t_1,t_2)} \int_{0}^{t_1} \beta(s,t_1, x_0, \hat{y}_s) (\nu(s,t_2) - \nu(s,t_1)) ds.
+CA(t_0,t_1) \approx  \frac{G(t_1,t_2)}{\delta_{t_1,t_2}P_{E}(0,t_1,t_2)} \int_{0}^{t_1} \beta(s,t_1, x_0, \bar{y}_s) \exp\left(-\int_{s}^{t_1} \partial_x \beta(u,t_1,x_0,y_0) \nu(u,t_2) du \right) (\nu(s,t_2) - \nu(s,t_1)) ds.
 \end{equation}
@@
 \end{example}
-
-\newpage
 
@@
 \renewcommand{\thesection}{\Alph{section}.\arabic{section}}
-\section{Malliavin derivative calculations}
-
-\subsection{Approximation of $\mathbb{E}_s^{T_p}\left(D_s x_{T_a}\right)$}
+\section{Approximation of $\mathbb{E}_s^{T_p}\left(D_s x_{T_a}\right)$}
 \label{expected_forward_measure_malliavin_derivative_x_t}
@@
 \end{equation*}
-Therefore, we have that
+In order to get an approximation for $D_sX_{T_a}$ we must to avoid the recurrence in the Malliavin derivative of $X_{T_a}$.
+Follow, the ideas of Piterrbarg Volume II, we can approximate $y_t$ the next way
+\begin{equation*}
+y_t \approx \int_{0}^{s} \exp\left(-2\int_{u}^{s} k_{u^{\prime}} du^{\prime} \right) \eta(u,x_0,y_0) du
+\end{equation*}
+Therefore, if we define $\bar{y}_t= \int_{0}^{s} \exp\left(-2\int_{u}^{s} k_{u^{\prime}} du^{\prime} \right) \eta(u,x_0,y_0)$, we have that
+\begin{equation*}
+X_{T_a} \approx \bar{X}_{T_a}:=\int_{0}^{T_a} \exp\left(-\int_{s}^{T_a}k_u du\right) \bar{y}_u du + \int_{0}^{T_a}  \exp\left(-\int_{s}^{T_a}k_u du \right) \eta(u,\bar{x}_u,\bar{y}_u) dW_u^{\mathbb{Q}}
+\end{equation*} 
+and therefore
+\begin{equation}\label{approximation_D_s_x_t}
+D_sX_{T_a} \approx  \exp\left(-\int_{s}^{T_a}k_u du \right) \eta(u,\bar{x}_s,\bar{y}_s)\bar{M}(s,T_a)
+\end{equation}
+where
+\begin{equation*}
+\bar{M}(s,T_a) = \exp\left(-\frac{\int_{s}^{t_0} \left(\partial_x \beta(u,T_a,\bar{x}_s,\bar{y}_s)\right)^{2} du}{2} + \int_{s}^{t_0} \partial_x \beta(u,T_a,\bar{x}_s,\bar{y}_s) dW^{\mathbb{Q}}_u \right)
+\end{equation*}
+Now, we must remember that by Girsanov's theorem we have that 
+\begin{equation*}
+dW^{\mathbb{Q}^{T_p}} = dW^{\mathbb{Q}} + \nu(t,T_p) dt 
+\end{equation*}
+and therefore 
+\begin{align}\label{approsimation_E_s_x_t}
+\mathbb{E}_s^{T_p}\left(D_s x_{T_a}\right) &= \exp\left(-\int_{s}^{T_a}k_u du \right) \eta(u,\bar{x}_s,\bar{y}_s) \exp\left(-\int_{s}^{T_a} \partial_x \beta(u,T_a,\bar{x}_s,\bar{y}_s) \nu(u,T_p) du \right) \nonumber \\
+&\approx \exp\left(-\int_{s}^{T_a}k_u du \right) \eta(u,x_0,y_0) \exp\left(-\int_{s}^{T_a} \partial_x \beta(u,T_a,x_0,y_0) \nu(u,T_p) du \right)
+\end{align}
 

### 2022-10-30 Latex/paper.tex
# typo in ois convexity

@@
 \end{align*}
-We must do several obeservations. The first observation is that
+We must do several obeservations. The first observation is that, we define $F(t,t_0,t_1) = \mathbb{E}^{\mathbb{Q}^{t_1}}\left( R(t_0,t_1)\right)$, then we have that
 \begin{align*}
-F(t,t_0,t_1)=\mathbb{E}_{t}^{\mathbb{Q}}\left(\exp\left(-\int_{t}^{t_0} r_{ois,u} du \right) R(t_0,t_1) \right) &= \frac{\frac{P_{ois}(t,t_0)}{P_{ois}(t,t_1)} - 1}{t_1 - t_0}, \quad t \in [0,t_0] \\
-F(t,t_0,t_1)=\mathbb{E}_{t}^{\mathbb{Q}}\left(\exp\left(-\int_{t}^{t_0} r_{ois,u} du \right) R(t_0,t_1) \right) &= \frac{1}{t_1 - t_0} \left(\frac{\left( \exp\left(\int_{t}^{t_1}r_{ois,u} du\right)\right)}{P_{ois}(t_0,t)}-1\right), \quad  t \in  [t_0, t_1].
+F(t,t_0,t_1)&= \frac{1}{P_{ois}(t,t_1)}  \mathbb{E}_{t}^{\mathbb{Q}}\left(\exp\left(-\int_{t}^{t_1} r_{ois,u} du \right) R(t_0,t_1) \right) = \frac{\frac{P_{ois}(t,t_0)}{P_{ois}(t,t_1)} - 1}{t_1 - t_0}, \quad t \in [0,t_0] \\
+F(t,t_0,t_1)&= \frac{1}{P_{ois}(t,t_1)} \mathbb{E}_{t}^{\mathbb{Q}}\left(\exp\left(-\int_{t}^{t_1} r_{ois,u} du \right) R(t_0,t_1) \right) = \frac{1}{t_1 - t_0} \left(\frac{\left( \exp\left(\int_{t}^{t_1}r_{ois,u} du\right)\right)}{P_{ois}(t_0,t)}-1\right), \quad  t \in  [t_0, t_1].
 \end{align*}
@@
 where $f(\cdot)$ is known as mapping function.
-There is a extensive literature how to define this function (see Piterbarg Volume III), in later we will see some particular examples.
+There is a extensive literature how to define this function (see Piterbarg Volume III), in later we will see some particular examples for this mapping function.
 Under the last assumption and applying Clark-Ocone to $f(S_{a,b}(t))$ we get
@@
 \begin{align*}
-CA_{CMS}(T_a,T_b) = \\
-01(0,T_a,T_b) \mathbb{E}^{\mathbb{Q}^{01(a,b)}}\left(S_{a,b}(T_a) \int_{0}^{T_a} \mathbb{E}_s^{01(a,b)}\left( f^{\prime}(S^{ois}_{a,b}(T_a)) \partial_{x}S^{ois}_{a,b}(T_a) D_s x_{T_a} \right) dW^{01(a,b)}_{s} \right)
+&CA_{CMS}(T_a,T_b)  \\
+=&01(0,T_a,T_b) \mathbb{E}^{\mathbb{Q}^{01(a,b)}}\left(S_{a,b}(T_a) \int_{0}^{T_a} \mathbb{E}_s^{01(a,b)}\left( f^{\prime}(S^{ois}_{a,b}(T_a)) \partial_{x}S^{ois}_{a,b}(T_a) D_s x_{T_a} \right) dW^{01(a,b)}_{s} \right)
 \end{align*}
-Now if we use again the Clark-Ocone representation, but in this case for $S_{a,b}(T_a)$, we can do the next approximation
+Now if we use again the Clark-Ocone representation, but in this case for $S_{a,b}(T_a)$ we get that
 \begin{align*}
@@
 \end{align*}
-Where we have used that $S_{a,b}(t)$ and $S^{ois}_{a,b}(T_a)$ are $01(a,b)$-martingale. Also, if we use Itô formula we get that
+Where we have used that $S_{a,b}(t)$ and $S^{ois}_{a,b}(T_a)$ are $01(a,b)$-martingale. Now, if we use Itô formula to $S^{ois}_{a,b}(t)$ and $S_{a,b}(t)$ we have that
 \begin{align*}
@@
 \end{align*}
-with initial condition respectivaly $S^{ois}_{a,b}(0)$ and $S_{a,b}(0)$. Then we have that
+with initial condition $S^{ois}_{a,b}(0)$ and $S_{a,b}(0)$ respectivaly. Then 
 \begin{align*}
@@
 \end{align*}
-Therefore, if se use the last equality we can approximate $CA_{CMS}(T_a,T_b)$ the next way
+Therefore, from the last equality we can approximate $CA_{CMS}(T_a,T_b)$ the next way
 
@@
 \begin{align*}
-CA_{CMS}(T_a,T_b) \\ 
-\approx 01(0,T_a,T_b) \alpha \partial_{x}S_{a,b}(0) \partial_{x}S^{ois}_{a,b}(0) \frac{ \sigma^2(1-\exp(-2kT_a))}{2k}  \\   
-= - P_{ois}(0,T_p) \left(G(T_a,T_p)+\frac{\partial_x 01(0,T_a,T_b)}{01(0,T_a,T_b)}\right) \partial_{x}S_{a,b}(0)  \frac{ \sigma^2(1-\exp(-2kT_a))}{2k}
+&CA_{CMS}(T_a,T_b) \\ 
+\approx& 01(0,T_a,T_b) \alpha \partial_{x}S_{a,b}(0) \partial_{x}S^{ois}_{a,b}(0) \frac{ \sigma^2(1-\exp(-2kT_a))}{2k}  \\   
+=& - P_{ois}(0,T_p) \left(G(T_a,T_p)+\frac{\partial_x 01(0,T_a,T_b)}{01(0,T_a,T_b)}\right) \partial_{x}S_{a,b}(0)  \frac{ \sigma^2(1-\exp(-2kT_a))}{2k}
 \end{align*}

### 2022-10-30 ConvexityAdjustment-Lib/ConvexityAdjusmentUnitTests/CmsConvexity.cs

@@ -16,7 +16,7 @@ namespace ConvexityAdjustmentUnitTests
             
             // Hull-White parameters
             double k = 0.0007;
-            double sigma = 0.015;
+            double sigma = 0.007;
 
             // Curves
             double discountFlatRate = 0.015;
@@ -35,12 +35,12 @@ namespace ConvexityAdjustmentUnitTests
             var tenorSwap = new ql.Period(5, ql.TimeUnit.Years);
 
             // Convexity test
-            var periodToCompute = new ql.Period(1, ql.TimeUnit.Years);
+            var periodToCompute = new ql.Period(30, ql.TimeUnit.Years);
             int numberOftimes = 1;
 
             List<ql.Date> datesToCompute = new List<ql.Date>{calendar.advance(startDate, periodToCompute)};
             List<double> deltaTimes = new List<double>{dc.yearFraction(startDate, datesToCompute[0])};
-            List<double> f0ts = new List<double>{discountCurve.link.forwardRate(deltaTimes[0], deltaTimes[0], ql.Compounding.Simple, ql.Frequency.NoFrequency).rate()};
+            List<double> f0ts = new List<double>{discountCurve.link.forwardRate(deltaTimes[0], deltaTimes[0], ql.Compounding.Continuous, ql.Frequency.NoFrequency).rate()};
             List<double> hjmAdjustment = new List<double>{ConvexityAdjustment_Lib.HullWhite.hjmAdjustment(deltaTimes[0], k, sigma)};
             var drift = new List<double>{ConvexityAdjustment_Lib.HullWhite.forwardMeasureAdjustment(deltaTimes[0], k, sigma)};
             
@@ -48,13 +48,13 @@ namespace ConvexityAdjustmentUnitTests
             {
                 datesToCompute.Add(calendar.advance(datesToCompute[i-1], periodToCompute));
                 deltaTimes.Add(dc.yearFraction(startDate, datesToCompute[i]));
-                f0ts.Add(discountCurve.link.forwardRate(deltaTimes[i], deltaTimes[i], ql.Compounding.Simple, ql.Frequency.NoFrequency).rate());
+                f0ts.Add(discountCurve.link.forwardRate(deltaTimes[i], deltaTimes[i], ql.Compounding.Continuous, ql.Frequency.NoFrequency).rate());
[…]

### 2022-10-31 Latex/paper.tex
# fix some bugs

@@
 \begin{equation}\label{hullwhite_cms_convexity}
-01(0,T_a,T_b)  f^{\prime}(S^{ois}_{a,b}(0)) \partial_{x}S_{a,b}(T_a) \partial_{x}S^{ois}_{a,b}(T_a) \frac{ \sigma^2(1-\exp(-2kT_a))}{2k} 
+01(0,T_a,T_b)  f^{\prime}(S^{ois}_{a,b}(T_a)) \partial_{x}S_{a,b}(0) \partial_{x}S^{ois}_{a,b}(0) \frac{ \sigma^2(1-\exp(-2kT_a))}{2k} 
 \end{equation}
@@
 &CA_{CMS}(T_a,T_b) \\ 
-\approx& 01(0,T_a,T_b) \alpha \partial_{x}S_{a,b}(0) \partial_{x}S^{ois}_{a,b}(0) \frac{ \sigma^2(1-\exp(-2kT_a))}{2k}  \\   
+\approx& \alpha 01(0,T_a,T_b) \partial_{x}S_{a,b}(0) \partial_{x}S^{ois}_{a,b}(0) \frac{ \sigma^2(1-\exp(-2kT_a))}{2k}  \\   
 =& - P_{ois}(0,T_p) \left(G(T_a,T_p)+\frac{\partial_x 01(0,T_a,T_b)}{01(0,T_a,T_b)}\right) \partial_{x}S_{a,b}(0)  \frac{ \sigma^2(1-\exp(-2kT_a))}{2k}
@@
 In order to get an approximation for $D_sX_{T_a}$ we must to avoid the recurrence in the Malliavin derivative of $X_{T_a}$.
-Follow, the ideas of Piterrbarg Volume II, we can approximate $y_t$ the next way
+Follow, the ideas of Piterbarg Volume II, we can approximate $y_t$ the next way
 \begin{equation*}

### 2022-10-31 ConvexityAdjustment-Lib/ConvexityAdjusmentUnitTests/CmsConvexity.cs

@@ -54,7 +54,7 @@ namespace ConvexityAdjustmentUnitTests
             }
             
             // MC
-            int numberOfSimulations = 10000;
+            int numberOfSimulations = 500000;
             ulong seed = 123545;
             
             // outputs
@@ -65,7 +65,8 @@ namespace ConvexityAdjustmentUnitTests
             var momentOrderTwo = new Dictionary<int, double>();
             var rateCmsForward = new List<double>();
             var annuity = new List<Tuple<double,double>>();
-            var partialOisSwap = new List<double>();
+            var partialOisSwapTa = new List<double>();
+            var partialOisSwapT0 = new List<double>();
             var partialVanillaSwap = new List<double>();
             var swapRates = new List<double>();
             var swapOisRates = new List<double>();
@@ -89,18 +90,23 @@ namespace ConvexityAdjustmentUnitTests
                     .withFloatingLegRule(ql.DateGeneration.Rule.Forward)
                     .value();
 
-                annuity.Add( model.GetAnnuity(startDate, datesToCompute[j], f0ts[j], staticSwap.fixedSchedule(),
+                annuity.Add( model.GetAnnuity(startDate, startDate, f0ts[j], staticSwap.fixedSchedule(),
                     staticSwap.fixedDayCount()));
                 
-                var swapOisDerivative = model.GetPartialDerivativeSwapRate(startDate, datesToCompute[j], f0ts[j],
+                var swapOisDerivativeT0 = model.GetPartialDerivativeSwapRate(startDate, startDate, f0ts[j],
                     staticSwap.floatingSchedule(), staticSwap.fixedSchedule(), staticSwap.floatingDayCount(),
                     staticSwap.fixedDayCount());
                 
-                var swapVanillaDerivative = model.GetPartialDerivativeSwapRate(startDate, datesToCompute[j], f0ts[j],
+                var swapOisDerivativeTa = model.GetPartialDerivativeSwapRate(startDate, datesToCompute[j], f0ts[j],
+                    staticSwap.floatingSchedule(), staticSwap.fixedSchedule(), staticSwap.floatingDayCount(),
+                    staticSwap.fixedDayCount());
+                
+                var swapVanillaDerivative = model.GetPartialDerivativeSwapRate(startDate, startDate, f0ts[j],
[…]

### 2022-10-31 ConvexityAdjustment-Lib/ConvexityAdjustment-Lib/HullWhite.cs

@@ -86,18 +86,19 @@ namespace ConvexityAdjustment_Lib
         }
 
         public static double convexityCms(ql.Handle<ql.YieldTermStructure> discountCurve,  ql.Date valueDate, ql.Date ta, ql.Date tb, ql.Date tp, double annuity,
-            double partialAnnuity, double partialVanillaSwap, double partialOisSwap, double swapRate, double swapOisRate, ql.DayCounter dc, double k, double sigma)
+            double partialAnnuity, double partialVanillaSwap, double partialOisSwap, double partialOisSwapT0 , ql.DayCounter dc, double k, double sigma)
         {
             var dta = dc.yearFraction(valueDate, ta);
             var dtp = dc.yearFraction(valueDate, tp);
             
             var dFtp = discountCurve.link.discount(tp);
             var dFta = discountCurve.link.discount(ta);
-            var m = - dFtp   * (beta(dta, dtp, k) + partialAnnuity / annuity);
+            var m = - dFtp  * (beta(dta, dtp, k) + partialAnnuity / annuity);
 
             var alpha = sigma * sigma * beta(0.0, dta, 2.0 * k);
+            var ratio = partialOisSwap / partialOisSwapT0;
             return m * alpha * partialVanillaSwap;
-            
+
         }
 
         #endregion

### 2022-10-31 ConvexityAdjustment-Lib/ConvexityAdjusmentUnitTests/CmsConvexity.cs
# some modifications in cms test

@@ -31,11 +31,11 @@ namespace ConvexityAdjustmentUnitTests
             ql.HullWhite model = new ql.HullWhite(discountCurve, k, sigma);
             
             // Swap product
-            var payPeriod = new ql.Period(ql.Frequency.Annual);
+            var payPeriod = new ql.Period(ql.Frequency.Semiannual);
             var tenorSwap = new ql.Period(5, ql.TimeUnit.Years);
 
             // Convexity test
-            var periodToCompute = new ql.Period(30, ql.TimeUnit.Years);
+            var periodToCompute = new ql.Period(5, ql.TimeUnit.Years);
             int numberOftimes = 1;
 
             List<ql.Date> datesToCompute = new List<ql.Date>{calendar.advance(startDate, periodToCompute)};
@@ -113,8 +113,7 @@ namespace ConvexityAdjustmentUnitTests
                 // ois swap rate
                 var tb =  calendar.advance(datesToCompute[j], tenorSwap,
                     ql.BusinessDayConvention.ModifiedFollowing);
-                var dfta = discountCurve.link.discount(datesToCompute[j]);
-                var oisSwapRate = (discountCurve.link.discount(datesToCompute[j]) - discountCurve.link.discount(tb)) / (dfta * annuity[j].Item1); 
+                var oisSwapRate = (discountCurve.link.discount(datesToCompute[j]) - discountCurve.link.discount(tb)) /  annuity[j].Item1; 
                 swapOisRates.Add(oisSwapRate);
                 
                 var payDate = calendar.advance(datesToCompute[j], payPeriod,
@@ -192,7 +191,7 @@ namespace ConvexityAdjustmentUnitTests
                 }
 
                 var error = dfMc - discountCurve.link.discount(tP);
-                var errorRi = (rtaMc -  swapOisRates[j]) / discountCurve.link.discount(datesToCompute[j]);
+                var errorRi = rtaMc -  swapOisRates[j] / discountCurve.link.discount(datesToCompute[j]);
                 
                 // Analytic convexity adjustment
                 double ca = ConvexityAdjustment_Lib.HullWhite.convexityCms(discountCurve, startDate, datesToCompute[j],

### 2022-11-01 Latex/paper.tex
Adding Description Section 4
Adding Description Section 4

@@
 \section{Convexity Adjustment}\label{sec:CA}
-$\cdots$  tengo que pensar que poner aqui como intro
+In this section, we derive the convexity adjustment for different products.
+The advantage of using the Malliavin calculus is that it allows us to derive a convexity adjustment directly for a general model.
+Since this convexity adjustment works for a general framework defined in the Cheyette model, it can be applied to all included models, such as the Hull-White model.
 

### 2022-11-01 Latex/paper.tex
# Some modifications in .tex to approximate the initial point x_0 and y_t_a

@@
 du \right)  + S_{a,b}(0) S^{ois}_{a,b}(0) \\
-&\approx  \partial_{x}S_{a,b}(0) \partial_{x}S^{ois}_{a,b}(0)\int_0^{T_a} \eta^{2}(u,x_0,\hat{y}_u) + S_{a,b}(0) S^{ois}_{a,b}(0).
-du
+&\approx  \partial_{x}S_{a,b}(0,\bar{x}_0, \bar{y}({T_a}) \partial_{x}S^{ois}_{a,b}(0,\bar{x}_0, \bar{y}({T_a}))\int_0^{T_a} \eta^{2}(u,\bar{x}_0, \bar{y}({T_a})) du \\
+&+ S_{a,b}(0) S^{ois}_{a,b}(0).
 \end{align*}
-Therefore, from the last equality we can approximate $CA_{CMS}(T_a,T_b)$ the next way
+
+Then, we can approximate $CA_{CMS}(T_a,T_b)$ the next way
 
 \fboxsep1em
-\fbox{\parbox{435pt}
+\fbox{\parbox{430pt}
 {
-\begin{equation}\label{cms_adjustment}
-CA_{CMS}(T_a,T_b) \approx 01(0,T_a,T_b)  f^{\prime}(S^{ois}_{a,b}(0)) \partial_{x}S_{a,b}(0) \partial_{x}S^{ois}_{a,b}(0)\int_0^{T_a} \eta^{2}(u,x_0,\hat{y}_u) du
-\end{equation}
+\begin{align}\label{cms_adjustment}
+&CA_{CMS}(T_a,T_b)  \\
+&\approx  01(0,T_a,T_b)  f^{\prime}(S^{ois}_{a,b}(0)) \nonumber \\
+&\cdot \partial_{x}S_{a,b}(0,\bar{x}_0, \bar{y}({T_a}) \partial_{x}S^{ois}_{a,b}(0,\bar{x}_0, \bar{y}({T_a}))\int_0^{T_a} \eta^{2}(u,\bar{x}_0, \bar{y}({T_a})) du \nonumber
+\end{align}
 }}
@@
 \begin{equation}\label{hullwhite_cms_convexity}
-01(0,T_a,T_b)  f^{\prime}(S^{ois}_{a,b}(T_a)) \partial_{x}S_{a,b}(0) \partial_{x}S^{ois}_{a,b}(0) \frac{ \sigma^2(1-\exp(-2kT_a))}{2k} 
+01(0,T_a,T_b)  f^{\prime}(S^{ois}_{a,b}(T_a)) \partial_{x}S_{a,b}(0,\bar{x}_0, \bar{y}({T_a}) \partial_{x}S^{ois}_{a,b}(0,\bar{x}_0, \bar{y}({T_a}) \frac{ \sigma^2(1-\exp(-2kT_a))}{2k} 
 \end{equation}
@@
 &CA_{CMS}(T_a,T_b) \\ 
-\approx& \alpha 01(0,T_a,T_b) \partial_{x}S_{a,b}(0) \partial_{x}S^{ois}_{a,b}(0) \frac{ \sigma^2(1-\exp(-2kT_a))}{2k}  \\   
-=& - P_{ois}(0,T_p) \left(G(T_a,T_p)+\frac{\partial_x 01(0,T_a,T_b)}{01(0,T_a,T_b)}\right) \partial_{x}S_{a,b}(0)  \frac{ \sigma^2(1-\exp(-2kT_a))}{2k}
+\approx& \alpha 01(0,T_a,T_b) \partial_{x}S_{a,b}(0,\bar{x}_0, \bar{y}({T_a}) \partial_{x}S^{ois}_{a,b}(0,\bar{x}_0, \bar{y}({T_a}) \frac{ \sigma^2(1-\exp(-2kT_a))}{2k}  \\   
+=& - P_{ois}(0,T_p) \left(G(T_a,T_p)+\frac{\partial_x 01(0,T_a,T_b)}{01(0,T_a,T_b)}\right) \partial_{x}S_{a,b}(0,\bar{x}_0, \bar{y}({T_a})) \frac{S^{ois}_{a,b}(0,\bar{x}_0, \bar{y}({T_a}))}{S^{ois}_{a,b}(0)}  \frac{ \sigma^2(1-\exp(-2kT_a))}{2k}
 \end{align*}
@@
 \end{equation*}
-Therefore, if we define $\bar{y}_t= \int_{0}^{s} \exp\left(-2\int_{u}^{s} k_{u^{\prime}} du^{\prime} \right) \eta(u,x_0,y_0)$, we have that
+Therefore, if we define $\bar{y}(t)= \int_{0}^{s} \exp\left(-2\int_{u}^{s} k_{u^{\prime}} du^{\prime} \right) \eta(u,x_0,y_0)$, we have that
 \begin{equation*}
-X_{T_a} \approx \bar{X}_{T_a}:=\int_{0}^{T_a} \exp\left(-\int_{s}^{T_a}k_u du\right) \bar{y}_u du + \int_{0}^{T_a}  \exp\left(-\int_{s}^{T_a}k_u du \right) \eta(u,\bar{x}_u,\bar{y}_u) dW_u^{\mathbb{Q}}
+X_{T_a} \approx \bar{X}(T_a):=\int_{0}^{T_a} \exp\left(-\int_{s}^{T_a}k_u du\right) \bar{y}(u) du + \int_{0}^{T_a}  \exp\left(-\int_{s}^{T_a}k_u du \right) \eta(u,\bar{x}(u),\bar{y}(u)) dW_u^{\mathbb{Q}}
 \end{equation*}
-and therefore
+With initial condition  $\bar{x}_{0}$ is such that $S_{a,b}(0,\bar{x}_0, \bar{y}({T_a})) = S_{a,b}(0)$ (see Piterbarg Volume II).
+Then we can do the next approximation for the Malliavin derivative of $X_{T_a}$
 \begin{equation}\label{approximation_D_s_x_t}
-D_sX_{T_a} \approx  \exp\left(-\int_{s}^{T_a}k_u du \right) \eta(u,\bar{x}_s,\bar{y}_s)\bar{M}(s,T_a)
+D_sX_{T_a} \approx  \exp\left(-\int_{s}^{T_a}k_u du \right) \eta(u,\bar{x}_0,\bar{y}_{T_a})\bar{M}(s,T_a)
 \end{equation}
@@
 \begin{equation*}
-\bar{M}(s,T_a) = \exp\left(-\frac{\int_{s}^{t_0} \left(\partial_x \beta(u,T_a,\bar{x}_s,\bar{y}_s)\right)^{2} du}{2} + \int_{s}^{t_0} \partial_x \beta(u,T_a,\bar{x}_s,\bar{y}_s) dW^{\mathbb{Q}}_u \right)
+\bar{M}(s,T_a) = \exp\left(-\frac{\int_{s}^{t_0} \left(\partial_x \beta(u,T_a,\bar{x}_0,\bar{y}_{T_a})\right)^{2} du}{2} + \int_{s}^{t_0} \partial_x \beta(u,T_a,\bar{x}_0,\bar{y}_{T_a}) dW^{\mathbb{Q}}_u \right)
 \end{equation*}
@@
 and therefore 
-\begin{align}\label{approsimation_E_s_x_t}
-\mathbb{E}_s^{T_p}\left(D_s x_{T_a}\right) &= \exp\left(-\int_{s}^{T_a}k_u du \right) \eta(u,\bar{x}_s,\bar{y}_s) \exp\left(-\int_{s}^{T_a} \partial_x \beta(u,T_a,\bar{x}_s,\bar{y}_s) \nu(u,T_p) du \right) \nonumber \\
-&\approx \exp\left(-\int_{s}^{T_a}k_u du \right) \eta(u,x_0,y_0) \exp\left(-\int_{s}^{T_a} \partial_x \beta(u,T_a,x_0,y_0) \nu(u,T_p) du \right)
-\end{align}
+\begin{equation}\label{approsimation_E_s_x_t}
+\mathbb{E}_s^{T_p}\left(D_s x_{T_a}\right) \approx \exp\left(-\int_{s}^{T_a}k_u du \right) \eta(u,\bar{x}_0,\bar{y}_{T_a}) \exp\left(-\int_{s}^{T_a} \partial_x \beta(u,T_a,\bar{x}_0,\bar{y}_{T_a}) \nu(u,T_p) du \right)
+\end{equation}
 

### 2022-11-01 Latex/paper.tex
Section 4: Wording

@@
 In this section, we derive the convexity adjustment for different products.
-The advantage of using the Malliavin calculus is that it allows us to derive a convexity adjustment directly for a general model.
-Since this convexity adjustment works for a general framework defined in the Cheyette model, it can be applied to all included models, such as the Hull-White model.
+The advantage of using the Malliavin calculus is that it allows us to derive a general representation formula for the convexity adjustment.
+Since the convexity adjustment is derived for the Cheyette model, it can be applied to all included models, such as the Hull-White model.
 
 \subsection{FRAs Vs futures}
-The cashflows in FRAs and futures are computing under different measures and consequently we have to adjust the futures price quote to transform them to FRAs price quote.
-As usual, we will define the forward rate  in time $t_0$ between $t_1$ and $t_2$ under the forward curve $E$ as
+The cash flows in FRAs and futures are computed under different measures.
+Consequently, we need to adjust the futures price quote to transform them into FRAs price quotes.
+As usual, we will define the forward rate at time $t_0$ between $t_1$ and $t_2$ under the forward curve $E$ as:
 \begin{equation}\label{forward_rate}
@@
 \end{equation} 
-where $P_{E}(t,T)$ is the discount factor for the curve $E$ from t to T and $\delta_{t_1,t_2}$ is the year fraction between $t_1$ and $t_2$.
-We must observe that $L_{E}(t, t_1, t_2)$ is a martingale under the forward measure $\mathbb{Q}^{t_2}$.
-Let us define the future rate
+where $P_{E}(t,T)$ is the discount factor for the curve $E$ from $t$ to $T$, and $\delta_{t_1,t_2}$ is the year fraction between $t_1$ and $t_2$.
+Observe that $L_{E}(t, t_1, t_2)$ is a martingale under the forward measure $\mathbb{Q}^{t_2}$.
+Let us define the conditional future rate as:
 \begin{equation}\label{future}
@@
 \end{equation}
-where the measure $\mathbb{Q}$ is the measure associated to the numeraire $B_t=\exp\left(\int_{0}^{t} r_{ois, s} ds \right)$ with $ r_{ois, t}$ the risk free short rate.
-From (\ref{forward_rate}) and (\ref{future}), we will define the convexity adjustment as
+where $\mathbb{Q}$ is the measure associated to the numeraire $B_t=\exp\left(\int_{0}^{t} r_{ois, s} ds \right)$ with $ r_{ois, t}$ the risk free short rate. Using
+\eqref{forward_rate} and \eqref{future}, we can express the convexity adjustment definition as:%From \eqref{forward_rate} and \eqref{future}, we will define the convexity adjustment as
 \begin{equation*}
-CA(t, t_0, t_1, t_2) = \hat{L}_{E}(t,t_0, t_1, t_2) - \mathbb{E}_t^{\mathbb{Q}^{t_2}}\left(L_{E}(t_0, t_1, t_2) \right)
+CA(t, t_0, t_1, t_2) = \hat{L}_{E}(t,t_0, t_1, t_2) - \mathbb{E}_t^{\mathbb{Q}^{t_2}}\left(L_{E}(t_0, t_1, t_2) \right).
 \end{equation*}
-With view to get a general representation formula of the convexity adjustment for the futures, we will use (\ref{clark-okone}) to 
-$L_{E}(t_0,t_1,t_2)$ i.e
-
+We use the Clark-Ocone formula with a view to obtaining a general representation formula of the convexity adjustment for futures. Applying \eqref{clark-okone} to 
+$L_{E}(t_0,t_1,t_2)$, we obtain
 \begin{equation}
@@
 \end{equation} 
-Therefore, if we take $\mathbb{E}^{\mathbb{Q}^{t2}}(\cdot)$ in the last equation, then we get
+Therefore, if we apply $\mathbb{E}^{\mathbb{Q}^{t2}}(\cdot)$ in the last equation, then we get
 \begin{equation*}

### 2022-11-23 ConvexityAdjustment-Lib/ConvexityAdjustment-Lib/HullWhite.cs
# New version cms convexity

@@ -96,7 +96,6 @@ namespace ConvexityAdjustment_Lib
             var m = - dFtp  * (beta(dta, dtp, k) + partialAnnuity / annuity);
 
             var alpha = sigma * sigma * beta(0.0, dta, 2.0 * k);
-            var ratio = partialOisSwap / partialOisSwapT0;
             return m * alpha * partialVanillaSwap;
 
         }
@@ -170,6 +169,7 @@ namespace ConvexityAdjustment_Lib
         public static double forwardMeasureAdjustment(double dtP, double k, double sigma)
         {
             return (sigma * sigma / k) * (dtP * Math.Exp(-k * dtP) - beta(dtP, 2.0 * dtP, k));
+            // return (sigma * sigma / k) * ( - dtP * Math.Exp(-k * dtP) + beta(0.0, dtP, k));
         }
 
         #endregion

### 2022-11-23 ConvexityAdjustment-Lib/ConvexityAdjustmentUnitTests/CmsConvexity.cs

@@ -1,0 +1,212 @@
+using NUnit.Framework;
+using ql = QLNet;
+
+namespace ConvexityAdjusmentUnitTests
+{
+    public class CmsConvexity
+    {
+        [Test]
+        public void HullWhiteCms()
+        {
+            // settings
+            var calendar = new ql.TARGET();
+            ql.DayCounter dc = new ql.Actual360();
+            ql.Date startDate =  calendar.adjust(ql.Settings.evaluationDate());
+            
+            // Hull-White parameters
+            double k = 0.0007;
+            double sigma = 0.007;
+
+            // Curves
+            double discountFlatRate = 0.015;
+            double basisSpread = 0.0;
+            ql.Quote quoteDiscountRate = new ql.SimpleQuote(discountFlatRate);
+            ql.Quote quoteSpread = new ql.SimpleQuote(basisSpread);
+            
+            ql.Handle<ql.YieldTermStructure> discountCurve =  new ql.Handle<ql.YieldTermStructure>(new ql.FlatForward(startDate, quoteDiscountRate, dc));
+            
+            // Model and process
+            ql.OrnsteinUhlenbeckProcess process = new ql.OrnsteinUhlenbeckProcess(k, sigma, 0.0, 0.0);
+            ql.HullWhite model = new ql.HullWhite(discountCurve, k, sigma);
+            
+            // Swap product
+            var payPeriod = new ql.Period(ql.Frequency.Annual);
+            var tenorSwap = new ql.Period(5, ql.TimeUnit.Years);
+
+            // Convexity test
+            var periodToCompute = new ql.Period(5, ql.TimeUnit.Years);
+            int numberOftimes = 1;
+
+            List<ql.Date> datesToCompute = new List<ql.Date>{calendar.advance(startDate, periodToCompute)};
+            List<double> deltaTimes = new List<double>{dc.yearFraction(startDate, datesToCompute[0])};
+            List<double> f0ts = new List<double>{discountCurve.link.forwardRate(deltaTimes[0], deltaTimes[0], ql.Compounding.Simple, ql.Frequency.NoFrequency).rate()};
+            List<double> hjmAdjustment = new List<double>{ConvexityAdjustment_Lib.HullWhite.hjmAdjustment(deltaTimes[0], k, sigma)};
+            var drift = new List<double>{ConvexityAdjustment_Lib.HullWhite.forwardMeasureAdjustment(deltaTimes[0], k, sigma)};
+            
+            for (int i = 1; i < numberOftimes; i++)
+            {
[…]

### 2022-11-23 ConvexityAdjustment-Lib/ConvexityAdjustmentUnitTests/CmsConvexityNewApproach.cs

@@ -1,10 +1,9 @@
-using System.Security.Cryptography.X509Certificates;
-using NUnit.Framework;
+﻿using NUnit.Framework;
 using ql = QLNet;
 
-namespace ConvexityAdjustmentUnitTests
+namespace ConvexityAdjusmentUnitTests
 {
-    public class CmsConvexity
+    public class CmsConvexityNewApproach
     {
         [Test]
         public void HullWhiteCms()
@@ -12,8 +11,8 @@ namespace ConvexityAdjustmentUnitTests
             // settings
             var calendar = new ql.TARGET();
             ql.DayCounter dc = new ql.Actual360();
-            ql.Date startDate =  calendar.adjust(ql.Settings.evaluationDate());
-            
+            ql.Date startDate = calendar.adjust(ql.Settings.evaluationDate());
+
             // Hull-White parameters
             double k = 0.0007;
             double sigma = 0.007;
@@ -23,40 +22,48 @@ namespace ConvexityAdjustmentUnitTests
             double basisSpread = 0.0;
             ql.Quote quoteDiscountRate = new ql.SimpleQuote(discountFlatRate);
             ql.Quote quoteSpread = new ql.SimpleQuote(basisSpread);
-            
-            ql.Handle<ql.YieldTermStructure> discountCurve =  new ql.Handle<ql.YieldTermStructure>(new ql.FlatForward(startDate, quoteDiscountRate, dc));
-            
+
+            ql.Handle<ql.YieldTermStructure> discountCurve =
+                new ql.Handle<ql.YieldTermStructure>(new ql.FlatForward(startDate, quoteDiscountRate, dc));
+
             // Model and process
             ql.OrnsteinUhlenbeckProcess process = new ql.OrnsteinUhlenbeckProcess(k, sigma, 0.0, 0.0);
             ql.HullWhite model = new ql.HullWhite(discountCurve, k, sigma);
-            
+
             // Swap product
-            var payPeriod = new ql.Period(ql.Frequency.Semiannual);
+            var payPeriod = new ql.Period(ql.Frequency.Annual);
             var tenorSwap = new ql.Period(5, ql.TimeUnit.Years);
 
             // Convexity test
-            var periodToCompute = new ql.Period(1, ql.TimeUnit.Years);
+            var periodToCompute = new ql.Period(5, ql.TimeUnit.Years);
             int numberOftimes = 1;
 
-            List<ql.Date> datesToCompute = new List<ql.Date>{calendar.advance(startDate, periodToCompute)};
[…]

### 2022-11-23 ConvexityAdjustment-Lib/ConvexityAdjustmentUnitTests/FraInArrears.cs

@@ -1,7 +1,7 @@
 ﻿using NUnit.Framework;
 using ql = QLNet;
 
-namespace ConvexityAdjustmentUnitTests
+namespace ConvexityAdjusmentUnitTests
 {
     public class ConvexityFraInArrears
     {

### 2022-11-23 ConvexityAdjustment-Lib/ConvexityAdjustmentUnitTests/FraVsFuturesTests.cs

@@ -1,7 +1,7 @@
 using NUnit.Framework;
 using ql = QLNet;
 
-namespace ConvexityAdjustmentUnitTests
+namespace ConvexityAdjusmentUnitTests
 {
     public class ConvexityFutureFras
     {

### 2022-11-23 ConvexityAdjustment-Lib/ConvexityAdjustmentUnitTests/SofrCovexity.cs

@@ -2,7 +2,7 @@
 using ql = QLNet;
 using NUnit.Framework;
 
-namespace ConvexityAdjustmentUnitTests
+namespace ConvexityAdjusmentUnitTests
 {
     public class ConvexityAdjustmentSofr
     {

### 2022-11-24 Latex/paper.tex
# new approach cms convexity

@@
 The advantage of using the Malliavin calculus is that it allows us to derive a general representation formula for the convexity adjustment.
+In order to introduce a general idea of the method.
+Let define a $Z_t = f(x_t)$.
+Now, we suppose that $Z_t$ is martingale under the measure $\mathbb{Q}_1$ and that we want to compute $\mathbb{E}^{\mathbb{Q}_2}\left(Z_T \right)$, where $\mathbb{Q}_2$ is a measure such that $\frac{d\mathbb{Q}_2}{d\mathbb{Q}_1} = \lambda_t$.
+
 Since the convexity adjustment is derived for the Cheyette model, it can be applied to all included models, such as the Hull-White model.
@@
 \begin{equation*}
-dW^{\mathbb{Q}^{t_2}} = dW^{\mathbb{Q}} + \nu(t,T_2) dt. 
+dW^{\mathbb{Q}^{t_2}} = dW^{\mathbb{Q}} + \nu(t,t_2) dt. 
 \end{equation*}
@@
 
+\newpage
+
 \subsection{CMSs}
@@
 
-We suppose, that we have a flow in $T_a < T_p < T_b$ with value $S_{a,b}(T_a)$. Then, the present value of this flow
+We suppose, that we have a flow in $T_a < T_p < T_b$ with value $S_{a,b}(T_a)$.
+Then, the present value of this flow under the differents measure $\mathbb{Q}^{T_a}$,$\mathbb{Q}^{01(a,b)}$ and $\mathbb{Q}^{T_p}$ respectivaly is
 \begin{align}\label{cms_expedted_value}
 P_{ois}(0,T_a)\mathbb{E}^{\mathbb{Q}^{T_{a}}}\left(S_{a,b}(T_a) P_{ois}(T_a,T_p) \right) &= 01(0,T_a,T_b) \mathbb{E}^{\mathbb{Q}^{01(a,b)}}\left(S_{a,b}(T_a) \frac{P_{ois}(T_a,T_p)}{01(T_a,T_a,T_b) }\right) \nonumber \\
-&= 01(0,T_a,T_b) \mathbb{E}^{\mathbb{Q}^{01(a,b)}}\left(S_{a,b}(T_a) M(T_a,T_p)\right)
+&= 01(0,T_a,T_b) \mathbb{E}^{\mathbb{Q}^{01(a,b)}}\left(S_{a,b}(T_a) M(T_a,T_p)\right) \\
+&=P_{ois}(0,T_p)\mathbb{E}^{\mathbb{Q}^{T_p}}\left(S_{a,b}(T_a)\right)
 \end{align}
-where $M(t, T_p)= \frac{P_{ois}(t,T_p) }{01(t,T_a,T_b)} $. In order to reduce the complexity to explain the movement od the forward curve, it is a common pratice to asumme that
+where $M(t, T_p)= \frac{P_{ois}(t,T_p) }{01(t,T_a,T_b)} $.
+From the definition of $S_{a,b}(t)$ and $S^{ois}_{a,b}(t)$, we have that both are martingale under the measure $\mathbb{Q}^{01(a,b)}$.
+Therefore, we will define the convexity adjustment for CMS the next  way
 \begin{equation*}
-M(t) = f(S^{ois}_{a,b}(t))
+CA_{cms}(T_0,T_p) = S_{a,b}(0) - \mathbb{E}^{\mathbb{Q}^{T_p}}\left(S_{a,b}(T_a)\right). 
 \end{equation*}
-where $f(\cdot)$ is known as mapping function.
-There is a extensive literature how to define this function (see Piterbarg Volume III), in later we will see some particular examples for this mapping function.
-Under the last assumption and applying Clark-Ocone to $f(S_{a,b}(t))$ we get
+We will follow the same strategy that in the last examples. From Clark-Ocone formula we have that
+\begin{equation*}
+S_{a,b}(T_a) = \mathbb{E}^{\mathbb{Q}^{T_p}}\left(S_{a,b}(T_a)\right) + \int_{0}^{T_a} \mathbb{E}_s^{\mathbb{Q}^{T_p}}\left(D_s S_{a,b}(T_a)\right) dW^{T_p}_s 
+\end{equation*} 
+Therefore, if we take $\mathbb{E}^{01(a,b)}$ and we use the Girsanov theorem  in the last expression, we get 
+\begin{equation*}
+S_{a,b}(0) = \mathbb{E}^{\mathbb{Q}^{T_p}}\left(S_{a,b}(T_a)\right) + \frac{01(0,T_a,T_b)}{P_{ois}(0,T_p)} \mathbb{E}^{T_p}\left(M(T_a,T_p) \int_{0}^{T_a} \mathbb{E}_s^{\mathbb{Q}^{T_p}}\left(D_s S_{a,b}(T_a)\right) dW^{T_p}_s \right)
+\end{equation*}
+Now, if we use that the Skorohod integral is the adjoint operator of the Malliavin derivative, we have that
 \begin{align*}
-f(S^{ois}_{a,b}(T_a)) &= \mathbb{E}^{\mathbb{Q}^{01(a,b)}}\left(f(S^{ois}_{a,b}(T_a)\right) + \int_{0}^{T_a} \mathbb{E}_s^{01(a,b)}\left( D_s (f(S^{ois}_{a,b}(T_a)) \right) dW^{01(a,b)}_{s} \\
-&= \frac{P_{ois}(0,T_p) }{01(0,T_a,T_b)} + \int_{0}^{T_a} \mathbb{E}_s^{01(a,b)}\left(f^{\prime}(S^{ois}_{a,b}(T_a) \partial_{x}S^{ois}_{a,b}(T_a) D_s x_{T_a} \right) dW^{01(a,b)}_{s}. 
+S_{a,b}(0) &= \mathbb{E}^{\mathbb{Q}^{T_p}}\left(S_{a,b}(T_a)\right) + \frac{01(0,T_a,T_b)}{P_{ois}(0,T_p)} \mathbb{E}^{T_p}\left(\int_{0}^{T_a} D_s M(T_a,T_p) \mathbb{E}_s^{\mathbb{Q}^{T_p}}\left(D_s S_{a,b}(T_a)\right) ds  \right) \\
+&=\mathbb{E}^{\mathbb{Q}^{T_p}}\left(S_{a,b}(T_a)\right) + \frac{01(0,T_a,T_b)}{P_{ois}(0,T_p)} \mathbb{E}^{T_p}\left(\int_{0}^{T_a} \mathbb{E}_s^{\mathbb{Q}^{T_p}}\left(D_s M(T_a,T_p)\right) \mathbb{E}_s^{\mathbb{Q}^{T_p}}\left(D_s S_{a,b}(T_a)\right) ds  \right).
 \end{align*}
-Therefore, we can define the convexity adjustment for a CMS the next way
+Then we have the next expression for the convexity adjustment
+\begin{equation*}
+CA_{cms}(T_0,T_p) = \frac{01(0,T_a,T_b)}{P_{ois}(0,T_p)} \mathbb{E}^{T_p}\left(\int_{0}^{T_a} \mathbb{E}_s^{\mathbb{Q}^{T_p}}\left(D_s M(T_a,T_p)\right) \mathbb{E}_s^{\mathbb{Q}^{T_p}}\left(D_s S_{a,b}(T_a)\right) ds  \right).
+\end{equation*}
+Now, if we do a freeze of $\partial_x M(t,T_p)$ and $\partial_x S_{a,b}(t)$, then we can do the next approximation for $CA_{ois}(T_0,T_p)$
 \begin{align*}
-&CA_{CMS}(T_a,T_b)  \\
-=&01(0,T_a,T_b) \mathbb{E}^{\mathbb{Q}^{01(a,b)}}\left(S_{a,b}(T_a) \int_{0}^{T_a} \mathbb{E}_s^{01(a,b)}\left( f^{\prime}(S^{ois}_{a,b}(T_a)) \partial_{x}S^{ois}_{a,b}(T_a) D_s x_{T_a} \right) dW^{01(a,b)}_{s} \right)
+CA_{cms}(T_0,T_p) &=  \frac{01(0,T_a,T_b)}{P_{ois}(0,T_p)} \mathbb{E}^{T_p}\left(\int_{0}^{T_a} \mathbb{E}^{T_p}_s \left(\partial_x M(T_a,T_p) D_s x_{T_a}\right) \mathbb{E}^{T_p}_s \left(\partial_x S_{a,b}(T_a)D_s x_{T_a} \right) ds \right) \\
+& \approx \frac{01(0,T_a,T_b)}{P_{ois}(0,T_p)} \partial_x M(T_a,T_p, x_0, y_0)  \partial_x S_{a,b}(T_a,x_0,y_0) \mathbb{E}^{\mathbb{Q}^{T_p}}\left(\int_{0}^{T_a} \left(D_s x_{T_a} \right)^{2} ds \right).
 \end{align*}
-Now if we use again the Clark-Ocone representation, but in this case for $S_{a,b}(T_a)$ we get that
+Now, if we use (\ref{approximation_D_s_x_t}) we can estimate  
+$
+ \mathbb{E}_s^{\mathbb{Q}^{T_p}}\left(\left(D_s x_{T_a} \right)^{2}\right)
+$
+the next way 
 \begin{align*} 
-CA_{CMS}(T_a,T_b) &\approx 01(0,T_a,T_b)  f^{\prime}(S^{ois}_{a,b}(0)) \mathbb{E}^{\mathbb{Q}^{01(a,b)}}\left(S_{a,b}(T_a) \left( S^{ois}_{a,b}(T_a) - S^{ois}_{a,b}(0)\right)\right) \\
-&= 01(0,T_a,T_b)  f^{\prime}(S^{ois}_{a,b}(0)) \mathbb{E}^{\mathbb{Q}^{01(a,b)}}\left(S^{ois}_{a,b}(T_a)S_{a,b}(T_a) -  S_{a,b}(0) S^{ois}_{a,b}(0)\right)
+\mathbb{E}_s^{\mathbb{Q}^{T_p}}\left(\left(D_s x_{T_a} \right)^{2}\right) &\approx \exp\left(-2 \int_{s}^{T_a}k_u du \right) \eta^{2}(s,\bar{x}_0,\bar{y}_{T_a}) \\
+& \cdot \exp\left(\int_{s}^{T_a} \left(\partial_x \beta(u,T_a,\bar{x}_0,\bar{y}_{T_a})\right)^{2} - 2 \exp\left(-\int_{s}^{T_a}k_u du\right) \partial_x (\bar{\nu}(u,T_a) \bar{\nu}(u,T_p)) \right) du
 \end{align*}
-Where we have used that $S_{a,b}(t)$ and $S^{ois}_{a,b}(T_a)$ are $01(a,b)$-martingale. Now, if we use Itô formula to $S^{ois}_{a,b}(t)$ and $S_{a,b}(t)$ we have that
+Therefore, we have that
 \begin{align*}
-dS^{ois}_{a,b}(t,x_t,y_t) &= \partial_{x}S^{ois}_{a,b}(t,x_t,y_t)\eta(t,x_t,y_t)dW^{01(a,b)}  \\
-dS_{a,b}(t,x_t,y_t) &= \partial_{x}S_{a,b}(t,x_t,y_t)\eta(t,x_t,y_t)dW^{01(a,b)} 
-\end{align*}
-with initial condition $S^{ois}_{a,b}(0)$ and $S_{a,b}(0)$ respectivaly. Then 
-\begin{align*}
-\mathbb{E}^{\mathbb{Q}^{01(a,b)}}\left(S^{ois}_{a,b}(T_a)S_{a,b}(T_a) \right) &= \mathbb{E}^{\mathbb{Q}^{01(a,b)}}\left(\int_0^{T_a} \partial_{x}S_{a,b}(u,x_u,y_u) \partial_{x}S^{ois}_{a,b}(u,x_u,y_u)  \eta^{2}(u,x_u,y_u)
-du \right)  + S_{a,b}(0) S^{ois}_{a,b}(0) \\
-&\approx  \partial_{x}S_{a,b}(0,\bar{x}_0, \bar{y}({T_a}) \partial_{x}S^{ois}_{a,b}(0,\bar{x}_0, \bar{y}({T_a}))\int_0^{T_a} \eta^{2}(u,\bar{x}_0, \bar{y}({T_a})) du \\
-&+ S_{a,b}(0) S^{ois}_{a,b}(0).
+CA_{cms}(T_0,T_p) &\approx 
 \end{align*}
 
-Then, we can approximate $CA_{CMS}(T_a,T_b)$ the next way
-
-\fboxsep1em
-\fbox{\parbox{430pt}
-{
-\begin{align}\label{cms_adjustment}
-&CA_{CMS}(T_a,T_b)  \\
-&\approx  01(0,T_a,T_b)  f^{\prime}(S^{ois}_{a,b}(0)) \nonumber \\
-&\cdot \partial_{x}S_{a,b}(0,\bar{x}_0, \bar{y}({T_a}) \partial_{x}S^{ois}_{a,b}(0,\bar{x}_0, \bar{y}({T_a}))\int_0^{T_a} \eta^{2}(u,\bar{x}_0, \bar{y}({T_a})) du \nonumber
-\end{align}
-}}
-
 \begin{example}
-In ghe case of a Hull-White model, we showed in the example  (\ref{example_convexity_hw_ois}) that 
+In the case of a Hull-White model, we showed in the example  (\ref{example_convexity_hw_ois}) that 
 $$
@@
 \begin{equation*}
-y_t \approx \int_{0}^{s} \exp\left(-2\int_{u}^{s} k_{u^{\prime}} du^{\prime} \right) \eta(u,x_0,y_0) du
+y_t \approx \int_{0}^{t} \exp\left(-2\int_{u}^{t} k_{u^{\prime}} du^{\prime} \right) \eta(u,x_0,y_0) du
 \end{equation*}
@@
 \begin{equation*}
-X_{T_a} \approx \bar{X}(T_a):=\int_{0}^{T_a} \exp\left(-\int_{s}^{T_a}k_u du\right) \bar{y}(u) du + \int_{0}^{T_a}  \exp\left(-\int_{s}^{T_a}k_u du \right) \eta(u,\bar{x}(u),\bar{y}(u)) dW_u^{\mathbb{Q}}
+X_{T_a} \approx \bar{X}(T_a):= \bar{x}_0  + \int_{0}^{T_a} \exp\left(-\int_{s}^{T_a}k_u du\right) \bar{y}(u) du + \int_{0}^{T_a}  \exp\left(-\int_{s}^{T_a}k_u du \right) \eta(u,\bar{x}(u),\bar{y}(u)) dW_u^{\mathbb{Q}}
 \end{equation*}
-With initial condition  $\bar{x}_{0}$ is such that $S_{a,b}(0,\bar{x}_0, \bar{y}({T_a})) = S_{a,b}(0)$ (see Piterbarg Volume II).
-Then we can do the next approximation for the Malliavin derivative of $X_{T_a}$
+With initial condition  $\bar{x}_{0}$ is such that $S_{a,b}(0,\bar{x}_0, \bar{y}({T_a})) = S_{a,b}(0)$ (see Piterbarg Volume II). Now, we must remember that by Girsanov's theorem we have that 
+\begin{equation*}
+dW^{\mathbb{Q}^{T_p}} = dW^{\mathbb{Q}} + \bar{\nu}(t,T_p) dt 
+\end{equation*}
+where $\bar{\nu}(t,T_p) = \int_{t}^{T_p} \eta(s,\bar{x}_s,\bar{y}_s) ds $. Then, we have the next approximation of $\bar{x}_{T_a}$
+\begin{align*}
+X_{T_a} &\approx \bar{x}_0  + \int_{0}^{T_a} \exp\left(-\int_{s}^{T_a}k_u du\right) \bar{y}_s ds - \int_{0}^{T_a} \exp\left(-\int_{s}^{T_a}k_u du\right) \bar{\nu}(s, T_p) \eta(s,\bar{x}_s,\bar{y}_s) ds +  \\
+&+ \int_{0}^{T_a}  \exp\left(-\int_{s}^{T_a}k_u du \right) \partial_x \eta(s,\bar{x}_s,\bar{y}_s) dW_s^{\mathbb{Q}}  
+\end{align*} 
+Therefore, if we taj¡ke the Malliavin derivative of $\bar{X}_{T_a}$ we get
 \begin{equation}\label{approximation_D_s_x_t}
-D_sX_{T_a} \approx  \exp\left(-\int_{s}^{T_a}k_u du \right) \eta(u,\bar{x}_0,\bar{y}_{T_a})\bar{M}(s,T_a)
+D_sX_{T_a} \approx  \exp\left(-\int_{s}^{T_a}k_u du \right) \eta(s,\bar{x}_0,\bar{y}_{T_a})\bar{M}(s,T_a)
 \end{equation}
 where
+\begin{align*}
+\bar{M}(s,T_a) &= \exp\left(-\int_{s}^{T_a} \left( \frac{\left(\partial_x \beta(u,T_a,\bar{x}_0,\bar{y}_{T_a})\right)^{2}}{2} - \exp\left(-\int_{u}^{T_a}k_u du\right) \partial_x (\bar{\nu}(u,T_a) \bar{\nu}(u,T_p))\right) du \right) \\
+&\cdot\exp\left(\int_{s}^{t_0} \partial_x \beta(u,T_a,\bar{x}_0,\bar{y}_{T_a}) dW^{\mathbb{Q}}_u \right)
+\end{align*}
+With $\beta(u,T_a,x,y) = \exp\left(-\int_{u}^{T_a}k_u du\right) \partial_x \eta(u,x,y)$.
+Therefore, if we use the last equalities, we get the next approximation of $\mathbb{E}_s^{T_p}\left(D_s x_{T_a}\right)$
+
+\begin{equation}\label{approsimation_E_s_x_t}
+\mathbb{E}_s^{T_p}\left(D_s x_{T_a}\right) \approx \eta(s,\bar{x_0},\bar{y}_{u}) \exp\left(-\int_{s}^{T_a}k_u du \right) \exp\left(-\int_{s}^{T_a} \exp\left(-\int_{u}^{T_a}k_u du\right)\partial_x (\bar{\nu}(u,T_a) \bar{\nu}(u,T_p)) du \right).
+\end{equation}
+
+\section{Approximation of $\mathbb{E}_s^{\mathbb{Q}}\left(D_s x_{T_a}\right)$}
+Following the same procedure as before, we have that
 \begin{equation*}
-\bar{M}(s,T_a) = \exp\left(-\frac{\int_{s}^{t_0} \left(\partial_x \beta(u,T_a,\bar{x}_0,\bar{y}_{T_a})\right)^{2} du}{2} + \int_{s}^{t_0} \partial_x \beta(u,T_a,\bar{x}_0,\bar{y}_{T_a}) dW^{\mathbb{Q}}_u \right)
+X_{T_a} \approx \bar{X}(T_a):= \bar{x}_0  + \int_{0}^{T_a} \exp\left(-\int_{s}^{T_a}k_u du\right) \bar{y}(u) du + \int_{0}^{T_a}  \exp\left(-\int_{s}^{T_a}k_u du \right) \eta(u,\bar{x}(u),\bar{y}(u)) dW_u^{\mathbb{Q}}
 \end{equation*}
-Now, we must remember that by Girsanov's theorem we have that 
-\begin{equation*}
-dW^{\mathbb{Q}^{T_p}} = dW^{\mathbb{Q}} + \nu(t,T_p) dt 
-\end{equation*}
-and therefore 
-\begin{equation}\label{approsimation_E_s_x_t}
-\mathbb{E}_s^{T_p}\left(D_s x_{T_a}\right) \approx \exp\left(-\int_{s}^{T_a}k_u du \right) \eta(u,\bar{x}_0,\bar{y}_{T_a}) \exp\left(-\int_{s}^{T_a} \partial_x \beta(u,T_a,\bar{x}_0,\bar{y}_{T_a}) \nu(u,T_p) du \right)
+and therefore (see (\ref{approsimation_E_s_x_t}))
+\begin{equation}
+D_sX_{T_a} \approx  \exp\left(-\int_{s}^{T_a}k_u du \right) \eta(s,\bar{x}_0,\bar{y}_{T_a})\bar{M}(s,T_a)
+\end{equation}
+Now, if we take $\mathbb{E}^{\mathbb{Q}}\left(\cdot\right)$ we get
+\begin{equation}\label{approsimation_spot_E_s_x_t}
+\mathbb{E}^{\mathbb{Q}}_s\left(D_sX_{T_a} \right) \approx \exp\left(-\int_{s}^{T_a}k_u du \right) \eta(s,\bar{x}_0,\bar{y}_{T_a})
 \end{equation}

### 2022-11-24 ConvexityAdjustment-Lib/ConvexityAdjustment-Lib/HullWhite.cs

@@ -100,6 +100,43 @@ namespace ConvexityAdjustment_Lib
 
         }
 
+        public static double convexityCmsNewApproach(ql.Handle<ql.YieldTermStructure> discountCurve,
+            ql.Date valueDate,
+            ql.Date ta,
+            ql.Date tb,
+            ql.Date tp,
+            double c,
+            double annuityOis,
+            double partialAnnuityOis,
+            ql.DayCounter dc,
+            double k,
+            double sigma)
+        {
+            
+            // anuuity and partial_x annuity for T_a
+            
+            var dta = dc.yearFraction(valueDate, ta);
+            var dtb = dc.yearFraction(valueDate, tb);
+            var dtp = dc.yearFraction(valueDate, tp);
+            
+            var dFtp = discountCurve.link.discount(tp);
+            var dFta = discountCurve.link.discount(ta);
+            var dFtb = discountCurve.link.discount(tb);
+            var dFTaTp = dFtp / dFta;
+            var dFtaTb = dFtb / dFta; 
+            
+            // Variance Hull-White model
+            var alpha = sigma * sigma * beta(0.0, dta, 2.0 * k);
+            var m = discountCurve.link.discount(ta) / annuityOis;
+            var partialM = - (m * partialAnnuityOis / annuityOis  + beta(dta, dtp, k) * dFTaTp / annuityOis);
+            var swapOisRate = (1.0 -dFtaTb) / annuityOis;
+            var partialSwapOis = (beta(dta, dtb, k) * dFtaTb /annuityOis - swapOisRate * partialAnnuityOis / annuityOis);
+
+
+            return (annuityOis * dFta / dFtp) * c * partialM * partialSwapOis * alpha;
+
+        }
+
         #endregion
         
         #region Process tools

### 2022-11-24 ConvexityAdjustment-Lib/ConvexityAdjustmentUnitTests/CmsConvexityNewApproach.cs

@@ -35,11 +35,12 @@ namespace ConvexityAdjusmentUnitTests
             var tenorSwap = new ql.Period(5, ql.TimeUnit.Years);
 
             // Convexity test
-            var periodToCompute = new ql.Period(5, ql.TimeUnit.Years);
+            var periodToCompute = new ql.Period(1, ql.TimeUnit.Years);
             int numberOftimes = 1;
 
             List<ql.Date> datesToCompute = new List<ql.Date> {calendar.advance(startDate, periodToCompute)};
             List<double> deltaTimes = new List<double> {dc.yearFraction(startDate, datesToCompute[0])};
+            
             List<double> f0ts = new List<double>
             {
                 discountCurve.link
@@ -47,17 +48,32 @@ namespace ConvexityAdjusmentUnitTests
             };
             List<double> hjmAdjustment = new List<double>
                 {ConvexityAdjustment_Lib.HullWhite.hjmAdjustment(deltaTimes[0], k, sigma)};
-            var drift = new List<double>
+            
+            var driftForwardMeasure = new List<double>
                 {ConvexityAdjustment_Lib.HullWhite.forwardMeasureAdjustment(deltaTimes[0], k, sigma)};
 
             for (int i = 1; i < numberOftimes; i++)
             {
+                // simulation date
                 datesToCompute.Add(calendar.advance(datesToCompute[i - 1], periodToCompute));
+                
+                // pay date
+                var dateToPay = calendar.advance(datesToCompute[i], payPeriod,
+                    ql.BusinessDayConvention.ModifiedFollowing, true);
+                var deltaTimeToPay = dc.yearFraction(startDate, dateToPay);
+                
+                // year fracction form value date to sampling date
                 deltaTimes.Add(dc.yearFraction(startDate, datesToCompute[i]));
+                
+                // initial forward curve
                 f0ts.Add(discountCurve.link.forwardRate(deltaTimes[i], deltaTimes[i], ql.Compounding.Simple,
                     ql.Frequency.NoFrequency).rate());
+                
+                // y_t term
                 hjmAdjustment.Add(ConvexityAdjustment_Lib.HullWhite.hjmAdjustment(deltaTimes[i], k, sigma));
-                drift.Add(ConvexityAdjustment_Lib.HullWhite.forwardMeasureAdjustment(deltaTimes[i], k, sigma));
+                
+                // forward measure adjustment
[…]

### 2022-12-03 Latex/paper.tex
# new approach to cms mc

@@
 \begin{equation*}
-S_{a,b}(0) = \mathbb{E}^{\mathbb{Q}^{T_p}}\left(S_{a,b}(T_a)\right) + \frac{01(0,T_a,T_b)}{P_{ois}(0,T_p)} \mathbb{E}^{T_p}\left(M(T_a,T_p) \int_{0}^{T_a} \mathbb{E}_s^{\mathbb{Q}^{T_p}}\left(D_s S_{a,b}(T_a)\right) dW^{T_p}_s \right)
+S_{a,b}(0) = \mathbb{E}^{\mathbb{Q}^{T_p}}\left(S_{a,b}(T_a)\right) + M(0,T_p) \mathbb{E}^{T_p}\left( \frac{1}{M(T_a,T_p)} \int_{0}^{T_a} \mathbb{E}_s^{\mathbb{Q}^{T_p}}\left(D_s S_{a,b}(T_a)\right) dW^{T_p}_s \right)
 \end{equation*}
@@
 \begin{align*}
-S_{a,b}(0) &= \mathbb{E}^{\mathbb{Q}^{T_p}}\left(S_{a,b}(T_a)\right) + \frac{01(0,T_a,T_b)}{P_{ois}(0,T_p)} \mathbb{E}^{T_p}\left(\int_{0}^{T_a} D_s M(T_a,T_p) \mathbb{E}_s^{\mathbb{Q}^{T_p}}\left(D_s S_{a,b}(T_a)\right) ds  \right) \\
-&=\mathbb{E}^{\mathbb{Q}^{T_p}}\left(S_{a,b}(T_a)\right) + \frac{01(0,T_a,T_b)}{P_{ois}(0,T_p)} \mathbb{E}^{T_p}\left(\int_{0}^{T_a} \mathbb{E}_s^{\mathbb{Q}^{T_p}}\left(D_s M(T_a,T_p)\right) \mathbb{E}_s^{\mathbb{Q}^{T_p}}\left(D_s S_{a,b}(T_a)\right) ds  \right).
+S_{a,b}(0) &= \mathbb{E}^{\mathbb{Q}^{T_p}}\left(S_{a,b}(T_a)\right) + M(0,T_p) \mathbb{E}^{T_p}\left(\int_{0}^{T_a} D_s \left(\frac{1}{M(T_a,T_p)} \right) \mathbb{E}_s^{\mathbb{Q}^{T_p}}\left(D_s S_{a,b}(T_a)\right) ds  \right) \\
+&=\mathbb{E}^{\mathbb{Q}^{T_p}}\left(S_{a,b}(T_a)\right) + M(0,T_p) \mathbb{E}^{T_p}\left(\int_{0}^{T_a} \mathbb{E}_s^{\mathbb{Q}^{T_p}}\left(\frac{1}{M(T_a,T_p)} \right) \mathbb{E}_s^{\mathbb{Q}^{T_p}}\left(D_s S_{a,b}(T_a)\right) ds  \right).
 \end{align*}
@@
 \begin{equation*}
-CA_{cms}(T_0,T_p) = \frac{01(0,T_a,T_b)}{P_{ois}(0,T_p)} \mathbb{E}^{T_p}\left(\int_{0}^{T_a} \mathbb{E}_s^{\mathbb{Q}^{T_p}}\left(D_s M(T_a,T_p)\right) \mathbb{E}_s^{\mathbb{Q}^{T_p}}\left(D_s S_{a,b}(T_a)\right) ds  \right).
+CA_{cms}(T_0,T_p) = - \frac{01(0,T_a,T_b)}{P_{ois}(0,T_p)} \mathbb{E}^{T_p}\left(\int_{0}^{T_a} \mathbb{E}_s^{\mathbb{Q}^{T_p}}\left(D_s \left(\frac{1}{M(T_a,T_p)}\right)\right) \mathbb{E}_s^{\mathbb{Q}^{T_p}}\left(D_s S_{a,b}(T_a)\right) ds  \right).
 \end{equation*}
@@
 \begin{align*}
-CA_{cms}(T_0,T_p) &=  \frac{01(0,T_a,T_b)}{P_{ois}(0,T_p)} \mathbb{E}^{T_p}\left(\int_{0}^{T_a} \mathbb{E}^{T_p}_s \left(\partial_x M(T_a,T_p) D_s x_{T_a}\right) \mathbb{E}^{T_p}_s \left(\partial_x S_{a,b}(T_a)D_s x_{T_a} \right) ds \right) \\
-& \approx \frac{01(0,T_a,T_b)}{P_{ois}(0,T_p)} \partial_x M(T_a,T_p, x_0, y_0)  \partial_x S_{a,b}(T_a,x_0,y_0) \mathbb{E}^{\mathbb{Q}^{T_p}}\left(\int_{0}^{T_a} \left(D_s x_{T_a} \right)^{2} ds \right).
+CA_{cms}(T_0,T_p) &=  - M(0,T_p) \mathbb{E}^{T_p}\left(\int_{0}^{T_a} \mathbb{E}^{T_p}_s \left(\partial_x \left(\frac{1}{M(T_a,T_p)}\right) D_s x_{T_a}\right) \mathbb{E}^{T_p}_s \left(\partial_x S_{a,b}(T_a)D_s x_{T_a} \right) ds \right) \\
+& \approx c \frac{ \partial_x M(T_a,T_p, x_0, y_0)}{M(T_a,T_p, x_0, y_0)}  \partial_x S^{ois}_{a,b}(T_a,x_0,y_0) \mathbb{E}^{\mathbb{Q}^{T_p}}\left(\int_{0}^{T_a} \left(D_s x_{T_a} \right)^{2} ds \right).
 \end{align*}
-Now, if we use (\ref{approximation_D_s_x_t}) we can estimate  
+with $c = \frac{S_{a,b}(0)}{S^{ois}_{a,b}(0)}$. Now, if we use (\ref{approximation_D_s_x_t}) we can estimate  
 $
@@
 \begin{example}
-In the case of a Hull-White model, we showed in the example  (\ref{example_convexity_hw_ois}) that 
+In the case of a Hull-White model, we showed  in (\ref{example_convexity_hw_ois}) that 
 $$
@@
 $$
+and
+$$
+D_s x_{T_a} = \sigma \exp(-(T_a - s))
+$$
+and therefore, we have that
+\begin{equation*}
+\mathbb{E}^{\mathbb{Q}^{T_p}}\left(\int_{0}^{T_a}(D_s x_{T_a})^{2} ds \right) = \sigma^{2} \frac{1 - \exp(-2kT_a)}{2k}.
+\end{equation*}
+
+In the next figure, we can see the convexity adjustment for a CMS where the tenor for the underlying swap is 5Y using the last approximation and Monte Carlo method
 \end{example}
-Therefore (\ref{cms_adjustment}) is reduced to
-\begin{equation}\label{hullwhite_cms_convexity}
-01(0,T_a,T_b)  f^{\prime}(S^{ois}_{a,b}(T_a)) \partial_{x}S_{a,b}(0,\bar{x}_0, \bar{y}({T_a}) \partial_{x}S^{ois}_{a,b}(0,\bar{x}_0, \bar{y}({T_a}) \frac{ \sigma^2(1-\exp(-2kT_a))}{2k} 
-\end{equation}
-A common practice in market, it is suppose that $f(x)=\alpha x + \beta$ (TSR model).
-We must to impose two equations in order to get $\alpha$ and $\beta$.
-The first equation follows straightforward from the definition of $M(t,T_p)$.
-Since, $M(t,T_p)$ is a $01(a,b)-$martingale we must have that
-\begin{equation*}
-\mathbb{E}^{01(a,b)}\left(\alpha S^{ois}_{a,b}(T_a) + \beta \right) = \frac{P_{ois}(0,T_p)}{01(0,T_a,T_b)}.
-\end{equation*}
-Therefore
-\begin{equation*}
-\beta = \frac{P_{ois}(0,T_p)}{01(0,T_a,T_b,x_0,y_0)} - \alpha S^{ois}_{a,b}(0,x_0,y_0).
-\end{equation*}
-Under a separable HJM dynamic we must have that
-\begin{equation*}
-\alpha \partial_{x} S^{ois}_{a,b}(0) = - M(0,T_p)\left(G(T_a,T_p)+\frac{\partial_x 01(0,T_a,T_b)}{01(0,T_a,T_b)}\right).
-\end{equation*}
-Then
-\begin{equation*}
-\alpha = -\frac{M(0,T_p)\left(G(T_a,T_p)+\frac{\partial_x 01(0,T_a,T_b)}{01(0,T_a,T_b)}\right)}{\partial_{x} S^{ois}_{a,b}(0)}.
-\end{equation*}
-Then from the last equalities, we can approximate the convexity adjustment of a CMS rate as
-\begin{align*}
-&CA_{CMS}(T_a,T_b) \\ 
-\approx& \alpha 01(0,T_a,T_b) \partial_{x}S_{a,b}(0,\bar{x}_0, \bar{y}({T_a}) \partial_{x}S^{ois}_{a,b}(0,\bar{x}_0, \bar{y}({T_a}) \frac{ \sigma^2(1-\exp(-2kT_a))}{2k}  \\   
-=& - P_{ois}(0,T_p) \left(G(T_a,T_p)+\frac{\partial_x 01(0,T_a,T_b)}{01(0,T_a,T_b)}\right) \partial_{x}S_{a,b}(0,\bar{x}_0, \bar{y}({T_a})) \frac{S^{ois}_{a,b}(0,\bar{x}_0, \bar{y}({T_a}))}{S^{ois}_{a,b}(0)}  \frac{ \sigma^2(1-\exp(-2kT_a))}{2k}
-\end{align*}
-In the next figure, we can see the convexity adjustment for a CMS where the tenor for the underlying swap is 5Y using the last approximation and Monte Carlo method
 

### 2022-12-03 ConvexityAdjustment-Lib/ConvexityAdjustment-Lib/HullWhite.cs

@@ -100,7 +100,7 @@ namespace ConvexityAdjustment_Lib
 
         }
 
-        public static double convexityCmsNewApproach(ql.Handle<ql.YieldTermStructure> discountCurve,
+        public static double ConvexityCmsNewApproach(ql.Handle<ql.YieldTermStructure> discountCurve,
             ql.Date valueDate,
             ql.Date ta,
             ql.Date tb,
@@ -125,15 +125,16 @@ namespace ConvexityAdjustment_Lib
             var dFTaTp = dFtp / dFta;
             var dFtaTb = dFtb / dFta; 
             
-            // Variance Hull-White model
+            // Hull-White's convexity adjustment parameter
             var alpha = sigma * sigma * beta(0.0, dta, 2.0 * k);
-            var m = discountCurve.link.discount(ta) / annuityOis;
-            var partialM = - (m * partialAnnuityOis / annuityOis  + beta(dta, dtp, k) * dFTaTp / annuityOis);
-            var swapOisRate = (1.0 -dFtaTb) / annuityOis;
-            var partialSwapOis = (beta(dta, dtb, k) * dFtaTb /annuityOis - swapOisRate * partialAnnuityOis / annuityOis);
+            var m = dFTaTp / annuityOis;
+            // var partialM = - m  * (partialAnnuityOis / annuityOis  + beta(dta, dtp, k));
+            var swapOisRate = (dFta - dFtb) / annuityOis;
+            var partialSwapOis = (beta(0.0, dtb, k) * dFtb - beta(0.0, dta, k) * dFta) /annuityOis - swapOisRate * partialAnnuityOis / annuityOis;
+            var integral = sigma * sigma * (beta(dta, 2.0 * dta, k) - 0.5 * beta(dta, 3.0 * dta, k)) / k;
 
-
-            return (annuityOis * dFta / dFtp) * c * partialM * partialSwapOis * alpha;
+            // return beta(dta, dtp, k) * c * (alpha * (partialSwapOis / dFta) + (swapOisRate / dFta) * integral);
+            return beta(dta, dtp, k) * alpha * c * (partialSwapOis / dFta);
 
         }
 
@@ -165,7 +166,7 @@ namespace ConvexityAdjustment_Lib
             return m * (part1 + part2);
         }
 
-
+      
         public static double getExpectedIntegralRt(double k, double sigma, double t0, double t1)
         {
 
@@ -185,7 +186,15 @@ namespace ConvexityAdjustment_Lib
 
             return i1 + i2;
         }
[…]

### 2022-12-03 ConvexityAdjustment-Lib/ConvexityAdjustmentUnitTests/CmsConvexityNewApproach.cs

@@ -15,7 +15,7 @@ namespace ConvexityAdjusmentUnitTests
 
             // Hull-White parameters
             double k = 0.0007;
-            double sigma = 0.007;
+            double sigma = 0.00000000001;
 
             // Curves
             double discountFlatRate = 0.015;
@@ -35,7 +35,7 @@ namespace ConvexityAdjusmentUnitTests
             var tenorSwap = new ql.Period(5, ql.TimeUnit.Years);
 
             // Convexity test
-            var periodToCompute = new ql.Period(1, ql.TimeUnit.Years);
+            var periodToCompute = new ql.Period(5, ql.TimeUnit.Years);
             int numberOftimes = 1;
 
             List<ql.Date> datesToCompute = new List<ql.Date> {calendar.advance(startDate, periodToCompute)};
@@ -46,11 +46,12 @@ namespace ConvexityAdjusmentUnitTests
                 discountCurve.link
                     .forwardRate(deltaTimes[0], deltaTimes[0], ql.Compounding.Simple, ql.Frequency.NoFrequency).rate()
             };
-            List<double> hjmAdjustment = new List<double>
-                {ConvexityAdjustment_Lib.HullWhite.hjmAdjustment(deltaTimes[0], k, sigma)};
             
-            var driftForwardMeasure = new List<double>
-                {ConvexityAdjustment_Lib.HullWhite.forwardMeasureAdjustment(deltaTimes[0], k, sigma)};
+            // List<double> hjmAdjustment = new List<double>
+            //     {ConvexityAdjustment_Lib.HullWhite.hjmAdjustment(deltaTimes[0], k, sigma)};
+            
+            // var driftForwardMeasure = new List<double>
+            //     {ConvexityAdjustment_Lib.HullWhite.forwardMeasureAdjustment(deltaTimes[0], k, sigma)};
 
             for (int i = 1; i < numberOftimes; i++)
             {
@@ -70,14 +71,14 @@ namespace ConvexityAdjusmentUnitTests
                     ql.Frequency.NoFrequency).rate());
                 
                 // y_t term
-                hjmAdjustment.Add(ConvexityAdjustment_Lib.HullWhite.hjmAdjustment(deltaTimes[i], k, sigma));
+                // hjmAdjustment.Add(ConvexityAdjustment_Lib.HullWhite.hjmAdjustment(deltaTimes[i], k, sigma));
                 
                 // forward measure adjustment
[…]

### 2022-12-03 ConvexityAdjustment-Lib/ConvexityAdjustmentUnitTests/FraInArrears.cs

@@ -75,24 +75,16 @@ namespace ConvexityAdjusmentUnitTests
                 
                 for (i = 0; i < numberOfSimulations; i++)
                 {
-                    // ql.Sample<ql.IPath> sample = generator.next();
-                    // var path = (ql.Path)sample.value;
                     var sample = rsg.nextSequence();
                     var path = sample.value;
                     
                     // sampling Libor
-                    // var stdLibor =
-                    //     Math.Sqrt(ConvexityAdjustment_Lib.HullWhite.LiborVariance(delta01, delta01, delta02, sigma, k));
                     var stdLibor = sigma * ConvexityAdjustment_Lib.HullWhite.beta(delta01, delta02, k);
-                    // var aux = Math.Pow(sigma * ConvexityAdjustment_Lib.HullWhite.beta(delta01, delta02,k), 2.0);
                     
                     // Dynamic included forward measure adjustment
                     var ztDelta = z0Delta * Math.Exp(-0.5 * stdLibor * stdLibor * delta01 + stdLibor * Math.Sqrt(delta01) * path[0]);
                     var libor = (ztDelta - 1.0) / (delta02 - delta01);
                     
-                    // var rt0 = path[path.length() - 1] + mt + f0t + adjFwdMeasure;
-                    // var df12 = model.discountBond(delta01, delta02, rt0);
-                    // var libor = (1.0 / df12 - 1.0) / (delta02 - delta01);
                     var ratio = curve.link.discount(delta02) / curve.link.discount(delta01);
                     var payOff = ratio * libor * (1.0 + (delta02 - delta01) * libor);
                     mean += payOff / numberOfSimulations;

### 2022-12-05 ConvexityAdjustment-Lib/ConvexityAdjustment-Lib/HullWhite.cs
# fix bugs in cms test

@@ -220,11 +220,11 @@ namespace ConvexityAdjustment_Lib
 
         public static double GetDriftIt(double t, double k, double sigma)
         {
-            var m = Math.Pow(sigma / k, 2.0);
-            var expKt = Math.Exp(-k * t);
-            var betaT = beta(0.0, t, k);
+            var m = 0.5 * Math.Pow(sigma / k, 2.0);
+            var auxValue = sigma * sigma * Math.Pow(t, 3.0) / 6.0;
+            return m * (t + beta(t, 2.0 * t, k) - beta(0.0, t, k)- beta(0.0, t, 2.0 * k));
 
-            return m * (betaT - expKt * t - beta(0.0, t, 2.0 * k) + expKt * betaT);
+            // return m * (betaT - expKt * t - beta(0.0, t, 2.0 * k) + expKt * betaT);
         }
 
         public static double GetCovarianceRtIt(double t, double k, double sigma)

### 2022-12-05 ConvexityAdjustment-Lib/ConvexityAdjustmentUnitTests/CmsConvexity.cs

@@ -90,18 +90,18 @@ namespace ConvexityAdjusmentUnitTests
                     .value();
 
                 annuity.Add( model.GetAnnuity(startDate, startDate, f0ts[j], staticSwap.fixedSchedule(),
-                    staticSwap.fixedDayCount()));
+                    discountCurve.link.dayCounter(),  staticSwap.fixedDayCount()));
                 
                 var swapOisDerivativeT0 = model.GetPartialDerivativeSwapRate(startDate, startDate, f0ts[j],
-                    staticSwap.floatingSchedule(), staticSwap.fixedSchedule(), staticSwap.floatingDayCount(),
+                    staticSwap.floatingSchedule(), staticSwap.fixedSchedule(), discountCurve.link.dayCounter(),  staticSwap.floatingDayCount(),
                     staticSwap.fixedDayCount());
                 
                 var swapOisDerivativeTa = model.GetPartialDerivativeSwapRate(startDate, startDate, f0ts[j],
-                    staticSwap.floatingSchedule(), staticSwap.fixedSchedule(), staticSwap.floatingDayCount(),
+                    staticSwap.floatingSchedule(),  staticSwap.fixedSchedule(), discountCurve.link.dayCounter(),  staticSwap.floatingDayCount(),
                     staticSwap.fixedDayCount());
                 
                 var swapVanillaDerivative = model.GetPartialDerivativeSwapRate(startDate, startDate, f0ts[j],
-                    staticSwap.floatingSchedule(), staticForwardCurve, staticSwap.fixedSchedule(), staticSwap.floatingDayCount(),
+                    staticSwap.floatingSchedule(), staticForwardCurve, staticSwap.fixedSchedule(), discountCurve.link.dayCounter(),  staticSwap.floatingDayCount(),
                     staticSwap.fixedDayCount());
                 
                 partialOisSwapT0.Add(swapOisDerivativeT0);

### 2022-12-05 ConvexityAdjustment-Lib/ConvexityAdjustmentUnitTests/CmsConvexityNewApproach.cs

@@ -15,7 +15,7 @@ namespace ConvexityAdjusmentUnitTests
 
             // Hull-White parameters
             double k = 0.0007;
-            double sigma = 0.00000000001;
+            double sigma = 0.01;
 
             // Curves
             double discountFlatRate = 0.015;
@@ -44,14 +44,8 @@ namespace ConvexityAdjusmentUnitTests
             List<double> f0ts = new List<double>
             {
                 discountCurve.link
-                    .forwardRate(deltaTimes[0], deltaTimes[0], ql.Compounding.Simple, ql.Frequency.NoFrequency).rate()
+                    .forwardRate(deltaTimes[0], deltaTimes[0], ql.Compounding.Continuous, ql.Frequency.NoFrequency,true).rate()
             };
-            
-            // List<double> hjmAdjustment = new List<double>
-            //     {ConvexityAdjustment_Lib.HullWhite.hjmAdjustment(deltaTimes[0], k, sigma)};
-            
-            // var driftForwardMeasure = new List<double>
-            //     {ConvexityAdjustment_Lib.HullWhite.forwardMeasureAdjustment(deltaTimes[0], k, sigma)};
 
             for (int i = 1; i < numberOftimes; i++)
             {
@@ -67,18 +61,13 @@ namespace ConvexityAdjusmentUnitTests
                 deltaTimes.Add(dc.yearFraction(startDate, datesToCompute[i]));
                 
                 // initial forward curve
-                f0ts.Add(discountCurve.link.forwardRate(deltaTimes[i], deltaTimes[i], ql.Compounding.Simple,
+                f0ts.Add(discountCurve.link.forwardRate(deltaTimes[i], deltaTimes[i], ql.Compounding.Continuous,
                     ql.Frequency.NoFrequency).rate());
                 
-                // y_t term
-                // hjmAdjustment.Add(ConvexityAdjustment_Lib.HullWhite.hjmAdjustment(deltaTimes[i], k, sigma));
-                
-                // forward measure adjustment
-                // driftForwardMeasure.Add(ConvexityAdjustment_Lib.HullWhite.forwardMeasureAdjustment(deltaTimes[i], k, sigma));
             }
 
             // MC
-            int numberOfSimulations = 200000;
+            int numberOfSimulations = 500000;
             ulong seed = 123545;
 
             // outputs
@@ -116,16 +105,19 @@ namespace ConvexityAdjusmentUnitTests
                     .value();
 
[…]

### 2022-12-31 ConvexityAdjustment-Lib/ConvexityAdjustment-Lib/HullWhite.cs
# new approach of cms convexity

@@ -129,14 +129,13 @@ namespace ConvexityAdjustment_Lib
             
             // Hull-White's convexity adjustment parameter
             var alpha = sigma * sigma * beta(0.0, dta, 2.0 * k);
-            var m = dFTaTp / annuityOisTa;
             var m0 = dFtp / annuityOisT0;
-            var partialM = - m  * (partialAnnuityOisTa / annuityOisTa  + beta(dta, dtp, k));
-            var swapOisRate = (1.0 - dFtaTb) / annuityOisTa;
-            var partialSwapOis = beta(dta, dtb, k) * dFtaTb /annuityOisTa - swapOisRate * partialAnnuityOisTa / annuityOisTa;
-
-            // return beta(dta, dtp, k) * c * (alpha * (partialSwapOis / dFta) + (swapOisRate / dFta) * integral);
-            return  c * (partialM / m0) *  partialSwapOis * alpha;
+            var partialM = - m0  * (partialAnnuityOisT0 / annuityOisT0  + beta(0.0, dtp, k));
+            var swapOisRate = (dFta - dFtb) / annuityOisT0;
+            var partialSwapOis = (beta(0, dtb, k) * dFtb - beta(0, dta, k) * dFta) / annuityOisT0 -
+                                 swapOisRate * partialAnnuityOisT0 / annuityOisT0; 
+         
+            return  c * (partialM *  partialSwapOis / m0) * alpha;
 
         }
 

### 2022-12-31 ConvexityAdjustment-Lib/ConvexityAdjustmentUnitTests/CmsConvexityNewApproach.cs

@@ -35,8 +35,8 @@ namespace ConvexityAdjusmentUnitTests
             var tenorSwap = new ql.Period(5, ql.TimeUnit.Years);
 
             // Convexity test
-            var periodToCompute = new ql.Period(10, ql.TimeUnit.Years);
-            int numberOftimes = 1;
+            var periodToCompute = new ql.Period(6, ql.TimeUnit.Months);
+            int numberOftimes = 40;
 
             List<ql.Date> datesToCompute = new List<ql.Date> {calendar.advance(startDate, periodToCompute)};
             List<double> deltaTimes = new List<double> {dc.yearFraction(startDate, datesToCompute[0])};
@@ -136,8 +136,6 @@ namespace ConvexityAdjusmentUnitTests
                 double c = swapRates[j] / swapOisRates[j];
                 ratioSwaps.Add(c);
                 
-                var tP = calendar.advance(datesToCompute[j], payPeriod,
-                    ql.BusinessDayConvention.ModifiedFollowing);
                 rateCmsForward.Add(staticSwap.fairRate());
             }
 
@@ -190,10 +188,10 @@ namespace ConvexityAdjusmentUnitTests
                 
                 // Moments to simulate
                 var varRt = ConvexityAdjustment_Lib.HullWhite.GetVarianceRt(deltaTimes[j], k, sigma);
-                var varIt = ConvexityAdjustment_Lib.HullWhite.GetVarianceIt(deltaTimeTp, k, sigma);
-                var covRtIt = ConvexityAdjustment_Lib.HullWhite.GetCovarianceRtIt(deltaTimes[j], deltaTimeTp, k, sigma);
+                var varIt = ConvexityAdjustment_Lib.HullWhite.GetVarianceIt(deltaTimes[j], k, sigma);
+                var covRtIt = ConvexityAdjustment_Lib.HullWhite.GetCovarianceRtIt(deltaTimes[j], deltaTimes[j], k, sigma);
                 var driftRt = ConvexityAdjustment_Lib.HullWhite.hjmAdjustment(deltaTimes[j], k, sigma);
-                var driftIt = ConvexityAdjustment_Lib.HullWhite.GetDriftIt(deltaTimeTp, k, sigma);
+                var driftIt = ConvexityAdjustment_Lib.HullWhite.GetDriftIt(deltaTimes[j], k, sigma);
                 var rho = covRtIt / Math.Sqrt(varIt * varRt);
[…]

### 2022-12-31 ConvexityAdjustment-Lib/ConvexityAdjustmentUnitTests/FraVsFuturesTests.cs

@@ -85,9 +85,7 @@ namespace ConvexityAdjusmentUnitTests
                     momentOrderTwoMean += (libor * libor) / numberOfSimulations;
                 }
                 
-                
                 // Convexity future
-                var varAnalyticXt = sigma * sigma * (1 - Math.Exp(-2.0 * k * delta00)) / (2.0 * k);
                 var mcFuturePrice = mean;
                 var stdMc = Math.Sqrt(momentOrderTwoMean - mean * mean);
                 var intervalConfidence = new double[]

### 2023-01-01 Latex/paper.tex
# new figures and some modifications in the examples

@@
 \end{equation*}
-
 We suppose, that we have a flow in $T_a < T_p < T_b$ with value $S_{a,b}(T_a)$.
-Then, the present value of this flow under the differents measure $\mathbb{Q}^{T_a}$,$\mathbb{Q}^{01(a,b)}$ and $\mathbb{Q}^{T_p}$ respectivaly is
-\begin{align}\label{cms_expedted_value}
-P_{ois}(0,T_a)\mathbb{E}^{\mathbb{Q}^{T_{a}}}\left(S_{a,b}(T_a) P_{ois}(T_a,T_p) \right) &= 01(0,T_a,T_b) \mathbb{E}^{\mathbb{Q}^{01(a,b)}}\left(S_{a,b}(T_a) \frac{P_{ois}(T_a,T_p)}{01(T_a,T_a,T_b) }\right) \nonumber \\
-&= 01(0,T_a,T_b) \mathbb{E}^{\mathbb{Q}^{01(a,b)}}\left(S_{a,b}(T_a) M(T_a,T_p)\right) \\
-&=P_{ois}(0,T_p)\mathbb{E}^{\mathbb{Q}^{T_p}}\left(S_{a,b}(T_a)\right)
+We know that, $S_{a,b}(T_a)$ is a martingale under the measure $\mathbb{Q}^{01}$, but not under the measure $\mathbb{Q}^{T_p}$.
+Therefore
+\begin{equation*}
+\mathbb{E}^{T_p}\left(S_{a,b}(T_a)\right) \neq S_{a,b}(0).
+\end{equation*}
+Then convexity adjustment for a CMS will be define as
+\begin{equation}
+CA_{CMS}(T_p) = \mathbb{E}^{T_p}\left(S_{a,b}(T_a)\right) - S_{a,b}(0).
+\end{equation} 
+Now, after some changes of measure, it is easy to show that
+\begin{equation}\label{expected_t_p_cms}
+\mathbb{E}^{T_p}\left(S_{a,b}(T_a)\right) = \frac{1}{M(0,T_p)} \mathbb{E}^{01}\left(S_{a,b}(T_a) M(T_a,T_p)\right)
+\end{equation}
+where $M(t,T_p)= \frac{P_{ois}(t,T_p)}{01(t,T_a,T_p)}$. Now ¡, if we apply Clark-Ocone formula to $S_{a,b}(T_a)$ and $M(T_a,T_p)$ we get
+\begin{align} \label{clark_ocone_swap_m}
+S_{a,b}(T_a) &= S_{a,b}(0) + \int_{0}^{T_a} \mathbb{E}_s^{01}\left(D_s S_{a,b}(T_a) \right) dW^{01}_s  \nonumber \\
+M(T_a,T_p) &= M(0,T_p)+ \int_{0}^{T_a} \mathbb{E}_s^{01}\left(D_s M(T_a,T_p)\right) dW^{01}_s
 \end{align}
-where $M(t, T_p)= \frac{P_{ois}(t,T_p) }{01(t,T_a,T_b)} $.
-From the definition of $S_{a,b}(t)$ and $S^{ois}_{a,b}(t)$, we have that both are martingale under the measure $\mathbb{Q}^{01(a,b)}$.
-Therefore, we will define the convexity adjustment for CMS the next  way
-\begin{equation*}
-CA_{cms}(T_0,T_p) = S_{a,b}(0) - \mathbb{E}^{\mathbb{Q}^{T_p}}\left(S_{a,b}(T_a)\right). 
-\end{equation*}
-We will follow the same strategy that in the last examples. From Clark-Ocone formula we have that
-\begin{equation*}
-S_{a,b}(T_a) = \mathbb{E}^{\mathbb{Q}^{T_p}}\left(S_{a,b}(T_a)\right) + \int_{0}^{T_a} \mathbb{E}_s^{\mathbb{Q}^{T_p}}\left(D_s S_{a,b}(T_a)\right) dW^{T_p}_s 
-\end{equation*} 
-Therefore, if we take $\mathbb{E}^{01(a,b)}$ and we use the Girsanov theorem  in the last expression, we get 
-\begin{equation*}
-S_{a,b}(0) = \mathbb{E}^{\mathbb{Q}^{T_p}}\left(S_{a,b}(T_a)\right) + M(0,T_p) \mathbb{E}^{T_p}\left( \frac{1}{M(T_a,T_p)} \int_{0}^{T_a} \mathbb{E}_s^{\mathbb{Q}^{T_p}}\left(D_s S_{a,b}(T_a)\right) dW^{T_p}_s \right)
-\end{equation*}
-Now, if we use that the Skorohod integral is the adjoint operator of the Malliavin derivative, we have that
-\begin{align*}
-S_{a,b}(0) &= \mathbb{E}^{\mathbb{Q}^{T_p}}\left(S_{a,b}(T_a)\right) + M(0,T_p) \mathbb{E}^{T_p}\left(\int_{0}^{T_a} D_s \left(\frac{1}{M(T_a,T_p)} \right) \mathbb{E}_s^{\mathbb{Q}^{T_p}}\left(D_s S_{a,b}(T_a)\right) ds  \right) \\
-&=\mathbb{E}^{\mathbb{Q}^{T_p}}\left(S_{a,b}(T_a)\right) + M(0,T_p) \mathbb{E}^{T_p}\left(\int_{0}^{T_a} \mathbb{E}_s^{\mathbb{Q}^{T_p}}\left(\frac{1}{M(T_a,T_p)} \right) \mathbb{E}_s^{\mathbb{Q}^{T_p}}\left(D_s S_{a,b}(T_a)\right) ds  \right).
-\end{align*}
-Then we have the next expression for the convexity adjustment
-\begin{equation*}
-CA_{cms}(T_0,T_p) = - \frac{01(0,T_a,T_b)}{P_{ois}(0,T_p)} \mathbb{E}^{T_p}\left(\int_{0}^{T_a} \mathbb{E}_s^{\mathbb{Q}^{T_p}}\left(D_s \left(\frac{1}{M(T_a,T_p)}\right)\right) \mathbb{E}_s^{\mathbb{Q}^{T_p}}\left(D_s S_{a,b}(T_a)\right) ds  \right).
-\end{equation*}
-Now, if we do a freeze of $\partial_x M(t,T_p)$ and $\partial_x S_{a,b}(t)$, then we can do the next approximation for $CA_{ois}(T_0,T_p)$
-\begin{align*}
-CA_{cms}(T_0,T_p) &=  - M(0,T_p) \mathbb{E}^{T_p}\left(\int_{0}^{T_a} \mathbb{E}^{T_p}_s \left(\partial_x \left(\frac{1}{M(T_a,T_p)}\right) D_s x_{T_a}\right) \mathbb{E}^{T_p}_s \left(\partial_x S_{a,b}(T_a)D_s x_{T_a} \right) ds \right) \\
-& \approx c \frac{ \partial_x M(T_a,T_p, x_0, y_0)}{M(T_a,T_p, x_0, y_0)}  \partial_x S^{ois}_{a,b}(T_a,x_0,y_0) \mathbb{E}^{\mathbb{Q}^{T_p}}\left(\int_{0}^{T_a} \left(D_s x_{T_a} \right)^{2} ds \right).
-\end{align*}
-with $c = \frac{S_{a,b}(0)}{S^{ois}_{a,b}(0)}$. Now, if we use (\ref{approximation_D_s_x_t}) we can estimate  
-$
- \mathbb{E}_s^{\mathbb{Q}^{T_p}}\left(\left(D_s x_{T_a} \right)^{2}\right)
-$
-the next way 
-\begin{align*} 
-\mathbb{E}_s^{\mathbb{Q}^{T_p}}\left(\left(D_s x_{T_a} \right)^{2}\right) &\approx \exp\left(-2 \int_{s}^{T_a}k_u du \right) \eta^{2}(s,\bar{x}_0,\bar{y}_{T_a}) \\
-& \cdot \exp\left(\int_{s}^{T_a} \left(\partial_x \beta(u,T_a,\bar{x}_0,\bar{y}_{T_a})\right)^{2} - 2 \exp\left(-\int_{s}^{T_a}k_u du\right) \partial_x (\bar{\nu}(u,T_a) \bar{\nu}(u,T_p)) \right) du
-\end{align*}
-Therefore, we have that
-\begin{align*}
-CA_{cms}(T_0,T_p) &\approx 
-\end{align*}
+Then, if we sustitute the last expressions in (\ref{expected_t_p_cms}) we have that
+\begin{align}
+\mathbb{E}^{T_p}\left(S_{a,b}(T_a)\right) &= S_{a,b}(0) + \frac{1}{M(0,T_p)} \mathbb{E}^{01}\left(\int_{0}^{T_a} \mathbb{E}^{01}_{s}\left(\partial_x S_{a,b}(T_a)  D_s x_{T_a} \right)
+\mathbb{E}^{01}_{s}\left(\partial_x M(T_a,T_p)  D_s x_{T_a} \right) ds \right) \nonumber \\
+&= S_{a,b}(0) + \frac{\partial_x S_{a,b}(0)\partial_x M(0,T_p)}{M(0,T_p)} \mathbb{E}^{01}\left(\int_{0}^{T_a}  \left(\mathbb{E}^{01}\left(D_s x_{T_a}\right)\right)^{2}
+ ds\right) \nonumber \\
+&+ \cdots
+\end{align}
 
 \begin{example}
-In the case of a Hull-White model, we showed  in (\ref{example_convexity_hw_ois}) that 
-$$
-\eta(t,x_t, y_t) = \sigma\exp(-kt)
-$$
-and
+In the case of a Hull-White model, we showed  in 
 $$
@@
 \begin{equation*}
-\mathbb{E}^{\mathbb{Q}^{T_p}}\left(\int_{0}^{T_a}(D_s x_{T_a})^{2} ds \right) = \sigma^{2} \frac{1 - \exp(-2kT_a)}{2k}.
+\mathbb{E}^{\mathbb{Q}^{01}}\left(\int_{0}^{T_a}(D_s x_{T_a})^{2} ds \right) = \sigma^{2} \frac{1 - \exp(-2kT_a)}{2k}.
 \end{equation*}
@@
 In the next figure, we can see the convexity adjustment for a CMS where the tenor for the underlying swap is 5Y using the last approximation and Monte Carlo method
+
+\begin{figure}[h]
+	\begin{center}
+		\includegraphics[scale=0.3]{Figures/cms_convexity_order_1.jpg}
+		\caption{Convexity Mc Vs Convexity Malliavin}
+	\end{center}
+\end{figure}
+
 \end{example}
@@
 Therefore, if we define $\bar{y}(t)= \int_{0}^{s} \exp\left(-2\int_{u}^{s} k_{u^{\prime}} du^{\prime} \right) \eta(u,x_0,y_0)$, we have that
-\begin{equation*}
+\begin{equation}\label{approximation_x_t_a}
 X_{T_a} \approx \bar{X}(T_a):= \bar{x}_0  + \int_{0}^{T_a} \exp\left(-\int_{s}^{T_a}k_u du\right) \bar{y}(u) du + \int_{0}^{T_a}  \exp\left(-\int_{s}^{T_a}k_u du \right) \eta(u,\bar{x}(u),\bar{y}(u)) dW_u^{\mathbb{Q}}
-\end{equation*}
+\end{equation}
 With initial condition  $\bar{x}_{0}$ is such that $S_{a,b}(0,\bar{x}_0, \bar{y}({T_a})) = S_{a,b}(0)$ (see Piterbarg Volume II). Now, we must remember that by Girsanov's theorem we have that 
@@
 
+\section{Approximation of $\mathbb{E}^{01}\left(x_t\right)$ and $\mathbb{E}^{01}\left(\left(x_t -\mathbb{E}^{01}\left(x_t\right)\right)^{2}\right)$}
+It is easy to show that the dynamic of the bond under HJM assumption is
+\begin{equation}
+\frac{dP(t,T)}{P(t,T)} = r_t dt - \nu(t,T)dW^{\mathbb{Q}}_t.  
+\end{equation}
+Therefore, if we apply Itô formula we have that 
+\begin{equation}\label{annuity_spot_dynamic}
+\frac{d01(t,T_a,T_b)}{01(t,T_a,T_b)} = r_t dt - \sigma_{01}(t,T_a,T_b)dW^{\mathbb{Q}}_t
+\end{equation}
+where 
+\begin{equation} \label{annuity_vol}
+\sigma_{01}(t,T_a,T_b) = \frac{\sum_{i=a+1}^{b} \delta_{i-1,i} P(t,T_i) \nu(t,T_i)}{01(t,T_a,T_b)}.
+\end{equation}
+From (\ref{annuity_spot_dynamic}) and using the Girsanov's theorem that 
+\begin{equation*}
+dW^{01}_t = dW^{\mathbb{Q}}_t - \sigma_{01}(t,T_a,T_b)dt. 
+\end{equation*}
+We will use the last equation to get an approximation of the mean and order two moment of $x_t$. We can do the next approximaition of  (\ref{annuity_vol})
+\begin{equation}
+\sigma_{01}(t,T_a,T_b) \approx \sum_{i=a+1}^{b} w_i \nu(t,T_i)
+\end{equation}
+with $w_i=\frac{\delta_{i-1,i} P(0,T_i)}{01(0,T_a,T_b)}$. Now, if we use (\ref{short_rate_cheyette}) and the last approximation we have that
+\begin{align}
+x_t &\approx \bar{x}_0  + \int_{0}^{t} \exp\left(-\int_{s}^{t}k_u du\right) \bar{y}(u) du + \int_{0}^{t}  \exp\left(-\int_{s}^{t}k_u du \right) \eta(u,\bar{x}(u),\bar{y}(u)) dW_u^{\mathbb{Q}} \nonumber \\
+&=  \bar{x}_0  + \int_{0}^{t} \exp\left(-\int_{s}^{t}k_u du\right) \bar{y}(u) du + \int_{0}^{t} \exp\left(-\int_{s}^{t}k_u du \right) \eta(u,\bar{x}(u),\bar{y}(u)) \sigma_{01}(u, T_a, T_b) du  + \nonumber \\
+& \int_{0}^{t} \exp\left(-\int_{s}^{t}k_u du \right) \eta(u,\bar{x}(u),\bar{y}(u)) dW_u^{01} 
+\end{align}
+Therefore, we have that
+\begin{align}
+\mathbb{E}^{01}\left(x_t\right) &\approx \bar{x}_0  + \int_{0}^{t} \exp\left(-\int_{s}^{t}k_u du\right) \bar{y}(u) du + \nonumber \\ &\int_{0}^{t} \exp\left(-\int_{s}^{t}k_u du \right) \eta(u,\bar{x}(u),\bar{y}(u)) \sigma_{01}(u, T_a, T_b) du \nonumber \\
+\mathbb{E}^{01}\left(\left(x_t -\mathbb{E}^{01}\left(x_t\right)\right)^{2}\right) &\approx \int_{0}^{t} \exp\left(- 2 \int_{s}^{t}k_u du \right) \eta^{2}(u,\bar{x}(u),\bar{y}(u)) du
+\end{align}
+
 % TODO: Change bibliographystyle according to the journal style - it should know the online entry, see Matsuda04

### 2023-01-01 ConvexityAdjustment-Lib/ConvexityAdjustmentUnitTests/FraInArrears.cs

@@ -32,7 +32,7 @@ namespace ConvexityAdjusmentUnitTests
             int numberOfSimulations = 2000000;
             ulong seed = 123545;
             int timeSteps = 1;
-            var numberOfMonths = 48;
+            var numberOfMonths = 240;
 
             List<double> t0s = new List<double>();
             List<double> caMc = new List<double>();

### 2023-01-01 ConvexityAdjustment-Lib/ConvexityAdjustmentUnitTests/FraVsFuturesTests.cs

@@ -34,7 +34,7 @@ namespace ConvexityAdjusmentUnitTests
             // double deltaTime = 0.01;
             // int timeSteps = (int)(length / deltaTime);
             int timeSteps = 1;
-            var numberOfMonths = 48;
+            var numberOfMonths = 240;
 
             List<double> t0s = new List<double>();
             List<double> caMc = new List<double>();

### 2023-01-01 ConvexityAdjustment-Lib/ConvexityAdjustmentUnitTests/SofrCovexity.cs

@@ -35,7 +35,7 @@ namespace ConvexityAdjusmentUnitTests
             // double deltaTime = 0.01;
             // int timeSteps = (int)(length / deltaTime);
             // int timeSteps = 1;
-            var numberOfMonths = 48;
+            var numberOfMonths = 240;
 
             List<double> t0s = new List<double>();
             List<double> caMc = new List<double>();

### 2023-01-02 Latex/paper.tex
# new example HW cms

@@
 \end{equation}
-where $M(t,T_p)= \frac{P_{ois}(t,T_p)}{01(t,T_a,T_p)}$. Now ¡, if we apply Clark-Ocone formula to $S_{a,b}(T_a)$ and $M(T_a,T_p)$ we get
-\begin{align} \label{clark_ocone_swap_m}
-S_{a,b}(T_a) &= S_{a,b}(0) + \int_{0}^{T_a} \mathbb{E}_s^{01}\left(D_s S_{a,b}(T_a) \right) dW^{01}_s  \nonumber \\
-M(T_a,T_p) &= M(0,T_p)+ \int_{0}^{T_a} \mathbb{E}_s^{01}\left(D_s M(T_a,T_p)\right) dW^{01}_s
-\end{align}
+where $M(t,T_p)= \frac{P_{ois}(t,T_p)}{01(t,T_a,T_p)}$. Now ¡, if we apply Clark-Ocone formula to $M(T_a,T_p)$ we get that
+\begin{equation} \label{clark_ocone_swap_m}
+M(T_a,T_p) = M(0,T_p)+ \int_{0}^{T_a} \mathbb{E}_s^{01}\left(D_s M(T_a,T_p)\right) dW^{01}_s
+\end{equation}
 Then, if we sustitute the last expressions in (\ref{expected_t_p_cms}) we have that
 \begin{align}
-\mathbb{E}^{T_p}\left(S_{a,b}(T_a)\right) &= S_{a,b}(0) + \frac{1}{M(0,T_p)} \mathbb{E}^{01}\left(\int_{0}^{T_a} \mathbb{E}^{01}_{s}\left(\partial_x S_{a,b}(T_a)  D_s x_{T_a} \right)
-\mathbb{E}^{01}_{s}\left(\partial_x M(T_a,T_p)  D_s x_{T_a} \right) ds \right) \nonumber \\
-&= S_{a,b}(0) + \frac{\partial_x S_{a,b}(0)\partial_x M(0,T_p)}{M(0,T_p)} \mathbb{E}^{01}\left(\int_{0}^{T_a}  \left(\mathbb{E}^{01}\left(D_s x_{T_a}\right)\right)^{2}
- ds\right) \nonumber \\
-&+ \cdots
+\mathbb{E}^{T_p}\left(S_{a,b}(T_a)\right) &= S_{a,b}(0) + \frac{1}{M(0,T_p)} \mathbb{E}^{01}\left( S_a,b(T_a) \int_{0}^{T_a} \mathbb{E}^{0,1}_s\left(D_sX_{T_a}\partial_x M(T_a,T_p)  \right) dW^{0,1}_s   \right) \nonumber \\
+&=  S_{a,b}(0) + \frac{1}{M(0,T_p)} \mathbb{E}^{01}\left(\int_{0}^{T_a} D_s X_{T_a} \partial_x S_{a,b}(T_a) \mathbb{E}^{0,1}_s\left(D_sX_{T_a}\partial_x M(T_a,T_p)  \right) ds   \right)
 \end{align}
@@
 \begin{example}
-In the case of a Hull-White model, we showed  in 
+In order to get a little bit of intuition we will use the las t expression for the particular case of a Hull-White model. In this case, is easy to show that 
 $$
@@
 $$
-and therefore, we have that
+therefore we have that 
 \begin{equation*}
-\mathbb{E}^{\mathbb{Q}^{01}}\left(\int_{0}^{T_a}(D_s x_{T_a})^{2} ds \right) = \sigma^{2} \frac{1 - \exp(-2kT_a)}{2k}.
+\mathbb{E}^{T_p}\left(S_{a,b}(T_a)\right) = S_{a,b}(0) + \frac{1}{M(0,T_p)} \mathbb{E}^{01}\left(\int_{0}^{T_a} (D_s X_{T_a})^{2}  \mathbb{E}^{0,1}_s\left(\partial_x S_{a,b}(s) \partial_x M(s,T_p)  \right) ds \right)
 \end{equation*}
+Now, if we apply again Clark-Ocone to $\partial_x M(s,T_p)$, we get that
+
+\begin{align*}
+\mathbb{E}^{T_p}\left(S_{a,b}(T_a)\right) &= S_{a,b}(0) + \frac{\partial_x S_{a,b}(0) \partial_x M(0,T_p)}{M(0,T_p)} \mathbb{E}^{01}\left(\int_{0}^{T_a} (D_s X_{T_a})^{2} ds \right) \\
+&+ \frac{1}{M(0,T_p)} \mathbb{E}^{01}\left(\partial_x S_{a,b}(s) \int_{0}^{T_a} (D_s X_{T_a})^{2} \int_{0}^{s} \partial^{2}_{x} S_{a,b}(u_1) \partial^{2}_{x} M(u_1,T_p) (D_{u_1}x_s)^{2}  du_1 ds \right)
+\end{align*}
+We must observe that, if we repeat the same argument and
 

### 2023-01-16 Latex/paper.tex
# new approximation cms convexity

@@
 \begin{example}
-In order to get a little bit of intuition we will use the las t expression for the particular case of a Hull-White model. In this case, is easy to show that 
+In order to get a little bit of intuition we will use the last expression for the particular case of a Hull-White model. In this case, is easy to show that 
 $$
@@
 \begin{equation*}
-\mathbb{E}^{T_p}\left(S_{a,b}(T_a)\right) = S_{a,b}(0) + \frac{1}{M(0,T_p)} \mathbb{E}^{01}\left(\int_{0}^{T_a} (D_s X_{T_a})^{2}  \mathbb{E}^{0,1}_s\left(\partial_x S_{a,b}(s) \partial_x M(s,T_p)  \right) ds \right)
+\mathbb{E}^{T_p}\left(S_{a,b}(T_a)\right) = S_{a,b}(0) + \frac{1}{M(0,T_p)} \mathbb{E}^{01}\left(\int_{0}^{T_a} (D_s X_{T_a})^{2} \partial_x S_{a,b}(s) \partial_x M(s,T_p) ds \right)
 \end{equation*}
@@
 \begin{align*}
-\mathbb{E}^{T_p}\left(S_{a,b}(T_a)\right) &= S_{a,b}(0) + \frac{\partial_x S_{a,b}(0) \partial_x M(0,T_p)}{M(0,T_p)} \mathbb{E}^{01}\left(\int_{0}^{T_a} (D_s X_{T_a})^{2} ds \right) \\
-&+ \frac{1}{M(0,T_p)} \mathbb{E}^{01}\left(\partial_x S_{a,b}(s) \int_{0}^{T_a} (D_s X_{T_a})^{2} \int_{0}^{s} \partial^{2}_{x} S_{a,b}(u_1) \partial^{2}_{x} M(u_1,T_p) (D_{u_1}x_s)^{2}  du_1 ds \right)
+\mathbb{E}^{T_p}\left(S_{a,b}(T_a)\right) &= S_{a,b}(0) + \frac{\partial_x S_{a,b}(0) \partial_x M(0,T_p)}{M(0,T_p)}\int_{0}^{T_a} (D_s X_{T_a})^{2} ds \\
+&+ \frac{1}{M(0,T_p)} \mathbb{E}^{01}\left(\int_{0}^{T_a} (D_s X_{T_a})^{2} \int_{0}^{s} \partial^{2}_{x} S_{a,b}(u_1) \partial^{2}_{x} M(u_1,T_p) (D_{u_1}x_s)^{2}  du_1 ds \right)
 \end{align*}
-We must observe that, if we repeat the same argument and
+We must observe that, that it is easy to get an extra term in the expansion, only we must repeat the same argument that before, but now in $\partial^{2}_x M(u_1, T_p)$ we will get the next approximation
 
-In the next figure, we can see the convexity adjustment for a CMS where the tenor for the underlying swap is 5Y using the last approximation and Monte Carlo method
-
+\begin{align*}
+\mathbb{E}^{T_p}\left(S_{a,b}(T_a)\right) &\approx S_{a,b}(0) + \frac{\partial_x S_{a,b}(0) \partial_x M(0,T_p)}{M(0,T_p)} \int_{0}^{T_a} (D_s X_{T_a})^{2} ds \\
+&+ \frac{\partial^{2}_{x} S_{a,b}(0) \partial^{2}_{x} M(0,T_p)}{M(0,T_p)} \int_{0}^{T_a} (D_s X_{T_a})^{2} \int_{0}^{s}  (D_{u_1}x_s)^{2}  du_1 ds
+\end{align*}
+In the next figure, we can see the convexity adjustment for a CMS where the tenor for the underlying swap is 5Y using the firt approximation and Monte Carlo method
 \begin{figure}[h]
 	\begin{center}
-		\includegraphics[scale=0.3]{Figures/cms_convexity_order_1.jpg}
+		\includegraphics[scale=0.25]{Figures/cms_convexity_order_1.jpg}
 		\caption{Convexity Mc Vs Convexity Malliavin}
@@
 \end{example}
+Now, we will continue with the generic case. Follow the same idea, that in the last example, if we apply Clark-Ocone to $\partial_x M(T_a,T_p)$ we have that
+\begin{equation*}
+\partial_x M(T_a,T_p) = \partial_x M(0,T_p) + \int_{0}^{T_a} \mathbb{E}_{u_1}^{01}\left(D_{u_1} \partial^{2}_x M(T_a,T_p) D_{u_1} x_{T_a} \right) dW^{01}_{u_1}  
+\end{equation*}
+Therefore
+\begin{align}\label{general_cms_approximatìon_first_step}
+\mathbb{E}^{T_p}\left(S_{a,b}(T_a)\right) &= S_{a,b}(0) + \frac{\partial_x M(0,T_p)}{M(0,T_p)} \mathbb{E}^{01}\left(\int_{0}^{T_a} D_s X_{T_a} \partial_x S_{a,b}(T_a)
+\mathbb{E}^{01}_s\left(D_s x_{T_a} \right) ds\right) \\
+&+ \frac{1}{M(0,T_p)} \mathbb{E}^{01}\left(\int_{0}^{T_a} \partial_x S_{a,b}(T_a) D_{s} X_{T_a} \int_{0}^{T_a} \mathbb{E}_{u_1}^{01}\left(D_{u_1} \partial^{2}_x M(T_a,T_p) D_{u_1} x_{T_a} \right) dW^{01}_{u_1} ds \right)
+\end{align}
+Let us define
+\begin{align*}
+A(T_a) &= \frac{\partial_x M(0,T_p)}{M(0,T_p)} \mathbb{E}^{01}\left(\int_{0}^{T_a} D_s X_{T_a} \partial_x S_{a,b}(T_a) \mathbb{E}^{01}_s\left(D_s x_{T_a} \right) ds\right) \\
+\epsilon(T_a) &= \frac{1}{M(0,T_p)} \mathbb{E}^{01}\left(\int_{0}^{T_a} \partial_x S_{a,b}(T_a) D_{s} X_{T_a} \int_{0}^{T_a} \mathbb{E}_{u_1}^{01}\left(D_{u_1} \partial^{2}_x M(T_a,T_p) D_{u_1} x_{T_a} \right) dW^{01}_{u_1} ds \right)
+\end{align*}
+If we use again Calrk-Ocone with $\partial_x S_{a,b}(T_a)$ we have that
+\begin{equation*}
+\partial_x S_{a,b}(T_a) = \partial_x S_{a,b}(0) + \int_{0}^{T_a} \mathbb{E}^{01}\left( \mathbb{E}^{01}\left( \partial^{2}_x S_{a,b}(T_a)\right) D_s X_{T_a}  dW^{01}_s  \right) 
+\end{equation*}
+Therefore
+\begin{equation*}
+A(T_a) =
+\end{equation*}
+
+\newpage
 
@@
 \begin{equation*}
-y_t \approx \int_{0}^{t} \exp\left(-2\int_{u}^{t} k_{u^{\prime}} du^{\prime} \right) \eta(u,x_0,y_0) du
+y_t \approx \int_{0}^{t} \exp\left(-2\int_{u}^{t} k_{u^{\prime}} du^{\prime} \right) \eta^{2}(u,x_0,y_0) du
 \end{equation*}
@@
 \begin{equation}\label{approximation_x_t_a}
-X_{T_a} \approx \bar{X}(T_a):= \bar{x}_0  + \int_{0}^{T_a} \exp\left(-\int_{s}^{T_a}k_u du\right) \bar{y}(u) du + \int_{0}^{T_a}  \exp\left(-\int_{s}^{T_a}k_u du \right) \eta(u,\bar{x}(u),\bar{y}(u)) dW_u^{\mathbb{Q}}
+X_{T_a} \approx \bar{X}(T_a):= \bar{x}_0(T_a)  + \int_{0}^{T_a} \exp\left(-\int_{s}^{T_a}k_u du\right) \bar{y}(u) du + \int_{0}^{T_a}  \exp\left(-\int_{s}^{T_a}k_u du \right) \eta(u,\bar{x}(u),\bar{y}(u)) dW_u^{\mathbb{Q}}
 \end{equation}
-With initial condition  $\bar{x}_{0}$ is such that $S_{a,b}(0,\bar{x}_0, \bar{y}({T_a})) = S_{a,b}(0)$ (see Piterbarg Volume II). Now, we must remember that by Girsanov's theorem we have that 
+With initial condition  $\bar{x}_{0}(T_a)$ is such that $S_{a,b}(0,\bar{x}_0(T_a), \bar{y}({T_a})) = S_{a,b}(0)$ (see Piterbarg Volume II).
+Now, we must remember that by Girsanov's theorem we have that
 \begin{equation*}
@@
 \begin{equation}\label{approsimation_E_s_x_t}
-\mathbb{E}_s^{T_p}\left(D_s x_{T_a}\right) \approx \eta(s,\bar{x_0},\bar{y}_{u}) \exp\left(-\int_{s}^{T_a}k_u du \right) \exp\left(-\int_{s}^{T_a} \exp\left(-\int_{u}^{T_a}k_u du\right)\partial_x (\bar{\nu}(u,T_a) \bar{\nu}(u,T_p)) du \right).
+\mathbb{E}_s^{T_p}\left(D_s x_{T_a}\right) \approx \eta(s,\bar{x_0(s)},\bar{y}_{s}) \exp\left(-\int_{s}^{T_a}k_u du \right) \exp\left(-\int_{s}^{T_a} \exp\left(-\int_{u}^{T_a}k_u du\right)\partial_x (\bar{\nu}(u,T_a) \bar{\nu}(u,T_p)) du \right).
 \end{equation}
@@
 
-\section{Approximation of $\mathbb{E}^{01}\left(x_t\right)$ and $\mathbb{E}^{01}\left(\left(x_t -\mathbb{E}^{01}\left(x_t\right)\right)^{2}\right)$}
+\section{Approximation of $\mathbb{E}^{01}\left(x_t\right)$}
 It is easy to show that the dynamic of the bond under HJM assumption is
@@
 \begin{align}
-\mathbb{E}^{01}\left(x_t\right) &\approx \bar{x}_0  + \int_{0}^{t} \exp\left(-\int_{s}^{t}k_u du\right) \bar{y}(u) du + \nonumber \\ &\int_{0}^{t} \exp\left(-\int_{s}^{t}k_u du \right) \eta(u,\bar{x}(u),\bar{y}(u)) \sigma_{01}(u, T_a, T_b) du \nonumber \\
-\mathbb{E}^{01}\left(\left(x_t -\mathbb{E}^{01}\left(x_t\right)\right)^{2}\right) &\approx \int_{0}^{t} \exp\left(- 2 \int_{s}^{t}k_u du \right) \eta^{2}(u,\bar{x}(u),\bar{y}(u)) du
+\mathbb{E}^{01}\left(x_t\right) &\approx \bar{x}_0  + \int_{0}^{t} \exp\left(-\int_{s}^{t}k_u du\right) \bar{y}(u) du \nonumber \\ 
++ &\int_{0}^{t} \exp\left(-\int_{s}^{t}k_u du \right) \eta(u,\bar{x}(u),\bar{y}(u)) \sigma_{01}(u, T_a, T_b) du
 \end{align}
+
+\section{Approximation of $\mathbb{E}^{01}\left(D_s x_{T_a} \right)$}
 

### 2023-01-16 ConvexityAdjustment-Lib/ConvexityAdjustment-Lib/HullWhite.cs

@@ -2,6 +2,48 @@
     
 namespace ConvexityAdjustment_Lib
 {
+    // ql.HullWhite model, ql.Date valueDate, ql.Schedule schedule, 
+    // ql.DayCounter dcCurve, ql.DayCounter dcSwap, double x
+    public class FSolverX0HullWHite: ql.ISolver1d
+    {
+        #region attributes
+
+        private ql.HullWhite _model;
+        private ql.Date _valueDate;
+        private ql.Schedule _schedule;
+        private ql.DayCounter _dcSwap;
+        private ql.DayCounter _dcCurve;
+        private double _swapRate;
+
+        #endregion
+
+        public FSolverX0HullWHite(ql.HullWhite model, ql.Date valueDate, ql.Schedule schedule,
+            ql.DayCounter dcCurve, ql.DayCounter dcSwap, double swapRate)
+        {
+            _model = model;
+            _valueDate = valueDate;
+            _schedule = schedule;
+            _dcSwap = dcSwap;
+            _dcCurve = dcCurve;
+            _swapRate = swapRate;
+        }
+
+
+        public override double value(double v)
+        {
+            double deltaTime = _dcCurve.yearFraction(_valueDate, _schedule.dates()[0]);
+            double f0t = _model.termStructure().link.forwardRate(deltaTime, deltaTime, ql.Compounding.Continuous,
+                ql.Frequency.NoFrequency, true).rate();
+            var annuity = _model.GetAnnuity(_schedule.dates()[0], _schedule.dates()[0], v + f0t, _schedule, _dcCurve, _dcSwap);
+            var dfTa = _model.termStructure().link.discount(_schedule.dates()[0]);
+            var dfTp = _model.termStructure().link.discount(_schedule.dates()[_schedule.Count - 1]);
+            return (1.0 - (dfTa / dfTp)) / annuity.Item1 - _swapRate;
+           
+        }
+    }
+
+
+
     public static class HullWhite
     {
         
@@ -100,6 +142,55 @@ namespace ConvexityAdjustment_Lib
 
         }
 
+        public static List<double> GetDerivativeMapping(ql.Handle<ql.YieldTermStructure> discountCurve,
+            ql.Date valueDate,
+            ql.Date tp,
+            double annuityOisT0,
+            double partialAnnuityOisT0,
+            double secondPartialAnnuityOisT0,
+            ql.DayCounter dc,
+            double k,
+            double sigma)
+        {
+            
[…]

### 2023-01-16 ConvexityAdjustment-Lib/ConvexityAdjustmentUnitTests/CmsConvexity.cs

@@ -63,7 +63,7 @@ namespace ConvexityAdjusmentUnitTests
             var std = new List<double>();
             var momentOrderTwo = new Dictionary<int, double>();
             var rateCmsForward = new List<double>();
-            var annuity = new List<Tuple<double,double>>();
+            var annuity = new List<Tuple<double,double, double>>();
             var partialOisSwapTa = new List<double>();
             var partialOisSwapT0 = new List<double>();
             var partialVanillaSwap = new List<double>();

### 2023-01-16 ConvexityAdjustment-Lib/ConvexityAdjustmentUnitTests/CmsConvexityNewApproach.cs

@@ -15,7 +15,7 @@ namespace ConvexityAdjusmentUnitTests
 
             // Hull-White parameters
             double k = 0.0007;
-            double sigma = 0.01;
+            double sigma = 0.007;
 
             // Curves
             double discountFlatRate = 0.015;
@@ -36,7 +36,7 @@ namespace ConvexityAdjusmentUnitTests
 
             // Convexity test
             var periodToCompute = new ql.Period(6, ql.TimeUnit.Months);
-            int numberOftimes = 40;
+            int numberOftimes = 60;
 
             List<ql.Date> datesToCompute = new List<ql.Date> {calendar.advance(startDate, periodToCompute)};
             List<double> deltaTimes = new List<double> {dc.yearFraction(startDate, datesToCompute[0])};
@@ -77,8 +77,8 @@ namespace ConvexityAdjusmentUnitTests
             var std = new List<double>();
             var momentOrderTwo = new Dictionary<int, double>();
             var rateCmsForward = new List<double>();
-            var annuityTa = new List<Tuple<double, double>>();
-            var annuityT0 = new List<Tuple<double, double>>();
+            var annuityTa = new List<Tuple<double, double, double>>();
+            var annuityT0 = new List<Tuple<double, double, double>>();
             
             // swap derivatives, rates ans ratio
             var partialOisSwap = new List<double>();
@@ -118,7 +118,6 @@ namespace ConvexityAdjusmentUnitTests
 
          
                 partialOisSwap.Add(swapOisDerivative);
-                // partialVanillaSwap.Add(swapVanillaDerivative);
                 var swapOisFairRate =
                     (discountCurve.link.discount(datesToCompute[j]) - discountCurve.link.discount(staticSwap.maturityDate())) /
                     annuityT0[j].Item1;
@@ -148,8 +147,7 @@ namespace ConvexityAdjusmentUnitTests
 
                 // Pay date
                 var tP = calendar.advance(datesToCompute[j], payPeriod, ql.BusinessDayConvention.ModifiedFollowing);
-                var deltaTimeTp = dc.yearFraction(startDate, tP);
-
+                
                 // Dynamics curve
                 ql.Handle<ql.YieldTermStructure> hullWhiteDiscountCurve =
                     new ql.Handle<ql.YieldTermStructure>(
@@ -174,15 +172,17 @@ namespace ConvexityAdjusmentUnitTests
                     .withFloatingLegRule(ql.DateGeneration.Rule.Forward)
                     .value();
 
[…]

### 2023-01-22 ConvexityAdjustment-Lib/ConvexityAdjustment-Lib/HullWhite.cs
# last steps in convexity adjustment to cms

@@ -1,4 +1,5 @@
-﻿using ql = QLNet;
+﻿using System.Globalization;
+using ql = QLNet;
     
 namespace ConvexityAdjustment_Lib
 {
@@ -35,9 +36,13 @@ namespace ConvexityAdjustment_Lib
             double f0t = _model.termStructure().link.forwardRate(deltaTime, deltaTime, ql.Compounding.Continuous,
                 ql.Frequency.NoFrequency, true).rate();
             var annuity = _model.GetAnnuity(_schedule.dates()[0], _schedule.dates()[0], v + f0t, _schedule, _dcCurve, _dcSwap);
-            var dfTa = _model.termStructure().link.discount(_schedule.dates()[0]);
-            var dfTp = _model.termStructure().link.discount(_schedule.dates()[_schedule.Count - 1]);
-            return (1.0 - (dfTa / dfTp)) / annuity.Item1 - _swapRate;
+            
+            // times
+            var dta = _dcCurve.yearFraction(_valueDate, _schedule.dates()[0]);
+            var dtb = _dcCurve.yearFraction(_valueDate, _schedule.dates()[_schedule.Count - 1]);
+
+            var dfTaTb = _model.discountBond(dta, dtb, v + f0t);
+            return (1.0 - dfTaTb) / annuity.Item1 - _swapRate;
            
         }
     }
@@ -191,19 +196,22 @@ namespace ConvexityAdjustment_Lib
             return derivativesM[0] + derivativesM[1] * alpha + derivativesM[2] * alphaOrderTwo;
         }
 
-        public static double ConvexityCmsNewApproach(ql.Handle<ql.YieldTermStructure> discountCurve,
+        public static double ConvexityCmsNewApproach(ql.HullWhite model,
             ql.Date valueDate,
             ql.Date ta,
             ql.Date tb,
             ql.Date tp,
             double c,
-            double annuityOisT0,
-            double partialAnnuityOisT0,
-            double secondPartialAnnuityOisT0,
+            double annuityT0,
+            double annuityOisTa,
+            double partialAnnuityOisTa,
+            double secondPartialAnnuityOisTa,
             ql.DayCounter dc,
-            double k,
-            double sigma)
+            double r0_Ta)
         {
+
+            var sigma = model.sigma();
+            var k = model.a();
             
             // anuuity and partial_x annuity for T_a
             
[…]

### 2023-01-22 ConvexityAdjustment-Lib/ConvexityAdjustmentUnitTests/CmsConvexityNewApproach.cs

@@ -15,7 +15,7 @@ namespace ConvexityAdjusmentUnitTests
 
             // Hull-White parameters
             double k = 0.0007;
-            double sigma = 0.007;
+            double sigma = 0.01;
 
             // Curves
             double discountFlatRate = 0.015;
@@ -35,8 +35,8 @@ namespace ConvexityAdjusmentUnitTests
             var tenorSwap = new ql.Period(5, ql.TimeUnit.Years);
 
             // Convexity test
-            var periodToCompute = new ql.Period(6, ql.TimeUnit.Months);
-            int numberOftimes = 60;
+            var periodToCompute = new ql.Period(10, ql.TimeUnit.Years);
+            int numberOfTimes = 1;
 
             List<ql.Date> datesToCompute = new List<ql.Date> {calendar.advance(startDate, periodToCompute)};
             List<double> deltaTimes = new List<double> {dc.yearFraction(startDate, datesToCompute[0])};
@@ -47,15 +47,10 @@ namespace ConvexityAdjusmentUnitTests
                     .forwardRate(deltaTimes[0], deltaTimes[0], ql.Compounding.Continuous, ql.Frequency.NoFrequency,true).rate()
             };
 
-            for (int i = 1; i < numberOftimes; i++)
+            for (int i = 1; i < numberOfTimes; i++)
             {
                 // simulation date
                 datesToCompute.Add(calendar.advance(datesToCompute[i - 1], periodToCompute));
-                
-                // pay date
-                var dateToPay = calendar.advance(datesToCompute[i], payPeriod,
-                    ql.BusinessDayConvention.ModifiedFollowing, true);
-                var deltaTimeToPay = dc.yearFraction(startDate, dateToPay);
                 
                 // year fracction form value date to sampling date
                 deltaTimes.Add(dc.yearFraction(startDate, datesToCompute[i]));
@@ -63,7 +58,6 @@ namespace ConvexityAdjusmentUnitTests
                 // initial forward curve
                 f0ts.Add(discountCurve.link.forwardRate(deltaTimes[i], deltaTimes[i], ql.Compounding.Continuous,
                     ql.Frequency.NoFrequency).rate());
-                
             }
 
             // MC
@@ -77,8 +71,8 @@ namespace ConvexityAdjusmentUnitTests
             var std = new List<double>();
             var momentOrderTwo = new Dictionary<int, double>();
             var rateCmsForward = new List<double>();
[…]

### 2023-01-23 ConvexityAdjustment-Lib/ConvexityAdjustment-Lib/HullWhite.cs
# new advances

@@ -1,6 +1,6 @@
-﻿using System.Globalization;
-using ql = QLNet;
-    
+﻿using ql = QLNet;
+using LA = MathNet.Numerics.LinearAlgebra;    
+
 namespace ConvexityAdjustment_Lib
 {
     // ql.HullWhite model, ql.Date valueDate, ql.Schedule schedule, 
@@ -145,55 +145,6 @@ namespace ConvexityAdjustment_Lib
             var alpha = sigma * sigma * beta(0.0, dta, 2.0 * k);
             return m * alpha * partialVanillaSwap;
 
-        }
-
-        public static List<double> GetDerivativeMapping(ql.Handle<ql.YieldTermStructure> discountCurve,
-            ql.Date valueDate,
-            ql.Date tp,
-            double annuityOisT0,
-            double partialAnnuityOisT0,
-            double secondPartialAnnuityOisT0,
-            ql.DayCounter dc,
-            double k,
-            double sigma)
-        {
-            
-            var dtp = dc.yearFraction(valueDate, tp);
-            var dFtp = discountCurve.link.discount(tp);
-            
-            // partial M
-            var m0 = dFtp / annuityOisT0;
-            var partialM = - m0  * (partialAnnuityOisT0 / annuityOisT0  + beta(0.0, dtp, k));
-            var partialSecondM = - partialM *  (partialAnnuityOisT0 / annuityOisT0  + beta(0.0, dtp, k)) - m0 * (secondPartialAnnuityOisT0 / annuityOisT0 - Math.Pow(partialAnnuityOisT0 / annuityOisT0, 2.0));       
-            
-            // output 
-            List<double> output = new List<double>{ m0, partialM, partialSecondM };
-            return output;
-        }
-
-        public static double GetMappingApproximation(ql.Handle<ql.YieldTermStructure> discountCurve,
-            ql.Date valueDate,
-            ql.Date ta,
-            ql.Date tp,
-            double annuityOisT0,
-            double partialAnnuityOisT0,
-            double secondPartialAnnuityOisT0,
-            ql.DayCounter dc,
-            double k,
-            double sigma)
-        {
-            var dta = dc.yearFraction(valueDate, ta);
-            
-            // Hull-White's convexity adjustment parameter
-            var alpha = sigma * sigma * beta(0.0, dta, 2.0 * k);
[…]

### 2023-01-24 Latex/paper.tex
# last steps in convexity adjustment to cms
# new version paper

@@
 Then, if we sustitute the last expressions in (\ref{expected_t_p_cms}) we have that
-\begin{align}
-\mathbb{E}^{T_p}\left(S_{a,b}(T_a)\right) &= S_{a,b}(0) + \frac{1}{M(0,T_p)} \mathbb{E}^{01}\left( S_a,b(T_a) \int_{0}^{T_a} \mathbb{E}^{0,1}_s\left(D_sX_{T_a}\partial_x M(T_a,T_p)  \right) dW^{0,1}_s   \right) \nonumber \\
-&=  S_{a,b}(0) + \frac{1}{M(0,T_p)} \mathbb{E}^{01}\left(\int_{0}^{T_a} D_s X_{T_a} \partial_x S_{a,b}(T_a) \mathbb{E}^{0,1}_s\left(D_sX_{T_a}\partial_x M(T_a,T_p)  \right) ds   \right)
+\begin{align}\label{cms_first_order_convexity}
+\mathbb{E}^{T_p}\left(S_{a,b}(T_a)\right) =& S_{a,b}(0) + \frac{1}{M(0,T_p)} \mathbb{E}^{01}\left( S_a,b(T_a) \int_{0}^{T_a} \mathbb{E}^{0,1}_s\left(D_sX_{T_a}\partial_x M(T_a,T_p)  \right) dW^{0,1}_s   \right) \nonumber \\
+=&  S_{a,b}(0) + \frac{1}{M(0,T_p)} \mathbb{E}^{01}\left(\int_{0}^{T_a} D_s X_{T_a} \partial_x S_{a,b}(T_a) \mathbb{E}^{0,1}_s\left(D_sX_{T_a}\partial_x M(T_a,T_p)  \right) ds   \right) \nonumber \\
+\approx&  S_{a,b}(0) + \frac{\partial_x S_{a,b}(T_a, \bar{x}_0(T_a),\bar{y}(T_a))\partial_x M(T_a,T_p, \bar{x}_0(T_a),\bar{y}(T_a))}{M(0,T_p)} \mathbb{E}^{0,1}\left( \int_{0}^{T_a} \left(\mathbb{E}_s^{0,1}\left( D_s x_{T_a}\right)\right)^{2} ds  \right)
 \end{align}
@@
 \begin{example}
-In order to get a little bit of intuition we will use the last expression for the particular case of a Hull-White model. In this case, is easy to show that 
+In order to check the accuracy of the last approximation, we will compute with Monte Carlo method the exact value of $\mathbb{E}^{T_p}\left(S_{a,b}(T_a)\right)$ under spot measure $\mathbb{Q}$ i.e we will compute  $\frac{1}{P(0,T_p)}  \mathbb{E}^{\mathbb{Q}}\left(\frac{S_{a,b}(T_a)}{\beta_{T_a}} \right)$.
+In the case of a Hull-White model, we have that
 $$
@@
 $$
-therefore we have that 
+therefore (\ref{cms_first_order_convexity}) is equal to
 \begin{equation*}
-\mathbb{E}^{T_p}\left(S_{a,b}(T_a)\right) = S_{a,b}(0) + \frac{1}{M(0,T_p)} \mathbb{E}^{01}\left(\int_{0}^{T_a} (D_s X_{T_a})^{2} \partial_x S_{a,b}(s) \partial_x M(s,T_p) ds \right)
+\mathbb{E}^{T_p}\left(S_{a,b}(T_a)\right) \approx  S_{a,b}(0) + \frac{\partial_x S_{a,b}(T_a, \bar{x}_0(T_a),\bar{y}(T_a))\partial_x M(T_a,T_p, \bar{x}_0(T_a),\bar{y}(T_a))}{M(0,T_p)} \frac{\sigma^{2}(1-\exp(-2kT_a))}{2k}.
 \end{equation*}
-Now, if we apply again Clark-Ocone to $\partial_x M(s,T_p)$, we get that
+In the next figure, we can see the convexity adjustment for a CMS where the tenor of the underlying swap is 5Y using the last approximation and Montecarlo method with parameters for the Hull-White model $\sigma=0.01$ and $k=0.0007$
 
-\begin{align*}
-\mathbb{E}^{T_p}\left(S_{a,b}(T_a)\right) &= S_{a,b}(0) + \frac{\partial_x S_{a,b}(0) \partial_x M(0,T_p)}{M(0,T_p)}\int_{0}^{T_a} (D_s X_{T_a})^{2} ds \\
-&+ \frac{1}{M(0,T_p)} \mathbb{E}^{01}\left(\int_{0}^{T_a} (D_s X_{T_a})^{2} \int_{0}^{s} \partial^{2}_{x} S_{a,b}(u_1) \partial^{2}_{x} M(u_1,T_p) (D_{u_1}x_s)^{2}  du_1 ds \right)
-\end{align*}
-We must observe that, that it is easy to get an extra term in the expansion, only we must repeat the same argument that before, but now in $\partial^{2}_x M(u_1, T_p)$ we will get the next approximation
-
-\begin{align*}
-\mathbb{E}^{T_p}\left(S_{a,b}(T_a)\right) &\approx S_{a,b}(0) + \frac{\partial_x S_{a,b}(0) \partial_x M(0,T_p)}{M(0,T_p)} \int_{0}^{T_a} (D_s X_{T_a})^{2} ds \\
-&+ \frac{\partial^{2}_{x} S_{a,b}(0) \partial^{2}_{x} M(0,T_p)}{M(0,T_p)} \int_{0}^{T_a} (D_s X_{T_a})^{2} \int_{0}^{s}  (D_{u_1}x_s)^{2}  du_1 ds
-\end{align*}
-In the next figure, we can see the convexity adjustment for a CMS where the tenor for the underlying swap is 5Y using the firt approximation and Monte Carlo method
 \begin{figure}[h]
@@
 \end{example}
-Now, we will continue with the generic case. Follow the same idea, that in the last example, if we apply Clark-Ocone to $\partial_x M(T_a,T_p)$ we have that
-\begin{equation*}
-\partial_x M(T_a,T_p) = \partial_x M(0,T_p) + \int_{0}^{T_a} \mathbb{E}_{u_1}^{01}\left(D_{u_1} \partial^{2}_x M(T_a,T_p) D_{u_1} x_{T_a} \right) dW^{01}_{u_1}  
-\end{equation*}
-Therefore
-\begin{align}\label{general_cms_approximatìon_first_step}
-\mathbb{E}^{T_p}\left(S_{a,b}(T_a)\right) &= S_{a,b}(0) + \frac{\partial_x M(0,T_p)}{M(0,T_p)} \mathbb{E}^{01}\left(\int_{0}^{T_a} D_s X_{T_a} \partial_x S_{a,b}(T_a)
-\mathbb{E}^{01}_s\left(D_s x_{T_a} \right) ds\right) \\
-&+ \frac{1}{M(0,T_p)} \mathbb{E}^{01}\left(\int_{0}^{T_a} \partial_x S_{a,b}(T_a) D_{s} X_{T_a} \int_{0}^{T_a} \mathbb{E}_{u_1}^{01}\left(D_{u_1} \partial^{2}_x M(T_a,T_p) D_{u_1} x_{T_a} \right) dW^{01}_{u_1} ds \right)
-\end{align}
-Let us define
-\begin{align*}
-A(T_a) &= \frac{\partial_x M(0,T_p)}{M(0,T_p)} \mathbb{E}^{01}\left(\int_{0}^{T_a} D_s X_{T_a} \partial_x S_{a,b}(T_a) \mathbb{E}^{01}_s\left(D_s x_{T_a} \right) ds\right) \\
-\epsilon(T_a) &= \frac{1}{M(0,T_p)} \mathbb{E}^{01}\left(\int_{0}^{T_a} \partial_x S_{a,b}(T_a) D_{s} X_{T_a} \int_{0}^{T_a} \mathbb{E}_{u_1}^{01}\left(D_{u_1} \partial^{2}_x M(T_a,T_p) D_{u_1} x_{T_a} \right) dW^{01}_{u_1} ds \right)
-\end{align*}
-If we use again Calrk-Ocone with $\partial_x S_{a,b}(T_a)$ we have that
-\begin{equation*}
-\partial_x S_{a,b}(T_a) = \partial_x S_{a,b}(0) + \int_{0}^{T_a} \mathbb{E}^{01}\left( \mathbb{E}^{01}\left( \partial^{2}_x S_{a,b}(T_a)\right) D_s X_{T_a}  dW^{01}_s  \right) 
-\end{equation*}
-Therefore
-\begin{equation*}
-A(T_a) =
-\end{equation*}
 

### 2023-01-24 Latex/paper.tex
# add new appendix

@@
 \end{equation*}
-In the next figure, we can see the convexity adjustment for a CMS where the tenor of the underlying swap is 5Y using the last approximation and Montecarlo method with parameters for the Hull-White model $\sigma=0.01$ and $k=0.0007$
+In the next figure, we can see the convexity adjustment for a CMS where the tenor of the underlying swap is 5Y using the last approximation and Montecarlo method with parameters for the Hull-White model $\sigma=0.007$ and $k=0.0007$
 
@@
 	\begin{center}
-		\includegraphics[scale=0.25]{Figures/cms_convexity_order_1.jpg}
+		\includegraphics[scale=0.25]{Figures/cms_convexity_order.jpg}
 		\caption{Convexity Mc Vs Convexity Malliavin}
@@
 \end{figure} 
-
 \end{example}
-
-\newpage
 
@@
 \end{equation*}
-Therefore, if we define $\bar{y}(t)= \int_{0}^{s} \exp\left(-2\int_{u}^{s} k_{u^{\prime}} du^{\prime} \right) \eta(u,x_0,y_0)$, we have that
+Therefore, if we define 
+\begin{equation}\label{y_t_approximation}
+\bar{y}(t)= \int_{0}^{s} \exp\left(-2\int_{u}^{s} k_{u^{\prime}} du^{\prime} \right) \eta(u,x_0,y_0), 
+\end{equation}
+we have that
 \begin{equation}\label{approximation_x_t_a}
@@
 
-\begin{equation}\label{approsimation_E_s_x_t}
+\begin{equation}\label{approximation_E_s_x_t}
 \mathbb{E}_s^{T_p}\left(D_s x_{T_a}\right) \approx \eta(s,\bar{x_0(s)},\bar{y}_{s}) \exp\left(-\int_{s}^{T_a}k_u du \right) \exp\left(-\int_{s}^{T_a} \exp\left(-\int_{u}^{T_a}k_u du\right)\partial_x (\bar{\nu}(u,T_a) \bar{\nu}(u,T_p)) du \right).
@@
 Following the same procedure as before, we have that
-\begin{equation*}
-X_{T_a} \approx \bar{X}(T_a):= \bar{x}_0  + \int_{0}^{T_a} \exp\left(-\int_{s}^{T_a}k_u du\right) \bar{y}(u) du + \int_{0}^{T_a}  \exp\left(-\int_{s}^{T_a}k_u du \right) \eta(u,\bar{x}(u),\bar{y}(u)) dW_u^{\mathbb{Q}}
-\end{equation*}
+\begin{equation}\label{approximation_x_t_a}
+X_{T_a} \approx \bar{X}_{T_a}:= \bar{x}_0  + \int_{0}^{T_a} \exp\left(-\int_{s}^{T_a}k_u du\right) \bar{y}(u) du + \int_{0}^{T_a}  \exp\left(-\int_{s}^{T_a}k_u du \right) \eta(u,\bar{x}(u),\bar{y}(u)) dW_u^{\mathbb{Q}}
+\end{equation}
 and therefore (see (\ref{approsimation_E_s_x_t}))
@@
 We will use the last equation to get an approximation of the mean and order two moment of $x_t$. We can do the next approximaition of  (\ref{annuity_vol})
-\begin{equation}
-\sigma_{01}(t,T_a,T_b) \approx \sum_{i=a+1}^{b} w_i \nu(t,T_i)
+\begin{equation}\label{approximation_o1_vol}
+\sigma_{01}(t,T_a,T_b) \approx \bar{\sigma}_{0,1}(t,T_a,T_b):= \sum_{i=a+1}^{b} w_i \nu(t,T_i)
 \end{equation}
@@
 \section{Approximation of $\mathbb{E}^{01}\left(D_s x_{T_a} \right)$}
+Let us to remember that $\nu(t,T_i)=h(t,x_t,y_t) \frac{G(t,T_i)}{\beta_{t,k}}$ with  $\beta_{t,k} = \exp\left(\int_{0}^{t}k(u)\right)$. Then, we can do the next approximation 
+$$
+\nu(t,T_i) \approx \nu(t,T_i, \bar{x}_t, \bar{y}_t),
+$$ 
+therefore 
+\begin{equation*}
+D_s \nu(t,T_i) \approx  \partial_x \nu(t,T_i, \bar{x}_t, \bar{y}_t) D_s \bar{x}_t  \frac{G(t,T_i)}{\beta_{t,k}}
+\end{equation*}
+A cosequence of the last approximation is that 
+\begin{equation}
+D_s \sigma_{0,1}(t,T_a,T_b) \approx  D_s \bar{x}_t \mu(t,T_a,T_b)
+\end{equation}
+Where 
+$$
+\mu(t,T_a,T_b) =  \sum_{i=a+1}^{b} w_i \partial_x \nu(t,T_i, \bar{x}_t, \bar{y}_t) \frac{G(t,T_i)}{\beta_{t,k}}.
+$$
+
+Now, if we use the last approximation and (\ref{approximation_o1_vol}) in (\ref{approximation_x_t_a}) together with the Girsanov's theorem, we have that
+\begin{align*}
+\bar{x}_{T_a} &\approx  \bar{x}_0  + \int_{0}^{T_a} \exp\left(-\int_{s}^{T_a}k_u du\right) \bar{y}(u) du + \int_{0}^{T_a} \exp\left(-\int_{s}^{T_a}k_u du\right) \bar{\sigma}_{01}(u,T_a,T_b) du \nonumber \\\
+&+  \int_{0}^{T_a}  \exp\left(-\int_{s}^{T_a}k_u du \right) \eta(u,\bar{x}(u),\bar{y}(u)) dW_u^{\mathbb{Q}^{01}}
+\end{align*}
+Therefore
+\begin{equation*}
+D_s \bar{x}_{T_a} \approx  \exp\left(-\int_{s}^{T_a}k_u du \right) \eta(s,\bar{x}_0,\bar{y}_{T_a})\bar{M}^{01}(s,T_a)
+\end{equation*}
+where
+\begin{align*}
+\bar{M}^{01}(s,T_a) &= \exp\left(-\int_{s}^{T_a} \left(\frac{\left(\partial_x \beta(u,T_a,\bar{x}_0,\bar{y}_{T_a})\right)^{2}}{2} + \exp\left(-\int_{u}^{T_a}k_u du\right)\eta(u,\bar{x}(u),\bar{y}(u) \mu(u,T_a,T_b) du \right)\right) \\
+&\cdot\exp\left(\int_{s}^{T_a} \partial_x \beta(u,T_a,\bar{x}_0,\bar{y}_{T_a}) dW^{\mathbb{Q}^{01}}_u \right)
+\end{align*}
+with $\beta(u,T_a,x,y) = \exp\left(-\int_{u}^{T_a}k_u du\right) \partial_x \eta(u,x,y)$. Then
+
+\begin{equation}\label{approximation_E_01_s_x_t}
+\mathbb{E}^{01}_s\left(D_s x_{T_a}\right) \approx \eta(s,\bar{x_0(s)},\bar{y}_{s}) \exp\left(-\int_{s}^{T_a}k_u du \right) \exp\left(-\int_{s}^{T_a} \exp\left(\int_{u}^{T_a}k_u du\right)\eta(u,\bar{x}(u),\bar{y}(u) \mu(u,T_a,T_b) du \right).
+\end{equation}
 

### 2023-01-24 ConvexityAdjustment-Lib/ConvexityAdjustmentUnitTests/CmsConvexityNewApproach.cs

@@ -15,7 +15,7 @@ namespace ConvexityAdjusmentUnitTests
 
             // Hull-White parameters
             double k = 0.0007;
-            double sigma = 0.01;
+            double sigma = 0.007;
 
             // Curves
             double discountFlatRate = 0.015;
@@ -35,8 +35,8 @@ namespace ConvexityAdjusmentUnitTests
             var tenorSwap = new ql.Period(5, ql.TimeUnit.Years);
 
             // Convexity test
-            var periodToCompute = new ql.Period(10, ql.TimeUnit.Years);
-            int numberOfTimes = 1;
+            var periodToCompute = new ql.Period(6, ql.TimeUnit.Months);
+            int numberOfTimes = 60;
 
             List<ql.Date> datesToCompute = new List<ql.Date> {calendar.advance(startDate, periodToCompute)};
             List<double> deltaTimes = new List<double> {dc.yearFraction(startDate, datesToCompute[0])};
@@ -172,10 +172,10 @@ namespace ConvexityAdjusmentUnitTests
                 var X0Root = ConvexityAdjustment_Lib.HullWhite.GetX0(model, startDate, swap.floatingSchedule(),
                     discountCurve.link.dayCounter(), swap.fixedDayCount(), swapRates[j]);
 
-                var annuityTa = model.GetAnnuity(datesToCompute[j], datesToCompute[j], X0Root + f0ts[j], swap.fixedSchedule(),
+                var annuityTa = model.GetAnnuity(startDate, datesToCompute[j], X0Root + f0ts[j], swap.fixedSchedule(),
                     discountCurve.link.dayCounter(), swap.fixedDayCount());
                 
-                var annuityT0 = model.GetAnnuity(startDate, datesToCompute[j], f0ts[j], swap.fixedSchedule(),
+                var annuityT0 = model.GetAnnuity(startDate, startDate, f0ts[j], swap.fixedSchedule(),
                     discountCurve.link.dayCounter(), swap.fixedDayCount());
 
                 rateCmsMc[datesToCompute[j].serialNumber()] = 0.0;
@@ -244,6 +244,7 @@ namespace ConvexityAdjusmentUnitTests
                     tP,
                     ratioSwaps[j],
                     annuityT0.Item1,
+                    annuityT0.Item2,
                     annuityTa.Item1,
                     annuityTa.Item2,
                     annuityTa.Item3,

### 2023-01-25 Latex/paper.tex
# more modifications

@@
 In this section, we derive the convexity adjustment for different products.
-The advantage of using the Malliavin calculus is that it allows us to derive a general representation formula for the convexity adjustment.
+The advantage of using the Malliavin calculus is that it allows us to derive a general representation formula .
 In order to introduce a general idea of the method.
 Let define a $Z_t = f(x_t)$.
-Now, we suppose that $Z_t$ is martingale under the measure $\mathbb{Q}_1$ and that we want to compute $\mathbb{E}^{\mathbb{Q}_2}\left(Z_T \right)$, where $\mathbb{Q}_2$ is a measure such that $\frac{d\mathbb{Q}_2}{d\mathbb{Q}_1} = \lambda_t$.
-
-Since the convexity adjustment is derived for the Cheyette model, it can be applied to all included models, such as the Hull-White model.
+Now, we suppose that $Z_t$ is martingale under the measure $\mathbb{Q}_1$ and that we want to compute $\mathbb{E}^{\mathbb{Q}_2}\left(Z_T \right)$, where $\mathbb{Q}_2$ is a measure such that $dW^{\mathbb{Q}_1}_t = dW^{\mathbb{Q}_2}_t +\lambda_t dt$.
+Then, if we use the Clark-Ocone representation, we have that
+\begin{equation*}
+f(x_t) = \mathbb{E}^{\mathbb{Q}_1}\left(f(x_t)\right) + \int_{0}^{t} \mathbb{E}^{\mathbb{Q}_1}_s\left( f^{\prime}(x_t) D_s x_t  \right) dW^{\mathbb{Q}_1}_s
+\end{equation*}
+Now, if we take $\mathbb{E}^{\mathbb{Q}_2}\left( \cdot \right)$ in the previous expression and we use the Girsanov's theorem, we get that
+\begin{equation}\label{general_convexity}
+\mathbb{E}^{\mathbb{Q}_2}\left( f(x_t) \right) = f(x_0) + \mathbb{E}^{\mathbb{Q}_1} \left(\int_{0}^{t}  \mathbb{E}^{\mathbb{Q}_1}_s\left( f^{\prime}(x_t) D_s x_t  \right) \lambda_s ds \right). 
+\end{equation}
+The second term, is the convexity adjustment to due to change of measure from $\mathbb{Q}_1$ to $\mathbb{Q}_2$.
+The differents choice of $f$, $\mathbb{Q}_1$ and $\mathbb{Q}_2$ will allow us to get an approximation of the convexity adjustment for the different case of interest.
 
@@
 Observe that $L_{E}(t, t_1, t_2)$ is a martingale under the forward measure $\mathbb{Q}^{t_2}$.
-Let us define the conditional future rate as:
+Let us define the future rate as:
 \begin{equation}\label{future}
@@
 where $\mathbb{Q}$ is the measure associated to the numeraire $B_t=\exp\left(\int_{0}^{t} r_{ois, s} ds \right)$ with $ r_{ois, t}$ the risk free short rate. Using
-\eqref{forward_rate} and \eqref{future}, we can express the convexity adjustment definition as:%From \eqref{forward_rate} and \eqref{future}, we will define the convexity adjustment as
+\eqref{forward_rate} and \eqref{future}, then the convexity adjustment definition is:%From \eqref{forward_rate} and \eqref{future}, we will define the convexity adjustment as
 \begin{equation*}
 CA(t, t_0, t_1, t_2) = \hat{L}_{E}(t,t_0, t_1, t_2) - \mathbb{E}_t^{\mathbb{Q}^{t_2}}\left(L_{E}(t_0, t_1, t_2) \right).
-\end{equation*}
-We use the Clark-Ocone formula with a view to obtaining a general representation formula of the convexity adjustment for futures. Applying \eqref{clark-okone} to 
-$L_{E}(t_0,t_1,t_2)$, we obtain
-\begin{equation}
-L_{E}(t_0,t_1,t_2) = \hat{L}_{E}(t,t_0, t_1, t_2) + \int_{0}^{t_0} \mathbb{E}_{s}\left(D_s L_{E}(t_0,t_1,t_2) \right) dW^{\mathbb{Q}}_s.
-\end{equation} 
-Therefore, if we apply $\mathbb{E}^{\mathbb{Q}^{t2}}(\cdot)$ in the last equation, then we get
-\begin{equation*}
-CA(t, t_0, t_1, t_2) = - \mathbb{E}^{\mathbb{Q}^{t2}}\left(\int_{0}^{t_0} \mathbb{E}^{\mathbb{Q}}_{s}\left(D_s L_{E}(t_0,t_1,t_2) \right) dW^{\mathbb{Q}}_s \right).
 \end{equation*}
@@
 \end{equation*} 
-Therefore, if we apply Girsanov's theorem to switch to measure $\mathbb{Q}^{t_2}$, we get that
+Now, if we use (\ref{general_convexity}) with $f(x_t)=L_{E}(t,t_0, t_1, t_2)$, $\mathbb{Q}_1=\mathbb{Q}$, $\mathbb{Q}_1=\mathbb{Q}^{t_2}$ and $\lambda_t = \nu(t,t_2)$,  we get that
 \begin{equation}\label{ca_general_future}
@@
 \end{equation}
-where $\nu(t,T)$ has been defined in (\ref{ois_forward_rate_curve}). Now, from the definition of $L_{E}(t,T)$ we have that
+where $\nu(t,T)$ has been defined in (\ref{ois_forward_rate_curve}). Now, from the definition of $L_{E}(t,T)$. Now, if we calculate the malliavin derive of $L_{E}(t_0,t_1,t_2)$ we have that
 \begin{equation*}
@@
 \end{equation*}
-If we use the representation formula (\ref{bond_ois}) we get that
+Now from the zero coupon representation formula (\ref{bond_ois}) we get that
 \begin{equation*}

### 2023-01-31 Latex/paper.tex
# last version i have to end cms section

--- 2023-01-24 Latex/paper.tex
@@
 From (\ref{ois_forward_rate_curve}) and since $f_{ois}(t,T)$ is a $\mathbb{Q}^{T}$ martingale, we have that
-\begin{equation*}
+\begin{equation}\label{girsanov_spot_forward}
 dW^{\mathbb{Q}^{t_2}} = dW^{\mathbb{Q}} + \nu(t,t_2) dt. 
-\end{equation*}
+\end{equation}
 Therefore, if we apply Girsanov's theorem to switch to measure $\mathbb{Q}^{t_2}$, we get that
@@
 \begin{equation*}
-D_s L_{E}(t_0,t_1,t_2) = \frac{H(t_0,t_1)}{\delta_{t_1,t_2}H(t_0,t_2)} D_s \left(\frac{P_{ois}(t_0,t_1)}{P_{ois}(t_0,t_2)}\right). 
+D_s L_{E}(t_0,t_1,t_2) = \frac{H(t_0,t_1)}{\delta_{t_1,t_2}H(t_0,t_2)} D_s \left(\frac{P_{ois}(t_0,t_1)}{P_{ois}(t_0,t_2)}\right) 
 \end{equation*}
@@
 \end{equation}
-Now from (\ref{approximation_D_s_x_t}) with $T_a=t_0$ and $\beta(t,t_0,x,y) = \exp\left(-\int_{s}^{T_a}k_u du \right) \eta(u,x,y)$ we have that
+If we use (\ref{approximation_D_s_x_t}) with $T_a=t_0$ and $\beta(t,t_0,x,y) = \exp\left(-\int_{s}^{T_a}k_u du \right) \eta(u,x,y)$ we have that
 \begin{align*}
@@
 \begin{equation}\label{approximation_clarkocone}
-\mathbb{E}_s\left( D_s L_{E}(t_0,t_1,t_2) \right) = \frac{P_{E}(0,t_1)}{\delta_{t_1,t_2} P_{E}(0,t_2)} \left(G(t_0,t_2) \frac{P_{ois}(0,t_2)}{P_{ois}(0,t_0)} - G(t_0,t_1) \frac{P_{ois}(0,t_1)}{P_{ois}(0,t_0)}\right)\beta(t,t_0,x_0,\bar{y}_s)\bar{M}(s,t_0)
+\mathbb{E}_s\left( D_s L_{E}(t_0,t_1,t_2) \right) = \frac{P_{E}(0,t_1)}{\delta_{t_1,t_2} P_{E}(0,t_2)} \left(G(t_0,t_2)  - G(t_0,t_1)\right)\beta(t,t_0,x_0,\bar{y}_s)\bar{M}(s,t_0)
 \end{equation}
-Now, from (\ref{ca_general_future}) and (\ref{approximation_clarkocone}) we have the next approximation for the convexity adjustmet for future
+Then from (\ref{ca_general_future}) and (\ref{approximation_clarkocone}) we have the next approximation for the convexity adjustmet for future
 \hspace{1cm}
@@
 {
-\begin{align}\label{ca_approximation_futures}
-CA(t,t_0,t_1)& \nonumber \\ 
-\approx& \frac{P_{E}(0,t_1)}{\delta_{t_1,t_2} P_{E}(0,t_2)} \left(G(t_0,t_2) \frac{P_{ois}(0,t_2)}{P_{ois}(0,t_0)} - G(t_0,t_1) \frac{P_{ois}(0,t_1)}{P_{ois}(0,t_0)}\right) \int_{0}^{t_0} \beta(s,t_0,x_0,\hat{y}_s) \nu(s,t_2) ds.
-\end{align}
+\begin{equation}\label{ca_approximation_futures}
+CA(t,t_0,t_1) \approx \frac{P_{E}(0,t_1)}{\delta_{t_1,t_2} P_{E}(0,t_2)} \left(G(t_0,t_2)  - G(t_0,t_1) \right) \int_{0}^{t_0} \beta(s,t_0,x_0,\hat{y}_s) \nu(s,t_2) ds. 
+\end{equation}
 }}
@@
 \end{example}
-With this parametrization, the Cheyette model is equiavalent to Hull-White model. It is easy to show that under this parametrization, the convexity adjustment (\ref{ca_approximation_futures}) is
+With this parametrization, the Cheyette model is equiavalent to Hull-White model. Also, from the definition of $g(\cdot)$ and $h(\cdot)$, we have that
+\begin{align*}
+\eta_s &= \sigma \exp(-ks)\\
+\beta(s,u, x_0, \bar{y}_s) &= \sigma \exp(-ku) \\
+\nu(s,t_2) &= \sigma \frac{\exp(-ks) - \exp(-kt_2)}{k}\\
+\end{align*}
+Then it easy to show that the convexity adjustment (\ref{ca_approximation_futures}) is
 \begin{align*}
@@
 \end{align*}
+\newpage
 In the next figure, we can check the accuracy of the last formula versus montecarlo. The parameters that we have used are $\sigma=0.015$, $k=0.003$ and flat curve with level $r=0.01$.
@@
 
-\newpage
-
 \subsection{OIS futures}
@@
 We must observe, that both $R(\cdot,t_0,t_1)$ and $R_{avg}(\cdot,t_0,t_1)$  are not predictible and they are only observable in $t_1$. However, since
-$R(\cdot,t_0,t_1)$ and $R_{avg}(\cdot,t_0,t_1)$ are flows that will be payed in $t_1$, we can considerer the expected value under the measure $\mathbb{Q}^{t_1}$ that will observable during whole period $[t_0, t_1]$.
+$R(\cdot,t_0,t_1)$ and $R_{avg}(\cdot,t_0,t_1)$ are flows that will be payed in $t_1$, we can considerer the expected value under the measure $\mathbb{Q}$ that will observable during whole period $[t_0, t_1]$.
 Let us define the next $\mathbb{Q}$ martingales
 \begin{align*} 
-\bar{R}(t,t_0,t_1) &= \mathbb{E}^{\mathbb{Q}}\left( R(t_0,t_1)  \right) \\
-\bar{R}_{avg}(t,t_0,t_1) &= \mathbb{E}^{\mathbb{Q}}\left( R_{avg}(t_0,t_1)  \right).
+\bar{R}(t,t_0,t_1) &= \mathbb{E}_t^{\mathbb{Q}}\left( R(t_0,t_1)  \right) \\
+\bar{R}_{avg}(t,t_0,t_1) &= \mathbb{E}_t^{\mathbb{Q}}\left( R_{avg}(t_0,t_1)  \right).
 \end{align*}
-We must do several obeservations. The first observation is that, we define $F(t,t_0,t_1) = \mathbb{E}^{\mathbb{Q}^{t_1}}\left( R(t_0,t_1)\right)$, then we have that
+We must do several obeservations. The first observation is that, if we define $F(t,t_0,t_1) = \mathbb{E}^{\mathbb{Q}^{t_1}}\left( R(t_0,t_1)\right)$, then we have that
 \begin{align*}
@@
 \begin{equation}\label{R_ois_avg}
-\mathbb{E}_{t}^{\mathbb{Q}}\left(R_{avg}(t_0,t_1) \right) = \mathbb{E}_t^{\mathbb{Q}}\left( \frac{\log\left(1+ \delta_{t_0,t_1} R(t_0,t_1) \right)}{\delta_{t_0,t_1}} \right)  
+\mathbb{E}^{\mathbb{Q}}\left(R_{avg}(t_0,t_1) \right) = \mathbb{E}^{\mathbb{Q}}\left( \frac{\log\left(1+ \delta_{t_0,t_1} R(t_0,t_1) \right)}{\delta_{t_0,t_1}} \right)  
 \end{equation}
@@
 \end{equation*}
-then for $t < t_0$ from (\ref{clark-okone}) and (\ref{approximation_D_s_x_t}), we have the next representation for $I(t_0,t_1)$
+If we take $D_s$ on $I(t_0,t_1)$ we have that
+\begin{equation*}
+D_sI(t_0,t_1) = \int_{\max(s, t_{0})}^{t_1}  D_s x_u du 
+\end{equation*}
+Now, if $t < t_0$, then from (\ref{clark-okone}) and (\ref{approximation_spot_E_s_x_t}), we have that 
 \begin{align}\label{apprx_I_t0_t1}
-I(t_0,t_1) &= \mathbb{E}^{\mathbb{Q}}\left(I(t_0,t_1)\right) + \int_{0}^{t_1}\int_{\max(s, t_{0})}^{t_1}  \mathbb{E}_s^{\mathbb{Q}}\left(\beta(s,u,x_s,y_s) \bar{M}(s,u) \right) du dW_s^{\mathbb{Q}} \nonumber \\
-&\approx \mathbb{E}^{\mathbb{Q}}\left(I(t_0,t_1)\right) + \int_{0}^{t_1}\int_{\max(s, t_{0})}^{t_1} \beta(s,u,x_0,\hat{y}_s) du dW_s^{\mathbb{Q}}\nonumber \\
-&= \mathbb{E}^{\mathbb{Q}}\left(I(t_0,t_1)\right) + \int_{0}^{t_1} g(s)h(s,x_0,\hat{y}_s)\int_{\max(s, t_{0})}^{t_1} \exp\left( -\int_{s}^{u} k_{s^{\prime}} ds^{\prime}\right) du dW_s^{\mathbb{Q}}.
+I(t_0,t_1) &= \mathbb{E}_t^{\mathbb{Q}}\left(I(t_0,t_1)\right) + \int_{t}^{t_1}\int_{\max(s, t_{0})}^{t_1}  \mathbb{E}_s^{\mathbb{Q}}\left(\beta(s,u,x_s,y_s) \bar{M}(s,u) \right) du dW_s^{\mathbb{Q}} \nonumber \\
+&\approx \mathbb{E}_t^{\mathbb{Q}}\left(I(t_0,t_1)\right) + \int_{t}^{t_1}\int_{\max(s, t_{0})}^{t_1} \beta(s,u,x_0,\bar{y}_s) du dW_s^{\mathbb{Q}}\nonumber \\
+&= \mathbb{E}_t^{\mathbb{Q}}\left(I(t_0,t_1)\right) + \int_{t}^{t_1} g(s)h(s,x_0,\bar{y}_s)\int_{\max(s, t_{0})}^{t_1} \exp\left( -\int_{s}^{u} k_{s^{\prime}} ds^{\prime}\right) du dW_s^{\mathbb{Q}}.
 \end{align}
-Therefore, we can get the next approximation
+Then, using the previous approximation, we get that
 \begin{align*}
-1 + \delta_{t_0,t_1}\mathbb{E}^{\mathbb{Q}^{t_1}}\left(R(t_0,t_1)\right) &= \mathbb{E}^{\mathbb{Q}^{t_1}}\left( \exp(I(t_0,t_1)) \right)\\
-&= \exp\left(\mathbb{E}^{\mathbb{Q}}\left(I(t_0,t_1)\right)\right)  \mathbb{E}^{\mathbb{Q}^{t_1}}\left(\exp\left(\int_{0}^{t_1} \Gamma(s,t_0,t_1)dW_s^{\mathbb{Q}}\right)\right)
+1 + \delta_{t_0,t_1}\mathbb{E}_t^{\mathbb{Q}}\left(R(t_0,t_1)\right) &= \mathbb{E}_t^{\mathbb{Q}}\left( \exp(I(t_0,t_1)) \right)\\
+&\approx \exp\left(\mathbb{E}_t^{\mathbb{Q}}\left(I(t_0,t_1)\right)\right)  \mathbb{E}^{\mathbb{Q}}\left(\exp\left(\int_{t}^{t_1} \Gamma(s,t_0,t_1)dW_s^{\mathbb{Q}}\right)\right)
 \end{align*}
-where $\Gamma(s,t_0,t_1)= g(s)h(s,x_0,\hat{y}_s)\int_{\max(s, t_{0})}^{t_1} \exp\left( -\int_{s}^{u} k_{s^{\prime}} ds^{\prime}\right)du$. Now, from the Girsanov's theorem we get that
-\begin{equation*}
-1 + \delta_{t_0,t_1}\mathbb{E}^{\mathbb{Q}}\left(R(t_0,t_1)\right) \approx \exp\left(\mathbb{E}^{\mathbb{Q}}\left(I(t_0,t_1)\right)\right)\exp\left(\int_{0}^{t_1}\frac{\Gamma^{2}(s,t_0,t_1)}{2} ds\right)
-\end{equation*}
-Therefore we have that
+where $\Gamma(s,t_0,t_1)= g(s)h(s,x_0,y_0)\int_{\max(s, t_{0})}^{t_1} \exp\left( -\int_{s}^{u} k_{s^{\prime}} ds^{\prime}\right)du$. 
+Since, the Girsanov's theorem (see (\ref{girsanov_spot_forward}))
+\begin{equation}\label{representation_i_0_t}
+1 + \delta_{t_0,t_1}\mathbb{E}^{\mathbb{Q}}\left(R(t_0,t_1)\right) \approx \exp\left(\mathbb{E}^{\mathbb{Q}}\left(I(t_0,t_1)\right)\right)\exp\left(\int_{t}^{t_1}\frac{ \Gamma^{2}(s,t_0,t_1)}{2} ds\right)
+\end{equation}
+Therefore
 
@@
 \begin{equation}\label{convexity_ois_future}
-\mathbb{E}^{\mathbb{Q}}\left(R(t_0,t_1)\right) \approx \frac{\exp\left(\mathbb{E}^{\mathbb{Q}}\left(I(t_0,t_1)\right)\right)\exp\left(\int_{0}^{t_1}\frac{\Gamma^{2}(s,t_0,t_1)}{2} ds\right) - 1}{\delta_{t_0,t_1}}
+\mathbb{E}_t^{\mathbb{Q}}\left(R(t_0,t_1)\right) \approx \frac{\exp\left(\mathbb{E}_t^{\mathbb{Q}}\left(I(t_0,t_1)\right)\right)\exp\left(\int_{t}^{t_1}\frac{\Gamma^{2}(s,t_0,t_1)}{2} ds\right) - 1}{\delta_{t_0,t_1}}
 \end{equation}
 }}
+In order to get an approximation of $\mathbb{E}^{\mathbb{Q}}\left(R_{avg}(t_0,t_1)\right)$ with base $\mathbb{E}^{\mathbb{Q}}\left(R(t_0,t_1)\right)$, we must note that 
+\begin{equation*}
+\mathbb{E}_t^{\mathbb{Q}}\left(R_{avg}(t_0,t_1)\right) = \frac{\mathbb{E}_t^{\mathbb{Q}}\left( \log(1+ \delta_{t_0,t_1} R(t_0,t_1))\right)}{ \delta_{t_0,t_1}}.
+\end{equation*}
+Then from (\ref{representation_i_0_t}) we get that
+\begin{equation}\label{convexity_avg_ois_future}
+\mathbb{E}_t^{\mathbb{Q}}\left(R_{avg}(t_0,t_1)\right) = \frac{\mathbb{E}_t^{\mathbb{Q}}\left(I(t_0,t_1)\right) }{\delta_{t_0,t_1}} \approx \frac{\log\left(1+\delta_{t_0,t_1}  \mathbb{E}_t^{\mathbb{Q}}\left(R(t_0,t_1)\right) \right)}{\delta_{t_0,t_1}} + \frac{\int_{0}^{t_1}  \Gamma^{2}(s,t_0,t_1) ds}{2\delta_{t_0,t_1}}
+\end{equation}
+The last step, is to use the basic inequality $\log(1+x) \approx x$
+when $x \approx 0$. If we do that, we get the next approximation for $\mathbb{E}^{\mathbb{Q}}\left(R_{avg}(t_0,t_1)\right)$
 
-We must note, that from (\ref{apprx_I_t0_t1}) and (\ref{R_ois_avg}) we can get an approximation for $R_{avg}(t_0,t_1)$
-
-\hspace{2cm}
 \fboxsep1em
-\fbox{\parbox{335pt}
+\fbox{\parbox{300pt}
 {
-\begin{equation}\label{convexity_avg_ois_future}
-R_{avg}(t_0,t_1) = \frac{\mathbb{E}^{\mathbb{Q}}\left(I(t_0,t_1)\right) }{\delta_{t_0,t_1}} \approx \frac{\log\left(1+\delta_{t_0,t_1}  \mathbb{E}^{\mathbb{Q}}\left(R(t_0,t_1)\right) \right)}{\delta_{t_0,t_1}} - \frac{\int_{0}^{t_1}\Gamma^{2}(s,t_0,t_1) ds}{2\delta_{t_0,t_1}}
-\end{equation}
+\begin{equation*}\label{convexity_avg_ois_future}
+\mathbb{E}_t^{\mathbb{Q}}\left(R_{avg}(t_0,t_1)\right) \approx  \mathbb{E}_t^{\mathbb{Q}}\left(R(t_0,t_1)\right) + \frac{\int_{0}^{t_1}\Gamma^{2}(s,t_0,t_1) ds}{2\delta_{t_0,t_1}}.
+\end{equation*}
 }}
-
-Therefore, since $\log(1+x)\approx x$ we have that
-
-\begin{equation*}
-R_{avg}(t_0,t_1) \approx  \mathbb{E}^{\mathbb{Q}}\left(R(t_0,t_1)\right) - \frac{\int_{0}^{t_1}\Gamma^{2}(s,t_0,t_1) ds}{2\delta_{t_0,t_1}}.
-\end{equation*}
 
@@
 \begin{align*}
-\eta_s &= \sigma \exp(-ks)\\
-\beta(s,u, x_0, \hat{y}_s) &= \sigma \exp(-ku) \\
-\nu(s,t_1) &= \sigma \frac{\exp(-ks) - \exp(-kt_1)}{k}\\
 \Gamma(s,t_0,t_1) &= \frac{\sigma \exp(-ks)}{k}\left(\exp(-k(\max(s,t_0) - s)) - \exp(-k(t_1-s))\right)\\
@@
 \end{align*}
-Then if we substitute the last equality in (\ref{convexity_ois_future}) we get the convexity adjustment for OIS future.
-The next figure, show accuracy of (\ref{convexity_ois_future}) in the case of Hull-White
+Then, if we substitute the last equalities in (\ref{convexity_ois_future}) we get an approximation for OIS future at $t=0$.
+The next figure, show accuracy of (\ref{convexity_ois_future}) for the particular case of a Hull-White model.
 
@@
 	\begin{center}
-		\includegraphics[scale=0.3]{Figures/convexity_ois.jpg}
+		\includegraphics[scale=0.2]{Figures/convexity_ois.jpg}
 		\caption{Convexity Mc Vs Convexity Malliavin}
@@
 \subsection{FRAs in arrears}
-The cash flows associated to a FRAs in arrears is $L_{E}(t_1,t_1,t_2)$ in $t_1$. Therefore the payment will be
+The price of a FRA in arrears, is the most classic example between the porducts with convexity adjustment.
+The cash flows associated to a FRAs in arrears is $L_{E}(t_1,t_1,t_2)$ in $t_1$.
+Therefore the payment will be
 \begin{equation}
@@
 
-\newpage
-
 \subsection{CMSs}
+In this last section we will study convexity adjustment for a CMS.
+Let us to introduce some notation, we will use it throughout the section.
 We will define the swap rate from $T_a$ to $T_b$ at time $t$
@@
 \end{align*}
-The same way, let us define
+The same way, we will define the OIS swap rate as
 \begin{equation*}
@@
 \end{equation*}
-We suppose, that we have a flow in $T_a < T_p < T_b$ with value $S_{a,b}(T_a)$.
+Now, we suppose that we have a flow in $T_a < T_p < T_b$ with value $S_{a,b}(T_a)$.
 We know that, $S_{a,b}(T_a)$ is a martingale under the measure $\mathbb{Q}^{01}$, but not under the measure $\mathbb{Q}^{T_p}$.
-Therefore
-\begin{equation*}
-\mathbb{E}^{T_p}\left(S_{a,b}(T_a)\right) \neq S_{a,b}(0).
-\end{equation*}
-Then convexity adjustment for a CMS will be define as
+Therefore, we we have to take into consideration the effect to compute the expected value of $S_{a,b}(T_a)$ in a measure which is not its natural measure.
+Then, the convexity adjustment for a CMS is
 \begin{equation}
@@
 \end{equation} 
-Now, after some changes of measure, it is easy to show that
-\begin{equation}\label{expected_t_p_cms}
-\mathbb{E}^{T_p}\left(S_{a,b}(T_a)\right) = \frac{1}{M(0,T_p)} \mathbb{E}^{01}\left(S_{a,b}(T_a) M(T_a,T_p)\right)
-\end{equation}
-where $M(t,T_p)= \frac{P_{ois}(t,T_p)}{01(t,T_a,T_p)}$. Now ¡, if we apply Clark-Ocone formula to $M(T_a,T_p)$ we get that
+After some changes of measure, it is easy to show that
+\begin{align}\label{expected_t_p_cms}
+\mathbb{E}^{T_p}\left(S_{a,b}(T_a)\right) &= \frac{1}{M(0,T_p)} \mathbb{E}^{01}\left(S_{a,b}(T_a) M(T_a,T_p)\right) \nonumber \\
+&= \frac{1}{M(0,T_p)} \mathbb{E}^{01}\left(S_{a,b}(T_a) \mathbb{E}^{01}\left( M(T_a,T_p)|S_{a,b}(T_a)\right) \right)
+\end{align}
+where $M(t,T_p)= \frac{P_{ois}(t,T_p)}{01(t,T_a,T_p)}$.
+It is common practice to assume that $M(T_a,T_p)$ is a funtion of the swap rate $S_{a,b}(T_a)$ i.e   $M(T_a,T_p)=f(S_{a,b}(T_a))$.
+The function $f(\cdot)$ is known as mapping function, and there is a vast literatura about how to choose it (see Piterbarg Volumen III, Hagan paper convexity withour replication).
+We will, try to do an approach, without to specify any mapping function.
+
+where $M(t,T_p)= \frac{P_{ois}(t,T_p)}{01(t,T_a,T_p)}$. Now, if we apply Clark-Ocone formula to $M(T_a,T_p)$ we get that
 \begin{equation} \label{clark_ocone_swap_m}
@@
 \end{equation*}
-In the next figure, we can see the convexity adjustment for a CMS where the tenor of the underlying swap is 5Y using the last approximation and Montecarlo method with parameters for the Hull-White model $\sigma=0.007$ and $k=0.0007$
+In the next figure, we can see the convexity adjustment for a CMS where the tenor of the underlying swap is 5Y using the last approximation and Montecarlo method with parameters for the Hull-White model $\sigma=0.01$ and $k=0.0007$
 
@@
 \end{example}
+
+\newpage
 
@@
 \end{equation*}
-Therefore, if we define 
-\begin{equation}\label{y_t_approximation}
-\bar{y}(t)= \int_{0}^{s} \exp\left(-2\int_{u}^{s} k_{u^{\prime}} du^{\prime} \right) \eta(u,x_0,y_0), 
-\end{equation}
-we have that
+Therefore, if we define $\bar{y}(t)= \int_{0}^{s} \exp\left(-2\int_{u}^{s} k_{u^{\prime}} du^{\prime} \right) \eta(u,x_0,y_0)$, we have that
 \begin{equation}\label{approximation_x_t_a}
@@
 \end{equation}
-With initial condition  $\bar{x}_{0}(T_a)$ is such that $S_{a,b}(0,\bar{x}_0(T_a), \bar{y}({T_a})) = S_{a,b}(0)$ (see Piterbarg Volume II).
-Now, we must remember that by Girsanov's theorem we have that
+With initial condition  $\bar{x}_{0}(T_a)$ is such that $S_{a,b}(T_a,\bar{x}_0(T_a), \bar{y}_{T_a}) = S_{a,b}(0)$ (see Piterbarg Volume II). Now, we must remember that 
 \begin{equation*}
@@
 \end{equation*}
-where $\bar{\nu}(t,T_p) = \int_{t}^{T_p} \eta(s,\bar{x}_s,\bar{y}_s) ds $. Then, we have the next approximation of $\bar{x}_{T_a}$
+where $\bar{\nu}(t,T_p) = \int_{t}^{T_p} \eta(s,\bar{x}_s,\bar{y}_s) ds $. Then, we have the next approximation of $\bar{x}_{T_a}$ under measure $\mathbb{Q}^{T_p}$
 \begin{align*}
 X_{T_a} &\approx \bar{x}_0  + \int_{0}^{T_a} \exp\left(-\int_{s}^{T_a}k_u du\right) \bar{y}_s ds - \int_{0}^{T_a} \exp\left(-\int_{s}^{T_a}k_u du\right) \bar{\nu}(s, T_p) \eta(s,\bar{x}_s,\bar{y}_s) ds +  \\
-&+ \int_{0}^{T_a}  \exp\left(-\int_{s}^{T_a}k_u du \right) \partial_x \eta(s,\bar{x}_s,\bar{y}_s) dW_s^{\mathbb{Q}}  
+&+ \int_{0}^{T_a}  \exp\left(-\int_{s}^{T_a}k_u du \right)\eta(s,\bar{x}_s,\bar{y}_s) dW_s^{\mathbb{Q}^{T_p}}  
 \end{align*} 
-Therefore, if we taj¡ke the Malliavin derivative of $\bar{X}_{T_a}$ we get
+Then, if we take $D_s$ on $\bar{X}_{T_a}$ we get that (esto hay que formalizarlo...)
 \begin{equation}\label{approximation_D_s_x_t}
-D_sX_{T_a} \approx  \exp\left(-\int_{s}^{T_a}k_u du \right) \eta(s,\bar{x}_0,\bar{y}_{T_a})\bar{M}(s,T_a)
+D_sX_{T_a} \approx  \exp\left(-\int_{s}^{T_a}k_u du \right) \eta(s,\bar{x}_0(T_a),\bar{y}(T_a))\bar{M}(s,T_a)
 \end{equation}
@@
 \begin{align*}
-\bar{M}(s,T_a) &= \exp\left(-\int_{s}^{T_a} \left( \frac{\left(\partial_x \beta(u,T_a,\bar{x}_0,\bar{y}_{T_a})\right)^{2}}{2} - \exp\left(-\int_{u}^{T_a}k_u du\right) \partial_x (\bar{\nu}(u,T_a) \bar{\nu}(u,T_p))\right) du \right) \\
+\bar{M}(s,T_a) &= \exp\left(-\int_{s}^{T_a} \left( \frac{\left(\partial_x \beta(u,T_a,\bar{x}_0,\bar{y}_{T_a})\right)^{2}}{2} - \exp\left(-\int_{u}^{T_a}k_u du\right) \partial_x (\eta(u, \bar{x}_u, \bar{y}_{u}) \bar{\nu}(u,T_p))\right) du \right) \\
 &\cdot\exp\left(\int_{s}^{t_0} \partial_x \beta(u,T_a,\bar{x}_0,\bar{y}_{T_a}) dW^{\mathbb{Q}}_u \right)
 \end{align*}
-With $\beta(u,T_a,x,y) = \exp\left(-\int_{u}^{T_a}k_u du\right) \partial_x \eta(u,x,y)$.
-Therefore, if we use the last equalities, we get the next approximation of $\mathbb{E}_s^{T_p}\left(D_s x_{T_a}\right)$
+With $\beta(u,T_a,x,y) = \exp\left(-\int_{u}^{T_a}k_u^{\prime} du^{\prime}\right) \partial_x \eta(u,x,y)$. Therefore, from previous equalities, we have that
 
-\begin{equation}\label{approximation_E_s_x_t}
-\mathbb{E}_s^{T_p}\left(D_s x_{T_a}\right) \approx \eta(s,\bar{x_0(s)},\bar{y}_{s}) \exp\left(-\int_{s}^{T_a}k_u du \right) \exp\left(-\int_{s}^{T_a} \exp\left(-\int_{u}^{T_a}k_u du\right)\partial_x (\bar{\nu}(u,T_a) \bar{\nu}(u,T_p)) du \right).
+\begin{equation}\label{approsimation_E_s_x_t}
+\mathbb{E}_s^{T_p}\left(D_s x_{T_a}\right) \approx \eta(s,\bar{x}_0(s),\bar{y}_s) \exp\left(-\int_{s}^{T_a}k_u du \right) \exp\left(-\int_{s}^{T_a} \exp\left(-\int_{u}^{T_a}k_u du\right)\partial_x (\eta(u, \bar{x}_u, \bar{y}_{u}) \bar{\nu}(u,T_p)) du \right).
 \end{equation}
@@
 Following the same procedure as before, we have that
-\begin{equation}\label{approximation_x_t_a}
-X_{T_a} \approx \bar{X}_{T_a}:= \bar{x}_0  + \int_{0}^{T_a} \exp\left(-\int_{s}^{T_a}k_u du\right) \bar{y}(u) du + \int_{0}^{T_a}  \exp\left(-\int_{s}^{T_a}k_u du \right) \eta(u,\bar{x}(u),\bar{y}(u)) dW_u^{\mathbb{Q}}
-\end{equation}
+\begin{equation*}
+X_{T_a} \approx \bar{X}(T_a):= \bar{x}_0  + \int_{0}^{T_a} \exp\left(-\int_{s}^{T_a}k_u du\right) \bar{y}(u) du + \int_{0}^{T_a}  \exp\left(-\int_{s}^{T_a}k_u du \right) \eta(u,\bar{x}(u),\bar{y}(u)) dW_u^{\mathbb{Q}}
+\end{equation*}
 and therefore (see (\ref{approsimation_E_s_x_t}))
@@
 Now, if we take $\mathbb{E}^{\mathbb{Q}}\left(\cdot\right)$ we get
-\begin{equation}\label{approsimation_spot_E_s_x_t}
+\begin{equation}\label{approximation_spot_E_s_x_t}
 \mathbb{E}^{\mathbb{Q}}_s\left(D_sX_{T_a} \right) \approx \exp\left(-\int_{s}^{T_a}k_u du \right) \eta(s,\bar{x}_0,\bar{y}_{T_a})
@@
 We will use the last equation to get an approximation of the mean and order two moment of $x_t$. We can do the next approximaition of  (\ref{annuity_vol})
-\begin{equation}\label{approximation_o1_vol}
-\sigma_{01}(t,T_a,T_b) \approx \bar{\sigma}_{0,1}(t,T_a,T_b):= \sum_{i=a+1}^{b} w_i \nu(t,T_i)
+\begin{equation}
+\sigma_{01}(t,T_a,T_b) \approx \sum_{i=a+1}^{b} w_i \nu(t,T_i)
 \end{equation}

### 2023-02-02 Latex/paper.tex
# last version paper

@@
 \begin{align*}
-01(t,T_a,T_b) = \sum_{j=1}^{n_f} \delta_{t^{f}_{i-1}, t^{f}_i} P_{ois}(t,t^{f}_{j}) \\
-T_a=T^{E}_0 < T^{E}_i< \cdots < T^{E}_{n_E}=T_b \quad i=0,\cdots,n_E&  \\
-T_a=T^{f}_0 < T^{f}_j< \cdots < T^{f}_{n_f}=T_b \quad j=0,\cdots,n_f&
+01(t,t_a,t_b) = \sum_{j=1}^{n_f} \delta_{t^{f}_{i-1}, t^{f}_i} P_{ois}(t,t^{f}_{j}) \\
+t_a=t^{E}_0 < t^{E}_i< \cdots < t^{E}_{n_E}=t_b \quad i=0,\cdots,n_E&  \\
+t_a=t^{f}_0 < t^{f}_j< \cdots < t^{f}_{n_f}=t_b \quad j=0,\cdots,n_f&
 \end{align*}
@@
 \begin{equation*}
-S^{ois}_{a,b}(t) = \frac{P_{ois}(t,T^{E}_a) - P_{ois}(t,T^{E}_b)}{01(t,T_a,T_b)}. 
+S^{ois}_{a,b}(t) = \frac{P_{ois}(t,T^{E}_a) - P_{ois}(t,T^{E}_b)}{01(t,t_a,t_b)}. 
 \end{equation*}
-Now, we suppose that we have a flow in $T_a < T_p < T_b$ with value $S_{a,b}(T_a)$.
-We know that, $S_{a,b}(T_a)$ is a martingale under the measure $\mathbb{Q}^{01}$, but not under the measure $\mathbb{Q}^{T_p}$.
-Therefore, we we have to take into consideration the effect to compute the expected value of $S_{a,b}(T_a)$ in a measure which is not its natural measure.
+
+\begin{remark}
+We must note that from (\ref{bond_forward})we have that
+\begin{equation*}
+S_{a,b}(t) = S^{ois}_{a,b}(t) + \frac{\sum_{i=1}^{n_E}\delta_{t^{E}_{i-1}, t^{E}_i} \alpha(t,t^{E}_{i-1}, t^{E}_{i}) P_{ois}(t,t^{E}_{i})} {01(t,t_a,t_b)}
+\end{equation*}
+where $ \alpha(t,t^{E}_{i-1}, t^{E}_{i})  = \frac{\frac{H(t,t^{E}_{i-1})}{H(t,t^{E}_{i})} - 1}{\delta_{t^{E}_{i-1}, t^{E}_i}}$.
+How we have a one-factor HJM model, we can suppose that variability of $\alpha(t,t^{E}_{i-1}, t^{E}_{i})$ is low, and therefore it is reasonable to freeze it at time $t=0$.
+Of this way, we have that
+\begin{equation}\label{approximation_basis_swap}
+S_{a,b}(t) \approx S^{ois}_{a,b}(t) + \frac{\sum_{i=1}^{n_E}\delta_{t^{E}_{i-1}, t^{E}_i} \alpha(0,t^{E}_{i-1}, t^{E}_{i}) P_{ois}(0,t^{E}_{i})} {01(0,t_a,t_b)}.
+\end{equation}
+
+\end{remark}
+
+Now, we suppose that we have a flow in $t_a < t_p < t_b$ with value $S_{a,b}(t_a)$.
+We know that, $S_{a,b}(t_a)$ is a martingale under the measure $\mathbb{Q}^{01}$, but not under the measure $\mathbb{Q}^{t_p}$.
+Therefore, we we have to take into consideration the effect to compute the expected value of $S_{a,b}(t_a)$ in a measure which is not its natural measure.
 Then, the convexity adjustment for a CMS is
 \begin{equation}
-CA_{CMS}(T_p) = \mathbb{E}^{T_p}\left(S_{a,b}(T_a)\right) - S_{a,b}(0).
+CA_{CMS}(t_p) = \mathbb{E}^{t_p}\left(S_{a,b}(t_a)\right) - S_{a,b}(0).
 \end{equation} 
@@
 \mathbb{E}^{T_p}\left(S_{a,b}(T_a)\right) &= \frac{1}{M(0,T_p)} \mathbb{E}^{01}\left(S_{a,b}(T_a) M(T_a,T_p)\right) \nonumber \\
-&= \frac{1}{M(0,T_p)} \mathbb{E}^{01}\left(S_{a,b}(T_a) \mathbb{E}^{01}\left( M(T_a,T_p)|S_{a,b}(T_a)\right) \right)
+&= \frac{1}{M(0,T_p)} \mathbb{E}^{01}\left(S_{a,b}(T_a) \mathbb{E}^{01}\left( M(T_a,T_p)|S_{a,b}(T_a)\right) \right) \nonumber\\
+\mathbb{E}^{T_p}\left(S_{a,b}(T_a)\right) &\approx  \frac{1}{M(0,T_p)} \mathbb{E}^{01}\left(S^{ois}_{a,b}(T_a) \mathbb{E}^{01}\left( M(T_a,T_p)|S_{a,b}(T_a)\right) \right) + \frac{\sum_{i=1}^{n_E}\delta_{t^{E}_{i-1}, t^{E}_i} \alpha(0,t^{E}_{i-1}, t^{E}_{i}) P_{ois}(0,t^{E}_{i})} {01(0,t_a,t_b)}
 \end{align}
-where $M(t,T_p)= \frac{P_{ois}(t,T_p)}{01(t,T_a,T_p)}$.
-It is common practice to assume that $M(T_a,T_p)$ is a funtion of the swap rate $S_{a,b}(T_a)$ i.e   $M(T_a,T_p)=f(S_{a,b}(T_a))$.
+with $M(t,T_p)= \frac{P_{ois}(t,T_p)}{01(t,T_a,T_p)}$.
+From te previous expression, we must note that under assumption of not stochastic basis, we must to compute the convexity adjustment for the OIS swap rate.
+Another, complicated point, is the expected value
+$$
+\mathbb{E}^{01}\left( M(T_a,T_p)|S_{a,b}(T_a)\right).
+$$
+In order to reduce this complexity, it is a common practice to assume that $M(T_a,T_p)$ is a funtion of the swap rate $S_{a,b}(T_a)$ i.e   $M(T_a,T_p)=f(S_{a,b}(T_a))$, of this way the last expected value is trivial.
 The function $f(\cdot)$ is known as mapping function, and there is a vast literatura about how to choose it (see Piterbarg Volumen III, Hagan paper convexity withour replication).
 We will, try to do an approach, without to specify any mapping function.
-
-where $M(t,T_p)= \frac{P_{ois}(t,T_p)}{01(t,T_a,T_p)}$. Now, if we apply Clark-Ocone formula to $M(T_a,T_p)$ we get that
+If we apply Clark-Ocone formula to $M(T_a,T_p)$ we get that
 \begin{equation} \label{clark_ocone_swap_m}
@@
 \begin{align}\label{cms_first_order_convexity}
-\mathbb{E}^{T_p}\left(S_{a,b}(T_a)\right) =& S_{a,b}(0) + \frac{1}{M(0,T_p)} \mathbb{E}^{01}\left( S_a,b(T_a) \int_{0}^{T_a} \mathbb{E}^{0,1}_s\left(D_sX_{T_a}\partial_x M(T_a,T_p)  \right) dW^{0,1}_s   \right) \nonumber \\
-=&  S_{a,b}(0) + \frac{1}{M(0,T_p)} \mathbb{E}^{01}\left(\int_{0}^{T_a} D_s X_{T_a} \partial_x S_{a,b}(T_a) \mathbb{E}^{0,1}_s\left(D_sX_{T_a}\partial_x M(T_a,T_p)  \right) ds   \right) \nonumber \\
-\approx&  S_{a,b}(0) + \frac{\partial_x S_{a,b}(T_a, \bar{x}_0(T_a),\bar{y}(T_a))\partial_x M(T_a,T_p, \bar{x}_0(T_a),\bar{y}(T_a))}{M(0,T_p)} \mathbb{E}^{0,1}\left( \int_{0}^{T_a} \left(\mathbb{E}_s^{0,1}\left( D_s x_{T_a}\right)\right)^{2} ds  \right)
+\mathbb{E}^{T_p}\left(S_{a,b}(T_a)\right) =& S^{ois}_{a,b}(0) + \frac{1}{M(0,T_p)} \mathbb{E}^{01}\left( S^{ois}_a,b(T_a) \int_{0}^{T_a} \mathbb{E}^{0,1}_s\left(D_sX_{T_a}\partial_x M(T_a,T_p)  \right) dW^{0,1}_s   \right) \nonumber \\
+=&  S^{ois}_{a,b}(0) + \frac{1}{M(0,T_p)} \mathbb{E}^{01}\left(\int_{0}^{T_a} D_s X_{T_a} \partial_x S_{a,b}(T_a) \mathbb{E}^{0,1}_s\left(D_sX_{T_a}\partial_x M(T_a,T_p)  \right) ds   \right) \nonumber \\
+\approx&  S^{ois}_{a,b}(0) + \frac{\partial_x S^{ois}_{a,b}(T_a, \bar{x}_0(T_a),\bar{y}(T_a))\partial_x M(T_a,T_p, \bar{x}_0(T_a),\bar{y}(T_a))}{M(0,T_p)} \mathbb{E}^{0,1}\left( \int_{0}^{T_a} \left(\mathbb{E}_s^{0,1}\left( D_s x_{T_a}\right)\right)^{2} ds  \right)
 \end{align}
@@
 \begin{example}
-In order to check the accuracy of the last approximation, we will compute with Monte Carlo method the exact value of $\mathbb{E}^{T_p}\left(S_{a,b}(T_a)\right)$ under spot measure $\mathbb{Q}$ i.e we will compute  $\frac{1}{P(0,T_p)}  \mathbb{E}^{\mathbb{Q}}\left(\frac{S_{a,b}(T_a)}{\beta_{T_a}} \right)$.
+In order to check the accuracy of the last approximation, we will compute with Monte Carlo method the exact value of $\mathbb{E}^{T_p}\left(S^{ois}_{a,b}(T_a)\right)$ under spot measure $\mathbb{Q}$ i.e we will compute  $\frac{1}{P(0,T_p)}  \mathbb{E}^{\mathbb{Q}}\left(\frac{S_{a,b}(T_a)}{\beta_{T_a}} \right)$.
 In the case of a Hull-White model, we have that
@@
 \begin{equation*}
-\mathbb{E}^{T_p}\left(S_{a,b}(T_a)\right) \approx  S_{a,b}(0) + \frac{\partial_x S_{a,b}(T_a, \bar{x}_0(T_a),\bar{y}(T_a))\partial_x M(T_a,T_p, \bar{x}_0(T_a),\bar{y}(T_a))}{M(0,T_p)} \frac{\sigma^{2}(1-\exp(-2kT_a))}{2k}.
+\mathbb{E}^{T_p}\left(S_{a,b}(T_a)\right) \approx  S^{ois}_{a,b}(0) + \frac{\partial_x S^{ois}_{a,b}(T_a, \bar{x}_0(T_a),\bar{y}(T_a))\partial_x M(T_a,T_p, \bar{x}_0(T_a),\bar{y}(T_a))}{M(0,T_p)} \frac{\sigma^{2}(1-\exp(-2kT_a))}{2k}.
 \end{equation*}
@@
 \begin{equation*}
-X_{T_a} \approx \bar{X}(T_a):= \bar{x}_0  + \int_{0}^{T_a} \exp\left(-\int_{s}^{T_a}k_u du\right) \bar{y}(u) du + \int_{0}^{T_a}  \exp\left(-\int_{s}^{T_a}k_u du \right) \eta(u,\bar{x}(u),\bar{y}(u)) dW_u^{\mathbb{Q}}
+X_{T_a} \approx \bar{X}(T_a):= \bar{x}_0(T_a)  + \int_{0}^{T_a} \exp\left(-\int_{s}^{T_a}k_u du\right) \bar{y}(u) du + \int_{0}^{T_a}  \exp\left(-\int_{s}^{T_a}k_u du \right) \eta(u,\bar{x}(u),\bar{y}(u)) dW_u^{\mathbb{Q}}
 \end{equation*}
@@
 \begin{equation}
-D_sX_{T_a} \approx  \exp\left(-\int_{s}^{T_a}k_u du \right) \eta(s,\bar{x}_0,\bar{y}_{T_a})\bar{M}(s,T_a)
+D_sX_{T_a} \approx  \exp\left(-\int_{s}^{T_a}k_u du \right) \eta(s,\bar{x}_0(T_a),\bar{y}_{T_a})\bar{M}(s,T_a)
 \end{equation}
@@
 \begin{equation}\label{approximation_spot_E_s_x_t}
-\mathbb{E}^{\mathbb{Q}}_s\left(D_sX_{T_a} \right) \approx \exp\left(-\int_{s}^{T_a}k_u du \right) \eta(s,\bar{x}_0,\bar{y}_{T_a})
+\mathbb{E}^{\mathbb{Q}}_s\left(D_sX_{T_a} \right) \approx \exp\left(-\int_{s}^{T_a}k_u du \right) \eta(s,\bar{x}_0(T_a),\bar{y}_{T_a})
 \end{equation}

### 2023-02-05 Latex/paper.tex
# refactoring of the code and last version of the paper

@@
 
-\affil[1]{CaixaBank,....}
+\affil[1]{CaixaBank, Quantitative Analyst Team, Plaza de Castilla, 3, 28046 Madrid, Spain}
 \affil[2]{Facultat de Matem\`{a}tiques i Inform\`{a}tica, Universitat de Barcelona, \authorcr Gran Via 585, 08007 Barcelona, Spain,\vspace*{3pt}}
@@
 Let us to introduce some notation, we will use it throughout the section.
-We will define the swap rate from $T_a$ to $T_b$ at time $t$
+We will define the swap rate from $t_a$ to $T_b$ at time $t$
 \begin{equation*}
-S_{a,b}(t) = \frac{\sum_{i=1}^{n_E}\delta_{t^{E}_{i-1}, t^{E}_i} L^{E}(t,t^{E}_{i-1}, t^{E}_{i}) P_{ois}(t,t^{E}_{i})}{01(t,T_a,T_b)}
+S_{a,b}(t) = \frac{\sum_{i=1}^{n_E}\delta_{t^{E}_{i-1}, t^{E}_i} L^{E}(t,t^{E}_{i-1}, t^{E}_{i}) P_{ois}(t,t^{E}_{i})}{01(t,t_a,T_b)}
 \end{equation*}
@@
 \begin{align}\label{expected_t_p_cms}
-\mathbb{E}^{T_p}\left(S_{a,b}(T_a)\right) &= \frac{1}{M(0,T_p)} \mathbb{E}^{01}\left(S_{a,b}(T_a) M(T_a,T_p)\right) \nonumber \\
-&= \frac{1}{M(0,T_p)} \mathbb{E}^{01}\left(S_{a,b}(T_a) \mathbb{E}^{01}\left( M(T_a,T_p)|S_{a,b}(T_a)\right) \right) \nonumber\\
-\mathbb{E}^{T_p}\left(S_{a,b}(T_a)\right) &\approx  \frac{1}{M(0,T_p)} \mathbb{E}^{01}\left(S^{ois}_{a,b}(T_a) \mathbb{E}^{01}\left( M(T_a,T_p)|S_{a,b}(T_a)\right) \right) + \frac{\sum_{i=1}^{n_E}\delta_{t^{E}_{i-1}, t^{E}_i} \alpha(0,t^{E}_{i-1}, t^{E}_{i}) P_{ois}(0,t^{E}_{i})} {01(0,t_a,t_b)}
+\mathbb{E}^{t_p}\left(S_{a,b}(t_a)\right) &= \frac{1}{M(0,t_p)} \mathbb{E}^{01}\left(S_{a,b}(t_a) M(t_a,t_p)\right) \nonumber \\
+&= \frac{1}{M(0,t_p)} \mathbb{E}^{01}\left(S_{a,b}(t_a) \mathbb{E}^{01}\left( M(t_a,t_p)|S_{a,b}(t_a)\right) \right) \nonumber\\
+\mathbb{E}^{t_p}\left(S_{a,b}(t_a)\right) &\approx  \frac{1}{M(0,t_p)} \mathbb{E}^{01}\left(S^{ois}_{a,b}(t_a) \mathbb{E}^{01}\left( M(t_a,t_p)|S_{a,b}(t_a)\right) \right) + \frac{\sum_{i=1}^{n_E}\delta_{t^{E}_{i-1}, t^{E}_i} \alpha(0,t^{E}_{i-1}, t^{E}_{i}) P_{ois}(0,t^{E}_{i})} {01(0,t_a,t_b)}
 \end{align}
-with $M(t,T_p)= \frac{P_{ois}(t,T_p)}{01(t,T_a,T_p)}$.
+with $M(t,t_p)= \frac{P_{ois}(t,t_p)}{01(t,t_a,t_p)}$.
 From te previous expression, we must note that under assumption of not stochastic basis, we must to compute the convexity adjustment for the OIS swap rate.
@@
 $$
-\mathbb{E}^{01}\left( M(T_a,T_p)|S_{a,b}(T_a)\right).
+\mathbb{E}^{01}\left( M(t_a,t_p)|S_{a,b}(t_a)\right).
 $$
-In order to reduce this complexity, it is a common practice to assume that $M(T_a,T_p)$ is a funtion of the swap rate $S_{a,b}(T_a)$ i.e   $M(T_a,T_p)=f(S_{a,b}(T_a))$, of this way the last expected value is trivial.
+In order to reduce this complexity, it is a common practice to assume that $M(t_a,t_p)$ is a funtion of the swap rate $S_{a,b}(t_a)$ i.e   $M(t_a,t_p)=f(S_{a,b}(t_a))$, of this way the last expected value is trivial.
 The function $f(\cdot)$ is known as mapping function, and there is a vast literatura about how to choose it (see Piterbarg Volumen III, Hagan paper convexity withour replication).
 We will, try to do an approach, without to specify any mapping function.
-If we apply Clark-Ocone formula to $M(T_a,T_p)$ we get that
+If we apply Clark-Ocone formula to $M(t_a,t_p)$ we get that
 \begin{equation} \label{clark_ocone_swap_m}
-M(T_a,T_p) = M(0,T_p)+ \int_{0}^{T_a} \mathbb{E}_s^{01}\left(D_s M(T_a,T_p)\right) dW^{01}_s
+M(t_a,t_p) = M(0,t_p)+ \int_{0}^{t_a} \mathbb{E}_s^{01}\left(D_s M(t_a,t_p)\right) dW^{01}_s
 \end{equation}
@@
 \begin{align}\label{cms_first_order_convexity}
-\mathbb{E}^{T_p}\left(S_{a,b}(T_a)\right) =& S^{ois}_{a,b}(0) + \frac{1}{M(0,T_p)} \mathbb{E}^{01}\left( S^{ois}_a,b(T_a) \int_{0}^{T_a} \mathbb{E}^{0,1}_s\left(D_sX_{T_a}\partial_x M(T_a,T_p)  \right) dW^{0,1}_s   \right) \nonumber \\
-=&  S^{ois}_{a,b}(0) + \frac{1}{M(0,T_p)} \mathbb{E}^{01}\left(\int_{0}^{T_a} D_s X_{T_a} \partial_x S_{a,b}(T_a) \mathbb{E}^{0,1}_s\left(D_sX_{T_a}\partial_x M(T_a,T_p)  \right) ds   \right) \nonumber \\
-\approx&  S^{ois}_{a,b}(0) + \frac{\partial_x S^{ois}_{a,b}(T_a, \bar{x}_0(T_a),\bar{y}(T_a))\partial_x M(T_a,T_p, \bar{x}_0(T_a),\bar{y}(T_a))}{M(0,T_p)} \mathbb{E}^{0,1}\left( \int_{0}^{T_a} \left(\mathbb{E}_s^{0,1}\left( D_s x_{T_a}\right)\right)^{2} ds  \right)
+\mathbb{E}^{t_p}\left(S_{a,b}(t_a)\right) =& S^{ois}_{a,b}(0) + \frac{1}{M(0,t_p)} \mathbb{E}^{01}\left( S^{ois}_a,b(t_a) \int_{0}^{t_a} \mathbb{E}^{0,1}_s\left(D_sX_{t_a}\partial_x M(t_a,t_p)  \right) dW^{0,1}_s   \right) \nonumber \\
+=&  S^{ois}_{a,b}(0) + \frac{1}{M(0,t_p)} \mathbb{E}^{01}\left(\int_{0}^{t_a} D_s X_{t_a} \partial_x S_{a,b}(t_a) \mathbb{E}^{0,1}_s\left(D_sX_{t_a}\partial_x M(t_a,t_p)  \right) ds   \right) \nonumber \\
+\approx&  S^{ois}_{a,b}(0) + \frac{\partial_x S^{ois}_{a,b}(t_a, \bar{x}_0(t_a),\bar{y}(t_a))\partial_x M(t_a,t_p, \bar{x}_0(t_a),\bar{y}(t_a))}{M(0,t_p)} \mathbb{E}^{0,1}\left( \int_{0}^{t_a} \left(\mathbb{E}_s^{0,1}\left( D_s x_{t_a}\right)\right)^{2} ds  \right)
 \end{align}
 
+\begin{remark}
+We must observe that, if we want to use the last approximation  we must be able to approximate $\mathbb{E}_s^{0,1}\left( D_s x_{t_a}\right)$.
+The simplest case, if when $\eta(t,x_t,y_t) \eta(t)$ as for example happens in the Hull-White model or Ho-Lee model.
+The general case, has been treated in (\ref{approximation_under_annuity_measeure_d_s}).
+\end{remark}
+
 \begin{example}
-In order to check the accuracy of the last approximation, we will compute with Monte Carlo method the exact value of $\mathbb{E}^{T_p}\left(S^{ois}_{a,b}(T_a)\right)$ under spot measure $\mathbb{Q}$ i.e we will compute  $\frac{1}{P(0,T_p)}  \mathbb{E}^{\mathbb{Q}}\left(\frac{S_{a,b}(T_a)}{\beta_{T_a}} \right)$.
+In order to check the accuracy of the last approximation, we will compute with Monte Carlo method the exact value of $\mathbb{E}^{t_p}\left(S^{ois}_{a,b}(t_a)\right)$ under spot measure $\mathbb{Q}$ i.e we will compute  $\frac{1}{P(0,t_p)}  \mathbb{E}^{\mathbb{Q}}\left(\frac{S_{a,b}(t_a)}{\beta_{t_a}} \right)$.
 In the case of a Hull-White model, we have that
 $$
-D_s x_{T_a} = \sigma \exp(-(T_a - s))
+D_s x_{t_a} = \sigma \exp(-(t_a - s))
 $$
@@
 \begin{equation*}
-\mathbb{E}^{T_p}\left(S_{a,b}(T_a)\right) \approx  S^{ois}_{a,b}(0) + \frac{\partial_x S^{ois}_{a,b}(T_a, \bar{x}_0(T_a),\bar{y}(T_a))\partial_x M(T_a,T_p, \bar{x}_0(T_a),\bar{y}(T_a))}{M(0,T_p)} \frac{\sigma^{2}(1-\exp(-2kT_a))}{2k}.
+\mathbb{E}^{t_p}\left(S_{a,b}(t_a)\right) \approx  S^{ois}_{a,b}(0) + \frac{\partial_x S^{ois}_{a,b}(t_a, \bar{x}_0(t_a),\bar{y}(t_a))\partial_x M(t_a,t_p, \bar{x}_0(t_a),\bar{y}(t_a))}{M(0,t_p)} \frac{\sigma^{2}(1-\exp(-2kt_a))}{2k}.
 \end{equation*}
@@
 \renewcommand{\thesection}{\Alph{section}.\arabic{section}}
-\section{Approximation of $\mathbb{E}_s^{T_p}\left(D_s x_{T_a}\right)$}
+\section{Approximation of $\mathbb{E}_s^{t_p}\left(D_s x_{t_a}\right)$}
 \label{expected_forward_measure_malliavin_derivative_x_t}
@@
 \begin{equation*}
-x_{T_a} = \int_{0}^{T_a} \exp\left(-\int_{s}^{T_a}k_u du\right) y_u du + \int_{0}^{T_a}  \exp\left(-\int_{s}^{T_a}k_u du \right) \eta(u,x_u,y_u) dW_u^{\mathbb{Q}}  
+x_{t_a} = \int_{0}^{t_a} \exp\left(-\int_{s}^{t_a}k_u du\right) y_u du + \int_{0}^{t_a}  \exp\left(-\int_{s}^{t_a}k_u du \right) \eta(u,x_u,y_u) dW_u^{\mathbb{Q}}  
 \end{equation*}
-In order to get an approximation for $D_sX_{T_a}$ we must to avoid the recurrence in the Malliavin derivative of $X_{T_a}$.
+In order to get an approximation for $D_sX_{t_a}$ we must to avoid the recurrence in the Malliavin derivative of $X_{t_a}$.
 Follow, the ideas of Piterbarg Volume II, we can approximate $y_t$ the next way
@@
 \begin{equation}\label{approximation_x_t_a}
-X_{T_a} \approx \bar{X}(T_a):= \bar{x}_0(T_a)  + \int_{0}^{T_a} \exp\left(-\int_{s}^{T_a}k_u du\right) \bar{y}(u) du + \int_{0}^{T_a}  \exp\left(-\int_{s}^{T_a}k_u du \right) \eta(u,\bar{x}(u),\bar{y}(u)) dW_u^{\mathbb{Q}}
+X_{t_a} \approx \bar{X}(t_a):= \bar{x}_0(t_a)  + \int_{0}^{t_a} \exp\left(-\int_{s}^{t_a}k_u du\right) \bar{y}(u) du + \int_{0}^{t_a}  \exp\left(-\int_{s}^{t_a}k_u du \right) \eta(u,\bar{x}(u),\bar{y}(u)) dW_u^{\mathbb{Q}}
 \end{equation}
-With initial condition  $\bar{x}_{0}(T_a)$ is such that $S_{a,b}(T_a,\bar{x}_0(T_a), \bar{y}_{T_a}) = S_{a,b}(0)$ (see Piterbarg Volume II). Now, we must remember that 
+With initial condition  $\bar{x}_{0}(t_a)$ is such that $S_{a,b}(t_a,\bar{x}_0(t_a), \bar{y}_{t_a}) = S_{a,b}(0)$ (see Piterbarg Volume II). Now, we must remember that 
 \begin{equation*}
-dW^{\mathbb{Q}^{T_p}} = dW^{\mathbb{Q}} + \bar{\nu}(t,T_p) dt 
+dW^{\mathbb{Q}^{t_p}} = dW^{\mathbb{Q}} + \bar{\nu}(t,t_p) dt 
 \end{equation*}
-where $\bar{\nu}(t,T_p) = \int_{t}^{T_p} \eta(s,\bar{x}_s,\bar{y}_s) ds $. Then, we have the next approximation of $\bar{x}_{T_a}$ under measure $\mathbb{Q}^{T_p}$
+where $\bar{\nu}(t,t_p) = \int_{t}^{t_p} \eta(s,\bar{x}_s,\bar{y}_s) ds $. Then, we have the next approximation of $\bar{x}_{t_a}$ under measure $\mathbb{Q}^{t_p}$
 \begin{align*}
-X_{T_a} &\approx \bar{x}_0  + \int_{0}^{T_a} \exp\left(-\int_{s}^{T_a}k_u du\right) \bar{y}_s ds - \int_{0}^{T_a} \exp\left(-\int_{s}^{T_a}k_u du\right) \bar{\nu}(s, T_p) \eta(s,\bar{x}_s,\bar{y}_s) ds +  \\
-&+ \int_{0}^{T_a}  \exp\left(-\int_{s}^{T_a}k_u du \right)\eta(s,\bar{x}_s,\bar{y}_s) dW_s^{\mathbb{Q}^{T_p}}  
+X_{t_a} &\approx \bar{x}_0  + \int_{0}^{t_a} \exp\left(-\int_{s}^{t_a}k_u du\right) \bar{y}_s ds - \int_{0}^{t_a} \exp\left(-\int_{s}^{t_a}k_u du\right) \bar{\nu}(s, t_p) \eta(s,\bar{x}_s,\bar{y}_s) ds +  \\
+&+ \int_{0}^{t_a}  \exp\left(-\int_{s}^{t_a}k_u du \right)\eta(s,\bar{x}_s,\bar{y}_s) dW_s^{\mathbb{Q}^{t_p}}  
 \end{align*} 
-Then, if we take $D_s$ on $\bar{X}_{T_a}$ we get that (esto hay que formalizarlo...)
+Then, if we take $D_s$ on $\bar{X}_{t_a}$ we get that (esto hay que formalizarlo...)
 \begin{equation}\label{approximation_D_s_x_t}
-D_sX_{T_a} \approx  \exp\left(-\int_{s}^{T_a}k_u du \right) \eta(s,\bar{x}_0(T_a),\bar{y}(T_a))\bar{M}(s,T_a)
+D_sX_{t_a} \approx  \exp\left(-\int_{s}^{t_a}k_u du \right) \eta(s,\bar{x}_0(t_a),\bar{y}(t_a))\bar{M}(s,t_a)
 \end{equation}
@@
 \begin{align*}
-\bar{M}(s,T_a) &= \exp\left(-\int_{s}^{T_a} \left( \frac{\left(\partial_x \beta(u,T_a,\bar{x}_0,\bar{y}_{T_a})\right)^{2}}{2} - \exp\left(-\int_{u}^{T_a}k_u du\right) \partial_x (\eta(u, \bar{x}_u, \bar{y}_{u}) \bar{\nu}(u,T_p))\right) du \right) \\
-&\cdot\exp\left(\int_{s}^{t_0} \partial_x \beta(u,T_a,\bar{x}_0,\bar{y}_{T_a}) dW^{\mathbb{Q}}_u \right)
+\bar{M}(s,t_a) &= \exp\left(-\int_{s}^{t_a} \left( \frac{\left(\partial_x \beta(u,t_a,\bar{x}_0,\bar{y}_{t_a})\right)^{2}}{2} - \exp\left(-\int_{u}^{t_a}k_u du\right) \partial_x (\eta(u, \bar{x}_u, \bar{y}_{u}) \bar{\nu}(u,t_p))\right) du \right) \\
+&\cdot\exp\left(\int_{s}^{t_0} \partial_x \beta(u,t_a,\bar{x}_0,\bar{y}_{t_a}) dW^{\mathbb{Q}}_u \right)
 \end{align*}
-With $\beta(u,T_a,x,y) = \exp\left(-\int_{u}^{T_a}k_u^{\prime} du^{\prime}\right) \partial_x \eta(u,x,y)$. Therefore, from previous equalities, we have that
+With $\beta(u,t_a,x,y) = \exp\left(-\int_{u}^{t_a}k_u^{\prime} du^{\prime}\right) \partial_x \eta(u,x,y)$. Therefore, from previous equalities, we have that
 
 \begin{equation}\label{approsimation_E_s_x_t}
-\mathbb{E}_s^{T_p}\left(D_s x_{T_a}\right) \approx \eta(s,\bar{x}_0(s),\bar{y}_s) \exp\left(-\int_{s}^{T_a}k_u du \right) \exp\left(-\int_{s}^{T_a} \exp\left(-\int_{u}^{T_a}k_u du\right)\partial_x (\eta(u, \bar{x}_u, \bar{y}_{u}) \bar{\nu}(u,T_p)) du \right).
+\mathbb{E}_s^{t_p}\left(D_s x_{t_a}\right) \approx \eta(s,\bar{x}_0(s),\bar{y}_s) \exp\left(-\int_{s}^{t_a}k_u du \right) \exp\left(-\int_{s}^{t_a} \exp\left(-\int_{u}^{t_a}k_u du\right)\partial_x (\eta(u, \bar{x}_u, \bar{y}_{u}) \bar{\nu}(u,t_p)) du \right).
 \end{equation}
 
-\section{Approximation of $\mathbb{E}_s^{\mathbb{Q}}\left(D_s x_{T_a}\right)$}
+\section{Approximation of $\mathbb{E}_s^{\mathbb{Q}}\left(D_s x_{t_a}\right)$}
 Following the same procedure as before, we have that
 \begin{equation*}
-X_{T_a} \approx \bar{X}(T_a):= \bar{x}_0(T_a)  + \int_{0}^{T_a} \exp\left(-\int_{s}^{T_a}k_u du\right) \bar{y}(u) du + \int_{0}^{T_a}  \exp\left(-\int_{s}^{T_a}k_u du \right) \eta(u,\bar{x}(u),\bar{y}(u)) dW_u^{\mathbb{Q}}
+X_{t_a} \approx \bar{X}(T_a):= \bar{x}_0(t_a)  + \int_{0}^{t_a} \exp\left(-\int_{s}^{t_a}k_u du\right) \bar{y}(u) du + \int_{0}^{t_a}  \exp\left(-\int_{s}^{t_a}k_u du \right) \eta(u,\bar{x}(u),\bar{y}(u)) dW_u^{\mathbb{Q}}
 \end{equation*}
@@
 \begin{equation}
-D_sX_{T_a} \approx  \exp\left(-\int_{s}^{T_a}k_u du \right) \eta(s,\bar{x}_0(T_a),\bar{y}_{T_a})\bar{M}(s,T_a)
+D_sX_{t_a} \approx  \exp\left(-\int_{s}^{t_a}k_u du \right) \eta(s,\bar{x}_0(t_a),\bar{y}_{T_a})\bar{M}(s,t_a)
 \end{equation}
@@
 \begin{equation}\label{approximation_spot_E_s_x_t}
-\mathbb{E}^{\mathbb{Q}}_s\left(D_sX_{T_a} \right) \approx \exp\left(-\int_{s}^{T_a}k_u du \right) \eta(s,\bar{x}_0(T_a),\bar{y}_{T_a})
+\mathbb{E}^{\mathbb{Q}}_s\left(D_sX_{t_a} \right) \approx \exp\left(-\int_{s}^{t_a}k_u du \right) \eta(s,\bar{x}_0(t_a),\bar{y}_{t_a})
 \end{equation}
 
-\section{Approximation of $\mathbb{E}^{01}\left(x_t\right)$}
+\section{Approximation of $\mathbb{E}^{01}\left(x_{t_a}\right)$}
 It is easy to show that the dynamic of the bond under HJM assumption is
@@
 \begin{equation}\label{annuity_spot_dynamic}
-\frac{d01(t,T_a,T_b)}{01(t,T_a,T_b)} = r_t dt - \sigma_{01}(t,T_a,T_b)dW^{\mathbb{Q}}_t
+\frac{d01(t,t_a,t_b)}{01(t,t_a,t_b)} = r_t dt - \sigma_{01}(t,t_a,t_b)dW^{\mathbb{Q}}_t
 \end{equation}
@@
 \begin{equation} \label{annuity_vol}
-\sigma_{01}(t,T_a,T_b) = \frac{\sum_{i=a+1}^{b} \delta_{i-1,i} P(t,T_i) \nu(t,T_i)}{01(t,T_a,T_b)}.
+\sigma_{01}(t,t_a,t_b) = \frac{\sum_{i=a+1}^{b} \delta_{i-1,i} P(t,t_i) \nu(t,t_i)}{01(t,t_a,t_b)}.
 \end{equation}
-From (\ref{annuity_spot_dynamic}) and using the Girsanov's theorem that 
+From (\ref{annuity_vol}) and since $\frac{P_{ois}(t,T)}{01(t)}$ is a martingale, we have that
 \begin{equation*}
-dW^{01}_t = dW^{\mathbb{Q}}_t - \sigma_{01}(t,T_a,T_b)dt. 
+dW^{01}_t = dW^{\mathbb{Q}}_t - \sigma_{01}(t,t_a,t_b)dt. 
 \end{equation*}
-We will use the last equation to get an approximation of the mean and order two moment of $x_t$. We can do the next approximaition of  (\ref{annuity_vol})
-\begin{equation}
-\sigma_{01}(t,T_a,T_b) \approx \sum_{i=a+1}^{b} w_i \nu(t,T_i)
+Thwn can do the next approximation of (\ref{annuity_vol})
+\begin{equation} \label{approximation_o1_vol}
+\bar{\sigma}_{01}(t,t_a,t_b) \approx \sum_{i=a+1}^{b} w_i \nu(t,t_i,x_0,y_0)
 \end{equation}
-with $w_i=\frac{\delta_{i-1,i} P(0,T_i)}{01(0,T_a,T_b)}$. Now, if we use (\ref{short_rate_cheyette}) and the last approximation we have that
+with $w_i=\frac{\delta_{i-1,i} P(0,T_i)}{01(0,t_a,t_b)}$. Now, if we use (\ref{short_rate_cheyette}) and the previous approximation we have that
 \begin{align}
-x_t &\approx \bar{x}_0  + \int_{0}^{t} \exp\left(-\int_{s}^{t}k_u du\right) \bar{y}(u) du + \int_{0}^{t}  \exp\left(-\int_{s}^{t}k_u du \right) \eta(u,\bar{x}(u),\bar{y}(u)) dW_u^{\mathbb{Q}} \nonumber \\
-&=  \bar{x}_0  + \int_{0}^{t} \exp\left(-\int_{s}^{t}k_u du\right) \bar{y}(u) du + \int_{0}^{t} \exp\left(-\int_{s}^{t}k_u du \right) \eta(u,\bar{x}(u),\bar{y}(u)) \sigma_{01}(u, T_a, T_b) du  + \nonumber \\
-& \int_{0}^{t} \exp\left(-\int_{s}^{t}k_u du \right) \eta(u,\bar{x}(u),\bar{y}(u)) dW_u^{01} 
+x_{t_a} &\approx \bar{x}_0(t_a)  + \int_{0}^{t_a} \exp\left(-\int_{s}^{t}k_u du\right) \bar{y}(u) du + \int_{0}^{t_a}  \exp\left(-\int_{s}^{t_a}k_u du \right) \eta(u,\bar{x}(u),\bar{y}(u)) dW_u^{\mathbb{Q}} \nonumber \\
+&=  \bar{x}_0(t)  + \int_{0}^{t_a} \exp\left(-\int_{s}^{t_a}k_u du\right) \bar{y}(u) du + \int_{0}^{t_a} \exp\left(-\int_{s}^{t_A}k_u du \right) \eta(u,\bar{x}(u),\bar{y}(u)) \bar{\sigma}_{01}(u, T_a, T_b) du  + \nonumber \\
+& \int_{0}^{t_a} \exp\left(-\int_{s}^{t_a}k_u du \right) \eta(u,\bar{x}(u),\bar{y}(u)) dW_u^{01} 
 \end{align}
@@
 \begin{align}
-\mathbb{E}^{01}\left(x_t\right) &\approx \bar{x}_0  + \int_{0}^{t} \exp\left(-\int_{s}^{t}k_u du\right) \bar{y}(u) du \nonumber \\ 
-+ &\int_{0}^{t} \exp\left(-\int_{s}^{t}k_u du \right) \eta(u,\bar{x}(u),\bar{y}(u)) \sigma_{01}(u, T_a, T_b) du
+\mathbb{E}^{01}\left(x_t\right) &\approx \bar{x}_0(t_a)  + \int_{0}^{t_a} \exp\left(-\int_{s}^{t_a}k_u du\right) \bar{y}(u) du \nonumber \\ 
++ &\int_{0}^{t_a} \exp\left(-\int_{s}^{t_a}k_u du \right) \eta(u,\bar{x}(u),\bar{y}(u)) \bar{\sigma}_{01}(u, t_a, t_b) du
 \end{align}
 
-\section{Approximation of $\mathbb{E}^{01}\left(D_s x_{T_a} \right)$}
-Let us to remember that $\nu(t,T_i)=h(t,x_t,y_t) \frac{G(t,T_i)}{\beta_{t,k}}$ with  $\beta_{t,k} = \exp\left(\int_{0}^{t}k(u)\right)$. Then, we can do the next approximation 
+\section{Approximation of $\mathbb{E}^{01}\left(D_s x_{t_a} \right)$}\label{approximation_under_annuity_measeure_d_s}
+Let us to remember that $\nu(t,t_i)=h(t,x_t,y_t) \frac{G(t,t_i)}{\beta_{t,k}}$ with  $\beta_{t,k} = \exp\left(\int_{0}^{t}k(u)\right)$. Then, we can do the next approximation 
 $$
-\nu(t,T_i) \approx \nu(t,T_i, \bar{x}_t, \bar{y}_t),
+\nu(t,t_i) \approx \nu(t,t_i, \bar{x}_t, \bar{y}_t),
 $$ 
@@
 \begin{equation*}
-D_s \nu(t,T_i) \approx  \partial_x \nu(t,T_i, \bar{x}_t, \bar{y}_t) D_s \bar{x}_t  \frac{G(t,T_i)}{\beta_{t,k}}
+D_s \nu(t,T_i) \approx  \partial_x \nu(t,T_i, \bar{x}_t, \bar{y}_t) D_s \bar{x}_t  \frac{G(t,t_i)}{\beta_{t,k}}
 \end{equation*}
@@
 \begin{equation}
-D_s \sigma_{0,1}(t,T_a,T_b) \approx  D_s \bar{x}_t \mu(t,T_a,T_b)
+D_s \sigma_{0,1}(t,t_a,t_b) \approx  D_s \bar{x}_t \mu(t,t_a,t_b)
 \end{equation}
-Where 
+where 
 $$
-\mu(t,T_a,T_b) =  \sum_{i=a+1}^{b} w_i \partial_x \nu(t,T_i, \bar{x}_t, \bar{y}_t) \frac{G(t,T_i)}{\beta_{t,k}}.
+\mu(t,T_a,T_b) =  \sum_{i=a+1}^{b} w_i \partial_x \nu(t,t_i, \bar{x}_t, \bar{y}_t) \frac{G(t,t_i)}{\beta_{t,k}}.
 $$
-
 Now, if we use the last approximation and (\ref{approximation_o1_vol}) in (\ref{approximation_x_t_a}) together with the Girsanov's theorem, we have that
 \begin{align*}
-\bar{x}_{T_a} &\approx  \bar{x}_0  + \int_{0}^{T_a} \exp\left(-\int_{s}^{T_a}k_u du\right) \bar{y}(u) du + \int_{0}^{T_a} \exp\left(-\int_{s}^{T_a}k_u du\right) \bar{\sigma}_{01}(u,T_a,T_b) du \nonumber \\\
-&+  \int_{0}^{T_a}  \exp\left(-\int_{s}^{T_a}k_u du \right) \eta(u,\bar{x}(u),\bar{y}(u)) dW_u^{\mathbb{Q}^{01}}
+\bar{x}_{T_a} &\approx  \bar{x}_0(t_a)  + \int_{0}^{t_a} \exp\left(-\int_{s}^{t_a}k_u du\right) \bar{y}(u) du + \int_{0}^{t_a} \exp\left(-\int_{s}^{t_a}k_u du\right) \bar{\sigma}_{01}(u,t_a,t_b) du \nonumber \\\
+&+  \int_{0}^{t_a}  \exp\left(-\int_{s}^{t_a}k_u du \right) \eta(u,\bar{x}(u),\bar{y}(u)) dW_u^{\mathbb{Q}^{01}}.
 \end{align*}
@@
 \begin{equation*}
-D_s \bar{x}_{T_a} \approx  \exp\left(-\int_{s}^{T_a}k_u du \right) \eta(s,\bar{x}_0,\bar{y}_{T_a})\bar{M}^{01}(s,T_a)
+D_s \bar{x}_{t_a} \approx  \exp\left(-\int_{s}^{t_a}k_u du \right) \eta(s,\bar{x}_0,\bar{y}_{t_a})\bar{M}^{01}(s,t_a)
 \end{equation*}
@@
 \begin{align*}
-\bar{M}^{01}(s,T_a) &= \exp\left(-\int_{s}^{T_a} \left(\frac{\left(\partial_x \beta(u,T_a,\bar{x}_0,\bar{y}_{T_a})\right)^{2}}{2} + \exp\left(-\int_{u}^{T_a}k_u du\right)\eta(u,\bar{x}(u),\bar{y}(u) \mu(u,T_a,T_b) du \right)\right) \\
-&\cdot\exp\left(\int_{s}^{T_a} \partial_x \beta(u,T_a,\bar{x}_0,\bar{y}_{T_a}) dW^{\mathbb{Q}^{01}}_u \right)
+\bar{M}^{01}(s,t_a) &= \exp\left(-\int_{s}^{t_a} \left(\frac{\left(\partial_x \beta(u,T_a,\bar{x}_0,\bar{y}_{t_a})\right)^{2}}{2} + \exp\left(-\int_{u}^{t_a}k_u du\right)\eta(u,\bar{x}(u),\bar{y}(u) \mu(u,t_a,t_b) du \right)\right) \\
+&\exp\left(\int_{s}^{t_a} \partial_x \beta(u,t_a,\bar{x}_0,\bar{y}_{t_a}) dW^{\mathbb{Q}^{01}}_u \right)
 \end{align*}
-with $\beta(u,T_a,x,y) = \exp\left(-\int_{u}^{T_a}k_u du\right) \partial_x \eta(u,x,y)$. Then
+and $\beta(u,t_a,x,y) = \exp\left(-\int_{u}^{t_a}k_u du\right) \partial_x \eta(u,x,y)$. Therefore
 
 \begin{equation}\label{approximation_E_01_s_x_t}
-\mathbb{E}^{01}_s\left(D_s x_{T_a}\right) \approx \eta(s,\bar{x_0(s)},\bar{y}_{s}) \exp\left(-\int_{s}^{T_a}k_u du \right) \exp\left(-\int_{s}^{T_a} \exp\left(\int_{u}^{T_a}k_u du\right)\eta(u,\bar{x}(u),\bar{y}(u) \mu(u,T_a,T_b) du \right).
+\mathbb{E}^{01}_s\left(D_s x_{t_a}\right) \approx \eta(s,\bar{x_0(s)},\bar{y}_{s}) \exp\left(-\int_{s}^{t_a}k_u du \right) \exp\left(-\int_{s}^{t_a} \exp\left(\int_{u}^{t_a}k_u du\right)\eta(u,\bar{x}(u),\bar{y}(u) \mu(u,t_a,t_b) du \right).
 \end{equation}

### 2023-02-05 ConvexityAdjustment-Lib/ConvexityAdjustment-Lib/HullWhite/HullWhite.cs

@@ -1,10 +1,9 @@
 ﻿using ql = QLNet;
 using LA = MathNet.Numerics.LinearAlgebra;    
 
-namespace ConvexityAdjustment_Lib
+namespace ConvexityAdjustment_Lib.HullWhite
 {
-    // ql.HullWhite model, ql.Date valueDate, ql.Schedule schedule, 
-    // ql.DayCounter dcCurve, ql.DayCounter dcSwap, double x
+   
     public class FSolverX0HullWHite: ql.ISolver1d
     {
         #region attributes
@@ -33,21 +32,19 @@ namespace ConvexityAdjustment_Lib
         public override double value(double v)
         {
             double deltaTime = _dcCurve.yearFraction(_valueDate, _schedule.dates()[0]);
-            double f0t = _model.termStructure().link.forwardRate(deltaTime, deltaTime, ql.Compounding.Continuous,
+            double f0T = _model.termStructure().link.forwardRate(deltaTime, deltaTime, ql.Compounding.Continuous,
                 ql.Frequency.NoFrequency, true).rate();
-            var annuity = _model.GetAnnuity(_schedule.dates()[0], _schedule.dates()[0], v + f0t, _schedule, _dcCurve, _dcSwap);
+            var annuity = _model.GetAnnuity(_schedule.dates()[0], _schedule.dates()[0], v + f0T, _schedule, _dcCurve, _dcSwap);
             
             // times
             var dta = _dcCurve.yearFraction(_valueDate, _schedule.dates()[0]);
             var dtb = _dcCurve.yearFraction(_valueDate, _schedule.dates()[_schedule.Count - 1]);
 
-            var dfTaTb = _model.discountBond(dta, dtb, v + f0t);
+            var dfTaTb = _model.discountBond(dta, dtb, v + f0T);
             return (1.0 - dfTaTb) / annuity.Item1 - _swapRate;
            
         }
     }
-
-
 
     public static class HullWhite
     {
@@ -127,9 +124,9 @@ namespace ConvexityAdjustment_Lib
             double i2 = m * (b2 + Math.Exp(-2.0 * k * t2) * delta12 - 2.0 * beta(t1+t2, 2.0*t2, k));
 
             var r01 = convexityOis(curve, k, sigma, t1, t2);
-            var logR01 = Math.Log(1.0 + delta12 * r01) / delta12;
+            // var logR01 = Math.Log(1.0 + delta12 * r01) / delta12;
             
[…]

### 2023-02-05 ConvexityAdjustment-Lib/ConvexityAdjustment-Lib/HullWhite/Sampling.cs

@@ -1,0 +1,182 @@
+﻿using ql = QLNet;
+
+namespace ConvexityAdjustment_Lib.HullWhite;
+
+public static class Sampling
+{
+    public static double[] getLiborPaths(ql.HullWhite model, 
+        ql.Date t0, 
+        ql.Date ta, 
+        ql.Date tb, 
+        ql.DayCounter dc, 
+        ulong seed, 
+        int numberOfPaths)
+    {
+        // path vector
+        double[] paths = new double[numberOfPaths];
+        
+        // yearfracs
+        double dT0Ta = dc.yearFraction(t0, ta);
+        double dT0Tb = dc.yearFraction(t0, tb);
+        double dTaTb = dc.yearFraction(ta, tb);
+
+        double sqrtdT0Ta = Math.Sqrt(dT0Ta);
+        
+        var rsg = (ql.InverseCumulativeRsg<ql.RandomSequenceGenerator<ql.MersenneTwisterUniformRng>, 
+                ql.InverseCumulativeNormal>) new ql.PseudoRandom().make_sequence_generator(numberOfPaths, seed);
+        
+        // mean, variance, ...
+        var stdLibor = model.sigma() * HullWhite.beta(dT0Ta, dT0Tb, model.a());
+        
+        var sample = rsg.nextSequence();
+        var zSampleValue = sample.value;
+        
+        // Initial z0
+        double f0T = model.termStructure().currentLink().forwardRate(dT0Ta, dT0Tb, ql.Compounding.Continuous, ql.Frequency.NoFrequency).rate();
+        var z0Delta = 1.0 + dTaTb * f0T;
+
+        for (int i = 0; i < numberOfPaths; i++)
+        {
+            var ztDelta = z0Delta * Math.Exp(-0.5 * stdLibor * stdLibor * dT0Ta + stdLibor * sqrtdT0Ta * zSampleValue[i]);
+            paths[i] = (ztDelta - 1.0) / dTaTb;
+        }
+
+        return paths;
+
+    }
+
+    public static double[] getRtPathSpotMeasure(ql.HullWhite model,
+        double t,
+        ulong seed,
+        int numberOfPaths)
+    {
+        // path vector
+        double[] paths = new double[numberOfPaths];
+        
+        // parameters
+        double sigma = model.sigma();
+        double k = model.a();
+        double betaT = HullWhite.beta(0.0, t, k);
+
+        // y_t and f0t
[…]

### 2023-02-05 ConvexityAdjustment-Lib/ConvexityAdjustmentUnitTests/CmsConvexity.cs

@@ -1,3 +1,4 @@
+using ConvexityAdjustment_Lib.HullWhite;
 using NUnit.Framework;
 using ql = QLNet;
 
@@ -40,16 +41,16 @@ namespace ConvexityAdjusmentUnitTests
             List<ql.Date> datesToCompute = new List<ql.Date>{calendar.advance(startDate, periodToCompute)};
             List<double> deltaTimes = new List<double>{dc.yearFraction(startDate, datesToCompute[0])};
             List<double> f0ts = new List<double>{discountCurve.link.forwardRate(deltaTimes[0], deltaTimes[0], ql.Compounding.Simple, ql.Frequency.NoFrequency).rate()};
-            List<double> hjmAdjustment = new List<double>{ConvexityAdjustment_Lib.HullWhite.hjmAdjustment(deltaTimes[0], k, sigma)};
-            var drift = new List<double>{ConvexityAdjustment_Lib.HullWhite.forwardMeasureAdjustment(deltaTimes[0], k, sigma)};
+            List<double> hjmAdjustment = new List<double>{HullWhite.hjmAdjustment(deltaTimes[0], k, sigma)};
+            var drift = new List<double>{HullWhite.forwardMeasureAdjustment(deltaTimes[0], k, sigma)};
             
             for (int i = 1; i < numberOftimes; i++)
             {
                 datesToCompute.Add(calendar.advance(datesToCompute[i-1], periodToCompute));
                 deltaTimes.Add(dc.yearFraction(startDate, datesToCompute[i]));
                 f0ts.Add(discountCurve.link.forwardRate(deltaTimes[i], deltaTimes[i], ql.Compounding.Simple, ql.Frequency.NoFrequency).rate());
-                hjmAdjustment.Add(ConvexityAdjustment_Lib.HullWhite.hjmAdjustment(deltaTimes[i], k, sigma));
-                drift.Add(ConvexityAdjustment_Lib.HullWhite.forwardMeasureAdjustment(deltaTimes[i], k, sigma));
+                hjmAdjustment.Add(HullWhite.hjmAdjustment(deltaTimes[i], k, sigma));
+                drift.Add(HullWhite.forwardMeasureAdjustment(deltaTimes[i], k, sigma));
             }
             
             // MC
@@ -195,7 +196,7 @@ namespace ConvexityAdjusmentUnitTests
                 var errorRi = rtaMc * discountCurve.link.discount(datesToCompute[j]) -  swapRates[j];
                 
[…]

### 2023-02-05 ConvexityAdjustment-Lib/ConvexityAdjustmentUnitTests/CmsConvexityNewApproach.cs

@@ -1,4 +1,5 @@
-﻿using NUnit.Framework;
+﻿using ConvexityAdjustment_Lib.HullWhite;
+using NUnit.Framework;
 using ql = QLNet;
 
 namespace ConvexityAdjusmentUnitTests
@@ -169,7 +170,7 @@ namespace ConvexityAdjusmentUnitTests
                     .withFloatingLegRule(ql.DateGeneration.Rule.Forward)
                     .value();
 
-                var X0Root = ConvexityAdjustment_Lib.HullWhite.GetX0(model, startDate, swap.floatingSchedule(),
+                var X0Root = HullWhite.getX0(model, startDate, swap.floatingSchedule(),
                     discountCurve.link.dayCounter(), swap.fixedDayCount(), swapRates[j]);
 
                 var annuityTa = model.GetAnnuity(startDate, datesToCompute[j], X0Root + f0ts[j], swap.fixedSchedule(),
@@ -190,11 +191,11 @@ namespace ConvexityAdjusmentUnitTests
                 var ratioDf = 1.0 / discountCurve.link.discount(tP);
                 
                 // Moments to simulate
-                var varRt = ConvexityAdjustment_Lib.HullWhite.GetVarianceRt(deltaTimes[j], k, sigma);
-                var varIt = ConvexityAdjustment_Lib.HullWhite.GetVarianceIt(deltaTimes[j], k, sigma);
-                var covRtIt = ConvexityAdjustment_Lib.HullWhite.GetCovarianceRtIt(deltaTimes[j], deltaTimes[j], k, sigma);
-                var driftRt = ConvexityAdjustment_Lib.HullWhite.hjmAdjustment(deltaTimes[j], k, sigma);
-                var driftIt = ConvexityAdjustment_Lib.HullWhite.GetDriftIt(deltaTimes[j], k, sigma);
+                var varRt = HullWhite.getVarianceRt(deltaTimes[j], k, sigma);
+                var varIt = HullWhite.getVarianceIt(deltaTimes[j], k, sigma);
+                var covRtIt = HullWhite.getCovarianceRtIt(deltaTimes[j], deltaTimes[j], k, sigma);
+                var driftRt = HullWhite.hjmAdjustment(deltaTimes[j], k, sigma);
+                var driftIt = HullWhite.getDriftIt(deltaTimes[j], k, sigma);
                 var rho = covRtIt / Math.Sqrt(varIt * varRt);
[…]

### 2023-02-05 ConvexityAdjustment-Lib/ConvexityAdjustmentUnitTests/FraInArrears.cs

@@ -1,4 +1,5 @@
-﻿using NUnit.Framework;
+﻿using ConvexityAdjustment_Lib.HullWhite;
+using NUnit.Framework;
 using ql = QLNet;
 
 namespace ConvexityAdjusmentUnitTests
@@ -79,7 +80,7 @@ namespace ConvexityAdjusmentUnitTests
                     var path = sample.value;
                     
                     // sampling Libor
-                    var stdLibor = sigma * ConvexityAdjustment_Lib.HullWhite.beta(delta01, delta02, k);
+                    var stdLibor = sigma * HullWhite.beta(delta01, delta02, k);
                     
                     // Dynamic included forward measure adjustment
                     var ztDelta = z0Delta * Math.Exp(-0.5 * stdLibor * stdLibor * delta01 + stdLibor * Math.Sqrt(delta01) * path[0]);
@@ -99,7 +100,7 @@ namespace ConvexityAdjusmentUnitTests
                 var convexityMc = mcFraInArrears - curve.currentLink()
                     .forwardRate(delta01, delta02, ql.Compounding.Continuous, ql.Frequency.NoFrequency).rate();
                 var convexityMalliavin =
-                    ConvexityAdjustment_Lib.HullWhite.convexityFraInArrears(curve, k, sigma, delta01, delta02, 0.0);
+                    HullWhite.convexityFraInArrears(curve, k, sigma, delta01, delta02, 0.0);
                 
                 // outputs
                 t0s.Add(delta01);

### 2023-02-05 ConvexityAdjustment-Lib/ConvexityAdjustmentUnitTests/FraVsFuturesTests.cs

@@ -1,3 +1,4 @@
+using ConvexityAdjustment_Lib.HullWhite;
 using NUnit.Framework;
 using ql = QLNet;
 
@@ -93,7 +94,7 @@ namespace ConvexityAdjusmentUnitTests
                 var convexityMc = mcFuturePrice - curve.currentLink()
                     .forwardRate(delta01, delta02, ql.Compounding.Simple, ql.Frequency.NoFrequency).rate() - spreadBasis;
                 var convexityMalliavin =
-                    ConvexityAdjustment_Lib.HullWhite.convexityFuture(curve, k, sigma, delta00, delta01, delta02, spreadBasis);
+                    HullWhite.convexityFuture(curve, k, sigma, delta00, delta01, delta02, spreadBasis);
                 
                 // outputs
                 t0s.Add(delta00);

### 2023-02-05 ConvexityAdjustment-Lib/ConvexityAdjustmentUnitTests/SofrCovexity.cs

@@ -1,4 +1,5 @@
 ﻿using ConvexityAdjustment_Lib;
+using ConvexityAdjustment_Lib.HullWhite;
 using ql = QLNet;
 using NUnit.Framework;
 

### 2023-02-12 Latex/paper.tex
I forgot a comma
# last version of the paper and refactoring

@@
 \usepackage[round]{natbib}
+\bibliographystyle{spbasic}
 \bibpunct[, ]{(}{)}{;}{a}{}{,}
@@
 
-\affil[1]{CaixaBank, Quantitative Analyst Team, Plaza de Castilla, 3, 28046 Madrid, Spain}
+\affil[1]{CaixaBank, Quantitative Analyst Team, Plaza de Castilla, 3, 28046 Madrid, Spain,}
 \affil[2]{Facultat de Matem\`{a}tiques i Inform\`{a}tica, Universitat de Barcelona, \authorcr Gran Via 585, 08007 Barcelona, Spain,\vspace*{3pt}}
@@
 In Section \ref{sec:Malliavin}, we make an introduction to Malliavin calculus.
-In Section \ref{sec:CA}, In Section \ref{sec:Numerical Results}, In Section \ref{sec:Conclusion}
+In Section \ref{sec:CA}, we compute the convexity adjsustment for several payoffs that are presents as usual way in the interest rate trading desks.
+As well, we do some numerical expresents to check the analytical results obtained.
+To end, in Section \ref{sec:Conclusion} we give the conclusions of the paper and future lines of research to explore.
 
@@
 In this section, we derive the convexity adjustment for different products.
-The advantage of using the Malliavin calculus is that it allows us to derive a general representation formula for the convexity adjustment.
+The advantage of using the Malliavin calculus is that it allows us to derive a general representation formula .
 In order to introduce a general idea of the method.
 Let define a $Z_t = f(x_t)$.
-Now, we suppose that $Z_t$ is martingale under the measure $\mathbb{Q}_1$ and that we want to compute $\mathbb{E}^{\mathbb{Q}_2}\left(Z_T \right)$, where $\mathbb{Q}_2$ is a measure such that $\frac{d\mathbb{Q}_2}{d\mathbb{Q}_1} = \lambda_t$.
-
-Since the convexity adjustment is derived for the Cheyette model, it can be applied to all included models, such as the Hull-White model.
-
+Now, we suppose that $Z_t$ is martingale under the measure $\mathbb{Q}_1$ and that we want to compute $\mathbb{E}^{\mathbb{Q}_2}\left(Z_T \right)$, where $\mathbb{Q}_2$ is a measure such that $dW^{\mathbb{Q}_1}_t = dW^{\mathbb{Q}_2}_t +\lambda_t dt$.
+Then, if we use the Clark-Ocone representation, we have that
+\begin{equation*}
+f(x_t) = \mathbb{E}^{\mathbb{Q}_1}\left(f(x_t)\right) + \int_{0}^{t} \mathbb{E}^{\mathbb{Q}_1}_s\left( f^{\prime}(x_t) D_s x_t  \right) dW^{\mathbb{Q}_1}_s
+\end{equation*}
+Now, if we take $\mathbb{E}^{\mathbb{Q}_2}\left( \cdot \right)$ in the previous expression and we use the Girsanov's theorem, we get that
+\begin{equation}\label{general_convexity}
+\mathbb{E}^{\mathbb{Q}_2}\left( f(x_t) \right) = f(x_0) + \mathbb{E}^{\mathbb{Q}_1} \left(\int_{0}^{t}  \mathbb{E}^{\mathbb{Q}_1}_s\left( f^{\prime}(x_t) D_s x_t  \right) \lambda_s ds \right). 
+\end{equation}
+The second term, is the convexity adjustment to due to change of measure from $\mathbb{Q}_1$ to $\mathbb{Q}_2$.
+The differents choice of $f$, $\mathbb{Q}_1$ and $\mathbb{Q}_2$ will allow us to get an approximation of the convexity adjustment for the different case of interest.
 \subsection{FRAs Vs futures}
@@
 where $\mathbb{Q}$ is the measure associated to the numeraire $B_t=\exp\left(\int_{0}^{t} r_{ois, s} ds \right)$ with $ r_{ois, t}$ the risk free short rate. Using
-\eqref{forward_rate} and \eqref{future}, we can express the convexity adjustment definition as:%From \eqref{forward_rate} and \eqref{future}, we will define the convexity adjustment as
+\eqref{forward_rate} and \eqref{future}, then the convexity adjustment definition is:
 \begin{equation*}
 CA(t, t_0, t_1, t_2) = \hat{L}_{E}(t,t_0, t_1, t_2) - \mathbb{E}_t^{\mathbb{Q}^{t_2}}\left(L_{E}(t_0, t_1, t_2) \right).
-\end{equation*}
-We use the Clark-Ocone formula with a view to obtaining a general representation formula of the convexity adjustment for futures. Applying \eqref{clark-okone} to 
-$L_{E}(t_0,t_1,t_2)$, we obtain
-\begin{equation}
-L_{E}(t_0,t_1,t_2) = \hat{L}_{E}(t,t_0, t_1, t_2) + \int_{0}^{t_0} \mathbb{E}_{s}\left(D_s L_{E}(t_0,t_1,t_2) \right) dW^{\mathbb{Q}}_s.
-\end{equation} 
-Therefore, if we apply $\mathbb{E}^{\mathbb{Q}^{t2}}(\cdot)$ in the last equation, then we get
-\begin{equation*}
-CA(t, t_0, t_1, t_2) = - \mathbb{E}^{\mathbb{Q}^{t2}}\left(\int_{0}^{t_0} \mathbb{E}^{\mathbb{Q}}_{s}\left(D_s L_{E}(t_0,t_1,t_2) \right) dW^{\mathbb{Q}}_s \right).
 \end{equation*}
@@
 \end{equation}
-Therefore, if we apply Girsanov's theorem to switch to measure $\mathbb{Q}^{t_2}$, we get that
+Now, if we use (\ref{general_convexity}) with $f(x_t)=L_{E}(t,t_0, t_1, t_2)$, $\mathbb{Q}_1=\mathbb{Q}$, $\mathbb{Q}_1=\mathbb{Q}^{t_2}$ and $\lambda_t = \nu(t,t_2)$,  we get that
 \begin{equation}\label{ca_general_future}
@@
 where $\Gamma(s,t_0,t_1)= g(s)h(s,x_0,y_0)\int_{\max(s, t_{0})}^{t_1} \exp\left( -\int_{s}^{u} k_{s^{\prime}} ds^{\prime}\right)du$. 
-Since, the Girsanov's theorem (see (\ref{girsanov_spot_forward}))
+Therefore, we have that
 \begin{equation}\label{representation_i_0_t}
-1 + \delta_{t_0,t_1}\mathbb{E}^{\mathbb{Q}}\left(R(t_0,t_1)\right) \approx \exp\left(\mathbb{E}^{\mathbb{Q}}\left(I(t_0,t_1)\right)\right)\exp\left(\int_{t}^{t_1}\frac{ \Gamma^{2}(s,t_0,t_1)}{2} ds\right)
+1 + \delta_{t_0,t_1}\mathbb{E}^{\mathbb{Q}}\left(R(t_0,t_1)\right) \approx \exp\left(\mathbb{E}^{\mathbb{Q}}\left(I(t_0,t_1)\right)\right)\exp\left(-\int_{t}^{t_1}\frac{\Gamma^{2}(s,t_0,t_1)}{2} ds\right)
 \end{equation}
@@
 \begin{equation}\label{convexity_ois_future}
-\mathbb{E}_t^{\mathbb{Q}}\left(R(t_0,t_1)\right) \approx \frac{\exp\left(\mathbb{E}_t^{\mathbb{Q}}\left(I(t_0,t_1)\right)\right)\exp\left(\int_{t}^{t_1}\frac{\Gamma^{2}(s,t_0,t_1)}{2} ds\right) - 1}{\delta_{t_0,t_1}}
+\mathbb{E}_t^{\mathbb{Q}}\left(R(t_0,t_1)\right) \approx \frac{\exp\left(\mathbb{E}_t^{\mathbb{Q}}\left(I(t_0,t_1)\right)\right)\exp\left(-\int_{t}^{t_1}\frac{\Gamma^{2}(s,t_0,t_1)}{2} ds\right) - 1}{\delta_{t_0,t_1}}
 \end{equation}
@@
 \begin{equation}\label{convexity_avg_ois_future}
-\mathbb{E}_t^{\mathbb{Q}}\left(R_{avg}(t_0,t_1)\right) = \frac{\mathbb{E}_t^{\mathbb{Q}}\left(I(t_0,t_1)\right) }{\delta_{t_0,t_1}} \approx \frac{\log\left(1+\delta_{t_0,t_1}  \mathbb{E}_t^{\mathbb{Q}}\left(R(t_0,t_1)\right) \right)}{\delta_{t_0,t_1}} + \frac{\int_{0}^{t_1}  \Gamma^{2}(s,t_0,t_1) ds}{2\delta_{t_0,t_1}}
+\mathbb{E}_t^{\mathbb{Q}}\left(R_{avg}(t_0,t_1)\right) = \frac{\mathbb{E}_t^{\mathbb{Q}}\left(I(t_0,t_1)\right) }{\delta_{t_0,t_1}} \approx \frac{\log\left(1+\delta_{t_0,t_1}  \mathbb{E}_t^{\mathbb{Q}}\left(R(t_0,t_1)\right) \right)}{\delta_{t_0,t_1}} - \frac{\int_{0}^{t_1}  \Gamma^{2}(s,t_0,t_1) ds}{2\delta_{t_0,t_1}}
 \end{equation}
@@
 {
-\begin{equation*}\label{convexity_avg_ois_future}
-\mathbb{E}_t^{\mathbb{Q}}\left(R_{avg}(t_0,t_1)\right) \approx  \mathbb{E}_t^{\mathbb{Q}}\left(R(t_0,t_1)\right) + \frac{\int_{0}^{t_1}\Gamma^{2}(s,t_0,t_1) ds}{2\delta_{t_0,t_1}}.
-\end{equation*}
+\begin{equation}\label{convexity_avg_ois_future}
+\mathbb{E}_t^{\mathbb{Q}}\left(R_{avg}(t_0,t_1)\right) \approx  \mathbb{E}_t^{\mathbb{Q}}\left(R(t_0,t_1)\right) - \frac{\int_{0}^{t_1}\Gamma^{2}(s,t_0,t_1) ds}{2\delta_{t_0,t_1}}.
+\end{equation}
 }}
@@
 &+ \frac{\sigma^{2}}{2k^{2}} \left(\frac{\exp(-2kt_0) - \exp(-2kt_1)}{2k} + \exp(-2kt_1)\delta_{t_0,t_1} - 2\frac{\exp(-k(t_0 + t_1)) - \exp(-kt_1)}{k}  \right)
-\end{align*}
+\end{align*}(we have to review this integral).
 Then, if we substitute the last equalities in (\ref{convexity_ois_future}) we get an approximation for OIS future at $t=0$.
-The next figure, show accuracy of (\ref{convexity_ois_future}) for the particular case of a Hull-White model.
-
-\begin{figure}[h]
-	\begin{center}
+The next figure, show accuracy of (\ref{convexity_ois_future}) and (\ref{convexity_avg_ois_future}) for the particular case of a Hull-White model.
+\begin{figure}
+\begin{subfigure}{.5\textwidth}
+  \centering
   \includegraphics[scale=0.2]{Figures/convexity_ois.jpg}
 		\caption{Convexity Mc Vs Convexity Malliavin}
-	\end{center}
+\end{subfigure}
+\begin{subfigure}{.5\textwidth}
+  \centering
+  \includegraphics[scale=0.2]{Figures/convexity_avg_ois.jpg}
+		\caption{Convexity Avg Mc Vs Convexity Avg Malliavin}
+\end{subfigure}
+\caption{Convexity adjustment for compounding and average OIS}
 \end{figure} 
+\end{example}
 
-\end{example}
+\newpage
 
@@
 
+\section{Conclusions}\label{sec:Conclusion}
+
 \section*{Appendix}
@@
 
+\section{Order of the approximation $\bar{y}_t$}
+Under the assumption of $\eta(t,\cdot,\cdot)$ is Lipschitz and with first derive continuous, we have that
+
+\section{Order of the approximation $\bar{x}_t$}
+
 % TODO: Change bibliographystyle according to the journal style - it should know the online entry, see Matsuda04
-\bibliographystyle{spbasic}
-\bibliography{references/references,references/references-books,references/references-own,references/references-online}
+\bibliography{references/references, references/references-books,references/references-own,references/references-online}
 %\bibliography{references-export}

### 2023-02-12 ConvexityAdjustment-Lib/ConvexityAdjustment-Lib/HullWhite/HullWhite.cs

@@ -113,20 +113,16 @@ namespace ConvexityAdjustment_Lib.HullWhite
         public static double convexityAvgOis(ql.Handle<ql.YieldTermStructure> curve, double k, double sigma, double t1,
             double t2)
         {
-            double b1 = beta(t1, t2, k);
             double b2 = beta(t1, t2, 2.0 * k);
             double delta12 = t2 - t1;
 
-            double df1 = curve.link.discount(t1, true);
-            double df2 = curve.link.discount(t2, true);
             double m = 0.5 * Math.Pow(sigma / k, 2.0);
-            double i1 = m * ( t1 * Math.Exp(- 2.0 * k * t1) + Math.Exp( - 2.0 * k * t2) * t1  - 2.0 * Math.Exp( - k * (t1 + t2)) * t1);
+            double i1 = m * t1 * (Math.Exp(- 2.0 * k * t1) + Math.Exp( - 2.0 * k * t2)  - 2.0 * Math.Exp( - k * (t1 + t2)));
             double i2 = m * (b2 + Math.Exp(-2.0 * k * t2) * delta12 - 2.0 * beta(t1+t2, 2.0*t2, k));
 
             var r01 = convexityOis(curve, k, sigma, t1, t2);
-            // var logR01 = Math.Log(1.0 + delta12 * r01) / delta12;
             
-            return r01 + (i1 + i2);
+            return r01 - (i1 + i2) / (t2 - t1);
         }
 
         public static double convexityCms(ql.Handle<ql.YieldTermStructure> discountCurve,  ql.Date valueDate, ql.Date ta, ql.Date tb, ql.Date tp, double annuity,

### 2023-02-12 ConvexityAdjustment-Lib/ConvexityAdjustment-Lib/HullWhite/Sampling.cs

@@ -4,6 +4,49 @@ namespace ConvexityAdjustment_Lib.HullWhite;
 
 public static class Sampling
 {
+
+    public static double[] getLiborPathsSpotMeasure(ql.HullWhite model, 
+        ql.Date t0, 
+        ql.Date ta, 
+        ql.Date tb, 
+        ql.DayCounter dc, 
+        ulong seed, 
+        int numberOfPaths)
+    {
+        // path vector
+        double[] paths = new double[numberOfPaths];
+        
+        // yearfracs
+        double dT0Ta = dc.yearFraction(t0, ta);
+        double dT0Tb = dc.yearFraction(t0, tb);
+        double dTaTb = dc.yearFraction(ta, tb);
+
+        var rsg = (ql.InverseCumulativeRsg<ql.RandomSequenceGenerator<ql.MersenneTwisterUniformRng>, 
+            ql.InverseCumulativeNormal>) new ql.PseudoRandom().make_sequence_generator(numberOfPaths, seed);
+        
+        // mean, variance, ...
+        var stdXt0 = model.sigma() * Math.Sqrt(HullWhite.beta(0.0, dT0Ta, 2.0 * model.a()));
+        var driftXt0 = HullWhite.hjmAdjustment(dT0Ta, model.a(), model.sigma());
+        
+        var sample = rsg.nextSequence();
+        var zSampleValue = sample.value;
+        
+        double f0T = model.termStructure().currentLink().forwardRate(dT0Ta, dT0Tb, ql.Compounding.Continuous, ql.Frequency.NoFrequency).rate();
+
+        for (int i = 0; i < numberOfPaths; i++)
+        {
+            var rT0 = driftXt0 + f0T + stdXt0 * zSampleValue[i];
+            var dfT0Ta = model.discountBond(dT0Ta, dT0Ta, rT0);
+            var dfT0Tb = model.discountBond(dT0Ta, dT0Tb, rT0);
+
+            paths[i] = (dfT0Ta / dfT0Tb - 1.0) / dTaTb;
+        }
+
+        return paths;
+        
+    }
+
+
     public static double[] getLiborPaths(ql.HullWhite model, 
         ql.Date t0, 
         ql.Date ta, 
@@ -166,7 +209,7 @@ public static class Sampling
         
         double dfT0 = model.termStructure().currentLink().discount(t0, true);
         double dfT1 = model.termStructure().currentLink().discount(t1, true);
[…]

### 2023-02-12 ConvexityAdjustment-Lib/ConvexityAdjustmentUnitTests/CmsConvexity.cs

@@ -1,19 +1,19 @@
-using ConvexityAdjustment_Lib.HullWhite;
-using NUnit.Framework;
+﻿using NUnit.Framework;
+using HullWhite = ConvexityAdjustment_Lib.HullWhite.HullWhite;
 using ql = QLNet;
 
-namespace ConvexityAdjusmentUnitTests
+namespace ConvexityAdjustmentUnitTests
 {
-    public class CmsConvexity
+    public class CmsConvexityNewApproach
     {
         [Test]
-        public void HullWhiteCms()
+        public void hullWhiteCms()
         {
             // settings
             var calendar = new ql.TARGET();
             ql.DayCounter dc = new ql.Actual360();
-            ql.Date startDate =  calendar.adjust(ql.Settings.evaluationDate());
-            
+            ql.Date startDate = calendar.adjust(ql.Settings.evaluationDate());
+
             // Hull-White parameters
             double k = 0.0007;
             double sigma = 0.007;
@@ -23,40 +23,48 @@ namespace ConvexityAdjusmentUnitTests
             double basisSpread = 0.0;
             ql.Quote quoteDiscountRate = new ql.SimpleQuote(discountFlatRate);
             ql.Quote quoteSpread = new ql.SimpleQuote(basisSpread);
-            
-            ql.Handle<ql.YieldTermStructure> discountCurve =  new ql.Handle<ql.YieldTermStructure>(new ql.FlatForward(startDate, quoteDiscountRate, dc));
-            
+
+            ql.Handle<ql.YieldTermStructure> discountCurve =
+                new ql.Handle<ql.YieldTermStructure>(new ql.FlatForward(startDate, quoteDiscountRate, dc));
+
             // Model and process
             ql.OrnsteinUhlenbeckProcess process = new ql.OrnsteinUhlenbeckProcess(k, sigma, 0.0, 0.0);
             ql.HullWhite model = new ql.HullWhite(discountCurve, k, sigma);
-            
+
             // Swap product
             var payPeriod = new ql.Period(ql.Frequency.Annual);
             var tenorSwap = new ql.Period(5, ql.TimeUnit.Years);
 
             // Convexity test
-            var periodToCompute = new ql.Period(5, ql.TimeUnit.Years);
-            int numberOftimes = 1;
+            var periodToCompute = new ql.Period(6, ql.TimeUnit.Months);
+            int numberOfTimes = 60;
 
-            List<ql.Date> datesToCompute = new List<ql.Date>{calendar.advance(startDate, periodToCompute)};
[…]

### 2023-02-12 ConvexityAdjustment-Lib/ConvexityAdjustmentUnitTests/CmsConvexityNewApproach.cs

@@ -1,266 +1,0 @@
-﻿using ConvexityAdjustment_Lib.HullWhite;
-using NUnit.Framework;
-using ql = QLNet;
-
-namespace ConvexityAdjusmentUnitTests
-{
-    public class CmsConvexityNewApproach
-    {
-        [Test]
-        public void HullWhiteCms()
-        {
-            // settings
-            var calendar = new ql.TARGET();
-            ql.DayCounter dc = new ql.Actual360();
-            ql.Date startDate = calendar.adjust(ql.Settings.evaluationDate());
-
-            // Hull-White parameters
-            double k = 0.0007;
-            double sigma = 0.007;
-
-            // Curves
-            double discountFlatRate = 0.015;
-            double basisSpread = 0.0;
-            ql.Quote quoteDiscountRate = new ql.SimpleQuote(discountFlatRate);
-            ql.Quote quoteSpread = new ql.SimpleQuote(basisSpread);
-
-            ql.Handle<ql.YieldTermStructure> discountCurve =
-                new ql.Handle<ql.YieldTermStructure>(new ql.FlatForward(startDate, quoteDiscountRate, dc));
-
-            // Model and process
-            ql.OrnsteinUhlenbeckProcess process = new ql.OrnsteinUhlenbeckProcess(k, sigma, 0.0, 0.0);
-            ql.HullWhite model = new ql.HullWhite(discountCurve, k, sigma);
-
-            // Swap product
-            var payPeriod = new ql.Period(ql.Frequency.Annual);
-            var tenorSwap = new ql.Period(5, ql.TimeUnit.Years);
-
-            // Convexity test
-            var periodToCompute = new ql.Period(6, ql.TimeUnit.Months);
-            int numberOfTimes = 60;
-
-            List<ql.Date> datesToCompute = new List<ql.Date> {calendar.advance(startDate, periodToCompute)};
-            List<double> deltaTimes = new List<double> {dc.yearFraction(startDate, datesToCompute[0])};
-            
-            List<double> f0ts = new List<double>
-            {
-                discountCurve.link
-                    .forwardRate(deltaTimes[0], deltaTimes[0], ql.Compounding.Continuous, ql.Frequency.NoFrequency,true).rate()
-            };
-
-            for (int i = 1; i < numberOfTimes; i++)
-            {
-                // simulation date
-                datesToCompute.Add(calendar.advance(datesToCompute[i - 1], periodToCompute));
-                
-                // year fracction form value date to sampling date
[…]

### 2023-02-12 ConvexityAdjustment-Lib/ConvexityAdjustmentUnitTests/FraInArrears.cs

@@ -2,12 +2,12 @@
 using NUnit.Framework;
 using ql = QLNet;
 
-namespace ConvexityAdjusmentUnitTests
+namespace ConvexityAdjustmentUnitTests
 {
-    public class ConvexityFraInArrears
+    public class ConvexityFraInArrearsNewVersion
     {
         [Test]
-        public void HullWhiteFraInArrears()
+        public void hullWhiteFraInArrearsNewVersion()
         {
             
             // settings
@@ -16,7 +16,6 @@ namespace ConvexityAdjusmentUnitTests
             // Hull-White parameters
             double k = 0.0007;
             double sigma = 0.01;
-            // double spreadBasis = 0.001;
 
             // Curves
             double flatRate = 0.01;
@@ -26,13 +25,11 @@ namespace ConvexityAdjusmentUnitTests
             ql.Handle<ql.YieldTermStructure> curve =  new ql.Handle<ql.YieldTermStructure>(new ql.FlatForward(startDate, quoteRate, dc));
             
             // Model and process
-            ql.OrnsteinUhlenbeckProcess process = new ql.OrnsteinUhlenbeckProcess(k, sigma, 0.0, 0.0);
             ql.HullWhite model = new ql.HullWhite(curve, k, sigma);
             
             // MC
-            int numberOfSimulations = 2000000;
+            int numberOfSimulations = 500000;
             ulong seed = 123545;
-            int timeSteps = 1;
             var numberOfMonths = 240;
 
             List<double> t0s = new List<double>();
@@ -49,54 +46,27 @@ namespace ConvexityAdjusmentUnitTests
                 double delta01 = dc.yearFraction(startDate, t1);
                 double delta02 = dc.yearFraction(startDate, t2);
                 
-                // Initial z0
-                double f0t = curve.currentLink().forwardRate(delta01, delta01, ql.Compounding.Continuous, ql.Frequency.NoFrequency).rate();
-                var z0Delta = 1.0 + (delta02 - delta01) * f0t;
-                
-                // List<double> mandatoryPoints = new List<double> { delta01};
-                double length = dc.yearFraction(startDate, t2);
-                
-                var rsg = (ql.InverseCumulativeRsg<ql.RandomSequenceGenerator<ql.MersenneTwisterUniformRng>, 
-                        ql.InverseCumulativeNormal>)
-                    new ql.PseudoRandom().make_sequence_generator(timeSteps, seed);
-
[…]

### 2023-02-12 ConvexityAdjustment-Lib/ConvexityAdjustmentUnitTests/FraVsFuturesTests.cs

@@ -1,13 +1,14 @@
 using ConvexityAdjustment_Lib.HullWhite;
 using NUnit.Framework;
+using HullWhite = ConvexityAdjustment_Lib.HullWhite.HullWhite;
 using ql = QLNet;
 
-namespace ConvexityAdjusmentUnitTests
+namespace ConvexityAdjustmentUnitTests
 {
     public class ConvexityFutureFras
     {
         [Test]
-        public void HullWhiteFraVsFutureConvexity()
+        public void hullWhiteFraVsFutureConvexity()
         {
             
             // settings
@@ -53,44 +54,47 @@ namespace ConvexityAdjusmentUnitTests
                 double delta01 = dc.yearFraction(startDate, t1);
                 double delta02 = dc.yearFraction(startDate, t2);
 
-                List<double> mandatoryPoints = new List<double> { delta00};
-                double length = dc.yearFraction(startDate, t2);
+                var libors = Sampling.getLiborPaths(model, t0, t1, t2, dc, seed, numberOfSimulations);
                 
-                var rsg = (ql.InverseCumulativeRsg<ql.RandomSequenceGenerator<ql.MersenneTwisterUniformRng>, 
-                        ql.InverseCumulativeNormal>)
-                    new ql.PseudoRandom().make_sequence_generator(timeSteps, seed);
+                // List<double> mandatoryPoints = new List<double> { delta00};
+                // double length = dc.yearFraction(startDate, t2);
+                
+                // var rsg = (ql.InverseCumulativeRsg<ql.RandomSequenceGenerator<ql.MersenneTwisterUniformRng>, 
+                //         ql.InverseCumulativeNormal>)
+                //     new ql.PseudoRandom().make_sequence_generator(timeSteps, seed);
 
-                ql.PathGenerator<ql.IRNG> generator = new ql.PathGenerator<ql.IRNG>(process, length, timeSteps, rsg, true, mandatoryPoints);
-                double f0t = curve.currentLink().forwardRate(delta00, delta00, ql.Compounding.Simple, ql.Frequency.NoFrequency).rate();
-                double expat = (1.0 - Math.Exp(-k * delta00)) / k ;
-                double mt = (sigma * sigma) / (2.0 * k) * (expat - Math.Exp(-k * delta00) * expat); 
+                // ql.PathGenerator<ql.IRNG> generator = new ql.PathGenerator<ql.IRNG>(process, length, timeSteps, rsg, true, mandatoryPoints);
[…]

### 2023-02-12 ConvexityAdjustment-Lib/ConvexityAdjustmentUnitTests/SofrCovexity.cs

@@ -1,23 +1,21 @@
-﻿using ConvexityAdjustment_Lib;
-using ConvexityAdjustment_Lib.HullWhite;
+﻿using NUnit.Framework;
+using HullWhite = ConvexityAdjustment_Lib.HullWhite.HullWhite;
+using HullWhiteSampling = ConvexityAdjustment_Lib.HullWhite.Sampling;
 using ql = QLNet;
-using NUnit.Framework;
 
-namespace ConvexityAdjusmentUnitTests
+namespace ConvexityAdjustmentUnitTests
 {
     public class ConvexityAdjustmentSofr
     {
         [Test]
-        public void HullWhiteSofrConvexity()
+        public void hullWhiteSofrConvexity()
         {
-            
             // settings
             var calendar = new ql.TARGET();
             
             // Hull-White parameters
             double k = 0.0001;
             double sigma = 0.01;
-            // double spreadBasis = 0.001;
 
             // Curves
             double flatRate = 0.01;
@@ -27,15 +25,11 @@ namespace ConvexityAdjusmentUnitTests
             ql.Handle<ql.YieldTermStructure> curve =  new ql.Handle<ql.YieldTermStructure>(new ql.FlatForward(startDate, quoteRate, dc));
             
             // Model and process
-            ql.OrnsteinUhlenbeckProcess process = new ql.OrnsteinUhlenbeckProcess(k, sigma, 0.0, 0.0);
             ql.HullWhite model = new ql.HullWhite(curve, k, sigma);
             
             // MC
             int numberOfSimulations = 2000000;
             ulong seed = 123545;
-            // double deltaTime = 0.01;
-            // int timeSteps = (int)(length / deltaTime);
-            // int timeSteps = 1;
             var numberOfMonths = 240;
 
             List<double> t0s = new List<double>();
@@ -46,55 +40,47 @@ namespace ConvexityAdjusmentUnitTests
 
             for (var j = 1; j < numberOfMonths + 1; j++)
             {
+                
+                
                 // Product
                 var t0 = calendar.advance(startDate, j, ql.TimeUnit.Months);
                 var t1 = calendar.advance(startDate, j, ql.TimeUnit.Months);
                 var t2 = calendar.advance(t1, 12, ql.TimeUnit.Months);
-                 
+                
                 // Delta times
                 double delta00 = dc.yearFraction(startDate, t0);
                 double delta01 = dc.yearFraction(startDate, t1);
                 double delta02 = dc.yearFraction(startDate, t2);
-
[…]

### 2023-02-14 Latex/paper.tex
# las version and fix bugs in ois convexity

@@
 Then from (\ref{representation_i_0_t}) we get that
+
+\fboxsep1em
+\fbox{\parbox{360pt}
+{
 \begin{equation}\label{convexity_avg_ois_future}
 \mathbb{E}_t^{\mathbb{Q}}\left(R_{avg}(t_0,t_1)\right) = \frac{\mathbb{E}_t^{\mathbb{Q}}\left(I(t_0,t_1)\right) }{\delta_{t_0,t_1}} \approx \frac{\log\left(1+\delta_{t_0,t_1}  \mathbb{E}_t^{\mathbb{Q}}\left(R(t_0,t_1)\right) \right)}{\delta_{t_0,t_1}} - \frac{\int_{0}^{t_1}  \Gamma^{2}(s,t_0,t_1) ds}{2\delta_{t_0,t_1}}
-\end{equation}
-The last step, is to use the basic inequality $\log(1+x) \approx x$
-when $x \approx 0$. If we do that, we get the next approximation for $\mathbb{E}^{\mathbb{Q}}\left(R_{avg}(t_0,t_1)\right)$
-
-\fboxsep1em
-\fbox{\parbox{300pt}
-{
-\begin{equation}\label{convexity_avg_ois_future}
-\mathbb{E}_t^{\mathbb{Q}}\left(R_{avg}(t_0,t_1)\right) \approx  \mathbb{E}_t^{\mathbb{Q}}\left(R(t_0,t_1)\right) - \frac{\int_{0}^{t_1}\Gamma^{2}(s,t_0,t_1) ds}{2\delta_{t_0,t_1}}.
 \end{equation}
@@
 \Gamma(s,t_0,t_1) &= \frac{\sigma \exp(-ks)}{k}\left(\exp(-k(\max(s,t_0) - s)) - \exp(-k(t_1-s))\right)\\
-\mathbb{E}^{\mathbb{Q}}\left(I(t_0,t_1)\right)&=-\log\left(\frac{P_{ois}(0,t_1)}{P_{ois}(0,t_0)}\right) + \frac{\sigma^{2}}{2k^{2}}\left(\delta_{t_0,t_1} - 2 \frac{\exp(-kt_0) - \exp(-kt_1)}{k} + \frac{\exp(-2kt_0) - \exp(-2kt_1)}{k}  \right).
+\mathbb{E}^{\mathbb{Q}}\left(I(t_0,t_1)\right)&=-\log\left(\frac{P_{ois}(0,t_1)}{P_{ois}(0,t_0)}\right) + \frac{\sigma^{2}}{2k^{2}}\left(\delta_{t_0,t_1} - 2 \frac{\exp(-kt_0) - \exp(-kt_1)}{k} + \frac{\exp(-2kt_0) - \exp(-2kt_1)}{2k}  \right).
 \end{align*}
@@
 \begin{align*}
-\frac{\int_{0}^{t_1} \Gamma^{2}(s,t_0,t_1) ds}{2} &= \frac{\sigma^{2}}{2k^{2}} \int_{0}^{t_1}  \exp(-2ks)\left(\exp(-k(\max(s,t_0) - s)) - \exp(-k(t_1 - s))\right)^{2} ds \\
-&= \frac{\sigma^{2}}{2k^{2}} \int_{0}^{t_0} \exp(-2ks)\left(\exp(-k(t_0 - s)) - \exp(-k(t_1 - s))\right)^{2} ds\\
-&+ \frac{\sigma^{2}}{2k^{2}} \int_{t_0}^{t_1} \exp(-2ks)\left(1 - \exp(-k\delta_{t_0,t_1})\right)^{2} ds\\
+\frac{\int_{0}^{t_1} \Gamma^{2}(s,t_0,t_1) ds}{2} &= \frac{\sigma^{2}}{2k^2} \int_{0}^{t_1}  \exp(-2ks)\left(\exp(-k(\max(s,t_0) - s)) - \exp(-k(t_1 - s))\right)^{2} ds \\
+&= \frac{\sigma^{2}}{2k^2} \int_{0}^{t_0} \exp(-2ks)\left(\exp(-k(t_0 - s)) - \exp(-k(t_1 - s))\right)^{2} ds\\
+&+ \frac{\sigma^{2}}{2k^2} \int_{t_0}^{t_1} \exp(-2ks)\left(1 - \exp(-k(t_1 - s))\right)^{2} ds\\
 &= \frac{\sigma^{2}t_0}{2k^{2}} \left( \exp(-kt_0) + \exp(-2kt_1) - 2 \exp(-k(t_1+t_0)) \right)\\  
-&+ \frac{\sigma^{2}}{2k^{2}} \left(\frac{\exp(-2kt_0) - \exp(-2kt_1)}{2k} + \exp(-2kt_1)\delta_{t_0,t_1} - 2\frac{\exp(-k(t_0 + t_1)) - \exp(-kt_1)}{k}  \right)
+&+ \frac{\sigma^{2}}{2k^{2}} \left(\frac{\exp(-2kt_0) - \exp(-2kt_1)}{2k}  + \exp(-kt0)t0 - 2 \frac{\exp(-2kt_0) - \exp(-k(t_0 + t_1))}{k}  \right)
 \end{align*}(we have to review this integral).
@@
 The next figure, show accuracy of (\ref{convexity_ois_future}) and (\ref{convexity_avg_ois_future}) for the particular case of a Hull-White model.
+
 \begin{figure}

### 2023-02-14 ConvexityAdjustment-Lib/ConvexityAdjustment-Lib/HullWhite/HullWhite.cs

@@ -104,8 +104,8 @@ namespace ConvexityAdjustment_Lib.HullWhite
             double df2 = curve.link.discount(t2, true);
             double m = 0.5 * Math.Pow(sigma / k, 2.0);
             double expected = -Math.Log(df2 / df1) + m * (delta12 - 2.0 * b1 + b2);
-            double i1 = m * ( t1 * Math.Exp(- 2.0 * k * t1) + Math.Exp( - 2.0 * k * t2) * t1  - 2.0 * Math.Exp( - k * (t1 + t2)) * t1);
-            double i2 = m * (b2 + Math.Exp(-2.0 * k * t2) * delta12 - 2.0 * beta(t1+t2, 2.0*t2, k));
+            double i1 = m * t1 * (Math.Exp(- 2.0 * k * t1) + Math.Exp( - 2.0 * k * t2) - 2.0 * Math.Exp( - k * (t1 + t2)));
+            double i2 = m *(b2 + Math.Exp(-2.0 * k*t2) * delta12 - 2.0 * beta(t1 + t2, 2.0 * t2, k));
 
             return (Math.Exp(expected + i1 + i2) - 1.0) / delta12;
         }
@@ -121,8 +121,9 @@ namespace ConvexityAdjustment_Lib.HullWhite
             double i2 = m * (b2 + Math.Exp(-2.0 * k * t2) * delta12 - 2.0 * beta(t1+t2, 2.0*t2, k));
 
             var r01 = convexityOis(curve, k, sigma, t1, t2);
+            var logR01 = Math.Log(1.0 + delta12 * r01) / delta12;
             
-            return r01 - (i1 + i2) / (t2 - t1);
+            return logR01 - (i1 + i2) / (t2 - t1);
         }
 
         public static double convexityCms(ql.Handle<ql.YieldTermStructure> discountCurve,  ql.Date valueDate, ql.Date ta, ql.Date tb, ql.Date tp, double annuity,
@@ -251,11 +252,9 @@ namespace ConvexityAdjustment_Lib.HullWhite
       
         public static double getExpectedIntegralRt(double k, double sigma, double t0, double t1)
         {
-
             var m = 0.5 * Math.Pow(sigma / k, 2.0);
             var delta = t1 - t0;
             return m * (delta - 2.0 * beta(t0, t1, k) + beta(t0, t1, 2.0 * k));
-
         }
         
         public static double getVarianceIntegralRt(double k, double sigma, double t0, double t1)

### 2023-02-14 ConvexityAdjustment-Lib/ConvexityAdjustment-Lib/HullWhite/Sampling.cs

@@ -1,4 +1,6 @@
 ﻿using ql = QLNet;
+using MathNet.Numerics.Distributions;
+using MathNet.Numerics.Random;
 
 namespace ConvexityAdjustment_Lib.HullWhite;
 
@@ -187,7 +189,7 @@ public static class Sampling
     public static double[,] getIntRtPathSpotMeasure(ql.HullWhite model,
         double t1,
         double t0,
-        ulong seed,
+        int seed,
         int numberOfPaths)
     {
         
@@ -199,24 +201,34 @@ public static class Sampling
         double k = model.a();
         double d01 = t1 - t0;
         
-        // path generator
-        var rsg = (ql.InverseCumulativeRsg<ql.RandomSequenceGenerator<ql.MersenneTwisterUniformRng>, 
-            ql.InverseCumulativeNormal>) new ql.PseudoRandom().make_sequence_generator(numberOfPaths, seed);
+        // random numbers with math.net
+        var rng = new MersenneTwister(seed);
+        double[] zSampleValue = new double[numberOfPaths];
+        Normal.Samples(rng, zSampleValue, 0.0, 1.0);
         
-        var zSampleValue = rsg.nextSequence();
+        
+        // path generator
+        // var rsg = (ql.InverseCumulativeRsg<ql.RandomSequenceGenerator<ql.MersenneTwisterUniformRng>, 
+        //     ql.InverseCumulativeNormal>) new ql.PseudoRandom().make_sequence_generator(numberOfPaths, seed);
+        
+        // var zSampleValue = rsg.nextSequence();
         var mu = HullWhite.getExpectedIntegralRt(k, sigma, t0, t1);
         var std = Math.Sqrt(HullWhite.getVarianceIntegralRt(k, sigma, t0, t1));
         
         double dfT0 = model.termStructure().currentLink().discount(t0, true);
         double dfT1 = model.termStructure().currentLink().discount(t1, true);
         double r0T = -Math.Log(dfT1 / dfT0);
-        
+
+        double meanAux = 0.0;
+        double meanZs = 0.0;
         for (int i = 0; i < numberOfPaths; i++)
         {
-            var it0Tot1 = mu + std * zSampleValue.value[i] + r0T;
+            var it0Tot1 = mu + std * zSampleValue[i] + r0T;
             paths[i,0] = (Math.Exp(it0Tot1) - 1.0) / d01;
             paths[i,1] = it0Tot1 / d01;
-           
[…]

### 2023-02-14 ConvexityAdjustment-Lib/ConvexityAdjustmentUnitTests/CmsConvexity.cs

@@ -4,7 +4,7 @@ using ql = QLNet;
 
 namespace ConvexityAdjustmentUnitTests
 {
-    public class CmsConvexityNewApproach
+    public class CmsConvexity
     {
         [Test]
         public void hullWhiteCms()

### 2023-02-14 ConvexityAdjustment-Lib/ConvexityAdjustmentUnitTests/SofrCovexity.cs

@@ -28,8 +28,8 @@ namespace ConvexityAdjustmentUnitTests
             ql.HullWhite model = new ql.HullWhite(curve, k, sigma);
             
             // MC
-            int numberOfSimulations = 2000000;
-            ulong seed = 123545;
+            int numberOfSimulations = 1000000;
+            int seed = 123545;
             var numberOfMonths = 240;
 
             List<double> t0s = new List<double>();
@@ -40,8 +40,6 @@ namespace ConvexityAdjustmentUnitTests
 
             for (var j = 1; j < numberOfMonths + 1; j++)
             {
-                
-                
                 // Product
                 var t0 = calendar.advance(startDate, j, ql.TimeUnit.Months);
                 var t1 = calendar.advance(startDate, j, ql.TimeUnit.Months);

### 2023-02-21 Latex/paper.tex
# last version
I'm aworking with the convergence order.

@@
 %%\newtheorem{exercise}[theorem]{Exercise} 
-%%\newtheorem{hypothesis}[theorem]{Hypothesis} 
+\newtheorem{hypothesis}[theorem]{Hypothesis} 
 \newtheorem{lemma}[theorem]{Lemma} 
@@
 \end{equation}
-with $g$ a positive time-dependent function and $h$ a non-negative process.
+with $g$ a positive time-dependent function and $h$ a non-negative process. In addition
+\begin{align*}
+\eta_t &= g(t)h(t,x_t,y_t)  \nonumber \\
+k_t &= - \frac{\partial_t g(t)}{g(t)}.
+\end{align*}
+Throught this paper, we assume the following hypotheses on $\eta(t,x,y)$.
+\begin{hypothesis}\label{boundedness_volatility} 
+The process $\eta_t$ is global Lipschitz and differentiable a.s. In addition, we will suppose that
+\begin{align*}
+a1 \leq \eta(t,x,y) \leq a2 \quad \forall (t,x,t) \in \mathbb{R}^{+} \times \mathbb{R} \times \mathbb{R}^{+}. \\
+|\eta(t,x_2,y_2) - \eta(t,x_2,y_2)| \leq C_{x,y}\left(|x_2 - x_1| + |y_2 - y_1| \right) \quad \forall (t,x,t) \in \mathbb{R}^{+} \times \mathbb{R} \times \mathbb{R}^{+} 
+\end{align*}
+\end{hypothesis}
+\begin{hypothesis}\label{boundedness_reversion} 
+The next integrals are finite
+\begin{align*}
+I_{1,k}(0,t) &= \int_{0}^{t} \exp\left(- 2 \int_{s}^{t} k(s^{\prime})ds^{\prime}\right)  ds < \infty \\
+I_{2,k}(0,t) &= \int_{0}^{t} \exp\left(- \int_{s}^{t} k(s^{\prime})ds^{\prime}\right) G(s,t) ds < \infty
+\end{align*}
+\end{hypothesis}
+\begin{remark}
+Notice that the above hypotheses have been chosen for the sake of simplicity, but they can be replaced by adequate integrability conditions.
+\end{remark}
+We must note, that under the hypothesis (\ref{boundedness_volatility}) $\partial_x \eta(t,x,y)$ and $\partial_y \eta(t,x,y)$ are bounded.
 This version of the HJM is also known as the Cheyette model, \cite{Cheyette}.
-It is easy to show (see \cite{Andreasen01}), that in this case (\ref{ois_forward_rate_curve})
+It is easy to show (see \cite{Andreasen01} that
 \begin{equation}
@@
 \end{align*}
-Then with a little bit of algebra and we use Itô formula we can show the next representation formula for $P_{ois}(t,T)$
+Now if we do a little bit of algebra and we use Itô formula we can show the next representation formula for $P_{ois}(t,T)$
 \begin{equation}\label{bond_ois}
@@
 \begin{equation}\label{malliavin_derive_L}
-D_s L_{E}(t_0,t_1,t_2) = \frac{H(t_0,t_1)}{\delta_{t_1,t_2}H(t_0,t_2)}\frac{\left(\partial_{x}P_{ois}(t_0,t_1)P_{ois}(t_0,t_2) - \partial_{x}P_{ois}(t_0,t_2) P_{ois}(t_0,t_1) \right)}{P^{2}_{ois}(t_0,t_2)} D_s x_{t_0}.
+D_s L_{E}(t_0,t_1,t_2) = \frac{H(t_0,t_1)}{\delta_{t_1,t_2}H(t_0,t_2)}\frac{\left(\partial_{x}P_{ois}(t_0,t_1)P_{ois}(t_0,t_2) - \partial_{x}P_{ois}(t_0,t_2) P_{ois}(t_0,t_1) \right)}{P^{2}_{ois}(t_0,t_2)} D_s x_{t_0}
 \end{equation}
@@
 \renewcommand{\thesection}{\Alph{section}.\arabic{section}}
+
+\section{Order of the approximation $\bar{y}_t$}
+Under the assumption of $\eta(t,\cdot,\cdot)$ is global Lipschitz and with first derive continuous, we have that
+\begin{align*}
+|\eta^{2}(t,x_t,y_t) - \eta^{2}(t,x_0,y_0)|&=|\eta(t,x_t,y_t) - \eta(t,x_0,y_0)||\eta(t,x_t,y_t) + \eta(t,x_0,y_0)| \nonumber \\ 
+&\leq C_{x,y}\left(|x_t - x_0| + |y_t - y_0|\right) + 
+\end{align*}
+
+\section{Order of the approximation $\bar{x}_t$}
+
 \section{Approximation of $\mathbb{E}_s^{t_p}\left(D_s x_{t_a}\right)$}
@@
 
-\section{Order of the approximation $\bar{y}_t$}
-Under the assumption of $\eta(t,\cdot,\cdot)$ is Lipschitz and with first derive continuous, we have that
-
-\section{Order of the approximation $\bar{x}_t$}
-
 % TODO: Change bibliographystyle according to the journal style - it should know the online entry, see Matsuda04

### 2023-02-22 Latex/paper.tex
# last version

@@
 \begin{align*}
-a1 \leq \eta(t,x,y) \leq a2 \quad \forall (t,x,t) \in \mathbb{R}^{+} \times \mathbb{R} \times \mathbb{R}^{+}. \\
-|\eta(t,x_2,y_2) - \eta(t,x_2,y_2)| \leq C_{x,y}\left(|x_2 - x_1| + |y_2 - y_1| \right) \quad \forall (t,x,t) \in \mathbb{R}^{+} \times \mathbb{R} \times \mathbb{R}^{+} 
+\alpha_1 \leq \eta(t,x,y) \leq \alpha_2 \quad \forall (t,x,y) \in \mathbb{R}^{+} \times \mathbb{R} \times \mathbb{R}^{+}. \\
+|\eta(t,x_2,y_2) - \eta(t,x_1,y_1)| \leq C_{x,y} \lVert (x_2-x_1,y_2-y_1)\rVert \quad \forall (t,x,y) \in \mathbb{R}^{+} \times \mathbb{R} \times \mathbb{R}^{+} 
 \end{align*}
+with $\lVert \cdot \rVert$ euclidean norm in $\mathbb{R}^{2}$.
 \end{hypothesis}
 \begin{hypothesis}\label{boundedness_reversion} 
-The next integrals are finite
-\begin{align*}
-I_{1,k}(0,t) &= \int_{0}^{t} \exp\left(- 2 \int_{s}^{t} k(s^{\prime})ds^{\prime}\right)  ds < \infty \\
-I_{2,k}(0,t) &= \int_{0}^{t} \exp\left(- \int_{s}^{t} k(s^{\prime})ds^{\prime}\right) G(s,t) ds < \infty
-\end{align*}
+The mean reversion function $k(\cdot)$ is positive a.s.
 \end{hypothesis}
@@
 \begin{align}\label{short_rate_cheyette}
-dx_t &= (-k_t x_t + y_t)dt + \eta_t dW_t^{\mathbb{Q}} \nonumber \\
+dx_t &= (-k_t x_t + y_t)dt + \eta(t,x_t,y_t) dW_t^{\mathbb{Q}} \nonumber \\
 dy_t &= (\eta^{2}_t - 2 k_t y_t) dt ,
@@
 
-\newpage
-
 \section{Conclusions}\label{sec:Conclusion}
@@
 \renewcommand{\thesection}{\Alph{section}.\arabic{section}}
-
-\section{Order of the approximation $\bar{y}_t$}
-Under the assumption of $\eta(t,\cdot,\cdot)$ is global Lipschitz and with first derive continuous, we have that
-\begin{align*}
-|\eta^{2}(t,x_t,y_t) - \eta^{2}(t,x_0,y_0)|&=|\eta(t,x_t,y_t) - \eta(t,x_0,y_0)||\eta(t,x_t,y_t) + \eta(t,x_0,y_0)| \nonumber \\ 
-&\leq C_{x,y}\left(|x_t - x_0| + |y_t - y_0|\right) + 
-\end{align*}
-
-\section{Order of the approximation $\bar{x}_t$}
 
@@
 
+\section{Order of the approximation $\bar{x}_t$}
+From (\ref{short_rate_cheyette}) is easy to show that
+\begin{equation*}
+x_{t_a} = \int_{0}^{t_a} \exp\left(-\int_{u}^{t_a}k_u du^{\prime}\right) G(u,t_a) \eta^{2}(u,x_u,y_u) du + \int_{0}^{t_a}  \exp\left(-\int_{u}^{t_a}k_u^{\prime} du \right) \eta(u,x_u,y_u) dW_u^{\mathbb{Q}}
+\end{equation*}
+Therefore, we have that
+\begin{align*}
+(x_{t_a} - \bar{x}_{t_a})^2 &\leq 2 \left(\int_{0}^{t_a} \exp\left(-\int_{u}^{t_a}k_u^{\prime} du^{\prime}\right) G(u,t_a) (\eta^{2}(u,x_u,y_u) - \eta^{2}(u,x_0,y_0)) du \right)^{2} \\ 
+&+ 2 \left(\int_{0}^{t_a}  \exp\left(-\int_{s}^{t_a}k_u^{\prime} du^{\prime} \right) (\eta(u,x_u,y_u)-\eta(u,\bar{x}_u,\bar{y}_u)) dW_u^{\mathbb{Q}}\right)^{2}
+\end{align*}
+Now, we will bound each integral term. We will call to the first term $(A)$ and the second $(B)$. From the hypothesis (\ref{boundedness_volatility}) we have that 
+\begin{align*}
+(A) &\leq 8 t_a \alpha^{2}_2 C^{2}_{x,y} \int_{0}^{t_a} \exp\left(-2\int_{u}^{t_a}k_u^{\prime} du^{\prime}\right) G^{2}(u,t_a) \|(x_u -x_0,y_u-y_0)\|^{2} du \\
+&\leq 16 t_a \alpha^{2}_2 C^{2}_{x,y} \int_{0}^{t_a} \exp\left(-2\int_{u}^{t_a}k_u^{\prime} du^{\prime}\right) G^{2}(u,t_a) \|(x_u - \bar{x}_u,y_u-\bar{y}_u)\|^{2} du \\
+&+ 16 t_a \alpha^{2}_2 C^{2}_{x,y} \int_{0}^{t_a} \exp\left(-2\int_{u}^{t_a}k_u^{\prime} du^{\prime}\right) G^{2}(u,t_a) \|(\bar{x}_u - x_0,\bar{y}_u-y_0)\|^{2} du
+\end{align*}
+and we take $\mathbb{E}^{\mathbb{Q}}\left(\cdot\right)$ on above inequality
+\begin{align*}
+\mathbb{E}^{\mathbb{Q}}\left((A)\right) &\leq 16  t_a \alpha^{2}_2 C^{2}_{x,y} \int_{0}^{t_a} \exp\left(-2\int_{s}^{t_a}k_u^{\prime} du^{\prime}\right) G^{2}(u,t_a) \mathbb{E}^{\mathbb{Q}}\left(\|(\bar{x}_u -x_0,\bar{y}_u-y_0)\|^{2}\right) du \\
+&+\leq 16  t_a \alpha^{2}_2 C^{2}_{x,y} \int_{0}^{t_a} \exp\left(-2\int_{s}^{t_a}k_u^{\prime} du^{\prime}\right) G^{2}(u,t_a) \mathbb{E}^{\mathbb{Q}}\left(\|(x_u - \bar{x}_u,y_u-\bar{y}_u)\|^{2}\right) du
+\end{align*}
+Again, from the hypotheses (\ref{boundedness_volatility}) and (\ref{boundedness_reversion}) we can show that 
+\begin{equation*}
+\mathbb{E}^{\mathbb{Q}}\left(\|(\bar{x}_u -x_0,\bar{y}_u-y_0)\|^{2}\right) = K h(u)
+\end{equation*}
+where $K$ is a constant with no dependency in $u$ and $h(u)\sim \mathcal{O}(u)$. In order to bound $(B)$, we will use the Doob's inequality and (\ref{boundedness_volatility}). Then
+\begin{align*}
+\mathbb{E}^{\mathbb{Q}}&\left((B)\right) \leq 2K \int_{0}^{t_a}  \exp\left(-2\int_{u}^{t_a}k_u^{\prime} du^{\prime} \right) (\eta(u,x_u,y_u)-\eta(u,\bar{x}_u,\bar{y}_u))^{2} du \\
+& \leq 2K C^{2}_{x,y} \int_{0}^{t_a}  \exp\left(-2\int_{u}^{t_a}k_u^{\prime} du^{\prime} \right) \mathbb{E}^{\mathbb{Q}}\left(\|(x_u - \bar{x}_u, y_u - \bar{y}_u) \|^{2}\right) du
+\end{align*}
+On other hand, we have that
+\begin{equation*}
+\mathbb{E}^{\mathbb{Q}}\left((y_{t_a} - \bar{y}_{t_a})^{2} \right) \leq 4 \alpha^{2}_{2} C^{2}_{x,y} \int_{0}^{t_a} \exp\left(-2\int_{u}^{t_a}k_u^{\prime} du^{\prime}\right)\mathbb{E}^{\mathbb{Q}}\left(\|(x_u-\bar{x}_u,y_u-\bar{y}_u)\|^{2}\right) du
+\end{equation*}
+Now, if we put all of the above together, we get that
+\begin{equation*}
+\mathbb{E}^{\mathbb{Q}}\left(\|(x_{t_a} - \bar{x}_{t_a},y_{t_a} - \bar{y}_{t_a})\|^{2}\right) \leq C_1H(t_a) + C_2\int_{0}^{t_a} \mathbb{E}^{\mathbb{Q}}\left(\|(x_{u} - \bar{x}_{u},y_{u} - \bar{y}_{u})\|^{2}\right) du
+\end{equation*}
+where $H(t_a) \mathcal{O}(t_a)$. To end, if we apply the Gronwall's lemma we have that
+\begin{equation*}
+\mathbb{E}^{\mathbb{Q}}\left(\|(x_{t_a} - \bar{x}_{t_a},y_{t_a} - \bar{y}_{t_a})\|^{2}\right) \leq C_1H(t_a) \exp\left(C_2 t_a\right)
+\end{equation*}
+
+\newpage
+
 % TODO: Change bibliographystyle according to the journal style - it should know the online entry, see Matsuda04

### 2023-02-26 Latex/paper.tex
# add \sim
# last version on the paper

@@
 \begin{hypothesis}\label{boundedness_reversion} 
-The mean reversion function $k(\cdot)$ is positive a.s.
+The mean reversion function $k(\cdot)$ is a continuous and positive a.s such that
+\begin{equation*}
+m_k < k(t) \leq M_k \quad \forall t \geq 0.
+\end{equation*}
+
+\begin{remark}
+Under these assumptions on $k(\cdot)$, we have that
+\begin{equation*}
+\lim_{t \to \infty}  I(\alpha,0,t):= \lim_{t \to \infty} \int_{0}^{t} \exp\left(-\alpha \int_{u}^{t} k(s) ds\right) du \leq \frac{1}{\alpha m_k} \quad \text{with} \quad \alpha > 0.
+\end{equation*}
+On other hand, as well it is easy to show that
+\begin{equation*}
+\lim_{t \to \infty}  J(\alpha,0,t):= \lim_{t \to \infty} \int_{0}^{t} G^{\alpha}(u,t) \exp\left(-\alpha \int_{u}^{t} k(s) ds\right) du \leq \frac{1}{\alpha m^{\alpha+1}_{k}}
+\end{equation*}
+\end{remark}
+
 \end{hypothesis}
@@
 \end{align*}
-\newpage
+
 In the next figure, we can check the accuracy of the last formula versus montecarlo. The parameters that we have used are $\sigma=0.015$, $k=0.003$ and flat curve with level $r=0.01$.
@@
 \newpage
-
 \subsection{FRAs in arrears}
@@
 \begin{align*}
-\mathbb{E}^{\mathbb{Q}}\left((A)\right) &\leq 16  t_a \alpha^{2}_2 C^{2}_{x,y} \int_{0}^{t_a} \exp\left(-2\int_{s}^{t_a}k_u^{\prime} du^{\prime}\right) G^{2}(u,t_a) \mathbb{E}^{\mathbb{Q}}\left(\|(\bar{x}_u -x_0,\bar{y}_u-y_0)\|^{2}\right) du \\
-&+\leq 16  t_a \alpha^{2}_2 C^{2}_{x,y} \int_{0}^{t_a} \exp\left(-2\int_{s}^{t_a}k_u^{\prime} du^{\prime}\right) G^{2}(u,t_a) \mathbb{E}^{\mathbb{Q}}\left(\|(x_u - \bar{x}_u,y_u-\bar{y}_u)\|^{2}\right) du
+\mathbb{E}^{\mathbb{Q}}\left((A)\right) &\leq 16  t_a \alpha^{2}_2 C^{2}_{x,y} \int_{0}^{t_a} \exp\left(-2\int_{u}^{t_a}k_u^{\prime} du^{\prime}\right) G^{2}(u,t_a) \mathbb{E}^{\mathbb{Q}}\left(\|(\bar{x}_u -x_0,\bar{y}_u-y_0)\|^{2}\right) du \\
+&+\leq 16  t_a \alpha^{2}_2 C^{2}_{x,y} \int_{0}^{t_a} \exp\left(-2\int_{u}^{t_a}k_u^{\prime} du^{\prime}\right) G^{2}(u,t_a) \mathbb{E}^{\mathbb{Q}}\left(\|(x_u - \bar{x}_u,y_u-\bar{y}_u)\|^{2}\right) du
 \end{align*}
@@
 \begin{equation*}
-\mathbb{E}^{\mathbb{Q}}\left(\|(\bar{x}_u -x_0,\bar{y}_u-y_0)\|^{2}\right) = K h(u)
+\mathbb{E}^{\mathbb{Q}}\left(\|(\bar{x}_u -x_0,\bar{y}_u-y_0)\|^{2}\right) \sim \mathcal{O}(I(0,u,2))
 \end{equation*}
-where $K$ is a constant with no dependency in $u$ and $h(u)\sim \mathcal{O}(u)$. In order to bound $(B)$, we will use the Doob's inequality and (\ref{boundedness_volatility}). Then
+In order to bound $(B)$, we will use the Doob's inequality and (\ref{boundedness_volatility}). Then
 \begin{align*}
@@
 \begin{equation*}
-\mathbb{E}^{\mathbb{Q}}\left(\|(x_{t_a} - \bar{x}_{t_a},y_{t_a} - \bar{y}_{t_a})\|^{2}\right) \leq C_1H(t_a) + C_2\int_{0}^{t_a} \mathbb{E}^{\mathbb{Q}}\left(\|(x_{u} - \bar{x}_{u},y_{u} - \bar{y}_{u})\|^{2}\right) du
+\mathbb{E}^{\mathbb{Q}}\left(\|(x_{t_a} - \bar{x}_{t_a},y_{t_a} - \bar{y}_{t_a})\|^{2}\right) \leq C_1H(t_a) + C_2\int_{0}^{t_a} \exp\left(-2\int_{u}^{t_a}k_u^{\prime} du^{\prime} \right) \mathbb{E}^{\mathbb{Q}}\left(\|(x_{u} - \bar{x}_{u},y_{u} - \bar{y}_{u})\|^{2}\right) du
 \end{equation*}
-where $H(t_a) \mathcal{O}(t_a)$. To end, if we apply the Gronwall's lemma we have that
+where $C_1$ and $C_1$ are adequate positive constants and $H(t_a) \sim \mathcal{O}(\int_{0}^{t_a} I(0,u,2) du)$. To end, if we apply a slightly modified version of the Gronwall's lemma we have that
 \begin{equation*}
-\mathbb{E}^{\mathbb{Q}}\left(\|(x_{t_a} - \bar{x}_{t_a},y_{t_a} - \bar{y}_{t_a})\|^{2}\right) \leq C_1H(t_a) \exp\left(C_2 t_a\right)
+\mathbb{E}^{\mathbb{Q}}\left(\|(x_{t_a} - \bar{x}_{t_a},y_{t_a} - \bar{y}_{t_a})\|^{2}\right) \leq C_1 H(t_a)+ \int_{0}^{t_a} \exp\left(- C_2 \int_{u}^{t} k(s^{\prime})  ds^{\prime} \right) H(u) du.
 \end{equation*}

### 2023-03-05 Latex/paper-resum.tex
New version
Moving the proofs to the appendix

--- 2023-02-21 Latex/paper.tex
@@
 \usepackage{multirow}
+\usepackage{float}
 
@@
 \section{Preliminaries and notation}\label{sec:Notation}
+In this section, we give the basic preliminaries and notation necessary throughout the paper.
+\subsection{A tale of two curves}
 Consider a continuous-time economy where zero-coupon bonds are traded for all maturities.
@@
 Clearly, $P(T,T)=1$.
-We define the compounded instantaneous forward rate forward rate as:
+The compounded instantaneous forward rate is defined as:
 \begin{eqnarray*}
@@
 \end{eqnarray*}
-We have that the price of a zero-coupon bond is given by
+Therefore, the zero-coupon bond price is given by
 \begin{eqnarray*}
@@
 
-Before the financial crisis, there was a single curve framework where there was a single curve for discounting and forecasting.
-Since then, the market has adopted a multi-curve approach with two different curves: the discounting curve and the estimation curve chosen based on the maturity of the underlying rate.
-The difference between these two curves is known as basis.
+Before the financial crisis, there was a single curve framework based on the same curve for discounting and forecasting.
+Since then, the market has adopted a multi-curve approach with two different curves: the discount curve and the estimation curve chosen based on the maturity of the underlying rate.
+The difference between these two curves is known as the basis.
 In this paper, we will assume that the basis are not stochastic.
-Therefore can be directly obtained from the market at time $t=0$.
+Therefore, it can be obtained directly from the market at time $t=0$.
 In other words, the estimation forward curve $f_{E}(t, T)$ is given by
@@
 
-We will assume that the $f_{ois}$ dynamics follows a single factor Heath-Jarrow-Morton model under the $\mathbb{Q}$-measure.
-Therefore, let $T>0$ a fixed time horizon, $t>0$ the starting time, and $W$ a Brownian motion defined on a complete probability space $(\omega, \mathcal{F}, \mathbb{P})$.
-Then, under the HJM we have the following dynamics
-\begin{align}\label{ois_forward_rate_curve}
-df_{ois}(t,T) &= \sigma(t,T)\nu(t,T)dt + \sigma(t,T)dW^{\mathbb{Q}}_t
-\end{align}
-where $\nu(t,T)=\int_{t}^{T}\sigma(t,s)ds$ and $\sigma(t, T)$ are $\mathcal{F}_{t}$-adapted process that are positive functions for all $t,T$ . In particular, we have that
-\begin{eqnarray*}
-f_{ois}(t,T)= -\partial_{T}\ln P_{ois}(t,T).
-\end{eqnarray*}
-
-In order to have a Markovian representation of the HJM, we will assume that the volatility is separable, i.e.
-\begin{equation}
-\sigma(t,T)= h(t)g(T).
-\end{equation}
-with $g$ a positive time-dependent function and $h$ a non-negative process. In addition
-\begin{align*}
-\eta_t &= g(t)h(t,x_t,y_t)  \nonumber \\
-k_t &= - \frac{\partial_t g(t)}{g(t)}.
-\end{align*}
-Throught this paper, we assume the following hypotheses on $\eta(t,x,y)$.
-\begin{hypothesis}\label{boundedness_volatility} 
-The process $\eta_t$ is global Lipschitz and differentiable a.s. In addition, we will suppose that
-\begin{align*}
-a1 \leq \eta(t,x,y) \leq a2 \quad \forall (t,x,t) \in \mathbb{R}^{+} \times \mathbb{R} \times \mathbb{R}^{+}. \\
-|\eta(t,x_2,y_2) - \eta(t,x_2,y_2)| \leq C_{x,y}\left(|x_2 - x_1| + |y_2 - y_1| \right) \quad \forall (t,x,t) \in \mathbb{R}^{+} \times \mathbb{R} \times \mathbb{R}^{+} 
-\end{align*}
-\end{hypothesis}
-\begin{hypothesis}\label{boundedness_reversion} 
-The next integrals are finite
-\begin{align*}
-I_{1,k}(0,t) &= \int_{0}^{t} \exp\left(- 2 \int_{s}^{t} k(s^{\prime})ds^{\prime}\right)  ds < \infty \\
-I_{2,k}(0,t) &= \int_{0}^{t} \exp\left(- \int_{s}^{t} k(s^{\prime})ds^{\prime}\right) G(s,t) ds < \infty
-\end{align*}
-\end{hypothesis}
-\begin{remark}
-Notice that the above hypotheses have been chosen for the sake of simplicity, but they can be replaced by adequate integrability conditions.
-\end{remark}
-We must note, that under the hypothesis (\ref{boundedness_volatility}) $\partial_x \eta(t,x,y)$ and $\partial_y \eta(t,x,y)$ are bounded.
-This version of the HJM is also known as the Cheyette model, \cite{Cheyette}.
-It is easy to show (see \cite{Andreasen01} that
-\begin{equation}
-r_{ois}(t)=f_{ois}(t,t)= f_{ois}(0,t) + x_t,
-\end{equation}  
-where
-\begin{align}\label{short_rate_cheyette}
-dx_t &= (-k_t x_t + y_t)dt + \eta_t dW_t^{\mathbb{Q}} \nonumber \\
-dy_t &= (\eta^{2}_t - 2 k_t y_t) dt ,
-\end{align} 
-with 
-\begin{align*}
-\eta_t &= g(t)h(t,x_t,y_t)  \nonumber \\
-k_t &= - \frac{\partial_t g(t)}{g(t)}.
-\end{align*}
-Now if we do a little bit of algebra and we use Itô formula we can show the next representation formula for $P_{ois}(t,T)$
-\begin{equation}\label{bond_ois}
-P_{ois}(t,T) = \frac{P_{ois}(0,T)}{P_{ois}(0,t)} \exp\left(-G(t,T)x_t - \frac{1}{2} G^{2}(t,T)y_t \right)
-\end{equation}
-where $G(t,T) = \int_{t}^{T} \exp\left(-\int_{t}^{u} k_s ds \right) du$. We must observe, that under the representation (\ref{estimation_forward_rate_curve}) we have that
+Given the discount curve $P_{ois}(t,T)$ and using the representation \eqref{estimation_forward_rate_curve}, it is possible to find the discount curve for the estimation curve using the relation
 \begin{equation}\label{bond_forward}
@@
 
-\section{Basic introduction to Malliavin calculus}\label{sec:Malliavin}
-Malliavin calculus is an infinite-dimensional calculus in a Gaussian space, that is, a stochastic calculus of variations.
-In other words, this is a theory that provides a way to calculate the derivatives of random variables defined in a Gaussian probability space with respect to the underlying noise.
-The initial objective of Malliavin was the study of the existence of densities of Wiener functionals such as solutions of stochastic differential equations.
-But, nowadays, it has become an important tool in stochastic analysis due to the increase in its applications.
-Some of these applications include stochastic calculus for fractional Brownian motion, central limit theorems for multiple stochastic integrals, and an extension of the Itô formula for anticipative processes, but especially mathematical finance.
-For example, we can apply Mallaivin calculus for computing hedging strategies, Greeks, or obtain price approximations.
-See, for example, \cite{AlosLorite} or \cite{Nualart} for more general content.\\
-
-In our case, we are interested in using the Malliavin calculus to apply the Clark–Ocone representation theorem. But, first of all, let's introduce some basic concepts.\\
-
-Now, we introduce the derivative operator in the Malliavin calculus sense and the divergence operator to establish the notation that we use in the remainder of the paper.\\
-
-Consider $W=\left\{W_{t}, t\in \left[0,T\right]\right\}$ a Brownian motion defined on a complete probability space $\left(\Omega, \mathcal{F}, \mathbb{P}\right)$.
-Let $H=L^{2}(\left[0,T\right])$ and denote by
+\subsection{The model}
+We will assume that the $f_{ois}$ dynamics follows a single factor Heath-Jarrow-Morton model under the $\mathbb{Q}$-measure.
+Therefore, let $T>0$ a fixed time horizon, $t>0$ the starting time, and $W$ a Brownian motion defined on a complete probability space $(\omega, \mathcal{F}, \mathbb{P})$.
+Then, the HJM model is defined by
+\begin{align}\label{ois_forward_rate_curve}
+df_{ois}(t,T) &= \sigma(t,T)\nu(t,T)dt + \sigma(t,T)dW^{\mathbb{Q}}_t
+\end{align}
+where $\nu(t,T)=\int_{t}^{T}\sigma(t,s)ds$ and $\sigma(t, T)$ are $\mathcal{F}_{t}$-adapted process that are positive functions for all $t,T$. In particular, we have that
 \begin{eqnarray*}
-W_{t} := \int^{T}_{0} t_{s} \d W_{s},
-\end{eqnarray*}
-the It\^o integral of a deterministic function $h \in H$, also known as Wiener integral. Let $\mathcal{S}$ be the set of smooth random variables of the form
-\begin{eqnarray*}
-F=f\left(W_{t_{1}}, \ldots, W{t_{n}}\right)
-\end{eqnarray*}
-with $t_{1}, \ldots, t_{n} \in \left[0,T\right]$ and $f$ is infinitely differentiable bounded function.
-
-\medbreak
-
-The derivative of a random variable $F$, $D_{s}F$, is defined as the stochastic process given by
-\begin{eqnarray*}
-D_{s}F = \sum^{n}_{i=1} \frac{\partial f}{\partial x_{i}}\left(W_{t_{1}}, \ldots, W_{t_{n}}\right)1_{\left[0, t_{j}\right]}(s), \hspace{0.4cm} s \in \left[0,T\right].
+f_{ois}(t,T)= -\partial_{T}\ln P_{ois}(t,T).
 \end{eqnarray*}
 
-The iterated derivative operator of a random variable $F$ is defined by
+To have a Markovian representation of the HJM, we will assume that the volatility is separable, i.e.
+\begin{equation}\label{separation_condition}
+\sigma(t,T)= h(t)g(T).
+\end{equation}
+with $g$ a positive time-dependent function and $h$ a non-negative process. In addition,
+\begin{align*}
+\eta_t &= g(t)h(t,x_t,y_t)  \nonumber \\
+k_t &= - \frac{\partial_t g(t)}{g(t)}.
+\end{align*}
+
+This version of the HJM is also known as the Cheyette model, \cite{Cheyette}. In \cite{AndreasenPiterbarg}, we have the following proposition.
+\begin{proposition}
+Consider the HJM model \eqref{ois_forward_rate_curve} with the separable volatility condition \eqref{separation_condition}. Define the stochastic processes $x(t)$ and $y(t)$ by
+\begin{align}\label{short_rate_cheyette}
+dx_t &= \left(-k(t) x(t) + y(t)\right)dt + \eta\left(t,x(t),y(t)\right) dW_t^{\mathbb{Q}} \nonumber \\
+dy_t &= \left(\eta^{2}(t) - 2 k(t) y(t)\right) dt ,\nonumber \\
+x(0) &=y(0)=0.
+\end{align}
+All zero-discount bonds are deterministic functions of the processes $x(t)$ and $y(t)$,
 \begin{eqnarray*}
-D^{m}_{s_{1}, \ldots, s_{m}} F = D_{s_{1}} \cdots D_{s_{m}}F, \hspace{0.4cm} s_{1}, \ldots, s_{m} \in \left[0,T\right].
+P_{ois}(t,T)=P(t, T, x(t), y(t)), 
 \end{eqnarray*}
+where 
+\begin{eqnarray}\label{bond_ois}
+P_{ois}(t,T,x,y) = \frac{P_{ois}(0,T)}{P_{ois}(0,t)} \exp\left(-G(t,T)x - \frac{1}{2} G^{2}(t,T)y \right),
+\end{eqnarray}
+where $G(t,T) = \int_{t}^{T} \exp\left(-\int_{t}^{u} k(s) ds \right) du$ and the short rate is
+\begin{equation}
+r_{ois}(t)=f_{ois}(t,t)= f_{ois}(0,t) + x(t).
+\end{equation} 
+\end{proposition}
 
-\cite{Nualart} stated that these operators are closable from $L^{p}(\Omega)$ into $L^{p}(\Omega; L^{2}\left[0,T\right])$ for any $p\geq1$, and we denote by $\mathbb{D}^{n,p}$ the closure of $\mathcal{S}$ with respect to the norm
-\begin{eqnarray*}
-\left\|F\right\|_{n,p} := \left(E\left[F\right]^{p} + \sum^{n}_{i=1} E\left\|D^{i} F\right\|^{p}_{L^{2}\left(\left[0,T\right]^{i}\right)} \right)^{\frac{1}{p}}.
-\end{eqnarray*}
+The whole interest rate curve can be reduced to the evolution of the two-state variables $x(t)$ and $y(t)$.
+The variable $x(t)$ constitutes the main yield curve driver, whereas $y(t)$ is an auxiliary `convexity' variable.
+Note that the function $y(t)$ is not deterministic, however, it does not have a diffusion term.
+We call such processes locally deterministic.
+\\
 
-\medbreak
+We can see from \eqref{short_rate_cheyette} that
+\begin{equation*}
+x(t_a) = \int_{0}^{t_a} \exp\left(-\int_{s}^{t_a}k(u) du\right) y(u) du + \int_{0}^{t_a}  \exp\left(-\int_{s}^{t_a}k(u) du \right) \eta(u,x(u),y(u)) dW_u^{\mathbb{Q}}. 
+\end{equation*}
 
-We define $\delta$ as the adjoint of derivative operator $D$, also referred to as the Skorohod integral.
-The domain of $\delta$, denoted by $Dom\text{ }\delta$, is the set of elements $u \in L^{2}([0,T] \times \Omega)$ such that there exists $\delta(u) \in L^{2}(\Omega)$ satisfying the duality relation
-\begin{eqnarray*}
-E\left[\delta(u) F \right] = E\left[\int^{T}_{0} \left(D_{s} F\right) u_{s} \d s\right].
-\end{eqnarray*}
+In order to have a more manageable model, we will follow the ideas of \cite{AndreasenPiterbarg} where the state variables are approximated. So, we can approximate $y(t)$ as
+\begin{equation}\label{approximation_y_t}
+y(t) \approx \bar{y}(t):=\int_{0}^{t} \exp\left(-2\int_{u}^{t} k(w) dw \right) \eta^{2}(u,x(0),y(0)) du
+\end{equation} 
+and
+\begin{eqnarray}
+X_{t_a} \approx \bar{X}(t_a):= \bar{x}_0(t_a)  &+& \int_{0}^{t_a} \exp\left(-\int_{s}^{t_a}k(u) du\right) \bar{y}(u) du \nonumber \\
+&+& \int_{0}^{t_a}  \exp\left(-\int_{s}^{t_a}k(u) du \right) \eta(u,\bar{x}(u),\bar{y}(u)) dW_u^{\mathbb{Q}}   \label{approximation_x_t_a}
+\end{eqnarray}
+with initial condition $\bar{x}_{0}(t_a)$ is such a way that  
+\begin{equation*}
+S_{a,b}(t_a,\bar{x}_0(t_a), \bar{y}_{t_a}) = S_{a,b}(0).
+\end{equation*}
 
-The operator $\delta$ is an extension of the Itô integral in the sense that the set $L^{2}_{a}([0,T] \times \Omega)$ of square integrable and adapted processes is included in $Dom\text{ }\delta$ and the operator $\delta$ restricted to $L^{2}_{a}([0,T] \times \Omega)$ coincides with the Itô stochastic integral.
+\subsection{Model constraints}
+To calculate the convergence order of the convexity adjustment approximation, we use the following hypotheses on $\eta(t,x,y)$.
+\begin{hypothesis}\label{boundedness_volatility} 
+The process $\eta_t$ is global Lipschitz and differentiable a.s. In addition, we will suppose that
+\begin{align*}
+\alpha_1 \leq \eta(t,x,y) \leq \alpha_2 \quad \forall (t,x,y) \in \mathbb{R}^{+} \times \mathbb{R} \times \mathbb{R}^{+}. \\
+|\eta(t,x_2,y_2) - \eta(t,x_1,y_1)| \leq C_{x,y} \lVert (x_2-x_1,y_2-y_1)\rVert \quad \forall (t,x,y) \in \mathbb{R}^{+} \times \mathbb{R} \times \mathbb{R}^{+} 
+\end{align*}
+with $\lVert \cdot \rVert$ euclidean norm in $\mathbb{R}^{2}$.
+\end{hypothesis}
 
-\medbreak
+The mean reversion function $k(\cdot)$ influences the range and flexibility of the volatility structure. The function is always positive and, in practice, it is usually low.
 
-For any $u \in Dom\text{ }\delta$, we will use the following notation
-\begin{eqnarray*}
-\delta(u)=\int^{T}_{0}u_{s}\d W_{s}.
-\end{eqnarray*}
+\begin{hypothesis}\label{boundedness_reversion} 
+The mean reversion function $k(\cdot)$ is a continuous and positive a.s such that
+\begin{equation*}
+m_k < k(t) \leq M_k \quad \forall t \geq 0.
+\end{equation*}
 
-\medbreak
+As a consequence.
+\begin{remark}
+Under these assumptions on $k(\cdot)$, we have that
+\begin{equation*}
+\lim_{t \to \infty}  I(\alpha,0,t):= \lim_{t \to \infty} \int_{0}^{t} \exp\left(-\alpha \int_{u}^{t} k(s) ds\right) du \leq \frac{1}{\alpha m_k} \quad \text{with} \quad \alpha > 0.
+\end{equation*}
+On other hand, 
+\begin{equation*}
+\lim_{t \to \infty}  J(\alpha,0,t):= \lim_{t \to \infty} \int_{0}^{t} G^{\alpha}(u,t) \exp\left(-\alpha \int_{u}^{t} k(s) ds\right) du \leq \frac{1}{\alpha m^{\alpha+1}_{k}}
+\end{equation*}
+\end{remark}
+\end{hypothesis}
 
-The representation of functionals of Brownian motion by stochastic integrals, also known as martingale representation, has been widely studied over the years.
-It states that if $F$ is a square-integrable random variable, there exists a unique adapted process $\varphi$ in $L^{2}(\Omega \times \left[0,T\right]; \mathbb{R}^{d})$ such that
-\begin{eqnarray*}
-F=E\left[F\right] + \sum^{n}_{i=1}\int^{T}_{0} \varphi^{i}_{s} dW^{i}_{s}.
-\end{eqnarray*}
-In other words, there exists a unique martingale representation or, more precisely, the integrand $\varphi$ in the representation exists and is unique in $L^{2}(\Omega \times \left[0,T\right]; \mathbb{R}^{d})$.
+The hypotheses have been chosen for simplicity, but they can be replaced by suitable integrability conditions.\\
 
-\medbreak
+Note, that under the hypothesis \eqref{boundedness_volatility}, $\partial_x \eta(t,x,y)$ and $\partial_y \eta(t,x,y)$ are bounded.
 
-Unfortunately, it is not easy to find an analytic representation of the process $\varphi$.
-Here, the Malliavin calculus helps us to find a solution.
-When the random variable $F$ is Malliavin differentiable, the process $\varphi$ appearing in It\^o's representation theorem, is given by
-\begin{eqnarray*}
-\varphi^{i}=E\left[D^{W^{i}}_{t}F|\mathcal{F}^{W}_{s}\right].
-\end{eqnarray*}
-In fact,
-\begin{eqnarray}\label{clark-okone}
-F=E\left[F\right] + \sum^{n}_{i=1}\int^{T}_{0} E\left[D^{W^{i}}_{t}F|\mathcal{F}^{W}_{s}\right] dW^{i}_{s}
-\end{eqnarray}
-is the Clark-Ocone representation formula.
+\subsection{Notation}
+\textcolor{red}{(Falta pasteleo)}\\
+$\delta_{t_1,t_2}=t_2 -t_1$ is the year fraction between $t_1$ and $t_2$.
 
@@
 \begin{equation}\label{forward_rate}
-L_{E}(t_0, t_1, t_2) = \frac{\left(\frac{P_{E}(t_0,t_1)}{P_{E}(t_0,t_2)} - 1 \right)}{\delta_{t_1,t_2}}
+L_{E}(t_0, t_1, t_2) = \frac{1}{\delta_{t_1,t_2}}\left(\frac{P_{E}(t_0,t_1)}{P_{E}(t_0,t_2)} - 1 \right)
 \end{equation} 
 where $P_{E}(t,T)$ is the discount factor for the curve $E$ from $t$ to $T$, and $\delta_{t_1,t_2}$ is the year fraction between $t_1$ and $t_2$.
-Observe that $L_{E}(t, t_1, t_2)$ is a martingale under the forward measure $\mathbb{Q}^{t_2}$.
-Let us define the future rate as:
-\begin{equation}\label{future}
-\hat{L}_{E}(t,t_0, t_1, t_2) = \mathbb{E}_t^{\mathbb{Q}}\left(L_{E}(t_0, t_1, t_2) \right), 
-\end{equation}
-where $\mathbb{Q}$ is the measure associated to the numeraire $B_t=\exp\left(\int_{0}^{t} r_{ois, s} ds \right)$ with $ r_{ois, t}$ the risk free short rate. Using
-\eqref{forward_rate} and \eqref{future}, then the convexity adjustment definition is:
-\begin{equation*}
-CA(t, t_0, t_1, t_2) = \hat{L}_{E}(t,t_0, t_1, t_2) - \mathbb{E}_t^{\mathbb{Q}^{t_2}}\left(L_{E}(t_0, t_1, t_2) \right).
-\end{equation*}
-From (\ref{ois_forward_rate_curve}) and since $f_{ois}(t,T)$ is a $\mathbb{Q}^{T}$ martingale, we have that
-\begin{equation}\label{girsanov_spot_forward}
-dW^{\mathbb{Q}^{t_2}} = dW^{\mathbb{Q}} + \nu(t,t_2) dt. 
-\end{equation}
-Now, if we use (\ref{general_convexity}) with $f(x_t)=L_{E}(t,t_0, t_1, t_2)$, $\mathbb{Q}_1=\mathbb{Q}$, $\mathbb{Q}_1=\mathbb{Q}^{t_2}$ and $\lambda_t = \nu(t,t_2)$,  we get that
-\begin{equation}\label{ca_general_future}
-CA(t, t_0, t_1, t_2) = \mathbb{E}^{\mathbb{Q}^{t2}}\left(\int_{0}^{t_0} \mathbb{E}^{\mathbb{Q}}_{s}\left(D_s L_{E}(t_0,t_1,t_2) \right) \nu(s,t_2) ds \right)
-\end{equation}
-where $\nu(t,T)$ has been defined in (\ref{ois_forward_rate_curve}). Now, from the definition of $L_{E}(t,T)$. Now, if we calculate the malliavin derive of $L_{E}(t_0,t_1,t_2)$ we have that
-\begin{equation*}
-D_s L_{E}(t_0,t_1,t_2) = \frac{H(t_0,t_1)}{\delta_{t_1,t_2}H(t_0,t_2)} D_s \left(\frac{P_{ois}(t_0,t_1)}{P_{ois}(t_0,t_2)}\right) 
-\end{equation*}
-Now from the zero coupon representation formula (\ref{bond_ois}) we get that
-\begin{equation*}
-D_s \left(\frac{P_{ois}(t_0,t_1)}{P_{ois}(t_0,t_2)}\right) = \frac{\left(\partial_{x}P_{ois}(t_0,t_1)P_{ois}(t_0,t_2) - \partial_{x}P_{ois}(t_0,t_2) P_{ois}(t_0,t_1) \right)}{P^{2}_{ois}(t_0,t_2)} D_s x_{t_0}
-\end{equation*}
-therefore
-\begin{equation}\label{malliavin_derive_L}
-D_s L_{E}(t_0,t_1,t_2) = \frac{H(t_0,t_1)}{\delta_{t_1,t_2}H(t_0,t_2)}\frac{\left(\partial_{x}P_{ois}(t_0,t_1)P_{ois}(t_0,t_2) - \partial_{x}P_{ois}(t_0,t_2) P_{ois}(t_0,t_1) \right)}{P^{2}_{ois}(t_0,t_2)} D_s x_{t_0}
-\end{equation}
-If we use (\ref{approximation_D_s_x_t}) with $T_a=t_0$ and $\beta(t,t_0,x,y) = \exp\left(-\int_{s}^{T_a}k_u du \right) \eta(u,x,y)$ we have that
-\begin{align*}
-D_s L_{E}(t_0,t_1,t_2) &\approx \frac{H(t_0,t_1)}{\delta_{t_1,t_2}H(t_0,t_2)}\frac{\left(\partial_{x}P_{ois}(t_0,t_1)P_{ois}(t_0,t_2) - \partial_{x}P_{ois}(t_0,t_2) P_{ois}(t_0,t_1) \right)}{P^{2}_{ois}(t_0,t_2)} \beta(t,t_0,\bar{x}_s,\bar{y}_s)\bar{M}(s,t_0) \nonumber \\
-\approx& \frac{P_{E}(0,t_1)}{\delta_{t_1,t_2} P_{E}(0,t_2)} \left(G(t_0,t_2) \frac{P_{ois}(0,t_2)}{P_{ois}(0,t_0)} - G(t_0,t_1) \frac{P_{ois}(0,t_1)}{P_{ois}(0,t_0)} \right)\beta(t,t_0,\bar{x}_s,\bar{y}_s)\bar{M}(s,t_0)
-\end{align*}
-and therefore
-\begin{equation}\label{approximation_clarkocone}
-\mathbb{E}_s\left( D_s L_{E}(t_0,t_1,t_2) \right) = \frac{P_{E}(0,t_1)}{\delta_{t_1,t_2} P_{E}(0,t_2)} \left(G(t_0,t_2)  - G(t_0,t_1)\right)\beta(t,t_0,x_0,\bar{y}_s)\bar{M}(s,t_0)
-\end{equation}
-Then from (\ref{ca_general_future}) and (\ref{approximation_clarkocone}) we have the next approximation for the convexity adjustmet for future
-\hspace{1cm}
-\fboxsep1em
-\fbox{\parbox{435pt}
-{
+
+\begin{theorem}\label{Th_CA_futures}[Convexity Adjustment approximation for Futures]
+Given the Cheyette model in \eqref{short_rate_cheyette}, the hypothesis \ref{boundedness_volatility} and \ref{boundedness_reversion}, and considering the approximations in \eqref{approximation_y_t} and \eqref{approximation_x_t_a}.
+Then, the convexity adjustment approximation for futures is
 \begin{equation}\label{ca_approximation_futures}
@@
 \end{equation}
-}}
+with 
+\begin{equation*}
+\beta(t,t_0,x,y) = \exp\left(-\int_{s}^{T_a}k_u du \right) \eta(u,x,y).
+\end{equation*}
+\end{theorem}
+\begin{proof}
+See appendix \ref{Proof_CA_futures}.
+\end{proof}
 
-\begin{example}\label{example_ca_future}
-Let us to set 
+\begin{example}[Convexity adjustment for futures under the Hull-White model]\label{example_ca_future}
+The Cheyette model can be reduced to Hull-White model using the following parameters
 \begin{align*}
-g(T) &= \exp(-kT) \\
-h(t) &= \sigma
+g(T) &= \exp(-kT), \\
+h(t) &= \sigma.
 \end{align*}
-\end{example}
-With this parametrization, the Cheyette model is equiavalent to Hull-White model. Also, from the definition of $g(\cdot)$ and $h(\cdot)$, we have that
+Moreover, from the definition of $g(\cdot)$ and $h(\cdot)$, we have that
 \begin{align*}
-\eta_s &= \sigma \exp(-ks)\\
-\beta(s,u, x_0, \bar{y}_s) &= \sigma \exp(-ku) \\
-\nu(s,t_2) &= \sigma \frac{\exp(-ks) - \exp(-kt_2)}{k}\\
+\eta_s &= \sigma \exp(-ks),\\
+\beta(s,u, x_0, \bar{y}_s) &= \sigma \exp(-ku),\\
+\nu(s,t_2) &= \sigma \frac{\exp(-ks) - \exp(-kt_2)}{k}.
 \end{align*}
-Then it easy to show that the convexity adjustment (\ref{ca_approximation_futures}) is
+Then the convexity adjustment \eqref{ca_approximation_futures} is
 \begin{align*}
@@
 \end{align*}
-\newpage
-In the next figure, we can check the accuracy of the last formula versus montecarlo. The parameters that we have used are $\sigma=0.015$, $k=0.003$ and flat curve with level $r=0.01$.
 
-\begin{figure}[h]
+In the Figure \ref{fig:Futures}, we can check the accuracy of the last formula versus Monte Carlo. The parameters that we have used are $\sigma=0.015$, $k=0.003$ and flat curve with level $r=0.01$.
+
+\begin{figure}[H]
 	\begin{center}
 		\includegraphics[scale=0.3]{Figures/future_convexity.jpg}
+	\end{center}
 	\caption{Convexity Mc Vs Convexity Malliavin}
-	\end{center}
+	\label{fig:Futures}
 \end{figure} 
+\end{example}
 
 \subsection{OIS futures}
-In this we will derive the covexity adjustment for overnight-indexed swap (OIS) under. We will define for $t_0 < t_1$
+In this section, we will derive the convexity adjustment for the overnight-indexed swap, also known as OIS.
+Given $t_0 < t_1$, we define \textcolor{red}{(qué es R y Ravg, tipo OIS y tipo OIS medio, nombre tecnico?)}
 \begin{align*}
-R(t_0,t_1) &= \frac{\exp\left(\int_{t_0}^{t_1}r_{ois,u} du \right) - 1}{t_1 - t_0} \\
-R_{avg}(t_0,t_1) &= \frac{\int_{t_0}^{t_1}r_{ois,u} du}{t_1 - t_0}.
+R(t_0,t_1) &:=\frac{1}{\delta_{t_0,t_1}} \left(\exp\left(\int_{t_0}^{t_1}r_{ois,u} du \right) - 1\right), \\
+R_{avg}(t_0,t_1) &:= \frac{1}{\delta_{t_0,t_1}}\int_{t_0}^{t_1}r_{ois,u} du.
 \end{align*}
-We must observe, that both $R(\cdot,t_0,t_1)$ and $R_{avg}(\cdot,t_0,t_1)$  are not predictible and they are only observable in $t_1$. However, since
-$R(\cdot,t_0,t_1)$ and $R_{avg}(\cdot,t_0,t_1)$ are flows that will be payed in $t_1$, we can considerer the expected value under the measure $\mathbb{Q}$ that will observable during whole period $[t_0, t_1]$.
-Let us define the next $\mathbb{Q}$ martingales
+We observe that $R(\cdot,t_0,t_1)$ and $R_{avg}(\cdot,t_0,t_1)$  are not predictable and are only observable in $t_1$. However, 
+$R(\cdot,t_0,t_1)$ and $R_{avg}(\cdot,t_0,t_1)$ are flows that will be payed in $t_1$.
+Therefore, we can consider that the expected value under the measure $\mathbb{Q}$ is observable during entire period $[t_0, t_1]$.
+Let us define the next $\mathbb{Q}$ martingales:
 \begin{align*} 
-\bar{R}(t,t_0,t_1) &= \mathbb{E}_t^{\mathbb{Q}}\left( R(t_0,t_1)  \right) \\
-\bar{R}_{avg}(t,t_0,t_1) &= \mathbb{E}_t^{\mathbb{Q}}\left( R_{avg}(t_0,t_1)  \right).
+\bar{R}(t,t_0,t_1) &:= \mathbb{E}_t^{\mathbb{Q}}\left( R(t_0,t_1)  \right), \\
+\bar{R}_{avg}(t,t_0,t_1) &:= \mathbb{E}_t^{\mathbb{Q}}\left( R_{avg}(t_0,t_1)  \right).
 \end{align*}
-We must do several obeservations. The first observation is that, if we define $F(t,t_0,t_1) = \mathbb{E}^{\mathbb{Q}^{t_1}}\left( R(t_0,t_1)\right)$, then we have that
-\begin{align*}
-F(t,t_0,t_1)&= \frac{1}{P_{ois}(t,t_1)}  \mathbb{E}_{t}^{\mathbb{Q}}\left(\exp\left(-\int_{t}^{t_1} r_{ois,u} du \right) R(t_0,t_1) \right) = \frac{\frac{P_{ois}(t,t_0)}{P_{ois}(t,t_1)} - 1}{t_1 - t_0}, \quad t \in [0,t_0] \\
-F(t,t_0,t_1)&= \frac{1}{P_{ois}(t,t_1)} \mathbb{E}_{t}^{\mathbb{Q}}\left(\exp\left(-\int_{t}^{t_1} r_{ois,u} du \right) R(t_0,t_1) \right) = \frac{1}{t_1 - t_0} \left(\frac{\left( \exp\left(\int_{t}^{t_1}r_{ois,u} du\right)\right)}{P_{ois}(t_0,t)}-1\right), \quad  t \in  [t_0, t_1].
-\end{align*}
-The can define the convexity adjustment for $ R(t_0,t_1)$ the next way
-\begin{equation}\label{R_ois_ca}
-CA_{ois}(t,t_0,t_1) = F(t,t_0,t_1) - \bar{R}(t,t_0,t_1) 
-\end{equation}
-The second observation, is that under the dyam we must do is that
-\begin{equation}\label{R_ois_avg}
-\mathbb{E}^{\mathbb{Q}}\left(R_{avg}(t_0,t_1) \right) = \mathbb{E}^{\mathbb{Q}}\left( \frac{\log\left(1+ \delta_{t_0,t_1} R(t_0,t_1) \right)}{\delta_{t_0,t_1}} \right)  
-\end{equation}
-In order to compute $\mathbb{E}^{\mathbb{Q}}\left(R(t_0,t_1\right)$, we will define
+
+Given $t_0\leq t_1$, we define \textcolor{red}{(qué es I, buscar nombre chulo)}
 \begin{equation*}
-I(t_0,t_1) = \int_{t_0}^{t_1} r_s ds
+I(t_0,t_1) := \int_{t_0}^{t_1} r_s ds.
 \end{equation*}
-If we take $D_s$ on $I(t_0,t_1)$ we have that
-\begin{equation*}
-D_sI(t_0,t_1) = \int_{\max(s, t_{0})}^{t_1}  D_s x_u du 
-\end{equation*}
-Now, if $t < t_0$, then from (\ref{clark-okone}) and (\ref{approximation_spot_E_s_x_t}), we have that 
-\begin{align}\label{apprx_I_t0_t1}
-I(t_0,t_1) &= \mathbb{E}_t^{\mathbb{Q}}\left(I(t_0,t_1)\right) + \int_{t}^{t_1}\int_{\max(s, t_{0})}^{t_1}  \mathbb{E}_s^{\mathbb{Q}}\left(\beta(s,u,x_s,y_s) \bar{M}(s,u) \right) du dW_s^{\mathbb{Q}} \nonumber \\
-&\approx \mathbb{E}_t^{\mathbb{Q}}\left(I(t_0,t_1)\right) + \int_{t}^{t_1}\int_{\max(s, t_{0})}^{t_1} \beta(s,u,x_0,\bar{y}_s) du dW_s^{\mathbb{Q}}\nonumber \\
-&= \mathbb{E}_t^{\mathbb{Q}}\left(I(t_0,t_1)\right) + \int_{t}^{t_1} g(s)h(s,x_0,\bar{y}_s)\int_{\max(s, t_{0})}^{t_1} \exp\left( -\int_{s}^{u} k_{s^{\prime}} ds^{\prime}\right) du dW_s^{\mathbb{Q}}.
-\end{align}
-Then, using the previous approximation, we get that
-\begin{align*}
-1 + \delta_{t_0,t_1}\mathbb{E}_t^{\mathbb{Q}}\left(R(t_0,t_1)\right) &= \mathbb{E}_t^{\mathbb{Q}}\left( \exp(I(t_0,t_1)) \right)\\
-&\approx \exp\left(\mathbb{E}_t^{\mathbb{Q}}\left(I(t_0,t_1)\right)\right)  \mathbb{E}^{\mathbb{Q}}\left(\exp\left(\int_{t}^{t_1} \Gamma(s,t_0,t_1)dW_s^{\mathbb{Q}}\right)\right)
-\end{align*}
-where $\Gamma(s,t_0,t_1)= g(s)h(s,x_0,y_0)\int_{\max(s, t_{0})}^{t_1} \exp\left( -\int_{s}^{u} k_{s^{\prime}} ds^{\prime}\right)du$. 
-Therefore, we have that
-\begin{equation}\label{representation_i_0_t}
-1 + \delta_{t_0,t_1}\mathbb{E}^{\mathbb{Q}}\left(R(t_0,t_1)\right) \approx \exp\left(\mathbb{E}^{\mathbb{Q}}\left(I(t_0,t_1)\right)\right)\exp\left(-\int_{t}^{t_1}\frac{\Gamma^{2}(s,t_0,t_1)}{2} ds\right)
-\end{equation}
-Therefore
 
-\hspace{2cm}
-\fboxsep1em
-\fbox{\parbox{335pt}
-{
+\begin{theorem}\label{Th_CA_OIS}[Convexity Adjustment approximation for OIS Futures]
+Given the Cheyette model in \eqref{short_rate_cheyette}, the hypothesis \ref{boundedness_volatility} and \ref{boundedness_reversion}, and considering the approximations in \eqref{approximation_y_t} and \eqref{approximation_x_t_a}.
+Then, the convexity adjustment approximation for OIS futures is
 \begin{equation}\label{convexity_ois_future}
@@
 \end{equation}
-}}
-In order to get an approximation of $\mathbb{E}^{\mathbb{Q}}\left(R_{avg}(t_0,t_1)\right)$ with base $\mathbb{E}^{\mathbb{Q}}\left(R(t_0,t_1)\right)$, we must note that 
-\begin{equation*}
-\mathbb{E}_t^{\mathbb{Q}}\left(R_{avg}(t_0,t_1)\right) = \frac{\mathbb{E}_t^{\mathbb{Q}}\left( \log(1+ \delta_{t_0,t_1} R(t_0,t_1))\right)}{ \delta_{t_0,t_1}}.
-\end{equation*}
-Then from (\ref{representation_i_0_t}) we get that
-
-\fboxsep1em
-\fbox{\parbox{360pt}
-{
+and for the average OIS future is
 \begin{equation}\label{convexity_avg_ois_future}
@@
 \end{equation}
-}}
+\end{theorem}
+\begin{proof}
+See appendix \ref{Proof_CA_OIS_futures}.
+\end{proof}
 
 \begin{remark}
-We must observe that for the case $t_0 < t < t_1$ we can compute the convexity adjusment in a similar way when $t < t_0$, but in this case we have to define
+We can calculate the convexity adjustment for the case $t_0 < t < t_1$ in a similar way to when $t < t_0$, for this we will define
 \begin{equation*}
-I(t,t_1)=\int_{t}^{t_1} r_s ds
+I(t,t_1):=\int_{t}^{t_1} r_s ds
 \end{equation*}
@@
 \begin{align*}
-R(t_0,t_1) &= \frac{\frac{\exp(\int_{t}^{t_1} r_{ois,s} ds )}{P_{ois}(t_0,t)} - 1}{t_1 - t_0} \\
-R_{avg}(t_0,t_1) &= \frac{\int_{t_0}^{t} r_{ois,s} ds}{t_1-t_0} +  \frac{\int_{t}^{t_1} r_{ois,s} ds}{t_1-t_0}.   
+R(t_0,t_1) &:= \frac{1}{\delta_{t_0,t_1}}\left(\frac{\exp(\int_{t}^{t_1} r_{ois,s} ds )}{P_{ois}(t_0,t)} - 1\right), \\
+R_{avg}(t_0,t_1) &:= \frac{1}{\delta_{t_0,t_1}}\left(\int_{t_0}^{t} r_{ois,s} ds + \int_{t}^{t_1} r_{ois,s} ds\right).   
 \end{align*}
@@
 
-\begin{example}\label{example_convexity_hw_ois}
-The same way that in the example (\ref{example_ca_future}), we will suppose a Hull-White model with constan mean reversion $k=0.003$ and volatility $\sigma=0.01$.
-It is easy to show in the case of the Hull-White model
+\begin{example}[Convexity adjustment for OIS futures under the Hull-White model]\label{example_convexity_hw_ois}
+Similarly to the Example \ref{example_ca_future}, we can find the equivalent parameters for the Hull-White model: 
 \begin{align*}
@@
 \end{align*}
-Therefore we have that
+Therefore, we have that
 \begin{align*}
@@
 &+ \frac{\sigma^{2}}{2k^{2}} \left(\frac{\exp(-2kt_0) - \exp(-2kt_1)}{2k}  + \exp(-kt0)t0 - 2 \frac{\exp(-2kt_0) - \exp(-k(t_0 + t_1))}{k}  \right)
-\end{align*}(we have to review this integral).
-Then, if we substitute the last equalities in (\ref{convexity_ois_future}) we get an approximation for OIS future at $t=0$.
-The next figure, show accuracy of (\ref{convexity_ois_future}) and (\ref{convexity_avg_ois_future}) for the particular case of a Hull-White model.
+\end{align*} \textcolor{red}{(we have to review this integral), Poner abreviado, calculo apendice}\\
+Then, if we substitute the last equalities in (\ref{convexity_ois_future}) we get an approximation for OIS future at $t=0$.\\
 
-\begin{figure}
+The next figure, show accuracy of (\ref{convexity_ois_future}) and (\ref{convexity_avg_ois_future}) for the Hull-White model case when the mean reversion is $k=0.003$ and volatility $\sigma=0.01$. 
+\begin{figure}[H]
 \begin{subfigure}{.5\textwidth}
@@
 
-\newpage
+\subsection{FRAs in arrears}
+A FRA in arrears is the most classic example among the products with convexity adjustment. The price is given by 
+\begin{equation}\label{FRAinArrear}
+P_{E}(0,t_1)\mathbb{E}^{\mathbb{Q}^{t_1}}\left(L_{E}(t_1,t_1,t_2)\right),
+\end{equation}
+i.e. the cash flow associated to a FRA in arrears is $L_{E}(t_1,t_1,t_2)$ in $t_1$.
 
-\subsection{FRAs in arrears}
-The price of a FRA in arrears, is the most classic example between the porducts with convexity adjustment.
-The cash flows associated to a FRAs in arrears is $L_{E}(t_1,t_1,t_2)$ in $t_1$.
-Therefore the payment will be
-\begin{equation}
-P_{E}(0,t_1)\mathbb{E}^{\mathbb{Q}^{t_1}}\left( L_{E}(t_1,t_1,t_2\right).
-\end{equation}
-The expected value is clearly taken with respect to the wrong martingale, because $L_{E}(t,t_1,t_2)$ is martingale under the measure $\mathbb{Q}^{t_2}$.
-In order to calculate, the convexity adjustment we will use as before Clark-Ocone to get a representation for $L_{E}(t_1,t_1,t_2)$ i.e
-\begin{equation}\label{general_convexity_fras}
-L_{E}(t_1,t_1,t_2) = \mathbb{E}^{\mathbb{Q}^{t_2}}\left(L_{E}(t_1,t_1,t_2) \right) + \int_{0}^{t_1} \mathbb{E}^{\mathbb{Q}^{t_2}}\left(D_s L_{E}(t_1,t_1,t_2) \right) dW^{\mathbb{Q}^{t_2}}_{s}
-\end{equation}
-The if we suppose the HJM dynamic (\ref{estimation_forward_rate_curve})and we take $\mathbb{E}^{^{\mathbb{Q}^{t_1}}}(\cdot)$ we get
-\begin{align*}
-\mathbb{E}^{\mathbb{Q}^{t_1}}\left(L_{E}(t_1,t_1,t_2) \right) &= L_{E}(0,t_1,t_2) + \mathbb{E}\left( \int_{0}^{t_1} \mathbb{E}^{\mathbb{Q}^{t_2}}\left(D_s L_{E}(t_1,t_1,t_2) \right) dW^{\mathbb{Q}^{t_2}}_{s}\right)\\
-&= L_{E}(0,t_1,t_2) + \mathbb{E}\left( \int_{0}^{t_1} \mathbb{E}^{\mathbb{Q}^{t_2}}\left(D_s L_{E}(t_1,t_1,t_2) \right) (\nu(s,t_2)-\nu(s,t_1)) ds \right)
-\end{align*}
-Where we have used that 
-\begin{equation*}
-dW^{\mathbb{Q}^{t_2}}_s = dW^{\mathbb{Q}^{t_1}}_s + (\nu(s,t_2) - \nu(s,t_1)) ds 
-\end{equation*}
-Now from (\ref{approximation_D_s_x_t}) we have that 
-\begin{equation*}
-D_s L(t_1,t_1,t_2) = \frac{G(t_1,t_2)}{\delta_{t_1,t_2}P_{E}(t_1,t_2)} D_s x_{t_1} \approx \frac{G(t_1,t_2)}{\delta_{t_1,t_2}P_{E}(0,t_1,t_2)} \beta(s,t_1, x_0, \bar{y}_s)\bar{M}(s,t_1)
-\end{equation*}
-Therefore, if we define and we use (\ref{approsimation_E_s_x_t}) we have that
-\begin{equation*}
-CA(t_0,t_1) = \mathbb{E}^{\mathbb{Q}^{t_1}}\left( L_{E}\left(t_1,t_1,t_2\right)\right) - L_{E}\left(0,t_1,t_2\right)
-\end{equation*}
-and we use the last approximation and (\ref{general_convexity_fras}), we can get the next approximation for $CA(t_0,t_1)$ 
-\hspace{2cm}
-\fboxsep1em
-\fbox{\parbox{475pt}
-{
-\begin{equation}\label{ca_approximations_fra_arrears}
-CA(t_0,t_1) \approx  \frac{G(t_1,t_2)}{\delta_{t_1,t_2}P_{E}(0,t_1,t_2)} \int_{0}^{t_1} \beta(s,t_1, x_0, \bar{y}_s) \exp\left(-\int_{s}^{t_1} \partial_x \beta(u,t_1,x_0,y_0) \nu(u,t_2) du \right) (\nu(s,t_2) - \nu(s,t_1)) ds.
-\end{equation}
-}}
-\begin{example}
-To check how works the last approximation.
-We will restrict a Hull-White model with mean reversion and volatility constant.
-We will use are $\sigma=0.1$, $k=0.007$ for our model.
-The analytical approximation that we get from (\ref{ca_approximation_futures}) is
+\begin{theorem}\label{Th_CA_FRAsinArrears}[Convexity Adjustment approximation for FRAs in Arrears]
+Given the Cheyette model in \eqref{short_rate_cheyette}, the hypothesis \ref{boundedness_volatility} and \ref{boundedness_reversion}, and considering the approximations in \eqref{approximation_y_t} and \eqref{approximation_x_t_a}.
+Then, the convexity adjustment approximation for FRAs in Arrears is
+\begin{align}\label{ca_approximations_fra_arrears}
+CA(t_0,t_1) \approx  \frac{G(t_1,t_2)}{\delta_{t_1,t_2}P_{E}(0,t_1,t_2)} \int_{0}^{t_1}& \beta(s,t_1, x_0, \bar{y}_s) \exp\left(-\int_{s}^{t_1} \partial_x \beta(u,t_1,x_0,y_0) \nu(u,t_2) du \right) \nonumber\\
+\qquad\qquad &\cdot \left(\nu(s,t_2) - \nu(s,t_1)\right) ds.
+\end{align}
+\end{theorem}
+\begin{proof}
+See appendix \ref{Proof_CA_FRAsinArrears}.
+\end{proof}
+
+\begin{example}[Convexity adjustment for FRAs in Arrears under the Hull-White model]\label{example_convexity_hw_FRAsinArrears}
+We can restrict the model the the Hull-White model with constant parameters. The analytical approximation that we get from \eqref{ca_approximations_fra_arrears} is
 \begin{equation*}
@@
 \end{equation*}
-We have checked the last approximation using MC method to compute the value of a FRA in arrears. We will show the result of the simulation in the next figure
-
-\begin{figure}[h]
+In Figure \ref{fig:FRA_HW}, we compare the approximation with a Monte Carlo method when the parameters are $\sigma=0.1$, $k=0.007$.
+\begin{figure}[H]
 		\begin{center}
 		\includegraphics[scale=0.3]{Figures/fra_convexity.jpg}
+		\end{center}
 		\caption{Convexity Mc Vs Convexity Malliavin}
-	\end{center}
+		\label{fig:FRA_HW}
 \end{figure}
-
 \end{example}
@@
 \subsection{CMSs}
-In this last section we will study convexity adjustment for a CMS.
-Let us to introduce some notation, we will use it throughout the section.
-We will define the swap rate from $t_a$ to $T_b$ at time $t$
+The last product we will approximate the convexity adjustment are CMS.
+We will introduce some notation that we will use throughout the section.
+We define the swap rate from $t_a$ to $T_b$ at time $t$ as
 \begin{equation*}
-S_{a,b}(t) = \frac{\sum_{i=1}^{n_E}\delta_{t^{E}_{i-1}, t^{E}_i} L^{E}(t,t^{E}_{i-1}, t^{E}_{i}) P_{ois}(t,t^{E}_{i})}{01(t,t_a,T_b)}
+S_{a,b}(t) := \frac{\sum_{i=1}^{n_E}\delta_{t^{E}_{i-1}, t^{E}_i} L^{E}(t,t^{E}_{i-1}, t^{E}_{i}) P_{ois}(t,t^{E}_{i})}{01(t,t_a,T_b)}
 \end{equation*}
@@
 \begin{remark}
-We must note that from (\ref{bond_forward})we have that
+Note from \eqref{bond_forward} that
 \begin{equation*}
@@
 \end{equation*}
-where $ \alpha(t,t^{E}_{i-1}, t^{E}_{i})  = \frac{\frac{H(t,t^{E}_{i-1})}{H(t,t^{E}_{i})} - 1}{\delta_{t^{E}_{i-1}, t^{E}_i}}$.
-How we have a one-factor HJM model, we can suppose that variability of $\alpha(t,t^{E}_{i-1}, t^{E}_{i})$ is low, and therefore it is reasonable to freeze it at time $t=0$.
-Of this way, we have that
+where 
+\begin{equation*}
+\alpha(t,t^{E}_{i-1}, t^{E}_{i})  = \frac{1}{\delta_{t^{E}_{i-1}, t^{E}_i}}\left(\frac{H(t,t^{E}_{i-1})}{H(t,t^{E}_{i})} - 1\right)
+\end{equation*}
+
+Under one-factor HJM model, we can suppose that variability of $\alpha(t,t^{E}_{i-1}, t^{E}_{i})$ is low. Therefore, it is reasonable to freeze it at time $t=0$. Having
 \begin{equation}\label{approximation_basis_swap}
@@
 \end{equation}
-
 \end{remark}
 
-Now, we suppose that we have a flow in $t_a < t_p < t_b$ with value $S_{a,b}(t_a)$.
-We know that, $S_{a,b}(t_a)$ is a martingale under the measure $\mathbb{Q}^{01}$, but not under the measure $\mathbb{Q}^{t_p}$.
-Therefore, we we have to take into consideration the effect to compute the expected value of $S_{a,b}(t_a)$ in a measure which is not its natural measure.
-Then, the convexity adjustment for a CMS is
+\begin{theorem}\label{Th_CA_CMS}[Convexity Adjustment approximation for CMS]
+Given the Cheyette model in \eqref{short_rate_cheyette}, the hypothesis \ref{boundedness_volatility} and \ref{boundedness_reversion}, and considering the approximations in \eqref{approximation_y_t} and \eqref{approximation_x_t_a}.
+Given
+\begin{equation}
+M(t,t_p)= \frac{P_{ois}(t,t_p)}{01(t,t_a,t_p)}
+\end{equation}
+and 
+\begin{align}\label{cms_first_order_convexity}
+\mathbb{E}^{t_p}\left(S_{a,b}(t_a)\right) \approx  S^{ois}_{a,b}(0) &+ \frac{\partial_x S^{ois}_{a,b}(t_a, \bar{x}_0(t_a),\bar{y}(t_a))\partial_x M(t_a,t_p, \bar{x}_0(t_a),\bar{y}(t_a))}{M(0,t_p)} \nonumber \\
+\qquad\qquad &\cdot \mathbb{E}^{0,1}\left( \int_{0}^{t_a} \left(\mathbb{E}_s^{0,1}\left( D_s x_{t_a}\right)\right)^{2} ds  \right)
+\end{align}
+Then, the convexity adjustment approximation for CMS is
 \begin{equation}
@@
 \end{equation} 
-After some changes of measure, it is easy to show that
-\begin{align}\label{expected_t_p_cms}
-\mathbb{E}^{t_p}\left(S_{a,b}(t_a)\right) &= \frac{1}{M(0,t_p)} \mathbb{E}^{01}\left(S_{a,b}(t_a) M(t_a,t_p)\right) \nonumber \\
-&= \frac{1}{M(0,t_p)} \mathbb{E}^{01}\left(S_{a,b}(t_a) \mathbb{E}^{01}\left( M(t_a,t_p)|S_{a,b}(t_a)\right) \right) \nonumber\\
-\mathbb{E}^{t_p}\left(S_{a,b}(t_a)\right) &\approx  \frac{1}{M(0,t_p)} \mathbb{E}^{01}\left(S^{ois}_{a,b}(t_a) \mathbb{E}^{01}\left( M(t_a,t_p)|S_{a,b}(t_a)\right) \right) + \frac{\sum_{i=1}^{n_E}\delta_{t^{E}_{i-1}, t^{E}_i} \alpha(0,t^{E}_{i-1}, t^{E}_{i}) P_{ois}(0,t^{E}_{i})} {01(0,t_a,t_b)}
-\end{align}
-with $M(t,t_p)= \frac{P_{ois}(t,t_p)}{01(t,t_a,t_p)}$.
-From te previous expression, we must note that under assumption of not stochastic basis, we must to compute the convexity adjustment for the OIS swap rate.
-Another, complicated point, is the expected value
-$$
-\mathbb{E}^{01}\left( M(t_a,t_p)|S_{a,b}(t_a)\right).
-$$
-In order to reduce this complexity, it is a common practice to assume that $M(t_a,t_p)$ is a funtion of the swap rate $S_{a,b}(t_a)$ i.e   $M(t_a,t_p)=f(S_{a,b}(t_a))$, of this way the last expected value is trivial.
-The function $f(\cdot)$ is known as mapping function, and there is a vast literatura about how to choose it (see Piterbarg Volumen III, Hagan paper convexity withour replication).
-We will, try to do an approach, without to specify any mapping function.
-If we apply Clark-Ocone formula to $M(t_a,t_p)$ we get that
-\begin{equation} \label{clark_ocone_swap_m}
-M(t_a,t_p) = M(0,t_p)+ \int_{0}^{t_a} \mathbb{E}_s^{01}\left(D_s M(t_a,t_p)\right) dW^{01}_s
-\end{equation}
-Then, if we sustitute the last expressions in (\ref{expected_t_p_cms}) we have that
-\begin{align}\label{cms_first_order_convexity}
-\mathbb{E}^{t_p}\left(S_{a,b}(t_a)\right) =& S^{ois}_{a,b}(0) + \frac{1}{M(0,t_p)} \mathbb{E}^{01}\left( S^{ois}_a,b(t_a) \int_{0}^{t_a} \mathbb{E}^{0,1}_s\left(D_sX_{t_a}\partial_x M(t_a,t_p)  \right) dW^{0,1}_s   \right) \nonumber \\
-=&  S^{ois}_{a,b}(0) + \frac{1}{M(0,t_p)} \mathbb{E}^{01}\left(\int_{0}^{t_a} D_s X_{t_a} \partial_x S_{a,b}(t_a) \mathbb{E}^{0,1}_s\left(D_sX_{t_a}\partial_x M(t_a,t_p)  \right) ds   \right) \nonumber \\
-\approx&  S^{ois}_{a,b}(0) + \frac{\partial_x S^{ois}_{a,b}(t_a, \bar{x}_0(t_a),\bar{y}(t_a))\partial_x M(t_a,t_p, \bar{x}_0(t_a),\bar{y}(t_a))}{M(0,t_p)} \mathbb{E}^{0,1}\left( \int_{0}^{t_a} \left(\mathbb{E}_s^{0,1}\left( D_s x_{t_a}\right)\right)^{2} ds  \right)
-\end{align}
+\end{theorem}
+\begin{proof}
+See appendix \ref{Proof_CA_CMS}.
+\end{proof}
 
 \begin{remark}
-We must observe that, if we want to use the last approximation  we must be able to approximate $\mathbb{E}_s^{0,1}\left( D_s x_{t_a}\right)$.
-The simplest case, if when $\eta(t,x_t,y_t) \eta(t)$ as for example happens in the Hull-White model or Ho-Lee model.
-The general case, has been treated in (\ref{approximation_under_annuity_measeure_d_s}).
+The key point is calculate an approximation of $\mathbb{E}_s^{0,1}\left( D_s x_{t_a}\right)$.
+The simplest cases are on the Hull-White or Ho-Lee model.
+The general case is treated in (\ref{approximation_under_annuity_measeure_d_s}).
 \end{remark}
 
-\begin{example}
-In order to check the accuracy of the last approximation, we will compute with Monte Carlo method the exact value of $\mathbb{E}^{t_p}\left(S^{ois}_{a,b}(t_a)\right)$ under spot measure $\mathbb{Q}$ i.e we will compute  $\frac{1}{P(0,t_p)}  \mathbb{E}^{\mathbb{Q}}\left(\frac{S_{a,b}(t_a)}{\beta_{t_a}} \right)$.
-In the case of a Hull-White model, we have that
-$$
-D_s x_{t_a} = \sigma \exp(-(t_a - s))
-$$
-therefore (\ref{cms_first_order_convexity}) is equal to
+\begin{example}[Convexity adjustment for CMS under the Hull-White model]
+To check the accuracy of the last approximation, we compute with a Monte Carlo the exact value of $\mathbb{E}^{t_p}\left(S^{ois}_{a,b}(t_a)\right)$ under spot measure $\mathbb{Q}$, i.e we will compute  $\frac{1}{P(0,t_p)}  \mathbb{E}^{\mathbb{Q}}\left(\frac{S_{a,b}(t_a)}{\beta_{t_a}} \right)$.\\
+In the Hull-White model case, we have that
+\begin{equation*}
+D_s x_{t_a} = \sigma \exp(-(t_a - s)).
+\end{equation*}
+Therefore, \eqref{cms_first_order_convexity} is equal to
 \begin{equation*}
@@
 \end{equation*}
-In the next figure, we can see the convexity adjustment for a CMS where the tenor of the underlying swap is 5Y using the last approximation and Montecarlo method with parameters for the Hull-White model $\sigma=0.01$ and $k=0.0007$
+
+In Figure \ref{fig:CMS}, we observe the CMS convexity adjustment when the tenor of the underlying swap is 5Y.
+We compare the last approximation and a Monte Carlo for a Hull-White model with parameters $\sigma=0.01$ and $k=0.0007$
 
@@
 		\includegraphics[scale=0.25]{Figures/cms_convexity_order.jpg}
+	\end{center}
 	\caption{Convexity Mc Vs Convexity Malliavin}
-	\end{center}
+	\label{fig:CMS}
 \end{figure} 
 \end{example}
-
-\newpage
 
@@
 
-\section{Order of the approximation $\bar{y}_t$}
-Under the assumption of $\eta(t,\cdot,\cdot)$ is global Lipschitz and with first derive continuous, we have that
-\begin{align*}
-|\eta^{2}(t,x_t,y_t) - \eta^{2}(t,x_0,y_0)|&=|\eta(t,x_t,y_t) - \eta(t,x_0,y_0)||\eta(t,x_t,y_t) + \eta(t,x_0,y_0)| \nonumber \\ 
-&\leq C_{x,y}\left(|x_t - x_0| + |y_t - y_0|\right) + 
-\end{align*}
-
-\section{Order of the approximation $\bar{x}_t$}
-
-\section{Approximation of $\mathbb{E}_s^{t_p}\left(D_s x_{t_a}\right)$}
-\label{expected_forward_measure_malliavin_derivative_x_t}
-From (\ref{short_rate_cheyette}) is easy to show that
-\begin{equation*}
-x_{t_a} = \int_{0}^{t_a} \exp\left(-\int_{s}^{t_a}k_u du\right) y_u du + \int_{0}^{t_a}  \exp\left(-\int_{s}^{t_a}k_u du \right) \eta(u,x_u,y_u) dW_u^{\mathbb{Q}}  
-\end{equation*}
-In order to get an approximation for $D_sX_{t_a}$ we must to avoid the recurrence in the Malliavin derivative of $X_{t_a}$.
-Follow, the ideas of Piterbarg Volume II, we can approximate $y_t$ the next way
-\begin{equation*}
-y_t \approx \int_{0}^{t} \exp\left(-2\int_{u}^{t} k_{u^{\prime}} du^{\prime} \right) \eta^{2}(u,x_0,y_0) du
-\end{equation*}
-Therefore, if we define $\bar{y}(t)= \int_{0}^{s} \exp\left(-2\int_{u}^{s} k_{u^{\prime}} du^{\prime} \right) \eta(u,x_0,y_0)$, we have that
-\begin{equation}\label{approximation_x_t_a}
-X_{t_a} \approx \bar{X}(t_a):= \bar{x}_0(t_a)  + \int_{0}^{t_a} \exp\left(-\int_{s}^{t_a}k_u du\right) \bar{y}(u) du + \int_{0}^{t_a}  \exp\left(-\int_{s}^{t_a}k_u du \right) \eta(u,\bar{x}(u),\bar{y}(u)) dW_u^{\mathbb{Q}}
-\end{equation}
-With initial condition  $\bar{x}_{0}(t_a)$ is such that $S_{a,b}(t_a,\bar{x}_0(t_a), \bar{y}_{t_a}) = S_{a,b}(0)$ (see Piterbarg Volume II). Now, we must remember that 
-\begin{equation*}
-dW^{\mathbb{Q}^{t_p}} = dW^{\mathbb{Q}} + \bar{\nu}(t,t_p) dt 
-\end{equation*}
-where $\bar{\nu}(t,t_p) = \int_{t}^{t_p} \eta(s,\bar{x}_s,\bar{y}_s) ds $. Then, we have the next approximation of $\bar{x}_{t_a}$ under measure $\mathbb{Q}^{t_p}$
-\begin{align*}
-X_{t_a} &\approx \bar{x}_0  + \int_{0}^{t_a} \exp\left(-\int_{s}^{t_a}k_u du\right) \bar{y}_s ds - \int_{0}^{t_a} \exp\left(-\int_{s}^{t_a}k_u du\right) \bar{\nu}(s, t_p) \eta(s,\bar{x}_s,\bar{y}_s) ds +  \\
-&+ \int_{0}^{t_a}  \exp\left(-\int_{s}^{t_a}k_u du \right)\eta(s,\bar{x}_s,\bar{y}_s) dW_s^{\mathbb{Q}^{t_p}}  
-\end{align*} 
-Then, if we take $D_s$ on $\bar{X}_{t_a}$ we get that (esto hay que formalizarlo...)
+\section{Auxiliary lemmas}
+\begin{lemma}\label{DsX}[Approximation $D_s x_{t_a}$]
+Given the Cheyette model in \eqref{short_rate_cheyette}, the hypothesis \ref{boundedness_volatility} and \ref{boundedness_reversion}, and considering the approximations in \eqref{approximation_y_t} and \eqref{approximation_x_t_a}.
+Then,
 \begin{equation}\label{approximation_D_s_x_t}
@@
 \end{align*}
-With $\beta(u,t_a,x,y) = \exp\left(-\int_{u}^{t_a}k_u^{\prime} du^{\prime}\right) \partial_x \eta(u,x,y)$. Therefore, from previous equalities, we have that
-
+With $\beta(u,t_a,x,y) = \exp\left(-\int_{u}^{t_a}k_u^{\prime} du^{\prime}\right) \partial_x \eta(u,x,y)$. Therefore, we have that
 \begin{equation}\label{approsimation_E_s_x_t}
@@
 \end{equation}
+\end{lemma}
+\begin{proof}
+To get an approximation for $D_sX_{t_a}$ we must to avoid the recurrence in the Malliavin derivative of $X_{t_a}$.
+For that reason, we will use the approximations \eqref{approximation_y_t} and \eqref{approximation_x_t_a}.\\
 
-\section{Approximation of $\mathbb{E}_s^{\mathbb{Q}}\left(D_s x_{t_a}\right)$}
+Using the relation 
+\begin{equation*}
+dW^{\mathbb{Q}^{t_p}} = dW^{\mathbb{Q}} + \bar{\nu}(t,t_p) dt \text{ where }\bar{\nu}(t,t_p) = \int_{t}^{t_p} \eta(s,\bar{x}_s,\bar{y}_s) ds,
+\end{equation*}
+we will represent an approximation of $X_{t_a}$ under the measure $\mathbb{Q}^{t_p}$ 
+\begin{align*}
+X_{t_a} \approx \bar{x}_0  &+ \int_{0}^{t_a} \exp\left(-\int_{s}^{t_a}k_u du\right) \bar{y}_s ds - \int_{0}^{t_a} \exp\left(-\int_{s}^{t_a}k_u du\right) \bar{\nu}(s, t_p) \eta(s,\bar{x}_s,\bar{y}_s) ds   \\
+&+ \int_{0}^{t_a}  \exp\left(-\int_{s}^{t_a}k_u du \right)\eta(s,\bar{x}_s,\bar{y}_s) dW_s^{\mathbb{Q}^{t_p}}. 
+\end{align*}
+\textcolor{red}{(Revisar)}
+\end{proof}
+
+\subsection{Approximation of $\mathbb{E}_s^{\mathbb{Q}}\left(D_s x_{t_a}\right)$}
 Following the same procedure as before, we have that
@@
 
-\section{Approximation of $\mathbb{E}^{01}\left(x_{t_a}\right)$}
-It is easy to show that the dynamic of the bond under HJM assumption is
+\section{Proofs}
+\subsection{Proof Theorem \ref{Th_CA_futures}}\label{Proof_CA_futures}
+Observe that $L_{E}(t, t_1, t_2)$ is a martingale under the forward measure $\mathbb{Q}^{t_2}$. Let us define the future rate as:    
+\begin{equation}\label{future}
+\hat{L}_{E}(t,t_0, t_1, t_2) = \mathbb{E}_t^{\mathbb{Q}}\left(L_{E}(t_0, t_1, t_2) \right), 
+\end{equation}
+where $\mathbb{Q}$ is the measure associated to the numeraire $B_t=\exp\left(\int_{0}^{t} r_{ois, s} ds \right)$ with $ r_{ois, t}$ the risk free short rate. Using
+\eqref{forward_rate} and \eqref{future}, then the convexity adjustment definition is:
+\begin{equation*}
+CA(t, t_0, t_1, t_2) = \hat{L}_{E}(t,t_0, t_1, t_2) - \mathbb{E}_t^{\mathbb{Q}^{t_2}}\left(L_{E}(t_0, t_1, t_2) \right).
+\end{equation*}
+From (\ref{ois_forward_rate_curve}) and since $f_{ois}(t,T)$ is a $\mathbb{Q}^{T}$ martingale, we have that
+\begin{equation}\label{girsanov_spot_forward}
+dW^{\mathbb{Q}^{t_2}} = dW^{\mathbb{Q}} + \nu(t,t_2) dt. 
+\end{equation}
+Applying (\ref{general_convexity}) with $f(x_t)=L_{E}(t,t_0, t_1, t_2)$, $\mathbb{Q}_1=\mathbb{Q}$, $\mathbb{Q}_1=\mathbb{Q}^{t_2}$ and $\lambda_t = \nu(t,t_2)$,  we get that
+\begin{equation}\label{ca_general_future}
+CA(t, t_0, t_1, t_2) = \mathbb{E}^{\mathbb{Q}^{t2}}\left(\int_{0}^{t_0} \mathbb{E}^{\mathbb{Q}}_{s}\left(D_s L_{E}(t_0,t_1,t_2) \right) \nu(s,t_2) ds \right)
+\end{equation}
+where $\nu(t,T)$ has been defined in (\ref{ois_forward_rate_curve}). Calculating the malliavin derive of $L_{E}(t_0,t_1,t_2)$ we have that
+\begin{equation*}
+D_s L_{E}(t_0,t_1,t_2) = \frac{H(t_0,t_1)}{\delta_{t_1,t_2}H(t_0,t_2)} D_s \left(\frac{P_{ois}(t_0,t_1)}{P_{ois}(t_0,t_2)}\right) 
+\end{equation*}
+Now from the zero coupon representation formula (\ref{bond_ois}), we get that
+\begin{equation*}
+D_s \left(\frac{P_{ois}(t_0,t_1)}{P_{ois}(t_0,t_2)}\right) = \frac{\left(\partial_{x}P_{ois}(t_0,t_1)P_{ois}(t_0,t_2) - \partial_{x}P_{ois}(t_0,t_2) P_{ois}(t_0,t_1) \right)}{P^{2}_{ois}(t_0,t_2)} D_s x_{t_0}.
+\end{equation*}
+Therefore
+\begin{equation}\label{malliavin_derive_L}
+D_s L_{E}(t_0,t_1,t_2) = \frac{H(t_0,t_1)}{\delta_{t_1,t_2}H(t_0,t_2)}\frac{\left(\partial_{x}P_{ois}(t_0,t_1)P_{ois}(t_0,t_2) - \partial_{x}P_{ois}(t_0,t_2) P_{ois}(t_0,t_1) \right)}{P^{2}_{ois}(t_0,t_2)} D_s x_{t_0}.
+\end{equation}
+If we use (\ref{approximation_D_s_x_t}) with $T_a=t_0$ and $\beta(t,t_0,x,y) = \exp\left(-\int_{s}^{T_a}k_u du \right) \eta(u,x,y)$, we have that
+\begin{align*}
+D_s L_{E}(t_0,t_1,t_2) &\approx \frac{H(t_0,t_1)}{\delta_{t_1,t_2}H(t_0,t_2)}\frac{\left(\partial_{x}P_{ois}(t_0,t_1)P_{ois}(t_0,t_2) - \partial_{x}P_{ois}(t_0,t_2) P_{ois}(t_0,t_1) \right)}{P^{2}_{ois}(t_0,t_2)} \beta(t,t_0,\bar{x}_s,\bar{y}_s)\bar{M}(s,t_0) \nonumber \\
+\approx& \frac{P_{E}(0,t_1)}{\delta_{t_1,t_2} P_{E}(0,t_2)} \left(G(t_0,t_2) \frac{P_{ois}(0,t_2)}{P_{ois}(0,t_0)} - G(t_0,t_1) \frac{P_{ois}(0,t_1)}{P_{ois}(0,t_0)} \right)\beta(t,t_0,\bar{x}_s,\bar{y}_s)\bar{M}(s,t_0).
+\end{align*}
+Therefore
+\begin{equation}\label{approximation_clarkocone}
+\mathbb{E}_s\left( D_s L_{E}(t_0,t_1,t_2) \right) = \frac{P_{E}(0,t_1)}{\delta_{t_1,t_2} P_{E}(0,t_2)} \left(G(t_0,t_2)  - G(t_0,t_1)\right)\beta(t,t_0,x_0,\bar{y}_s)\bar{M}(s,t_0).
+\end{equation}
+Then from (\ref{ca_general_future}) and (\ref{approximation_clarkocone}) we find the approximation for the convexity adjustment for futures.
+
+\subsection{Proof Theorem \ref{Th_CA_OIS}}\label{Proof_CA_OIS_futures}
+To prove it, we will do several observations. The first observation is that if we define $F(t,t_0,t_1) = \mathbb{E}^{\mathbb{Q}^{t_1}}\left( R(t_0,t_1)\right)$, then we have that
+\begin{align*}
+F(t,t_0,t_1)&= \frac{1}{P_{ois}(t,t_1)}  \mathbb{E}_{t}^{\mathbb{Q}}\left(\exp\left(-\int_{t}^{t_1} r_{ois,u} du \right) R(t_0,t_1) \right) = \frac{1}{\delta_{t_0,t_1}}\left(\frac{P_{ois}(t,t_0)}{P_{ois}(t,t_1)} - 1\right), \quad t \in [0,t_0] \\
+F(t,t_0,t_1)&= \frac{1}{P_{ois}(t,t_1)} \mathbb{E}_{t}^{\mathbb{Q}}\left(\exp\left(-\int_{t}^{t_1} r_{ois,u} du \right) R(t_0,t_1) \right) = \frac{1}{\delta_{t_0,t_1}} \left(\frac{\left( \exp\left(\int_{t}^{t_1}r_{ois,u} du\right)\right)}{P_{ois}(t_0,t)}-1\right), \quad  t \in  [t_0, t_1].
+\end{align*}
+The convexity adjustment for $ R(t_0,t_1)$ can be defined as
+\begin{equation}\label{R_ois_ca}
+CA_{ois}(t,t_0,t_1) = F(t,t_0,t_1) - \bar{R}(t,t_0,t_1).
+\end{equation}
+The second observation is that we have the following equivalence
+\begin{equation}\label{R_ois_avg}
+\mathbb{E}^{\mathbb{Q}}\left(R_{avg}(t_0,t_1) \right) = \mathbb{E}^{\mathbb{Q}}\left( \frac{\log\left(1+ \delta_{t_0,t_1} R(t_0,t_1) \right)}{\delta_{t_0,t_1}} \right)  \end{equation}
+To compute $\mathbb{E}^{\mathbb{Q}}\left(R(t_0,t_1)\right)$, we apply $D_s$ on $I(t_0,t_1)$ obtaining that
+\begin{equation*}
+D_s I(t_0,t_1) = \int_{\max(s, t_{0})}^{t_1}  D_s x_u du 
+\end{equation*}
+Now, if $t < t_0$, then from (\ref{clark-okone}) and (\ref{approximation_spot_E_s_x_t}), we have that 
+\begin{align}\label{apprx_I_t0_t1}
+I(t_0,t_1) &= \mathbb{E}_t^{\mathbb{Q}}\left(I(t_0,t_1)\right) + \int_{t}^{t_1}\int_{\max(s, t_{0})}^{t_1}  \mathbb{E}_s^{\mathbb{Q}}\left(\beta(s,u,x_s,y_s) \bar{M}(s,u) \right) du dW_s^{\mathbb{Q}} \nonumber \\
+&\approx \mathbb{E}_t^{\mathbb{Q}}\left(I(t_0,t_1)\right) + \int_{t}^{t_1}\int_{\max(s, t_{0})}^{t_1} \beta(s,u,x_0,\bar{y}_s) du dW_s^{\mathbb{Q}}\nonumber \\
+&= \mathbb{E}_t^{\mathbb{Q}}\left(I(t_0,t_1)\right) + \int_{t}^{t_1} g(s)h(s,x_0,\bar{y}_s)\int_{\max(s, t_{0})}^{t_1} \exp\left( -\int_{s}^{u} k_{s^{\prime}} ds^{\prime}\right) du dW_s^{\mathbb{Q}}.
+\end{align}
+Then, using the previous approximation, we get that
+\begin{align*}
+1 + \delta_{t_0,t_1}\mathbb{E}_t^{\mathbb{Q}}\left(R(t_0,t_1)\right) &= \mathbb{E}_t^{\mathbb{Q}}\left( \exp(I(t_0,t_1)) \right)\\
+&\approx \exp\left(\mathbb{E}_t^{\mathbb{Q}}\left(I(t_0,t_1)\right)\right)  \mathbb{E}^{\mathbb{Q}}\left(\exp\left(\int_{t}^{t_1} \Gamma(s,t_0,t_1)dW_s^{\mathbb{Q}}\right)\right)
+\end{align*}
+where $\Gamma(s,t_0,t_1)= g(s)h(s,x_0,y_0)\int_{\max(s, t_{0})}^{t_1} \exp\left( -\int_{s}^{u} k_{s^{\prime}} ds^{\prime}\right)du$.\\
+Therefore, we have that
+\begin{equation}\label{representation_i_0_t}
+1 + \delta_{t_0,t_1}\mathbb{E}^{\mathbb{Q}}\left(R(t_0,t_1)\right) \approx \exp\left(\mathbb{E}^{\mathbb{Q}}\left(I(t_0,t_1)\right)\right)\exp\left(-\int_{t}^{t_1}\frac{\Gamma^{2}(s,t_0,t_1)}{2} ds\right).
+\end{equation}
+Then, we obtain \eqref{convexity_ois_future}.
+
+In order to get an approximation of $\mathbb{E}^{\mathbb{Q}}\left(R_{avg}(t_0,t_1)\right)$ with base $\mathbb{E}^{\mathbb{Q}}\left(R(t_0,t_1)\right)$, we must note that 
+\begin{equation*}
+\mathbb{E}_t^{\mathbb{Q}}\left(R_{avg}(t_0,t_1)\right) = \frac{\mathbb{E}_t^{\mathbb{Q}}\left( \log(1+ \delta_{t_0,t_1} R(t_0,t_1))\right)}{ \delta_{t_0,t_1}}.
+\end{equation*}
+Then from (\ref{representation_i_0_t}), we get \eqref{convexity_avg_ois_future}.
+
+\subsection{Proof Theorem \ref{Th_CA_FRAsinArrears}}\label{Proof_CA_FRAsinArrears}
+$L_{E}(t,t_1,t_2)$ is martingale under the measure $\mathbb{Q}^{t_2}$, therefore the expected value of \eqref{FRAinArrear} is taken with respect to the wrong martingale.
+To calculate the convexity adjustment we use the Clark-Ocone to get a representation for $L_{E}(t_1,t_1,t_2)$ i.e
+\begin{equation}\label{general_convexity_fras}
+L_{E}(t_1,t_1,t_2) = \mathbb{E}^{\mathbb{Q}^{t_2}}\left(L_{E}(t_1,t_1,t_2) \right) + \int_{0}^{t_1} \mathbb{E}^{\mathbb{Q}^{t_2}}\left(D_s L_{E}(t_1,t_1,t_2) \right) dW^{\mathbb{Q}^{t_2}}_{s}
+\end{equation}
+Under the HJM dynamics, we have the relation
+\begin{equation*}
+dW^{\mathbb{Q}^{t_2}}_s = dW^{\mathbb{Q}^{t_1}}_s + (\nu(s,t_2) - \nu(s,t_1)) ds. 
+\end{equation*}
+Taking $\mathbb{E}^{^{\mathbb{Q}^{t_1}}}(\cdot)$, we get that
+\begin{align*}
+\mathbb{E}^{\mathbb{Q}^{t_1}}\left(L_{E}(t_1,t_1,t_2) \right) &= L_{E}(0,t_1,t_2) + \mathbb{E}\left( \int_{0}^{t_1} \mathbb{E}^{\mathbb{Q}^{t_2}}\left(D_s L_{E}(t_1,t_1,t_2) \right) dW^{\mathbb{Q}^{t_2}}_{s}\right)\\
+&= L_{E}(0,t_1,t_2) + \mathbb{E}\left( \int_{0}^{t_1} \mathbb{E}^{\mathbb{Q}^{t_2}}\left(D_s L_{E}(t_1,t_1,t_2) \right) (\nu(s,t_2)-\nu(s,t_1)) ds \right).
+\end{align*}
+Now from (\ref{approximation_D_s_x_t}) we have that 
+\begin{eqnarray*}
+D_s L(t_1,t_1,t_2) &=& \frac{G(t_1,t_2)}{\delta_{t_1,t_2}P_{E}(t_1,t_2)} D_s x_{t_1}\\
+&\approx& \frac{G(t_1,t_2)}{\delta_{t_1,t_2}P_{E}(0,t_1,t_2)} \beta(s,t_1, x_0, \bar{y}_s)\bar{M}(s,t_1)
+\end{eqnarray*}
+Therefore, if we define and we use (\ref{approsimation_E_s_x_t}) we have that
+\begin{equation*}
+CA(t_0,t_1) = \mathbb{E}^{\mathbb{Q}^{t_1}}\left( L_{E}\left(t_1,t_1,t_2\right)\right) - L_{E}\left(0,t_1,t_2\right)
+\end{equation*}
+and we use the last approximation and (\ref{general_convexity_fras}), we can get the next approximation for $CA(t_0,t_1)$.
+
+\subsection{Proof Theorem \ref{Th_CA_CMS}}\label{Proof_CA_CMS}
+Assume we have a cash flow in $t_a < t_p < t_b$ with value $S_{a,b}(t_a)$.
+$S_{a,b}(t_a)$ is a martingale under the measure $\mathbb{Q}^{01}$, but not under the measure $\mathbb{Q}^{t_p}$.
+Therefore, we take into consideration the effect to compute the expected value of $S_{a,b}(t_a)$ in a measure which is not its natural measure.
+Then, the convexity adjustment for a CMS is
 \begin{equation}
-\frac{dP(t,T)}{P(t,T)} = r_t dt - \nu(t,T)dW^{\mathbb{Q}}_t.  
+CA_{CMS}(t_p) = \mathbb{E}^{t_p}\left(S_{a,b}(t_a)\right) - S_{a,b}(0).
 \end{equation} 
-Therefore, if we apply Itô formula we have that 
-\begin{equation}\label{annuity_spot_dynamic}
-\frac{d01(t,t_a,t_b)}{01(t,t_a,t_b)} = r_t dt - \sigma_{01}(t,t_a,t_b)dW^{\mathbb{Q}}_t
-\end{equation}
-where 
-\begin{equation} \label{annuity_vol}
-\sigma_{01}(t,t_a,t_b) = \frac{\sum_{i=a+1}^{b} \delta_{i-1,i} P(t,t_i) \nu(t,t_i)}{01(t,t_a,t_b)}.
-\end{equation}
-From (\ref{annuity_vol}) and since $\frac{P_{ois}(t,T)}{01(t)}$ is a martingale, we have that
-\begin{equation*}
-dW^{01}_t = dW^{\mathbb{Q}}_t - \sigma_{01}(t,t_a,t_b)dt. 
-\end{equation*}
-Thwn can do the next approximation of (\ref{annuity_vol})
-\begin{equation} \label{approximation_o1_vol}
-\bar{\sigma}_{01}(t,t_a,t_b) \approx \sum_{i=a+1}^{b} w_i \nu(t,t_i,x_0,y_0)
-\end{equation}
-with $w_i=\frac{\delta_{i-1,i} P(0,T_i)}{01(0,t_a,t_b)}$. Now, if we use (\ref{short_rate_cheyette}) and the previous approximation we have that
+After some changes of measure, we can see that
 \begin{align}
-x_{t_a} &\approx \bar{x}_0(t_a)  + \int_{0}^{t_a} \exp\left(-\int_{s}^{t}k_u du\right) \bar{y}(u) du + \int_{0}^{t_a}  \exp\left(-\int_{s}^{t_a}k_u du \right) \eta(u,\bar{x}(u),\bar{y}(u)) dW_u^{\mathbb{Q}} \nonumber \\
-&=  \bar{x}_0(t)  + \int_{0}^{t_a} \exp\left(-\int_{s}^{t_a}k_u du\right) \bar{y}(u) du + \int_{0}^{t_a} \exp\left(-\int_{s}^{t_A}k_u du \right) \eta(u,\bar{x}(u),\bar{y}(u)) \bar{\sigma}_{01}(u, T_a, T_b) du  + \nonumber \\
-& \int_{0}^{t_a} \exp\left(-\int_{s}^{t_a}k_u du \right) \eta(u,\bar{x}(u),\bar{y}(u)) dW_u^{01} 
+\mathbb{E}^{t_p}\left(S_{a,b}(t_a)\right) &= \frac{1}{M(0,t_p)} \mathbb{E}^{01}\left(S_{a,b}(t_a) M(t_a,t_p)\right) \nonumber \\
+&= \frac{1}{M(0,t_p)} \mathbb{E}^{01}\left(S_{a,b}(t_a) \mathbb{E}^{01}\left( M(t_a,t_p)|S_{a,b}(t_a)\right) \right) \nonumber
 \end{align}
-Therefore, we have that
-\begin{align}
-\mathbb{E}^{01}\left(x_t\right) &\approx \bar{x}_0(t_a)  + \int_{0}^{t_a} \exp\left(-\int_{s}^{t_a}k_u du\right) \bar{y}(u) du \nonumber \\ 
-+ &\int_{0}^{t_a} \exp\left(-\int_{s}^{t_a}k_u du \right) \eta(u,\bar{x}(u),\bar{y}(u)) \bar{\sigma}_{01}(u, t_a, t_b) du
+with $M(t,t_p)= \frac{P_{ois}(t,t_p)}{01(t,t_a,t_p)}$.\\
+
+Then, we can approximate it by
+\begin{align}\label{expected_t_p_cms}
+\mathbb{E}^{t_p}\left(S_{a,b}(t_a)\right) &\approx  \frac{1}{M(0,t_p)} \mathbb{E}^{01}\left(S^{ois}_{a,b}(t_a) \mathbb{E}^{01}\left( M(t_a,t_p)|S_{a,b}(t_a)\right) \right) \\
+\qquad\qquad &+ \frac{\sum_{i=1}^{n_E}\delta_{t^{E}_{i-1}, t^{E}_i} \alpha(0,t^{E}_{i-1}, t^{E}_{i}) P_{ois}(0,t^{E}_{i})} {01(0,t_a,t_b)}.
 \end{align}
 
-\section{Approximation of $\mathbb{E}^{01}\left(D_s x_{t_a} \right)$}\label{approximation_under_annuity_measeure_d_s}
-Let us to remember that $\nu(t,t_i)=h(t,x_t,y_t) \frac{G(t,t_i)}{\beta_{t,k}}$ with  $\beta_{t,k} = \exp\left(\int_{0}^{t}k(u)\right)$. Then, we can do the next approximation 
-$$
-\nu(t,t_i) \approx \nu(t,t_i, \bar{x}_t, \bar{y}_t),
-$$ 
-therefore 
-\begin{equation*}
-D_s \nu(t,T_i) \approx  \partial_x \nu(t,T_i, \bar{x}_t, \bar{y}_t) D_s \bar{x}_t  \frac{G(t,t_i)}{\beta_{t,k}}
-\end{equation*}
-A cosequence of the last approximation is that 
-\begin{equation}
-D_s \sigma_{0,1}(t,t_a,t_b) \approx  D_s \bar{x}_t \mu(t,t_a,t_b)
+From the previous expression, we must note that under assumption of not stochastic basis, we must to compute the convexity adjustment for the OIS swap rate.
+But a complicated point is calculate the expected value
+\begin{equation}\label{Exp_M_conditional}
+\mathbb{E}^{01}\left( M(t_a,t_p)|S_{a,b}(t_a)\right).
 \end{equation}
-where 
-$$
-\mu(t,T_a,T_b) =  \sum_{i=a+1}^{b} w_i \partial_x \nu(t,t_i, \bar{x}_t, \bar{y}_t) \frac{G(t,t_i)}{\beta_{t,k}}.
-$$
-Now, if we use the last approximation and (\ref{approximation_o1_vol}) in (\ref{approximation_x_t_a}) together with the Girsanov's theorem, we have that
-\begin{align*}
-\bar{x}_{T_a} &\approx  \bar{x}_0(t_a)  + \int_{0}^{t_a} \exp\left(-\int_{s}^{t_a}k_u du\right) \bar{y}(u) du + \int_{0}^{t_a} \exp\left(-\int_{s}^{t_a}k_u du\right) \bar{\sigma}_{01}(u,t_a,t_b) du \nonumber \\\
-&+  \int_{0}^{t_a}  \exp\left(-\int_{s}^{t_a}k_u du \right) \eta(u,\bar{x}(u),\bar{y}(u)) dW_u^{\mathbb{Q}^{01}}.
-\end{align*}
-Therefore
-\begin{equation*}
-D_s \bar{x}_{t_a} \approx  \exp\left(-\int_{s}^{t_a}k_u du \right) \eta(s,\bar{x}_0,\bar{y}_{t_a})\bar{M}^{01}(s,t_a)
-\end{equation*}
-where
-\begin{align*}
-\bar{M}^{01}(s,t_a) &= \exp\left(-\int_{s}^{t_a} \left(\frac{\left(\partial_x \beta(u,T_a,\bar{x}_0,\bar{y}_{t_a})\right)^{2}}{2} + \exp\left(-\int_{u}^{t_a}k_u du\right)\eta(u,\bar{x}(u),\bar{y}(u) \mu(u,t_a,t_b) du \right)\right) \\
-&\exp\left(\int_{s}^{t_a} \partial_x \beta(u,t_a,\bar{x}_0,\bar{y}_{t_a}) dW^{\mathbb{Q}^{01}}_u \right)
-\end{align*}
-and $\beta(u,t_a,x,y) = \exp\left(-\int_{u}^{t_a}k_u du\right) \partial_x \eta(u,x,y)$. Therefore
+In order to reduce this complexity, it is a common practice to assume that $M(t_a,t_p)$ is a function of the swap rate $S_{a,b}(t_a)$, i.e   $M(t_a,t_p)=f(S_{a,b}(t_a))$.
+This assumption makes trivial to calculate \ref{Exp_M_conditional}.
+The function $f(\cdot)$ is known as mapping function.
+There is a vast literature about how to choose it (see \cite{AndreasenPiterbargIII} or \cite{Hagan20}).
+\\
 
-\begin{equation}\label{approximation_E_01_s_x_t}
-\mathbb{E}^{01}_s\left(D_s x_{t_a}\right) \approx \eta(s,\bar{x_0(s)},\bar{y}_{s}) \exp\left(-\int_{s}^{t_a}k_u du \right) \exp\left(-\int_{s}^{t_a} \exp\left(\int_{u}^{t_a}k_u du\right)\eta(u,\bar{x}(u),\bar{y}(u) \mu(u,t_a,t_b) du \right).
+We will do an approach without to specify any mapping function. If we apply Clark-Ocone formula to $M(t_a,t_p)$ we get that
+\begin{equation} \label{clark_ocone_swap_m}
+M(t_a,t_p) = M(0,t_p)+ \int_{0}^{t_a} \mathbb{E}_s^{01}\left(D_s M(t_a,t_p)\right) dW^{01}_s
 \end{equation}
+Then, if we substitute the last expressions in (\ref{expected_t_p_cms}) we have that
+\begin{align}\label{cms_first_order_convexity_prev}
+\mathbb{E}^{t_p}\left(S_{a,b}(t_a)\right) =& S^{ois}_{a,b}(0) + \frac{1}{M(0,t_p)} \mathbb{E}^{01}\left( S^{ois}_a,b(t_a) \int_{0}^{t_a} \mathbb{E}^{0,1}_s\left(D_sX_{t_a}\partial_x M(t_a,t_p)  \right) dW^{0,1}_s   \right) \nonumber \\
+=&  S^{ois}_{a,b}(0) + \frac{1}{M(0,t_p)} \mathbb{E}^{01}\left(\int_{0}^{t_a} D_s X_{t_a} \partial_x S_{a,b}(t_a) \mathbb{E}^{0,1}_s\left(D_sX_{t_a}\partial_x M(t_a,t_p)  \right) ds   \right).
+\end{align}
+The final approximation comes directly from \eqref{cms_first_order_convexity}
 

### 2023-03-14 Latex/paper-resum.tex
# last version of the paper

@@
 \begin{equation}\label{approximation_y_t}
-y(t) \approx \bar{y}(t):=\int_{0}^{t} \exp\left(-2\int_{u}^{t} k(w) dw \right) \eta^{2}(u,x(0),y(0)) du
+\bar{y}(t):=\int_{0}^{t} \exp\left(-2\int_{u}^{t} k(w) dw \right) \eta^{2}(u,x(0),y(0)) du
 \end{equation} 
@@
 \begin{eqnarray}
-X_{t_a} \approx \bar{X}(t_a):= \bar{x}_0(t_a)  &+& \int_{0}^{t_a} \exp\left(-\int_{s}^{t_a}k(u) du\right) \bar{y}(u) du \nonumber \\
+\bar{x}_{t_a}:= \bar{x}_0(t_a)  &+& \int_{0}^{t_a} \exp\left(-\int_{s}^{t_a}k(u) du\right) \bar{y}(u) du \nonumber \\
 &+& \int_{0}^{t_a}  \exp\left(-\int_{s}^{t_a}k(u) du \right) \eta(u,\bar{x}(u),\bar{y}(u)) dW_u^{\mathbb{Q}}   \label{approximation_x_t_a}
 \end{eqnarray}
-with initial condition $\bar{x}_{0}(t_a)$ is such a way that  
-\begin{equation*}
-S_{a,b}(t_a,\bar{x}_0(t_a), \bar{y}_{t_a}) = S_{a,b}(0).
-\end{equation*}
+with initial condition $\bar{x}_{0}(t_a)$ will be chosen appropriately depending on the case. In the appendix ($\cdots$), we can find the order of this approxiamtion.
 
@@
 \section{Auxiliary lemmas}
-\begin{lemma}\label{DsX}[Approximation $D_s x_{t_a}$]
+\begin{lemma}\label{DsX}[Approximation $D_s \bar{x}_{t_a}$]
 Given the Cheyette model in \eqref{short_rate_cheyette}, the hypothesis \ref{boundedness_volatility} and \ref{boundedness_reversion}, and considering the approximations in \eqref{approximation_y_t} and \eqref{approximation_x_t_a}.
@@
 \begin{equation}\label{approximation_D_s_x_t}
-D_sX_{t_a} \approx  \exp\left(-\int_{s}^{t_a}k_u du \right) \eta(s,\bar{x}_0(t_a),\bar{y}(t_a))\bar{M}(s,t_a)
+D_s \bar{x}_{t_a} = \exp\left(-\int_{s}^{t_a}k_u du \right) \eta(s,\bar{x}_s,\bar{y}_s)\bar{M}(s,t_a)
 \end{equation}
@@
 \begin{equation}\label{approsimation_E_s_x_t}
-\mathbb{E}_s^{t_p}\left(D_s x_{t_a}\right) \approx \eta(s,\bar{x}_0(s),\bar{y}_s) \exp\left(-\int_{s}^{t_a}k_u du \right) \exp\left(-\int_{s}^{t_a} \exp\left(-\int_{u}^{t_a}k_u du\right)\partial_x (\eta(u, \bar{x}_u, \bar{y}_{u}) \bar{\nu}(u,t_p)) du \right).
+\mathbb{E}_s^{t_p}\left(D_s \bar{x}_{t_a}\right) \eta(s,\bar{x}_s,\bar{y}_s) \exp\left(-\int_{s}^{t_a}k_u du \right) \mathbb{E}^{t_p}_s\left(\exp\left(-\int_{s}^{t_a} \exp\left(-\int_{u}^{t_a}k_u du\right)\partial_x (\eta(u, \bar{x}_u, \bar{y}_{u}) \bar{\nu}(u,t_p))|_{\bar{x}_u=\bar{x}_0(t_a)} du \right)\right).
 \end{equation}
@@
 \begin{proof}
-To get an approximation for $D_sX_{t_a}$ we must to avoid the recurrence in the Malliavin derivative of $X_{t_a}$.
-For that reason, we will use the approximations \eqref{approximation_y_t} and \eqref{approximation_x_t_a}.\\
-
 Using the relation 
 \begin{equation*}
-dW^{\mathbb{Q}^{t_p}} = dW^{\mathbb{Q}} + \bar{\nu}(t,t_p) dt \text{ where }\bar{\nu}(t,t_p) = \int_{t}^{t_p} \eta(s,\bar{x}_s,\bar{y}_s) ds,
+dW^{\mathbb{Q}^{t_p}} = dW^{\mathbb{Q}} + \bar{\nu}(t,t_p) dt
 \end{equation*}
-we will represent an approximation of $X_{t_a}$ under the measure $\mathbb{Q}^{t_p}$ 
+where $\bar{\nu}(t,t_p) = \int_{t}^{t_p} \eta(s,\bar{x}_s,\bar{y}_s) ds$.
+We must observe, that, we can approximate $x_s$ by $\mathbb{E}^{t_p}(x_s) = \bar{x}_0(t_p) + \mathcal{O}(\int_{0}^{s}\exp\left(-\int_{s}^{t_a}k_u du ds\right))$.
+Therefore, we can do the next approximation
+\begin{equation*}
+\bar{\nu}(t,t_p)\approx \int_{t}^{t_p} \eta(s,\bar{x}_0(t_p),\bar{y}_s) ds.
+\end{equation*}
+Then, we have that under the measure $\mathbb{Q}^{t_p}$ 
 \begin{align*}
-X_{t_a} \approx \bar{x}_0  &+ \int_{0}^{t_a} \exp\left(-\int_{s}^{t_a}k_u du\right) \bar{y}_s ds - \int_{0}^{t_a} \exp\left(-\int_{s}^{t_a}k_u du\right) \bar{\nu}(s, t_p) \eta(s,\bar{x}_s,\bar{y}_s) ds   \\
+\bar{x}_{t_a} = \bar{x}_0(t_a) &+ \int_{0}^{t_a} \exp\left(-\int_{s}^{t_a}k_u du\right) \bar{y}_s ds - \int_{0}^{t_a} \exp\left(-\int_{s}^{t_a}k_u du\right) \bar{\nu}(s, t_p) \eta(s,\bar{x}_s,\bar{y}_s) ds   \\
 &+ \int_{0}^{t_a}  \exp\left(-\int_{s}^{t_a}k_u du \right)\eta(s,\bar{x}_s,\bar{y}_s) dW_s^{\mathbb{Q}^{t_p}}. 
 \end{align*}
-\textcolor{red}{(Revisar)}
+Now, if we apply $D_s$ in above equality and we use the last approximation we have that
+\begin{equation*}
+\mathbb{E}_s(D_s \bar{x}_{t_a}) \approx \eta(s,\bar{x}_s,\bar{y}_s) \exp\left(-\int_{s}^{t_a}k_u du \right) \mathbb{E}^{t_p}_s\left(\exp\left(-\int_{s}^{t_a} \exp\left(-\int_{u}^{t_a}k_u du\right)\partial_x (\eta(u, \bar{x}_u, \bar{y}_{u}) \bar{\nu}(u,t_p))|_{\bar{x}_u=\bar{x}_0(t_a)} du \right)\right)
+\end{equation*}
 \end{proof}
 
-\subsection{Approximation of $\mathbb{E}_s^{\mathbb{Q}}\left(D_s x_{t_a}\right)$}
-Following the same procedure as before, we have that
-\begin{equation*}
-X_{t_a} \approx \bar{X}(T_a):= \bar{x}_0(t_a)  + \int_{0}^{t_a} \exp\left(-\int_{s}^{t_a}k_u du\right) \bar{y}(u) du + \int_{0}^{t_a}  \exp\left(-\int_{s}^{t_a}k_u du \right) \eta(u,\bar{x}(u),\bar{y}(u)) dW_u^{\mathbb{Q}}
-\end{equation*}
+\subsection{Approximation of $\mathbb{E}_s^{\mathbb{Q}}\left(D_s \bar{x}_{t_a}\right)$}
+As above appendix we have that
+\begin{align*}
+\bar{x}_{t_a} &= \bar{x}_0(t_a) + \int_{0}^{t_a} \exp\left(-\int_{s}^{t_a}k_u du\right) \bar{y}_u du + \int_{0}^{t_a} \exp\left(-\int_{s}^{t_a}k_u du \right) \eta(u,\bar{x}_u,\bar{y}_u) dW_u^{\mathbb{Q}}\\
+\end{align*}
 and therefore (see (\ref{approsimation_E_s_x_t}))
 \begin{equation}
-D_sX_{t_a} \approx  \exp\left(-\int_{s}^{t_a}k_u du \right) \eta(s,\bar{x}_0(t_a),\bar{y}_{T_a})\bar{M}(s,t_a)
+D_s \bar{x}_{t_a} =  \exp\left(-\int_{s}^{t_a}k_u du \right) \eta(s,\bar{x}_s,\bar{y}_{s})\bar{M}(s,t_a)
 \end{equation}
@@
 \begin{equation}\label{approximation_spot_E_s_x_t}
-\mathbb{E}^{\mathbb{Q}}_s\left(D_sX_{t_a} \right) \approx \exp\left(-\int_{s}^{t_a}k_u du \right) \eta(s,\bar{x}_0(t_a),\bar{y}_{t_a})
+\mathbb{E}^{\mathbb{Q}}_s\left(D_s \bar{x}_{t_a} \right)=\exp\left(-\int_{s}^{t_a}k_u du \right) \eta(s,\bar{x}_s,\bar{y}_{s})
 \end{equation}
+Therefore, we have that
+\begin{equation}\label{approximation_spot_E_s_x_t}
+\mathbb{E}^{\mathbb{Q}}_s\left(D_s \bar{x}_{t_a} \right)= \exp\left(-\int_{s}^{t_a}k_u du \right) \eta(s,\bar{x}_0(t_a),\bar{y}_{s}) + E(s)
+\end{equation}
+where $\mathbb{E}(E^{2}(s)) \sim \mathcal{O}(s)$ when $s \to 0$.
 
@@
 \end{align}
-The final approximation comes directly from \eqref{cms_first_order_convexity}
+The final ap
+From \eqref{cms_first_order_convexity_prev}, we can approximate \eqref{cms_first_order_convexity}.
 

### 2023-03-14 Latex/paper-resum.tex
# last version of the paper resume

@@
 
+\section{Basic introduction to Malliavin calculus}\label{sec:Malliavin}
+Malliavin calculus is an infinite-dimensional calculus in a Gaussian space, that is, a stochastic calculus of variations.
+In other words, this is a theory that provides a way to calculate the derivatives of random variables defined in a Gaussian probability space with respect to the underlying noise.
+The initial objective of Malliavin was the study of the existence of densities of Wiener functionals such as solutions of stochastic differential equations.
+But, nowadays, it has become an important tool in stochastic analysis due to the increase in its applications.
+Some of these applications include stochastic calculus for fractional Brownian motion, central limit theorems for multiple stochastic integrals, and an extension of the Itô formula for anticipative processes, but especially mathematical finance.
+For example, we can apply Mallaivin calculus for computing hedging strategies, Greeks, or obtain price approximations.
+See, for example, \cite{AlosLorite} or \cite{Nualart} for more general content.\\
+
+In our case, we are interested in using the Malliavin calculus to apply the Clark–Ocone representation theorem. But, first of all, let's introduce some basic concepts.\\
+
+Now, we introduce the derivative operator in the Malliavin calculus sense and the divergence operator to establish the notation that we use in the remainder of the paper.\\
+
+Consider $W=\left\{W_{t}, t\in \left[0,T\right]\right\}$ a Brownian motion defined on a complete probability space $\left(\Omega, \mathcal{F}, \mathbb{P}\right)$.
+Let $H=L^{2}(\left[0,T\right])$ and denote by
+\begin{eqnarray*}
+W_{t} := \int^{T}_{0} t_{s} \d W_{s},
+\end{eqnarray*}
+the It\^o integral of a deterministic function $h \in H$, also known as Wiener integral. Let $\mathcal{S}$ be the set of smooth random variables of the form
+\begin{eqnarray*}
+F=f\left(W_{t_{1}}, \ldots, W{t_{n}}\right)
+\end{eqnarray*}
+with $t_{1}, \ldots, t_{n} \in \left[0,T\right]$ and $f$ is infinitely differentiable bounded function.
+
+\medbreak
+
+The derivative of a random variable $F$, $D_{s}F$, is defined as the stochastic process given by
+\begin{eqnarray*}
+D_{s}F = \sum^{n}_{i=1} \frac{\partial f}{\partial x_{i}}\left(W_{t_{1}}, \ldots, W_{t_{n}}\right)1_{\left[0, t_{j}\right]}(s), \hspace{0.4cm} s \in \left[0,T\right].
+\end{eqnarray*}
+
+The iterated derivative operator of a random variable $F$ is defined by
+\begin{eqnarray*}
+D^{m}_{s_{1}, \ldots, s_{m}} F = D_{s_{1}} \cdots D_{s_{m}}F, \hspace{0.4cm} s_{1}, \ldots, s_{m} \in \left[0,T\right].
+\end{eqnarray*}
+
+\cite{Nualart} stated that these operators are closable from $L^{p}(\Omega)$ into $L^{p}(\Omega; L^{2}\left[0,T\right])$ for any $p\geq1$, and we denote by $\mathbb{D}^{n,p}$ the closure of $\mathcal{S}$ with respect to the norm
+\begin{eqnarray*}
+\left\|F\right\|_{n,p} := \left(E\left[F\right]^{p} + \sum^{n}_{i=1} E\left\|D^{i} F\right\|^{p}_{L^{2}\left(\left[0,T\right]^{i}\right)} \right)^{\frac{1}{p}}.
+\end{eqnarray*}
+
+\medbreak
+
+We define $\delta$ as the adjoint of derivative operator $D$, also referred to as the Skorohod integral.
+The domain of $\delta$, denoted by $Dom\text{ }\delta$, is the set of elements $u \in L^{2}([0,T] \times \Omega)$ such that there exists $\delta(u) \in L^{2}(\Omega)$ satisfying the duality relation
+\begin{eqnarray*}
+E\left[\delta(u) F \right] = E\left[\int^{T}_{0} \left(D_{s} F\right) u_{s} \d s\right].
+\end{eqnarray*}
+
+The operator $\delta$ is an extension of the Itô integral in the sense that the set $L^{2}_{a}([0,T] \times \Omega)$ of square integrable and adapted processes is included in $Dom\text{ }\delta$ and the operator $\delta$ restricted to $L^{2}_{a}([0,T] \times \Omega)$ coincides with the Itô stochastic integral.
+
+\medbreak
+
+For any $u \in Dom\text{ }\delta$, we will use the following notation
+\begin{eqnarray*}
+\delta(u)=\int^{T}_{0}u_{s}\d W_{s}.
+\end{eqnarray*}
+
+\medbreak
+
+The representation of functionals of Brownian motion by stochastic integrals, also known as martingale representation, has been widely studied over the years.
+It states that if $F$ is a square-integrable random variable, there exists a unique adapted process $\varphi$ in $L^{2}(\Omega \times \left[0,T\right]; \mathbb{R}^{d})$ such that
+\begin{eqnarray*}
+F=E\left[F\right] + \sum^{n}_{i=1}\int^{T}_{0} \varphi^{i}_{s} dW^{i}_{s}.
+\end{eqnarray*}
+In other words, there exists a unique martingale representation or, more precisely, the integrand $\varphi$ in the representation exists and is unique in $L^{2}(\Omega \times \left[0,T\right]; \mathbb{R}^{d})$.
+
+\medbreak
+
+Unfortunately, it is not easy to find an analytic representation of the process $\varphi$.
+Here, the Malliavin calculus helps us to find a solution.
+When the random variable $F$ is Malliavin differentiable, the process $\varphi$ appearing in It\^o's representation theorem, is given by
+\begin{eqnarray*}
+\varphi^{i}=E\left[D^{W^{i}}_{t}F|\mathcal{F}^{W}_{s}\right].
+\end{eqnarray*}
+In fact,
+\begin{eqnarray}\label{clark-okone}
+F=E\left[F\right] + \sum^{n}_{i=1}\int^{T}_{0} E\left[D^{W^{i}}_{t}F|\mathcal{F}^{W}_{s}\right] dW^{i}_{s}
+\end{eqnarray}
+is the Clark-Ocone representation formula.
+
 \section{Preliminaries and notation}\label{sec:Notation}
@@
 \end{eqnarray}
-with initial condition $\bar{x}_{0}(t_a)$ will be chosen appropriately depending on the case. In the appendix ($\cdots$), we can find the order of this approxiamtion.
+with initial condition $\bar{x}_{0}(t_a)$ will be chosen appropriately depending on the case.
+In the appendix \ref{estimation_error_l2} we can find the estimation for $\mathbb{E}((x_t-\bar{x}_t)^{2})$.
 
@@
 
-The hypotheses have been chosen for simplicity, but they can be replaced by suitable integrability conditions.\\
-
-Note, that under the hypothesis \eqref{boundedness_volatility}, $\partial_x \eta(t,x,y)$ and $\partial_y \eta(t,x,y)$ are bounded.
-
-\subsection{Notation}
-\textcolor{red}{(Falta pasteleo)}\\
-$\delta_{t_1,t_2}=t_2 -t_1$ is the year fraction between $t_1$ and $t_2$.
+The hypotheses have been chosen for simplicity, but they can be replaced by suitable integrability conditions.
+We should also note that under the hypothesis \eqref{boundedness_volatility}, $\partial_x \eta(t,x,y)$ and $\partial_y \eta(t,x,y)$ are bounded.
 
@@
 In this section, we derive the convexity adjustment for different products.
-The advantage of using the Malliavin calculus is that it allows us to derive a general representation formula .
+The advantage of using the Malliavin calculus, is that it allows us to derive a general representation formula for the convexity adjustmet Even, how we will see later, it is possible to get closed formulas for the convexity adjusment when the volatility of the Cheyette model is time dependent.
+
 In order to introduce a general idea of the method.
@@
 \subsection{OIS futures}
-In this section, we will derive the convexity adjustment for the overnight-indexed swap, also known as OIS.
-Given $t_0 < t_1$, we define \textcolor{red}{(qué es R y Ravg, tipo OIS y tipo OIS medio, nombre tecnico?)}
-\begin{align*}
-R(t_0,t_1) &:=\frac{1}{\delta_{t_0,t_1}} \left(\exp\left(\int_{t_0}^{t_1}r_{ois,u} du \right) - 1\right), \\
-R_{avg}(t_0,t_1) &:= \frac{1}{\delta_{t_0,t_1}}\int_{t_0}^{t_1}r_{ois,u} du.
-\end{align*}
-We observe that $R(\cdot,t_0,t_1)$ and $R_{avg}(\cdot,t_0,t_1)$  are not predictable and are only observable in $t_1$. However, 
+In this section, we will derive the convexity adjustment for short-term interest rate swap, also known as STIRs.
+It is common in the market to find two version of these futures, depending on how the fixings of the refrence index are using.
+Given $t_0 < t_1$, we will define the overnight compounding rate as
+\begin{equation*}
+R(t_0,t_1) :=\frac{1}{\delta_{t_0,t_1}} \left(\exp\left(\int_{t_0}^{t_1}r_{ois,u} du \right) - 1\right)
+\end{equation*}
+and the overnight average rate as
+\begin{equation*}
+R_{avg}(t_0,t_1) := \frac{1}{\delta_{t_0,t_1}}\int_{t_0}^{t_1}r_{ois,u} du.
+\end{equation*}
+We observe that both, $R(\cdot,t_0,t_1)$ and $R_{avg}(\cdot,t_0,t_1)$  are not predictable and are only observable in $t_1$. However, 
 $R(\cdot,t_0,t_1)$ and $R_{avg}(\cdot,t_0,t_1)$ are flows that will be payed in $t_1$.
@@
 
-Given $t_0\leq t_1$, we define \textcolor{red}{(qué es I, buscar nombre chulo)}
+To clarify the convexity expression and the calculations, we will define 
 \begin{equation*}
-I(t_0,t_1) := \int_{t_0}^{t_1} r_s ds.
+I(t_0,t_1) := \int_{t_0}^{t_1} r_{ois,s} ds.
 \end{equation*}
@@
 \end{theorem}
+with  $\Gamma(s,t_0,t_1)= \eta(s,x_0,y_0)\int_{\max(s, t_{0})}^{t_1} \exp\left( -\int_{s}^{u} k_{s^{\prime}} ds^{\prime}\right)du$
 \begin{proof}
@@
 \end{proof}
+
+\begin{remark}
+We must note that (\ref{convexity_ois_future}) and (\ref{convexity_avg_ois_future}) are exact when $\eta(t,x_t, y_t)$ is only a time dependent function, how is the case of a Hull-White model.
+\end{remark}
 
@@
 &+ \frac{\sigma^{2}}{2k^{2}} \left(\frac{\exp(-2kt_0) - \exp(-2kt_1)}{2k}  + \exp(-kt0)t0 - 2 \frac{\exp(-2kt_0) - \exp(-k(t_0 + t_1))}{k}  \right)
-\end{align*} \textcolor{red}{(we have to review this integral), Poner abreviado, calculo apendice}\\
+\end{align*}
 Then, if we substitute the last equalities in (\ref{convexity_ois_future}) we get an approximation for OIS future at $t=0$.\\
@@
 \begin{align}\label{cms_first_order_convexity}
-\mathbb{E}^{t_p}\left(S_{a,b}(t_a)\right) \approx  S^{ois}_{a,b}(0) &+ \frac{\partial_x S^{ois}_{a,b}(t_a, \bar{x}_0(t_a),\bar{y}(t_a))\partial_x M(t_a,t_p, \bar{x}_0(t_a),\bar{y}(t_a))}{M(0,t_p)} \nonumber \\
-\qquad\qquad &\cdot \mathbb{E}^{0,1}\left( \int_{0}^{t_a} \left(\mathbb{E}_s^{0,1}\left( D_s x_{t_a}\right)\right)^{2} ds  \right)
+\mathbb{E}^{t_p}\left(S_{a,b}(t_a)\right) &\approx  S^{ois}_{a,b}(0) + \frac{\partial_x S_{a,b}(t_a,\bar{x}_0(t_a), \bar{y}_0) \partial_x M(t_a,t_p,\bar{x}_0(t_a), \bar{y}_0)} \nonumber \\
+&\cdot \int_{0}^{t_a}  \beta^2(s,t_a,\bar{x}_0(t_a),\bar{y}_s) \exp\left(-2\int_{s}^{t_a}\beta(u,t_a,\bar{x}_{0}(t_a),\bar{y}_u) \mu(u,t_a,t_b) du \right)ds 
 \end{align}
-Then, the convexity adjustment approximation for CMS is
+with  $\beta(u,t_a,x,y) = \exp\left(-\int_{u}^{t_a}k_u du\right)\eta(u,x,y)$. Then, the convexity adjustment approximation for CMS is
 \begin{equation}
@@
 \section{Conclusions}\label{sec:Conclusion}
+In the present paper, we have shown how we can use Malliavin calculus to find the convexity adjustment for several typical interest rate products.
+We have seen, that Malliavin calculus provides us with a simple way to get a template for the convexity adjustment of several products under a general Cheyette model dynamic with one factor.
+The method is extrapolated with little effort to a Cheyette model with stochastic volatility, or even a  Cheyette model with several factors.
+We have also seen, the good accuracy of the formulas that we have got using this method.
 
@@
 With $\beta(u,t_a,x,y) = \exp\left(-\int_{u}^{t_a}k_u^{\prime} du^{\prime}\right) \partial_x \eta(u,x,y)$. Therefore, we have that
-\begin{equation}\label{approsimation_E_s_x_t}
-\mathbb{E}_s^{t_p}\left(D_s \bar{x}_{t_a}\right) \eta(s,\bar{x}_s,\bar{y}_s) \exp\left(-\int_{s}^{t_a}k_u du \right) \mathbb{E}^{t_p}_s\left(\exp\left(-\int_{s}^{t_a} \exp\left(-\int_{u}^{t_a}k_u du\right)\partial_x (\eta(u, \bar{x}_u, \bar{y}_{u}) \bar{\nu}(u,t_p))|_{\bar{x}_u=\bar{x}_0(t_a)} du \right)\right).
-\end{equation}
+\begin{align}\label{approsimation_E_s_x_t}
+\mathbb{E}_s^{t_p}\left(D_s \bar{x}_{t_a}\right) &\approx \eta(s,\bar{x}_s,\bar{y}_s) \exp\left(-\int_{s}^{t_a}k_u du \right) \nonumber  \\
+&\cdot \mathbb{E}^{t_p}_s\left(\exp\left(-\int_{s}^{t_a} \exp\left(-\int_{u}^{t_a}k_u du\right)\partial_x (\eta(u, \bar{x}_u, \bar{y}_{u}) \bar{\nu}(u,t_p))|_{\bar{x}_u=\bar{x}_0(t_a)} du \right)\right).
+\end{align}
 \end{lemma}
@@
 Now, if we apply $D_s$ in above equality and we use the last approximation we have that
+\begin{align*}
+\mathbb{E}_s(D_s \bar{x}_{t_a}) &\approx \eta(s,\bar{x}_s,\bar{y}_s) \exp\left(-\int_{s}^{t_a}k_u du \right)\\ &\cdot \mathbb{E}^{t_p}_s\left(\exp\left(-\int_{s}^{t_a} \exp\left(-\int_{u}^{t_a}k_u du\right)\partial_x (\eta(u, \bar{x}_u, \bar{y}_{u}) \bar{\nu}(u,t_p))|_{\bar{x}_u=\bar{x}_0(t_a)} du \right)\right)
+\end{align*}
+\end{proof}
+\subsection{Estimation of $\mathbb{E}_s^{\mathbb{Q}}\left((x_t - \bar{x}_{t})^{2}\right)$}\label{estimation_error_l2}
+In order to get the order of the aproximation, we will use the ideas of the paper \cite{B-G-M-2008}.
+Basically, we will define a parametrization of the process $x_{t,\epsilon}$ e $y_{t,\epsilon}$ with $\epsilon \in [0,1]$.
+The role of $\epsilon$ is only as interpolator parameter between process.
+We will suppose the next parametrization of the Cheyette model
+\begin{align}\label{parametric_process}
+y_{\epsilon,t} &= \int_{0}^{t} \exp\left(-2 \int_{u}^{t} k(u^{\prime}) du^{\prime}\right) \epsilon^{2} \eta^{2}(u,x_{\epsilon,u},y_{\epsilon,u}) du \\
+x_{\epsilon, t} &= \int_{0}^{t} \exp\left(-\int_{u}^{t} k(u^{\prime}) du^{\prime}\right) \bar{y}_{\epsilon,u} du + \int_{0}^{t} \exp\left(-\int_{u}^{t} k(u^{\prime}) du^{\prime}\right) \epsilon \eta(u,x_{\epsilon,u},y_{\epsilon,u})  \bar{y}_u du
+\end{align}
+The reason of $\epsilon^{2}$ in $y_{\epsilon,t}$ is because $\mathbb{E}\left(y_t\right)= \mathbb{V}ar(x_t)$.
+Then, if the scale of $x_{\epsilon,t}$ is $\epsilon$ then the scale of $y_{\epsilon,t}$ must be $\epsilon^{2}$.
+We will start with the estimation of $\mathbb{E}((y_t - \bar{y}_t)^{2})$.
+We will define the next parametrization for $\nu in [0,1]$
 \begin{equation*}
-\mathbb{E}_s(D_s \bar{x}_{t_a}) \approx \eta(s,\bar{x}_s,\bar{y}_s) \exp\left(-\int_{s}^{t_a}k_u du \right) \mathbb{E}^{t_p}_s\left(\exp\left(-\int_{s}^{t_a} \exp\left(-\int_{u}^{t_a}k_u du\right)\partial_x (\eta(u, \bar{x}_u, \bar{y}_{u}) \bar{\nu}(u,t_p))|_{\bar{x}_u=\bar{x}_0(t_a)} du \right)\right)
+z^{\nu}_{u} = \eta^{2}(u, \nu x_u, \nu y_u).
 \end{equation*}
-\end{proof}
+Then we have that $z^{1}_{u} = \eta(u,x_u,y_u$ y $z^{0}_{u} = \eta(u,0,0)$. Therefore
+\begin{align*}
+\eta^{2}(u, x_u, y_u) &= \eta^{2}(u, 0, 0) + \int_{0}^{1} \partial_{\nu}z^{nu}_{u} d\nu \\ 
+&=  \eta^{2}(u, 0, 0) + 2 \int_{0}^{1} \eta(u, \nu x_u, \nu y_u)   \nabla_{x,y}\eta(u, \nu x_u, \nu y_u) \cdot (x_u, y_u) d\nu.
+\end{align*}
+Then we have that
+\begin{equation*}
+y_t = \bar{y}_t + E_{y}(t)
+\end{equation*}
+with 
+$$
+E_{y}(t)= 2 \int_{0}^{t} \exp\left(- 2\int_{u}^{t} k(u^{\prime}) du^{\prime}\right)  \int_{0}^{1} \eta(u, \nu x_u, \nu y_u)   \nabla_{x,y}\eta(u, \nu x_u, \nu y_u) \cdot (x_u, y_u) d\nu du
+$$
+Now, from Cauchy-Schwarz inequality we have that
+\begin{align} \label{upper_bound_E_y}
+\mathbb{E}((E_{y}(t))^{2}) &\leq 4 \mathbb{E}\left(\int_{0}^{t} \exp\left(-4 \int_{u}^{t} k(u^{\prime}) du^{\prime}\right)  \left(\int_{0}^{1} \eta(u, \nu x_u, \nu y_u)   \|\nabla_{x,y}\eta(u, \nu x_u, \nu y_u)\|^{2} \|(x_u, y_u)\| d\nu \right)^2 du \right) ^{2}\nonumber \\
+&\leq 4 \|\eta\|^{2}_{\infty} \max(\|\partial_x\eta\|^{2}_{\infty},\partial_y\|\eta\|^{2}_{\infty} ) \int_{0}^{t} \mathbb{E}\left( \|(x_u, y_u)\|^{2}\right) du = M^{y}_k \int_{0}^{t} \mathbb{E}\left( \|(x_u, y_u)\|^{2}\right) du
+\end{align}
+The next step is to estimate $\mathbb{E}((x_t - \bar{x}_t)^{2})$. From the definition of $x_t$, we have that
+\begin{equation*}
+x_t = \int_{0}^{t} \exp\left(- \int_{u}^{t} k(u^{\prime}) du^{\prime}\right) \bar{y}_u du + \int_{0}^{t} \exp\left(- \int_{u}^{t} k(u^{\prime}) du^{\prime}\right) E{y}(u) du + \int_{0}^{t} \eta(t,x_u,y_u) dW_u.
+\end{equation*}
+In order, to find a expansion of $\eta(t,x_u,y_u)$ centrered in $\bar{y}_u$, we will define $z^{\nu}_{u} = (1-\nu)\bar{y}_{u} + \nu y_u$. Then
+\begin{equation*}
+\eta(t,x_u,y_u) = \eta(t,x_u,\bar{y}_u) + \int_{0}^{1}\partial_y\eta(t,x_u,z^{\nu}_{u}) E_{y}(u) d\nu
+\end{equation*}
+We will define $E_{x}(u) = \int_{0}^{1}\partial_y\eta(t,x_u,z^{\nu}_{u}) E_{y}(u) d\nu$. Then we have the next representation of $x_t$
+\begin{equation*}
+x_t = \bar{x}_t + \int_{0}^{t} \exp\left(- \int_{u}^{t} k(u^{\prime}) du^{\prime}\right) E_{y}(u) du + \int_{0}^{t} \exp\left(- \int_{u}^{t} k(u^{\prime}) du^{\prime}\right) E_{x}(u) dW_u.
+\end{equation*}
+We must note that
+\begin{equation*}
+ \mathbb{E}((E_x(u))^{2}) \leq \|\partial_y \eta \|^{2}_{\infty} \mathbb{E}((E_{y}(u))^{2})   
+\end{equation*}
+Tne using \ref{upper_bound_E_y} we get that
+\begin{equation}\label{upper_bound_E_x}
+ \mathbb{E}((E_x(u))^{2}) \leq 4 \|\eta\|^{2}_{\infty} \|\partial_y \eta\|^{2}_{\infty} \max(\|\partial_x\eta\|^{2}_{\infty},\partial_y\|\eta\|^{2}_{\infty} ) \int_{0}^{u} \mathbb{E}\left( \|(x_s, y_s)\|^{2}\right) ds
+\end{equation}
+Then from (\ref{upper_bound_E_x}) and (\ref{upper_bound_E_y}) we get that 
+\begin{align*}
+\mathbb{E}((x_t - \bar{x}_t)^{2}) & \leq 2 \mathbb{E}\left( \int_{0}^{t} \exp\left(- \int_{u}^{t} k(u^{\prime}) du^{\prime}\right) E_{y}(u) du    \right)^2 + \mathbb{E}\left( \int_{0}^{t} \exp\left(- \int_{u}^{t} k(u^{\prime}) du^{\prime}\right) E_{x}(u) dW_u\right)^{2} \\
+&\leq 2 \mathbb{E}\int_{0}^{t} \exp\left(- 2\int_{u}^{t} k(u^{\prime}) du^{\prime}\right) \mathbb{E}(E^{2}_{y}(u)) du + \int_{0}^{t} \exp\left(- 2\int_{u}^{t} k(u^{\prime}) du^{\prime}\right) \mathbb{E}(E^{2}_{x}(u)) du
+\end{align*}
+Them if we join each part, we have that for an adequate constant $M^{x}_k$ 
+\begin{equation*}
+\mathbb{E}((x_t - \bar{x}_t)^{2}) \leq M^{x}_k \int_{0}^{t} \exp\left(- 2\int_{u}^{t} k(u^{\prime}) du^{\prime}\right) \mathbb{E}\left( \|(x_u, y_u)\|^{2}\right) du 
+\end{equation*}
+To end, only we have to estimate $\mathbb{E}\left( \|(x_s, y_s)\|^{2}\right)$.
+We will start with $\mathbb{E}(y^{2}_u)$.From the definition of $y_t$ and since $\|\eta\|_{\infty} < \infty$, we have that
+\begin{equation*}
+\mathbb{E}(y^{2}_u) \leq \|\eta\|^{2}_{\infty} \int_{0}^{u} \exp\left(- 2\int_{s}^{u} k(u^{\prime}) du^{\prime}\right) ds.
+\end{equation*}
+We must note that at the short term and under asummptions (\ref{boundedness_reversion}) we have that
+\begin{equation*}
+\lim_{t \to 0} \mathbb{E}(y^{2}_u) = \|\eta\|^{2}_{\infty} t
+\end{equation*}
+and 
+\begin{equation*}
+\lim_{t \to \infty} \mathbb{E}(y^{2}_u) < \infty.
+\end{equation*}
+Now $\mathbb{E}(x^{2}_u)$. From the definition of $x_t$ and using $(a+b)^2 \leq 2(a^{2}+ b^{2})$ we have that
+\begin{align*}
+\mathbb{E}(x^{2}_u) &\leq 2 \mathbb{E}\left(\int_{0}^{u} \exp\left(- \int_{s}^{u} k(u^{\prime}) du^{\prime}\right) y_s  ds \right)^{2} +  2 \mathbb{E}\left(\int_{0}^{u} \exp\left(- \int_{s}^{u} k(u^{\prime}) du^{\prime}\right) \eta(s,x_s,y_s)  dW_s \right)^{2} \nonumber \\
+&\leq 2 \int_{0}^{u} \exp\left(- 2\int_{s}^{u} k(u^{\prime}) du^{\prime}\right) \mathbb{E}\left(y_s\right)^{2} ds + 2 \int_{0}^{u} \exp\left(- 2 \int_{s}^{u} k(u^{\prime}) du^{\prime}\right) \mathbb{E}\left(\eta^{2}(s,x_s,y_s)\right) ds \\
+&\leq 2 \|\eta\|_{\infty} \int_{0}^{u} \exp\left(- 2\int_{s}^{u} k(u^{\prime}) du^{\prime}\right) \int_{0}^{s}  \exp\left(- 2\int_{s_1}^{s} k(u^{\prime}) du^{\prime}\right) ds_1 ds +  2 \|\eta\|_{\infty} \int_{0}^{u} \exp\left(- 2\int_{s}^{u} k(u^{\prime}) du^{\prime}\right) ds
+\end{align*}
+Then as before at the short term
+$$
+\lim_{t \to 0} \mathbb{E}(x^{2}_u) = 2\|\eta\|^{2}_{\infty} t
+$$
+and when ($u \to \infty$) we have that $\mathbb{E}(x^{2}_u)$ remains bounded. Then, if we use the above inequalities 
+\begin{align*}
+\mathbb{E}((y_t - \bar{y}_t)^{2}) &\leq M^{y}_k \int_{0}^{t}  \exp\left(- 2\int_{u}^{t} k(u^{\prime}) du^{\prime}\right)  \int_{0}^{u} \exp\left(- 2\int_{s}^{u} k(u^{\prime}) du^{\prime}\right) ds du
+\end{align*}
+and
+\begin{align*}
+\mathbb{E}((x_t - \bar{x}_t)^{2}) &\leq 2 M^{x}_k \|\eta\|_{\infty} \int_{0}^{t} \exp\left(- 2\int_{u}^{t} k(u^{\prime}) du^{\prime}\right)   \int_{0}^{u} \exp\left(- 2\int_{s}^{u} k(u^{\prime}) du^{\prime}\right) \int_{0}^{s}  \exp\left(- 2\int_{s_1}^{s} k(u^{\prime}) du^{\prime}\right) ds_1 ds du \\
+&+ (2 M^{x}_K \|\eta\|_{\infty} + 1) \int_{0}^{t}  \exp\left(- 2\int_{u}^{t} k(u^{\prime}) du^{\prime}\right)  \int_{0}^{u} \exp\left(- 2\int_{s}^{u} k(u^{\prime}) du^{\prime}\right) ds du
+\end{align*}
 
@@
 where $\mathbb{E}(E^{2}(s)) \sim \mathcal{O}(s)$ when $s \to 0$.
+
+\subsection{Approximation of $\mathbb{E}^{01}\left(\bar{x}_{t_a}\right)$}
+It is easy to show that the dynamic of the bond under HJM assumption is
+\begin{equation}
+\frac{dP(t,T)}{P(t,T)} = r_t dt - \nu(t,T)dW^{\mathbb{Q}}_t.  
+\end{equation}
+Therefore, if we apply Itô formula we have that 
+\begin{equation}\label{annuity_spot_dynamic}
+\frac{d01(t,t_a,t_b)}{01(t,t_a,t_b)} = r_t dt - \sigma_{01}(t,t_a,t_b)dW^{\mathbb{Q}}_t
+\end{equation}
+where 
+\begin{equation} \label{annuity_vol}
+\sigma_{01}(t,t_a,t_b) = \frac{\sum_{i=a+1}^{b} \delta_{i-1,i} P(t,t_i) \nu(t,t_i)}{01(t,t_a,t_b)}.
+\end{equation}
+From (\ref{annuity_vol}) and since $\frac{P_{ois}(t,T)}{01(t)}$ is a martingale, we have that
+\begin{equation*}
+dW^{01}_t = dW^{\mathbb{Q}}_t - \sigma_{01}(t,t_a,t_b)dt. 
+\end{equation*}
+Thwn can do the next approximation of (\ref{annuity_vol})
+\begin{equation} \label{approximation_o1_vol}
+\bar{\sigma}_{01}(t,t_a,t_b) \approx \sum_{i=a+1}^{b} w_i \nu(t,t_i,x_0,y_0)
+\end{equation}
+with $w_i=\frac{\delta_{i-1,i} P(0,T_i)}{01(0,t_a,t_b)}$. Now, if we use (\ref{short_rate_cheyette}) and the previous approximation we have that
+\begin{align}
+\bar{x}_{t_a} &\approx \bar{x}_0(t_a)  + \int_{0}^{t_a} \exp\left(-\int_{s}^{t}k_u du\right) \bar{y}(u) du + \int_{0}^{t_a}  \exp\left(-\int_{s}^{t_a}k_u du \right) \eta(u,\bar{x}(u),\bar{y}(u)) dW_u^{\mathbb{Q}} \nonumber \\
+&=  \bar{x}_0(t)  + \int_{0}^{t_a} \exp\left(-\int_{s}^{t_a}k_u du\right) \bar{y}(u) du + \int_{0}^{t_a} \exp\left(-\int_{s}^{t_A}k_u du \right) \eta(u,\bar{x}(u),\bar{y}(u)) \bar{\sigma}_{01}(u, T_a, T_b) du  + \nonumber \\
+& \int_{0}^{t_a} \exp\left(-\int_{s}^{t_a}k_u du \right) \eta(u,\bar{x}(u),\bar{y}(u)) dW_u^{01} 
+\end{align}
+Therefore, we have that
+\begin{align}
+\mathbb{E}^{01}\left(\bar{x}_t\right) &\approx \bar{x}_0(t_a)  + \int_{0}^{t_a} \exp\left(-\int_{s}^{t_a}k_u du\right) \bar{y}(u) du \nonumber \\ 
++ &\int_{0}^{t_a} \exp\left(-\int_{s}^{t_a}k_u du \right) \eta(u,\bar{x}(u),\bar{y}(u)) \bar{\sigma}_{01}(u, t_a, t_b) du
+\end{align}
+
+\subsection{Approximation of $\mathbb{E}^{01}\left(D_s \bar{x}_{t_a} \right)$}\label{approximation_under_annuity_measeure_d_s}
+Let us to remember that $\nu(t,t_i)=h(t,\bar{x}_t,\bar{y}_t) \frac{G(t,t_i)}{\beta_{t,k}}$ with  $\beta_{t,k} = \exp\left(\int_{0}^{t}k(u)\right)$.
+Therefore 
+\begin{equation*}
+D_s \nu(t,T_i) = \partial_x \nu(t,T_i, \bar{x}_t, \bar{y}_t) D_s \bar{x}_t  \frac{G(t,t_i)}{\beta_{t,k}}.
+\end{equation*}
+Then we have that
+\begin{equation}
+D_s \sigma_{0,1}(t,t_a,t_b) \approx  D_s \bar{x}_t \mu(t,t_a,t_b)
+\end{equation}
+where 
+$$
+\mu(t,T_a,T_b) =  \sum_{i=a+1}^{b} w_i \partial_x \nu(t,t_i, \bar{x}_t, \bar{y}_t) \frac{G(t,t_i)}{\beta_{t,k}}.
+$$
+Now, if we use the last approximation and (\ref{approximation_o1_vol}) in (\ref{approximation_x_t_a}) together with the Girsanov's theorem, we have that
+\begin{align*}
+\bar{x}_{T_a} &\approx  \bar{x}_0(t_a)  + \int_{0}^{t_a} \exp\left(-\int_{s}^{t_a}k_u du\right) \bar{y}(u) du + \int_{0}^{t_a} \exp\left(-\int_{s}^{t_a}k_u du\right) \bar{\sigma}_{01}(u,t_a,t_b) du \nonumber \\\
+&+  \int_{0}^{t_a}  \exp\left(-\int_{s}^{t_a}k_u du \right) \eta(u,\bar{x}(u),\bar{y}(u)) dW_u^{\mathbb{Q}^{01}}.
+\end{align*}
+Therefore
+\begin{equation*}
+D_s \bar{x}_{t_a} \approx  \exp\left(-\int_{s}^{t_a}k_u du \right) \eta(s,\bar{x}_0,\bar{y}_{t_a})\bar{M}^{01}(s,t_a)
+\end{equation*}
+where
+\begin{align*}
+\bar{M}^{01}(s,t_a) &= \exp\left(-\int_{s}^{t_a} \left(\frac{\left(\partial_x \beta(u,T_a,\bar{x}_0,\bar{y}_{t_a})\right)^{2}}{2} + \exp\left(-\int_{u}^{t_a}k_u du\right)\eta(u,\bar{x}(u),\bar{y}(u) \mu(u,t_a,t_b) du \right)\right) \\
+&\exp\left(\int_{s}^{t_a} \partial_x \beta(u,t_a,\bar{x}_0,\bar{y}_{t_a}) dW^{\mathbb{Q}^{01}}_u \right)
+\end{align*}
+and $\beta(u,t_a,x,y) = \exp\left(-\int_{u}^{t_a}k_u du\right)\eta(u,x,y)$. Then
+
+\begin{align}\label{approximation_E_01_Ds_x_t}
+\mathbb{E}^{01}_s\left(D_s \bar{x}_{t_a}\right) &\approx \beta(s,t_a,\bar{x}_s,\bar{y}_s)  \mathbb{E}_s^{01}\left(\exp\left(-\int_{s}^{t_a}\beta(u,t_a,\bar{x}_u,\bar{y}_u) \mu(u,t_a,t_b) du \right)\right) \nonumber \\
+&\approx \beta(s,t_a,\bar{x}_s,\bar{y}_s) \exp\left(-\int_{s}^{t_a}\beta(u,t_a,\bar{x}_{0}(t_a),\bar{y}_u) \mu(u,t_a,t_b) du \right)
+\end{align}
 
@@
 \begin{align}\label{cms_first_order_convexity_prev}
-\mathbb{E}^{t_p}\left(S_{a,b}(t_a)\right) =& S^{ois}_{a,b}(0) + \frac{1}{M(0,t_p)} \mathbb{E}^{01}\left( S^{ois}_a,b(t_a) \int_{0}^{t_a} \mathbb{E}^{0,1}_s\left(D_sX_{t_a}\partial_x M(t_a,t_p)  \right) dW^{0,1}_s   \right) \nonumber \\
-=&  S^{ois}_{a,b}(0) + \frac{1}{M(0,t_p)} \mathbb{E}^{01}\left(\int_{0}^{t_a} D_s X_{t_a} \partial_x S_{a,b}(t_a) \mathbb{E}^{0,1}_s\left(D_sX_{t_a}\partial_x M(t_a,t_p)  \right) ds   \right).
+\mathbb{E}^{t_p}\left(S_{a,b}(t_a)\right) =& S^{ois}_{a,b}(0) + \frac{1}{M(0,t_p)} \mathbb{E}^{01}\left( S^{ois}_{a,b}(t_a) \int_{0}^{t_a} \mathbb{E}^{0,1}_s\left(D_s x_{t_a}\partial_x M(t_a,t_p)  \right) dW^{0,1}_s   \right) \nonumber \\
+=&  S^{ois}_{a,b}(0) + \frac{1}{M(0,t_p)} \mathbb{E}^{01}\left(\int_{0}^{t_a} D_s x_{t_a} \partial_x S_{a,b}(t_a) \mathbb{E}^{0,1}_s\left(D_s x_{t_a}\partial_x M(t_a,t_p)  \right) ds   \right)
 \end{align}
-The final ap
+Now if we use (\ref{approximation_E_01_Ds_x_t}) we have that
+\begin{align}
+\mathbb{E}^{t_p}\left(S_{a,b}(t_a)\right) &\approx  S^{ois}_{a,b}(0) + \frac{\partial_x S_{a,b}(t_a,\bar{x}_0(t_a), \bar{y}_0) \partial_x M(t_a,t_p,\bar{x}_0(t_a), \bar{y}_0)} \nonumber \\
+&\cdot \int_{0}^{t_a}  \beta^2(s,t_a,\bar{x}_0(t_a),\bar{y}_s) \exp\left(-2\int_{s}^{t_a}\beta(u,t_a,\bar{x}_{0}(t_a),\bar{y}_u) \mu(u,t_a,t_b) du \right)ds 
+\end{align}
+
 From \eqref{cms_first_order_convexity_prev}, we can approximate \eqref{cms_first_order_convexity}.

### 2023-03-18 Latex/paper-resum.tex
# last version

@@
 Then, the convexity adjustment approximation for FRAs in Arrears is
-\begin{align}\label{ca_approximations_fra_arrears}
-CA(t_0,t_1) \approx  \frac{G(t_1,t_2)}{\delta_{t_1,t_2}P_{E}(0,t_1,t_2)} \int_{0}^{t_1}& \beta(s,t_1, x_0, \bar{y}_s) \exp\left(-\int_{s}^{t_1} \partial_x \beta(u,t_1,x_0,y_0) \nu(u,t_2) du \right) \nonumber\\
-\qquad\qquad &\cdot \left(\nu(s,t_2) - \nu(s,t_1)\right) ds.
-\end{align}
+\begin{equation}\label{ca_approximations_fra_arrears}
+CA(t_0,t_1) \approx   \frac{G(t_1,t_2)}{\delta_{t_1,t_2}P_{E}(0,t_1,t_2)} \beta(s,t_1, \bar{x}_0(t_1), \bar{y}_s) \int_{0}^{t_1} \bar{DM}(s,t_1) (\bar{\nu}(s,t_2,\bar{x}_{0}(t_1))-\bar{\nu}(s,t_1,\bar{x}_{0}(t_1))) ds
+\end{equation}
 \end{theorem}
@@
 \begin{equation}\label{approximation_D_s_x_t}
-D_s \bar{x}_{t_a} = \exp\left(-\int_{s}^{t_a}k_u du \right) \eta(s,\bar{x}_s,\bar{y}_s)\bar{M}(s,t_a)
+D_s \bar{x}_{t_a} = \beta(s,t_a,\bar{x}_s,\bar{y}_s) \bar{M}(s,t_a)
 \end{equation}
@@
 \end{align*}
-With $\beta(u,t_a,x,y) = \exp\left(-\int_{u}^{t_a}k_u^{\prime} du^{\prime}\right) \partial_x \eta(u,x,y)$. Therefore, we have that
+With $\beta(u,t_a,x,y) = \exp\left(-\int_{u}^{t_a}k_u^{\prime} du^{\prime}\right) \partial_x \eta(u,x,y)$. Then, we have that
 \begin{align}\label{approsimation_E_s_x_t}
-\mathbb{E}_s^{t_p}\left(D_s \bar{x}_{t_a}\right) &\approx \eta(s,\bar{x}_s,\bar{y}_s) \exp\left(-\int_{s}^{t_a}k_u du \right) \nonumber  \\
-&\cdot \mathbb{E}^{t_p}_s\left(\exp\left(-\int_{s}^{t_a} \exp\left(-\int_{u}^{t_a}k_u du\right)\partial_x (\eta(u, \bar{x}_u, \bar{y}_{u}) \bar{\nu}(u,t_p))|_{\bar{x}_u=\bar{x}_0(t_a)} du \right)\right).
-\end{align}
+\mathbb{E}_s^{t_p}\left(D_s \bar{x}_{t_a}\right) &\approx \beta(s,t_a,\bar{x}_s,\bar{y}_s) \bar{DM}(s,t_a).
+\end{align}
+where 
+\begin{align*}
+\bar{DM}(s,t_a) &= \mathbb{E}^{t_p}_s\left(\exp\left(-\int_{s}^{t_a} \exp\left(-\int_{u}^{t_a}k_u du\right)\partial_x \eta(u, \bar{x}_0(t_a), \bar{y}_{u}) \bar{\nu}(u,t_p, \bar{x}_0(t_a)) \right.
+\right.
+\\
+&+ \left. \left. \eta(u,\bar{x}_0(t_a), \bar{y}_{u})) \partial_x \bar{\nu}(t,t_p, \bar{x}_0(t_a)) du \right)\right) 
+\end{align*}
 \end{lemma}
@@
 \end{equation*}
-where $\bar{\nu}(t,t_p) = \int_{t}^{t_p} \eta(s,\bar{x}_s,\bar{y}_s) ds$.
-We must observe, that, we can approximate $x_s$ by $\mathbb{E}^{t_p}(x_s) = \bar{x}_0(t_p) + \mathcal{O}(\int_{0}^{s}\exp\left(-\int_{s}^{t_a}k_u du ds\right))$.
-Therefore, we can do the next approximation
-\begin{equation*}
-\bar{\nu}(t,t_p)\approx \int_{t}^{t_p} \eta(s,\bar{x}_0(t_p),\bar{y}_s) ds.
-\end{equation*}
+where $\bar{\nu}(t,t_p) = \int_{t}^{t_p} \eta(s,\bar{x}_s,\bar{y}_s) ds$. We must observe, that we can approximate $x_s$ by 
+$$
+\mathbb{E}^{t_p}(x_s) = \bar{x}_0(t_a) + \mathcal{O}\left(\int_{0}^{s}\exp\left(-\int_{u}^{t_a}k_u^{\prime} du^{\prime}\right) du \right)
+$$. Let define
+\begin{align*}
+\bar{\nu}(t,t_p, \bar{x}_0(t_a))&:= \int_{t}^{t_p} \eta(s,\bar{x}_0(t_a),\bar{y}_s) ds\\
+\partial_x \bar{\nu}(t,t_p, \bar{x}_0(t_a))&:= \int_{t}^{t_p} \partial_x \eta(s,\bar{x}_0(t_a),\bar{y}_s) ds\\
+\end{align*}
 Then, we have that under the measure $\mathbb{Q}^{t_p}$ 
@@
 \begin{align*}
-\mathbb{E}_s(D_s \bar{x}_{t_a}) &\approx \eta(s,\bar{x}_s,\bar{y}_s) \exp\left(-\int_{s}^{t_a}k_u du \right)\\ &\cdot \mathbb{E}^{t_p}_s\left(\exp\left(-\int_{s}^{t_a} \exp\left(-\int_{u}^{t_a}k_u du\right)\partial_x (\eta(u, \bar{x}_u, \bar{y}_{u}) \bar{\nu}(u,t_p))|_{\bar{x}_u=\bar{x}_0(t_a)} du \right)\right)
+\mathbb{E}_s(D_s \bar{x}_{t_a}) &\approx \eta(s,\bar{x}_s,\bar{y}_s) \exp\left(-\int_{s}^{t_a}k_u du \right)\\ &\cdot \mathbb{E}^{t_p}_s\left(\exp\left(-\int_{s}^{t_a} \exp\left(-\int_{u}^{t_a}k_u du\right)\partial_x (\eta(u, \bar{x}_0(t_a), \bar{y}_{u})) \bar{\nu}(u,t_p, \bar{x}_0(t_a)) \right.
+\right.
+\\
+&+ \left. \left. \eta(u, \bar{x}_0(t_a), \bar{y}_{u})) \partial_x  \bar{\nu}(t,t_p, \bar{x}_0(t_a)) du \right)\right) 
 \end{align*}
@@
 \begin{equation}\label{general_convexity_fras}
-L_{E}(t_1,t_1,t_2) = \mathbb{E}^{\mathbb{Q}^{t_2}}\left(L_{E}(t_1,t_1,t_2) \right) + \int_{0}^{t_1} \mathbb{E}^{\mathbb{Q}^{t_2}}\left(D_s L_{E}(t_1,t_1,t_2) \right) dW^{\mathbb{Q}^{t_2}}_{s}
+L_{E}(t_1,t_1,t_2) = \mathbb{E}^{t_2}\left(L_{E}(t_1,t_1,t_2) \right) + \int_{0}^{t_1} \mathbb{E}^{t_2}\left(D_s L_{E}(t_1,t_1,t_2) \right) dW^{\mathbb{Q}^{t_2}}_{s}
 \end{equation}
@@
 \begin{align*}
-\mathbb{E}^{\mathbb{Q}^{t_1}}\left(L_{E}(t_1,t_1,t_2) \right) &= L_{E}(0,t_1,t_2) + \mathbb{E}\left( \int_{0}^{t_1} \mathbb{E}^{\mathbb{Q}^{t_2}}\left(D_s L_{E}(t_1,t_1,t_2) \right) dW^{\mathbb{Q}^{t_2}}_{s}\right)\\
-&= L_{E}(0,t_1,t_2) + \mathbb{E}\left( \int_{0}^{t_1} \mathbb{E}^{\mathbb{Q}^{t_2}}\left(D_s L_{E}(t_1,t_1,t_2) \right) (\nu(s,t_2)-\nu(s,t_1)) ds \right).
+\mathbb{E}^{t_1}\left(L_{E}(t_1,t_1,t_2) \right) &= L_{E}(0,t_1,t_2) + \mathbb{E}^{t_1}\left( \int_{0}^{t_1} \mathbb{E}_s^{t_2}\left(D_s L_{E}(t_1,t_1,t_2) \right) dW^{t_2}_{s}\right)\\
+&= L_{E}(0,t_1,t_2) + \mathbb{E}^{t_1}\left( \int_{0}^{t_1} \mathbb{E}_s^{t_2}\left(D_s L_{E}(t_1,t_1,t_2) \right) (\nu(s,t_2)-\nu(s,t_1)) ds \right).
 \end{align*}
@@
 D_s L(t_1,t_1,t_2) &=& \frac{G(t_1,t_2)}{\delta_{t_1,t_2}P_{E}(t_1,t_2)} D_s x_{t_1}\\
-&\approx& \frac{G(t_1,t_2)}{\delta_{t_1,t_2}P_{E}(0,t_1,t_2)} \beta(s,t_1, x_0, \bar{y}_s)\bar{M}(s,t_1)
-\end{eqnarray*}
-Therefore, if we define and we use (\ref{approsimation_E_s_x_t}) we have that
-\begin{equation*}
-CA(t_0,t_1) = \mathbb{E}^{\mathbb{Q}^{t_1}}\left( L_{E}\left(t_1,t_1,t_2\right)\right) - L_{E}\left(0,t_1,t_2\right)
-\end{equation*}
-and we use the last approximation and (\ref{general_convexity_fras}), we can get the next approximation for $CA(t_0,t_1)$.
+&\approx& \frac{G(t_1,t_2)}{\delta_{t_1,t_2}P_{E}(0,t_1,t_2)} \beta(s,t_1, \bar{x}_0(t_1), \bar{y}_s)\bar{DM}(s,t_1)
+\end{eqnarray*}
+If we use the above approximation, we get
+\begin{equation*}
+CA(t_0,t_1) = \frac{G(t_1,t_2)}{\delta_{t_1,t_2}P_{E}(0,t_1,t_2)} \beta(s,t_1, \bar{x}_0(t_1), \bar{y}_s) \int_{0}^{t_1} \bar{DM}(s,t_1) (\bar{\nu}(s,t_2,\bar{x}_{0}(t_1))-\bar{\nu}(s,t_1,\bar{x}_{0}(t_1))) ds
+\end{equation*}
+with $\bar{\nu}(t,t_p, \bar{x}_0(t_a))= \int_{t}^{t_p} \eta(s,\bar{x}_0(t_a),\bar{y}_s) ds$.
 
@@
 In order to reduce this complexity, it is a common practice to assume that $M(t_a,t_p)$ is a function of the swap rate $S_{a,b}(t_a)$, i.e   $M(t_a,t_p)=f(S_{a,b}(t_a))$.
-This assumption makes trivial to calculate \ref{Exp_M_conditional}.
+This assumption makes trivial to calculate (\ref{Exp_M_conditional}).
 The function $f(\cdot)$ is known as mapping function.
@@
 \end{align}
-
-From \eqref{cms_first_order_convexity_prev}, we can approximate \eqref{cms_first_order_convexity}.
+In this case, we will choose $\bar{x}_0(t_a)$ such that $S_{a,b}(t_a,\bar{x}_0(t_a),\bar{y}_{t_a})=S_{a,b}(0)$.
 

### 2023-03-18 Latex/paper-resum.tex
# last version of the paper where we have fixed some notation typos.

@@
 where $P_{E}(t,T)$ is the discount factor for the curve $E$ from $t$ to $T$, and $\delta_{t_1,t_2}$ is the year fraction between $t_1$ and $t_2$.
+we must note, that $L_{E}(t_0, t_1, t_2)$ is a martingale under the forward measure $\mathbb{Q}^{t_2}$ associated with the numeraire $P_{ois}(t,t_2)$.
 
@@
 \begin{equation}\label{convexity_ois_future}
-\mathbb{E}_t^{\mathbb{Q}}\left(R(t_0,t_1)\right) \approx \frac{\exp\left(\mathbb{E}_t^{\mathbb{Q}}\left(I(t_0,t_1)\right)\right)\exp\left(-\int_{t}^{t_1}\frac{\Gamma^{2}(s,t_0,t_1)}{2} ds\right) - 1}{\delta_{t_0,t_1}}
+\bar{R}(t_0,t_1) \approx \frac{\exp\left(\mathbb{E}_t^{\mathbb{Q}}\left(I(t_0,t_1)\right)\right)\exp\left(-\int_{t}^{t_1}\frac{\Gamma^{2}(s,t_0,t_1)}{2} ds\right) - 1}{\delta_{t_0,t_1}}
 \end{equation}
@@
 \begin{equation}\label{convexity_avg_ois_future}
-\mathbb{E}_t^{\mathbb{Q}}\left(R_{avg}(t_0,t_1)\right) = \frac{\mathbb{E}_t^{\mathbb{Q}}\left(I(t_0,t_1)\right) }{\delta_{t_0,t_1}} \approx \frac{\log\left(1+\delta_{t_0,t_1}  \mathbb{E}_t^{\mathbb{Q}}\left(R(t_0,t_1)\right) \right)}{\delta_{t_0,t_1}} - \frac{\int_{0}^{t_1}  \Gamma^{2}(s,t_0,t_1) ds}{2\delta_{t_0,t_1}}
+\bar{R}_{avg}(t_0,t_1) = \frac{\mathbb{E}_t^{\mathbb{Q}}\left(I(t_0,t_1)\right) }{\delta_{t_0,t_1}} \approx \frac{\log\left(1+\delta_{t_0,t_1}  \mathbb{E}_t^{\mathbb{Q}}\left(R(t_0,t_1)\right) \right)}{\delta_{t_0,t_1}} - \frac{\int_{0}^{t_1}  \Gamma^{2}(s,t_0,t_1) ds}{2\delta_{t_0,t_1}}
 \end{equation}
@@
 
-The next figure, show accuracy of (\ref{convexity_ois_future}) and (\ref{convexity_avg_ois_future}) for the Hull-White model case when the mean reversion is $k=0.003$ and volatility $\sigma=0.01$. 
+The next figure, show accuracy of (\ref{convexity_ois_future}) and (\ref{convexity_avg_ois_future}).
+The parameters that we have used to run the Monte Carlo have been $k=0.003$ and volatility $\sigma=0.01$ and flat curve $r=0.01$.
 \begin{figure}[H]
@@
 \end{equation}
-and 
-\begin{align}\label{cms_first_order_convexity}
-\mathbb{E}^{t_p}\left(S_{a,b}(t_a)\right) &\approx  S^{ois}_{a,b}(0) + \frac{\partial_x S_{a,b}(t_a,\bar{x}_0(t_a), \bar{y}_0) \partial_x M(t_a,t_p,\bar{x}_0(t_a), \bar{y}_0)} \nonumber \\
+Then, we have the temporal convexity adjusment for a CMS rate is approximated by
+\begin{align} \label{cms_first_order_convexity}
+CA_{CMS}(t_p) &\approx \frac{\partial_x S_{a,b}(t_a,\bar{x}_0(t_a), \bar{y}_0) \partial_x M(t_a,t_p,\bar{x}_0(t_a), \bar{y}_0)}{M(0,t_p)} \nonumber \\
 &\cdot \int_{0}^{t_a}  \beta^2(s,t_a,\bar{x}_0(t_a),\bar{y}_s) \exp\left(-2\int_{s}^{t_a}\beta(u,t_a,\bar{x}_{0}(t_a),\bar{y}_u) \mu(u,t_a,t_b) du \right)ds 
 \end{align}
-with  $\beta(u,t_a,x,y) = \exp\left(-\int_{u}^{t_a}k_u du\right)\eta(u,x,y)$. Then, the convexity adjustment approximation for CMS is
-\begin{equation}
-CA_{CMS}(t_p) = \mathbb{E}^{t_p}\left(S_{a,b}(t_a)\right) - S_{a,b}(0).
-\end{equation} 
+with  $\beta(u,t_a,x,y) = \exp\left(-\int_{u}^{t_a}k_u du\right)\eta(u,x,y)$.
 \end{theorem}
@@
 \begin{align*}
-\bar{DM}(s,t_a) &= \mathbb{E}^{t_p}_s\left(\exp\left(-\int_{s}^{t_a} \exp\left(-\int_{u}^{t_a}k_u du\right)\partial_x \eta(u, \bar{x}_0(t_a), \bar{y}_{u}) \bar{\nu}(u,t_p, \bar{x}_0(t_a)) \right.
+\bar{DM}(s,t_a) &= \mathbb{E}^{t_p}_s\left(\exp\left(-\int_{s}^{t_a} \exp\left(-\int_{u}^{t_a}k_u du\right)\left(\partial_x \eta(u, \bar{x}_0(t_a), \bar{y}_{u}) \bar{\nu}(u,t_p, \bar{x}_0(t_a)) \right.
+\right.
 \right.
 \\
-&+ \left. \left. \eta(u,\bar{x}_0(t_a), \bar{y}_{u})) \partial_x \bar{\nu}(t,t_p, \bar{x}_0(t_a)) du \right)\right) 
+&+ \left. \left. \left. \eta(u,\bar{x}_0(t_a), \bar{y}_{u})) \partial_x \bar{\nu}(t,t_p, \bar{x}_0(t_a)) du \right) \right)\right) 
 \end{align*}
@@
 \begin{align*}
-\mathbb{E}_s(D_s \bar{x}_{t_a}) &\approx \eta(s,\bar{x}_s,\bar{y}_s) \exp\left(-\int_{s}^{t_a}k_u du \right)\\ &\cdot \mathbb{E}^{t_p}_s\left(\exp\left(-\int_{s}^{t_a} \exp\left(-\int_{u}^{t_a}k_u du\right)\partial_x (\eta(u, \bar{x}_0(t_a), \bar{y}_{u})) \bar{\nu}(u,t_p, \bar{x}_0(t_a)) \right.
+\mathbb{E}_s(D_s \bar{x}_{t_a}) &\approx \eta(s,\bar{x}_s,\bar{y}_s) \exp\left(-\int_{s}^{t_a}k_u du \right)\\ &\cdot \mathbb{E}^{t_p}_s\left(\exp\left(-\int_{s}^{t_a} \exp\left(-\int_{u}^{t_a}k_u du\right)\left(\partial_x (\eta(u, \bar{x}_0(t_a), \bar{y}_{u})) \bar{\nu}(u,t_p, \bar{x}_0(t_a)) \right.
+\right.
 \right.
 \\
-&+ \left. \left. \eta(u, \bar{x}_0(t_a), \bar{y}_{u})) \partial_x  \bar{\nu}(t,t_p, \bar{x}_0(t_a)) du \right)\right) 
+&+ \left. \left. \left. \eta(u, \bar{x}_0(t_a), \bar{y}_{u})) \partial_x  \bar{\nu}(t,t_p, \bar{x}_0(t_a)) du \right)\right)\right) 
 \end{align*}
@@
 \end{equation*}
-Taking $\mathbb{E}^{^{\mathbb{Q}^{t_1}}}(\cdot)$, we get that
+Taking $\mathbb{E}^{^{t_1}}(\cdot)$, we get that
 \begin{align*}

### 2023-03-18 Latex/paper-resum.tex
# last version of the paper where we have fixed some notation typos.

@@
 In order to reduce this complexity, it is a common practice to assume that $M(t_a,t_p)$ is a function of the swap rate $S_{a,b}(t_a)$, i.e   $M(t_a,t_p)=f(S_{a,b}(t_a))$.
-This assumption makes trivial to calculate (\ref{Exp_M_conditional}).
+Under this assumption (\ref{Exp_M_conditional}) is trivial to calulate it.
 The function $f(\cdot)$ is known as mapping function.
@@
 \\
-
-We will do an approach without to specify any mapping function. If we apply Clark-Ocone formula to $M(t_a,t_p)$ we get that
+In this case, we will choose $\bar{x}_0(t_a)$ such that $S_{a,b}(t_a,\bar{x}_0(t_a),\bar{y}_{t_a})=S_{a,b}(0)$. If we apply Clark-Ocone formula to $M(t_a,t_p)$ we get that
 \begin{equation} \label{clark_ocone_swap_m}
@@
 \end{align}
-Now if we use (\ref{approximation_E_01_Ds_x_t}) we have that
+Now if we use (\ref{approximation_E_01_Ds_x_t}) and choose $\bar{x}_0(t_a)$ such that $S_{a,b}(t_a,\bar{x}_0(t_a),\bar{y}_{t_a})=S_{a,b}(0)$, we have that
 \begin{align}
@@
 \end{align}
-In this case, we will choose $\bar{x}_0(t_a)$ such that $S_{a,b}(t_a,\bar{x}_0(t_a),\bar{y}_{t_a})=S_{a,b}(0)$.
 

### 2023-03-27 Latex/paper-resum.tex
# last version with correction in appendix

@@
 \begin{equation}\label{ca_approximation_futures}
-CA(t,t_0,t_1) \approx \frac{P_{E}(0,t_1)}{\delta_{t_1,t_2} P_{E}(0,t_2)} \left(G(t_0,t_2)  - G(t_0,t_1) \right) \int_{0}^{t_0} \beta(s,t_0,x_0,\hat{y}_s) \nu(s,t_2) ds. 
+CA(t,t_0,t_1) \approx \frac{P_{E}(0,t_1)}{\delta_{t_1,t_2} P_{E}(0,t_2)} \left(G(t_0,t_2)  - G(t_0,t_1) \right) \int_{0}^{t_0} \beta(s,t_0,\bar{x}_0(t_0),\bar{y}_s) \nu(s,t_2) ds. 
 \end{equation}
@@
 \begin{equation*}
-\beta(t,t_0,x,y) = \exp\left(-\int_{s}^{T_a}k_u du \right) \eta(u,x,y).
+\beta(t,t_0,x,y) = \exp\left(-\int_{s}^{t_0}k_u du \right) \eta(u,x,y).
 \end{equation*}
@@
 \section{Auxiliary lemmas}
-\begin{lemma}\label{DsX}[Approximation $D_s \bar{x}_{t_a}$]
-Given the Cheyette model in \eqref{short_rate_cheyette}, the hypothesis \ref{boundedness_volatility} and \ref{boundedness_reversion}, and considering the approximations in \eqref{approximation_y_t} and \eqref{approximation_x_t_a}.
-Then,
-\begin{equation}\label{approximation_D_s_x_t}
-D_s \bar{x}_{t_a} = \beta(s,t_a,\bar{x}_s,\bar{y}_s) \bar{M}(s,t_a)
-\end{equation}
-where
-\begin{align*}
-\bar{M}(s,t_a) &= \exp\left(-\int_{s}^{t_a} \left( \frac{\left(\partial_x \beta(u,t_a,\bar{x}_0,\bar{y}_{t_a})\right)^{2}}{2} - \exp\left(-\int_{u}^{t_a}k_u du\right) \partial_x (\eta(u, \bar{x}_u, \bar{y}_{u}) \bar{\nu}(u,t_p))\right) du \right) \\
-&\cdot\exp\left(\int_{s}^{t_0} \partial_x \beta(u,t_a,\bar{x}_0,\bar{y}_{t_a}) dW^{\mathbb{Q}}_u \right)
-\end{align*}
-With $\beta(u,t_a,x,y) = \exp\left(-\int_{u}^{t_a}k_u^{\prime} du^{\prime}\right) \partial_x \eta(u,x,y)$. Then, we have that
-\begin{align}\label{approsimation_E_s_x_t}
-\mathbb{E}_s^{t_p}\left(D_s \bar{x}_{t_a}\right) &\approx \beta(s,t_a,\bar{x}_s,\bar{y}_s) \bar{DM}(s,t_a).
-\end{align}
-where 
-\begin{align*}
-\bar{DM}(s,t_a) &= \mathbb{E}^{t_p}_s\left(\exp\left(-\int_{s}^{t_a} \exp\left(-\int_{u}^{t_a}k_u du\right)\left(\partial_x \eta(u, \bar{x}_0(t_a), \bar{y}_{u}) \bar{\nu}(u,t_p, \bar{x}_0(t_a)) \right.
-\right.
-\right.
-\\
-&+ \left. \left. \left. \eta(u,\bar{x}_0(t_a), \bar{y}_{u})) \partial_x \bar{\nu}(t,t_p, \bar{x}_0(t_a)) du \right) \right)\right) 
-\end{align*}
-\end{lemma}
-\begin{proof}
-Using the relation 
-\begin{equation*}
-dW^{\mathbb{Q}^{t_p}} = dW^{\mathbb{Q}} + \bar{\nu}(t,t_p) dt
-\end{equation*}
-where $\bar{\nu}(t,t_p) = \int_{t}^{t_p} \eta(s,\bar{x}_s,\bar{y}_s) ds$. We must observe, that we can approximate $x_s$ by 
-$$
-\mathbb{E}^{t_p}(x_s) = \bar{x}_0(t_a) + \mathcal{O}\left(\int_{0}^{s}\exp\left(-\int_{u}^{t_a}k_u^{\prime} du^{\prime}\right) du \right)
-$$. Let define
-\begin{align*}
-\bar{\nu}(t,t_p, \bar{x}_0(t_a))&:= \int_{t}^{t_p} \eta(s,\bar{x}_0(t_a),\bar{y}_s) ds\\
-\partial_x \bar{\nu}(t,t_p, \bar{x}_0(t_a))&:= \int_{t}^{t_p} \partial_x \eta(s,\bar{x}_0(t_a),\bar{y}_s) ds\\
-\end{align*}
-Then, we have that under the measure $\mathbb{Q}^{t_p}$ 
-\begin{align*}
-\bar{x}_{t_a} = \bar{x}_0(t_a) &+ \int_{0}^{t_a} \exp\left(-\int_{s}^{t_a}k_u du\right) \bar{y}_s ds - \int_{0}^{t_a} \exp\left(-\int_{s}^{t_a}k_u du\right) \bar{\nu}(s, t_p) \eta(s,\bar{x}_s,\bar{y}_s) ds   \\
-&+ \int_{0}^{t_a}  \exp\left(-\int_{s}^{t_a}k_u du \right)\eta(s,\bar{x}_s,\bar{y}_s) dW_s^{\mathbb{Q}^{t_p}}. 
-\end{align*}
-Now, if we apply $D_s$ in above equality and we use the last approximation we have that
-\begin{align*}
-\mathbb{E}_s(D_s \bar{x}_{t_a}) &\approx \eta(s,\bar{x}_s,\bar{y}_s) \exp\left(-\int_{s}^{t_a}k_u du \right)\\ &\cdot \mathbb{E}^{t_p}_s\left(\exp\left(-\int_{s}^{t_a} \exp\left(-\int_{u}^{t_a}k_u du\right)\left(\partial_x (\eta(u, \bar{x}_0(t_a), \bar{y}_{u})) \bar{\nu}(u,t_p, \bar{x}_0(t_a)) \right.
-\right.
-\right.
-\\
-&+ \left. \left. \left. \eta(u, \bar{x}_0(t_a), \bar{y}_{u})) \partial_x  \bar{\nu}(t,t_p, \bar{x}_0(t_a)) du \right)\right)\right) 
-\end{align*}
-\end{proof}
 \subsection{Estimation of $\mathbb{E}_s^{\mathbb{Q}}\left((x_t - \bar{x}_{t})^{2}\right)$}\label{estimation_error_l2}
@@
 \end{align}
-The reason of $\epsilon^{2}$ in $y_{\epsilon,t}$ is because $\mathbb{E}\left(y_t\right)= \mathbb{V}ar(x_t)$.
+The reason of $\epsilon^{2}$ in $y_{\epsilon,t}$ is because $\mathbb{E}^{\mathbb{Q}}\left(y_t\right)= \mathbb{V}ar(x_t)$.
 Then, if the scale of $x_{\epsilon,t}$ is $\epsilon$ then the scale of $y_{\epsilon,t}$ must be $\epsilon^{2}$.
-We will start with the estimation of $\mathbb{E}((y_t - \bar{y}_t)^{2})$.
-We will define the next parametrization for $\nu in [0,1]$
+We will start with the estimation of $\mathbb{E}^{\mathbb{Q}}((y_t - \bar{y}_t)^{2})$.
+We will define the next parametrization for $\nu \in [0,1]$
 \begin{equation*}
@@
 \begin{align*}
-\eta^{2}(u, x_u, y_u) &= \eta^{2}(u, 0, 0) + \int_{0}^{1} \partial_{\nu}z^{nu}_{u} d\nu \\ 
+\eta^{2}(u, x_u, y_u) &= \eta^{2}(u, 0, 0) + \int_{0}^{1} \partial_{\nu}z^{\nu}_{u} d\nu \\ 
 &=  \eta^{2}(u, 0, 0) + 2 \int_{0}^{1} \eta(u, \nu x_u, \nu y_u)   \nabla_{x,y}\eta(u, \nu x_u, \nu y_u) \cdot (x_u, y_u) d\nu.
@@
 \begin{align} \label{upper_bound_E_y}
-\mathbb{E}((E_{y}(t))^{2}) &\leq 4 \mathbb{E}\left(\int_{0}^{t} \exp\left(-4 \int_{u}^{t} k(u^{\prime}) du^{\prime}\right)  \left(\int_{0}^{1} \eta(u, \nu x_u, \nu y_u)   \|\nabla_{x,y}\eta(u, \nu x_u, \nu y_u)\|^{2} \|(x_u, y_u)\| d\nu \right)^2 du \right) ^{2}\nonumber \\
-&\leq 4 \|\eta\|^{2}_{\infty} \max(\|\partial_x\eta\|^{2}_{\infty},\partial_y\|\eta\|^{2}_{\infty} ) \int_{0}^{t} \mathbb{E}\left( \|(x_u, y_u)\|^{2}\right) du = M^{y}_k \int_{0}^{t} \mathbb{E}\left( \|(x_u, y_u)\|^{2}\right) du
-\end{align}
-The next step is to estimate $\mathbb{E}((x_t - \bar{x}_t)^{2})$. From the definition of $x_t$, we have that
-\begin{equation*}
-x_t = \int_{0}^{t} \exp\left(- \int_{u}^{t} k(u^{\prime}) du^{\prime}\right) \bar{y}_u du + \int_{0}^{t} \exp\left(- \int_{u}^{t} k(u^{\prime}) du^{\prime}\right) E{y}(u) du + \int_{0}^{t} \eta(t,x_u,y_u) dW_u.
+\mathbb{E}^{\mathbb{Q}}((E_{y}(t))^{2}) &\leq 4 \mathbb{E}^{\mathbb{Q}}\left(\int_{0}^{t} \exp\left(-4 \int_{u}^{t} k(u^{\prime}) du^{\prime}\right)  \left(\int_{0}^{1} \eta(u, \nu x_u, \nu y_u)   \|\nabla_{x,y}\eta(u, \nu x_u, \nu y_u)\|^{2} \|(x_u, y_u)\| d\nu \right)^2 du \right) ^{2}\nonumber \\
+&\leq 4 \|\eta\|^{2}_{\infty} \max(\|\partial_x\eta\|^{2}_{\infty},\|\partial_y \eta\|^{2}_{\infty} ) \int_{0}^{t} \mathbb{E}^{\mathbb{Q}}\left( \|(x_u, y_u)\|^{2}\right) du = M^{y}_k \int_{0}^{t} \mathbb{E}^{\mathbb{Q}}\left( \|(x_u, y_u)\|^{2}\right) du
+\end{align}
+The next step is to estimate $\mathbb{E}^{\mathbb{Q}}((x_t - \bar{x}_t)^{2})$. From the definition of $x_t$, we have that
+\begin{equation*}
+x_t = \int_{0}^{t} \exp\left(- \int_{u}^{t} k(u^{\prime}) du^{\prime}\right) \bar{y}_u du + \int_{0}^{t} \exp\left(- \int_{u}^{t} k(u^{\prime}) du^{\prime}\right) E_{y}(u) du + \int_{0}^{t} \eta(t,x_u,y_u) dW_u.
 \end{equation*}
@@
 \begin{equation*}
- \mathbb{E}((E_x(u))^{2}) \leq \|\partial_y \eta \|^{2}_{\infty} \mathbb{E}((E_{y}(u))^{2})   
-\end{equation*}
-Tne using \ref{upper_bound_E_y} we get that
+ \mathbb{E}^{\mathbb{Q}}((E_x(u))^{2}) \leq \|\partial_y \eta \|^{2}_{\infty} \mathbb{E}^{\mathbb{Q}}((E_{y}(u))^{2})   
+\end{equation*}
+Then using (\ref{upper_bound_E_y}) we get that
 \begin{equation}\label{upper_bound_E_x}
- \mathbb{E}((E_x(u))^{2}) \leq 4 \|\eta\|^{2}_{\infty} \|\partial_y \eta\|^{2}_{\infty} \max(\|\partial_x\eta\|^{2}_{\infty},\partial_y\|\eta\|^{2}_{\infty} ) \int_{0}^{u} \mathbb{E}\left( \|(x_s, y_s)\|^{2}\right) ds
+ \mathbb{E}^{\mathbb{Q}}((E_x(u))^{2}) \leq 4 \|\eta\|^{2}_{\infty} \|\partial_y \eta\|^{2}_{\infty} \max(\|\partial_x\eta\|^{2}_{\infty},\|\partial_y \eta\|^{2}_{\infty} ) \int_{0}^{u} \mathbb{E}^{\mathbb{Q}}\left( \|(x_s, y_s)\|^{2}\right) ds
 \end{equation}
@@
 \begin{align*}
-\mathbb{E}((x_t - \bar{x}_t)^{2}) & \leq 2 \mathbb{E}\left( \int_{0}^{t} \exp\left(- \int_{u}^{t} k(u^{\prime}) du^{\prime}\right) E_{y}(u) du    \right)^2 + \mathbb{E}\left( \int_{0}^{t} \exp\left(- \int_{u}^{t} k(u^{\prime}) du^{\prime}\right) E_{x}(u) dW_u\right)^{2} \\
-&\leq 2 \mathbb{E}\int_{0}^{t} \exp\left(- 2\int_{u}^{t} k(u^{\prime}) du^{\prime}\right) \mathbb{E}(E^{2}_{y}(u)) du + \int_{0}^{t} \exp\left(- 2\int_{u}^{t} k(u^{\prime}) du^{\prime}\right) \mathbb{E}(E^{2}_{x}(u)) du
+\mathbb{E}^{\mathbb{Q}}((x_t - \bar{x}_t)^{2}) & \leq 2 \mathbb{E}^{\mathbb{Q}}\left( \int_{0}^{t} \exp\left(- \int_{u}^{t} k(u^{\prime}) du^{\prime}\right) E_{y}(u) du    \right)^2 + \mathbb{E}^{\mathbb{Q}}\left( \int_{0}^{t} \exp\left(- \int_{u}^{t} k(u^{\prime}) du^{\prime}\right) E_{x}(u) dW_u\right)^{2} \\
+&\leq 2 \mathbb{E}^{\mathbb{Q}}\int_{0}^{t} \exp\left(- 2\int_{u}^{t} k(u^{\prime}) du^{\prime}\right) \mathbb{E}^{\mathbb{Q}}(E^{2}_{y}(u)) du + \int_{0}^{t} \exp\left(- 2\int_{u}^{t} k(u^{\prime}) du^{\prime}\right) \mathbb{E}^{\mathbb{Q}}(E^{2}_{x}(u)) du
 \end{align*}
@@
 \begin{equation*}
-\mathbb{E}((x_t - \bar{x}_t)^{2}) \leq M^{x}_k \int_{0}^{t} \exp\left(- 2\int_{u}^{t} k(u^{\prime}) du^{\prime}\right) \mathbb{E}\left( \|(x_u, y_u)\|^{2}\right) du 
-\end{equation*}
-To end, only we have to estimate $\mathbb{E}\left( \|(x_s, y_s)\|^{2}\right)$.
-We will start with $\mathbb{E}(y^{2}_u)$.From the definition of $y_t$ and since $\|\eta\|_{\infty} < \infty$, we have that
-\begin{equation*}
-\mathbb{E}(y^{2}_u) \leq \|\eta\|^{2}_{\infty} \int_{0}^{u} \exp\left(- 2\int_{s}^{u} k(u^{\prime}) du^{\prime}\right) ds.
+\mathbb{E}^{\mathbb{Q}}((x_t - \bar{x}_t)^{2}) \leq M^{x}_k \int_{0}^{t} \exp\left(- 2\int_{u}^{t} k(u^{\prime}) du^{\prime}\right) \mathbb{E}^{\mathbb{Q}}\left( \|(x_u, y_u)\|^{2}\right) du 
+\end{equation*}
+To end, only we have to estimate $\mathbb{E}^{\mathbb{Q}}\left( \|(x_s, y_s)\|^{2}\right)$. From the definition of $y_t$ and since $\|\eta\|_{\infty} < \infty$, we have that
+\begin{equation*}
+\mathbb{E}^{\mathbb{Q}}(y^{2}_u) \leq \|\eta\|^{2}_{\infty} \int_{0}^{u} \exp\left(- 2\int_{s}^{u} k(u^{\prime}) du^{\prime}\right) ds.
 \end{equation*}
@@
 \begin{equation*}
-\lim_{t \to 0} \mathbb{E}(y^{2}_u) = \|\eta\|^{2}_{\infty} t
+\lim_{t \to 0} \mathbb{E}^{\mathbb{Q}}(y^{2}_u) = \|\eta\|^{2}_{\infty} t
 \end{equation*}
@@
 \begin{equation*}
-\lim_{t \to \infty} \mathbb{E}(y^{2}_u) < \infty.
-\end{equation*}
-Now $\mathbb{E}(x^{2}_u)$. From the definition of $x_t$ and using $(a+b)^2 \leq 2(a^{2}+ b^{2})$ we have that
-\begin{align*}
-\mathbb{E}(x^{2}_u) &\leq 2 \mathbb{E}\left(\int_{0}^{u} \exp\left(- \int_{s}^{u} k(u^{\prime}) du^{\prime}\right) y_s  ds \right)^{2} +  2 \mathbb{E}\left(\int_{0}^{u} \exp\left(- \int_{s}^{u} k(u^{\prime}) du^{\prime}\right) \eta(s,x_s,y_s)  dW_s \right)^{2} \nonumber \\
-&\leq 2 \int_{0}^{u} \exp\left(- 2\int_{s}^{u} k(u^{\prime}) du^{\prime}\right) \mathbb{E}\left(y_s\right)^{2} ds + 2 \int_{0}^{u} \exp\left(- 2 \int_{s}^{u} k(u^{\prime}) du^{\prime}\right) \mathbb{E}\left(\eta^{2}(s,x_s,y_s)\right) ds \\
+\lim_{t \to \infty} \mathbb{E}^{\mathbb{Q}}(y^{2}_u) < \infty.
+\end{equation*}
+Now $\mathbb{E}^{\mathbb{Q}}(x^{2}_u)$. From the definition of $x_t$ and using $(a+b)^2 \leq 2(a^{2}+ b^{2})$ we have that
+\begin{align*}
+\mathbb{E}^{\mathbb{Q}}(x^{2}_u) &\leq 2 \mathbb{E}^{\mathbb{Q}}\left(\int_{0}^{u} \exp\left(- \int_{s}^{u} k(u^{\prime}) du^{\prime}\right) y_s  ds \right)^{2} +  2 \mathbb{E}^{\mathbb{Q}}\left(\int_{0}^{u} \exp\left(- \int_{s}^{u} k(u^{\prime}) du^{\prime}\right) \eta(s,x_s,y_s)  dW_s \right)^{2} \nonumber \\
+&\leq 2 \int_{0}^{u} \exp\left(- 2\int_{s}^{u} k(u^{\prime}) du^{\prime}\right) \mathbb{E}^{\mathbb{Q}}\left(y_s\right)^{2} ds + 2 \int_{0}^{u} \exp\left(- 2 \int_{s}^{u} k(u^{\prime}) du^{\prime}\right) \mathbb{E}^{\mathbb{Q}}\left(\eta^{2}(s,x_s,y_s)\right) ds \\
 &\leq 2 \|\eta\|_{\infty} \int_{0}^{u} \exp\left(- 2\int_{s}^{u} k(u^{\prime}) du^{\prime}\right) \int_{0}^{s}  \exp\left(- 2\int_{s_1}^{s} k(u^{\prime}) du^{\prime}\right) ds_1 ds +  2 \|\eta\|_{\infty} \int_{0}^{u} \exp\left(- 2\int_{s}^{u} k(u^{\prime}) du^{\prime}\right) ds
@@
 $$
-\lim_{t \to 0} \mathbb{E}(x^{2}_u) = 2\|\eta\|^{2}_{\infty} t
+\lim_{t \to 0} \mathbb{E}^{\mathbb{Q}}(x^{2}_u) = 2\|\eta\|^{2}_{\infty} t
 $$
-and when ($u \to \infty$) we have that $\mathbb{E}(x^{2}_u)$ remains bounded. Then, if we use the above inequalities 
-\begin{align*}
-\mathbb{E}((y_t - \bar{y}_t)^{2}) &\leq M^{y}_k \int_{0}^{t}  \exp\left(- 2\int_{u}^{t} k(u^{\prime}) du^{\prime}\right)  \int_{0}^{u} \exp\left(- 2\int_{s}^{u} k(u^{\prime}) du^{\prime}\right) ds du
+and when ($u \to \infty$) we have that $\mathbb{E}^{\mathbb{Q}}(x^{2}_u)$ remains bounded. Then, if we use the above inequalities 
+\begin{align*}
+\mathbb{E}^{\mathbb{Q}}((y_t - \bar{y}_t)^{2}) &\leq M^{y}_k \int_{0}^{t}  \exp\left(- 2\int_{u}^{t} k(u^{\prime}) du^{\prime}\right)  \int_{0}^{u} \exp\left(- 2\int_{s}^{u} k(u^{\prime}) du^{\prime}\right) ds du
 \end{align*}
@@
 \begin{align*}
-\mathbb{E}((x_t - \bar{x}_t)^{2}) &\leq 2 M^{x}_k \|\eta\|_{\infty} \int_{0}^{t} \exp\left(- 2\int_{u}^{t} k(u^{\prime}) du^{\prime}\right)   \int_{0}^{u} \exp\left(- 2\int_{s}^{u} k(u^{\prime}) du^{\prime}\right) \int_{0}^{s}  \exp\left(- 2\int_{s_1}^{s} k(u^{\prime}) du^{\prime}\right) ds_1 ds du \\
-&+ (2 M^{x}_K \|\eta\|_{\infty} + 1) \int_{0}^{t}  \exp\left(- 2\int_{u}^{t} k(u^{\prime}) du^{\prime}\right)  \int_{0}^{u} \exp\left(- 2\int_{s}^{u} k(u^{\prime}) du^{\prime}\right) ds du
-\end{align*}
+\mathbb{E}^{\mathbb{Q}}((x_t - \bar{x}_t)^{2}) &\leq 2 M^{x}_k \|\eta\|_{\infty} \int_{0}^{t} \exp\left(- 2\int_{u}^{t} k(u^{\prime}) du^{\prime}\right)   \int_{0}^{u} \exp\left(- 2\int_{s}^{u} k(u^{\prime}) du^{\prime}\right) \int_{0}^{s}  \exp\left(- 2\int_{s_1}^{s} k(u^{\prime}) du^{\prime}\right) ds_1 ds du \\
+&+ (2 M^{x}_K \|\eta\|_{\infty} + 1) \int_{0}^{t}  \exp\left(- 2\int_{u}^{t} k(u^{\prime}) du^{\prime}\right)  \int_{0}^{u} \exp\left(- 2\int_{s}^{u} k(u^{\prime}) du^{\prime}\right) ds du.
+\end{align*}
+Therefore, we have that
+\begin{align*}
+\mathbb{E}^{\mathbb{Q}}((x_t - \bar{x}_t)^{2}) &\leq \frac{2}{3} M^{x}_k \|\eta\|_{\infty} \left( \int_{0}^{t} \exp\left(- 2\int_{u}^{t} k(u^{\prime}) \right) du  \right)^{3}  \\
+&+ \frac{(2 M^{x}_K \|\eta\|_{\infty} + 1)}{2} \left( \int_{0}^{t}  \exp\left(- 2\int_{u}^{t} k(u^{\prime}) \right) du  \right)^{2}.
+\end{align*}
+
+\begin{lemma}\label{DsX}[Approximation $D_s \bar{x}_{t_a}$]
+Given the Cheyette model in \eqref{short_rate_cheyette}, the hypothesis \ref{boundedness_volatility} and \ref{boundedness_reversion}, and considering the approximations in \eqref{approximation_y_t} and \eqref{approximation_x_t_a}.
+Then,
+\begin{align}\label{approximation_D_s_x_t}
+D_s \bar{x}_{t_a} &= \beta(s,t_a,\bar{x}_s,\bar{y}_s) \bar{M}(s,t_a,t_p) \quad \text{under the measure $\mathbb{Q}^{t_p}$} \nonumber \\
+D_s \bar{x}_{t_a} &= \beta(s,t_a,\bar{x}_s,\bar{y}_s) \bar{M}(s,t_a)  \quad \text{under the measure $\mathbb{Q}$}
+\end{align}
+where
+\begin{align*}
+\bar{M}(s,t_a,t_p) &= \exp\left(-\int_{s}^{t_a} \left( \frac{\left(\partial_x \beta(u,t_a,\bar{x}_0,\bar{y}_{t_a})\right)^{2}}{2} - \exp\left(-\int_{u}^{t_a}k_u du\right) \partial_x (\eta(u, \bar{x}_u, \bar{y}_{u}) \bar{\nu}(u,t_p))\right) du \right) \\
+&\cdot\exp\left(\int_{s}^{t_0} \partial_x \beta(u,t_a,\bar{x}_0,\bar{y}_{t_a}) dW^{\mathbb{Q}}_u \right)
+\end{align*}
+and
+\begin{equation*}
+\bar{M}(s,t_a) = \exp\left(-\int_{s}^{t_a} \left( \frac{\left(\partial_x \beta(u,t_a,\bar{x}_0,\bar{y}_{t_a})\right)^{2}}{2} - \right) du \right) \exp\left(\int_{s}^{t_0} \partial_x \beta(u,t_a,\bar{x}_0,\bar{y}_{t_a}) dW^{\mathbb{Q}}_u \right)
+\end{equation*} 
+With $\beta(u,t_a,x,y) = \exp\left(-\int_{u}^{t_a}k_u^{\prime} du^{\prime}\right) \partial_x \eta(u,x,y)$. We have also that
+\begin{align}\label{approsimation_E_s_x_t}
+\mathbb{E}_s^{t_p}\left(D_s \bar{x}_{t_a}\right) &\approx \beta(s,t_a,\bar{x}_s,\bar{y}_s) \bar{DM}(s,t_a) \nonumber \\
+\mathbb{E}_s^{\mathbb{Q}}\left(D_s \bar{x}_{t_a}\right)&\approx \beta(s,t_a,\bar{x}_s,\bar{y}_s)
+\end{align}
+where 
+\begin{align*}
+\bar{DM}(s,t_a) &= \mathbb{E}^{t_p}_s\left(\exp\left(-\int_{s}^{t_a} \exp\left(-\int_{u}^{t_a}k_u du\right)\left(\partial_x \eta(u, \bar{x}_0(t_a), \bar{y}_{u}) \bar{\nu}(u,t_p, \bar{x}_0(t_a)) \right.
+\right.
+\right.
+\\
+&+ \left. \left. \left. \eta(u,\bar{x}_0(t_a), \bar{y}_{u})) \partial_x \bar{\nu}(t,t_p, \bar{x}_0(t_a)) \right)  du \right)\right) 
+\end{align*}
+with  
+\begin{align*}
+\bar{\nu}(t,t_p) &= \int_{t}^{t_p} \eta(s,\bar{x}_s,\bar{y}_s) ds \\
+\bar{\nu}(t,t_p, x_0) &= \int_{t}^{t_p} \eta(s,x,\bar{y}_s) ds \\
+\partial_x \bar{\nu}(t,t_p,x_0) &= \int_{t}^{t_p} \eta(s,x_0,\bar{y}_s) ds\\
+\end{align*}
+\end{lemma}
+\begin{proof}
+From 
+\begin{equation*}
+dW^{\mathbb{Q}^{t_p}} = dW^{\mathbb{Q}} + \bar{\nu}(t,t_p) dt
+\end{equation*}
+we have that under the measure $\mathbb{Q}^{t_p}$ 
+\begin{align*}
+\bar{x}_{t_a} = \bar{x}_0(t_a) &+ \int_{0}^{t_a} \exp\left(-\int_{s}^{t_a}k_u du\right) \bar{y}_s ds - \int_{0}^{t_a} \exp\left(-\int_{s}^{t_a}k_u du\right) \bar{\nu}(s, t_p) \eta(s,\bar{x}_s,\bar{y}_s) ds   \\
+&+ \int_{0}^{t_a}  \exp\left(-\int_{s}^{t_a}k_u du \right)\eta(s,\bar{x}_s,\bar{y}_s) dW_s^{\mathbb{Q}^{t_p}}. 
+\end{align*}
+Now, if we apply $D_s$ in above equality and we use the last approximation we have that
+\begin{align*}
+\mathbb{E}^{t_p}_s(D_s \bar{x}_{t_a}) &\approx \eta(s,\bar{x}_s,\bar{y}_s) \exp\left(-\int_{s}^{t_a}k_u du \right)\\ &\cdot \exp\left(-\int_{s}^{t_a} \exp\left(-\int_{u}^{t_a}k_u du\right)\left(\partial_x (\eta(u, \bar{x}_0(t_a), \bar{y}_{u})) \bar{\nu}(u,t_p, \bar{x}_0(t_a)) \right.
+\right.
+\\
+&+  \left. \left. \eta(u, \bar{x}_0(t_a), \bar{y}_{u})) \partial_x  \bar{\nu}(t,t_p, \bar{x}_0(t_a)) du \right)\right)
+\end{align*}
+\end{proof}
 
@@
 \end{equation}
-where $\mathbb{E}(E^{2}(s)) \sim \mathcal{O}(s)$ when $s \to 0$.
+where $\mathbb{E}^{\mathbb{Q}}(E^{2}(s)) \sim \mathcal{O}(s)$ when $s \to 0$.
 

### 2023-03-27 Latex/paper-resum.tex
# last error that has been fixed. I have to end a.1.4 appendix.

@@
 \begin{eqnarray}
-\bar{x}_{t_a}:= \bar{x}_0(t_a)  &+& \int_{0}^{t_a} \exp\left(-\int_{s}^{t_a}k(u) du\right) \bar{y}(u) du \nonumber \\
-&+& \int_{0}^{t_a}  \exp\left(-\int_{s}^{t_a}k(u) du \right) \eta(u,\bar{x}(u),\bar{y}(u)) dW_u^{\mathbb{Q}}   \label{approximation_x_t_a}
+\bar{x}_{t_a}:= \bar{x}_0(t_a)  &+& \int_{0}^{t_a} \exp\left(-\int_{s}^{t_a}k(u) du\right) \bar{y}_u du \nonumber \\
+&+& \int_{0}^{t_a}  \exp\left(-\int_{s}^{t_a}k(u) du \right) \eta(u,\bar{x}(u),\bar{y}_u) dW_u^{\mathbb{Q}}   \label{approximation_x_t_a}
 \end{eqnarray}
@@
 \end{align*}
-
-To clarify the convexity expression and the calculations, we will define 
+Before to continue, we will do several observations. The first observation is that if we define $F(t,t_0,t_1) = \mathbb{E}^{\mathbb{Q}^{t_1}}\left( R(t_0,t_1)\right)$, then we have that
+\begin{align*}
+F(t,t_0,t_1)&= \frac{1}{P_{ois}(t,t_1)}  \mathbb{E}_{t}^{\mathbb{Q}}\left(\exp\left(-\int_{t}^{t_1} r_{ois,u} du \right) R(t_0,t_1) \right) = \frac{1}{\delta_{t_0,t_1}}\left(\frac{P_{ois}(t,t_0)}{P_{ois}(t,t_1)} - 1\right), \quad t \in [0,t_0] \\
+F(t,t_0,t_1)&= \frac{1}{P_{ois}(t,t_1)} \mathbb{E}_{t}^{\mathbb{Q}}\left(\exp\left(-\int_{t}^{t_1} r_{ois,u} du \right) R(t_0,t_1) \right) = \frac{1}{\delta_{t_0,t_1}} \left(\frac{\left( \exp\left(\int_{t}^{t_1}r_{ois,u} du\right)\right)}{P_{ois}(t_0,t)}-1\right), \quad  t \in  [t_0, t_1].
+\end{align*}
+Then the convexity adjustment for $ R(t_0,t_1)$ is
+\begin{equation}\label{R_ois_ca}
+CA_{ois}(t,t_0,t_1) = F(t,t_0,t_1) - \bar{R}(t,t_0,t_1).
+\end{equation}
+The second observation is that we have the following equivalence
+\begin{equation}\label{R_ois_avg}
+\mathbb{E}^{\mathbb{Q}}\left(R_{avg}(t_0,t_1) \right) = \mathbb{E}^{\mathbb{Q}}\left( \frac{\log\left(1+ \delta_{t_0,t_1} R(t_0,t_1) \right)}{\delta_{t_0,t_1}} \right)  \end{equation}
+In order, to clarify the convexity expression and the calculations, we will define 
 \begin{equation*}
@@
 \end{equation}
-Now, if we take $\mathbb{E}^{\mathbb{Q}}\left(\cdot\right)$ we get
+Now, if we take $\mathbb{E}_s^{\mathbb{Q}}\left(\cdot\right)$ we get
 \begin{equation}\label{approximation_spot_E_s_x_t}
@@
 \begin{equation}\label{approximation_spot_E_s_x_t}
-\mathbb{E}^{\mathbb{Q}}_s\left(D_s \bar{x}_{t_a} \right)= \exp\left(-\int_{s}^{t_a}k_u du \right) \eta(s,\bar{x}_0(t_a),\bar{y}_{s}) + E(s)
-\end{equation}
-where $\mathbb{E}^{\mathbb{Q}}(E^{2}(s)) \sim \mathcal{O}(s)$ when $s \to 0$.
+\mathbb{E}^{\mathbb{Q}}_s\left(D_s \bar{x}_{t_a} \right) \approx \exp\left(-\int_{s}^{t_a}k_u du \right) \eta(s,\bar{x}_0(t_a),\bar{y}_{s})
+\end{equation}
 
@@
 \begin{equation}
-\frac{dP(t,T)}{P(t,T)} = r_t dt - \nu(t,T)dW^{\mathbb{Q}}_t.  
-\end{equation}
-Therefore, if we apply Itô formula we have that 
+\frac{dP(t,T)}{P(t,T)} = r_t dt - \nu(t,T)dW^{\mathbb{Q}}_t  
+\end{equation}
+where we must rememebr that  $\nu(t,T)=\int_{t}^{T}\sigma(t,s) ds$. Therefore, if we apply Itô formula we have that 
 \begin{equation}\label{annuity_spot_dynamic}
@@
 \end{equation}
-where 
+with 
 \begin{equation} \label{annuity_vol}
@@
 \end{equation}
-From (\ref{annuity_vol}) and since $\frac{P_{ois}(t,T)}{01(t)}$ is a martingale, we have that
+Now, if we define $w_i(t)=\frac{\delta_{i-1,i} P(t,t_i)}{01(t,t_a,t_b)}$, then
+\begin{equation*}
+\sigma_{01}(t,t_a,t_b) = \sum_{i=a+1}^{b}  w_i(t) \nu(t,t_i).
+\end{equation*}
+Now, from (\ref{annuity_vol}) and since $\frac{P_{ois}(t,T)}{01(t)}$ is a martingale, we have that
 \begin{equation*}
@@
 \end{equation*}
-Thwn can do the next approximation of (\ref{annuity_vol})
-\begin{equation} \label{approximation_o1_vol}
-\bar{\sigma}_{01}(t,t_a,t_b) \approx \sum_{i=a+1}^{b} w_i \nu(t,t_i,x_0,y_0)
-\end{equation}
-with $w_i=\frac{\delta_{i-1,i} P(0,T_i)}{01(0,t_a,t_b)}$. Now, if we use (\ref{short_rate_cheyette}) and the previous approximation we have that
+Then, if we do a freezing of the weights $w_i(t)$, we get the next approximation of (\ref{annuity_vol})
+\begin{equation*} \label{approximation_o1_vol}
+\bar{\sigma}_{01}(t,t_a,t_b) \approx \sum_{i=a+1}^{b} w_i(0) \nu(t,t_i)
+\end{equation*}
+If we use (\ref{short_rate_cheyette}) and above approximation, we have that
 \begin{align}
-\bar{x}_{t_a} &\approx \bar{x}_0(t_a)  + \int_{0}^{t_a} \exp\left(-\int_{s}^{t}k_u du\right) \bar{y}(u) du + \int_{0}^{t_a}  \exp\left(-\int_{s}^{t_a}k_u du \right) \eta(u,\bar{x}(u),\bar{y}(u)) dW_u^{\mathbb{Q}} \nonumber \\
-&=  \bar{x}_0(t)  + \int_{0}^{t_a} \exp\left(-\int_{s}^{t_a}k_u du\right) \bar{y}(u) du + \int_{0}^{t_a} \exp\left(-\int_{s}^{t_A}k_u du \right) \eta(u,\bar{x}(u),\bar{y}(u)) \bar{\sigma}_{01}(u, T_a, T_b) du  + \nonumber \\
-& \int_{0}^{t_a} \exp\left(-\int_{s}^{t_a}k_u du \right) \eta(u,\bar{x}(u),\bar{y}(u)) dW_u^{01} 
+\bar{x}_{t_a} &\approx \bar{x}_0(t_a)  + \int_{0}^{t_a} \exp\left(-\int_{s}^{t}k_u du\right) \bar{y}_u du + \int_{0}^{t_a}  \exp\left(-\int_{s}^{t_a}k_u du \right) \eta(u,\bar{x}(u),\bar{y}_u) dW_u^{\mathbb{Q}} \nonumber \\
+&=  \bar{x}_0(t)  + \int_{0}^{t_a} \exp\left(-\int_{s}^{t_a}k_u du\right) \bar{y}_u du + \int_{0}^{t_a} \exp\left(-\int_{s}^{t_a}k_u du \right) \eta(u,\bar{x}_u,\bar{y}_u) \bar{\sigma}_{01}(u, t_a, t_b) du  + \nonumber \\
+& \int_{0}^{t_a} \exp\left(-\int_{s}^{t_a}k_u du \right) \eta(u,\bar{x}_u,\bar{y}_u) dW_u^{01} 
 \end{align}
@@
 \begin{align}
-\mathbb{E}^{01}\left(\bar{x}_t\right) &\approx \bar{x}_0(t_a)  + \int_{0}^{t_a} \exp\left(-\int_{s}^{t_a}k_u du\right) \bar{y}(u) du \nonumber \\ 
-+ &\int_{0}^{t_a} \exp\left(-\int_{s}^{t_a}k_u du \right) \eta(u,\bar{x}(u),\bar{y}(u)) \bar{\sigma}_{01}(u, t_a, t_b) du
-\end{align}
+\mathbb{E}^{01}\left(\bar{x}_t\right) &\approx \bar{x}_0(t_a)  + \int_{0}^{t_a} \exp\left(-\int_{s}^{t_a}k_u du\right) \bar{y}_u du \nonumber \\ 
++ &\int_{0}^{t_a} \exp\left(-\int_{s}^{t_a}k_u du \right) \eta(u,\bar{x}_u,\bar{y}_u) \bar{\sigma}_{01}(u, t_a, t_b,\bar{x}_0(t_a)) du
+\end{align}
+with
+$$
+\bar{\sigma}_{01}(u, t_a, t_b,\bar{x}_0(t_a)) = \sum_{i=a+1}^{b} w_i(0) \nu(t,t_i,\bar{x}_0(t_a))
+$$
+and
+$$
+\nu(t,t_i,\bar{x}_0(t_a)) = \int_{t}^{t_i} \sigma(t,u,\bar{x}_0(t_a),\bar{y}_u) du.
+$$
 
@@
 \begin{align*}
-\bar{x}_{T_a} &\approx  \bar{x}_0(t_a)  + \int_{0}^{t_a} \exp\left(-\int_{s}^{t_a}k_u du\right) \bar{y}(u) du + \int_{0}^{t_a} \exp\left(-\int_{s}^{t_a}k_u du\right) \bar{\sigma}_{01}(u,t_a,t_b) du \nonumber \\\
-&+  \int_{0}^{t_a}  \exp\left(-\int_{s}^{t_a}k_u du \right) \eta(u,\bar{x}(u),\bar{y}(u)) dW_u^{\mathbb{Q}^{01}}.
+\bar{x}_{T_a} &\approx  \bar{x}_0(t_a)  + \int_{0}^{t_a} \exp\left(-\int_{s}^{t_a}k_u du\right) \bar{y}_u du + \int_{0}^{t_a} \exp\left(-\int_{s}^{t_a}k_u du\right) \bar{\sigma}_{01}(u,t_a,t_b) du \nonumber \\\
+&+  \int_{0}^{t_a}  \exp\left(-\int_{s}^{t_a}k_u du \right) \eta(u,\bar{x}_u,\bar{y}_u) dW_u^{\mathbb{Q}^{01}}.
 \end{align*}
@@
 \begin{align*}
-\bar{M}^{01}(s,t_a) &= \exp\left(-\int_{s}^{t_a} \left(\frac{\left(\partial_x \beta(u,T_a,\bar{x}_0,\bar{y}_{t_a})\right)^{2}}{2} + \exp\left(-\int_{u}^{t_a}k_u du\right)\eta(u,\bar{x}(u),\bar{y}(u) \mu(u,t_a,t_b) du \right)\right) \\
+\bar{M}^{01}(s,t_a) &= \exp\left(-\int_{s}^{t_a} \left(\frac{\left(\partial_x \beta(u,T_a,\bar{x}_0,\bar{y}_{t_a})\right)^{2}}{2} + \exp\left(-\int_{u}^{t_a}k_u du\right)\eta(u,\bar{x}_u,\bar{y}_u \mu(u,t_a,t_b) du \right)\right) \\
 &\exp\left(\int_{s}^{t_a} \partial_x \beta(u,t_a,\bar{x}_0,\bar{y}_{t_a}) dW^{\mathbb{Q}^{01}}_u \right)
@@
 \end{equation}
-If we use (\ref{approximation_D_s_x_t}) with $T_a=t_0$ and $\beta(t,t_0,x,y) = \exp\left(-\int_{s}^{T_a}k_u du \right) \eta(u,x,y)$, we have that
+If we use (\ref{approsimation_E_s_x_t}) with $T_a=t_0$ and $\beta(t,t_0,x,y) = \exp\left(-\int_{s}^{T_a}k_u du \right) \eta(u,x,y)$, we have that
 \begin{align*}
@@
 \begin{equation}\label{approximation_clarkocone}
-\mathbb{E}_s\left( D_s L_{E}(t_0,t_1,t_2) \right) = \frac{P_{E}(0,t_1)}{\delta_{t_1,t_2} P_{E}(0,t_2)} \left(G(t_0,t_2)  - G(t_0,t_1)\right)\beta(t,t_0,x_0,\bar{y}_s)\bar{M}(s,t_0).
+\mathbb{E}_s\left( D_s L_{E}(t_0,t_1,t_2) \right) = \frac{P_{E}(0,t_1)}{\delta_{t_1,t_2} P_{E}(0,t_2)} \left(G(t_0,t_2)  - G(t_0,t_1)\right)\beta(t,t_0,x_0,\bar{y}_s).
 \end{equation}
@@
 \subsection{Proof Theorem \ref{Th_CA_OIS}}\label{Proof_CA_OIS_futures}
-To prove it, we will do several observations. The first observation is that if we define $F(t,t_0,t_1) = \mathbb{E}^{\mathbb{Q}^{t_1}}\left( R(t_0,t_1)\right)$, then we have that
-\begin{align*}
-F(t,t_0,t_1)&= \frac{1}{P_{ois}(t,t_1)}  \mathbb{E}_{t}^{\mathbb{Q}}\left(\exp\left(-\int_{t}^{t_1} r_{ois,u} du \right) R(t_0,t_1) \right) = \frac{1}{\delta_{t_0,t_1}}\left(\frac{P_{ois}(t,t_0)}{P_{ois}(t,t_1)} - 1\right), \quad t \in [0,t_0] \\
-F(t,t_0,t_1)&= \frac{1}{P_{ois}(t,t_1)} \mathbb{E}_{t}^{\mathbb{Q}}\left(\exp\left(-\int_{t}^{t_1} r_{ois,u} du \right) R(t_0,t_1) \right) = \frac{1}{\delta_{t_0,t_1}} \left(\frac{\left( \exp\left(\int_{t}^{t_1}r_{ois,u} du\right)\right)}{P_{ois}(t_0,t)}-1\right), \quad  t \in  [t_0, t_1].
-\end{align*}
-The convexity adjustment for $ R(t_0,t_1)$ can be defined as
-\begin{equation}\label{R_ois_ca}
-CA_{ois}(t,t_0,t_1) = F(t,t_0,t_1) - \bar{R}(t,t_0,t_1).
-\end{equation}
-The second observation is that we have the following equivalence
-\begin{equation}\label{R_ois_avg}
-\mathbb{E}^{\mathbb{Q}}\left(R_{avg}(t_0,t_1) \right) = \mathbb{E}^{\mathbb{Q}}\left( \frac{\log\left(1+ \delta_{t_0,t_1} R(t_0,t_1) \right)}{\delta_{t_0,t_1}} \right)  \end{equation}
-To compute $\mathbb{E}^{\mathbb{Q}}\left(R(t_0,t_1)\right)$, we apply $D_s$ on $I(t_0,t_1)$ obtaining that
+To compute $\mathbb{E}^{\mathbb{Q}}\left(R(t_0,t_1)\right)$ we will use (\ref{general_convexity}), with $\mathbb{Q}_2 = \mathbb{Q}$, $\mathbb{Q}_1 = \mathbb{Q}^{t_1}$ and $x_{t_1}=R(t_0,t_1)$.
+If we apply $D_s$ on $I(t_0,t_1)$ we obtain that
 \begin{equation*}

### 2023-03-28 Latex/paper-resum.tex
Changes Abstract/Conclusions
Changes in the Abstract and the conclusions. Change on the last figure's position.

@@
 
-\title{\textcolor{Navy}{\textsc{Convexity adjustments with a bit of Malliavin}}}
+\title{\textcolor{Navy}{\textsc{Convexity adjustments \`a la Malliavin}}}
 
@@
 \begin{abstract}
-AA
+In this paper, we develop a novel method based on the Malliavin calculus to find an approximation for the convexity adjustment for various classical interest rate products.
+Malliavin calculus provides a simple way to get a template for the convexity adjustment.
+We find the approximation for Futures, OIS Futures, FRAs, and CMSs under a general family of the one-factor Cheyette model.
+We have also seen the excellent quality of the numerical accuracy of the formulas obtained.
 \end{abstract}
@@
 
-\begin{figure}[h]
+\begin{figure}[H]
 	\begin{center}
@@
 \section{Conclusions}\label{sec:Conclusion}
-In the present paper, we have shown how we can use Malliavin calculus to find the convexity adjustment for several typical interest rate products.
-We have seen, that Malliavin calculus provides us with a simple way to get a template for the convexity adjustment of several products under a general Cheyette model dynamic with one factor.
-The method is extrapolated with little effort to a Cheyette model with stochastic volatility, or even a  Cheyette model with several factors.
-We have also seen, the good accuracy of the formulas that we have got using this method.
+In the present paper, we develop a novel method based on the Malliavin calculus to find an approximation for the convexity adjustment for various classical interest rate products.
+Although the convexity adjustment could be calculated using other techniques, Malliavin calculus provides a simple way to get a template for the convexity adjustment.
+We find the approximation for Futures, OIS Futures, FRAs, and CMSs under a general family of the one-factor Cheyette model.
+We have also seen the excellent quality of the numerical accuracy of the formulas obtained.
+
+In future work, the methodology could be extrapolated to a Cheyette model with stochastic volatility or even to a model with several factors.
 

### 2023-03-31 Latex/paper-resum.tex
# last version. I have ended the appendix a.1.4

@@
 \begin{eqnarray}
-\bar{x}_{t_a}:= \bar{x}_0(t_a)  &+& \int_{0}^{t_a} \exp\left(-\int_{s}^{t_a}k(u) du\right) \bar{y}_u du \nonumber \\
+\bar{x}_{t_a}:= \bar{x}_0(t_a)&+&\int_{0}^{t_a} \exp\left(-\int_{s}^{t_a}k(u) du\right) \bar{y}_u du \nonumber \\
 &+& \int_{0}^{t_a}  \exp\left(-\int_{s}^{t_a}k(u) du \right) \eta(u,\bar{x}(u),\bar{y}_u) dW_u^{\mathbb{Q}}   \label{approximation_x_t_a}
@@
 \begin{equation}\label{ca_approximation_futures}
-CA(t,t_0,t_1) \approx \frac{P_{E}(0,t_1)}{\delta_{t_1,t_2} P_{E}(0,t_2)} \left(G(t_0,t_2)  - G(t_0,t_1) \right) \int_{0}^{t_0} \beta(s,t_0,\bar{x}_0(t_0),\bar{y}_s) \nu(s,t_2) ds. 
+CA(t,t_0,t_1) = \frac{P_{E}(0,t_1)}{\delta_{t_1,t_2} P_{E}(0,t_2)} \left(G(t_0,t_2)  - G(t_0,t_1) \right) \int_{0}^{t_0} \beta(s,t_0,\bar{x}_0(t_0),\bar{y}_s) \nu(s,t_2) ds + E(t_0). 
 \end{equation}
@@
 \end{equation*}
+And $\|E(t_0)\|^{2}_{2} \sim \mathcal{O}(t_0) \quad \text{when} \quad t_0 \to 0$ and $\|E(t_0)\|^{2}_{2} < \infty \quad \text{when} \quad t_0 \to \infty$. 
 \end{theorem}
@@
 \begin{equation}\label{convexity_ois_future}
-\bar{R}(t_0,t_1) \approx \frac{\exp\left(\mathbb{E}_t^{\mathbb{Q}}\left(I(t_0,t_1)\right)\right)\exp\left(-\int_{t}^{t_1}\frac{\Gamma^{2}(s,t_0,t_1)}{2} ds\right) - 1}{\delta_{t_0,t_1}}
+\bar{R}(t_0,t_1) = \frac{\exp\left(\mathbb{E}_t^{\mathbb{Q}}\left(I(t_0,t_1)\right)\right)\exp\left(-\int_{t}^{t_1}\frac{\Gamma^{2}(s,t_0,t_1)}{2} ds\right) - 1}{\delta_{t_0,t_1}} + E(t_0)
 \end{equation}
@@
 \end{theorem}
-with  $\Gamma(s,t_0,t_1)= \eta(s,x_0,y_0)\int_{\max(s, t_{0})}^{t_1} \exp\left( -\int_{s}^{u} k_{s^{\prime}} ds^{\prime}\right)du$
+where  $\Gamma(s,t_0,t_1)= \eta(s,x_0,y_0)\int_{\max(s, t_{0})}^{t_1} \exp\left( -\int_{s}^{u} k_{s^{\prime}} ds^{\prime}\right)du$, and $\|E(t_0)\|^{2}_{2} \sim \mathcal{O}(t_0) \quad \text{when} \quad t_0 \to 0$ and $\|E(t_0)\|^{2}_{2} < \infty \quad \text{when} \quad t_0 \to \infty$.
 \begin{proof}
@@
 \begin{equation}\label{ca_approximations_fra_arrears}
-CA(t_0,t_1) \approx   \frac{G(t_1,t_2)}{\delta_{t_1,t_2}P_{E}(0,t_1,t_2)} \beta(s,t_1, \bar{x}_0(t_1), \bar{y}_s) \int_{0}^{t_1} \bar{DM}(s,t_1) (\bar{\nu}(s,t_2,\bar{x}_{0}(t_1))-\bar{\nu}(s,t_1,\bar{x}_{0}(t_1))) ds
-\end{equation}
+CA(t_0,t_1) =   \frac{G(t_1,t_2)}{\delta_{t_1,t_2}P_{E}(0,t_1,t_2)} \beta(s,t_1, \bar{x}_0(t_1), \bar{y}_s) \int_{0}^{t_1} \bar{DM}(s,t_1) (\bar{\nu}(s,t_2,\bar{x}_{0}(t_1))-\bar{\nu}(s,t_1,\bar{x}_{0}(t_1))) ds E(t_1)
+\end{equation}
+with $\|E(t_1)\|^{2}_{2} \sim \mathcal{O}(t_1) \quad \text{when} \quad t_1 \to 0$ and $\|E(t_1)\|^{2}_{2} < \infty \quad \text{when} \quad t_1 \to \infty$
 \end{theorem}
@@
 
-Under one-factor HJM model, we can suppose that variability of $\alpha(t,t^{E}_{i-1}, t^{E}_{i})$ is low. Therefore, it is reasonable to freeze it at time $t=0$. Having
+We will suppose that variability of spread term structure $\alpha(t,t^{E}_{i-1}, t^{E}_{i})$ is low. Therefore, it is reasonable to freeze it at time $t=0$. Having
 \begin{equation}\label{approximation_basis_swap}
@@
 CA_{CMS}(t_p) &\approx \frac{\partial_x S_{a,b}(t_a,\bar{x}_0(t_a), \bar{y}_0) \partial_x M(t_a,t_p,\bar{x}_0(t_a), \bar{y}_0)}{M(0,t_p)} \nonumber \\
-&\cdot \int_{0}^{t_a}  \beta^2(s,t_a,\bar{x}_0(t_a),\bar{y}_s) \exp\left(-2\int_{s}^{t_a}\beta(u,t_a,\bar{x}_{0}(t_a),\bar{y}_u) \mu(u,t_a,t_b) du \right)ds 
+&\cdot \int_{0}^{t_a}  \beta^2(s,t_a,\bar{x}_0(t_a),\bar{y}_s) \exp\left(-2\int_{s}^{t_a}\partial_x (\beta(u,t_a,\bar{x}_u,\bar{y}_u) \mu(u,\bar{x}_u, \bar{y}_u,t_a,t_b))|_{\bar{x}_u=\bar{x}_{0}(t_a)}  du \right)ds \nonumber \\
+&+ E(t_a)
 \end{align}
 with  $\beta(u,t_a,x,y) = \exp\left(-\int_{u}^{t_a}k_u du\right)\eta(u,x,y)$.
+And $\|E(t_a)\|^{2}_{2} \sim \mathcal{O}(t_a) \quad \text{when} \quad t_a \to 0$ and $\|E(t_a)\|^{2}_{2} < \infty \quad \text{when} \quad t_a \to \infty$
 \end{theorem}
@@
 \begin{remark}
-The key point is calculate an approximation of $\mathbb{E}_s^{0,1}\left( D_s x_{t_a}\right)$.
+The key point is calculate an approximation of $\mathbb{E}_s^{0,1}\left( D_s \bar{x}_{t_a}\right)$.
 The simplest cases are on the Hull-White or Ho-Lee model.
@@
 \begin{example}[Convexity adjustment for CMS under the Hull-White model]
-To check the accuracy of the last approximation, we compute with a Monte Carlo the exact value of $\mathbb{E}^{t_p}\left(S^{ois}_{a,b}(t_a)\right)$ under spot measure $\mathbb{Q}$, i.e we will compute  $\frac{1}{P(0,t_p)}  \mathbb{E}^{\mathbb{Q}}\left(\frac{S_{a,b}(t_a)}{\beta_{t_a}} \right)$.\\
-In the Hull-White model case, we have that
+To check the accuracy of the last approximation, we compute with a Monte Carlo the exact value of $\mathbb{E}^{t_p}\left(S^{ois}_{a,b}(t_a)\right)$ under spot measure $\mathbb{Q}$, i.e we will compute  $\frac{1}{P(0,t_p)}  \mathbb{E}^{\mathbb{Q}}\left(\frac{S_{a,b}(t_a)}{\beta_{t_a}} \right)$.
+For the Hull-White model case, we have that
 \begin{equation*}
@@
 \end{equation*}
+and the volatility is only time-dependent i.e 
+$$
+\partial_x (\beta(u,t_a,\bar{x}_u,\bar{y}_u) \mu(u,\bar{x}_u, \bar{y}_u,t_a,t_b)) = 0.
+$$
 Therefore, \eqref{cms_first_order_convexity} is equal to
@@
 
-In Figure \ref{fig:CMS}, we observe the CMS convexity adjustment when the tenor of the underlying swap is 5Y.
-We compare the last approximation and a Monte Carlo for a Hull-White model with parameters $\sigma=0.01$ and $k=0.0007$
+In Figure \ref{fig:CMS}, we can observe the CMS convexity adjustment when the tenor of the underlying swap is 5Y.
+We have compared the above approximation and a Monte Carlo for a Hull-White model with parameters $\sigma=0.01$ and $k=0.0007$
 
@@
 \subsection{Approximation of $\mathbb{E}^{01}\left(D_s \bar{x}_{t_a} \right)$}\label{approximation_under_annuity_measeure_d_s}
-Let us to remember that $\nu(t,t_i)=h(t,\bar{x}_t,\bar{y}_t) \frac{G(t,t_i)}{\beta_{t,k}}$ with  $\beta_{t,k} = \exp\left(\int_{0}^{t}k(u)\right)$.
+Let us to remember that $\nu(t,t_i)=h(t,\bar{x}_t,\bar{y}_t) \frac{G(t,t_i)}{\beta_{t,k}(t)}$ with  $\beta_{t,k}(t) = \exp\left(\int_{0}^{t}k(u)\right)$.
 Therefore 
@@
 \begin{equation}
-D_s \sigma_{0,1}(t,t_a,t_b) \approx  D_s \bar{x}_t \mu(t,t_a,t_b)
+D_s \sigma_{0,1}(t,t_a,t_b) =  D_s \bar{x}_t \mu(t,\bar{x}_t, \bar{y}_t, t_a,t_b)
 \end{equation}
@@
 $$
-\mu(t,T_a,T_b) =  \sum_{i=a+1}^{b} w_i \partial_x \nu(t,t_i, \bar{x}_t, \bar{y}_t) \frac{G(t,t_i)}{\beta_{t,k}}.
+\mu(t,\bar{x}_t, \bar{y}_t, t_a,t_b) =  \sum_{i=a+1}^{b} w_i(t) \partial_x \nu(t,t_i, \bar{x}_t, \bar{y}_t) \frac{G(t,t_i)}{\beta_{t,k}}.
 $$
-Now, if we use the last approximation and (\ref{approximation_o1_vol}) in (\ref{approximation_x_t_a}) together with the Girsanov's theorem, we have that
-\begin{align*}
-\bar{x}_{T_a} &\approx  \bar{x}_0(t_a)  + \int_{0}^{t_a} \exp\left(-\int_{s}^{t_a}k_u du\right) \bar{y}_u du + \int_{0}^{t_a} \exp\left(-\int_{s}^{t_a}k_u du\right) \bar{\sigma}_{01}(u,t_a,t_b) du \nonumber \\\
+and $\frac{\delta_{i-1,i} P(t,t_i)}{01(t,t_a,t_b)}$. Now, from (\ref{approximation_x_t_a}) together with the Girsanov's theorem, we have that
+\begin{align*}
+\bar{x}_{T_a} &=  \bar{x}_0(t_a)  + \int_{0}^{t_a} \exp\left(-\int_{s}^{t_a}k_u du\right) \bar{y}_u du + \int_{0}^{t_a} \exp\left(-\int_{s}^{t_a}k_u du\right) \sigma_{01}(u,t_a,t_b) \mu(u,\bar{x}_u, \bar{y}_u, t_a,t_b) du \nonumber \\\
 &+  \int_{0}^{t_a}  \exp\left(-\int_{s}^{t_a}k_u du \right) \eta(u,\bar{x}_u,\bar{y}_u) dW_u^{\mathbb{Q}^{01}}.
 \end{align*}
-Therefore
-\begin{equation*}
-D_s \bar{x}_{t_a} \approx  \exp\left(-\int_{s}^{t_a}k_u du \right) \eta(s,\bar{x}_0,\bar{y}_{t_a})\bar{M}^{01}(s,t_a)
+Then, if we take $D_s$ we get that
+\begin{equation*}
+D_s \bar{x}_{t_a} = \exp\left(-\int_{s}^{t_a}k_u du \right) \eta(s,\bar{x}_0,\bar{y}_{t_a})\bar{M}^{01}(s,t_a)
 \end{equation*}
@@
 \begin{align*}
-\bar{M}^{01}(s,t_a) &= \exp\left(-\int_{s}^{t_a} \left(\frac{\left(\partial_x \beta(u,T_a,\bar{x}_0,\bar{y}_{t_a})\right)^{2}}{2} + \exp\left(-\int_{u}^{t_a}k_u du\right)\eta(u,\bar{x}_u,\bar{y}_u \mu(u,t_a,t_b) du \right)\right) \\
+\bar{M}^{01}(s,t_a) &= \exp\left(-\int_{s}^{t_a} \left(\frac{\left(\partial_x \beta(u,t_a,\bar{x}_u,\bar{y}_{u})\right)^{2}}{2} + \partial_x (\beta(u,t_a,\bar{x}_u,\bar{y}_{u}) \mu(u,\bar{x}_u,\bar{y}_u,t_a,t_b)) du \right)\right) \\
 &\exp\left(\int_{s}^{t_a} \partial_x \beta(u,t_a,\bar{x}_0,\bar{y}_{t_a}) dW^{\mathbb{Q}^{01}}_u \right)
 \end{align*}
-and $\beta(u,t_a,x,y) = \exp\left(-\int_{u}^{t_a}k_u du\right)\eta(u,x,y)$. Then
+and $\beta(u,t_a,x,y) = \exp\left(-\int_{u}^{t_a}k_u du\right)\eta(u,x,y)$.
 
 \begin{align}\label{approximation_E_01_Ds_x_t}
-\mathbb{E}^{01}_s\left(D_s \bar{x}_{t_a}\right) &\approx \beta(s,t_a,\bar{x}_s,\bar{y}_s)  \mathbb{E}_s^{01}\left(\exp\left(-\int_{s}^{t_a}\beta(u,t_a,\bar{x}_u,\bar{y}_u) \mu(u,t_a,t_b) du \right)\right) \nonumber \\
-&\approx \beta(s,t_a,\bar{x}_s,\bar{y}_s) \exp\left(-\int_{s}^{t_a}\beta(u,t_a,\bar{x}_{0}(t_a),\bar{y}_u) \mu(u,t_a,t_b) du \right)
+\mathbb{E}^{01}_s\left(D_s \bar{x}_{t_a}\right) &= \beta(s,t_a,\bar{x}_s,\bar{y}_s)  \mathbb{E}_s^{01}\left(\exp\left(-\int_{s}^{t_a}\partial_x (\beta(u,t_a,\bar{x}_u,\bar{y}_u) \mu(u,\bar{x}_u, \bar{y}_u,t_a,t_b)) du \right)\right) \nonumber \\
+&\approx \beta(s,t_a,\bar{x}_s,\bar{y}_s) \exp\left(-\int_{s}^{t_a}\partial_x (\beta(u,t_a,\bar{x}_u,\bar{y}_u) \mu(u,\bar{x}_u, \bar{y}_u,t_a,t_b))|_{\bar{x}_u=\bar{x}_{0}(t_a)}  du \right)
 \end{align}
@@
 \\
-In this case, we will choose $\bar{x}_0(t_a)$ such that $S_{a,b}(t_a,\bar{x}_0(t_a),\bar{y}_{t_a})=S_{a,b}(0)$. If we apply Clark-Ocone formula to $M(t_a,t_p)$ we get that
+In this case, we will choose $\bar{x}_0(t_a)$ such that $S_{a,b}(t_a,\bar{x}_0(t_a),\bar{y}_{t_a})=S_{a,b}(0)$. Now, if we apply Clark-Ocone formula to $M(t_a,t_p)$ we get that
 \begin{equation} \label{clark_ocone_swap_m}
@@
 \end{align}
-Now if we use (\ref{approximation_E_01_Ds_x_t}) and choose $\bar{x}_0(t_a)$ such that $S_{a,b}(t_a,\bar{x}_0(t_a),\bar{y}_{t_a})=S_{a,b}(0)$, we have that
+Now from (\ref{approximation_E_01_Ds_x_t}) and choosing $\bar{x}_0(t_a)$ such that $S_{a,b}(t_a,\bar{x}_0(t_a),\bar{y}_{t_a})=S_{a,b}(0)$, we have that
 \begin{align}
 \mathbb{E}^{t_p}\left(S_{a,b}(t_a)\right) &\approx  S^{ois}_{a,b}(0) + \frac{\partial_x S_{a,b}(t_a,\bar{x}_0(t_a), \bar{y}_0) \partial_x M(t_a,t_p,\bar{x}_0(t_a), \bar{y}_0)} \nonumber \\
-&\cdot \int_{0}^{t_a}  \beta^2(s,t_a,\bar{x}_0(t_a),\bar{y}_s) \exp\left(-2\int_{s}^{t_a}\beta(u,t_a,\bar{x}_{0}(t_a),\bar{y}_u) \mu(u,t_a,t_b) du \right)ds 
+&\cdot \int_{0}^{t_a}  \beta^2(s,t_a,\bar{x}_0(t_a),\bar{y}_s)\exp\left(-\int_{s}^{t_a}\partial_x (\beta(u,t_a,\bar{x}_u,\bar{y}_u) \mu(u,\bar{x}_u, \bar{y}_u,t_a,t_b))|_{\bar{x}_u=\bar{x}_{0}(t_a)}  du \right)ds
 \end{align}

### 2023-03-31 Latex/paper-resum.tex
Change on the curves definitions

@@
 
-Before the financial crisis, there was a single curve framework based on the same curve for discounting and forecasting.
+%Before the financial crisis, there was a single curve framework based on the same curve for discounting and forecasting.
 Since then, the market has adopted a multi-curve approach with two different curves: the discount curve and the estimation curve chosen based on the maturity of the underlying rate.
@@
 In other words, the estimation forward curve $f_{E}(t, T)$ is given by
+%\begin{equation}\label{estimation_forward_rate_curve}
+%f_{E}(t,T) = f_{ois}(t,T) + s(t,T)
+%\end{equation}
+%where and $f_{ois}$ is the discount curve and $s(t,T)$ are the basis between the two curves, i.e. $s(t,T)= f_{E}(0,T) - f_{ois}(0,T)$.\\
+
+Before the financial crisis, there was a single curve framework based on the same curve for discounting and forecasting.
+Since then, the market has adopted a multi-curve approach with two different curves: the discount curve and the estimation curve.
+We will use the following notation:
+\begin{itemize}
+	\item The \textbf{\textit{discount curve}} is built with OIS instruments which are considered the best approximation for the risk-free rate.
+We will denote the forward discount rate curve by $f_{ois}(t,T)$ and the discount curve by $P_{ois}(t,T)$.
+
+	\item The \textbf{\textit{estimation curve}} is chosen based on the maturity of the underlying rate.
+Until the crisis, the spread between the OIS and the Ibor was negligible.
+For example, the OIS 6M and Ibor 6M.
+Nowadays, due to credit and liquidity reasons, there is a spread between them.
+As a consequence, the estimation curve is tenor-dependent.
+We will denote the forward estimation rate curve by $f_{E}(t,T)$ and the estimation discount curve by $P_{E}(t,T)$.
+
+	\item The \textbf{\textit{basis curve}} is the difference between the estimation curve and the discount curve, i.e.
+$s(t,t+T)= f_{E}(0,T) - f_{ois}(0,T)$.
+In this paper, we will assume that the basis are not stochastic.
+Therefore, it can be obtained directly from the market at time $t=0$.
+The basis curve is denoted by $s(t,T)$.
+	\end{itemize}
+
+Consequently, the estimation forward curve $f_{E}(t, T)$ is given by
 \begin{equation}\label{estimation_forward_rate_curve}
-f_{E}(t,T) = f_{ois}(t,T) + s(t,T)
-\end{equation}
-where and $f_{ois}$ is the discount curve and $s(t,T)$ are the basis between the two curves, i.e. $s(t,T)= f_{E}(0,T) - f_{ois}(0,T)$.\\
+f_{E}(t,T) = f_{ois}(t,T) + s(t,T).
+\end{equation}
 
@@
 \subsection{The model}
-We will assume that the $f_{ois}$ dynamics follows a single factor Heath-Jarrow-Morton model under the $\mathbb{Q}$-measure.
+We will assume that the $f_{ois}$ dynamics follows a single factor Heath-Jarrow-Morton (HJM) model under the $\mathbb{Q}$-measure.
 Therefore, let $T>0$ a fixed time horizon, $t>0$ the starting time, and $W$ a Brownian motion defined on a complete probability space $(\omega, \mathcal{F}, \mathbb{P})$.

### 2023-04-01 Latex/paper-resum.tex
# last version

@@
 \begin{itemize}
-	\item The \textbf{\textit{discount curve}} is built with OIS instruments which are considered the best approximation for the risk-free rate.
+	\item The \textbf{\textit{discount forward curve}} is built with OIS instruments which are considered the best approximation for the risk-free rate.
 We will denote the forward discount rate curve by $f_{ois}(t,T)$ and the discount curve by $P_{ois}(t,T)$.
 
-	\item The \textbf{\textit{estimation curve}} is chosen based on the maturity of the underlying rate.
+	\item The \textbf{\textit{estimation forward curve}} is chosen based on the maturity of the underlying rate.
 Until the crisis, the spread between the OIS and the Ibor was negligible.
@@
 
-	\item The \textbf{\textit{basis curve}} is the difference between the estimation curve and the discount curve, i.e.
-$s(t,t+T)= f_{E}(0,T) - f_{ois}(0,T)$.
+	\item The \textbf{\textit{basis forward curve}} is the difference between the estimation forward curve and the discount forward curve, i.e.
+$s(t,T)= f_{E}(t,T) - f_{ois}(t,T)$.
 In this paper, we will assume that the basis are not stochastic.
-Therefore, it can be obtained directly from the market at time $t=0$.
-The basis curve is denoted by $s(t,T)$.
+Therefore, it can be obtained directly from the market at time $t=0$ i.e $s(t,t + u)= s(0,u)$ for $u \geq 0$.
 	\end{itemize}
@@
 with initial condition $\bar{x}_{0}(t_a)$ will be chosen appropriately depending on the case.
-In the appendix \ref{estimation_error_l2} we can find the estimation for $\mathbb{E}((x_t-\bar{x}_t)^{2})$.
+In the appendix \ref{estimation_error_l2} we can find the estimation for $\mathbb{E}((x_t-\bar{x}_t)^{2})$ and thr order of this approximation.
 
@@
 \begin{align*}
-\alpha_1 \leq \eta(t,x,y) \leq \alpha_2 \quad \forall (t,x,y) \in \mathbb{R}^{+} \times \mathbb{R} \times \mathbb{R}^{+}. \\
+\alpha_1 \leq \eta(t,x,y) \leq \alpha_2 \quad \forall (t,x,y) \in \mathbb{R}^{+} \times \mathbb{R} \times \mathbb{R}^{+} \quad \text{and} \quad \alpha_1, \alpha_2 > 0. \\
 |\eta(t,x_2,y_2) - \eta(t,x_1,y_1)| \leq C_{x,y} \lVert (x_2-x_1,y_2-y_1)\rVert \quad \forall (t,x,y) \in \mathbb{R}^{+} \times \mathbb{R} \times \mathbb{R}^{+} 
@@
 
-In order to introduce a general idea of the method.
-Let define a $Z_t = f(x_t)$.
-Now, we suppose that $Z_t$ is martingale under the measure $\mathbb{Q}_1$ and that we want to compute $\mathbb{E}^{\mathbb{Q}_2}\left(Z_T \right)$, where $\mathbb{Q}_2$ is a measure such that $dW^{\mathbb{Q}_1}_t = dW^{\mathbb{Q}_2}_t +\lambda_t dt$.
+To introduce a general idea of the method, let us define the process $Z_t = f(x_t)$.
+Now, we suppose that $Z_t$ is martingale under the measure $\mathbb{Q}_1$, but we want to compute $\mathbb{E}^{\mathbb{Q}_2}\left(Z_T \right)$, where $\mathbb{Q}_2$ is a measure under which $Z_t$ is not martingale and such that $dW^{\mathbb{Q}_1}_t = dW^{\mathbb{Q}_2}_t +\lambda_t dt$.
 Then, if we use the Clark-Ocone representation, we have that
@@
 I(t_0,t_1) &= \mathbb{E}_t^{\mathbb{Q}}\left(I(t_0,t_1)\right) + \int_{t}^{t_1}\int_{\max(s, t_{0})}^{t_1}  \mathbb{E}_s^{\mathbb{Q}}\left(\beta(s,u,x_s,y_s) \bar{M}(s,u) \right) du dW_s^{\mathbb{Q}} \nonumber \\
-&\approx \mathbb{E}_t^{\mathbb{Q}}\left(I(t_0,t_1)\right) + \int_{t}^{t_1}\int_{\max(s, t_{0})}^{t_1} \beta(s,u,x_0,\bar{y}_s) du dW_s^{\mathbb{Q}}\nonumber \\
-&= \mathbb{E}_t^{\mathbb{Q}}\left(I(t_0,t_1)\right) + \int_{t}^{t_1} g(s)h(s,x_0,\bar{y}_s)\int_{\max(s, t_{0})}^{t_1} \exp\left( -\int_{s}^{u} k_{s^{\prime}} ds^{\prime}\right) du dW_s^{\mathbb{Q}}.
+&\approx \mathbb{E}_t^{\mathbb{Q}}\left(I(t_0,t_1)\right) + \int_{t}^{t_1}\int_{\max(s, t_{0})}^{t_1} \beta(s,u,\bar{x}_0(t_1),\bar{y}_s) du dW_s^{\mathbb{Q}}\nonumber \\
+&= \mathbb{E}_t^{\mathbb{Q}}\left(I(t_0,t_1)\right) + \int_{t}^{t_1} g(s)h(s,\bar{x}_0(t_1),\bar{y}_s)\int_{\max(s, t_{0})}^{t_1} \exp\left( -\int_{s}^{u} k_{s^{\prime}} ds^{\prime}\right) du dW_s^{\mathbb{Q}}.
 \end{align}
@@
 \begin{equation*}
-CA(t_0,t_1) = \frac{G(t_1,t_2)}{\delta_{t_1,t_2}P_{E}(0,t_1,t_2)} \beta(s,t_1, \bar{x}_0(t_1), \bar{y}_s) \int_{0}^{t_1} \bar{DM}(s,t_1) (\bar{\nu}(s,t_2,\bar{x}_{0}(t_1))-\bar{\nu}(s,t_1,\bar{x}_{0}(t_1))) ds
+CA(t_0,t_1) \approx \frac{G(t_1,t_2)}{\delta_{t_1,t_2}P_{E}(0,t_1,t_2)} \beta(s,t_1, \bar{x}_0(t_1), \bar{y}_s) \int_{0}^{t_1} \bar{DM}(s,t_1) (\bar{\nu}(s,t_2,\bar{x}_{0}(t_1))-\bar{\nu}(s,t_1,\bar{x}_{0}(t_1))) ds
 \end{equation*}

### 2023-04-07 Latex/paper-resum.tex
improve writing
Improve writing.
- The strcutue of the paper ...
- Ending 3.2

@@
 The structure of the paper is as follows.
-In Section \ref{sec:Notation}, we give the basic preliminaries and our notation related to Interest Rates models.
-This notation will be used throughout the paper without being repeated in particular theorems unless we find it useful to do so in order to guide the reader through the results.
-In Section \ref{sec:Malliavin}, we make an introduction to Malliavin calculus.
-In Section \ref{sec:CA}, we compute the convexity adjsustment for several payoffs that are presents as usual way in the interest rate trading desks.
-As well, we do some numerical expresents to check the analytical results obtained.
-To end, in Section \ref{sec:Conclusion} we give the conclusions of the paper and future lines of research to explore.
+In Section \ref{sec:Malliavin}, we give a brief introduction to Malliavin calculus.
+In Section \ref{sec:Notation}, we provide preliminary information and discuss the notation used in the article.
+The notation introduced will not be repeated unless necessary to guide the reader through the results.
+In Section \ref{sec:CA}, we compute the convexity adjustment for several payoffs commonly negotiated in the interest rate trading desks.
+We also present some numerical experiments to check the accuracy of the analytical results obtained.
+We provide the code for these examples at \url{https://github.com/Dagalon/GeneralConvexityAdjustment}.
+The conclusions can be found in Section \ref{sec:Conclusion}, as well as future lines of research to explore.
 
@@
 with initial condition $\bar{x}_{0}(t_a)$ will be chosen appropriately depending on the case.
-In the appendix \ref{estimation_error_l2} we can find the estimation for $\mathbb{E}((x_t-\bar{x}_t)^{2})$ and thr order of this approximation.
+In the appendix \ref{estimation_error_l2} we can find the estimation for $\mathbb{E}((x_t-\bar{x}_t)^{2})$ and the approximation order.
 

### 2023-04-09 Latex/paper-resum.tex
Add Thanks to ...
Add Thanks to ..
Styling
Styling

@@
 
+\newcommand\blfootnote[1]{%
+  \begingroup
+  \renewcommand\thefootnote{}\footnote{#1}%
+  \addtocounter{footnote}{-1}%
+  \endgroup
+}
+
 \title{\textcolor{Navy}{\textsc{Convexity adjustments \`a la Malliavin}}}
@@
 %\clearpage
+\blfootnote{The authors would like to thank Elisa Al\`os for helpful discussions.}
 
@@
 To introduce a general idea of the method, let us define the process $Z_t = f(x_t)$.
-Now, we suppose that $Z_t$ is martingale under the measure $\mathbb{Q}_1$, but we want to compute $\mathbb{E}^{\mathbb{Q}_2}\left(Z_T \right)$, where $\mathbb{Q}_2$ is a measure under which $Z_t$ is not martingale and such that $dW^{\mathbb{Q}_1}_t = dW^{\mathbb{Q}_2}_t +\lambda_t dt$.
+Now, we suppose that $Z_t$ is martingale under the measure $\mathbb{Q}_1$, but we want to compute $\mathbb{E}^{\mathbb{Q}_2}\left[Z_T \right]$, where $\mathbb{Q}_2$ is a measure under which $Z_t$ is not martingale and such that $dW^{\mathbb{Q}_1}_t = dW^{\mathbb{Q}_2}_t +\lambda_t dt$.
 Then, if we use the Clark-Ocone representation, we have that
 \begin{equation*}
-f(x_t) = \mathbb{E}^{\mathbb{Q}_1}\left(f(x_t)\right) + \int_{0}^{t} \mathbb{E}^{\mathbb{Q}_1}_s\left( f^{\prime}(x_t) D_s x_t  \right) dW^{\mathbb{Q}_1}_s
+f(x_t) = \mathbb{E}^{\mathbb{Q}_1}\left[f(x_t)\right] + \int_{0}^{t} \mathbb{E}^{\mathbb{Q}_1}_s\left[ f^{\prime}(x_t) D_s x_t  \right] dW^{\mathbb{Q}_1}_s
 \end{equation*}
@@
 \begin{equation}\label{general_convexity}
-\mathbb{E}^{\mathbb{Q}_2}\left( f(x_t) \right) = f(x_0) + \mathbb{E}^{\mathbb{Q}_1} \left(\int_{0}^{t}  \mathbb{E}^{\mathbb{Q}_1}_s\left( f^{\prime}(x_t) D_s x_t  \right) \lambda_s ds \right). 
+\mathbb{E}^{\mathbb{Q}_2}\left[ f(x_t) \right] = f(x_0) + \mathbb{E}^{\mathbb{Q}_1} \left[\int_{0}^{t}  \mathbb{E}^{\mathbb{Q}_1}_s\left[ f^{\prime}(x_t) D_s x_t  \right] \lambda_s ds \right]. 
 \end{equation}
@@
 \begin{equation}\label{ca_approximation_futures}
-CA(t,t_0,t_1) = \frac{P_{E}(0,t_1)}{\delta_{t_1,t_2} P_{E}(0,t_2)} \left(G(t_0,t_2)  - G(t_0,t_1) \right) \int_{0}^{t_0} \beta(s,t_0,\bar{x}_0(t_0),\bar{y}_s) \nu(s,t_2) ds + E(t_0). 
+CA(t,t_0,t_1) = \frac{P_{E}(0,t_1)}{\delta_{t_1,t_2} P_{E}(0,t_2)} \left(G(t_0,t_2)  - G(t_0,t_1) \right) \int_{0}^{t_0} \beta(s,t_0,\bar{x}_0(t_0),\bar{y}_s) \nu(s,t_2) ds + E[t_0]. 
 \end{equation}
@@
 \end{equation*}
-And $\|E(t_0)\|^{2}_{2} \sim \mathcal{O}(t_0) \quad \text{when} \quad t_0 \to 0$ and $\|E(t_0)\|^{2}_{2} < \infty \quad \text{when} \quad t_0 \to \infty$. 
+and $\|E\left[t_0\right]\|^{2}_{2} \sim \mathcal{O}(t_0)$ when $t_0 \to 0$ and $\|E\left[t_0\right]\|^{2}_{2} < \infty$ when $t_0 \to \infty$. 
 \end{theorem}
@@
 \begin{align*} 
-\bar{R}(t,t_0,t_1) &:= \mathbb{E}_t^{\mathbb{Q}}\left( R(t_0,t_1)  \right), \\
-\bar{R}_{avg}(t,t_0,t_1) &:= \mathbb{E}_t^{\mathbb{Q}}\left( R_{avg}(t_0,t_1)  \right).
-\end{align*}
-Before to continue, we will do several observations. The first observation is that if we define $F(t,t_0,t_1) = \mathbb{E}^{\mathbb{Q}^{t_1}}\left( R(t_0,t_1)\right)$, then we have that
-\begin{align*}
-F(t,t_0,t_1)&= \frac{1}{P_{ois}(t,t_1)}  \mathbb{E}_{t}^{\mathbb{Q}}\left(\exp\left(-\int_{t}^{t_1} r_{ois,u} du \right) R(t_0,t_1) \right) = \frac{1}{\delta_{t_0,t_1}}\left(\frac{P_{ois}(t,t_0)}{P_{ois}(t,t_1)} - 1\right), \quad t \in [0,t_0] \\
-F(t,t_0,t_1)&= \frac{1}{P_{ois}(t,t_1)} \mathbb{E}_{t}^{\mathbb{Q}}\left(\exp\left(-\int_{t}^{t_1} r_{ois,u} du \right) R(t_0,t_1) \right) = \frac{1}{\delta_{t_0,t_1}} \left(\frac{\left( \exp\left(\int_{t}^{t_1}r_{ois,u} du\right)\right)}{P_{ois}(t_0,t)}-1\right), \quad  t \in  [t_0, t_1].
+\bar{R}(t,t_0,t_1) &:= \mathbb{E}_t^{\mathbb{Q}}\left[ R(t_0,t_1)  \right], \\
+\bar{R}_{avg}(t,t_0,t_1) &:= \mathbb{E}_t^{\mathbb{Q}}\left[ R_{avg}(t_0,t_1)  \right].
+\end{align*}
+Before to continue, we will do several observations.
+The first observation is that if we define $F(t,t_0,t_1) = \mathbb{E}^{\mathbb{Q}^{t_1}}\left( R(t_0,t_1)\right)$, then we have that when $t \in [0,t_0]$
+\begin{align*}
+F(t,t_0,t_1)&= \frac{1}{P_{ois}(t,t_1)}  \mathbb{E}_{t}^{\mathbb{Q}}\left[\exp\left(-\int_{t}^{t_1} r_{ois,u} du \right) R(t_0,t_1) \right]\\
+&= \frac{1}{\delta_{t_0,t_1}}\left(\frac{P_{ois}(t,t_0)}{P_{ois}(t,t_1)} - 1\right), %, \quad t \in [0,t_0] \\
+%\end{align*}
+\intertext{and when $t \in  [t_0, t_1]$, we have}
+%\begin{align*}
+F(t,t_0,t_1)&= \frac{1}{P_{ois}(t,t_1)} \mathbb{E}_{t}^{\mathbb{Q}}\left[\exp\left(-\int_{t}^{t_1} r_{ois,u} du \right) R(t_0,t_1) \right]\\
+ &= \frac{1}{\delta_{t_0,t_1}} \left(\frac{\exp\left(\int_{t}^{t_1}r_{ois,u} du\right)}{P_{ois}(t_0,t)}-1\right).%, \quad  t \in  [t_0, t_1].
 \end{align*}
@@
 \begin{equation}\label{R_ois_avg}
-\mathbb{E}^{\mathbb{Q}}\left(R_{avg}(t_0,t_1) \right) = \mathbb{E}^{\mathbb{Q}}\left( \frac{\log\left(1+ \delta_{t_0,t_1} R(t_0,t_1) \right)}{\delta_{t_0,t_1}} \right)  \end{equation}
+\mathbb{E}^{\mathbb{Q}}\left(R_{avg}(t_0,t_1) \right) =\frac{1}{\delta_{t_0,t_1}} \mathbb{E}^{\mathbb{Q}}\left[ \log\left(1+ \delta_{t_0,t_1} R(t_0,t_1) \right) \right]  \end{equation}
 In order, to clarify the convexity expression and the calculations, we will define 
@@
 \begin{equation}\label{convexity_ois_future}
-\bar{R}(t_0,t_1) = \frac{\exp\left(\mathbb{E}_t^{\mathbb{Q}}\left(I(t_0,t_1)\right)\right)\exp\left(-\int_{t}^{t_1}\frac{\Gamma^{2}(s,t_0,t_1)}{2} ds\right) - 1}{\delta_{t_0,t_1}} + E(t_0)
+\bar{R}(t_0,t_1) = \frac{1}{\delta_{t_0,t_1}}\left(\exp\left(\mathbb{E}_t^{\mathbb{Q}}\left[I(t_0,t_1)\right]\right)\exp\left(-\frac{1}{2}\int_{t}^{t_1}\Gamma^{2}(s,t_0,t_1) ds\right) - 1\right) + E[t_0],
 \end{equation}
@@
 \begin{equation}\label{convexity_avg_ois_future}
-\bar{R}_{avg}(t_0,t_1) = \frac{\mathbb{E}_t^{\mathbb{Q}}\left(I(t_0,t_1)\right) }{\delta_{t_0,t_1}} \approx \frac{\log\left(1+\delta_{t_0,t_1}  \mathbb{E}_t^{\mathbb{Q}}\left(R(t_0,t_1)\right) \right)}{\delta_{t_0,t_1}} - \frac{\int_{0}^{t_1}  \Gamma^{2}(s,t_0,t_1) ds}{2\delta_{t_0,t_1}}
-\end{equation}
+\bar{R}_{avg}(t_0,t_1) = \frac{\mathbb{E}_t^{\mathbb{Q}}\left[I(t_0,t_1)\right] }{\delta_{t_0,t_1}} \approx \frac{1}{\delta_{t_0,t_1}}\left(\log\left(1+\delta_{t_0,t_1}  \mathbb{E}_t^{\mathbb{Q}}\left[R(t_0,t_1)\right] \right) - \frac{1}{2}\int_{0}^{t_1}  \Gamma^{2}(s,t_0,t_1) ds\right)
+\end{equation}
+where  
+\begin{equation}
+\Gamma(s,t_0,t_1)= \eta(s,x_0,y_0)\int_{\max(s, t_{0})}^{t_1} \exp\left( -\int_{s}^{u} k_{s^{\prime}} ds^{\prime}\right)du, 
+\end{equation}
+and $\|E[t_0]\|^{2}_{2} \sim \mathcal{O}(t_0)$ when $t_0 \to 0$ and $\|E[t_0]\|^{2}_{2} < \infty$ when $t_0 \to \infty$.
 \end{theorem}
-where  $\Gamma(s,t_0,t_1)= \eta(s,x_0,y_0)\int_{\max(s, t_{0})}^{t_1} \exp\left( -\int_{s}^{u} k_{s^{\prime}} ds^{\prime}\right)du$, and $\|E(t_0)\|^{2}_{2} \sim \mathcal{O}(t_0) \quad \text{when} \quad t_0 \to 0$ and $\|E(t_0)\|^{2}_{2} < \infty \quad \text{when} \quad t_0 \to \infty$.
 \begin{proof}
@@
 \begin{remark}
-We can calculate the convexity adjustment for the case $t_0 < t < t_1$ in a similar way to when $t < t_0$, for this we will define
+We can calculate the convexity adjustment for the case $t_0 < t < t_1$ similarly to when $t < t_0$. For this, we will define
 \begin{equation*}
@@
 \begin{align*}
-\Gamma(s,t_0,t_1) &= \frac{\sigma \exp(-ks)}{k}\left(\exp(-k(\max(s,t_0) - s)) - \exp(-k(t_1-s))\right)\\
-\mathbb{E}^{\mathbb{Q}}\left(I(t_0,t_1)\right)&=-\log\left(\frac{P_{ois}(0,t_1)}{P_{ois}(0,t_0)}\right) + \frac{\sigma^{2}}{2k^{2}}\left(\delta_{t_0,t_1} - 2 \frac{\exp(-kt_0) - \exp(-kt_1)}{k} + \frac{\exp(-2kt_0) - \exp(-2kt_1)}{2k}  \right).
+\Gamma(s,t_0,t_1) &= \frac{\sigma \exp(-ks)}{k}\biggl(\exp(-k(\max(s,t_0) - s)) - \exp(-k(t_1-s))\biggr),\\
+\mathbb{E}^{\mathbb{Q}}\left[I(t_0,t_1)\right]&=-\log\left(\frac{P_{ois}(0,t_1)}{P_{ois}(0,t_0)}\right)\\
+& \text{ }\text{ }\text{ }+ \frac{\sigma^{2}}{2k^{2}}\left(\delta_{t_0,t_1} - 2 \frac{\exp(-kt_0) - \exp(-kt_1)}{k} + \frac{\exp(-2kt_0) - \exp(-2kt_1)}{2k}  \right).
 \end{align*}
 Therefore, we have that
-\begin{align*}
-\frac{\int_{0}^{t_1} \Gamma^{2}(s,t_0,t_1) ds}{2} &= \frac{\sigma^{2}}{2k^2} \int_{0}^{t_1}  \exp(-2ks)\left(\exp(-k(\max(s,t_0) - s)) - \exp(-k(t_1 - s))\right)^{2} ds \\
-&= \frac{\sigma^{2}}{2k^2} \int_{0}^{t_0} \exp(-2ks)\left(\exp(-k(t_0 - s)) - \exp(-k(t_1 - s))\right)^{2} ds\\
-&+ \frac{\sigma^{2}}{2k^2} \int_{t_0}^{t_1} \exp(-2ks)\left(1 - \exp(-k(t_1 - s))\right)^{2} ds\\
-&= \frac{\sigma^{2}t_0}{2k^{2}} \left( \exp(-kt_0) + \exp(-2kt_1) - 2 \exp(-k(t_1+t_0)) \right)\\  
-&+ \frac{\sigma^{2}}{2k^{2}} \left(\frac{\exp(-2kt_0) - \exp(-2kt_1)}{2k}  + \exp(-kt0)t0 - 2 \frac{\exp(-2kt_0) - \exp(-k(t_0 + t_1))}{k}  \right)
+%\begin{align*}
+%\frac{\int_{0}^{t_1} \Gamma^{2}(s,t_0,t_1) ds}{2} &= \frac{\sigma^{2}}{2k^2} \int_{0}^{t_1}  \exp(-2ks)\left(\exp(-k(\max(s,t_0) - s)) - \exp(-k(t_1 - s))\right)^{2} ds \\
+%&= \frac{\sigma^{2}}{2k^2} \int_{0}^{t_0} \exp(-2ks)\left(\exp(-k(t_0 - s)) - \exp(-k(t_1 - s))\right)^{2} ds\\
+%&+ \frac{\sigma^{2}}{2k^2} \int_{t_0}^{t_1} \exp(-2ks)\left(1 - \exp(-k(t_1 - s))\right)^{2} ds\\
+%&= \frac{\sigma^{2}t_0}{2k^{2}} \left( \exp(-kt_0) + \exp(-2kt_1) - 2 \exp(-k(t_1+t_0)) \right)\\  
+%&+ \frac{\sigma^{2}}{2k^{2}} \left(\frac{\exp(-2kt_0) - \exp(-2kt_1)}{2k}  + \exp(-kt0)t0 - 2 \frac{\exp(-2kt_0) - \exp(-k(t_0 + t_1))}{k}  \right)
+%\end{align*}
+\begin{align*}
+\frac{1}{2}\int_{0}^{t_1} \Gamma^{2}(s,t_0,t_1) ds &= \frac{\sigma^{2}t_0}{2k^{2}} \biggl( \exp(-kt_0) + \exp(-2kt_1) - 2 \exp(-k(t_1+t_0)) \biggr)\\  
+&+ \frac{\sigma^{2}}{2k^{2}} \biggl(\frac{\exp(-2kt_0) - \exp(-2kt_1)}{2k}  + \exp(-kt_0)t_0 \\
+&\quad - 2 \frac{\exp(-2kt_0) - \exp(-k(t_0 + t_1))}{k}  \biggr).
 \end{align*}

### 2023-04-12 Latex/paper-resum.tex
Stylish 2

@@
 
-\author[1,2]{David Garcia-Lorite\thanks{Corresponding author, \email{dddd@caixabank.es}}}
+\author[1,2]{David Garcia-Lorite\thanks{Corresponding author, \email{david.garcia.lorite@gmail.com}}}
 \author[3]{Ra\'{u}l Merino}
@@
 %\clearpage
-\blfootnote{The authors would like to thank Elisa Al\`os for helpful discussions.}
+\blfootnote{The authors would like to thank Elisa Al\`os and Josep Vives for helpful discussions.}
 
@@
 \begin{equation}\label{ca_approximation_futures}
-CA(t,t_0,t_1) = \frac{P_{E}(0,t_1)}{\delta_{t_1,t_2} P_{E}(0,t_2)} \left(G(t_0,t_2)  - G(t_0,t_1) \right) \int_{0}^{t_0} \beta(s,t_0,\bar{x}_0(t_0),\bar{y}_s) \nu(s,t_2) ds + E[t_0]. 
+CA(t,t_0,t_1) = \frac{P_{E}(0,t_1)}{\delta_{t_1,t_2} P_{E}(0,t_2)} \left(G(t_0,t_2)  - G(t_0,t_1) \right) \int_{0}^{t_0} \beta(s,t_0,\bar{x}_0(t_0),\bar{y}_s) \nu(s,t_2) ds + E(t_0). 
 \end{equation}
@@
 \end{equation*}
-and $\|E\left[t_0\right]\|^{2}_{2} \sim \mathcal{O}(t_0)$ when $t_0 \to 0$ and $\|E\left[t_0\right]\|^{2}_{2} < \infty$ when $t_0 \to \infty$. 
+and $\|E\left(t_0\right)\|^{2}_{2} \sim \mathcal{O}(t_0)$ when $t_0 \to 0$ and $\|E\left(t_0\right)\|^{2}_{2} < \infty$ when $t_0 \to \infty$. 
 \end{theorem}
@@
 In this section, we will derive the convexity adjustment for short-term interest rate swap, also known as STIRs.
-It is common in the market to find two version of these futures, depending on how the fixings of the refrence index are using.
+It is common in the market to find two version of these futures, depending on how the fixings of the reference index are using.
 Given $t_0 < t_1$, we will define the overnight compounding rate as
@@
 \begin{equation}\label{convexity_ois_future}
-\bar{R}(t_0,t_1) = \frac{1}{\delta_{t_0,t_1}}\left(\exp\left(\mathbb{E}_t^{\mathbb{Q}}\left[I(t_0,t_1)\right]\right)\exp\left(-\frac{1}{2}\int_{t}^{t_1}\Gamma^{2}(s,t_0,t_1) ds\right) - 1\right) + E[t_0],
+\bar{R}(t_0,t_1) = \frac{1}{\delta_{t_0,t_1}}\left(\exp\left(\mathbb{E}_t^{\mathbb{Q}}\left[I(t_0,t_1)\right]\right)\exp\left(-\frac{1}{2}\int_{t}^{t_1}\Gamma^{2}(s,t_0,t_1) ds\right) - 1\right) + E(t_0),
 \end{equation}
@@
 \end{equation}
-and $\|E[t_0]\|^{2}_{2} \sim \mathcal{O}(t_0)$ when $t_0 \to 0$ and $\|E[t_0]\|^{2}_{2} < \infty$ when $t_0 \to \infty$.
+and $\|E(t_0)\|^{2}_{2} \sim \mathcal{O}(t_0)$ when $t_0 \to 0$ and $\|E(t_0)\|^{2}_{2} < \infty$ when $t_0 \to \infty$.
 \end{theorem}
@@
 We can calculate the convexity adjustment for the case $t_0 < t < t_1$ similarly to when $t < t_0$. For this, we will define
-\begin{equation*}
-I(t,t_1):=\int_{t}^{t_1} r_s ds
-\end{equation*}
-and 
-\begin{align*}
-R(t_0,t_1) &:= \frac{1}{\delta_{t_0,t_1}}\left(\frac{\exp(\int_{t}^{t_1} r_{ois,s} ds )}{P_{ois}(t_0,t)} - 1\right), \\
+\begin{align*}
+I(t,t_1)&:=\int_{t}^{t_1} r_s ds,\\
+R(t_0,t_1) &:= \frac{1}{\delta_{t_0,t_1}}\left(\frac{\exp\left(\int_{t}^{t_1} r_{ois,s} ds\right)}{P_{ois}(t_0,t)} - 1\right), \\
+\intertext{and}
 R_{avg}(t_0,t_1) &:= \frac{1}{\delta_{t_0,t_1}}\left(\int_{t_0}^{t} r_{ois,s} ds + \int_{t}^{t_1} r_{ois,s} ds\right).   
@@
 \begin{equation}\label{FRAinArrear}
-P_{E}(0,t_1)\mathbb{E}^{\mathbb{Q}^{t_1}}\left(L_{E}(t_1,t_1,t_2)\right),
+P_{E}(0,t_1)\mathbb{E}^{\mathbb{Q}^{t_1}}\left[L_{E}(t_1,t_1,t_2)\right],
 \end{equation}
@@
 Then, the convexity adjustment approximation for FRAs in Arrears is
-\begin{equation}\label{ca_approximations_fra_arrears}
-CA(t_0,t_1) =   \frac{G(t_1,t_2)}{\delta_{t_1,t_2}P_{E}(0,t_1,t_2)} \beta(s,t_1, \bar{x}_0(t_1), \bar{y}_s) \int_{0}^{t_1} \bar{DM}(s,t_1) (\bar{\nu}(s,t_2,\bar{x}_{0}(t_1))-\bar{\nu}(s,t_1,\bar{x}_{0}(t_1))) ds E(t_1)
-\end{equation}
+\begin{align}\label{ca_approximations_fra_arrears}
+CA(t_0,t_1) =   &\frac{G(t_1,t_2)}{\delta_{t_1,t_2}P_{E}(0,t_1,t_2)} \beta(s,t_1, \bar{x}_0(t_1), \bar{y}_s) E(t_1) \nonumber \\
+&\cdot \int_{0}^{t_1} \overline{DM}(s,t_1) (\bar{\nu}(s,t_2,\bar{x}_{0}(t_1))-\bar{\nu}(s,t_1,\bar{x}_{0}(t_1))) ds 
+\end{align}
 with $\|E(t_1)\|^{2}_{2} \sim \mathcal{O}(t_1) \quad \text{when} \quad t_1 \to 0$ and $\|E(t_1)\|^{2}_{2} < \infty \quad \text{when} \quad t_1 \to \infty$
@@
 \begin{equation*}
-CA(t_0,t_1) \approx \frac{G(t_1,t_2)}{\delta_{t_1,t_2}P_{E}(0,t_1,t_2)}  \frac{\sigma^{2}}{k} \int_{0}^{t_1} \exp(- k(t_1 + u)) -   \exp(- k(t_2 + u)) du 
+CA(t_0,t_1) \approx \frac{G(t_1,t_2)}{\delta_{t_1,t_2}P_{E}(0,t_1,t_2)}  \frac{\sigma^{2}}{k} \int_{0}^{t_1} \Bigl(\exp(- k(t_1 + u)) -   \exp(- k(t_2 + u))\Bigr) du 
 \end{equation*}
@@
 \end{equation}
-Then, we have the temporal convexity adjusment for a CMS rate is approximated by
+Then, we have the temporal convexity adjustment for a CMS rate is approximated by
 \begin{align} \label{cms_first_order_convexity}
-CA_{CMS}(t_p) &\approx \frac{\partial_x S_{a,b}(t_a,\bar{x}_0(t_a), \bar{y}_0) \partial_x M(t_a,t_p,\bar{x}_0(t_a), \bar{y}_0)}{M(0,t_p)} \nonumber \\
-&\cdot \int_{0}^{t_a}  \beta^2(s,t_a,\bar{x}_0(t_a),\bar{y}_s) \exp\left(-2\int_{s}^{t_a}\partial_x (\beta(u,t_a,\bar{x}_u,\bar{y}_u) \mu(u,\bar{x}_u, \bar{y}_u,t_a,t_b))|_{\bar{x}_u=\bar{x}_{0}(t_a)}  du \right)ds \nonumber \\
-&+ E(t_a)
+CA(t_p) &\approx  E(t_a) + \frac{\partial_x S_{a,b}(t_a,\bar{x}_0(t_a), \bar{y}_0) \partial_x M(t_a,t_p,\bar{x}_0(t_a), \bar{y}_0)}{M(0,t_p)} \nonumber \\
+&\cdot \int_{0}^{t_a}  \beta^2(s,t_a,\bar{x}_0(t_a),\bar{y}_s) \exp\left(-2\int_{s}^{t_a}\partial_x (\beta(u,t_a,\bar{x}_u,\bar{y}_u) \mu(u,\bar{x}_u, \bar{y}_u,t_a,t_b))|_{\bar{x}_u=\bar{x}_{0}(t_a)}  du \right)ds \nonumber
 \end{align}
@@
 \section{Auxiliary lemmas}
-\subsection{Estimation of $\mathbb{E}_s^{\mathbb{Q}}\left((x_t - \bar{x}_{t})^{2}\right)$}\label{estimation_error_l2}
-In order to get the order of the aproximation, we will use the ideas of the paper \cite{B-G-M-2008}.
-Basically, we will define a parametrization of the process $x_{t,\epsilon}$ e $y_{t,\epsilon}$ with $\epsilon \in [0,1]$.
-The role of $\epsilon$ is only as interpolator parameter between process.
+\subsection{Estimation of $\mathbb{E}_s^{\mathbb{Q}}\left[(x_t - \bar{x}_{t})^{2}\right]$}\label{estimation_error_l2}
+In order to get the order of the approximation, we will use the ideas of the paper \cite{B-G-M-2008}.
+Basically, we will define a parametrization of the process $x_{t,\epsilon}$ and $y_{t,\epsilon}$ with $\epsilon \in [0,1]$.
+The role of $\epsilon$ is only as interpolation parameter between process.
 We will suppose the next parametrization of the Cheyette model
@@
 \end{align}
-The reason of $\epsilon^{2}$ in $y_{\epsilon,t}$ is because $\mathbb{E}^{\mathbb{Q}}\left(y_t\right)= \mathbb{V}ar(x_t)$.
+The reason of $\epsilon^{2}$ in $y_{\epsilon,t}$ is because $\mathbb{E}^{\mathbb{Q}}\left[y_t\right]= \mathbb{V}ar(x_t)$.
 Then, if the scale of $x_{\epsilon,t}$ is $\epsilon$ then the scale of $y_{\epsilon,t}$ must be $\epsilon^{2}$.
-We will start with the estimation of $\mathbb{E}^{\mathbb{Q}}((y_t - \bar{y}_t)^{2})$.
+We will start with the estimation of $\mathbb{E}^{\mathbb{Q}}\left[(y_t - \bar{y}_t)^{2}\right]$.
 We will define the next parametrization for $\nu \in [0,1]$
@@
 \end{equation*}
-Then we have that $z^{1}_{u} = \eta(u,x_u,y_u$ y $z^{0}_{u} = \eta(u,0,0)$. Therefore
+Then we have that $z^{1}_{u} = \eta(u,x_u,y_u)$ y $z^{0}_{u} = \eta(u,0,0)$. Therefore
 \begin{align*}
@@
 \begin{equation*}
-y_t = \bar{y}_t + E_{y}(t)
+y_t = \bar{y}_t + E_{y}\left[t\right]
 \end{equation*}
@@
 \begin{align} \label{upper_bound_E_y}
-\mathbb{E}^{\mathbb{Q}}((E_{y}(t))^{2}) &\leq 4 \mathbb{E}^{\mathbb{Q}}\left(\int_{0}^{t} \exp\left(-4 \int_{u}^{t} k(u^{\prime}) du^{\prime}\right)  \left(\int_{0}^{1} \eta(u, \nu x_u, \nu y_u)   \|\nabla_{x,y}\eta(u, \nu x_u, \nu y_u)\|^{2} \|(x_u, y_u)\| d\nu \right)^2 du \right) ^{2}\nonumber \\
-&\leq 4 \|\eta\|^{2}_{\infty} \max(\|\partial_x\eta\|^{2}_{\infty},\|\partial_y \eta\|^{2}_{\infty} ) \int_{0}^{t} \mathbb{E}^{\mathbb{Q}}\left( \|(x_u, y_u)\|^{2}\right) du = M^{y}_k \int_{0}^{t} \mathbb{E}^{\mathbb{Q}}\left( \|(x_u, y_u)\|^{2}\right) du
-\end{align}
-The next step is to estimate $\mathbb{E}^{\mathbb{Q}}((x_t - \bar{x}_t)^{2})$. From the definition of $x_t$, we have that
-\begin{equation*}
-x_t = \int_{0}^{t} \exp\left(- \int_{u}^{t} k(u^{\prime}) du^{\prime}\right) \bar{y}_u du + \int_{0}^{t} \exp\left(- \int_{u}^{t} k(u^{\prime}) du^{\prime}\right) E_{y}(u) du + \int_{0}^{t} \eta(t,x_u,y_u) dW_u.
-\end{equation*}
-In order, to find a expansion of $\eta(t,x_u,y_u)$ centrered in $\bar{y}_u$, we will define $z^{\nu}_{u} = (1-\nu)\bar{y}_{u} + \nu y_u$. Then
-\begin{equation*}
-\eta(t,x_u,y_u) = \eta(t,x_u,\bar{y}_u) + \int_{0}^{1}\partial_y\eta(t,x_u,z^{\nu}_{u}) E_{y}(u) d\nu
-\end{equation*}
-We will define $E_{x}(u) = \int_{0}^{1}\partial_y\eta(t,x_u,z^{\nu}_{u}) E_{y}(u) d\nu$. Then we have the next representation of $x_t$
-\begin{equation*}
-x_t = \bar{x}_t + \int_{0}^{t} \exp\left(- \int_{u}^{t} k(u^{\prime}) du^{\prime}\right) E_{y}(u) du + \int_{0}^{t} \exp\left(- \int_{u}^{t} k(u^{\prime}) du^{\prime}\right) E_{x}(u) dW_u.
+\mathbb{E}^{\mathbb{Q}}\left[(E_{y}\left[t\right])^{2}\right] &\leq 4 \mathbb{E}^{\mathbb{Q}}\left[\int_{0}^{t} \exp\left(-4 \int_{u}^{t} k(u^{\prime}) du^{\prime}\right)  \left(\int_{0}^{1} \eta(u, \nu x_u, \nu y_u)   \|\nabla_{x,y}\eta(u, \nu x_u, \nu y_u)\|^{2} \|(x_u, y_u)\| d\nu \right)^2 du \right] ^{2}\nonumber \\
+&\leq 4 \|\eta\|^{2}_{\infty} \max(\|\partial_x\eta\|^{2}_{\infty},\|\partial_y \eta\|^{2}_{\infty} ) \int_{0}^{t} \mathbb{E}^{\mathbb{Q}}\left[ \|(x_u, y_u)\|^{2}\right] du  \nonumber \\
+&= M^{y}_k \int_{0}^{t} \mathbb{E}^{\mathbb{Q}}\left[\|(x_u, y_u)\|^{2}\right] du
+\end{align}
+The next step is to estimate $\mathbb{E}^{\mathbb{Q}}\left[(x_t - \bar{x}_t)^{2}\right]$. From the definition of $x_t$, we have that
+\begin{equation*}
+x_t = \int_{0}^{t} \exp\left(- \int_{u}^{t} k(u^{\prime}) du^{\prime}\right) \bar{y}_u du + \int_{0}^{t} \exp\left(- \int_{u}^{t} k(u^{\prime}) du^{\prime}\right) E_{y}[u] du + \int_{0}^{t} \eta(t,x_u,y_u) dW_u.
+\end{equation*}
+In order, to find a expansion of $\eta(t,x_u,y_u)$ centered in $\bar{y}_u$, we will define $z^{\nu}_{u} = (1-\nu)\bar{y}_{u} + \nu y_u$. Then
+\begin{equation*}
+\eta(t,x_u,y_u) = \eta(t,x_u,\bar{y}_u) + \int_{0}^{1}\partial_y\eta(t,x_u,z^{\nu}_{u}) E_{y}[u] d\nu
+\end{equation*}
+We will define $E_{x}(u) = \int_{0}^{1}\partial_y\eta(t,x_u,z^{\nu}_{u}) E_{y}[u] d\nu$. Then we have the next representation of $x_t$
+\begin{equation*}
+x_t = \bar{x}_t + \int_{0}^{t} \exp\left(- \int_{u}^{t} k(u^{\prime}) du^{\prime}\right) E_{y}[u] du + \int_{0}^{t} \exp\left(- \int_{u}^{t} k(u^{\prime}) du^{\prime}\right) E_{x}[u] dW_u.
 \end{equation*}
@@
 \begin{equation*}
- \mathbb{E}^{\mathbb{Q}}((E_x(u))^{2}) \leq \|\partial_y \eta \|^{2}_{\infty} \mathbb{E}^{\mathbb{Q}}((E_{y}(u))^{2})   
+ \mathbb{E}^{\mathbb{Q}}[(E_x[u])^{2}] \leq \|\partial_y \eta \|^{2}_{\infty} \mathbb{E}^{\mathbb{Q}}[(E_{y}[u])^{2}]  
 \end{equation*}
@@
 \begin{equation}\label{upper_bound_E_x}
- \mathbb{E}^{\mathbb{Q}}((E_x(u))^{2}) \leq 4 \|\eta\|^{2}_{\infty} \|\partial_y \eta\|^{2}_{\infty} \max(\|\partial_x\eta\|^{2}_{\infty},\|\partial_y \eta\|^{2}_{\infty} ) \int_{0}^{u} \mathbb{E}^{\mathbb{Q}}\left( \|(x_s, y_s)\|^{2}\right) ds
+ \mathbb{E}^{\mathbb{Q}}[(E_x[u])^{2}] \leq 4 \|\eta\|^{2}_{\infty} \|\partial_y \eta\|^{2}_{\infty} \max(\|\partial_x\eta\|^{2}_{\infty},\|\partial_y \eta\|^{2}_{\infty} ) \int_{0}^{u} \mathbb{E}^{\mathbb{Q}}\left[ \|(x_s, y_s)\|^{2}\right] ds
 \end{equation}
@@
 \begin{align*}
-\mathbb{E}^{\mathbb{Q}}((x_t - \bar{x}_t)^{2}) & \leq 2 \mathbb{E}^{\mathbb{Q}}\left( \int_{0}^{t} \exp\left(- \int_{u}^{t} k(u^{\prime}) du^{\prime}\right) E_{y}(u) du    \right)^2 + \mathbb{E}^{\mathbb{Q}}\left( \int_{0}^{t} \exp\left(- \int_{u}^{t} k(u^{\prime}) du^{\prime}\right) E_{x}(u) dW_u\right)^{2} \\
-&\leq 2 \mathbb{E}^{\mathbb{Q}}\int_{0}^{t} \exp\left(- 2\int_{u}^{t} k(u^{\prime}) du^{\prime}\right) \mathbb{E}^{\mathbb{Q}}(E^{2}_{y}(u)) du + \int_{0}^{t} \exp\left(- 2\int_{u}^{t} k(u^{\prime}) du^{\prime}\right) \mathbb{E}^{\mathbb{Q}}(E^{2}_{x}(u)) du
+\mathbb{E}^{\mathbb{Q}}[(x_t - \bar{x}_t)^{2}] & \leq 2 \mathbb{E}^{\mathbb{Q}}\left[ \int_{0}^{t} \exp\left(- \int_{u}^{t} k(u^{\prime}) du^{\prime}\right) E_{y}(u) du    \right]^2\\
+&+ \mathbb{E}^{\mathbb{Q}}\left[ \int_{0}^{t} \exp\left(- \int_{u}^{t} k(u^{\prime}) du^{\prime}\right) E_{x}(u) dW_u\right]^{2} \\
+&\leq 2 \mathbb{E}^{\mathbb{Q}}\left[\int_{0}^{t} \exp\left(- 2\int_{u}^{t} k(u^{\prime}) du^{\prime}\right) \mathbb{E}^{\mathbb{Q}}(E^{2}_{y}(u)) du\right]\\
+&+ \int_{0}^{t} \exp\left(- 2\int_{u}^{t} k(u^{\prime}) du^{\prime}\right) \mathbb{E}^{\mathbb{Q}}[E^{2}_{x}[u]] du   
 \end{align*}
@@
 \begin{equation*}
-\mathbb{E}^{\mathbb{Q}}((x_t - \bar{x}_t)^{2}) \leq M^{x}_k \int_{0}^{t} \exp\left(- 2\int_{u}^{t} k(u^{\prime}) du^{\prime}\right) \mathbb{E}^{\mathbb{Q}}\left( \|(x_u, y_u)\|^{2}\right) du 
-\end{equation*}
-To end, only we have to estimate $\mathbb{E}^{\mathbb{Q}}\left( \|(x_s, y_s)\|^{2}\right)$. From the definition of $y_t$ and since $\|\eta\|_{\infty} < \infty$, we have that
-\begin{equation*}
-\mathbb{E}^{\mathbb{Q}}(y^{2}_u) \leq \|\eta\|^{2}_{\infty} \int_{0}^{u} \exp\left(- 2\int_{s}^{u} k(u^{\prime}) du^{\prime}\right) ds.
-\end{equation*}
-We must note that at the short term and under asummptions (\ref{boundedness_reversion}) we have that
-\begin{equation*}
-\lim_{t \to 0} \mathbb{E}^{\mathbb{Q}}(y^{2}_u) = \|\eta\|^{2}_{\infty} t
+\mathbb{E}^{\mathbb{Q}}[(x_t - \bar{x}_t)^{2}]\leq M^{x}_k \int_{0}^{t} \exp\left(- 2\int_{u}^{t} k(u^{\prime}) du^{\prime}\right) \mathbb{E}^{\mathbb{Q}}\left[ \|(x_u, y_u)\|^{2}\right] du 
+\end{equation*}
+To end, only we have to estimate $\mathbb{E}^{\mathbb{Q}}\left[ \|(x_s, y_s)\|^{2}\right]$. From the definition of $y_t$ and since $\|\eta\|_{\infty} < \infty$, we have that
+\begin{equation*}
+\mathbb{E}^{\mathbb{Q}}[y^{2}_u] \leq \|\eta\|^{2}_{\infty} \int_{0}^{u} \exp\left(- 2\int_{s}^{u} k(u^{\prime}) du^{\prime}\right) ds.
+\end{equation*}
+We must note that at the short term and under assumptions (\ref{boundedness_reversion}) we have that
+\begin{equation*}
+\lim_{t \to 0} \mathbb{E}^{\mathbb{Q}}[y^{2}_u] = \|\eta\|^{2}_{\infty} t
 \end{equation*}
@@
 \begin{equation*}
-\lim_{t \to \infty} \mathbb{E}^{\mathbb{Q}}(y^{2}_u) < \infty.
-\end{equation*}
-Now $\mathbb{E}^{\mathbb{Q}}(x^{2}_u)$. From the definition of $x_t$ and using $(a+b)^2 \leq 2(a^{2}+ b^{2})$ we have that
-\begin{align*}
-\mathbb{E}^{\mathbb{Q}}(x^{2}_u) &\leq 2 \mathbb{E}^{\mathbb{Q}}\left(\int_{0}^{u} \exp\left(- \int_{s}^{u} k(u^{\prime}) du^{\prime}\right) y_s  ds \right)^{2} +  2 \mathbb{E}^{\mathbb{Q}}\left(\int_{0}^{u} \exp\left(- \int_{s}^{u} k(u^{\prime}) du^{\prime}\right) \eta(s,x_s,y_s)  dW_s \right)^{2} \nonumber \\
-&\leq 2 \int_{0}^{u} \exp\left(- 2\int_{s}^{u} k(u^{\prime}) du^{\prime}\right) \mathbb{E}^{\mathbb{Q}}\left(y_s\right)^{2} ds + 2 \int_{0}^{u} \exp\left(- 2 \int_{s}^{u} k(u^{\prime}) du^{\prime}\right) \mathbb{E}^{\mathbb{Q}}\left(\eta^{2}(s,x_s,y_s)\right) ds \\
-&\leq 2 \|\eta\|_{\infty} \int_{0}^{u} \exp\left(- 2\int_{s}^{u} k(u^{\prime}) du^{\prime}\right) \int_{0}^{s}  \exp\left(- 2\int_{s_1}^{s} k(u^{\prime}) du^{\prime}\right) ds_1 ds +  2 \|\eta\|_{\infty} \int_{0}^{u} \exp\left(- 2\int_{s}^{u} k(u^{\prime}) du^{\prime}\right) ds
+\lim_{t \to \infty} \mathbb{E}^{\mathbb{Q}}[y^{2}_u] < \infty.
+\end{equation*}
+Now $\mathbb{E}^{\mathbb{Q}}[x^{2}_u]$. From the definition of $x_t$ and using $(a+b)^2 \leq 2(a^{2}+ b^{2})$ we have that
+\begin{align*}
+\mathbb{E}^{\mathbb{Q}}[x^{2}_u] &\leq 2 \mathbb{E}^{\mathbb{Q}}\left[\int_{0}^{u} \exp\left(- \int_{s}^{u} k(u^{\prime}) du^{\prime}\right) y_s  ds \right]^{2} +  2 \mathbb{E}^{\mathbb{Q}}\left[\int_{0}^{u} \exp\left(- \int_{s}^{u} k(u^{\prime}) du^{\prime}\right) \eta(s,x_s,y_s)  dW_s \right]^{2} \nonumber \\
+&\leq 2 \int_{0}^{u} \exp\left(- 2\int_{s}^{u} k(u^{\prime}) du^{\prime}\right) \mathbb{E}^{\mathbb{Q}}\left[y_s\right]^{2} ds + 2 \int_{0}^{u} \exp\left(- 2 \int_{s}^{u} k(u^{\prime}) du^{\prime}\right) \mathbb{E}^{\mathbb{Q}}\left[\eta^{2}(s,x_s,y_s)\right] ds \\
+&\leq 2 \|\eta\|_{\infty} \int_{0}^{u} \exp\left(- 2\int_{s}^{u} k(u^{\prime}) du^{\prime}\right) \int_{0}^{s}  \exp\left(- 2\int_{s_1}^{s} k(u^{\prime}) du^{\prime}\right) ds_1 ds\\
+&+  2 \|\eta\|_{\infty} \int_{0}^{u} \exp\left(- 2\int_{s}^{u} k(u^{\prime}) du^{\prime}\right) ds
 \end{align*}
@@
 $$
-\lim_{t \to 0} \mathbb{E}^{\mathbb{Q}}(x^{2}_u) = 2\|\eta\|^{2}_{\infty} t
+\lim_{t \to 0} \mathbb{E}^{\mathbb{Q}}[x^{2}_u] = 2\|\eta\|^{2}_{\infty} t
 $$
@@
 \begin{align*}
-\mathbb{E}^{\mathbb{Q}}((y_t - \bar{y}_t)^{2}) &\leq M^{y}_k \int_{0}^{t}  \exp\left(- 2\int_{u}^{t} k(u^{\prime}) du^{\prime}\right)  \int_{0}^{u} \exp\left(- 2\int_{s}^{u} k(u^{\prime}) du^{\prime}\right) ds du
+\mathbb{E}^{\mathbb{Q}}[(y_t - \bar{y}_t)^{2}] &\leq M^{y}_k \int_{0}^{t}  \exp\left(- 2\int_{u}^{t} k(u^{\prime}) du^{\prime}\right)  \int_{0}^{u} \exp\left(- 2\int_{s}^{u} k(u^{\prime}) du^{\prime}\right) ds du
 \end{align*}
@@
 \begin{align*}
-\mathbb{E}^{\mathbb{Q}}((x_t - \bar{x}_t)^{2}) &\leq 2 M^{x}_k \|\eta\|_{\infty} \int_{0}^{t} \exp\left(- 2\int_{u}^{t} k(u^{\prime}) du^{\prime}\right)   \int_{0}^{u} \exp\left(- 2\int_{s}^{u} k(u^{\prime}) du^{\prime}\right) \int_{0}^{s}  \exp\left(- 2\int_{s_1}^{s} k(u^{\prime}) du^{\prime}\right) ds_1 ds du \\
+\mathbb{E}^{\mathbb{Q}}[(x_t - \bar{x}_t)^{2}] &\leq 2 M^{x}_k \|\eta\|_{\infty} \int_{0}^{t} \exp\left(- 2\int_{u}^{t} k(u^{\prime}) du^{\prime}\right)\int_{0}^{u} \exp\left(- 2\int_{s}^{u} k(u^{\prime}) du^{\prime}\right) \cdot \\
+& \qquad \hspace{1.5cm} \cdot \int_{0}^{s}  \exp\left(- 2\int_{s_1}^{s} k(u^{\prime}) du^{\prime}\right) ds_1 ds du \\
 &+ (2 M^{x}_K \|\eta\|_{\infty} + 1) \int_{0}^{t}  \exp\left(- 2\int_{u}^{t} k(u^{\prime}) du^{\prime}\right)  \int_{0}^{u} \exp\left(- 2\int_{s}^{u} k(u^{\prime}) du^{\prime}\right) ds du.
@@
 \begin{align*}
-\mathbb{E}^{\mathbb{Q}}((x_t - \bar{x}_t)^{2}) &\leq \frac{2}{3} M^{x}_k \|\eta\|_{\infty} \left( \int_{0}^{t} \exp\left(- 2\int_{u}^{t} k(u^{\prime}) \right) du  \right)^{3}  \\
+\mathbb{E}^{\mathbb{Q}}[(x_t - \bar{x}_t)^{2}] &\leq \frac{2}{3} M^{x}_k \|\eta\|_{\infty} \left( \int_{0}^{t} \exp\left(- 2\int_{u}^{t} k(u^{\prime}) \right) du  \right)^{3}  \\
 &+ \frac{(2 M^{x}_K \|\eta\|_{\infty} + 1)}{2} \left( \int_{0}^{t}  \exp\left(- 2\int_{u}^{t} k(u^{\prime}) \right) du  \right)^{2}.
@@
 \begin{align*}
-\bar{DM}(s,t_a) &= \mathbb{E}^{t_p}_s\left(\exp\left(-\int_{s}^{t_a} \exp\left(-\int_{u}^{t_a}k_u du\right)\left(\partial_x \eta(u, \bar{x}_0(t_a), \bar{y}_{u}) \bar{\nu}(u,t_p, \bar{x}_0(t_a)) \right.
+\overline{DM}(s,t_a) &= \mathbb{E}^{t_p}_s\left(\exp\left(-\int_{s}^{t_a} \exp\left(-\int_{u}^{t_a}k_u du\right)\left(\partial_x \eta(u, \bar{x}_0(t_a), \bar{y}_{u}) \bar{\nu}(u,t_p, \bar{x}_0(t_a)) \right.
 \right.
@@
 
-\subsection{Approximation of $\mathbb{E}_s^{\mathbb{Q}}\left(D_s \bar{x}_{t_a}\right)$}
+\subsection{Approximation of $\mathbb{E}_s^{\mathbb{Q}}\left[D_s \bar{x}_{t_a}\right]$}
 As above appendix we have that
 \begin{align*}
-\bar{x}_{t_a} &= \bar{x}_0(t_a) + \int_{0}^{t_a} \exp\left(-\int_{s}^{t_a}k_u du\right) \bar{y}_u du + \int_{0}^{t_a} \exp\left(-\int_{s}^{t_a}k_u du \right) \eta(u,\bar{x}_u,\bar{y}_u) dW_u^{\mathbb{Q}}\\
+\bar{x}_{t_a} &= \bar{x}_0(t_a) + \int_{0}^{t_a} \exp\left(-\int_{s}^{t_a}k_u du\right) \bar{y}_u du + \int_{0}^{t_a} \exp\left(-\int_{s}^{t_a}k_u du \right) \eta(u,\bar{x}_u,\bar{y}_u) dW_u^{\mathbb{Q}}
 \end{align*}
@@
 \end{equation}
-Now, if we take $\mathbb{E}_s^{\mathbb{Q}}\left(\cdot\right)$ we get
+Now, if we take $\mathbb{E}_s^{\mathbb{Q}}\left[\cdot\right]$ we get
 \begin{equation}\label{approximation_spot_E_s_x_t}
@@
 
-\subsection{Approximation of $\mathbb{E}^{01}\left(\bar{x}_{t_a}\right)$}
+\subsection{Approximation of $\mathbb{E}^{01}\left[\bar{x}_{t_a}\right]$}
 It is easy to show that the dynamic of the bond under HJM assumption is
@@
 \end{equation}
-where we must rememebr that  $\nu(t,T)=\int_{t}^{T}\sigma(t,s) ds$. Therefore, if we apply Itô formula we have that 
+where we must remember that  $\nu(t,T)=\int_{t}^{T}\sigma(t,s) ds$. Therefore, if we apply Itô formula we have that 
 \begin{equation}\label{annuity_spot_dynamic}
@@
 \bar{x}_{t_a} &\approx \bar{x}_0(t_a)  + \int_{0}^{t_a} \exp\left(-\int_{s}^{t}k_u du\right) \bar{y}_u du + \int_{0}^{t_a}  \exp\left(-\int_{s}^{t_a}k_u du \right) \eta(u,\bar{x}(u),\bar{y}_u) dW_u^{\mathbb{Q}} \nonumber \\
-&=  \bar{x}_0(t)  + \int_{0}^{t_a} \exp\left(-\int_{s}^{t_a}k_u du\right) \bar{y}_u du + \int_{0}^{t_a} \exp\left(-\int_{s}^{t_a}k_u du \right) \eta(u,\bar{x}_u,\bar{y}_u) \bar{\sigma}_{01}(u, t_a, t_b) du  + \nonumber \\
-& \int_{0}^{t_a} \exp\left(-\int_{s}^{t_a}k_u du \right) \eta(u,\bar{x}_u,\bar{y}_u) dW_u^{01} 
+&=  \bar{x}_0(t)  + \int_{0}^{t_a} \exp\left(-\int_{s}^{t_a}k_u du\right) \bar{y}_u du + \int_{0}^{t_a} \exp\left(-\int_{s}^{t_a}k_u du \right) \eta(u,\bar{x}_u,\bar{y}_u) \bar{\sigma}_{01}(u, t_a, t_b) du  \nonumber \\
+&\hspace{1.2cm} + \int_{0}^{t_a} \exp\left(-\int_{s}^{t_a}k_u du \right) \eta(u,\bar{x}_u,\bar{y}_u) dW_u^{01} 
 \end{align}
@@
 \begin{align}
-\mathbb{E}^{01}\left(\bar{x}_t\right) &\approx \bar{x}_0(t_a)  + \int_{0}^{t_a} \exp\left(-\int_{s}^{t_a}k_u du\right) \bar{y}_u du \nonumber \\ 
-+ &\int_{0}^{t_a} \exp\left(-\int_{s}^{t_a}k_u du \right) \eta(u,\bar{x}_u,\bar{y}_u) \bar{\sigma}_{01}(u, t_a, t_b,\bar{x}_0(t_a)) du
+\mathbb{E}^{01}\left[\bar{x}_t\right] &\approx \bar{x}_0(t_a)  + \int_{0}^{t_a} \exp\left(-\int_{s}^{t_a}k_u du\right) \bar{y}_u du \nonumber \\ 
+&\hspace{1.3cm} + \int_{0}^{t_a} \exp\left(-\int_{s}^{t_a}k_u du \right) \eta(u,\bar{x}_u,\bar{y}_u) \bar{\sigma}_{01}(u, t_a, t_b,\bar{x}_0(t_a)) du
 \end{align}

### 2023-04-14 Latex/paper-resum.tex
Stylish III

@@
 In this section, we derive the convexity adjustment for different products.
-The advantage of using the Malliavin calculus, is that it allows us to derive a general representation formula for the convexity adjustmet Even, how we will see later, it is possible to get closed formulas for the convexity adjusment when the volatility of the Cheyette model is time dependent.
-
-To introduce a general idea of the method, let us define the process $Z_t = f(x_t)$.
-Now, we suppose that $Z_t$ is martingale under the measure $\mathbb{Q}_1$, but we want to compute $\mathbb{E}^{\mathbb{Q}_2}\left[Z_T \right]$, where $\mathbb{Q}_2$ is a measure under which $Z_t$ is not martingale and such that $dW^{\mathbb{Q}_1}_t = dW^{\mathbb{Q}_2}_t +\lambda_t dt$.
+The advantage of using the Malliavin calculus is that it allows us to derive a general representation formula for the convexity adjustment.
+Furthermore, as we will see later, it is possible to obtain closed formulas for the convexity adjustment when the volatility of the Cheyette model is time dependent.
+
+We are going to introduce a general idea of the method.
+Let us define the process $Z_t = f(x_t)$.
+Suppose that $Z_t$ is a martingale under the measure $\mathbb{Q}_1$.
+However, we are interested in calculate $\mathbb{E}^{\mathbb{Q}_2}\left[Z_T \right]$ where $\mathbb{Q}_2$ is a measure under which $Z_t$ is not martingale and such that $dW^{\mathbb{Q}_1}_t = dW^{\mathbb{Q}_2}_t +\lambda_t dt$.
 Then, if we use the Clark-Ocone representation, we have that
@@
 \end{equation*}
-Now, if we take $\mathbb{E}^{\mathbb{Q}_2}\left( \cdot \right)$ in the previous expression and we use the Girsanov's theorem, we get that
+Now, taking $\mathbb{E}^{\mathbb{Q}_2}\left( \cdot \right)$ in the previous expression and using Girsanov's theorem, we get that
 \begin{equation}\label{general_convexity}
@@
 \end{equation}
-The second term, is the convexity adjustment to due to change of measure from $\mathbb{Q}_1$ to $\mathbb{Q}_2$.
-The differents choice of $f$, $\mathbb{Q}_1$ and $\mathbb{Q}_2$ will allow us to get an approximation of the convexity adjustment for the different case of interest.
+The second term is the convexity adjustment due to the change of measure from $\mathbb{Q}_1$ to $\mathbb{Q}_2$.
+The different choices of $f$, $\mathbb{Q}_1$, and $\mathbb{Q}_2$ will allow us to obtain a convexity adjustment approximation for the different cases of interest.
 \subsection{FRAs Vs futures}
@@
 
-\subsection{Approximation of $\mathbb{E}^{01}\left(D_s \bar{x}_{t_a} \right)$}\label{approximation_under_annuity_measeure_d_s}
+\subsection{Approximation of $\mathbb{E}^{01}\left[D_s \bar{x}_{t_a} \right]$}\label{approximation_under_annuity_measeure_d_s}
 Let us to remember that $\nu(t,t_i)=h(t,\bar{x}_t,\bar{y}_t) \frac{G(t,t_i)}{\beta_{t,k}(t)}$ with  $\beta_{t,k}(t) = \exp\left(\int_{0}^{t}k(u)\right)$.
@@
 \begin{align*}
-\bar{x}_{T_a} &=  \bar{x}_0(t_a)  + \int_{0}^{t_a} \exp\left(-\int_{s}^{t_a}k_u du\right) \bar{y}_u du + \int_{0}^{t_a} \exp\left(-\int_{s}^{t_a}k_u du\right) \sigma_{01}(u,t_a,t_b) \mu(u,\bar{x}_u, \bar{y}_u, t_a,t_b) du \nonumber \\\
+\bar{x}_{T_a} =  \bar{x}_0(t_a)  &+ \int_{0}^{t_a} \exp\left(-\int_{s}^{t_a}k_u du\right) \bar{y}_u du \nonumber \\\ 
+&+ \int_{0}^{t_a} \exp\left(-\int_{s}^{t_a}k_u du\right) \sigma_{01}(u,t_a,t_b) \mu(u,\bar{x}_u, \bar{y}_u, t_a,t_b) du \nonumber \\\
 &+  \int_{0}^{t_a}  \exp\left(-\int_{s}^{t_a}k_u du \right) \eta(u,\bar{x}_u,\bar{y}_u) dW_u^{\mathbb{Q}^{01}}.
@@
 \begin{align*}
-\bar{M}^{01}(s,t_a) &= \exp\left(-\int_{s}^{t_a} \left(\frac{\left(\partial_x \beta(u,t_a,\bar{x}_u,\bar{y}_{u})\right)^{2}}{2} + \partial_x (\beta(u,t_a,\bar{x}_u,\bar{y}_{u}) \mu(u,\bar{x}_u,\bar{y}_u,t_a,t_b)) du \right)\right) \\
+\bar{M}^{01}(s,t_a) = &\exp\left(-\int_{s}^{t_a} \left(\frac{\left(\partial_x \beta(u,t_a,\bar{x}_u,\bar{y}_{u})\right)^{2}}{2} + \partial_x (\beta(u,t_a,\bar{x}_u,\bar{y}_{u}) \mu(u,\bar{x}_u,\bar{y}_u,t_a,t_b)) du \right)\right) \\
 &\exp\left(\int_{s}^{t_a} \partial_x \beta(u,t_a,\bar{x}_0,\bar{y}_{t_a}) dW^{\mathbb{Q}^{01}}_u \right)
@@
 \begin{align}\label{approximation_E_01_Ds_x_t}
-\mathbb{E}^{01}_s\left(D_s \bar{x}_{t_a}\right) &= \beta(s,t_a,\bar{x}_s,\bar{y}_s)  \mathbb{E}_s^{01}\left(\exp\left(-\int_{s}^{t_a}\partial_x (\beta(u,t_a,\bar{x}_u,\bar{y}_u) \mu(u,\bar{x}_u, \bar{y}_u,t_a,t_b)) du \right)\right) \nonumber \\
+\mathbb{E}^{01}_s\left[D_s \bar{x}_{t_a}\right] &= \beta(s,t_a,\bar{x}_s,\bar{y}_s)  \mathbb{E}_s^{01}\left(\exp\left(-\int_{s}^{t_a}\partial_x (\beta(u,t_a,\bar{x}_u,\bar{y}_u) \mu(u,\bar{x}_u, \bar{y}_u,t_a,t_b)) du \right)\right) \nonumber \\
 &\approx \beta(s,t_a,\bar{x}_s,\bar{y}_s) \exp\left(-\int_{s}^{t_a}\partial_x (\beta(u,t_a,\bar{x}_u,\bar{y}_u) \mu(u,\bar{x}_u, \bar{y}_u,t_a,t_b))|_{\bar{x}_u=\bar{x}_{0}(t_a)}  du \right)
@@
 \begin{equation}\label{future}
-\hat{L}_{E}(t,t_0, t_1, t_2) = \mathbb{E}_t^{\mathbb{Q}}\left(L_{E}(t_0, t_1, t_2) \right), 
+\hat{L}_{E}(t,t_0, t_1, t_2) = \mathbb{E}_t^{\mathbb{Q}}\left[L_{E}(t_0, t_1, t_2) \right], 
 \end{equation}
@@
 \begin{equation*}
-CA(t, t_0, t_1, t_2) = \hat{L}_{E}(t,t_0, t_1, t_2) - \mathbb{E}_t^{\mathbb{Q}^{t_2}}\left(L_{E}(t_0, t_1, t_2) \right).
+CA(t, t_0, t_1, t_2) = \hat{L}_{E}(t,t_0, t_1, t_2) - \mathbb{E}_t^{\mathbb{Q}^{t_2}}\left[L_{E}(t_0, t_1, t_2) \right].
 \end{equation*}
@@
 \begin{equation}\label{ca_general_future}
-CA(t, t_0, t_1, t_2) = \mathbb{E}^{\mathbb{Q}^{t2}}\left(\int_{0}^{t_0} \mathbb{E}^{\mathbb{Q}}_{s}\left(D_s L_{E}(t_0,t_1,t_2) \right) \nu(s,t_2) ds \right)
+CA(t, t_0, t_1, t_2) = \mathbb{E}^{\mathbb{Q}^{t2}}\left[\int_{0}^{t_0} \mathbb{E}^{\mathbb{Q}}_{s}\Bigl[D_s L_{E}(t_0,t_1,t_2) \Bigr] \nu(s,t_2) ds \right]
 \end{equation}
@@
 \begin{equation*}
-D_s \left(\frac{P_{ois}(t_0,t_1)}{P_{ois}(t_0,t_2)}\right) = \frac{\left(\partial_{x}P_{ois}(t_0,t_1)P_{ois}(t_0,t_2) - \partial_{x}P_{ois}(t_0,t_2) P_{ois}(t_0,t_1) \right)}{P^{2}_{ois}(t_0,t_2)} D_s x_{t_0}.
+D_s \left(\frac{P_{ois}(t_0,t_1)}{P_{ois}(t_0,t_2)}\right) = \frac{\partial_{x}P_{ois}(t_0,t_1)P_{ois}(t_0,t_2) - \partial_{x}P_{ois}(t_0,t_2) P_{ois}(t_0,t_1)}{P^{2}_{ois}(t_0,t_2)} D_s x_{t_0}.
 \end{equation*}
@@
 \begin{equation}\label{malliavin_derive_L}
-D_s L_{E}(t_0,t_1,t_2) = \frac{H(t_0,t_1)}{\delta_{t_1,t_2}H(t_0,t_2)}\frac{\left(\partial_{x}P_{ois}(t_0,t_1)P_{ois}(t_0,t_2) - \partial_{x}P_{ois}(t_0,t_2) P_{ois}(t_0,t_1) \right)}{P^{2}_{ois}(t_0,t_2)} D_s x_{t_0}.
+D_s L_{E}(t_0,t_1,t_2) = \frac{H(t_0,t_1)}{\delta_{t_1,t_2}H(t_0,t_2)}\frac{\partial_{x}P_{ois}(t_0,t_1)P_{ois}(t_0,t_2) - \partial_{x}P_{ois}(t_0,t_2) P_{ois}(t_0,t_1) }{P^{2}_{ois}(t_0,t_2)} D_s x_{t_0}.
 \end{equation}
@@
 \begin{align*}
-D_s L_{E}(t_0,t_1,t_2) &\approx \frac{H(t_0,t_1)}{\delta_{t_1,t_2}H(t_0,t_2)}\frac{\left(\partial_{x}P_{ois}(t_0,t_1)P_{ois}(t_0,t_2) - \partial_{x}P_{ois}(t_0,t_2) P_{ois}(t_0,t_1) \right)}{P^{2}_{ois}(t_0,t_2)} \beta(t,t_0,\bar{x}_s,\bar{y}_s)\bar{M}(s,t_0) \nonumber \\
+D_s L_{E}(t_0,t_1,t_2) &\approx \frac{H(t_0,t_1)}{\delta_{t_1,t_2}H(t_0,t_2)}\frac{\partial_{x}P_{ois}(t_0,t_1)P_{ois}(t_0,t_2) - \partial_{x}P_{ois}(t_0,t_2) P_{ois}(t_0,t_1)}{P^{2}_{ois}(t_0,t_2)} \beta(t,t_0,\bar{x}_s,\bar{y}_s)\bar{M}(s,t_0) \nonumber \\
 \approx& \frac{P_{E}(0,t_1)}{\delta_{t_1,t_2} P_{E}(0,t_2)} \left(G(t_0,t_2) \frac{P_{ois}(0,t_2)}{P_{ois}(0,t_0)} - G(t_0,t_1) \frac{P_{ois}(0,t_1)}{P_{ois}(0,t_0)} \right)\beta(t,t_0,\bar{x}_s,\bar{y}_s)\bar{M}(s,t_0).
@@
 \begin{equation}\label{approximation_clarkocone}
-\mathbb{E}_s\left( D_s L_{E}(t_0,t_1,t_2) \right) = \frac{P_{E}(0,t_1)}{\delta_{t_1,t_2} P_{E}(0,t_2)} \left(G(t_0,t_2)  - G(t_0,t_1)\right)\beta(t,t_0,x_0,\bar{y}_s).
+\mathbb{E}_s\left[ D_s L_{E}(t_0,t_1,t_2) \right] = \frac{P_{E}(0,t_1)}{\delta_{t_1,t_2} P_{E}(0,t_2)} \left(G(t_0,t_2)  - G(t_0,t_1)\right)\beta(t,t_0,x_0,\bar{y}_s).
 \end{equation}
@@
 \subsection{Proof Theorem \ref{Th_CA_OIS}}\label{Proof_CA_OIS_futures}
-To compute $\mathbb{E}^{\mathbb{Q}}\left(R(t_0,t_1)\right)$ we will use (\ref{general_convexity}), with $\mathbb{Q}_2 = \mathbb{Q}$, $\mathbb{Q}_1 = \mathbb{Q}^{t_1}$ and $x_{t_1}=R(t_0,t_1)$.
+To compute $\mathbb{E}^{\mathbb{Q}}\left[R(t_0,t_1)\right]$ we will use (\ref{general_convexity}), with $\mathbb{Q}_2 = \mathbb{Q}$, $\mathbb{Q}_1 = \mathbb{Q}^{t_1}$ and $x_{t_1}=R(t_0,t_1)$.
 If we apply $D_s$ on $I(t_0,t_1)$ we obtain that
@@
 \begin{align}\label{apprx_I_t0_t1}
-I(t_0,t_1) &= \mathbb{E}_t^{\mathbb{Q}}\left(I(t_0,t_1)\right) + \int_{t}^{t_1}\int_{\max(s, t_{0})}^{t_1}  \mathbb{E}_s^{\mathbb{Q}}\left(\beta(s,u,x_s,y_s) \bar{M}(s,u) \right) du dW_s^{\mathbb{Q}} \nonumber \\
-&\approx \mathbb{E}_t^{\mathbb{Q}}\left(I(t_0,t_1)\right) + \int_{t}^{t_1}\int_{\max(s, t_{0})}^{t_1} \beta(s,u,\bar{x}_0(t_1),\bar{y}_s) du dW_s^{\mathbb{Q}}\nonumber \\
-&= \mathbb{E}_t^{\mathbb{Q}}\left(I(t_0,t_1)\right) + \int_{t}^{t_1} g(s)h(s,\bar{x}_0(t_1),\bar{y}_s)\int_{\max(s, t_{0})}^{t_1} \exp\left( -\int_{s}^{u} k_{s^{\prime}} ds^{\prime}\right) du dW_s^{\mathbb{Q}}.
+I(t_0,t_1) &= \mathbb{E}_t^{\mathbb{Q}}\left[I(t_0,t_1)\right] + \int_{t}^{t_1}\int_{\max(s, t_{0})}^{t_1}  \mathbb{E}_s^{\mathbb{Q}}\left[\beta(s,u,x_s,y_s) \bar{M}(s,u) \right] du dW_s^{\mathbb{Q}} \nonumber \\
+&\approx \mathbb{E}_t^{\mathbb{Q}}\left[I(t_0,t_1)\right] + \int_{t}^{t_1}\int_{\max(s, t_{0})}^{t_1} \beta(s,u,\bar{x}_0(t_1),\bar{y}_s) du dW_s^{\mathbb{Q}}\nonumber \\
+&= \mathbb{E}_t^{\mathbb{Q}}\left[I(t_0,t_1)\right] + \int_{t}^{t_1} g(s)h(s,\bar{x}_0(t_1),\bar{y}_s)\int_{\max(s, t_{0})}^{t_1} \exp\left( -\int_{s}^{u} k_{s^{\prime}} ds^{\prime}\right) du dW_s^{\mathbb{Q}}.
 \end{align}
@@
 \begin{align*}
-1 + \delta_{t_0,t_1}\mathbb{E}_t^{\mathbb{Q}}\left(R(t_0,t_1)\right) &= \mathbb{E}_t^{\mathbb{Q}}\left( \exp(I(t_0,t_1)) \right)\\
-&\approx \exp\left(\mathbb{E}_t^{\mathbb{Q}}\left(I(t_0,t_1)\right)\right)  \mathbb{E}^{\mathbb{Q}}\left(\exp\left(\int_{t}^{t_1} \Gamma(s,t_0,t_1)dW_s^{\mathbb{Q}}\right)\right)
-\end{align*}
-where $\Gamma(s,t_0,t_1)= g(s)h(s,x_0,y_0)\int_{\max(s, t_{0})}^{t_1} \exp\left( -\int_{s}^{u} k_{s^{\prime}} ds^{\prime}\right)du$.\\
+1 + \delta_{t_0,t_1}\mathbb{E}_t^{\mathbb{Q}}\left[R(t_0,t_1)\right] &= \mathbb{E}_t^{\mathbb{Q}}\left[ \exp(I(t_0,t_1)) \right]\\
+&\approx \exp\left(\mathbb{E}_t^{\mathbb{Q}}\left[I(t_0,t_1)\right]\right)  \mathbb{E}^{\mathbb{Q}}\left[\exp\left(\int_{t}^{t_1} \Gamma(s,t_0,t_1)dW_s^{\mathbb{Q}}\right)\right]
+\end{align*}
+where 
+\begin{align*}
+\Gamma(s,t_0,t_1)= g(s)h(s,x_0,y_0)\int_{\max(s, t_{0})}^{t_1} \exp\left( -\int_{s}^{u} k_{s^{\prime}} ds^{\prime}\right)du.
+\end{align*}
 Therefore, we have that
 \begin{equation}\label{representation_i_0_t}
-1 + \delta_{t_0,t_1}\mathbb{E}^{\mathbb{Q}}\left(R(t_0,t_1)\right) \approx \exp\left(\mathbb{E}^{\mathbb{Q}}\left(I(t_0,t_1)\right)\right)\exp\left(-\int_{t}^{t_1}\frac{\Gamma^{2}(s,t_0,t_1)}{2} ds\right).
+1 + \delta_{t_0,t_1}\mathbb{E}^{\mathbb{Q}}\left[R(t_0,t_1)\right] \approx \exp\left(\mathbb{E}^{\mathbb{Q}}\left[I(t_0,t_1)\right]\right)\exp\left(-\frac{1}{2}\int_{t}^{t_1}\Gamma^{2}(s,t_0,t_1) ds\right).
 \end{equation}
@@
 
-In order to get an approximation of $\mathbb{E}^{\mathbb{Q}}\left(R_{avg}(t_0,t_1)\right)$ with base $\mathbb{E}^{\mathbb{Q}}\left(R(t_0,t_1)\right)$, we must note that 
-\begin{equation*}
-\mathbb{E}_t^{\mathbb{Q}}\left(R_{avg}(t_0,t_1)\right) = \frac{\mathbb{E}_t^{\mathbb{Q}}\left( \log(1+ \delta_{t_0,t_1} R(t_0,t_1))\right)}{ \delta_{t_0,t_1}}.
+In order to get an approximation of $\mathbb{E}^{\mathbb{Q}}\left[R_{avg}(t_0,t_1)\right]$ with base $\mathbb{E}^{\mathbb{Q}}\left[R(t_0,t_1)\right]$, we must note that 
+\begin{equation*}
+\mathbb{E}_t^{\mathbb{Q}}\left[R_{avg}(t_0,t_1)\right] = \frac{\mathbb{E}_t^{\mathbb{Q}}\biggl[ \log\Bigl(1+ \delta_{t_0,t_1} R(t_0,t_1)\Bigr)\biggr]}{ \delta_{t_0,t_1}}.
 \end{equation*}
@@
 \begin{equation}\label{general_convexity_fras}
-L_{E}(t_1,t_1,t_2) = \mathbb{E}^{t_2}\left(L_{E}(t_1,t_1,t_2) \right) + \int_{0}^{t_1} \mathbb{E}^{t_2}\left(D_s L_{E}(t_1,t_1,t_2) \right) dW^{\mathbb{Q}^{t_2}}_{s}
+L_{E}(t_1,t_1,t_2) = \mathbb{E}^{t_2}\Bigl[L_{E}(t_1,t_1,t_2) \Bigr] + \int_{0}^{t_1} \mathbb{E}^{t_2}\Bigl[D_s L_{E}(t_1,t_1,t_2) \Bigr] dW^{\mathbb{Q}^{t_2}}_{s}
 \end{equation}
@@
 \begin{equation*}
-dW^{\mathbb{Q}^{t_2}}_s = dW^{\mathbb{Q}^{t_1}}_s + (\nu(s,t_2) - \nu(s,t_1)) ds. 
+dW^{\mathbb{Q}^{t_2}}_s = dW^{\mathbb{Q}^{t_1}}_s + \Bigl(\nu(s,t_2) - \nu(s,t_1)\Bigr) ds. 
 \end{equation*}
@@
 \begin{align*}
-\mathbb{E}^{t_1}\left(L_{E}(t_1,t_1,t_2) \right) &= L_{E}(0,t_1,t_2) + \mathbb{E}^{t_1}\left( \int_{0}^{t_1} \mathbb{E}_s^{t_2}\left(D_s L_{E}(t_1,t_1,t_2) \right) dW^{t_2}_{s}\right)\\
-&= L_{E}(0,t_1,t_2) + \mathbb{E}^{t_1}\left( \int_{0}^{t_1} \mathbb{E}_s^{t_2}\left(D_s L_{E}(t_1,t_1,t_2) \right) (\nu(s,t_2)-\nu(s,t_1)) ds \right).
+\mathbb{E}^{t_1}\left[L_{E}(t_1,t_1,t_2) \right] &= L_{E}(0,t_1,t_2) + \mathbb{E}^{t_1}\left[ \int_{0}^{t_1} \mathbb{E}_s^{t_2}\Bigl[D_s L_{E}(t_1,t_1,t_2)\Bigr] dW^{t_2}_{s}\right]\\
+&= L_{E}(0,t_1,t_2) + \mathbb{E}^{t_1}\left[ \int_{0}^{t_1} \mathbb{E}_s^{t_2}\Bigl[D_s L_{E}(t_1,t_1,t_2) \Bigr] \Bigl(\nu(s,t_2)-\nu(s,t_1)\Bigr) ds \right].
 \end{align*}
@@
 D_s L(t_1,t_1,t_2) &=& \frac{G(t_1,t_2)}{\delta_{t_1,t_2}P_{E}(t_1,t_2)} D_s x_{t_1}\\
-&\approx& \frac{G(t_1,t_2)}{\delta_{t_1,t_2}P_{E}(0,t_1,t_2)} \beta(s,t_1, \bar{x}_0(t_1), \bar{y}_s)\bar{DM}(s,t_1)
+&\approx& \frac{G(t_1,t_2)}{\delta_{t_1,t_2}P_{E}(0,t_1,t_2)} \beta(s,t_1, \bar{x}_0(t_1), \bar{y}_s)\overline{DM}(s,t_1)
 \end{eqnarray*}
@@
 \begin{equation*}
-CA(t_0,t_1) \approx \frac{G(t_1,t_2)}{\delta_{t_1,t_2}P_{E}(0,t_1,t_2)} \beta(s,t_1, \bar{x}_0(t_1), \bar{y}_s) \int_{0}^{t_1} \bar{DM}(s,t_1) (\bar{\nu}(s,t_2,\bar{x}_{0}(t_1))-\bar{\nu}(s,t_1,\bar{x}_{0}(t_1))) ds
-\end{equation*}
-with $\bar{\nu}(t,t_p, \bar{x}_0(t_a))= \int_{t}^{t_p} \eta(s,\bar{x}_0(t_a),\bar{y}_s) ds$.
+CA(t_0,t_1) \approx \frac{G(t_1,t_2)}{\delta_{t_1,t_2}P_{E}(0,t_1,t_2)} \beta(s,t_1, \bar{x}_0(t_1), \bar{y}_s) \int_{0}^{t_1} \overline{DM}(s,t_1) \Bigl(\bar{\nu}(s,t_2,\bar{x}_{0}(t_1))-\bar{\nu}(s,t_1,\bar{x}_{0}(t_1))\Bigr) ds
+\end{equation*}
+with 
+\begin{equation*}
+\bar{\nu}(t,t_p, \bar{x}_0(t_a))= \int_{t}^{t_p} \eta(s,\bar{x}_0(t_a),\bar{y}_s) ds.   
+\end{equation*}
 
@@
 \begin{equation}
-CA_{CMS}(t_p) = \mathbb{E}^{t_p}\left(S_{a,b}(t_a)\right) - S_{a,b}(0).
+CA_{CMS}(t_p) = \mathbb{E}^{t_p}\left[S_{a,b}(t_a)\right] - S_{a,b}(0).
 \end{equation} 
@@
 \begin{align}
-\mathbb{E}^{t_p}\left(S_{a,b}(t_a)\right) &= \frac{1}{M(0,t_p)} \mathbb{E}^{01}\left(S_{a,b}(t_a) M(t_a,t_p)\right) \nonumber \\
-&= \frac{1}{M(0,t_p)} \mathbb{E}^{01}\left(S_{a,b}(t_a) \mathbb{E}^{01}\left( M(t_a,t_p)|S_{a,b}(t_a)\right) \right) \nonumber
-\end{align}
-with $M(t,t_p)= \frac{P_{ois}(t,t_p)}{01(t,t_a,t_p)}$.\\
-
+\mathbb{E}^{t_p}\left(S_{a,b}(t_a)\right) &= \frac{1}{M(0,t_p)} \mathbb{E}^{01}\left[S_{a,b}(t_a) M(t_a,t_p)\right] \nonumber \\
+&= \frac{1}{M(0,t_p)} \mathbb{E}^{01}\biggl[S_{a,b}(t_a) \mathbb{E}^{01}\Bigl[ M(t_a,t_p)|S_{a,b}(t_a)\Bigr] \biggr] \nonumber
+\end{align}
+with 
+\begin{align*}
+M(t,t_p)= \frac{P_{ois}(t,t_p)}{01(t,t_a,t_p)}.
+\end{align*}
 Then, we can approximate it by
 \begin{align}\label{expected_t_p_cms}
-\mathbb{E}^{t_p}\left(S_{a,b}(t_a)\right) &\approx  \frac{1}{M(0,t_p)} \mathbb{E}^{01}\left(S^{ois}_{a,b}(t_a) \mathbb{E}^{01}\left( M(t_a,t_p)|S_{a,b}(t_a)\right) \right) \\
+\mathbb{E}^{t_p}\left(S_{a,b}(t_a)\right) &\approx  \frac{1}{M(0,t_p)} \mathbb{E}^{01}\biggl[S^{ois}_{a,b}(t_a) \mathbb{E}^{01}\Bigl[ M(t_a,t_p)|S_{a,b}(t_a)\Bigr] \biggr] \\
 \qquad\qquad &+ \frac{\sum_{i=1}^{n_E}\delta_{t^{E}_{i-1}, t^{E}_i} \alpha(0,t^{E}_{i-1}, t^{E}_{i}) P_{ois}(0,t^{E}_{i})} {01(0,t_a,t_b)}.
@@
 \begin{equation}\label{Exp_M_conditional}
-\mathbb{E}^{01}\left( M(t_a,t_p)|S_{a,b}(t_a)\right).
+\mathbb{E}^{01}\Bigl[ M(t_a,t_p)|S_{a,b}(t_a)\Bigr].
 \end{equation}
 In order to reduce this complexity, it is a common practice to assume that $M(t_a,t_p)$ is a function of the swap rate $S_{a,b}(t_a)$, i.e   $M(t_a,t_p)=f(S_{a,b}(t_a))$.
-Under this assumption (\ref{Exp_M_conditional}) is trivial to calulate it.
+Under this assumption (\ref{Exp_M_conditional}) is trivial to calculate it.
 The function $f(\cdot)$ is known as mapping function.
@@
 \begin{equation} \label{clark_ocone_swap_m}
-M(t_a,t_p) = M(0,t_p)+ \int_{0}^{t_a} \mathbb{E}_s^{01}\left(D_s M(t_a,t_p)\right) dW^{01}_s
+M(t_a,t_p) = M(0,t_p)+ \int_{0}^{t_a} \mathbb{E}_s^{01}\Bigl[D_s M(t_a,t_p)\Bigr] dW^{01}_s
 \end{equation}
@@
 \begin{align}\label{cms_first_order_convexity_prev}
-\mathbb{E}^{t_p}\left(S_{a,b}(t_a)\right) =& S^{ois}_{a,b}(0) + \frac{1}{M(0,t_p)} \mathbb{E}^{01}\left( S^{ois}_{a,b}(t_a) \int_{0}^{t_a} \mathbb{E}^{0,1}_s\left(D_s x_{t_a}\partial_x M(t_a,t_p)  \right) dW^{0,1}_s   \right) \nonumber \\
-=&  S^{ois}_{a,b}(0) + \frac{1}{M(0,t_p)} \mathbb{E}^{01}\left(\int_{0}^{t_a} D_s x_{t_a} \partial_x S_{a,b}(t_a) \mathbb{E}^{0,1}_s\left(D_s x_{t_a}\partial_x M(t_a,t_p)  \right) ds   \right)
+\mathbb{E}^{t_p}\left(S_{a,b}(t_a)\right) =& S^{ois}_{a,b}(0) + \frac{1}{M(0,t_p)} \mathbb{E}^{01}\left[ S^{ois}_{a,b}(t_a) \int_{0}^{t_a} \mathbb{E}^{0,1}_s\Bigl[D_s x_{t_a}\partial_x M(t_a,t_p)  \Bigr] dW^{0,1}_s   \right] \nonumber \\
+=&  S^{ois}_{a,b}(0) + \frac{1}{M(0,t_p)} \mathbb{E}^{01}\left[\int_{0}^{t_a} D_s x_{t_a} \partial_x S_{a,b}(t_a) \mathbb{E}^{0,1}_s\Bigl[D_s x_{t_a}\partial_x M(t_a,t_p)  \Bigr] ds   \right]
 \end{align}
@@
 \begin{align}
-\mathbb{E}^{t_p}\left(S_{a,b}(t_a)\right) &\approx  S^{ois}_{a,b}(0) + \frac{\partial_x S_{a,b}(t_a,\bar{x}_0(t_a), \bar{y}_0) \partial_x M(t_a,t_p,\bar{x}_0(t_a), \bar{y}_0)} \nonumber \\
+\mathbb{E}^{t_p}\left[S_{a,b}(t_a)\right] &\approx  S^{ois}_{a,b}(0) + \frac{\partial_x S_{a,b}(t_a,\bar{x}_0(t_a), \bar{y}_0) \partial_x M(t_a,t_p,\bar{x}_0(t_a), \bar{y}_0)} {M(0,t_p)}\nonumber \\
 &\cdot \int_{0}^{t_a}  \beta^2(s,t_a,\bar{x}_0(t_a),\bar{y}_s)\exp\left(-\int_{s}^{t_a}\partial_x (\beta(u,t_a,\bar{x}_u,\bar{y}_u) \mu(u,\bar{x}_u, \bar{y}_u,t_a,t_b))|_{\bar{x}_u=\bar{x}_{0}(t_a)}  du \right)ds

### 2023-04-16 Latex/paper-resum.tex
Stylish IV

@@
 where $P_{E}(t,T)$ is the discount factor for the curve $E$ from $t$ to $T$, and $\delta_{t_1,t_2}$ is the year fraction between $t_1$ and $t_2$.
-we must note, that $L_{E}(t_0, t_1, t_2)$ is a martingale under the forward measure $\mathbb{Q}^{t_2}$ associated with the numeraire $P_{ois}(t,t_2)$.
+Note that $L_{E}(t_0, t_1, t_2)$ is a martingale under the forward measure $\mathbb{Q}^{t_2}$ associated with the numeraire $P_{ois}(t,t_2)$.
 
@@
 
-In the Figure \ref{fig:Futures}, we can check the accuracy of the last formula versus Monte Carlo. The parameters that we have used are $\sigma=0.015$, $k=0.003$ and flat curve with level $r=0.01$.
+In the Figure \ref{fig:Futures}, we can check the accuracy of the last formula versus Monte Carlo. The parameters used are $\sigma=0.015$, $k=0.003$, and flat curve with level $r=0.01$.
 
@@
 \subsection{OIS futures}
-In this section, we will derive the convexity adjustment for short-term interest rate swap, also known as STIRs.
-It is common in the market to find two version of these futures, depending on how the fixings of the reference index are using.
+In this section, we will derive the convexity adjustment for short-term interest rate swaps, also known as STIRs.
+It is common in the market to find two versions of these futures, depending on how the fixings of the reference index are used.
 Given $t_0 < t_1$, we will define the overnight compounding rate as
@@
 $R(\cdot,t_0,t_1)$ and $R_{avg}(\cdot,t_0,t_1)$ are flows that will be payed in $t_1$.
-Therefore, we can consider that the expected value under the measure $\mathbb{Q}$ is observable during entire period $[t_0, t_1]$.
+Therefore, we can consider that the expected value under the measure $\mathbb{Q}$ is observable during the entire period $[t_0, t_1]$.
 Let us define the next $\mathbb{Q}$ martingales:
@@
 \end{align*}
-Before to continue, we will do several observations.
+Before continuing, we will do several observations.
 The first observation is that if we define $F(t,t_0,t_1) = \mathbb{E}^{\mathbb{Q}^{t_1}}\left( R(t_0,t_1)\right)$, then we have that when $t \in [0,t_0]$
@@
 \mathbb{E}^{\mathbb{Q}}\left(R_{avg}(t_0,t_1) \right) =\frac{1}{\delta_{t_0,t_1}} \mathbb{E}^{\mathbb{Q}}\left[ \log\left(1+ \delta_{t_0,t_1} R(t_0,t_1) \right) \right]  \end{equation}
-In order, to clarify the convexity expression and the calculations, we will define 
+To clarify the convexity expression and the calculations, we will define 
 \begin{equation*}
@@
 
-The next figure, show accuracy of (\ref{convexity_ois_future}) and (\ref{convexity_avg_ois_future}).
-The parameters that we have used to run the Monte Carlo have been $k=0.003$ and volatility $\sigma=0.01$ and flat curve $r=0.01$.
+The following figure shows the accuracy of (\ref{convexity_ois_future}) and (\ref{convexity_avg_ois_future}).
+The parameters used to run the Monte Carlo have been $k=0.003$, a volatility $\sigma=0.01$, and flat curve $r=0.01$.
 \begin{figure}[H]
@@
 \subsection{FRAs in arrears}
-A FRA in arrears is the most classic example among the products with convexity adjustment. The price is given by 
+A FRA in arrears is the most classic example among convexity adjustment products. The price is given by
 \begin{equation}\label{FRAinArrear}
@@
 \end{equation}
-i.e. the cash flow associated to a FRA in arrears is $L_{E}(t_1,t_1,t_2)$ in $t_1$.
+i.e. the cash flow associated with a FRA in arrears is $L_{E}(t_1,t_1,t_2)$ in $t_1$.
 
@@
 CA(t_0,t_1) =   &\frac{G(t_1,t_2)}{\delta_{t_1,t_2}P_{E}(0,t_1,t_2)} \beta(s,t_1, \bar{x}_0(t_1), \bar{y}_s) E(t_1) \nonumber \\
-&\cdot \int_{0}^{t_1} \overline{DM}(s,t_1) (\bar{\nu}(s,t_2,\bar{x}_{0}(t_1))-\bar{\nu}(s,t_1,\bar{x}_{0}(t_1))) ds 
+&\cdot \int_{0}^{t_1} \overline{DM}(s,t_1) \Bigl(\bar{\nu}(s,t_2,\bar{x}_{0}(t_1))-\bar{\nu}(s,t_1,\bar{x}_{0}(t_1))\Bigr) ds 
 \end{align}
@@
 \begin{example}[Convexity adjustment for FRAs in Arrears under the Hull-White model]\label{example_convexity_hw_FRAsinArrears}
-We can restrict the model the the Hull-White model with constant parameters. The analytical approximation that we get from \eqref{ca_approximations_fra_arrears} is
+The model can be restricted to a Hull-White model with constant parameters. The analytical approximation obtained from \eqref{ca_approximations_fra_arrears} is
 \begin{equation*}
@@
 \end{equation*}
-In Figure \ref{fig:FRA_HW}, we compare the approximation with a Monte Carlo method when the parameters are $\sigma=0.1$, $k=0.007$.
+In Figure \ref{fig:FRA_HW}, we compare the approximation with a Monte Carlo method when the parameters are $\sigma=0.1$ and $k=0.007$.
 \begin{figure}[H]
@@
 \begin{equation*}
-\alpha(t,t^{E}_{i-1}, t^{E}_{i})  = \frac{1}{\delta_{t^{E}_{i-1}, t^{E}_i}}\left(\frac{H(t,t^{E}_{i-1})}{H(t,t^{E}_{i})} - 1\right)
+\alpha(t,t^{E}_{i-1}, t^{E}_{i})  = \frac{1}{\delta_{t^{E}_{i-1}, t^{E}_i}}\left(\frac{H(t,t^{E}_{i-1})}{H(t,t^{E}_{i})} - 1\right).
 \end{equation*}
@@
 \begin{align} \label{cms_first_order_convexity}
-CA(t_p) &\approx  E(t_a) + \frac{\partial_x S_{a,b}(t_a,\bar{x}_0(t_a), \bar{y}_0) \partial_x M(t_a,t_p,\bar{x}_0(t_a), \bar{y}_0)}{M(0,t_p)} \nonumber \\
+CA(t_p) &\approx  E(t_a) + \frac{\partial_x S_{a,b}(t_a,\bar{x}_0(t_a), \bar{y}_0) \partial_x M(t_a,t_p,\bar{x}_0(t_a), \bar{y}_0)}{M(0,t_p)}  \\
 &\cdot \int_{0}^{t_a}  \beta^2(s,t_a,\bar{x}_0(t_a),\bar{y}_s) \exp\left(-2\int_{s}^{t_a}\partial_x (\beta(u,t_a,\bar{x}_u,\bar{y}_u) \mu(u,\bar{x}_u, \bar{y}_u,t_a,t_b))|_{\bar{x}_u=\bar{x}_{0}(t_a)}  du \right)ds \nonumber
@@
 \begin{remark}
-The key point is calculate an approximation of $\mathbb{E}_s^{0,1}\left( D_s \bar{x}_{t_a}\right)$.
+The key point is calculate an approximation of $\mathbb{E}_s^{0,1}\left[ D_s \bar{x}_{t_a}\right]$.
 The simplest cases are on the Hull-White or Ho-Lee model.
@@
 \begin{example}[Convexity adjustment for CMS under the Hull-White model]
-To check the accuracy of the last approximation, we compute with a Monte Carlo the exact value of $\mathbb{E}^{t_p}\left(S^{ois}_{a,b}(t_a)\right)$ under spot measure $\mathbb{Q}$, i.e we will compute  $\frac{1}{P(0,t_p)}  \mathbb{E}^{\mathbb{Q}}\left(\frac{S_{a,b}(t_a)}{\beta_{t_a}} \right)$.
+To check the accuracy of the last approximation, we compute with a Monte Carlo the exact value of $\mathbb{E}^{t_p}\left[S^{ois}_{a,b}(t_a)\right]$ under spot measure $\mathbb{Q}$, i.e we will compute  $\frac{1}{P(0,t_p)}  \mathbb{E}^{\mathbb{Q}}\left[\frac{S_{a,b}(t_a)}{\beta_{t_a}} \right]$.
 For the Hull-White model case, we have that
@@
 We find the approximation for Futures, OIS Futures, FRAs, and CMSs under a general family of the one-factor Cheyette model.
-We have also seen the excellent quality of the numerical accuracy of the formulas obtained.
+We have also seen the excellent quality of the numerical accuracy of the formulas obtained.\\
 
@@
 \subsection{Estimation of $\mathbb{E}_s^{\mathbb{Q}}\left[(x_t - \bar{x}_{t})^{2}\right]$}\label{estimation_error_l2}
-In order to get the order of the approximation, we will use the ideas of the paper \cite{B-G-M-2008}.
+To obtain the order of the approximation, we will use the ideas of the paper \cite{B-G-M-2008}.
 Basically, we will define a parametrization of the process $x_{t,\epsilon}$ and $y_{t,\epsilon}$ with $\epsilon \in [0,1]$.
-The role of $\epsilon$ is only as interpolation parameter between process.
-We will suppose the next parametrization of the Cheyette model
+The role of $\epsilon$ is only as an interpolation parameter between the process.
+We will suppose the next Cheyette model parametrization
 \begin{align}\label{parametric_process}
@@
 The reason of $\epsilon^{2}$ in $y_{\epsilon,t}$ is because $\mathbb{E}^{\mathbb{Q}}\left[y_t\right]= \mathbb{V}ar(x_t)$.
-Then, if the scale of $x_{\epsilon,t}$ is $\epsilon$ then the scale of $y_{\epsilon,t}$ must be $\epsilon^{2}$.
-We will start with the estimation of $\mathbb{E}^{\mathbb{Q}}\left[(y_t - \bar{y}_t)^{2}\right]$.
-We will define the next parametrization for $\nu \in [0,1]$
+Therefore, if the scale of $x_{\epsilon,t}$ is $\epsilon$, then the scale of $y_{\epsilon,t}$ must be $\epsilon^{2}$.\\
+
+We will start with the estimation of $\mathbb{E}^{\mathbb{Q}}\left[(y_t - \bar{y}_t)^{2}\right]$. We will define the next parametrization for $\nu \in [0,1]$
 \begin{equation*}
@@
 \end{equation*}
-Then we have that $z^{1}_{u} = \eta(u,x_u,y_u)$ y $z^{0}_{u} = \eta(u,0,0)$. Therefore
+Then, we have that $z^{1}_{u} = \eta(u,x_u,y_u)$ y $z^{0}_{u} = \eta(u,0,0)$. Therefore,
 \begin{align*}
@@
 \end{align*}
-Then we have that
+Moreover, we have that
 \begin{equation*}
@@
 $$
-E_{y}(t)= 2 \int_{0}^{t} \exp\left(- 2\int_{u}^{t} k(u^{\prime}) du^{\prime}\right)  \int_{0}^{1} \eta(u, \nu x_u, \nu y_u)   \nabla_{x,y}\eta(u, \nu x_u, \nu y_u) \cdot (x_u, y_u) d\nu du
+E_{y}\left[t\right]= 2 \int_{0}^{t} \exp\left(- 2\int_{u}^{t} k(u^{\prime}) du^{\prime}\right)  \int_{0}^{1} \eta(u, \nu x_u, \nu y_u)   \nabla_{x,y}\eta(u, \nu x_u, \nu y_u) \cdot (x_u, y_u) d\nu du
 $$
-Now, from Cauchy-Schwarz inequality we have that
+Now, from Cauchy-Schwarz inequality, we obtain that
 \begin{align} \label{upper_bound_E_y}
@@
 &\leq 4 \|\eta\|^{2}_{\infty} \max(\|\partial_x\eta\|^{2}_{\infty},\|\partial_y \eta\|^{2}_{\infty} ) \int_{0}^{t} \mathbb{E}^{\mathbb{Q}}\left[ \|(x_u, y_u)\|^{2}\right] du  \nonumber \\
-&= M^{y}_k \int_{0}^{t} \mathbb{E}^{\mathbb{Q}}\left[\|(x_u, y_u)\|^{2}\right] du
+&= M^{y}_k \int_{0}^{t} \mathbb{E}^{\mathbb{Q}}\left[\|(x_u, y_u)\|^{2}\right] du.
 \end{align}
@@
 \end{equation*}
-In order, to find a expansion of $\eta(t,x_u,y_u)$ centered in $\bar{y}_u$, we will define $z^{\nu}_{u} = (1-\nu)\bar{y}_{u} + \nu y_u$. Then
-\begin{equation*}
-\eta(t,x_u,y_u) = \eta(t,x_u,\bar{y}_u) + \int_{0}^{1}\partial_y\eta(t,x_u,z^{\nu}_{u}) E_{y}[u] d\nu
-\end{equation*}
-We will define $E_{x}(u) = \int_{0}^{1}\partial_y\eta(t,x_u,z^{\nu}_{u}) E_{y}[u] d\nu$. Then we have the next representation of $x_t$
+To find a expansion of $\eta(t,x_u,y_u)$ centered in $\bar{y}_u$, we will define $z^{\nu}_{u} = (1-\nu)\bar{y}_{u} + \nu y_u$. Then
+\begin{equation*}
+\eta(t,x_u,y_u) = \eta(t,x_u,\bar{y}_u) + \int_{0}^{1}\partial_y\eta(t,x_u,z^{\nu}_{u}) E_{y}[u] d\nu.
+\end{equation*}
+We will define 
+\begin{equation*}
+E_{x}\left[u\right] = \int_{0}^{1}\partial_y\eta(t,x_u,z^{\nu}_{u}) E_{y}[u] d\nu. 
+\end{equation*}
+Therefore, we have the next representation of $x_t$:
 \begin{equation*}
@@
 \end{equation*}
-We must note that
-\begin{equation*}
- \mathbb{E}^{\mathbb{Q}}[(E_x[u])^{2}] \leq \|\partial_y \eta \|^{2}_{\infty} \mathbb{E}^{\mathbb{Q}}[(E_{y}[u])^{2}]  
-\end{equation*}
-Then using (\ref{upper_bound_E_y}) we get that
+Note that
+\begin{equation*}
+ \mathbb{E}^{\mathbb{Q}}[(E_x[u])^{2}] \leq \|\partial_y \eta \|^{2}_{\infty} \mathbb{E}^{\mathbb{Q}}[(E_{y}[u])^{2}]. 
+\end{equation*}
+Using (\ref{upper_bound_E_y}), we get that
 \begin{equation}\label{upper_bound_E_x}
- \mathbb{E}^{\mathbb{Q}}[(E_x[u])^{2}] \leq 4 \|\eta\|^{2}_{\infty} \|\partial_y \eta\|^{2}_{\infty} \max(\|\partial_x\eta\|^{2}_{\infty},\|\partial_y \eta\|^{2}_{\infty} ) \int_{0}^{u} \mathbb{E}^{\mathbb{Q}}\left[ \|(x_s, y_s)\|^{2}\right] ds
-\end{equation}
-Then from (\ref{upper_bound_E_x}) and (\ref{upper_bound_E_y}) we get that 
+ \mathbb{E}^{\mathbb{Q}}[(E_x[u])^{2}] \leq 4 \|\eta\|^{2}_{\infty} \|\partial_y \eta\|^{2}_{\infty} \max(\|\partial_x\eta\|^{2}_{\infty},\|\partial_y \eta\|^{2}_{\infty} ) \int_{0}^{u} \mathbb{E}^{\mathbb{Q}}\left[ \|(x_s, y_s)\|^{2}\right] ds.
+\end{equation}
+By using \eqref{upper_bound_E_x} and \eqref{upper_bound_E_y}, we have that 
 \begin{align*}
@@
 &\leq 2 \mathbb{E}^{\mathbb{Q}}\left[\int_{0}^{t} \exp\left(- 2\int_{u}^{t} k(u^{\prime}) du^{\prime}\right) \mathbb{E}^{\mathbb{Q}}(E^{2}_{y}(u)) du\right]\\
-&+ \int_{0}^{t} \exp\left(- 2\int_{u}^{t} k(u^{\prime}) du^{\prime}\right) \mathbb{E}^{\mathbb{Q}}[E^{2}_{x}[u]] du   
-\end{align*}
-Them if we join each part, we have that for an adequate constant $M^{x}_k$ 
-\begin{equation*}
-\mathbb{E}^{\mathbb{Q}}[(x_t - \bar{x}_t)^{2}]\leq M^{x}_k \int_{0}^{t} \exp\left(- 2\int_{u}^{t} k(u^{\prime}) du^{\prime}\right) \mathbb{E}^{\mathbb{Q}}\left[ \|(x_u, y_u)\|^{2}\right] du 
-\end{equation*}
-To end, only we have to estimate $\mathbb{E}^{\mathbb{Q}}\left[ \|(x_s, y_s)\|^{2}\right]$. From the definition of $y_t$ and since $\|\eta\|_{\infty} < \infty$, we have that
+&+ \int_{0}^{t} \exp\left(- 2\int_{u}^{t} k(u^{\prime}) du^{\prime}\right) \mathbb{E}^{\mathbb{Q}}[E^{2}_{x}[u]] du. 
+\end{align*}
+Join each part and for an adequate constant $M^{x}_k$, we have the following inequality 
+\begin{equation*}
+\mathbb{E}^{\mathbb{Q}}[(x_t - \bar{x}_t)^{2}]\leq M^{x}_k \int_{0}^{t} \exp\left(- 2\int_{u}^{t} k(u^{\prime}) du^{\prime}\right) \mathbb{E}^{\mathbb{Q}}\left[ \|(x_u, y_u)\|^{2}\right] du.
+\end{equation*}
+Finally, we only have to estimate $\mathbb{E}^{\mathbb{Q}}\left[ \|(x_s, y_s)\|^{2}\right]$. From the definition of $y_t$ and given that $\|\eta\|_{\infty} < \infty$, we have that
 \begin{equation*}
@@
 \end{equation*}
-We must note that at the short term and under assumptions (\ref{boundedness_reversion}) we have that
+We must note that at the short term and under assumptions (\ref{boundedness_reversion}), we get that
 \begin{equation*}
@@
 \end{equation*}
-Now $\mathbb{E}^{\mathbb{Q}}[x^{2}_u]$. From the definition of $x_t$ and using $(a+b)^2 \leq 2(a^{2}+ b^{2})$ we have that
+Now, we will estimate $\mathbb{E}^{\mathbb{Q}}[x^{2}_u]$. From the definition of $x_t$ and using $(a+b)^2 \leq 2(a^{2}+ b^{2})$, we have that
 \begin{align*}
@@
 \end{align*}
-Then as before at the short term
+So as before at the short term
 $$
@@
 $$
-and when ($u \to \infty$) we have that $\mathbb{E}^{\mathbb{Q}}(x^{2}_u)$ remains bounded. Then, if we use the above inequalities 
+and when ($u \to \infty$) we have that $\mathbb{E}^{\mathbb{Q}}[x^{2}_u]$ remains bounded. Then, if we use the above inequalities 
 \begin{align*}
@@
 \end{equation*} 
-With $\beta(u,t_a,x,y) = \exp\left(-\int_{u}^{t_a}k_u^{\prime} du^{\prime}\right) \partial_x \eta(u,x,y)$. We have also that
+with $\beta(u,t_a,x,y) = \exp\left(-\int_{u}^{t_a}k_u^{\prime} du^{\prime}\right) \partial_x \eta(u,x,y)$.\\
+
+We have also that
 \begin{align}\label{approsimation_E_s_x_t}
-\mathbb{E}_s^{t_p}\left(D_s \bar{x}_{t_a}\right) &\approx \beta(s,t_a,\bar{x}_s,\bar{y}_s) \bar{DM}(s,t_a) \nonumber \\
-\mathbb{E}_s^{\mathbb{Q}}\left(D_s \bar{x}_{t_a}\right)&\approx \beta(s,t_a,\bar{x}_s,\bar{y}_s)
+\mathbb{E}_s^{t_p}\left[D_s \bar{x}_{t_a}\right] &\approx \beta(s,t_a,\bar{x}_s,\bar{y}_s) \overline{DM}(s,t_a), \nonumber \\
+\mathbb{E}_s^{\mathbb{Q}}\left[D_s \bar{x}_{t_a}\right]&\approx \beta(s,t_a,\bar{x}_s,\bar{y}_s)
 \end{align}
@@
 \begin{align*}
-\overline{DM}(s,t_a) &= \mathbb{E}^{t_p}_s\left(\exp\left(-\int_{s}^{t_a} \exp\left(-\int_{u}^{t_a}k_u du\right)\left(\partial_x \eta(u, \bar{x}_0(t_a), \bar{y}_{u}) \bar{\nu}(u,t_p, \bar{x}_0(t_a)) \right.
-\right.
-\right.
-\\
-&+ \left. \left. \left. \eta(u,\bar{x}_0(t_a), \bar{y}_{u})) \partial_x \bar{\nu}(t,t_p, \bar{x}_0(t_a)) \right)  du \right)\right) 
+\overline{DM}(s,t_a) &= \mathbb{E}^{t_p}_s\biggl[\exp\biggr(-\int_{s}^{t_a} \exp\Bigl(-\int_{u}^{t_a}k_u du\Bigr) \Bigl(\partial_x \eta(u, \bar{x}_0(t_a), \bar{y}_{u}) \bar{\nu}(u,t_p, \bar{x}_0(t_a)) + \eta(u,\bar{x}_0(t_a), \bar{y}_{u})\Bigr) \\
+\qquad &\hspace{3cm} \cdot \partial_x \bar{\nu} (t,t_p, \bar{x}_0(t_a)) du\biggr)\biggr]
 \end{align*}
@@
 \begin{align*}
-\bar{\nu}(t,t_p) &= \int_{t}^{t_p} \eta(s,\bar{x}_s,\bar{y}_s) ds \\
-\bar{\nu}(t,t_p, x_0) &= \int_{t}^{t_p} \eta(s,x,\bar{y}_s) ds \\
-\partial_x \bar{\nu}(t,t_p,x_0) &= \int_{t}^{t_p} \eta(s,x_0,\bar{y}_s) ds\\
+\bar{\nu}(t,t_p) &= \int_{t}^{t_p} \eta(s,\bar{x}_s,\bar{y}_s) ds, \\
+\bar{\nu}(t,t_p, x_0) &= \int_{t}^{t_p} \eta(s,x,\bar{y}_s) ds,\\
+\intertext{and}
+\partial_x \bar{\nu}(t,t_p,x_0) &= \int_{t}^{t_p} \eta(s,x_0,\bar{y}_s) ds
 \end{align*}
@@
 \begin{align*}
-\mathbb{E}^{t_p}_s(D_s \bar{x}_{t_a}) &\approx \eta(s,\bar{x}_s,\bar{y}_s) \exp\left(-\int_{s}^{t_a}k_u du \right)\\ &\cdot \exp\left(-\int_{s}^{t_a} \exp\left(-\int_{u}^{t_a}k_u du\right)\left(\partial_x (\eta(u, \bar{x}_0(t_a), \bar{y}_{u})) \bar{\nu}(u,t_p, \bar{x}_0(t_a)) \right.
-\right.
-\\
-&+  \left. \left. \eta(u, \bar{x}_0(t_a), \bar{y}_{u})) \partial_x  \bar{\nu}(t,t_p, \bar{x}_0(t_a)) du \right)\right)
+\mathbb{E}^{t_p}_s[D_s \bar{x}_{t_a}] &\approx \eta(s,\bar{x}_s,\bar{y}_s) \exp\left(-\int_{s}^{t_a}k_u du \right)\\ &\cdot \exp\biggr(-\int_{s}^{t_a} \exp\Bigl(-\int_{u}^{t_a}k_u du\Bigr) \Bigl(\partial_x \eta(u, \bar{x}_0(t_a), \bar{y}_{u}) \bar{\nu}(u,t_p, \bar{x}_0(t_a)) + \eta(u,\bar{x}_0(t_a), \bar{y}_{u})\Bigr) \\
+\qquad &\hspace{3cm} \cdot \partial_x \bar{\nu} (t,t_p, \bar{x}_0(t_a)) du\biggr)
 \end{align*}
@@
 \subsection{Approximation of $\mathbb{E}_s^{\mathbb{Q}}\left[D_s \bar{x}_{t_a}\right]$}
-As above appendix we have that
+As in the previous appendix, we have
 \begin{align*}
@@
 \begin{equation}
-D_s \bar{x}_{t_a} =  \exp\left(-\int_{s}^{t_a}k_u du \right) \eta(s,\bar{x}_s,\bar{y}_{s})\bar{M}(s,t_a)
-\end{equation}
-Now, if we take $\mathbb{E}_s^{\mathbb{Q}}\left[\cdot\right]$ we get
+D_s \bar{x}_{t_a} =  \exp\left(-\int_{s}^{t_a}k_u du \right) \eta(s,\bar{x}_s,\bar{y}_{s})\bar{M}(s,t_a).
+\end{equation}
+Now, if we take $\mathbb{E}_s^{\mathbb{Q}}\left[\cdot\right]$, we get
 \begin{equation}\label{approximation_spot_E_s_x_t}
-\mathbb{E}^{\mathbb{Q}}_s\left(D_s \bar{x}_{t_a} \right)=\exp\left(-\int_{s}^{t_a}k_u du \right) \eta(s,\bar{x}_s,\bar{y}_{s})
-\end{equation}
-Therefore, we have that
+\mathbb{E}^{\mathbb{Q}}_s\left(D_s \bar{x}_{t_a} \right)=\exp\left(-\int_{s}^{t_a}k_u du \right) \eta(s,\bar{x}_s,\bar{y}_{s}).
+\end{equation}
+Then, we obtain that
 \begin{equation}\label{approximation_spot_E_s_x_t}
-\mathbb{E}^{\mathbb{Q}}_s\left(D_s \bar{x}_{t_a} \right) \approx \exp\left(-\int_{s}^{t_a}k_u du \right) \eta(s,\bar{x}_0(t_a),\bar{y}_{s})
+\mathbb{E}^{\mathbb{Q}}_s\left(D_s \bar{x}_{t_a} \right) \approx \exp\left(-\int_{s}^{t_a}k_u du \right) \eta(s,\bar{x}_0(t_a),\bar{y}_{s}).
 \end{equation}
@@
 \subsection{Approximation of $\mathbb{E}^{01}\left[\bar{x}_{t_a}\right]$}
-It is easy to show that the dynamic of the bond under HJM assumption is
+It is easy to show that the bond dynamics under the HJM assumption is
 \begin{equation}
@@
 \end{equation}
-Now, if we define $w_i(t)=\frac{\delta_{i-1,i} P(t,t_i)}{01(t,t_a,t_b)}$, then
+We define $w_i(t)=\frac{\delta_{i-1,i} P(t,t_i)}{01(t,t_a,t_b)}$, then
 \begin{equation*}
@@
 \end{equation*}
-Now, from (\ref{annuity_vol}) and since $\frac{P_{ois}(t,T)}{01(t)}$ is a martingale, we have that
+From (\ref{annuity_vol}) and since $\frac{P_{ois}(t,T)}{01(t)}$ is a martingale, we have that
 \begin{equation*}
@@
 \end{equation*}
-Then, if we do a freezing of the weights $w_i(t)$, we get the next approximation of (\ref{annuity_vol})
+Then, if we freeze the weights $w_i(t)$, we get the next approximation of (\ref{annuity_vol})
 \begin{equation*} \label{approximation_o1_vol}
-\bar{\sigma}_{01}(t,t_a,t_b) \approx \sum_{i=a+1}^{b} w_i(0) \nu(t,t_i)
-\end{equation*}
-If we use (\ref{short_rate_cheyette}) and above approximation, we have that
+\bar{\sigma}_{01}(t,t_a,t_b) \approx \sum_{i=a+1}^{b} w_i(0) \nu(t,t_i).
+\end{equation*}
+Using (\ref{short_rate_cheyette}) and above approximation, we obtain that
 \begin{align}
@@
 &=  \bar{x}_0(t)  + \int_{0}^{t_a} \exp\left(-\int_{s}^{t_a}k_u du\right) \bar{y}_u du + \int_{0}^{t_a} \exp\left(-\int_{s}^{t_a}k_u du \right) \eta(u,\bar{x}_u,\bar{y}_u) \bar{\sigma}_{01}(u, t_a, t_b) du  \nonumber \\
-&\hspace{1.2cm} + \int_{0}^{t_a} \exp\left(-\int_{s}^{t_a}k_u du \right) \eta(u,\bar{x}_u,\bar{y}_u) dW_u^{01} 
+&\hspace{1.2cm} + \int_{0}^{t_a} \exp\left(-\int_{s}^{t_a}k_u du \right) \eta(u,\bar{x}_u,\bar{y}_u) dW_u^{01}.
 \end{align}
@@
 \end{equation*}
-Then we have that
+Then, we have that
 \begin{equation}
@@
 $$
-\mu(t,\bar{x}_t, \bar{y}_t, t_a,t_b) =  \sum_{i=a+1}^{b} w_i(t) \partial_x \nu(t,t_i, \bar{x}_t, \bar{y}_t) \frac{G(t,t_i)}{\beta_{t,k}}.
+\mu(t,\bar{x}_t, \bar{y}_t, t_a,t_b) =  \sum_{i=a+1}^{b} w_i(t) \partial_x \nu(t,t_i, \bar{x}_t, \bar{y}_t) \frac{G(t,t_i)}{\beta_{t,k}},
 $$
-and $\frac{\delta_{i-1,i} P(t,t_i)}{01(t,t_a,t_b)}$. Now, from (\ref{approximation_x_t_a}) together with the Girsanov's theorem, we have that
+and $\frac{\delta_{i-1,i} P(t,t_i)}{01(t,t_a,t_b)}$. From (\ref{approximation_x_t_a})  and the Girsanov's theorem, we get that
 \begin{align*}
@@
 \end{align*}
-Then, if we take $D_s$ we get that
+Then, taking $D_s$, we have that
 \begin{equation*}
@@
 \end{align*}
-and $\beta(u,t_a,x,y) = \exp\left(-\int_{u}^{t_a}k_u du\right)\eta(u,x,y)$.
-
+and $\beta(u,t_a,x,y) = \exp\left(-\int_{u}^{t_a}k_u du\right)\eta(u,x,y)$.\\
+Then, 
 \begin{align}\label{approximation_E_01_Ds_x_t}
@@
 \begin{equation}\label{future}
-\hat{L}_{E}(t,t_0, t_1, t_2) = \mathbb{E}_t^{\mathbb{Q}}\left[L_{E}(t_0, t_1, t_2) \right], 
+\hat{L}_{E}(t,t_0, t_1, t_2) = \mathbb{E}_t^{\mathbb{Q}}\left[L_{E}(t_0, t_1, t_2) \right]
 \end{equation}
 where $\mathbb{Q}$ is the measure associated to the numeraire $B_t=\exp\left(\int_{0}^{t} r_{ois, s} ds \right)$ with $ r_{ois, t}$ the risk free short rate. Using
-\eqref{forward_rate} and \eqref{future}, then the convexity adjustment definition is:
+\eqref{forward_rate} and \eqref{future}, then the convexity adjustment definition is
 \begin{equation*}
@@
 \begin{equation*}
-D_s L_{E}(t_0,t_1,t_2) = \frac{H(t_0,t_1)}{\delta_{t_1,t_2}H(t_0,t_2)} D_s \left(\frac{P_{ois}(t_0,t_1)}{P_{ois}(t_0,t_2)}\right) 
-\end{equation*}
-Now from the zero coupon representation formula (\ref{bond_ois}), we get that
+D_s L_{E}(t_0,t_1,t_2) = \frac{H(t_0,t_1)}{\delta_{t_1,t_2}H(t_0,t_2)} D_s \left(\frac{P_{ois}(t_0,t_1)}{P_{ois}(t_0,t_2)}\right).
+\end{equation*}
+Now from the zero-coupon representation formula (\ref{bond_ois}), we get that
 \begin{equation*}
@@
 \begin{equation*}
-D_s I(t_0,t_1) = \int_{\max(s, t_{0})}^{t_1}  D_s x_u du 
+D_s I(t_0,t_1) = \int_{\max(s, t_{0})}^{t_1}  D_s x_u du.
 \end{equation*}
@@
 \end{equation}
-Then, we obtain \eqref{convexity_ois_future}.
+Then, we obtain \eqref{convexity_ois_future}.\\
 
@@
 $L_{E}(t,t_1,t_2)$ is martingale under the measure $\mathbb{Q}^{t_2}$, therefore the expected value of \eqref{FRAinArrear} is taken with respect to the wrong martingale.
-To calculate the convexity adjustment we use the Clark-Ocone to get a representation for $L_{E}(t_1,t_1,t_2)$ i.e
+To calculate the convexity adjustment, we use the Clark-Ocone to get a representation for $L_{E}(t_1,t_1,t_2)$, i.e
 \begin{equation}\label{general_convexity_fras}
-L_{E}(t_1,t_1,t_2) = \mathbb{E}^{t_2}\Bigl[L_{E}(t_1,t_1,t_2) \Bigr] + \int_{0}^{t_1} \mathbb{E}^{t_2}\Bigl[D_s L_{E}(t_1,t_1,t_2) \Bigr] dW^{\mathbb{Q}^{t_2}}_{s}
+L_{E}(t_1,t_1,t_2) = \mathbb{E}^{t_2}\Bigl[L_{E}(t_1,t_1,t_2) \Bigr] + \int_{0}^{t_1} \mathbb{E}^{t_2}\Bigl[D_s L_{E}(t_1,t_1,t_2) \Bigr] dW^{\mathbb{Q}^{t_2}}_{s}.
 \end{equation}
@@
 D_s L(t_1,t_1,t_2) &=& \frac{G(t_1,t_2)}{\delta_{t_1,t_2}P_{E}(t_1,t_2)} D_s x_{t_1}\\
-&\approx& \frac{G(t_1,t_2)}{\delta_{t_1,t_2}P_{E}(0,t_1,t_2)} \beta(s,t_1, \bar{x}_0(t_1), \bar{y}_s)\overline{DM}(s,t_1)
-\end{eqnarray*}
-If we use the above approximation, we get
+&\approx& \frac{G(t_1,t_2)}{\delta_{t_1,t_2}P_{E}(0,t_1,t_2)} \beta(s,t_1, \bar{x}_0(t_1), \bar{y}_s)\overline{DM}(s,t_1).
+\end{eqnarray*}
+Using the above approximation, we get
 \begin{equation*}
@@
 $S_{a,b}(t_a)$ is a martingale under the measure $\mathbb{Q}^{01}$, but not under the measure $\mathbb{Q}^{t_p}$.
-Therefore, we take into consideration the effect to compute the expected value of $S_{a,b}(t_a)$ in a measure which is not its natural measure.
+Therefore, we take into consideration the effect to compute the expected value of $S_{a,b}(t_a)$ in a measure that is not its natural measure.
 Then, the convexity adjustment for a CMS is
@@
 
-From the previous expression, we must note that under assumption of not stochastic basis, we must to compute the convexity adjustment for the OIS swap rate.
-But a complicated point is calculate the expected value
+From the previous expression, we must note that under the assumption that there are not stochastic basis, we must compute the convexity adjustment for the OIS swap rate.
+But a complicated point is calculating the expected value
 \begin{equation}\label{Exp_M_conditional}
@@
 \end{equation}
-In order to reduce this complexity, it is a common practice to assume that $M(t_a,t_p)$ is a function of the swap rate $S_{a,b}(t_a)$, i.e   $M(t_a,t_p)=f(S_{a,b}(t_a))$.
+To reduce this complexity, it is a common practice to assume that $M(t_a,t_p)$ is a function of the swap rate $S_{a,b}(t_a)$, i.e   $M(t_a,t_p)=f(S_{a,b}(t_a))$.
 Under this assumption (\ref{Exp_M_conditional}) is trivial to calculate it.
-The function $f(\cdot)$ is known as mapping function.
+The function $f(\cdot)$ is known as the mapping function.
 There is a vast literature about how to choose it (see \cite{AndreasenPiterbargIII} or \cite{Hagan20}).
@@
 \begin{equation} \label{clark_ocone_swap_m}
-M(t_a,t_p) = M(0,t_p)+ \int_{0}^{t_a} \mathbb{E}_s^{01}\Bigl[D_s M(t_a,t_p)\Bigr] dW^{01}_s
-\end{equation}
-Then, if we substitute the last expressions in (\ref{expected_t_p_cms}) we have that
+M(t_a,t_p) = M(0,t_p)+ \int_{0}^{t_a} \mathbb{E}_s^{01}\Bigl[D_s M(t_a,t_p)\Bigr] dW^{01}_s.
+\end{equation}
+Then, if we substitute the last expressions in (\ref{expected_t_p_cms}), we obtain that
 \begin{align}\label{cms_first_order_convexity_prev}
 \mathbb{E}^{t_p}\left(S_{a,b}(t_a)\right) =& S^{ois}_{a,b}(0) + \frac{1}{M(0,t_p)} \mathbb{E}^{01}\left[ S^{ois}_{a,b}(t_a) \int_{0}^{t_a} \mathbb{E}^{0,1}_s\Bigl[D_s x_{t_a}\partial_x M(t_a,t_p)  \Bigr] dW^{0,1}_s   \right] \nonumber \\
-=&  S^{ois}_{a,b}(0) + \frac{1}{M(0,t_p)} \mathbb{E}^{01}\left[\int_{0}^{t_a} D_s x_{t_a} \partial_x S_{a,b}(t_a) \mathbb{E}^{0,1}_s\Bigl[D_s x_{t_a}\partial_x M(t_a,t_p)  \Bigr] ds   \right]
+=&  S^{ois}_{a,b}(0) + \frac{1}{M(0,t_p)} \mathbb{E}^{01}\left[\int_{0}^{t_a} D_s x_{t_a} \partial_x S_{a,b}(t_a) \mathbb{E}^{0,1}_s\Bigl[D_s x_{t_a}\partial_x M(t_a,t_p)  \Bigr] ds   \right].
 \end{align}

### 2023-04-16 Latex/paper-resum.tex
Stylish V

@@
 The advantage of using the Malliavin calculus is that it allows us to derive a general representation formula for the convexity adjustment.
-Furthermore, as we will see later, it is possible to obtain closed formulas for the convexity adjustment when the volatility of the Cheyette model is time dependent.
+Furthermore, as we will see later, it is possible to obtain closed formulas for the convexity adjustment when the volatility of the Cheyette model is time-dependent.
 
@@
 \begin{remark}
-We must note that (\ref{convexity_ois_future}) and (\ref{convexity_avg_ois_future}) are exact when $\eta(t,x_t, y_t)$ is only a time dependent function, how is the case of a Hull-White model.
+We must note that (\ref{convexity_ois_future}) and (\ref{convexity_avg_ois_future}) are exact when $\eta(t,x_t, y_t)$ is only a time-dependent function, how is the case of a Hull-White model.
 \end{remark}

### 2023-04-18 Latex/paper-resum.tex
Stylish (Josep)

@@
 \begin{abstract}
-In this paper, we develop a novel method based on the Malliavin calculus to find an approximation for the convexity adjustment for various classical interest rate products.
+In this paper, we develop a novel method based on Malliavin calculus to find an approximation for the convexity adjustment for various classical interest rate products.
 Malliavin calculus provides a simple way to get a template for the convexity adjustment.
@@
 \section{Basic introduction to Malliavin calculus}\label{sec:Malliavin}
-Malliavin calculus is an infinite-dimensional calculus in a Gaussian space, that is, a stochastic calculus of variations.
+Malliavin calculus is an infinite-dimensional calculus in a Gaussian space.
 In other words, this is a theory that provides a way to calculate the derivatives of random variables defined in a Gaussian probability space with respect to the underlying noise.
@@
 Some of these applications include stochastic calculus for fractional Brownian motion, central limit theorems for multiple stochastic integrals, and an extension of the Itô formula for anticipative processes, but especially mathematical finance.
-For example, we can apply Mallaivin calculus for computing hedging strategies, Greeks, or obtain price approximations.
+For example, we can apply Malliavin calculus for computing hedging strategies, Greeks, or obtain price approximations.
 See, for example, \cite{AlosLorite} or \cite{Nualart} for more general content.\\
@@
 
-Consider $W=\left\{W_{t}, t\in \left[0,T\right]\right\}$ a Brownian motion defined on a complete probability space $\left(\Omega, \mathcal{F}, \mathbb{P}\right)$.
+Consider $W=\left\{W_{t}, t\in \left[0,T\right]\right\}$ a Brownian motion defined on a complete probability space $\left(\Omega, \mathcal{F}, \mathbb{P}\right)$ such that  $\mathcal{F}$ is generated by $W$, equipped with its Brownian filtration $(\mathcal{F}_{t})_{t\geq0}$.
 Let $H=L^{2}(\left[0,T\right])$ and denote by
 \begin{eqnarray*}
-W_{t} := \int^{T}_{0} t_{s} \d W_{s},
+W(t) := \int^{T}_{0} h(s) \d W_{s},
 \end{eqnarray*}
@@
 \begin{eqnarray*}
-F=f\left(W_{t_{1}}, \ldots, W{t_{n}}\right)
-\end{eqnarray*}
-with $t_{1}, \ldots, t_{n} \in \left[0,T\right]$ and $f$ is infinitely differentiable bounded function.
+F=f\left(W(t_{1}), \ldots, W(t_{n})\right)
+\end{eqnarray*}
+with $t_{1}, \ldots, t_{n} \in \left[0,T\right]$ and $f$ is a infinitely differentiable bounded function.
 
@@
 \begin{eqnarray*}
-D_{s}F = \sum^{n}_{i=1} \frac{\partial f}{\partial x_{i}}\left(W_{t_{1}}, \ldots, W_{t_{n}}\right)1_{\left[0, t_{j}\right]}(s), \hspace{0.4cm} s \in \left[0,T\right].
-\end{eqnarray*}
-
-The iterated derivative operator of a random variable $F$ is defined by
-\begin{eqnarray*}
-D^{m}_{s_{1}, \ldots, s_{m}} F = D_{s_{1}} \cdots D_{s_{m}}F, \hspace{0.4cm} s_{1}, \ldots, s_{m} \in \left[0,T\right].
-\end{eqnarray*}
+D_{s}F = \sum^{n}_{i=1} \frac{\partial f}{\partial x_{i}}\left(W(t_{1}), \ldots, W(t_{n})\right)1_{\left[0, t_{j}\right]}(s), \hspace{0.4cm} s \in \left[0,T\right].
+\end{eqnarray*}
+
+%The iterated derivative operator of a random variable $F$ is defined by
+%\begin{eqnarray*}
+%D^{m}_{s_{1}, \ldots, s_{m}} F = D_{s_{1}} \cdots D_{s_{m}}F, \hspace{0.4cm} s_{1}, \ldots, s_{m} \in \left[0,T\right].
+%\end{eqnarray*}
 
@@
 \begin{eqnarray*}
-E\left[\delta(u) F \right] = E\left[\int^{T}_{0} \left(D_{s} F\right) u_{s} \d s\right].
+E\left[\delta(u) F \right] = E\left[\int^{T}_{0} D_{s} F u_{s} \d s\right].
 \end{eqnarray*}
@@
 The representation of functionals of Brownian motion by stochastic integrals, also known as martingale representation, has been widely studied over the years.
-It states that if $F$ is a square-integrable random variable, there exists a unique adapted process $\varphi$ in $L^{2}(\Omega \times \left[0,T\right]; \mathbb{R}^{d})$ such that
-\begin{eqnarray*}
-F=E\left[F\right] + \sum^{n}_{i=1}\int^{T}_{0} \varphi^{i}_{s} dW^{i}_{s}.
-\end{eqnarray*}
-In other words, there exists a unique martingale representation or, more precisely, the integrand $\varphi$ in the representation exists and is unique in $L^{2}(\Omega \times \left[0,T\right]; \mathbb{R}^{d})$.
+It states that if $F$ is a square-integrable random variable, there exists a unique adapted process $\varphi$ in $L^{2}(\Omega \times \left[0,T\right]; \mathbb{R})$ such that
+\begin{eqnarray*}
+F=E\left[F\right] +\int^{T}_{0} \varphi^{i}_{s} dW^{i}_{s}.
+\end{eqnarray*}
+In other words, there exists a unique martingale representation or, more precisely, the integrand $\varphi$ in the representation exists and is unique in $L^{2}(\Omega \times \left[0,T\right]; \mathbb{R})$.
 
@@
 \begin{eqnarray*}
-\varphi^{i}=E\left[D^{W^{i}}_{t}F|\mathcal{F}^{W}_{s}\right].
+\varphi^{i}=E\left[D^{W}_{s}F|\mathcal{F}_{s}\right].
 \end{eqnarray*}
@@
 \begin{eqnarray}\label{clark-okone}
-F=E\left[F\right] + \sum^{n}_{i=1}\int^{T}_{0} E\left[D^{W^{i}}_{t}F|\mathcal{F}^{W}_{s}\right] dW^{i}_{s}
+F=E\left[F\right] + \int^{T}_{0} E\left[D^{W}_{s}F|\mathcal{F}_{s}\right] dW_{s}
 \end{eqnarray}
@@
 We will assume that the $f_{ois}$ dynamics follows a single factor Heath-Jarrow-Morton (HJM) model under the $\mathbb{Q}$-measure.
-Therefore, let $T>0$ a fixed time horizon, $t>0$ the starting time, and $W$ a Brownian motion defined on a complete probability space $(\omega, \mathcal{F}, \mathbb{P})$.
+Therefore, let $T>0$ a fixed time horizon, $t>0$ the starting time, and $W$ a Brownian motion defined on a complete probability space $(\Omega, \mathcal{F}, \mathbb{P})$.
 Then, the HJM model is defined by
@@
 \begin{equation}\label{separation_condition}
-\sigma(t,T)= h(t)g(T).
-\end{equation}
-with $g$ a positive time-dependent function and $h$ a non-negative process. In addition,
+\sigma(t,T)= h(t)g(T)
+\end{equation}
+with $g$ a positive time-dependent function and $h$ a non-negative process. This version of the HJM is also known as the Cheyette model, \cite{Cheyette}.\\
+
+In particular, following \cite{AndreasenPiterbarg}, we will define
 \begin{align*}
@@
 \end{align*}
-
-This version of the HJM is also known as the Cheyette model, \cite{Cheyette}. In \cite{AndreasenPiterbarg}, we have the following proposition.
+Then, we have the following proposition.
 \begin{proposition}
@@
 \begin{equation*}
-x(t_a) = \int_{0}^{t_a} \exp\left(-\int_{s}^{t_a}k(u) du\right) y(u) du + \int_{0}^{t_a}  \exp\left(-\int_{s}^{t_a}k(u) du \right) \eta(u,x(u),y(u)) dW_u^{\mathbb{Q}}. 
+x(t_a) = \int_{0}^{t_a} \exp\left(-\int_{u}^{t_a}k(w) dw\right) y(u) du + \int_{0}^{t_a}  \exp\left(-\int_{s}^{t_a}k(u) du \right) \eta(u,x(u),y(u)) dW_u^{\mathbb{Q}}. 
 \end{equation*}
@@
 \begin{eqnarray}
-\bar{x}_{t_a}:= \bar{x}_0(t_a)&+&\int_{0}^{t_a} \exp\left(-\int_{s}^{t_a}k(u) du\right) \bar{y}_u du \nonumber \\
-&+& \int_{0}^{t_a}  \exp\left(-\int_{s}^{t_a}k(u) du \right) \eta(u,\bar{x}(u),\bar{y}_u) dW_u^{\mathbb{Q}}   \label{approximation_x_t_a}
+\bar{x}_{t_a}:= \bar{x}_0(t_a)&+&\int_{0}^{t_a} \exp\left(-\int_{u}^{t_a}k(w) dw\right) \bar{y}_u du \nonumber \\
+&+& \int_{0}^{t_a}  \exp\left(-\int_{u}^{t_a}k(w) dw \right) \eta(u,\bar{x}(u),\bar{y}_u) dW_u^{\mathbb{Q}}   \label{approximation_x_t_a}
 \end{eqnarray}
 with initial condition $\bar{x}_{0}(t_a)$ will be chosen appropriately depending on the case.
-In the appendix \ref{estimation_error_l2} we can find the estimation for $\mathbb{E}((x_t-\bar{x}_t)^{2})$ and the approximation order.
+In the appendix \ref{estimation_error_l2} we can find the estimation for $\mathbb{E}\left[(x_t-\bar{x}_t)^{2}\right]$ and the approximation order.
 
@@
 Let us define the process $Z_t = f(x_t)$.
-Suppose that $Z_t$ is a martingale under the measure $\mathbb{Q}_1$.
+Suppose that $Z_t$ is a martingale under a measure $\mathbb{Q}_1$.
 However, we are interested in calculate $\mathbb{E}^{\mathbb{Q}_2}\left[Z_T \right]$ where $\mathbb{Q}_2$ is a measure under which $Z_t$ is not martingale and such that $dW^{\mathbb{Q}_1}_t = dW^{\mathbb{Q}_2}_t +\lambda_t dt$.
@@
 \begin{equation}\label{general_convexity}
-\mathbb{E}^{\mathbb{Q}_2}\left[ f(x_t) \right] = f(x_0) + \mathbb{E}^{\mathbb{Q}_1} \left[\int_{0}^{t}  \mathbb{E}^{\mathbb{Q}_1}_s\left[ f^{\prime}(x_t) D_s x_t  \right] \lambda_s ds \right]. 
+\mathbb{E}^{\mathbb{Q}_2}\left[ f(x_t) \right] = f(x_0) + \mathbb{E}^{\mathbb{Q}_2} \left[\int_{0}^{t}  \mathbb{E}^{\mathbb{Q}_1}_s\left[ f^{\prime}(x_t) D_s x_t  \right] \lambda_s ds \right]. 
 \end{equation}
@@
 \begin{theorem}\label{Th_CA_futures}[Convexity Adjustment approximation for Futures]
-Given the Cheyette model in \eqref{short_rate_cheyette}, the hypothesis \ref{boundedness_volatility} and \ref{boundedness_reversion}, and considering the approximations in \eqref{approximation_y_t} and \eqref{approximation_x_t_a}.
+Given the Cheyette model in \eqref{short_rate_cheyette}, the hypotheses \ref{boundedness_volatility} and \ref{boundedness_reversion}, and considering the approximations in \eqref{approximation_y_t} and \eqref{approximation_x_t_a}.
 Then, the convexity adjustment approximation for futures is
 \begin{equation}\label{ca_approximation_futures}
-CA(t,t_0,t_1) = \frac{P_{E}(0,t_1)}{\delta_{t_1,t_2} P_{E}(0,t_2)} \left(G(t_0,t_2)  - G(t_0,t_1) \right) \int_{0}^{t_0} \beta(s,t_0,\bar{x}_0(t_0),\bar{y}_s) \nu(s,t_2) ds + E(t_0). 
+CA(t,t_0,t_1) = \frac{P_{E}(0,t_1)}{\delta_{t_1,t_2} P_{E}(0,t_2)} \biggl(G(t_0,t_2)  - G(t_0,t_1) \biggr) \int_{0}^{t_0} \beta(s,t_0,\bar{x}_0(t_0),\bar{y}_s) \nu(s,t_2) ds + E(t_0). 
 \end{equation}
@@
 \begin{equation*}
-\beta(t,t_0,x,y) = \exp\left(-\int_{s}^{t_0}k_u du \right) \eta(u,x,y).
+\beta(t,t_0,x,y) = \exp\left(-\int_{u}^{t_0}k(w) dw \right) \eta(u,x,y).
 \end{equation*}
@@
 	\end{center}
-	\caption{Convexity Mc Vs Convexity Malliavin}
+	\caption{MonteCarlo Simulation vs Malliavin}
 	\label{fig:Futures}
@@
 \begin{equation*}
-R(t_0,t_1) :=\frac{1}{\delta_{t_0,t_1}} \left(\exp\left(\int_{t_0}^{t_1}r_{ois,u} du \right) - 1\right)
+R(t_0,t_1) :=\frac{1}{\delta_{t_0,t_1}} \left(\exp\left(\int_{t_0}^{t_1}r_{ois}(u) du \right) - 1\right)
 \end{equation*}
@@
 \begin{equation*}
-R_{avg}(t_0,t_1) := \frac{1}{\delta_{t_0,t_1}}\int_{t_0}^{t_1}r_{ois,u} du.
+R_{avg}(t_0,t_1) := \frac{1}{\delta_{t_0,t_1}}\int_{t_0}^{t_1}r_{ois}(u) du.
 \end{equation*}
@@
 Before continuing, we will do several observations.
-The first observation is that if we define $F(t,t_0,t_1) = \mathbb{E}^{\mathbb{Q}^{t_1}}\left( R(t_0,t_1)\right)$, then we have that when $t \in [0,t_0]$
-\begin{align*}
-F(t,t_0,t_1)&= \frac{1}{P_{ois}(t,t_1)}  \mathbb{E}_{t}^{\mathbb{Q}}\left[\exp\left(-\int_{t}^{t_1} r_{ois,u} du \right) R(t_0,t_1) \right]\\
+The first observation is that if we define $F(t,t_0,t_1) = \mathbb{E}^{\mathbb{Q}^{t_1}}\left[ R(t_0,t_1)\right]$, then we have that when $t \in [0,t_0]$
+\begin{align*}
+F(t,t_0,t_1)&= \frac{1}{P_{ois}(t,t_1)}  \mathbb{E}_{t}^{\mathbb{Q}}\left[\exp\left(-\int_{t}^{t_1} r_{ois}(u) du \right) R(t_0,t_1) \right]\\
 &= \frac{1}{\delta_{t_0,t_1}}\left(\frac{P_{ois}(t,t_0)}{P_{ois}(t,t_1)} - 1\right), %, \quad t \in [0,t_0] \\
@@
 %\begin{align*}
-F(t,t_0,t_1)&= \frac{1}{P_{ois}(t,t_1)} \mathbb{E}_{t}^{\mathbb{Q}}\left[\exp\left(-\int_{t}^{t_1} r_{ois,u} du \right) R(t_0,t_1) \right]\\
- &= \frac{1}{\delta_{t_0,t_1}} \left(\frac{\exp\left(\int_{t}^{t_1}r_{ois,u} du\right)}{P_{ois}(t_0,t)}-1\right).%, \quad  t \in  [t_0, t_1].
-\end{align*}
-Then the convexity adjustment for $ R(t_0,t_1)$ is
+F(t,t_0,t_1)&= \frac{1}{P_{ois}(t,t_1)} \mathbb{E}_{t}^{\mathbb{Q}}\left[\exp\left(-\int_{t}^{t_1} r_{ois}(u) du \right) R(t_0,t_1) \right]\\
+ &= \frac{1}{\delta_{t_0,t_1}} \left(\frac{\exp\left(\int_{t}^{t_1}r_{ois}(u) du\right)}{P_{ois}(t_0,t)}-1\right).%, \quad  t \in  [t_0, t_1].
+\end{align*}
+Then, the convexity adjustment for $ R(t_0,t_1)$ is
 \begin{equation}\label{R_ois_ca}
@@
 \mathbb{E}^{\mathbb{Q}}\left(R_{avg}(t_0,t_1) \right) =\frac{1}{\delta_{t_0,t_1}} \mathbb{E}^{\mathbb{Q}}\left[ \log\left(1+ \delta_{t_0,t_1} R(t_0,t_1) \right) \right]  \end{equation}
-To clarify the convexity expression and the calculations, we will define 
+To clarify the convexity expression and the calculations, we define 
 \begin{equation*}
@@
 \begin{theorem}\label{Th_CA_OIS}[Convexity Adjustment approximation for OIS Futures]
-Given the Cheyette model in \eqref{short_rate_cheyette}, the hypothesis \ref{boundedness_volatility} and \ref{boundedness_reversion}, and considering the approximations in \eqref{approximation_y_t} and \eqref{approximation_x_t_a}.
+Given the Cheyette model in \eqref{short_rate_cheyette}, the hypotheses \ref{boundedness_volatility} and \ref{boundedness_reversion}, and considering the approximations in \eqref{approximation_y_t} and \eqref{approximation_x_t_a}.
 Then, the convexity adjustment approximation for OIS futures is
@@
 \begin{equation}\label{convexity_avg_ois_future}
-\bar{R}_{avg}(t_0,t_1) = \frac{\mathbb{E}_t^{\mathbb{Q}}\left[I(t_0,t_1)\right] }{\delta_{t_0,t_1}} \approx \frac{1}{\delta_{t_0,t_1}}\left(\log\left(1+\delta_{t_0,t_1}  \mathbb{E}_t^{\mathbb{Q}}\left[R(t_0,t_1)\right] \right) - \frac{1}{2}\int_{0}^{t_1}  \Gamma^{2}(s,t_0,t_1) ds\right)
+\bar{R}_{avg}(t_0,t_1) = \frac{\mathbb{E}_t^{\mathbb{Q}}\left[I(t_0,t_1)\right] }{\delta_{t_0,t_1}} \approx \frac{1}{\delta_{t_0,t_1}}\left(\log\left(1+\delta_{t_0,t_1}  \mathbb{E}_t^{\mathbb{Q}}\left[R(t_0,t_1)\right] \right) - \frac{1}{2}\int_{0}^{t_1}  \Gamma^{2}(s,t_0,t_1) ds\right),
 \end{equation}
@@
 \begin{remark}
-We must note that (\ref{convexity_ois_future}) and (\ref{convexity_avg_ois_future}) are exact when $\eta(t,x_t, y_t)$ is only a time-dependent function, how is the case of a Hull-White model.
+We must note that (\ref{convexity_ois_future}) and (\ref{convexity_avg_ois_future}) are exact when $\eta(t,x_t, y_t)$ is only a time-dependent function, as in the case of the Hull-White model.
 \end{remark}
@@
 \begin{align*}
-I(t,t_1)&:=\int_{t}^{t_1} r_s ds,\\
-R(t_0,t_1) &:= \frac{1}{\delta_{t_0,t_1}}\left(\frac{\exp\left(\int_{t}^{t_1} r_{ois,s} ds\right)}{P_{ois}(t_0,t)} - 1\right), \\
+I(t,t_1)&:=\int_{t}^{t_1} r_{ois}(s) ds,\\
+R(t_0,t_1) &:= \frac{1}{\delta_{t_0,t_1}}\left(\frac{\exp\left(\int_{t}^{t_1} r_{ois}(s) ds\right)}{P_{ois}(t_0,t)} - 1\right), \\
 \intertext{and}
-R_{avg}(t_0,t_1) &:= \frac{1}{\delta_{t_0,t_1}}\left(\int_{t_0}^{t} r_{ois,s} ds + \int_{t}^{t_1} r_{ois,s} ds\right).   
+R_{avg}(t_0,t_1) &:= \frac{1}{\delta_{t_0,t_1}}\left(\int_{t_0}^{t} r_{ois}(s) ds + \int_{t}^{t_1} r_{ois}(s) ds\right).   
 \end{align*}
@@
 \begin{theorem}\label{Th_CA_FRAsinArrears}[Convexity Adjustment approximation for FRAs in Arrears]
-Given the Cheyette model in \eqref{short_rate_cheyette}, the hypothesis \ref{boundedness_volatility} and \ref{boundedness_reversion}, and considering the approximations in \eqref{approximation_y_t} and \eqref{approximation_x_t_a}.
+Given the Cheyette model in \eqref{short_rate_cheyette}, the hypotheses \ref{boundedness_volatility} and \ref{boundedness_reversion}, and considering the approximations in \eqref{approximation_y_t} and \eqref{approximation_x_t_a}.
 Then, the convexity adjustment approximation for FRAs in Arrears is
@@
 \begin{theorem}\label{Th_CA_CMS}[Convexity Adjustment approximation for CMS]
-Given the Cheyette model in \eqref{short_rate_cheyette}, the hypothesis \ref{boundedness_volatility} and \ref{boundedness_reversion}, and considering the approximations in \eqref{approximation_y_t} and \eqref{approximation_x_t_a}.
+Given the Cheyette model in \eqref{short_rate_cheyette}, the hypotheses \ref{boundedness_volatility} and \ref{boundedness_reversion}, and considering the approximations in \eqref{approximation_y_t} and \eqref{approximation_x_t_a}.
 Given
@@
 \begin{lemma}\label{DsX}[Approximation $D_s \bar{x}_{t_a}$]
-Given the Cheyette model in \eqref{short_rate_cheyette}, the hypothesis \ref{boundedness_volatility} and \ref{boundedness_reversion}, and considering the approximations in \eqref{approximation_y_t} and \eqref{approximation_x_t_a}.
+Given the Cheyette model in \eqref{short_rate_cheyette}, the hypotheses \ref{boundedness_volatility} and \ref{boundedness_reversion}, and considering the approximations in \eqref{approximation_y_t} and \eqref{approximation_x_t_a}.
 Then,

### 2023-04-19 ConvexityAdjustment-Lib/ConvexityAdjustment-Lib/HullWhite/HullWhite.cs
# remove some lines of code and include parenthesis

@@ -126,22 +126,7 @@ namespace ConvexityAdjustment_Lib.HullWhite
             return logR01 - (i1 + i2) / (t2 - t1);
         }
 
-        public static double convexityCms(ql.Handle<ql.YieldTermStructure> discountCurve,  ql.Date valueDate, ql.Date ta, ql.Date tb, ql.Date tp, double annuity,
-            double partialAnnuity, double partialVanillaSwap, double partialOisSwap, double partialOisSwapT0 , ql.DayCounter dc, double k, double sigma)
-        {
-            var dta = dc.yearFraction(valueDate, ta);
-            var dtp = dc.yearFraction(valueDate, tp);
-            
-            var dFtp = discountCurve.link.discount(tp);
-            var dFta = discountCurve.link.discount(ta);
-            var m = - dFtp  * (beta(dta, dtp, k) + partialAnnuity / annuity);
-
-            var alpha = sigma * sigma * beta(0.0, dta, 2.0 * k);
-            return m * alpha * partialVanillaSwap;
-
-        }
-
-        public static double convexityCmsNewApproach(ql.HullWhite model,
+        public static double convexityCms(ql.HullWhite model,
             ql.Date valueDate,
             ql.Date ta,
             ql.Date tb,

### 2023-04-19 ConvexityAdjustment-Lib/ConvexityAdjustmentUnitTests/CmsConvexity.cs

@@ -72,8 +72,6 @@ namespace ConvexityAdjustmentUnitTests
             var std = new List<double>();
             var momentOrderTwo = new Dictionary<int, double>();
             var rateCmsForward = new List<double>();
-            // var annuityTa = new List<Tuple<double, double, double>>();
-            // var annuityT0 = new List<Tuple<double, double, double>>();
             
             // swap derivatives, rates ans ratio
             var partialOisSwap = new List<double>();
@@ -100,13 +98,6 @@ namespace ConvexityAdjustmentUnitTests
                     .withFloatingLegRule(ql.DateGeneration.Rule.Forward)
                     .value();
                 
-           
-                // annuityTa.Add(model.GetAnnuity(startDate, datesToCompute[j], f0ts[j], staticSwap.fixedSchedule(),
-                //     discountCurve.link.dayCounter(), staticSwap.fixedDayCount()));
-                //
-                // annuityT0.Add(model.GetAnnuity(startDate, startDate, f0ts[j], staticSwap.fixedSchedule(),
-                //     discountCurve.link.dayCounter(), staticSwap.fixedDayCount()));
-
                 var swapOisDerivative = model.GetPartialDerivativeSwapRate(startDate, startDate, f0ts[j],
                     staticSwap.floatingSchedule(), staticSwap.fixedSchedule(), discountCurve.link.dayCounter(),  staticSwap.floatingDayCount(),
                     staticSwap.fixedDayCount());
@@ -185,8 +176,6 @@ namespace ConvexityAdjustmentUnitTests
                 // variables to check od the simulation
                 var dfMC = -0.5;
                 var meanI0t = 0.0;
-                // var varNoise = 0.0;
-                // var meanNoise = 0.0;
 
                 var ratioDf = 1.0 / discountCurve.link.discount(tP);
                 
@@ -227,18 +216,15 @@ namespace ConvexityAdjustmentUnitTests
                     double annuity = Math.Abs(swap.fixedLegNPV());
                     double mTa = pTaTp / annuity;
                     
-                    // double payoffMc =  ratioDf * swapRate * pTaTp / bt;
                     double payoffMc =  ratioDf * pTaTp * swapRate / bt;
 
                     rateCmsMc[datesToCompute[j].serialNumber()] += payoffMc / numberOfSimulations;
                     momentOrderTwo[datesToCompute[j].serialNumber()] += (payoffMc * payoffMc / numberOfSimulations);
[…]

### 2023-04-19 ConvexityAdjustment-Lib/ConvexityAdjustmentUnitTests/FraVsFuturesTests.cs

@@ -33,9 +33,6 @@ namespace ConvexityAdjustmentUnitTests
             // MC
             int numberOfSimulations = 2000000;
             ulong seed = 123545;
-            // double deltaTime = 0.01;
-            // int timeSteps = (int)(length / deltaTime);
-            int timeSteps = 1;
             var numberOfMonths = 240;
 
             List<double> t0s = new List<double>();
@@ -56,18 +53,6 @@ namespace ConvexityAdjustmentUnitTests
 
                 var libors = Sampling.getLiborPaths(model, t0, t1, t2, dc, seed, numberOfSimulations);
                 
-                // List<double> mandatoryPoints = new List<double> { delta00};
-                // double length = dc.yearFraction(startDate, t2);
-                
-                // var rsg = (ql.InverseCumulativeRsg<ql.RandomSequenceGenerator<ql.MersenneTwisterUniformRng>, 
-                //         ql.InverseCumulativeNormal>)
-                //     new ql.PseudoRandom().make_sequence_generator(timeSteps, seed);
-
-                // ql.PathGenerator<ql.IRNG> generator = new ql.PathGenerator<ql.IRNG>(process, length, timeSteps, rsg, true, mandatoryPoints);
-                // double f0t = curve.currentLink().forwardRate(delta00, delta00, ql.Compounding.Simple, ql.Frequency.NoFrequency).rate();
-                // double expat = (1.0 - Math.Exp(-k * delta00)) / k ;
-                // double mt = (sigma * sigma) / (2.0 * k) * (expat - Math.Exp(-k * delta00) * expat); 
-                
                 // Path generator
                 var mean = 0.0;
                 // var meanXt0 = 0.0;
@@ -76,15 +61,7 @@ namespace ConvexityAdjustmentUnitTests
                 
                 for (var i = 0; i < numberOfSimulations; i++)
                 {
-                    // ql.Sample<ql.IPath> sample = generator.next();
-                    // var path = (ql.Path)sample.value;
-                    // var rt0 = path[path.length() - 1] + mt + f0t;
-                    // var df01 = model.discountBond(delta00, delta01, rt0) * Math.Exp(- spreadBasis * (delta01 - delta00));
-                    // var df02 = model.discountBond(delta00, delta02, rt0) *  Math.Exp(- spreadBasis * (delta02 - delta00));
-                    // var libor = ((df01 / df02) - 1.0) / (delta02 - delta01);
                     mean += (libors[i] / numberOfSimulations);
[…]

### 2023-04-19 ConvexityAdjustment-Lib/ConvexityAdjustmentUnitTests/SofrCovexity.cs

@@ -77,8 +77,6 @@ namespace ConvexityAdjustmentUnitTests
                 var dfTb = curve.link.discount(delta02);
                 var forward = ((dfTa / dfTb) - 1.0) / (delta02 - delta01);
                 
-                // var forward =  curve.currentLink().
-                //     forwardRate(delta01, delta02, ql.Compounding.Compounded).rate();
 
                 var convexityMc = mcFuturePrice - forward;
                 var convexityAvgMc = avgMean - forward;

### 2023-04-19 Latex/paper-resum.tex
# remove some lines of code and include parenthesis
Stylish (Josep II)

@@
 \begin{equation*}
-x(t_a) = \int_{0}^{t_a} \exp\left(-\int_{u}^{t_a}k(w) dw\right) y(u) du + \int_{0}^{t_a}  \exp\left(-\int_{s}^{t_a}k(u) du \right) \eta(u,x(u),y(u)) dW_u^{\mathbb{Q}}. 
+x(t_a) = \int_{0}^{t_a} \exp\left(-\int_{u}^{t_a}k(w) dw\right) y(u) du + \int_{0}^{t_a}  \exp\left(-\int_{u}^{t_a}k(w) dw \right) \eta(u,x(u),y(u)) dW_u^{\mathbb{Q}}. 
 \end{equation*}
@@
 \begin{equation}\label{ca_approximation_futures}
-CA(t,t_0,t_1) = \frac{P_{E}(0,t_1)}{\delta_{t_1,t_2} P_{E}(0,t_2)} \biggl(G(t_0,t_2)  - G(t_0,t_1) \biggr) \int_{0}^{t_0} \beta(s,t_0,\bar{x}_0(t_0),\bar{y}_s) \nu(s,t_2) ds + E(t_0). 
+CA(t,t_0,t_1) = \frac{P_{E}(0,t_1)}{\delta_{t_1,t_2} P_{E}(0,t_2)} \biggl(G(t_0,t_2)  - G(t_0,t_1) \biggr) \int_{0}^{t_0} \beta(s,t_0,\bar{x}_0(t_0),\bar{y}_s) \nu(s,t_2) ds + E(t_0)
 \end{equation}
@@
 \begin{equation*}
-\beta(t,t_0,x,y) = \exp\left(-\int_{u}^{t_0}k(w) dw \right) \eta(u,x,y).
-\end{equation*}
-and $\|E\left(t_0\right)\|^{2}_{2} \sim \mathcal{O}(t_0)$ when $t_0 \to 0$ and $\|E\left(t_0\right)\|^{2}_{2} < \infty$ when $t_0 \to \infty$. 
+\beta(u,t_0,x,y) = \exp\left(-\int_{u}^{t_0}k(w) dw \right) \eta(u,x,y).
+\end{equation*}
+The error in the approximation model behaves as $\|E\left(t_0\right)\|^{2}_{2} \sim \mathcal{O}(t_0)$ when $t_0 \to 0$ and $\|E\left(t_0\right)\|^{2}_{2} < \infty$ when $t_0 \to \infty$. 
 \end{theorem}
@@
 	\end{center}
-	\caption{MonteCarlo Simulation vs Malliavin}
+	\caption{Futures: MonteCarlo Simulation vs Malliavin}
 	\label{fig:Futures}
@@
 \begin{equation}\label{R_ois_avg}
-\mathbb{E}^{\mathbb{Q}}\left(R_{avg}(t_0,t_1) \right) =\frac{1}{\delta_{t_0,t_1}} \mathbb{E}^{\mathbb{Q}}\left[ \log\left(1+ \delta_{t_0,t_1} R(t_0,t_1) \right) \right]  \end{equation}
+\mathbb{E}^{\mathbb{Q}}\left[R_{avg}(t_0,t_1) \right] =\frac{1}{\delta_{t_0,t_1}} \mathbb{E}^{\mathbb{Q}}\left[ \log\left(1+ \delta_{t_0,t_1} R(t_0,t_1) \right) \right]  \end{equation}
 To clarify the convexity expression and the calculations, we define 
 \begin{equation*}
-I(t_0,t_1) := \int_{t_0}^{t_1} r_{ois,s} ds.
+I(t_0,t_1) := \int_{t_0}^{t_1} r_{ois}(s) ds.
 \end{equation*}
@@
 \begin{equation}
-\Gamma(s,t_0,t_1)= \eta(s,x_0,y_0)\int_{\max(s, t_{0})}^{t_1} \exp\left( -\int_{s}^{u} k_{s^{\prime}} ds^{\prime}\right)du, 
-\end{equation}
-and $\|E(t_0)\|^{2}_{2} \sim \mathcal{O}(t_0)$ when $t_0 \to 0$ and $\|E(t_0)\|^{2}_{2} < \infty$ when $t_0 \to \infty$.
+\Gamma(s,t_0,t_1)= \eta(s,x_0,y_0)\int_{\max(s, t_{0})}^{t_1} \exp\left( -\int_{s}^{u} k(w) dw\right)du.
+\end{equation}
+The error in the approximation model behaves as $\|E(t_0)\|^{2}_{2} \sim \mathcal{O}(t_0)$ when $t_0 \to 0$ and $\|E(t_0)\|^{2}_{2} < \infty$ when $t_0 \to \infty$.
 \end{theorem}
@@
 \end{align*}
-Then, if we substitute the last equalities in (\ref{convexity_ois_future}) we get an approximation for OIS future at $t=0$.\\
+Then, if we substitute the last equalities in (\ref{convexity_ois_future}), we get an approximation for OIS future at $t=0$.\\
 
 The following figure shows the accuracy of (\ref{convexity_ois_future}) and (\ref{convexity_avg_ois_future}).
-The parameters used to run the Monte Carlo have been $k=0.003$, a volatility $\sigma=0.01$, and flat curve $r=0.01$.
+The parameters used to run the Monte Carlo have been $k=0.003$, $\sigma=0.01$, and flat curve $r=0.01$.
 \begin{figure}[H]
@@
   \includegraphics[scale=0.2]{Figures/convexity_ois.jpg}
-		\caption{Convexity Mc Vs Convexity Malliavin}
+		\caption{OIS Future: MonteCarlo Simulation vs Malliavin}
 \end{subfigure}
@@
   \includegraphics[scale=0.2]{Figures/convexity_avg_ois.jpg}
-		\caption{Convexity Avg Mc Vs Convexity Avg Malliavin}
+		\caption{Average OIS Future: MonteCarlo Simulation vs Malliavin}
 \end{subfigure}
@@
 \begin{align}\label{ca_approximations_fra_arrears}
-CA(t_0,t_1) =   &\frac{G(t_1,t_2)}{\delta_{t_1,t_2}P_{E}(0,t_1,t_2)} \beta(s,t_1, \bar{x}_0(t_1), \bar{y}_s) E(t_1) \nonumber \\
-&\cdot \int_{0}^{t_1} \overline{DM}(s,t_1) \Bigl(\bar{\nu}(s,t_2,\bar{x}_{0}(t_1))-\bar{\nu}(s,t_1,\bar{x}_{0}(t_1))\Bigr) ds 
-\end{align}
-with $\|E(t_1)\|^{2}_{2} \sim \mathcal{O}(t_1) \quad \text{when} \quad t_1 \to 0$ and $\|E(t_1)\|^{2}_{2} < \infty \quad \text{when} \quad t_1 \to \infty$
+CA(t_0,t_1) =   &\frac{G(t_1,t_2)}{\delta_{t_1,t_2}P_{E}(0,t_1,t_2)} \beta(s,t_1, \bar{x}_0(t_1), \bar{y}_s) \nonumber \\
+&\cdot \int_{0}^{t_1} \overline{DM}(s,t_1) \Bigl(\bar{\nu}(s,t_2,\bar{x}_{0}(t_1))-\bar{\nu}(s,t_1,\bar{x}_{0}(t_1))\Bigr) ds  + E(t_1).
+\end{align}
+The error in the approximation model behaves as $\|E(t_1)\|^{2}_{2} \sim \mathcal{O}(t_1) \quad \text{when} \quad t_1 \to 0$ and $\|E(t_1)\|^{2}_{2} < \infty \quad \text{when} \quad t_1 \to \infty$
 \end{theorem}
@@
 		\end{center}
-		\caption{Convexity Mc Vs Convexity Malliavin}
+		\caption{FRA in Arrears: MonteCarlo Simulation vs Malliavin}
 		\label{fig:FRA_HW}
@@
 
-We will suppose that variability of spread term structure $\alpha(t,t^{E}_{i-1}, t^{E}_{i})$ is low. Therefore, it is reasonable to freeze it at time $t=0$. Having
+We will suppose that variability of spread term structure $\alpha(t,t^{E}_{i-1}, t^{E}_{i})$ is low. Therefore, it is reasonable to freeze it at time $t=0$. Then, we have that
 \begin{equation}\label{approximation_basis_swap}
@@
 \begin{theorem}\label{Th_CA_CMS}[Convexity Adjustment approximation for CMS]
-Given the Cheyette model in \eqref{short_rate_cheyette}, the hypotheses \ref{boundedness_volatility} and \ref{boundedness_reversion}, and considering the approximations in \eqref{approximation_y_t} and \eqref{approximation_x_t_a}.
-Given
+Given the Cheyette model in \eqref{short_rate_cheyette}, the hypotheses \ref{boundedness_volatility} and \ref{boundedness_reversion}, and considering the approximations in \eqref{approximation_y_t} and \eqref{approximation_x_t_a}, and
 \begin{equation}
-M(t,t_p)= \frac{P_{ois}(t,t_p)}{01(t,t_a,t_p)}
+M(t,t_p)= \frac{P_{ois}(t,t_p)}{01(t,t_a,t_p)}.
 \end{equation}
@@
 \begin{align} \label{cms_first_order_convexity}
-CA(t_p) &\approx  E(t_a) + \frac{\partial_x S_{a,b}(t_a,\bar{x}_0(t_a), \bar{y}_0) \partial_x M(t_a,t_p,\bar{x}_0(t_a), \bar{y}_0)}{M(0,t_p)}  \\
-&\cdot \int_{0}^{t_a}  \beta^2(s,t_a,\bar{x}_0(t_a),\bar{y}_s) \exp\left(-2\int_{s}^{t_a}\partial_x (\beta(u,t_a,\bar{x}_u,\bar{y}_u) \mu(u,\bar{x}_u, \bar{y}_u,t_a,t_b))|_{\bar{x}_u=\bar{x}_{0}(t_a)}  du \right)ds \nonumber
-\end{align}
-with  $\beta(u,t_a,x,y) = \exp\left(-\int_{u}^{t_a}k_u du\right)\eta(u,x,y)$.
+CA(t_p) &\approx  \frac{\partial_x S_{a,b}(t_a,\bar{x}_0(t_a), \bar{y}_0) \partial_x M(t_a,t_p,\bar{x}_0(t_a), \bar{y}_0)}{M(0,t_p)} \int_{0}^{t_a}  \beta^2(s,t_a,\bar{x}_0(t_a),\bar{y}_s) \\
+&\cdot  \exp\left(-2\int_{s}^{t_a}\partial_x (\beta(u,t_a,\bar{x}_u,\bar{y}_u) \mu(u,\bar{x}_u, \bar{y}_u,t_a,t_b))|_{\bar{x}_u=\bar{x}_{0}(t_a)}  du \right)ds + E(t_a)\nonumber 
+\end{align}
+with  $\beta(u,t_a,x,y) = \exp\left(-\int_{u}^{t_a}k_w dw\right)\eta(u,x,y)$.
 And $\|E(t_a)\|^{2}_{2} \sim \mathcal{O}(t_a) \quad \text{when} \quad t_a \to 0$ and $\|E(t_a)\|^{2}_{2} < \infty \quad \text{when} \quad t_a \to \infty$
@@
 \begin{remark}
-The key point is calculate an approximation of $\mathbb{E}_s^{0,1}\left[ D_s \bar{x}_{t_a}\right]$.
+The key point is to calculate an approximation of $\mathbb{E}_s^{0,1}\left[ D_s \bar{x}_{t_a}\right]$.
 The simplest cases are on the Hull-White or Ho-Lee model.
@@
 \begin{example}[Convexity adjustment for CMS under the Hull-White model]
-To check the accuracy of the last approximation, we compute with a Monte Carlo the exact value of $\mathbb{E}^{t_p}\left[S^{ois}_{a,b}(t_a)\right]$ under spot measure $\mathbb{Q}$, i.e we will compute  $\frac{1}{P(0,t_p)}  \mathbb{E}^{\mathbb{Q}}\left[\frac{S_{a,b}(t_a)}{\beta_{t_a}} \right]$.
+To check the accuracy of the last approximation, we compute with a Monte Carlo simulation the exact value of $\mathbb{E}^{t_p}\left[S^{ois}_{a,b}(t_a)\right]$ under spot measure $\mathbb{Q}$, i.e we will compute  $\frac{1}{P(0,t_p)}  \mathbb{E}^{\mathbb{Q}}\left[\frac{S_{a,b}(t_a)}{\beta_{t_a}} \right]$.
 For the Hull-White model case, we have that
 \begin{equation*}
-D_s x_{t_a} = \sigma \exp(-(t_a - s)).
+D_s x_{t_a} = \sigma \exp(-(t_a - s)),
 \end{equation*}
@@
 In Figure \ref{fig:CMS}, we can observe the CMS convexity adjustment when the tenor of the underlying swap is 5Y.
-We have compared the above approximation and a Monte Carlo for a Hull-White model with parameters $\sigma=0.01$ and $k=0.0007$
+We have compared the above approximation and a Monte Carlo simulation for a Hull-White model with parameters $\sigma=0.01$ and $k=0.0007$
 
@@
 \subsection{Estimation of $\mathbb{E}_s^{\mathbb{Q}}\left[(x_t - \bar{x}_{t})^{2}\right]$}\label{estimation_error_l2}
-To obtain the order of the approximation, we will use the ideas of the paper \cite{B-G-M-2008}.
+To obtain the order of the approximation, we will use the ideas of the paper \cite{BGM}.
 Basically, we will define a parametrization of the process $x_{t,\epsilon}$ and $y_{t,\epsilon}$ with $\epsilon \in [0,1]$.
@@
 \begin{align*}
-\overline{DM}(s,t_a) &= \mathbb{E}^{t_p}_s\biggl[\exp\biggr(-\int_{s}^{t_a} \exp\Bigl(-\int_{u}^{t_a}k_u du\Bigr) \Bigl(\partial_x \eta(u, \bar{x}_0(t_a), \bar{y}_{u}) \bar{\nu}(u,t_p, \bar{x}_0(t_a)) + \eta(u,\bar{x}_0(t_a), \bar{y}_{u})\Bigr) \\
+\overline{DM}(s,t_a) &= \mathbb{E}^{t_p}_s\biggl[\exp\biggr(-\int_{s}^{t_a} \exp\Bigl(-\int_{u}^{t_a}k_u du\Bigr) \Bigl(\partial_x \eta(u, \bar{x}_0(t_a), \bar{y}_{u}) \bar{\nu}(u,t_p, \bar{x}_0(t_a)) + \eta(u,\bar{x}_0(t_a), \bar{y}_{u}) \\
 \qquad &\hspace{3cm} \cdot \partial_x \bar{\nu} (t,t_p, \bar{x}_0(t_a)) du\biggr)\biggr]
@@
 \begin{align*}
-\mathbb{E}^{t_p}_s[D_s \bar{x}_{t_a}] &\approx \eta(s,\bar{x}_s,\bar{y}_s) \exp\left(-\int_{s}^{t_a}k_u du \right)\\ &\cdot \exp\biggr(-\int_{s}^{t_a} \exp\Bigl(-\int_{u}^{t_a}k_u du\Bigr) \Bigl(\partial_x \eta(u, \bar{x}_0(t_a), \bar{y}_{u}) \bar{\nu}(u,t_p, \bar{x}_0(t_a)) + \eta(u,\bar{x}_0(t_a), \bar{y}_{u})\Bigr) \\
+\mathbb{E}^{t_p}_s[D_s \bar{x}_{t_a}] &\approx \eta(s,\bar{x}_s,\bar{y}_s) \exp\left(-\int_{s}^{t_a}k_u du \right)\\ &\cdot \exp\biggr(-\int_{s}^{t_a} \exp\Bigl(-\int_{u}^{t_a}k_u du\Bigr) \Bigl(\partial_x \eta(u, \bar{x}_0(t_a), \bar{y}_{u}) \bar{\nu}(u,t_p, \bar{x}_0(t_a)) + \eta(u,\bar{x}_0(t_a), \bar{y}_{u}) \\
 \qquad &\hspace{3cm} \cdot \partial_x \bar{\nu} (t,t_p, \bar{x}_0(t_a)) du\biggr)
@@
 \end{equation}
-where $\nu(t,T)$ has been defined in (\ref{ois_forward_rate_curve}). Calculating the malliavin derive of $L_{E}(t_0,t_1,t_2)$ we have that
+where $\nu(t,T)$ has been defined in (\ref{ois_forward_rate_curve}). Calculating the Malliavin derivative of $L_{E}(t_0,t_1,t_2)$ we have that
 \begin{equation*}

### 2023-04-24 Latex/paper-resum.tex
# bounded general error
Stylish

@@
 The different choices of $f$, $\mathbb{Q}_1$, and $\mathbb{Q}_2$ will allow us to obtain a convexity adjustment approximation for the different cases of interest.
+
 \subsection{FRAs Vs futures}
@@
 Consequently, we need to adjust the futures price quote to transform them into FRAs price quotes.
-As usual, we will define the forward rate at time $t_0$ between $t_1$ and $t_2$ under the forward curve $E$ as:
+On one hand, we define the forward rate at time $t_0$ between $t_1$ and $t_2$ under the forward curve $E$ as:
 \begin{equation}\label{forward_rate}
@@
 \end{equation} 
-where $P_{E}(t,T)$ is the discount factor for the curve $E$ from $t$ to $T$, and $\delta_{t_1,t_2}$ is the year fraction between $t_1$ and $t_2$.
-Note that $L_{E}(t_0, t_1, t_2)$ is a martingale under the forward measure $\mathbb{Q}^{t_2}$ associated with the numeraire $P_{ois}(t,t_2)$.
+where $P_{E}(t,T)$ is the discount factor for the curve $E$ from $t$ to $T$, and $\delta_{t_1,t_2}$ is the year fraction between $t_1$ and $t_2$, and $t_{0}\leq t_{1} \leq t_{2}$.
+Note that $L_{E}(t_0, t_1, t_2)$ is a martingale under the forward measure $\mathbb{Q}^{t_2}$ associated with the numeraire $P_{ois}(t,t_2)$.\\
+
+On the other hand, given $t\leq t_{0}$, let us define the future rate as:    
+\begin{equation}\label{future}
+\hat{L}_{E}(t,t_0, t_1, t_2) = \mathbb{E}_t^{\mathbb{Q}}\left[L_{E}(t_0, t_1, t_2) \right]
+\end{equation}
+where $\mathbb{Q}$ is the measure associated to the numeraire $B_t=\exp\left(\int_{0}^{t} r_{ois}(s) ds \right)$ with $ r_{ois}(t)$ the risk free short rate. Using
+\eqref{forward_rate} and \eqref{future}, then the convexity adjustment definition is
+\begin{equation*}
+CA(t, t_0, t_1, t_2) = \hat{L}_{E}(t,t_0, t_1, t_2) - \mathbb{E}_t^{\mathbb{Q}^{t_2}}\left[L_{E}(t_0, t_1, t_2) \right].
+\end{equation*}
+
+In the following theorem, we specify the convexity adjustment for the futures.
 
@@
 \begin{equation}\label{ca_approximation_futures}
-CA(t,t_0,t_1) = \frac{P_{E}(0,t_1)}{\delta_{t_1,t_2} P_{E}(0,t_2)} \biggl(G(t_0,t_2)  - G(t_0,t_1) \biggr) \int_{0}^{t_0} \beta(s,t_0,\bar{x}_0(t_0),\bar{y}_s) \nu(s,t_2) ds + E(t_0)
+CA(t,t_0,t_1, t_2) = \frac{P_{E}(0,t_1)}{\delta_{t_1,t_2} P_{E}(0,t_2)} \biggl(G(t_0,t_2)  - G(t_0,t_1) \biggr) \int_{0}^{t_0} \beta(s,t_0,\bar{x}_0(t_0),\bar{y}_s) \nu(s,t_2) ds + E(t_0)
 \end{equation}
@@
 	\end{center}
-	\caption{Futures: MonteCarlo Simulation vs Malliavin}
+	\caption{Futures: Comparison Malliavin vs MC Simulation}
 	\label{fig:Futures}
@@
   \includegraphics[scale=0.2]{Figures/convexity_ois.jpg}
-		\caption{OIS Future: MonteCarlo Simulation vs Malliavin}
+		\caption{Compounding OIS Future}
 \end{subfigure}
@@
   \includegraphics[scale=0.2]{Figures/convexity_avg_ois.jpg}
-		\caption{Average OIS Future: MonteCarlo Simulation vs Malliavin}
+		\caption{Average OIS Future}
 \end{subfigure}
-\caption{Convexity adjustment for compounding and average OIS}
+\caption{OIS Futures: Comparison Malliavin vs MC Simulation}
 \end{figure} 
@@
 \begin{align}\label{ca_approximations_fra_arrears}
-CA(t_0,t_1) =   &\frac{G(t_1,t_2)}{\delta_{t_1,t_2}P_{E}(0,t_1,t_2)} \beta(s,t_1, \bar{x}_0(t_1), \bar{y}_s) \nonumber \\
+CA(t_0,t_1,t_2) =   &\frac{G(t_1,t_2)}{\delta_{t_1,t_2}P_{E}(0,t_1,t_2)} \beta(s,t_1, \bar{x}_0(t_1), \bar{y}_s) \nonumber \\
 &\cdot \int_{0}^{t_1} \overline{DM}(s,t_1) \Bigl(\bar{\nu}(s,t_2,\bar{x}_{0}(t_1))-\bar{\nu}(s,t_1,\bar{x}_{0}(t_1))\Bigr) ds  + E(t_1).
@@
 \begin{equation*}
-CA(t_0,t_1) \approx \frac{G(t_1,t_2)}{\delta_{t_1,t_2}P_{E}(0,t_1,t_2)}  \frac{\sigma^{2}}{k} \int_{0}^{t_1} \Bigl(\exp(- k(t_1 + u)) -   \exp(- k(t_2 + u))\Bigr) du 
+CA(t_0,t_1,t_2) \approx \frac{G(t_1,t_2)}{\delta_{t_1,t_2}P_{E}(0,t_1,t_2)}  \frac{\sigma^{2}}{k} \int_{0}^{t_1} \Bigl(\exp(- k(t_1 + u)) -   \exp(- k(t_2 + u))\Bigr) du 
 \end{equation*}
@@
 		\end{center}
-		\caption{FRA in Arrears: MonteCarlo Simulation vs Malliavin}
+		\caption{FRA in Arrears: Comparison Malliavin vs MC Simulation}
 		\label{fig:FRA_HW}
@@
 \end{align}
-with  $\beta(u,t_a,x,y) = \exp\left(-\int_{u}^{t_a}k_w dw\right)\eta(u,x,y)$.
-And $\|E(t_a)\|^{2}_{2} \sim \mathcal{O}(t_a) \quad \text{when} \quad t_a \to 0$ and $\|E(t_a)\|^{2}_{2} < \infty \quad \text{when} \quad t_a \to \infty$
+with  
+\begin{equation*}
+\beta(u,t_a,x,y) = \exp\left(-\int_{u}^{t_a}k(w) dw\right)\eta(u,x,y).
+\end{equation*} 
+The error in the approximation model behaves as $\|E(t_a)\|^{2}_{2} \sim \mathcal{O}(t_a) \quad \text{when} \quad t_a \to 0$ and $\|E(t_a)\|^{2}_{2} < \infty \quad \text{when} \quad t_a \to \infty$
 \end{theorem}
@@
 	\end{center}
-	\caption{Convexity Mc Vs Convexity Malliavin}
+	\caption{CMS: Comparison Malliavin vs MC Simulation}
 	\label{fig:CMS}
@@
 To obtain the order of the approximation, we will use the ideas of the paper \cite{BGM}.
-Basically, we will define a parametrization of the process $x_{t,\epsilon}$ and $y_{t,\epsilon}$ with $\epsilon \in [0,1]$.
+Basically, we will define a parametrization of the processes $x_{t,\epsilon}$ and $y_{t,\epsilon}$ with $\epsilon \in [0,1]$.
 The role of $\epsilon$ is only as an interpolation parameter between the process.
@@
 \begin{align}\label{parametric_process}
-y_{\epsilon,t} &= \int_{0}^{t} \exp\left(-2 \int_{u}^{t} k(u^{\prime}) du^{\prime}\right) \epsilon^{2} \eta^{2}(u,x_{\epsilon,u},y_{\epsilon,u}) du \\
-x_{\epsilon, t} &= \int_{0}^{t} \exp\left(-\int_{u}^{t} k(u^{\prime}) du^{\prime}\right) \bar{y}_{\epsilon,u} du + \int_{0}^{t} \exp\left(-\int_{u}^{t} k(u^{\prime}) du^{\prime}\right) \epsilon \eta(u,x_{\epsilon,u},y_{\epsilon,u})  \bar{y}_u du
+y_{\epsilon,t} &= \int_{0}^{t} \exp\left(-2 \int_{u}^{t} k(w) dw\right) \epsilon^{2} \eta^{2}(u,x_{\epsilon,u},y_{\epsilon,u}) du \\
+x_{\epsilon, t} &= \int_{0}^{t} \exp\left(-\int_{u}^{t} k(w) dw\right) \bar{y}_{\epsilon,u} du + \int_{0}^{t} \exp\left(-\int_{u}^{t} k(u^{\prime}) du^{\prime}\right) \epsilon \eta(u,x_{\epsilon,u},y_{\epsilon,u})  \bar{y}_u du
 \end{align}
@@
 \end{equation*}
-Then, we have that $z^{1}_{u} = \eta(u,x_u,y_u)$ y $z^{0}_{u} = \eta(u,0,0)$. Therefore,
+Then, we have that $z^{1}_{u} = \eta(u,x_u,y_u)$ and $z^{0}_{u} = \eta(u,0,0)$. Therefore,
 \begin{align*}
@@
 \begin{equation*}
-y_t = \bar{y}_t + E_{y}\left[t\right]
+y_t = \bar{y}_t + E_{y}\left(t\right)
 \end{equation*}
@@
 $$
-E_{y}\left[t\right]= 2 \int_{0}^{t} \exp\left(- 2\int_{u}^{t} k(u^{\prime}) du^{\prime}\right)  \int_{0}^{1} \eta(u, \nu x_u, \nu y_u)   \nabla_{x,y}\eta(u, \nu x_u, \nu y_u) \cdot (x_u, y_u) d\nu du
+E_{y}\left(t\right)= 2 \int_{0}^{t} \exp\left(- 2\int_{u}^{t} k(w) dw\right)  \int_{0}^{1} \eta(u, \nu x_u, \nu y_u)   \nabla_{x,y}\eta(u, \nu x_u, \nu y_u) \cdot (x_u, y_u) d\nu du.
 $$
@@
 \begin{align} \label{upper_bound_E_y}
-\mathbb{E}^{\mathbb{Q}}\left[(E_{y}\left[t\right])^{2}\right] &\leq 4 \mathbb{E}^{\mathbb{Q}}\left[\int_{0}^{t} \exp\left(-4 \int_{u}^{t} k(u^{\prime}) du^{\prime}\right)  \left(\int_{0}^{1} \eta(u, \nu x_u, \nu y_u)   \|\nabla_{x,y}\eta(u, \nu x_u, \nu y_u)\|^{2} \|(x_u, y_u)\| d\nu \right)^2 du \right] ^{2}\nonumber \\
+\mathbb{E}^{\mathbb{Q}}\left[(E_{y}\left(t\right))^{2}\right] &\leq 4 \mathbb{E}^{\mathbb{Q}}\left[\int_{0}^{t} \exp\left(-4 \int_{u}^{t} k(w) dw\right)  \left(\int_{0}^{1} \eta(u, \nu x_u, \nu y_u)   \|\nabla_{x,y}\eta(u, \nu x_u, \nu y_u)\|^{2} \|(x_u, y_u)\| d\nu \right)^2 du \right] ^{2}\nonumber \\
 &\leq 4 \|\eta\|^{2}_{\infty} \max(\|\partial_x\eta\|^{2}_{\infty},\|\partial_y \eta\|^{2}_{\infty} ) \int_{0}^{t} \mathbb{E}^{\mathbb{Q}}\left[ \|(x_u, y_u)\|^{2}\right] du  \nonumber \\
@@
 \begin{equation*}
-x_t = \int_{0}^{t} \exp\left(- \int_{u}^{t} k(u^{\prime}) du^{\prime}\right) \bar{y}_u du + \int_{0}^{t} \exp\left(- \int_{u}^{t} k(u^{\prime}) du^{\prime}\right) E_{y}[u] du + \int_{0}^{t} \eta(t,x_u,y_u) dW_u.
+x_t = \int_{0}^{t} \exp\left(- \int_{u}^{t} k(w) dw\right) \bar{y}_u du + \int_{0}^{t} \exp\left(- \int_{u}^{t} k(w) dw\right) E_{y}(u) du + \int_{0}^{t} \eta(t,x_u,y_u) dW_u. 
 \end{equation*}
@@
 \begin{equation*}
-\eta(t,x_u,y_u) = \eta(t,x_u,\bar{y}_u) + \int_{0}^{1}\partial_y\eta(t,x_u,z^{\nu}_{u}) E_{y}[u] d\nu.
+\eta(t,x_u,y_u) = \eta(t,x_u,\bar{y}_u) + \int_{0}^{1}\partial_y\eta(t,x_u,z^{\nu}_{u}) E_{y}(u) d\nu.
 \end{equation*}
@@
 \begin{equation*}
-E_{x}\left[u\right] = \int_{0}^{1}\partial_y\eta(t,x_u,z^{\nu}_{u}) E_{y}[u] d\nu. 
+E_{x}\left(u\right) = \int_{0}^{1}\partial_y\eta(t,x_u,z^{\nu}_{u}) E_{y}(u) d\nu. 
 \end{equation*}
@@
 \begin{equation*}
-x_t = \bar{x}_t + \int_{0}^{t} \exp\left(- \int_{u}^{t} k(u^{\prime}) du^{\prime}\right) E_{y}[u] du + \int_{0}^{t} \exp\left(- \int_{u}^{t} k(u^{\prime}) du^{\prime}\right) E_{x}[u] dW_u.
+x_t = \bar{x}_t + \int_{0}^{t} \exp\left(- \int_{u}^{t} k(w) dw\right) E_{y}(u) du + \int_{0}^{t} \exp\left(- \int_{u}^{t} k(w) dw\right) E_{x}(u) dW_u.
 \end{equation*}
@@
 \begin{equation*}
- \mathbb{E}^{\mathbb{Q}}[(E_x[u])^{2}] \leq \|\partial_y \eta \|^{2}_{\infty} \mathbb{E}^{\mathbb{Q}}[(E_{y}[u])^{2}]. 
+ \mathbb{E}^{\mathbb{Q}}[(E_x(u))^{2}] \leq \|\partial_y \eta \|^{2}_{\infty} \mathbb{E}^{\mathbb{Q}}[(E_{y}(u))^{2}]. 
 \end{equation*}
@@
 \begin{equation}\label{upper_bound_E_x}
- \mathbb{E}^{\mathbb{Q}}[(E_x[u])^{2}] \leq 4 \|\eta\|^{2}_{\infty} \|\partial_y \eta\|^{2}_{\infty} \max(\|\partial_x\eta\|^{2}_{\infty},\|\partial_y \eta\|^{2}_{\infty} ) \int_{0}^{u} \mathbb{E}^{\mathbb{Q}}\left[ \|(x_s, y_s)\|^{2}\right] ds.
+ \mathbb{E}^{\mathbb{Q}}[(E_x(u))^{2}] \leq 4 \|\eta\|^{2}_{\infty} \|\partial_y \eta\|^{2}_{\infty} \max(\|\partial_x\eta\|^{2}_{\infty},\|\partial_y \eta\|^{2}_{\infty} ) \int_{0}^{u} \mathbb{E}^{\mathbb{Q}}\left[ \|(x_s, y_s)\|^{2}\right] ds.
 \end{equation}
@@
 \begin{align*}
-\mathbb{E}^{\mathbb{Q}}[(x_t - \bar{x}_t)^{2}] & \leq 2 \mathbb{E}^{\mathbb{Q}}\left[ \int_{0}^{t} \exp\left(- \int_{u}^{t} k(u^{\prime}) du^{\prime}\right) E_{y}(u) du    \right]^2\\
-&+ \mathbb{E}^{\mathbb{Q}}\left[ \int_{0}^{t} \exp\left(- \int_{u}^{t} k(u^{\prime}) du^{\prime}\right) E_{x}(u) dW_u\right]^{2} \\
-&\leq 2 \mathbb{E}^{\mathbb{Q}}\left[\int_{0}^{t} \exp\left(- 2\int_{u}^{t} k(u^{\prime}) du^{\prime}\right) \mathbb{E}^{\mathbb{Q}}(E^{2}_{y}(u)) du\right]\\
-&+ \int_{0}^{t} \exp\left(- 2\int_{u}^{t} k(u^{\prime}) du^{\prime}\right) \mathbb{E}^{\mathbb{Q}}[E^{2}_{x}[u]] du. 
+\mathbb{E}^{\mathbb{Q}}[(x_t - \bar{x}_t)^{2}] & \leq 2 \mathbb{E}^{\mathbb{Q}}\left[ \int_{0}^{t} \exp\left(- \int_{u}^{t} k(w) dw\right) E_{y}(u) du    \right]^2\\
+&+ \mathbb{E}^{\mathbb{Q}}\left[ \int_{0}^{t} \exp\left(- \int_{u}^{t} k(w) dw\right) E_{x}(u) dW_u\right]^{2} \\
+&\leq 2 \mathbb{E}^{\mathbb{Q}}\left[\int_{0}^{t} \exp\left(- 2\int_{u}^{t} k(w) dw\right) \mathbb{E}^{\mathbb{Q}}(E^{2}_{y}(u)) du\right]\\
+&+ \int_{0}^{t} \exp\left(- 2\int_{u}^{t} k(w) dw\right) \mathbb{E}^{\mathbb{Q}}[E^{2}_{x}(u)] du. 
 \end{align*}
@@
 \begin{equation*}
-\mathbb{E}^{\mathbb{Q}}[(x_t - \bar{x}_t)^{2}]\leq M^{x}_k \int_{0}^{t} \exp\left(- 2\int_{u}^{t} k(u^{\prime}) du^{\prime}\right) \mathbb{E}^{\mathbb{Q}}\left[ \|(x_u, y_u)\|^{2}\right] du.
+\mathbb{E}^{\mathbb{Q}}[(x_t - \bar{x}_t)^{2}]\leq M^{x}_k \int_{0}^{t} \exp\left(- 2\int_{u}^{t} k(w) dw\right) \mathbb{E}^{\mathbb{Q}}\left[ \|(x_u, y_u)\|^{2}\right] du.
 \end{equation*}
@@
 \begin{equation*}
-\mathbb{E}^{\mathbb{Q}}[y^{2}_u] \leq \|\eta\|^{2}_{\infty} \int_{0}^{u} \exp\left(- 2\int_{s}^{u} k(u^{\prime}) du^{\prime}\right) ds.
-\end{equation*}
-We must note that at the short term and under assumptions (\ref{boundedness_reversion}), we get that
+\mathbb{E}^{\mathbb{Q}}[y^{2}_u] \leq \|\eta\|^{2}_{\infty} \int_{0}^{u} \exp\left(- 2\int_{s}^{u} k(w) dw\right) ds.
+\end{equation*}
+We must note that at the short term and under the Hypothesis (\ref{boundedness_reversion}), we get that
 \begin{equation*}
@@
 \begin{align*}
-\mathbb{E}^{\mathbb{Q}}[x^{2}_u] &\leq 2 \mathbb{E}^{\mathbb{Q}}\left[\int_{0}^{u} \exp\left(- \int_{s}^{u} k(u^{\prime}) du^{\prime}\right) y_s  ds \right]^{2} +  2 \mathbb{E}^{\mathbb{Q}}\left[\int_{0}^{u} \exp\left(- \int_{s}^{u} k(u^{\prime}) du^{\prime}\right) \eta(s,x_s,y_s)  dW_s \right]^{2} \nonumber \\
-&\leq 2 \int_{0}^{u} \exp\left(- 2\int_{s}^{u} k(u^{\prime}) du^{\prime}\right) \mathbb{E}^{\mathbb{Q}}\left[y_s\right]^{2} ds + 2 \int_{0}^{u} \exp\left(- 2 \int_{s}^{u} k(u^{\prime}) du^{\prime}\right) \mathbb{E}^{\mathbb{Q}}\left[\eta^{2}(s,x_s,y_s)\right] ds \\
-&\leq 2 \|\eta\|_{\infty} \int_{0}^{u} \exp\left(- 2\int_{s}^{u} k(u^{\prime}) du^{\prime}\right) \int_{0}^{s}  \exp\left(- 2\int_{s_1}^{s} k(u^{\prime}) du^{\prime}\right) ds_1 ds\\
-&+  2 \|\eta\|_{\infty} \int_{0}^{u} \exp\left(- 2\int_{s}^{u} k(u^{\prime}) du^{\prime}\right) ds
+\mathbb{E}^{\mathbb{Q}}[x^{2}_u] &\leq 2 \mathbb{E}^{\mathbb{Q}}\left[\int_{0}^{u} \exp\left(- \int_{s}^{u} k(w) dw\right) y_s  ds \right]^{2} +  2 \mathbb{E}^{\mathbb{Q}}\left[\int_{0}^{u} \exp\left(- \int_{s}^{u} k(w) dw\right) \eta(s,x_s,y_s)  dW_s \right]^{2} \nonumber \\
+&\leq 2 \int_{0}^{u} \exp\left(- 2\int_{s}^{u} k(w) dw\right) \mathbb{E}^{\mathbb{Q}}\left[y_s\right]^{2} ds + 2 \int_{0}^{u} \exp\left(- 2 \int_{s}^{u} k(w) dw\right) \mathbb{E}^{\mathbb{Q}}\left[\eta^{2}(s,x_s,y_s)\right] ds \\
+&\leq 2 \|\eta\|_{\infty} \int_{0}^{u} \exp\left(- 2\int_{s}^{u} k(w) dw\right) \int_{0}^{s}  \exp\left(- 2\int_{s_1}^{s} k(w) dw\right) ds_1 ds\\
+&+  2 \|\eta\|_{\infty} \int_{0}^{u} \exp\left(- 2\int_{s}^{u} k(w) dw\right) ds
 \end{align*}
@@
 $$
-and when ($u \to \infty$) we have that $\mathbb{E}^{\mathbb{Q}}[x^{2}_u]$ remains bounded. Then, if we use the above inequalities 
-\begin{align*}
-\mathbb{E}^{\mathbb{Q}}[(y_t - \bar{y}_t)^{2}] &\leq M^{y}_k \int_{0}^{t}  \exp\left(- 2\int_{u}^{t} k(u^{\prime}) du^{\prime}\right)  \int_{0}^{u} \exp\left(- 2\int_{s}^{u} k(u^{\prime}) du^{\prime}\right) ds du
+and when $u \to \infty$, we have that $\mathbb{E}^{\mathbb{Q}}[x^{2}_u]$ remains bounded. Then, if we use the above inequalities 
+\begin{align*}
+\mathbb{E}^{\mathbb{Q}}[(y_t - \bar{y}_t)^{2}] &\leq M^{y}_k \int_{0}^{t}  \exp\left(- 2\int_{u}^{t} k(w) dw\right)  \int_{0}^{u} \exp\left(- 2\int_{s}^{u} k(w) dw\right) ds du
 \end{align*}
@@
 \begin{align*}
-\mathbb{E}^{\mathbb{Q}}[(x_t - \bar{x}_t)^{2}] &\leq 2 M^{x}_k \|\eta\|_{\infty} \int_{0}^{t} \exp\left(- 2\int_{u}^{t} k(u^{\prime}) du^{\prime}\right)\int_{0}^{u} \exp\left(- 2\int_{s}^{u} k(u^{\prime}) du^{\prime}\right) \cdot \\
-& \qquad \hspace{1.5cm} \cdot \int_{0}^{s}  \exp\left(- 2\int_{s_1}^{s} k(u^{\prime}) du^{\prime}\right) ds_1 ds du \\
-&+ (2 M^{x}_K \|\eta\|_{\infty} + 1) \int_{0}^{t}  \exp\left(- 2\int_{u}^{t} k(u^{\prime}) du^{\prime}\right)  \int_{0}^{u} \exp\left(- 2\int_{s}^{u} k(u^{\prime}) du^{\prime}\right) ds du.
+\mathbb{E}^{\mathbb{Q}}[(x_t - \bar{x}_t)^{2}] &\leq 2 M^{x}_k \|\eta\|_{\infty} \int_{0}^{t} \exp\left(- 2\int_{u}^{t} k(w) dw\right)\int_{0}^{u} \exp\left(- 2\int_{s}^{u} k(w) dw\right) \cdot \\
+& \qquad \hspace{1.5cm} \cdot \int_{0}^{s}  \exp\left(- 2\int_{s_1}^{s} k(w) dw\right) ds_1 ds du \\
+&+ (2 M^{x}_K \|\eta\|_{\infty} + 1) \int_{0}^{t}  \exp\left(- 2\int_{u}^{t} k(w) dw\right)  \int_{0}^{u} \exp\left(- 2\int_{s}^{u} k(w) dw\right) ds du.
 \end{align*}
@@
 \begin{align*}
-\mathbb{E}^{\mathbb{Q}}[(x_t - \bar{x}_t)^{2}] &\leq \frac{2}{3} M^{x}_k \|\eta\|_{\infty} \left( \int_{0}^{t} \exp\left(- 2\int_{u}^{t} k(u^{\prime}) \right) du  \right)^{3}  \\
-&+ \frac{(2 M^{x}_K \|\eta\|_{\infty} + 1)}{2} \left( \int_{0}^{t}  \exp\left(- 2\int_{u}^{t} k(u^{\prime}) \right) du  \right)^{2}.
-\end{align*}
+\mathbb{E}^{\mathbb{Q}}[(x_t - \bar{x}_t)^{2}] &\leq \frac{2}{3} M^{x}_k \|\eta\|_{\infty} \left( \int_{0}^{t} \exp\left(- 2\int_{u}^{t} k(w)dw \right) du  \right)^{3}  \\
+&+ \frac{(2 M^{x}_K \|\eta\|_{\infty} + 1)}{2} \left( \int_{0}^{t}  \exp\left(- 2\int_{u}^{t} k(w)dw \right) du  \right)^{2}.
+\end{align*}
+\begin{lemma}\label{f_x_y}[Estimation $f(x_t,y_t)$] Given $f$ continuous and derivable, with $\|\partial_x f\|_{\infty} <\infty$ and $\|\partial_y f\|_{\infty}<\infty$. Then
+\begin{equation*}
+f(x_t,y_t)=f(\bar{x}_t,\bar{y}_t) + E(t)
+\end{equation*}
+where $E(t)=\int_{0}^{1} \nabla_{x,y}\eta (u, x_{\epsilon,t}, y_{\epsilon,t}) d\epsilon$ and
+\begin{align*}
+x_{\epsilon,t} &= \epsilon x_t + (1-\epsilon) \bar{x}_t,\\
+y_{\epsilon,t} &= \epsilon y_t + (1-\epsilon) \bar{y}_t.
+\end{align*}
+In addition, we have that 
+\begin{equation*}
+\mathbb{E}[E^{2}(t)] \leq \max(\|\partial_x f\|_{\infty}, \|\partial_x f\|_{\infty}) \mathbb{E}^{\mathbb{Q}}[(x_t - \bar{x}_t)^{2}].
+\end{equation*}
+\end{lemma}
+\begin{proof}
+\end{proof}
 
@@
 \begin{align}\label{approximation_D_s_x_t}
-D_s \bar{x}_{t_a} &= \beta(s,t_a,\bar{x}_s,\bar{y}_s) \bar{M}(s,t_a,t_p) \quad \text{under the measure $\mathbb{Q}^{t_p}$} \nonumber \\
+D_s \bar{x}_{t_a} &= \beta(s,t_a,\bar{x}_s,\bar{y}_s) \bar{M}(s,t_a,t_p) \quad \text{under the measure $\mathbb{Q}^{t_p}$}, \nonumber \\
 D_s \bar{x}_{t_a} &= \beta(s,t_a,\bar{x}_s,\bar{y}_s) \bar{M}(s,t_a)  \quad \text{under the measure $\mathbb{Q}$}
@@
 \bar{M}(s,t_a,t_p) &= \exp\left(-\int_{s}^{t_a} \left( \frac{\left(\partial_x \beta(u,t_a,\bar{x}_0,\bar{y}_{t_a})\right)^{2}}{2} - \exp\left(-\int_{u}^{t_a}k_u du\right) \partial_x (\eta(u, \bar{x}_u, \bar{y}_{u}) \bar{\nu}(u,t_p))\right) du \right) \\
-&\cdot\exp\left(\int_{s}^{t_0} \partial_x \beta(u,t_a,\bar{x}_0,\bar{y}_{t_a}) dW^{\mathbb{Q}}_u \right)
+&\cdot\exp\left(\int_{s}^{t_0} \partial_x \beta(u,t_a,\bar{x}_0,\bar{y}_{t_a}) dW^{\mathbb{Q}}_u \right),
 \end{align*}
@@
 \end{equation*} 
-with $\beta(u,t_a,x,y) = \exp\left(-\int_{u}^{t_a}k_u^{\prime} du^{\prime}\right) \partial_x \eta(u,x,y)$.\\
+with 
+\begin{equation*}
+\beta(u,t_a,x,y) = \exp\left(-\int_{u}^{t_a}k(w) dw\right) \partial_x \eta(u,x,y).
+\end{equation*}
 
@@
 \begin{align*}
-\overline{DM}(s,t_a) &= \mathbb{E}^{t_p}_s\biggl[\exp\biggr(-\int_{s}^{t_a} \exp\Bigl(-\int_{u}^{t_a}k_u du\Bigr) \Bigl(\partial_x \eta(u, \bar{x}_0(t_a), \bar{y}_{u}) \bar{\nu}(u,t_p, \bar{x}_0(t_a)) + \eta(u,\bar{x}_0(t_a), \bar{y}_{u}) \\
+\overline{DM}(s,t_a) &= \mathbb{E}^{t_p}_s\biggl[\exp\biggr(-\int_{s}^{t_a} \exp\Bigl(-\int_{u}^{t_a}k(w) dw\Bigr) \Bigl(\partial_x \eta(u, \bar{x}_0(t_a), \bar{y}_{u}) \bar{\nu}(u,t_p, \bar{x}_0(t_a)) + \eta(u,\bar{x}_0(t_a), \bar{y}_{u}) \\
 \qquad &\hspace{3cm} \cdot \partial_x \bar{\nu} (t,t_p, \bar{x}_0(t_a)) du\biggr)\biggr]
@@
 \intertext{and}
-\partial_x \bar{\nu}(t,t_p,x_0) &= \int_{t}^{t_p} \eta(s,x_0,\bar{y}_s) ds
+\partial_x \bar{\nu}(t,t_p,x_0) &= \int_{t}^{t_p} \eta(s,x_0,\bar{y}_s) ds.
 \end{align*}
@@
 \begin{align*}
-\bar{x}_{t_a} = \bar{x}_0(t_a) &+ \int_{0}^{t_a} \exp\left(-\int_{s}^{t_a}k_u du\right) \bar{y}_s ds - \int_{0}^{t_a} \exp\left(-\int_{s}^{t_a}k_u du\right) \bar{\nu}(s, t_p) \eta(s,\bar{x}_s,\bar{y}_s) ds   \\
-&+ \int_{0}^{t_a}  \exp\left(-\int_{s}^{t_a}k_u du \right)\eta(s,\bar{x}_s,\bar{y}_s) dW_s^{\mathbb{Q}^{t_p}}. 
-\end{align*}
-Now, if we apply $D_s$ in above equality and we use the last approximation we have that
-\begin{align*}
-\mathbb{E}^{t_p}_s[D_s \bar{x}_{t_a}] &\approx \eta(s,\bar{x}_s,\bar{y}_s) \exp\left(-\int_{s}^{t_a}k_u du \right)\\ &\cdot \exp\biggr(-\int_{s}^{t_a} \exp\Bigl(-\int_{u}^{t_a}k_u du\Bigr) \Bigl(\partial_x \eta(u, \bar{x}_0(t_a), \bar{y}_{u}) \bar{\nu}(u,t_p, \bar{x}_0(t_a)) + \eta(u,\bar{x}_0(t_a), \bar{y}_{u}) \\
+\bar{x}_{t_a} = \bar{x}_0(t_a) &+ \int_{0}^{t_a} \exp\left(-\int_{s}^{t_a}k(w) dw\right) \bar{y}_s ds - \int_{0}^{t_a} \exp\left(-\int_{s}^{t_a}k(w) dw\right) \bar{\nu}(s, t_p) \eta(s,\bar{x}_s,\bar{y}_s) ds   \\
+&+ \int_{0}^{t_a}  \exp\left(-\int_{s}^{t_a}k(w) dw \right)\eta(s,\bar{x}_s,\bar{y}_s) dW_s^{\mathbb{Q}^{t_p}}. 
+\end{align*}
+Now, if we apply $D_s$ in the above equality and we use the last approximation, we have that
+\begin{align*}
+\mathbb{E}^{t_p}_s[D_s \bar{x}_{t_a}] &\approx \eta(s,\bar{x}_s,\bar{y}_s) \exp\left(-\int_{s}^{t_a}k(w) dw \right)\\ &\cdot \exp\biggr(-\int_{s}^{t_a} \exp\Bigl(-\int_{u}^{t_a}k(w) dw\Bigr) \Bigl(\partial_x \eta(u, \bar{x}_0(t_a), \bar{y}_{u}) \bar{\nu}(u,t_p, \bar{x}_0(t_a)) + \eta(u,\bar{x}_0(t_a), \bar{y}_{u}) \\
 \qquad &\hspace{3cm} \cdot \partial_x \bar{\nu} (t,t_p, \bar{x}_0(t_a)) du\biggr)
@@
 \begin{align*}
-\bar{x}_{t_a} &= \bar{x}_0(t_a) + \int_{0}^{t_a} \exp\left(-\int_{s}^{t_a}k_u du\right) \bar{y}_u du + \int_{0}^{t_a} \exp\left(-\int_{s}^{t_a}k_u du \right) \eta(u,\bar{x}_u,\bar{y}_u) dW_u^{\mathbb{Q}}
+\bar{x}_{t_a} &= \bar{x}_0(t_a) + \int_{0}^{t_a} \exp\left(-\int_{s}^{t_a}k(w) dw\right) \bar{y}_u du + \int_{0}^{t_a} \exp\left(-\int_{s}^{t_a}k(w) dw \right) \eta(u,\bar{x}_u,\bar{y}_u) dW_u^{\mathbb{Q}}
 \end{align*}
@@
 \begin{equation}
-D_s \bar{x}_{t_a} =  \exp\left(-\int_{s}^{t_a}k_u du \right) \eta(s,\bar{x}_s,\bar{y}_{s})\bar{M}(s,t_a).
+D_s \bar{x}_{t_a} =  \exp\left(-\int_{s}^{t_a}k(w) dw \right) \eta(s,\bar{x}_s,\bar{y}_{s})\bar{M}(s,t_a).
 \end{equation}
@@
 \begin{equation}\label{approximation_spot_E_s_x_t}
-\mathbb{E}^{\mathbb{Q}}_s\left(D_s \bar{x}_{t_a} \right)=\exp\left(-\int_{s}^{t_a}k_u du \right) \eta(s,\bar{x}_s,\bar{y}_{s}).
+\mathbb{E}^{\mathbb{Q}}_s\left(D_s \bar{x}_{t_a} \right)=\exp\left(-\int_{s}^{t_a}k(w) dw \right) \eta(s,\bar{x}_s,\bar{y}_{s}).
 \end{equation}
@@
 \begin{equation}\label{approximation_spot_E_s_x_t}
-\mathbb{E}^{\mathbb{Q}}_s\left(D_s \bar{x}_{t_a} \right) \approx \exp\left(-\int_{s}^{t_a}k_u du \right) \eta(s,\bar{x}_0(t_a),\bar{y}_{s}).
+\mathbb{E}^{\mathbb{Q}}_s\left(D_s \bar{x}_{t_a} \right) \approx \exp\left(-\int_{s}^{t_a}k(w) dw \right) \eta(s,\bar{x}_0(t_a),\bar{y}_{s}).
 \end{equation}
@@
 \end{equation}
-where we must remember that  $\nu(t,T)=\int_{t}^{T}\sigma(t,s) ds$. Therefore, if we apply Itô formula we have that 
+where we must remember that  $\nu(t,T)=\int_{t}^{T}\sigma(t,s) ds$. Therefore, if we apply the Itô formula we have that 
 \begin{equation}\label{annuity_spot_dynamic}
@@
 \end{equation*}
-Using (\ref{short_rate_cheyette}) and above approximation, we obtain that
+Using (\ref{short_rate_cheyette}) and the above approximation, we obtain that
 \begin{align}
-\bar{x}_{t_a} &\approx \bar{x}_0(t_a)  + \int_{0}^{t_a} \exp\left(-\int_{s}^{t}k_u du\right) \bar{y}_u du + \int_{0}^{t_a}  \exp\left(-\int_{s}^{t_a}k_u du \right) \eta(u,\bar{x}(u),\bar{y}_u) dW_u^{\mathbb{Q}} \nonumber \\
-&=  \bar{x}_0(t)  + \int_{0}^{t_a} \exp\left(-\int_{s}^{t_a}k_u du\right) \bar{y}_u du + \int_{0}^{t_a} \exp\left(-\int_{s}^{t_a}k_u du \right) \eta(u,\bar{x}_u,\bar{y}_u) \bar{\sigma}_{01}(u, t_a, t_b) du  \nonumber \\
-&\hspace{1.2cm} + \int_{0}^{t_a} \exp\left(-\int_{s}^{t_a}k_u du \right) \eta(u,\bar{x}_u,\bar{y}_u) dW_u^{01}.
+\bar{x}_{t_a} &\approx \bar{x}_0(t_a)  + \int_{0}^{t_a} \exp\left(-\int_{s}^{t}k(w) dw\right) \bar{y}_u du + \int_{0}^{t_a}  \exp\left(-\int_{s}^{t_a}k(w) dw\right) \eta(u,\bar{x}(u),\bar{y}_u) dW_u^{\mathbb{Q}} \nonumber \\
+&=  \bar{x}_0(t)  + \int_{0}^{t_a} \exp\left(-\int_{s}^{t_a}k(w) dw\right) \bar{y}_u du + \int_{0}^{t_a} \exp\left(-\int_{s}^{t_a}k(w) dw \right) \eta(u,\bar{x}_u,\bar{y}_u) \bar{\sigma}_{01}(u, t_a, t_b) du  \nonumber \\
+&\hspace{1.2cm} + \int_{0}^{t_a} \exp\left(-\int_{s}^{t_a}k(w) dw \right) \eta(u,\bar{x}_u,\bar{y}_u) dW_u^{01}.
 \end{align}
@@
 \begin{align}
-\mathbb{E}^{01}\left[\bar{x}_t\right] &\approx \bar{x}_0(t_a)  + \int_{0}^{t_a} \exp\left(-\int_{s}^{t_a}k_u du\right) \bar{y}_u du \nonumber \\ 
-&\hspace{1.3cm} + \int_{0}^{t_a} \exp\left(-\int_{s}^{t_a}k_u du \right) \eta(u,\bar{x}_u,\bar{y}_u) \bar{\sigma}_{01}(u, t_a, t_b,\bar{x}_0(t_a)) du
+\mathbb{E}^{01}\left[\bar{x}_t\right] &\approx \bar{x}_0(t_a)  + \int_{0}^{t_a} \exp\left(-\int_{s}^{t_a}k(w) dw\right) \bar{y}_u du \nonumber \\ 
+&\hspace{1.3cm} + \int_{0}^{t_a} \exp\left(-\int_{s}^{t_a}k(w) dw\right) \eta(u,\bar{x}_u,\bar{y}_u) \bar{\sigma}_{01}(u, t_a, t_b,\bar{x}_0(t_a)) du
 \end{align}
@@
 \begin{align*}
-\bar{x}_{T_a} =  \bar{x}_0(t_a)  &+ \int_{0}^{t_a} \exp\left(-\int_{s}^{t_a}k_u du\right) \bar{y}_u du \nonumber \\\ 
-&+ \int_{0}^{t_a} \exp\left(-\int_{s}^{t_a}k_u du\right) \sigma_{01}(u,t_a,t_b) \mu(u,\bar{x}_u, \bar{y}_u, t_a,t_b) du \nonumber \\\
-&+  \int_{0}^{t_a}  \exp\left(-\int_{s}^{t_a}k_u du \right) \eta(u,\bar{x}_u,\bar{y}_u) dW_u^{\mathbb{Q}^{01}}.
+\bar{x}_{T_a} =  \bar{x}_0(t_a)  &+ \int_{0}^{t_a} \exp\left(-\int_{s}^{t_a}k(w) dw\right) \bar{y}_u du \nonumber \\\ 
+&+ \int_{0}^{t_a} \exp\left(-\int_{s}^{t_a}k(w) dw\right) \sigma_{01}(u,t_a,t_b) \mu(u,\bar{x}_u, \bar{y}_u, t_a,t_b) du \nonumber \\\
+&+  \int_{0}^{t_a}  \exp\left(-\int_{s}^{t_a}k(w) dw \right) \eta(u,\bar{x}_u,\bar{y}_u) dW_u^{\mathbb{Q}^{01}}.
 \end{align*}
@@
 \begin{equation*}
-D_s \bar{x}_{t_a} = \exp\left(-\int_{s}^{t_a}k_u du \right) \eta(s,\bar{x}_0,\bar{y}_{t_a})\bar{M}^{01}(s,t_a)
+D_s \bar{x}_{t_a} = \exp\left(-\int_{s}^{t_a}k(w) dw \right) \eta(s,\bar{x}_0,\bar{y}_{t_a})\bar{M}^{01}(s,t_a)
 \end{equation*}
@@
 \end{align*}
-and $\beta(u,t_a,x,y) = \exp\left(-\int_{u}^{t_a}k_u du\right)\eta(u,x,y)$.\\
+and 
+\begin{equation*}
+\beta(u,t_a,x,y) = \exp\left(-\int_{u}^{t_a}k(w) dw\right)\eta(u,x,y).
+\end{equation*}
 Then, 
@@
 \subsection{Proof Theorem \ref{Th_CA_futures}}\label{Proof_CA_futures}
-Observe that $L_{E}(t, t_1, t_2)$ is a martingale under the forward measure $\mathbb{Q}^{t_2}$. Let us define the future rate as:    
-\begin{equation}\label{future}
-\hat{L}_{E}(t,t_0, t_1, t_2) = \mathbb{E}_t^{\mathbb{Q}}\left[L_{E}(t_0, t_1, t_2) \right]
-\end{equation}
-where $\mathbb{Q}$ is the measure associated to the numeraire $B_t=\exp\left(\int_{0}^{t} r_{ois, s} ds \right)$ with $ r_{ois, t}$ the risk free short rate. Using
-\eqref{forward_rate} and \eqref{future}, then the convexity adjustment definition is
+%Observe that $L_{E}(t, t_1, t_2)$ is a martingale under the forward measure $\mathbb{Q}^{t_2}$. Let us define the future rate as:    
+%\begin{equation}\label{future}
+%\hat{L}_{E}(t,t_0, t_1, t_2) = \mathbb{E}_t^{\mathbb{Q}}\left[L_{E}(t_0, t_1, t_2) \right]
+%\end{equation}
+%where $\mathbb{Q}$ is the measure associated to the numeraire $B_t=\exp\left(\int_{0}^{t} r_{ois, s} ds \right)$ with $ r_{ois, t}$ the risk free short rate. Using
+%\eqref{forward_rate} and \eqref{future}, then the convexity adjustment definition is
+Note that
 \begin{equation*}
@@
 \begin{equation}\label{approximation_clarkocone}
-\mathbb{E}_s\left[ D_s L_{E}(t_0,t_1,t_2) \right] = \frac{P_{E}(0,t_1)}{\delta_{t_1,t_2} P_{E}(0,t_2)} \left(G(t_0,t_2)  - G(t_0,t_1)\right)\beta(t,t_0,x_0,\bar{y}_s).
+\mathbb{E}_s\left[ D_s L_{E}(t_0,t_1,t_2) \right] = \frac{P_{E}(0,t_1)}{\delta_{t_1,t_2} P_{E}(0,t_2)} \Bigl(G(t_0,t_2)  - G(t_0,t_1)\Bigr)\beta(t,t_0,x_0,\bar{y}_s).
 \end{equation}
@@
 $L_{E}(t,t_1,t_2)$ is martingale under the measure $\mathbb{Q}^{t_2}$, therefore the expected value of \eqref{FRAinArrear} is taken with respect to the wrong martingale.
-To calculate the convexity adjustment, we use the Clark-Ocone to get a representation for $L_{E}(t_1,t_1,t_2)$, i.e
+To calculate the convexity adjustment, we use the Clark-Ocone formula to get a representation for $L_{E}(t_1,t_1,t_2)$, i.e
 \begin{equation}\label{general_convexity_fras}

### 2023-04-24 Latex/paper-resum.tex
Stylish

@@
 \mathbb{E}^{01}_s\left[D_s \bar{x}_{t_a}\right] &= \beta(s,t_a,\bar{x}_s,\bar{y}_s)  \mathbb{E}_s^{01}\left(\exp\left(-\int_{s}^{t_a}\partial_x (\beta(u,t_a,\bar{x}_u,\bar{y}_u) \mu(u,\bar{x}_u, \bar{y}_u,t_a,t_b)) du \right)\right) \nonumber \\
-&\approx \beta(s,t_a,\bar{x}_s,\bar{y}_s) \exp\left(-\int_{s}^{t_a}\partial_x (\beta(u,t_a,\bar{x}_u,\bar{y}_u) \mu(u,\bar{x}_u, \bar{y}_u,t_a,t_b))|_{\bar{x}_u=\bar{x}_{0}(t_a)}  du \right)
+&\approx \beta(s,t_a,\bar{x}_s,\bar{y}_s) \exp\left(-\int_{s}^{t_a}\partial_x (\beta(u,t_a,\bar{x}_u,\bar{y}_u) \mu(u,\bar{x}_u, \bar{y}_u,t_a,t_b))|_{\bar{x}_u=\bar{x}_{0}(t_a)}  du \right).
 \end{align}
@@
 &\approx \mathbb{E}_t^{\mathbb{Q}}\left[I(t_0,t_1)\right] + \int_{t}^{t_1}\int_{\max(s, t_{0})}^{t_1} \beta(s,u,\bar{x}_0(t_1),\bar{y}_s) du dW_s^{\mathbb{Q}}\nonumber \\
-&= \mathbb{E}_t^{\mathbb{Q}}\left[I(t_0,t_1)\right] + \int_{t}^{t_1} g(s)h(s,\bar{x}_0(t_1),\bar{y}_s)\int_{\max(s, t_{0})}^{t_1} \exp\left( -\int_{s}^{u} k_{s^{\prime}} ds^{\prime}\right) du dW_s^{\mathbb{Q}}.
+&= \mathbb{E}_t^{\mathbb{Q}}\left[I(t_0,t_1)\right] + \int_{t}^{t_1} g(s)h(s,\bar{x}_0(t_1),\bar{y}_s)\int_{\max(s, t_{0})}^{t_1} \exp\left( -\int_{s}^{u} k(w) dw\right) du dW_s^{\mathbb{Q}}.
 \end{align}
@@
 \begin{align*}
-\Gamma(s,t_0,t_1)= g(s)h(s,x_0,y_0)\int_{\max(s, t_{0})}^{t_1} \exp\left( -\int_{s}^{u} k_{s^{\prime}} ds^{\prime}\right)du.
+\Gamma(s,t_0,t_1)= g(s)h(s,x_0,y_0)\int_{\max(s, t_{0})}^{t_1} \exp\left( -\int_{s}^{u} k(w) dw\right)du.
 \end{align*}
@@
 Assume we have a cash flow in $t_a < t_p < t_b$ with value $S_{a,b}(t_a)$.
-$S_{a,b}(t_a)$ is a martingale under the measure $\mathbb{Q}^{01}$, but not under the measure $\mathbb{Q}^{t_p}$.
+Recall that $S_{a,b}(t_a)$ is a martingale under the measure $\mathbb{Q}^{01}$, but not under the measure $\mathbb{Q}^{t_p}$.
 Therefore, we take into consideration the effect to compute the expected value of $S_{a,b}(t_a)$ in a measure that is not its natural measure.
@@
 From the previous expression, we must note that under the assumption that there are not stochastic basis, we must compute the convexity adjustment for the OIS swap rate.
-But a complicated point is calculating the expected value
+But a complicated point is to calculating the expected value
 \begin{equation}\label{Exp_M_conditional}
@@
 \\
-In this case, we will choose $\bar{x}_0(t_a)$ such that $S_{a,b}(t_a,\bar{x}_0(t_a),\bar{y}_{t_a})=S_{a,b}(0)$. Now, if we apply Clark-Ocone formula to $M(t_a,t_p)$ we get that
+In this case, we will choose $\bar{x}_0(t_a)$ such that $S_{a,b}(t_a,\bar{x}_0(t_a),\bar{y}_{t_a})=S_{a,b}(0)$. Now, if we apply the Clark-Ocone formula to $M(t_a,t_p)$ we get that
 \begin{equation} \label{clark_ocone_swap_m}
@@
 \mathbb{E}^{t_p}\left[S_{a,b}(t_a)\right] &\approx  S^{ois}_{a,b}(0) + \frac{\partial_x S_{a,b}(t_a,\bar{x}_0(t_a), \bar{y}_0) \partial_x M(t_a,t_p,\bar{x}_0(t_a), \bar{y}_0)} {M(0,t_p)}\nonumber \\
-&\cdot \int_{0}^{t_a}  \beta^2(s,t_a,\bar{x}_0(t_a),\bar{y}_s)\exp\left(-\int_{s}^{t_a}\partial_x (\beta(u,t_a,\bar{x}_u,\bar{y}_u) \mu(u,\bar{x}_u, \bar{y}_u,t_a,t_b))|_{\bar{x}_u=\bar{x}_{0}(t_a)}  du \right)ds
+&\cdot \int_{0}^{t_a}  \beta^2(s,t_a,\bar{x}_0(t_a),\bar{y}_s)\exp\left(-\int_{s}^{t_a}\partial_x (\beta(u,t_a,\bar{x}_u,\bar{y}_u) \mu(u,\bar{x}_u, \bar{y}_u,t_a,t_b))|_{\bar{x}_u=\bar{x}_{0}(t_a)}  du \right)ds.
 \end{align}

### 2023-04-24 Latex/paper-resum.tex
# last lemma bounded error

--- 2023-04-19 Latex/paper-resum.tex
@@
 \end{equation*}
-The error in the approximation model behaves as $\|E\left(t_0\right)\|^{2}_{2} \sim \mathcal{O}(t_0)$ when $t_0 \to 0$ and $\|E\left(t_0\right)\|^{2}_{2} < \infty$ when $t_0 \to \infty$. 
+The error $E(t_0)$ is given by (\ref{f_x_y}) with $f(x,y)=\frac{1}{\delta_{t_1,t_2}}\left(\frac{P_{E}(t_0,t_1,x,y)}{P_{E}(t_0,t_2,x,y)} - 1 \right)$ and behaves as $\mathcal{O}(t_0)$ when $t_0 \to 0$ and $\|E(t_0)\|^{2}_{2} < \infty$ when $t_0 \to \infty$.
 \end{theorem}
@@
 \end{equation}
-The error in the approximation model behaves as $\|E(t_0)\|^{2}_{2} \sim \mathcal{O}(t_0)$ when $t_0 \to 0$ and $\|E(t_0)\|^{2}_{2} < \infty$ when $t_0 \to \infty$.
+The error $E(t_0)$ is given by (\ref{f_x_y}) with $f(x,y)=\frac{\frac{1}{P_{ois}(t_0,t_1,x,y)} -1}{\delta_{t_0,t_1}}$ and behaves as $\mathcal{O}(t_0)$ when $t_0 \to 0$ and $\|E(t_0)\|^{2}_{2} < \infty$ when $t_0 \to \infty$.
 \end{theorem}
@@
 \end{align}
-The error in the approximation model behaves as $\|E(t_1)\|^{2}_{2} \sim \mathcal{O}(t_1) \quad \text{when} \quad t_1 \to 0$ and $\|E(t_1)\|^{2}_{2} < \infty \quad \text{when} \quad t_1 \to \infty$
+The error $E(t_1)$ is given by (\ref{f_x_y}) with $f(x,y)=\frac{1}{\delta_{t_1,t_2}}\left(\frac{1}{P_{E}(t_1,t_2,x,y)} - 1 \right)$ and behaves as $\mathcal{O}(t_1)$ when $t_1 \to 0$ and $\|E(t_1)\|^{2}_{2} < \infty$ when $t_1 \to \infty$.
 \end{theorem}
@@
 \end{align}
-with  $\beta(u,t_a,x,y) = \exp\left(-\int_{u}^{t_a}k_w dw\right)\eta(u,x,y)$.
-And $\|E(t_a)\|^{2}_{2} \sim \mathcal{O}(t_a) \quad \text{when} \quad t_a \to 0$ and $\|E(t_a)\|^{2}_{2} < \infty \quad \text{when} \quad t_a \to \infty$
+with  $\beta(u,t_a,x,y) = \exp\left(-\int_{u}^{t_a}k_w dw\right)\eta(u,x,y)$ and the error $E(t_a)$ is given by (\ref{f_x_y}) with $f(x,y)=\frac{1}{\delta_{t_1,t_2}}\left(\frac{P_{E}(t_0,t_1,x,y)}{P_{E}(t_0,t_2,x,y)} - 1 \right)$ and behaves as $\mathcal{O}(t_a)$ when $t_a \to 0$ and $\|E(t_a)\|^{2}_{2} < \infty$ when $t_a \to \infty$.
 \end{theorem}
@@
 \end{align*}
+\begin{lemma}\label{f_x_y}[Estimation $f(x_t,y_t)$] Given $f$ continuous and derivable, with $\|\partial_x f\|_{\infty} <\infty$ and $\|\partial_y f\|_{\infty}<\infty$. Then
+\begin{equation*}
+f(x_t,y_t)=f(\bar{x}_t,\bar{y}_t) + E(t)
+\end{equation*}
+where $E(t)=\int_{0}^{1} \nabla_{x,y}\ (u, x_{\epsilon,t}, y_{\epsilon,t}) \cdot (x_t - \bar{x}_t,y_t - \bar{y}_t) d\epsilon$ and
+\begin{align*}
+x_{\epsilon,t} &= \epsilon x_t + (1-\epsilon) \bar{x}_t \\
+y_{\epsilon,t} &= \epsilon y_t + (1-\epsilon) \bar{y}_t.
+\end{align*}
+In addition, we have that 
+\begin{equation*}
+\mathbb{E}[E^{2}(t)] \leq \max(\|\partial_x f\|_{\infty}, \|\partial_x f\|_{\infty}) \mathbb{E}^{\mathbb{Q}}[\|(x_t - \bar{x}_t,y_t - \bar{y}_t)\|^{2}].
+\end{equation*}
+\end{lemma}
+\begin{proof}
+From the definition of $x_{\epsilon,t}$ and $y_{\epsilon,t}$ we have by the fundamental theorem calculus that
+
+\begin{equation*}
+f(x_t,y_t) - f(\bar{x}_t,\bar{y}_t) = \int_{0}^{1} \nabla_{x,y}f (u, x_{\epsilon,t}, y_{\epsilon,t})\cdot (x_t - \bar{x}_t,y_t - \bar{y}_t) d\epsilon
+\end{equation*}
+Now, if we use Cauchy-Schwarz and boundness of partial derivatives of $f$ we have that
+\begin{equation*}
+\mathbb{E}^{\mathbb{Q}}[(f(x_t,y_t) - f(\bar{x}_t,\bar{y}_t))^{2}] \leq \max(\|\partial_x f\|_{\infty}, \|\partial_x f\|_{\infty}) \mathbb{E}^{\mathbb{Q}}[\|(x_t - \bar{x}_t,y_t - \bar{y}_t)\|^{2}].
+\end{equation*}
+
+\end{proof}
 
@@
 \overline{DM}(s,t_a) &= \mathbb{E}^{t_p}_s\biggl[\exp\biggr(-\int_{s}^{t_a} \exp\Bigl(-\int_{u}^{t_a}k_u du\Bigr) \Bigl(\partial_x \eta(u, \bar{x}_0(t_a), \bar{y}_{u}) \bar{\nu}(u,t_p, \bar{x}_0(t_a)) + \eta(u,\bar{x}_0(t_a), \bar{y}_{u}) \\
-\qquad &\hspace{3cm} \cdot \partial_x \bar{\nu} (t,t_p, \bar{x}_0(t_a)) du\biggr)\biggr]
+\qquad &\hspace{3cm} \cdot \partial_x \bar{\nu} (t,t_p, \bar{x}_0(t_a))\biggr) du\biggr)\biggr]
 \end{align*}

### 2023-04-24 Latex/paper-resum.tex
# fix some bugs in .tex file

@@
 \end{equation*}
-The error $E(t_0)$ is given by (\ref{f_x_y}) with $f(x,y)=\frac{1}{\delta_{t_1,t_2}}\left(\frac{P_{E}(t_0,t_1,x,y)}{P_{E}(t_0,t_2,x,y)} - 1 \right)$ and behaves as $\mathcal{O}(t_0)$ when $t_0 \to 0$ and $\|E(t_0)\|^{2}_{2} < \infty$ when $t_0 \to \infty$.
+The error $E(t_0)$ is given by (\ref{f_x_y}) with $f(x,y)=\frac{\frac{P_{ois}(t_0,t_1,x,y)}{P_{ois}(t_0,t_2,x,y)} -1}{\delta_{t_0,t_1}}$ and behaves as $\mathcal{O}(t_0)$ when $t_0 \to 0$ and $\|E(t_0)\|^{2}_{2} < \infty$ when $t_0 \to \infty$.
 \end{theorem}
@@
 \end{align}
-with  $\beta(u,t_a,x,y) = \exp\left(-\int_{u}^{t_a}k_w dw\right)\eta(u,x,y)$ and the error $E(t_a)$ is given by (\ref{f_x_y}) with $f(x,y)=\frac{1}{\delta_{t_1,t_2}}\left(\frac{P_{E}(t_0,t_1,x,y)}{P_{E}(t_0,t_2,x,y)} - 1 \right)$ and behaves as $\mathcal{O}(t_a)$ when $t_a \to 0$ and $\|E(t_a)\|^{2}_{2} < \infty$ when $t_a \to \infty$.
+with  $\beta(u,t_a,x,y) = \exp\left(-\int_{u}^{t_a}k_w dw\right)\eta(u,x,y)$ and the error $E(t_a)$ is given by (\ref{f_x_y}) with $f(x,y)=M(t_a,t_p,x,y)S_{a,b}(t_a,x,y)$ and behaves as $\mathcal{O}(t_a)$ when $t_a \to 0$ and $\|E(t_a)\|^{2}_{2} < \infty$ when $t_a \to \infty$.
 \end{theorem}

### 2023-04-24 Latex/paper-resum.tex
# last changes

@@
 
-The following figure shows the accuracy of (\ref{convexity_ois_future}) and (\ref{convexity_avg_ois_future}).
+The following figures show the accuracy of (\ref{convexity_ois_future}) and (\ref{convexity_avg_ois_future}).
 The parameters used to run the Monte Carlo have been $k=0.003$, $\sigma=0.01$, and flat curve $r=0.01$.
+
 \begin{figure}[H]
-\begin{subfigure}{.5\textwidth}
-  \centering
-  \includegraphics[scale=0.2]{Figures/convexity_ois.jpg}
+	\begin{center}
+		\includegraphics[scale=0.3]{Figures/convexity_ois.jpg}
+	\end{center}
 	\caption{OIS Future: MonteCarlo Simulation vs Malliavin}
-\end{subfigure}
-\begin{subfigure}{.5\textwidth}
-  \centering
-  \includegraphics[scale=0.2]{Figures/convexity_avg_ois.jpg}
+	\label{fig:Futures}
+\end{figure}
+
+\begin{figure}[H]
+	\begin{center}
+		\includegraphics[scale=0.3]{Figures/convexity_avg_ois.jpg}
+	\end{center}
 	\caption{Average OIS Future: MonteCarlo Simulation vs Malliavin}
-\end{subfigure}
-\caption{Convexity adjustment for compounding and average OIS}
+	\label{fig:Futures}
 \end{figure} 

### 2023-04-25 Latex/paper-resum.tex
Stylish

@@
 \end{equation} 
-where $P_{E}(t,T)$ is the discount factor for the curve $E$ from $t$ to $T$, and $\delta_{t_1,t_2}$ is the year fraction between $t_1$ and $t_2$.
-Note that $L_{E}(t_0, t_1, t_2)$ is a martingale under the forward measure $\mathbb{Q}^{t_2}$ associated with the numeraire $P_{ois}(t,t_2)$.
+where $P_{E}(t,T)$ is the discount factor for the curve $E$ from $t$ to $T$, and $\delta_{t_1,t_2}$ is the year fraction between $t_1$ and $t_2$ and, $t_{0}\leq t_{1} \leq t_{2}$.
+Note that $L_{E}(t_0, t_1, t_2)$ is a martingale under the forward measure $\mathbb{Q}^{t_2}$ associated with the numeraire $P_{ois}(t,t_2)$.\\
+
+On the other hand, given $t\leq t_{0}$, let us define the future rate as:    
+\begin{equation}\label{future}
+\hat{L}_{E}(t,t_0, t_1, t_2) = \mathbb{E}_t^{\mathbb{Q}}\left[L_{E}(t_0, t_1, t_2) \right]
+\end{equation}
+where $\mathbb{Q}$ is the measure associated to the numeraire $B_t=\exp\left(\int_{0}^{t} r_{ois}(s) ds \right)$ with $ r_{ois}(t)$ the risk free short rate. Using
+\eqref{forward_rate} and \eqref{future}, then the convexity adjustment definition is
+\begin{equation*}
+CA(t, t_0, t_1, t_2) = \hat{L}_{E}(t,t_0, t_1, t_2) - \mathbb{E}_t^{\mathbb{Q}^{t_2}}\left[L_{E}(t_0, t_1, t_2) \right].
+\end{equation*}
+
+In the following theorem, we specify the convexity adjustment for the futures.
 
@@
 \end{equation*}
-The error $E(t_0)$ is given by (\ref{f_x_y}) with $f(x,y)=\frac{\frac{P_{ois}(t_0,t_1,x,y)}{P_{ois}(t_0,t_2,x,y)} -1}{\delta_{t_0,t_1}}$ and behaves as $\mathcal{O}(t_0)$ when $t_0 \to 0$ and $\|E(t_0)\|^{2}_{2} < \infty$ when $t_0 \to \infty$.
+The error $E(t_0)$ is given by (\ref{f_x_y}) with $f(x,y)=\frac{1}{\delta_{t_0,t_1}}\left(\frac{P_{ois}(t_0,t_1,x,y)}{P_{ois}(t_0,t_2,x,y)} -1\right)$ and behaves as $\mathcal{O}(t_0)$ when $t_0 \to 0$ and $\|E(t_0)\|^{2}_{2} < \infty$ when $t_0 \to \infty$.
 \end{theorem}
@@
 \begin{align*}
-CA(t_0,t_1) & \approx \frac{\sigma^{2} \exp(-k t_0)  P_{E}(0,t_1)}{\delta_{t_1,t_2} P_{E}(0,t_2)} \left(\frac{1 - \exp(- k t_0)}{k^{2}} - \frac{t_0 \exp(-k t_2)}{k} \right).   
-\end{align*}
-
-In the Figure \ref{fig:Futures}, we can check the accuracy of the last formula versus Monte Carlo. The parameters used are $\sigma=0.015$, $k=0.003$, and flat curve with level $r=0.01$.
+CA(t_0,t_1, t_2) & \approx \frac{\sigma^{2} \exp(-k t_0)  P_{E}(0,t_1)}{\delta_{t_1,t_2} P_{E}(0,t_2)} \left(\frac{1 - \exp(- k t_0)}{k^{2}} - \frac{t_0 \exp(-k t_2)}{k} \right).   
+\end{align*}
+
+In the Figure \ref{fig:Futures}, we can check the accuracy of the last formula versus Monte Carlo simulation. The parameters used are $\sigma=0.015$, $k=0.003$, and flat curve with level $r=0.01$.
 
@@
 \end{equation}
-The error $E(t_0)$ is given by (\ref{f_x_y}) with $f(x,y)=\frac{\frac{1}{P_{ois}(t_0,t_1,x,y)} -1}{\delta_{t_0,t_1}}$ and behaves as $\mathcal{O}(t_0)$ when $t_0 \to 0$ and $\|E(t_0)\|^{2}_{2} < \infty$ when $t_0 \to \infty$.
+The error $E(t_0)$ is given by (\ref{f_x_y}) with $f(x,y)=\frac{1}{\delta_{t_0,t_1}}\left(\frac{1}{P_{ois}(t_0,t_1,x,y)} -1\right)$ and behaves as $\mathcal{O}(t_0)$ when $t_0 \to 0$ and $\|E(t_0)\|^{2}_{2} < \infty$ when $t_0 \to \infty$.
 \end{theorem}
@@
 	\end{center}
-	\caption{OIS Future: MonteCarlo Simulation vs Malliavin}
+	\caption{Compounding OIS Future: Comparison Malliavin vs MC Simulation}
 	\label{fig:Futures}
@@
 	\end{center}
-	\caption{Average OIS Future: MonteCarlo Simulation vs Malliavin}
+	\caption{Average OIS Future: Comparison Malliavin vs MC Simulation}
 	\label{fig:Futures}
@@
 \begin{align}\label{parametric_process}
-y_{\epsilon,t} &= \int_{0}^{t} \exp\left(-2 \int_{u}^{t} k(u^{\prime}) du^{\prime}\right) \epsilon^{2} \eta^{2}(u,x_{\epsilon,u},y_{\epsilon,u}) du \\
-x_{\epsilon, t} &= \int_{0}^{t} \exp\left(-\int_{u}^{t} k(u^{\prime}) du^{\prime}\right) \bar{y}_{\epsilon,u} du + \int_{0}^{t} \exp\left(-\int_{u}^{t} k(u^{\prime}) du^{\prime}\right) \epsilon \eta(u,x_{\epsilon,u},y_{\epsilon,u})  \bar{y}_u du
+y_{\epsilon,t} &= \int_{0}^{t} \exp\left(-2 \int_{u}^{t} k(w) dw\right) \epsilon^{2} \eta^{2}(u,x_{\epsilon,u},y_{\epsilon,u}) du \\
+x_{\epsilon, t} &= \int_{0}^{t} \exp\left(-\int_{u}^{t} k(w) dw\right) \bar{y}_{\epsilon,u} du + \int_{0}^{t} \exp\left(-\int_{u}^{t} k(w) dw\right) \epsilon \eta(u,x_{\epsilon,u},y_{\epsilon,u})  \bar{y}_u du
 \end{align}
@@
 $$
-E_{y}\left[t\right]= 2 \int_{0}^{t} \exp\left(- 2\int_{u}^{t} k(u^{\prime}) du^{\prime}\right)  \int_{0}^{1} \eta(u, \nu x_u, \nu y_u)   \nabla_{x,y}\eta(u, \nu x_u, \nu y_u) \cdot (x_u, y_u) d\nu du
+E_{y}\left(t\right)= 2 \int_{0}^{t} \exp\left(- 2\int_{u}^{t} k(w) dw\right)  \int_{0}^{1} \eta(u, \nu x_u, \nu y_u)   \nabla_{x,y}\eta(u, \nu x_u, \nu y_u) \cdot (x_u, y_u) d\nu du
 $$
@@
 \begin{equation*}
-\mathbb{E}^{\mathbb{Q}}[y^{2}_u] \leq \|\eta\|^{2}_{\infty} \int_{0}^{u} \exp\left(- 2\int_{s}^{u} k(u^{\prime}) du^{\prime}\right) ds.
-\end{equation*}
-We must note that at the short term and under assumptions (\ref{boundedness_reversion}), we get that
+\mathbb{E}^{\mathbb{Q}}[y^{2}_u] \leq \|\eta\|^{2}_{\infty} \int_{0}^{u} \exp\left(- 2\int_{s}^{u} k(w) dw\right) ds.
+\end{equation*}
+We must note that at the short term and under the assumptions (\ref{boundedness_reversion}), we get that
 \begin{equation*}
@@
 \begin{align*}
-\mathbb{E}^{\mathbb{Q}}[x^{2}_u] &\leq 2 \mathbb{E}^{\mathbb{Q}}\left[\int_{0}^{u} \exp\left(- \int_{s}^{u} k(u^{\prime}) du^{\prime}\right) y_s  ds \right]^{2} +  2 \mathbb{E}^{\mathbb{Q}}\left[\int_{0}^{u} \exp\left(- \int_{s}^{u} k(u^{\prime}) du^{\prime}\right) \eta(s,x_s,y_s)  dW_s \right]^{2} \nonumber \\
-&\leq 2 \int_{0}^{u} \exp\left(- 2\int_{s}^{u} k(u^{\prime}) du^{\prime}\right) \mathbb{E}^{\mathbb{Q}}\left[y_s\right]^{2} ds + 2 \int_{0}^{u} \exp\left(- 2 \int_{s}^{u} k(u^{\prime}) du^{\prime}\right) \mathbb{E}^{\mathbb{Q}}\left[\eta^{2}(s,x_s,y_s)\right] ds \\
-&\leq 2 \|\eta\|_{\infty} \int_{0}^{u} \exp\left(- 2\int_{s}^{u} k(u^{\prime}) du^{\prime}\right) \int_{0}^{s}  \exp\left(- 2\int_{s_1}^{s} k(u^{\prime}) du^{\prime}\right) ds_1 ds\\
-&+  2 \|\eta\|_{\infty} \int_{0}^{u} \exp\left(- 2\int_{s}^{u} k(u^{\prime}) du^{\prime}\right) ds
+\mathbb{E}^{\mathbb{Q}}[x^{2}_u] &\leq 2 \mathbb{E}^{\mathbb{Q}}\left[\int_{0}^{u} \exp\left(- \int_{s}^{u} k(w) dw\right) y_s  ds \right]^{2} +  2 \mathbb{E}^{\mathbb{Q}}\left[\int_{0}^{u} \exp\left(- \int_{s}^{u} k(w) dw\right) \eta(s,x_s,y_s)  dW_s \right]^{2} \nonumber \\
+&\leq 2 \int_{0}^{u} \exp\left(- 2\int_{s}^{u} k(w) dw\right) \mathbb{E}^{\mathbb{Q}}\left[y_s\right]^{2} ds + 2 \int_{0}^{u} \exp\left(- 2 \int_{s}^{u} k(w) dw\right) \mathbb{E}^{\mathbb{Q}}\left[\eta^{2}(s,x_s,y_s)\right] ds \\
+&\leq 2 \|\eta\|_{\infty} \int_{0}^{u} \exp\left(- 2\int_{s}^{u} k(w) dw\right) \int_{0}^{s}  \exp\left(- 2\int_{s_1}^{s} k(w) dw\right) ds_1 ds\\
+&+  2 \|\eta\|_{\infty} \int_{0}^{u} \exp\left(- 2\int_{s}^{u} k(w) dw\right) ds.
 \end{align*}
@@
 \begin{align*}
-\mathbb{E}^{\mathbb{Q}}[(x_t - \bar{x}_t)^{2}] &\leq \frac{2}{3} M^{x}_k \|\eta\|_{\infty} \left( \int_{0}^{t} \exp\left(- 2\int_{u}^{t} k(u^{\prime}) \right) du  \right)^{3}  \\
-&+ \frac{(2 M^{x}_K \|\eta\|_{\infty} + 1)}{2} \left( \int_{0}^{t}  \exp\left(- 2\int_{u}^{t} k(u^{\prime}) \right) du  \right)^{2}.
+\mathbb{E}^{\mathbb{Q}}[(x_t - \bar{x}_t)^{2}] &\leq \frac{2}{3} M^{x}_k \|\eta\|_{\infty} \left( \int_{0}^{t} \exp\left(- 2\int_{u}^{t} k(w)dw \right) du  \right)^{3}  \\
+&+ \frac{(2 M^{x}_K \|\eta\|_{\infty} + 1)}{2} \left( \int_{0}^{t}  \exp\left(- 2\int_{u}^{t} k(w)dw \right) du  \right)^{2}.
 \end{align*}
@@
 \begin{align*}
-x_{\epsilon,t} &= \epsilon x_t + (1-\epsilon) \bar{x}_t \\
+x_{\epsilon,t} &= \epsilon x_t + (1-\epsilon) \bar{x}_t, \\
 y_{\epsilon,t} &= \epsilon y_t + (1-\epsilon) \bar{y}_t.
@@
 \end{equation*} 
-with $\beta(u,t_a,x,y) = \exp\left(-\int_{u}^{t_a}k_u^{\prime} du^{\prime}\right) \partial_x \eta(u,x,y)$.\\
+with $\beta(u,t_a,x,y) = \exp\left(-\int_{u}^{t_a}k(w)dw\right) \partial_x \eta(u,x,y)$.\\
 
@@
 \overline{DM}(s,t_a) &= \mathbb{E}^{t_p}_s\biggl[\exp\biggr(-\int_{s}^{t_a} \exp\Bigl(-\int_{u}^{t_a}k_u du\Bigr) \Bigl(\partial_x \eta(u, \bar{x}_0(t_a), \bar{y}_{u}) \bar{\nu}(u,t_p, \bar{x}_0(t_a)) + \eta(u,\bar{x}_0(t_a), \bar{y}_{u}) \\
-\qquad &\hspace{3cm} \cdot \partial_x \bar{\nu} (t,t_p, \bar{x}_0(t_a))\biggr) du\biggr)\biggr]
+\qquad &\hspace{3cm} \cdot \partial_x \bar{\nu} (t,t_p, \bar{x}_0(t_a))\Bigr) du\biggr)\biggr]
 \end{align*}
@@
 \begin{align*}
-\bar{x}_{t_a} = \bar{x}_0(t_a) &+ \int_{0}^{t_a} \exp\left(-\int_{s}^{t_a}k_u du\right) \bar{y}_s ds - \int_{0}^{t_a} \exp\left(-\int_{s}^{t_a}k_u du\right) \bar{\nu}(s, t_p) \eta(s,\bar{x}_s,\bar{y}_s) ds   \\
-&+ \int_{0}^{t_a}  \exp\left(-\int_{s}^{t_a}k_u du \right)\eta(s,\bar{x}_s,\bar{y}_s) dW_s^{\mathbb{Q}^{t_p}}. 
-\end{align*}
-Now, if we apply $D_s$ in above equality and we use the last approximation we have that
-\begin{align*}
-\mathbb{E}^{t_p}_s[D_s \bar{x}_{t_a}] &\approx \eta(s,\bar{x}_s,\bar{y}_s) \exp\left(-\int_{s}^{t_a}k_u du \right)\\ &\cdot \exp\biggr(-\int_{s}^{t_a} \exp\Bigl(-\int_{u}^{t_a}k_u du\Bigr) \Bigl(\partial_x \eta(u, \bar{x}_0(t_a), \bar{y}_{u}) \bar{\nu}(u,t_p, \bar{x}_0(t_a)) + \eta(u,\bar{x}_0(t_a), \bar{y}_{u}) \\
-\qquad &\hspace{3cm} \cdot \partial_x \bar{\nu} (t,t_p, \bar{x}_0(t_a)) du\biggr)
+\bar{x}_{t_a} = \bar{x}_0(t_a) &+ \int_{0}^{t_a} \exp\left(-\int_{s}^{t_a}k(w)dw\right) \bar{y}_s ds - \int_{0}^{t_a} \exp\left(-\int_{s}^{t_a}k(w)dw\right) \bar{\nu}(s, t_p) \eta(s,\bar{x}_s,\bar{y}_s) ds   \\
+&+ \int_{0}^{t_a}  \exp\left(-\int_{s}^{t_a}k(w)dw \right)\eta(s,\bar{x}_s,\bar{y}_s) dW_s^{\mathbb{Q}^{t_p}}. 
+\end{align*}
+Now, if we apply $D_s$ in the above equality and we use the last approximation we have that
+\begin{align*}
+\mathbb{E}^{t_p}_s[D_s \bar{x}_{t_a}] &\approx \eta(s,\bar{x}_s,\bar{y}_s) \exp\left(-\int_{s}^{t_a}k(w)dw \right)\\ &\cdot \exp\biggr(-\int_{s}^{t_a} \exp\Bigl(-\int_{u}^{t_a}k(w)dw\Bigr) \Bigl(\partial_x \eta(u, \bar{x}_0(t_a), \bar{y}_{u}) \bar{\nu}(u,t_p, \bar{x}_0(t_a)) + \eta(u,\bar{x}_0(t_a), \bar{y}_{u}) \\
+\qquad &\hspace{3cm} \cdot \partial_x \bar{\nu} (t,t_p, \bar{x}_0(t_a))\Bigr) du\biggr).
 \end{align*}
@@
 \begin{align*}
-\bar{x}_{t_a} &= \bar{x}_0(t_a) + \int_{0}^{t_a} \exp\left(-\int_{s}^{t_a}k_u du\right) \bar{y}_u du + \int_{0}^{t_a} \exp\left(-\int_{s}^{t_a}k_u du \right) \eta(u,\bar{x}_u,\bar{y}_u) dW_u^{\mathbb{Q}}
+\bar{x}_{t_a} &= \bar{x}_0(t_a) + \int_{0}^{t_a} \exp\left(-\int_{s}^{t_a}k(w)dw\right) \bar{y}_u du + \int_{0}^{t_a} \exp\left(-\int_{s}^{t_a}k(w)dw \right) \eta(u,\bar{x}_u,\bar{y}_u) dW_u^{\mathbb{Q}}
 \end{align*}
@@
 \begin{equation}
-D_s \bar{x}_{t_a} =  \exp\left(-\int_{s}^{t_a}k_u du \right) \eta(s,\bar{x}_s,\bar{y}_{s})\bar{M}(s,t_a).
+D_s \bar{x}_{t_a} =  \exp\left(-\int_{s}^{t_a}k(w)dw \right) \eta(s,\bar{x}_s,\bar{y}_{s})\bar{M}(s,t_a).
 \end{equation}
@@
 \begin{equation}\label{approximation_spot_E_s_x_t}
-\mathbb{E}^{\mathbb{Q}}_s\left(D_s \bar{x}_{t_a} \right)=\exp\left(-\int_{s}^{t_a}k_u du \right) \eta(s,\bar{x}_s,\bar{y}_{s}).
+\mathbb{E}^{\mathbb{Q}}_s\left(D_s \bar{x}_{t_a} \right)=\exp\left(-\int_{s}^{t_a}k(w)dw \right) \eta(s,\bar{x}_s,\bar{y}_{s}).
 \end{equation}
@@
 \begin{equation}\label{approximation_spot_E_s_x_t}
-\mathbb{E}^{\mathbb{Q}}_s\left(D_s \bar{x}_{t_a} \right) \approx \exp\left(-\int_{s}^{t_a}k_u du \right) \eta(s,\bar{x}_0(t_a),\bar{y}_{s}).
+\mathbb{E}^{\mathbb{Q}}_s\left(D_s \bar{x}_{t_a} \right) \approx \exp\left(-\int_{s}^{t_a}k(w)dw \right) \eta(s,\bar{x}_0(t_a),\bar{y}_{s}).
 \end{equation}
@@
 \end{equation*}
-Using (\ref{short_rate_cheyette}) and above approximation, we obtain that
+Using (\ref{short_rate_cheyette}) and the above approximation, we obtain that
 \begin{align}
-\bar{x}_{t_a} &\approx \bar{x}_0(t_a)  + \int_{0}^{t_a} \exp\left(-\int_{s}^{t}k_u du\right) \bar{y}_u du + \int_{0}^{t_a}  \exp\left(-\int_{s}^{t_a}k_u du \right) \eta(u,\bar{x}(u),\bar{y}_u) dW_u^{\mathbb{Q}} \nonumber \\
-&=  \bar{x}_0(t)  + \int_{0}^{t_a} \exp\left(-\int_{s}^{t_a}k_u du\right) \bar{y}_u du + \int_{0}^{t_a} \exp\left(-\int_{s}^{t_a}k_u du \right) \eta(u,\bar{x}_u,\bar{y}_u) \bar{\sigma}_{01}(u, t_a, t_b) du  \nonumber \\
-&\hspace{1.2cm} + \int_{0}^{t_a} \exp\left(-\int_{s}^{t_a}k_u du \right) \eta(u,\bar{x}_u,\bar{y}_u) dW_u^{01}.
+\bar{x}_{t_a} &\approx \bar{x}_0(t_a)  + \int_{0}^{t_a} \exp\left(-\int_{s}^{t}k(w)dw\right) \bar{y}_u du + \int_{0}^{t_a}  \exp\left(-\int_{s}^{t_a}k(w)dw \right) \eta(u,\bar{x}(u),\bar{y}_u) dW_u^{\mathbb{Q}} \nonumber \\
+&=  \bar{x}_0(t)  + \int_{0}^{t_a} \exp\left(-\int_{s}^{t_a}k(w)dw\right) \bar{y}_u du + \int_{0}^{t_a} \exp\left(-\int_{s}^{t_a}k(w)dw \right) \eta(u,\bar{x}_u,\bar{y}_u) \bar{\sigma}_{01}(u, t_a, t_b) du  \nonumber \\
+&\hspace{1.2cm} + \int_{0}^{t_a} \exp\left(-\int_{s}^{t_a}k(w)dw\right) \eta(u,\bar{x}_u,\bar{y}_u) dW_u^{01}.
 \end{align}
@@
 \begin{align}
-\mathbb{E}^{01}\left[\bar{x}_t\right] &\approx \bar{x}_0(t_a)  + \int_{0}^{t_a} \exp\left(-\int_{s}^{t_a}k_u du\right) \bar{y}_u du \nonumber \\ 
-&\hspace{1.3cm} + \int_{0}^{t_a} \exp\left(-\int_{s}^{t_a}k_u du \right) \eta(u,\bar{x}_u,\bar{y}_u) \bar{\sigma}_{01}(u, t_a, t_b,\bar{x}_0(t_a)) du
+\mathbb{E}^{01}\left[\bar{x}_t\right] &\approx \bar{x}_0(t_a)  + \int_{0}^{t_a} \exp\left(-\int_{s}^{t_a}k(w)dw\right) \bar{y}_u du \nonumber \\ 
+&\hspace{1.3cm} + \int_{0}^{t_a} \exp\left(-\int_{s}^{t_a}k(w)dw\right) \eta(u,\bar{x}_u,\bar{y}_u) \bar{\sigma}_{01}(u, t_a, t_b,\bar{x}_0(t_a)) du
 \end{align}
@@
 \subsection{Approximation of $\mathbb{E}^{01}\left[D_s \bar{x}_{t_a} \right]$}\label{approximation_under_annuity_measeure_d_s}
-Let us to remember that $\nu(t,t_i)=h(t,\bar{x}_t,\bar{y}_t) \frac{G(t,t_i)}{\beta_{t,k}(t)}$ with  $\beta_{t,k}(t) = \exp\left(\int_{0}^{t}k(u)\right)$.
+Let us to remember that $\nu(t,t_i)=h(t,\bar{x}_t,\bar{y}_t) \frac{G(t,t_i)}{\beta_{t,k}(t)}$ with  $\beta_{t,k}(t) = \exp\left(\int_{0}^{t}k(w)dw\right)$.
 Therefore 
@@
 \begin{align*}
-\bar{x}_{T_a} =  \bar{x}_0(t_a)  &+ \int_{0}^{t_a} \exp\left(-\int_{s}^{t_a}k_u du\right) \bar{y}_u du \nonumber \\\ 
-&+ \int_{0}^{t_a} \exp\left(-\int_{s}^{t_a}k_u du\right) \sigma_{01}(u,t_a,t_b) \mu(u,\bar{x}_u, \bar{y}_u, t_a,t_b) du \nonumber \\\
-&+  \int_{0}^{t_a}  \exp\left(-\int_{s}^{t_a}k_u du \right) \eta(u,\bar{x}_u,\bar{y}_u) dW_u^{\mathbb{Q}^{01}}.
+\bar{x}_{T_a} =  \bar{x}_0(t_a)  &+ \int_{0}^{t_a} \exp\left(-\int_{s}^{t_a}k(w)dw\right) \bar{y}_u du \nonumber \\\ 
+&+ \int_{0}^{t_a} \exp\left(-\int_{s}^{t_a}k(w)dw\right) \sigma_{01}(u,t_a,t_b) \mu(u,\bar{x}_u, \bar{y}_u, t_a,t_b) du \nonumber \\\
+&+  \int_{0}^{t_a}  \exp\left(-\int_{s}^{t_a}k(w)dw \right) \eta(u,\bar{x}_u,\bar{y}_u) dW_u^{\mathbb{Q}^{01}}.
 \end{align*}
@@
 \begin{equation*}
-D_s \bar{x}_{t_a} = \exp\left(-\int_{s}^{t_a}k_u du \right) \eta(s,\bar{x}_0,\bar{y}_{t_a})\bar{M}^{01}(s,t_a)
+D_s \bar{x}_{t_a} = \exp\left(-\int_{s}^{t_a}k(w)dw \right) \eta(s,\bar{x}_0,\bar{y}_{t_a})\bar{M}^{01}(s,t_a)
 \end{equation*}
@@
 \end{align*}
-and $\beta(u,t_a,x,y) = \exp\left(-\int_{u}^{t_a}k_u du\right)\eta(u,x,y)$.\\
+and $\beta(u,t_a,x,y) = \exp\left(-\int_{u}^{t_a}k(w)dw\right)\eta(u,x,y)$.\\
 Then, 
@@
 \subsection{Proof Theorem \ref{Th_CA_futures}}\label{Proof_CA_futures}
-Observe that $L_{E}(t, t_1, t_2)$ is a martingale under the forward measure $\mathbb{Q}^{t_2}$. Let us define the future rate as:    
-\begin{equation}\label{future}
-\hat{L}_{E}(t,t_0, t_1, t_2) = \mathbb{E}_t^{\mathbb{Q}}\left[L_{E}(t_0, t_1, t_2) \right]
-\end{equation}
-where $\mathbb{Q}$ is the measure associated to the numeraire $B_t=\exp\left(\int_{0}^{t} r_{ois, s} ds \right)$ with $ r_{ois, t}$ the risk free short rate. Using
-\eqref{forward_rate} and \eqref{future}, then the convexity adjustment definition is
+%Observe that $L_{E}(t, t_1, t_2)$ is a martingale under the forward measure $\mathbb{Q}^{t_2}$. Let us define the future rate as:    
+%\begin{equation}\label{future}
+%\hat{L}_{E}(t,t_0, t_1, t_2) = \mathbb{E}_t^{\mathbb{Q}}\left[L_{E}(t_0, t_1, t_2) \right]
+%\end{equation}
+%where $\mathbb{Q}$ is the measure associated to the numeraire $B_t=\exp\left(\int_{0}^{t} r_{ois, s} ds \right)$ with $ r_{ois, t}$ the risk free short rate. Using
+%\eqref{forward_rate} and \eqref{future}, then the convexity adjustment definition is
+%\begin{equation*}
+%CA(t, t_0, t_1, t_2) = \hat{L}_{E}(t,t_0, t_1, t_2) - \mathbb{E}_t^{\mathbb{Q}^{t_2}}\left[L_{E}(t_0, t_1, t_2) \right].
+%\end{equation*}
+Note that
 \begin{equation*}
@@
 \end{equation}
-If we use (\ref{approsimation_E_s_x_t}) with $T_a=t_0$ and $\beta(t,t_0,x,y) = \exp\left(-\int_{s}^{T_a}k_u du \right) \eta(u,x,y)$, we have that
+If we use (\ref{approsimation_E_s_x_t}) with $T_a=t_0$ and $\beta(t,t_0,x,y) = \exp\left(-\int_{s}^{T_a}k(w)dw \right) \eta(u,x,y)$, we have that
 \begin{align*}
@@
 &\approx \mathbb{E}_t^{\mathbb{Q}}\left[I(t_0,t_1)\right] + \int_{t}^{t_1}\int_{\max(s, t_{0})}^{t_1} \beta(s,u,\bar{x}_0(t_1),\bar{y}_s) du dW_s^{\mathbb{Q}}\nonumber \\
-&= \mathbb{E}_t^{\mathbb{Q}}\left[I(t_0,t_1)\right] + \int_{t}^{t_1} g(s)h(s,\bar{x}_0(t_1),\bar{y}_s)\int_{\max(s, t_{0})}^{t_1} \exp\left( -\int_{s}^{u} k_{s^{\prime}} ds^{\prime}\right) du dW_s^{\mathbb{Q}}.
+&= \mathbb{E}_t^{\mathbb{Q}}\left[I(t_0,t_1)\right] + \int_{t}^{t_1} g(s)h(s,\bar{x}_0(t_1),\bar{y}_s)\int_{\max(s, t_{0})}^{t_1} \exp\left( -\int_{s}^{u} k(w)dw \right) du dW_s^{\mathbb{Q}}.
 \end{align}
@@
 \begin{align*}
-\Gamma(s,t_0,t_1)= g(s)h(s,x_0,y_0)\int_{\max(s, t_{0})}^{t_1} \exp\left( -\int_{s}^{u} k_{s^{\prime}} ds^{\prime}\right)du.
+\Gamma(s,t_0,t_1)= g(s)h(s,x_0,y_0)\int_{\max(s, t_{0})}^{t_1} \exp\left( -\int_{s}^{u} k(w)dw \right)du.
 \end{align*}
@@
 \begin{equation*}
-CA(t_0,t_1) \approx \frac{G(t_1,t_2)}{\delta_{t_1,t_2}P_{E}(0,t_1,t_2)} \beta(s,t_1, \bar{x}_0(t_1), \bar{y}_s) \int_{0}^{t_1} \overline{DM}(s,t_1) \Bigl(\bar{\nu}(s,t_2,\bar{x}_{0}(t_1))-\bar{\nu}(s,t_1,\bar{x}_{0}(t_1))\Bigr) ds
+CA(t_0,t_1,t_2) \approx \frac{G(t_1,t_2)}{\delta_{t_1,t_2}P_{E}(0,t_1,t_2)} \beta(s,t_1, \bar{x}_0(t_1), \bar{y}_s) \int_{0}^{t_1} \overline{DM}(s,t_1) \Bigl(\bar{\nu}(s,t_2,\bar{x}_{0}(t_1))-\bar{\nu}(s,t_1,\bar{x}_{0}(t_1))\Bigr) ds
 \end{equation*}
@@
 From the previous expression, we must note that under the assumption that there are not stochastic basis, we must compute the convexity adjustment for the OIS swap rate.
-But a complicated point is calculating the expected value
+But a complicated point is to calculate the expected value
 \begin{equation}\label{Exp_M_conditional}

### 2023-08-04 Latex/paper-resum.tex
# last modificatons in the paper. Fras futures and Fras in arrears.

@@
 g(T) &= \exp(-kT), \\
-h(t) &= \sigma.
+h(t) &= \exp(k t) \sigma.
 \end{align*}
@@
 \begin{align*}
-\eta_s &= \sigma \exp(-ks),\\
-\beta(s,u, x_0, \bar{y}_s) &= \sigma \exp(-ku),\\
-\nu(s,t_2) &= \sigma \frac{\exp(-ks) - \exp(-kt_2)}{k}.
+\eta_s &= \sigma ,\\
+\beta(s,u, x_0, \bar{y}_s) &= \sigma \exp(-k(u-s)),\\
+\nu(s,t_2) &= \sigma \frac{1 - \exp(-k(t_2-s))}{k}.
 \end{align*}
@@
 \begin{align}\label{ca_approximations_fra_arrears}
-CA(t_0,t_1) =   &\frac{G(t_1,t_2)}{\delta_{t_1,t_2}P_{E}(0,t_1,t_2)} \beta(s,t_1, \bar{x}_0(t_1), \bar{y}_s) \nonumber \\
-&\cdot \int_{0}^{t_1} \overline{DM}(s,t_1) \Bigl(\bar{\nu}(s,t_2,\bar{x}_{0}(t_1))-\bar{\nu}(s,t_1,\bar{x}_{0}(t_1))\Bigr) ds  + E(t_1).
+CA(t_0,t_1) =   &\frac{G(t_1,t_2)}{\delta_{t_1,t_2}P_{E}(0,t_1,t_2)}  \nonumber \\
+&\cdot \int_{0}^{t_1} \beta(s,t_1, \bar{x}_0(t_1), \bar{y}_s) \overline{DM}(s,t_1) \Bigl(\bar{\nu}(s,t_2,\bar{x}_{0}(t_1))-\bar{\nu}(s,t_1,\bar{x}_{0}(t_1))\Bigr) ds  + E(t_1).
 \end{align}
@@
 \begin{equation*}
-CA(t_0,t_1) \approx \frac{G(t_1,t_2)}{\delta_{t_1,t_2}P_{E}(0,t_1,t_2)}  \frac{\sigma^{2}}{k} \int_{0}^{t_1} \Bigl(\exp(- k(t_1 + u)) -   \exp(- k(t_2 + u))\Bigr) du 
+CA(t_0,t_1) \approx \frac{G(t_1,t_2)}{\delta_{t_1,t_2}P_{E}(0,t_1,t_2)}  \frac{\sigma^{2}}{k} \int_{0}^{t_1} \Bigl(\exp(- k(t_1 - u)) -   \exp(- k(t_2 - u))\Bigr) \exp(- k(t_1 - u)) du 
 \end{equation*}
@@
 D_s L_{E}(t_0,t_1,t_2) &\approx \frac{H(t_0,t_1)}{\delta_{t_1,t_2}H(t_0,t_2)}\frac{\partial_{x}P_{ois}(t_0,t_1)P_{ois}(t_0,t_2) - \partial_{x}P_{ois}(t_0,t_2) P_{ois}(t_0,t_1)}{P^{2}_{ois}(t_0,t_2)} \beta(t,t_0,\bar{x}_s,\bar{y}_s)\bar{M}(s,t_0) \nonumber \\
-\approx& \frac{P_{E}(0,t_1)}{\delta_{t_1,t_2} P_{E}(0,t_2)} \left(G(t_0,t_2) \frac{P_{ois}(0,t_2)}{P_{ois}(0,t_0)} - G(t_0,t_1) \frac{P_{ois}(0,t_1)}{P_{ois}(0,t_0)} \right)\beta(t,t_0,\bar{x}_s,\bar{y}_s)\bar{M}(s,t_0).
+\approx& \frac{P_{E}(0,t_1)}{\delta_{t_1,t_2} P_{E}(0,t_2)} \left(G(t_0,t_2) - G(t_0,t_1) \right)\beta(t,t_0,\bar{x}_s,\bar{y}_s)\bar{M}(s,t_0).
 \end{align*}
@@
 \begin{equation}\label{approximation_clarkocone}
-\mathbb{E}_s\left[ D_s L_{E}(t_0,t_1,t_2) \right] = \frac{P_{E}(0,t_1)}{\delta_{t_1,t_2} P_{E}(0,t_2)} \Bigl(G(t_0,t_2)  - G(t_0,t_1)\Bigr)\beta(t,t_0,x_0,\bar{y}_s).
+\mathbb{E}_s\left[ D_s L_{E}(t_0,t_1,t_2) \right] = \frac{P_{E}(0,t_1)}{\delta_{t_1,t_2} P_{E}(0,t_2)} \Bigl(G(t_0,t_2)  - G(t_0,t_1)\Bigr)\beta(s,t_0,x_0,\bar{y}_s).
 \end{equation}
@@
 \begin{equation*}
-CA(t_0,t_1,t_2) \approx \frac{G(t_1,t_2)}{\delta_{t_1,t_2}P_{E}(0,t_1,t_2)} \beta(s,t_1, \bar{x}_0(t_1), \bar{y}_s) \int_{0}^{t_1} \overline{DM}(s,t_1) \Bigl(\bar{\nu}(s,t_2,\bar{x}_{0}(t_1))-\bar{\nu}(s,t_1,\bar{x}_{0}(t_1))\Bigr) ds
+CA(t_0,t_1,t_2) \approx \frac{G(t_1,t_2)}{\delta_{t_1,t_2}P_{E}(0,t_1,t_2)} \int_{0}^{t_1} \beta(s,t_1, \bar{x}_0(t_1), \bar{y}_s) \overline{DM}(s,t_1) \Bigl(\bar{\nu}(s,t_2,\bar{x}_{0}(t_1))-\bar{\nu}(s,t_1,\bar{x}_{0}(t_1))\Bigr) ds
 \end{equation*}

### 2023-08-07 ConvexityAdjustment-Lib/ConvexityAdjustmentUnitTests/FraInArrears.cs
# convexity adjusment fras fixed

@@ -28,7 +28,7 @@ namespace ConvexityAdjustmentUnitTests
             ql.HullWhite model = new ql.HullWhite(curve, k, sigma);
             
             // MC
-            int numberOfSimulations = 500000;
+            int numberOfSimulations = 1000000;
             ulong seed = 123545;
             var numberOfMonths = 240;
 
@@ -36,7 +36,7 @@ namespace ConvexityAdjustmentUnitTests
             List<double> caMc = new List<double>();
             List<double> caMalliavin = new List<double>();
 
-            for (var j = numberOfMonths; j < numberOfMonths + 1; j++)
+            for (var j = 1; j < numberOfMonths + 1; j++)
             {
                 // Product
                 var t1 = calendar.advance(startDate, j, ql.TimeUnit.Months);

### 2023-08-07 Latex/paper-resum.tex
# last version of the paper with some typos fixed

@@
 \begin{equation}\label{R_ois_ca}
-CA_{ois}(t,t_0,t_1) = F(t,t_0,t_1) - \bar{R}(t,t_0,t_1).
-\end{equation}
-The second observation is that we have the following equivalence
+CA_{ois}(t,t_0,t_1) = \bar{R}(t,t_0,t_1) - F(t,t_0,t_1).
+\end{equation}
+The second observation, is that we have the following equality
 \begin{equation}\label{R_ois_avg}
 \mathbb{E}^{\mathbb{Q}}\left[R_{avg}(t_0,t_1) \right] =\frac{1}{\delta_{t_0,t_1}} \mathbb{E}^{\mathbb{Q}}\left[ \log\left(1+ \delta_{t_0,t_1} R(t_0,t_1) \right) \right]  \end{equation}
-To clarify the convexity expression and the calculations, we define 
+To avoid complexity with the notation, we will define 
 \begin{equation*}

### 2023-08-24 Latex/paper-resum.tex
# last modifications in.tex and code

@@
 \begin{align} \label{cms_first_order_convexity}
-CA(t_p) &\approx  \frac{\partial_x S_{a,b}(t_a,\bar{x}_0(t_a), \bar{y}_0) \partial_x M(t_a,t_p,\bar{x}_0(t_a), \bar{y}_0)}{M(0,t_p)} \int_{0}^{t_a}  \beta^2(s,t_a,\bar{x}_0(t_a),\bar{y}_s) \\
+CA(t_p) &\approx  \frac{\partial_x S_{a,b}(t_a,\bar{x}_0(t_a), \bar{y}_{t_a}) \partial_x M(t_a,t_p,\bar{x}_0(t_a), \bar{y}_{t_a})}{M(0,t_p)} \int_{0}^{t_a}  \beta^2(s,t_a,\bar{x}_0(t_a),\bar{y}_s) \\
 &\cdot  \exp\left(-2\int_{s}^{t_a}\partial_x (\beta(u,t_a,\bar{x}_u,\bar{y}_u) \mu(u,\bar{x}_u, \bar{y}_u,t_a,t_b))|_{\bar{x}_u=\bar{x}_{0}(t_a)}  du \right)ds + E(t_a)\nonumber 
@@
 \begin{example}[Convexity adjustment for CMS under the Hull-White model]
-To check the accuracy of the last approximation, we compute with a Monte Carlo simulation the exact value of $\mathbb{E}^{t_p}\left[S^{ois}_{a,b}(t_a)\right]$ under spot measure $\mathbb{Q}$, i.e we will compute  $\frac{1}{P(0,t_p)}  \mathbb{E}^{\mathbb{Q}}\left[\frac{S_{a,b}(t_a)}{\beta_{t_a}} \right]$.
+To check the accuracy of the last approximation, we compute with a Monte Carlo simulation the exact value of $\mathbb{E}^{t_p}\left[S^{ois}_{a,b}(t_a)\right]$ under spot measure $\mathbb{Q}$, i.e we will compute  $\frac{1}{P_{ois}(0,t_a)}  \mathbb{E}^{\mathbb{Q}}\left[\frac{S_{a,b}(t_a) P_{ois}(t_a,t_p)}{\beta_{t_a}} \right]$.
 For the Hull-White model case, we have that
@@
 \begin{equation*}
-\mathbb{E}^{t_p}\left(S_{a,b}(t_a)\right) \approx  S^{ois}_{a,b}(0) + \frac{\partial_x S^{ois}_{a,b}(t_a, \bar{x}_0(t_a),\bar{y}(t_a))\partial_x M(t_a,t_p, \bar{x}_0(t_a),\bar{y}(t_a))}{M(0,t_p)} \frac{\sigma^{2}(1-\exp(-2kt_a))}{2k}.
+\mathbb{E}^{t_p}\left(S_{a,b}(t_a)\right) \approx  S^{ois}_{a,b}(0) + \frac{\partial_x S^{ois}_{a,b}(t_a, \bar{x}_0(t_a),\bar{y}_{t_a})\partial_x M(t_a,t_p, \bar{x}_0(t_a),\bar{y}_{t_a})}{M(0,t_p)} \frac{\sigma^{2}(1-\exp(-2kt_a))}{2k}.
 \end{equation*}
@@
 \begin{align*}
-\bar{x}_{T_a} =  \bar{x}_0(t_a)  &+ \int_{0}^{t_a} \exp\left(-\int_{s}^{t_a}k(w)dw\right) \bar{y}_u du \nonumber \\\ 
+\bar{x}_{t_a} =  \bar{x}_0(t_a)  &+ \int_{0}^{t_a} \exp\left(-\int_{s}^{t_a}k(w)dw\right) \bar{y}_u du \nonumber \\\ 
 &+ \int_{0}^{t_a} \exp\left(-\int_{s}^{t_a}k(w)dw\right) \sigma_{01}(u,t_a,t_b) \mu(u,\bar{x}_u, \bar{y}_u, t_a,t_b) du \nonumber \\\
@@
 \begin{equation*}
-D_s \bar{x}_{t_a} = \exp\left(-\int_{s}^{t_a}k(w)dw \right) \eta(s,\bar{x}_0,\bar{y}_{t_a})\bar{M}^{01}(s,t_a)
+D_s \bar{x}_{t_a} = \exp\left(-\int_{s}^{t_a}k(w)dw \right) \eta(s,\bar{x}_{t_a},\bar{y}_{t_a})\bar{M}^{01}(s,t_a)
 \end{equation*}
@@
 \end{align*}
-Then, we can approximate it by
+Then, we can approximate $\mathbb{E}^{t_p}\left(S_{a,b}(t_a)\right)$ by
 \begin{align}\label{expected_t_p_cms}
@@
 There is a vast literature about how to choose it (see \cite{AndreasenPiterbargIII} or \cite{Hagan20}).
+In the present paper, we will not assume any mapping function.
 \\
-In this case, we will choose $\bar{x}_0(t_a)$ such that $S_{a,b}(t_a,\bar{x}_0(t_a),\bar{y}_{t_a})=S_{a,b}(0)$. Now, if we apply the Clark-Ocone formula to $M(t_a,t_p)$ we get that
+We will choose $\bar{x}_0(t_a)$ such that $S^{ois}_{a,b}(t_a,\bar{x}_0(t_a),\bar{y}_{t_a})=S^{ois}_{a,b}(t_a,0,0)$. Now, if we apply the Clark-Ocone formula to $M(t_a,t_p)$ we get that
 \begin{equation} \label{clark_ocone_swap_m}
@@
 \mathbb{E}^{t_p}\left(S_{a,b}(t_a)\right) =& S^{ois}_{a,b}(0) + \frac{1}{M(0,t_p)} \mathbb{E}^{01}\left[ S^{ois}_{a,b}(t_a) \int_{0}^{t_a} \mathbb{E}^{0,1}_s\Bigl[D_s x_{t_a}\partial_x M(t_a,t_p)  \Bigr] dW^{0,1}_s   \right] \nonumber \\
-=&  S^{ois}_{a,b}(0) + \frac{1}{M(0,t_p)} \mathbb{E}^{01}\left[\int_{0}^{t_a} D_s x_{t_a} \partial_x S_{a,b}(t_a) \mathbb{E}^{0,1}_s\Bigl[D_s x_{t_a}\partial_x M(t_a,t_p)  \Bigr] ds   \right].
-\end{align}
-Now from (\ref{approximation_E_01_Ds_x_t}) and choosing $\bar{x}_0(t_a)$ such that $S_{a,b}(t_a,\bar{x}_0(t_a),\bar{y}_{t_a})=S_{a,b}(0)$, we have that
+=&  S^{ois}_{a,b}(0) + \frac{1}{M(0,t_p)} \mathbb{E}^{01}\left[\int_{0}^{t_a} D_s x_{t_a} \partial_x S^{ois}_{a,b}(t_a) \mathbb{E}^{0,1}_s\Bigl[D_s x_{t_a}\partial_x M(t_a,t_p)  \Bigr] ds   \right].
+\end{align}
+Now from (\ref{approximation_E_01_Ds_x_t}) and choosing $\bar{x}_0(t_a)$ such that $S^{ois}_{a,b}(t_a,\bar{x}_0(t_a),\bar{y}_{t_a})=S^{ois}_{a,b}(0)$, we have that
 \begin{align}
-\mathbb{E}^{t_p}\left[S_{a,b}(t_a)\right] &\approx  S^{ois}_{a,b}(0) + \frac{\partial_x S_{a,b}(t_a,\bar{x}_0(t_a), \bar{y}_0) \partial_x M(t_a,t_p,\bar{x}_0(t_a), \bar{y}_0)} {M(0,t_p)}\nonumber \\
+\mathbb{E}^{t_p}\left[S_{a,b}(t_a)\right] &\approx  S^{ois}_{a,b}(0) + \frac{\partial_x S^{ois}_{a,b}(t_a,\bar{x}_0(t_a), \bar{y}_{t_a}) \partial_x M(t_a,t_p,\bar{x}_0(t_a), \bar{y}_{t_a})} {M(0,t_p)}\nonumber \\
 &\cdot \int_{0}^{t_a}  \beta^2(s,t_a,\bar{x}_0(t_a),\bar{y}_s)\exp\left(-\int_{s}^{t_a}\partial_x (\beta(u,t_a,\bar{x}_u,\bar{y}_u) \mu(u,\bar{x}_u, \bar{y}_u,t_a,t_b))|_{\bar{x}_u=\bar{x}_{0}(t_a)}  du \right)ds.

### 2023-08-24 ConvexityAdjustment-Lib/ConvexityAdjustment-Lib/HullWhite/HullWhite.cs

@@ -35,6 +35,7 @@ namespace ConvexityAdjustment_Lib.HullWhite
             double deltaTime = _dcCurve.yearFraction(_valueDate, _schedule.dates()[0]);
             double f0T = _model.termStructure().link.forwardRate(deltaTime, deltaTime, ql.Compounding.Continuous,
                 ql.Frequency.NoFrequency, true).rate();
+            // var annuity = _model.GetAnnuity(_schedule.dates()[0], _schedule.dates()[0], v + f0T, _schedule, _dcCurve, _dcSwap);
             var annuity = _model.GetAnnuity(_schedule.dates()[0], _schedule.dates()[0], v + f0T, _schedule, _dcCurve, _dcSwap);
             
             // times
@@ -283,7 +284,8 @@ namespace ConvexityAdjustment_Lib.HullWhite
         {
             double m = Math.Pow(sigma / k, 2.0);
             return m * (beta(0, t, 2.0 * k) + Math.Exp(-2.0 * k * t) * t -
-                                    2.0 * Math.Exp(-k * t) * beta(0.0, t, k));
+                                2.0 * Math.Exp(-k * t) * beta(0.0, t, k));
+            // return m * (t + beta(0.0, t, 2.0 * k) - 2.0 * beta(0.0, t,  k));
         }
 
 
@@ -313,7 +315,10 @@ namespace ConvexityAdjustment_Lib.HullWhite
         public static double getDriftIt(double t, double k, double sigma)
         {
             var m = 0.5 * Math.Pow(sigma / k, 2.0);
-            return m * (t + beta(t, 2.0 * t, k) - beta(0.0, t, k)- beta(0.0, t, 2.0 * k));
+            // return m * (t + beta(t, 2.0 * t, k) - beta(0.0, t, k)- beta(0.0, t, 2.0 * k));
+            // var m = 0.5 * Math.Pow(sigma / k, 2.0);
+            // return m * (t + beta(0.0,  t, 2.0 * k) - 2.0 * beta(0.0, t, k));
+            return m * (t + beta(0.0, t, 2.0 * k) - 2.0 * beta(0.0, t, k));
         }
 
         public static double getCovarianceRtIt(double t1, double t2, double k, double sigma)

### 2023-08-24 ConvexityAdjustment-Lib/ConvexityAdjustmentUnitTests/CmsConvexity.cs

@@ -16,7 +16,7 @@ namespace ConvexityAdjustmentUnitTests
 
             // Hull-White parameters
             double k = 0.0007;
-            double sigma = 0.007;
+            double sigma = 0.01;
 
             // Curves
             double discountFlatRate = 0.015;
@@ -96,6 +96,7 @@ namespace ConvexityAdjustmentUnitTests
                     .withPricingEngine(discountEngine)
                     .withFixedLegRule(ql.DateGeneration.Rule.Forward)
                     .withFloatingLegRule(ql.DateGeneration.Rule.Forward)
+                    .withFloatingLegDayCount(discountCurve.link.dayCounter())
                     .value();
                 
                 var swapOisDerivative = model.GetPartialDerivativeSwapRate(startDate, startDate, f0ts[j],
@@ -103,28 +104,16 @@ namespace ConvexityAdjustmentUnitTests
                     staticSwap.fixedDayCount());
 
 
-                var annuityT0 = model.GetAnnuity(startDate, startDate, f0ts[j], staticSwap.fixedSchedule(),
+                var annuity = model.GetAnnuity(startDate, startDate, f0ts[j], staticSwap.fixedSchedule(),
                     discountCurve.link.dayCounter(), staticSwap.fixedDayCount());
          
                 partialOisSwap.Add(swapOisDerivative);
-                var swapOisFairRate =
-                    (discountCurve.link.discount(datesToCompute[j]) - discountCurve.link.discount(staticSwap.maturityDate())) /
-                    annuityT0.Item1;
+                
+                var swapOisFairRate = (discountCurve.link.discount(datesToCompute[j]) - discountCurve.link.discount(staticSwap.maturityDate())) / annuity.Item1;
                 swapRates.Add(swapOisFairRate);
-
-                // ois swap rate
-                var tb = staticSwap.maturityDate();
                 
-                var oisSwapRate =
-                    (discountCurve.link.discount(datesToCompute[j]) - discountCurve.link.discount(tb)) /
-                    annuityT0.Item1;
-                swapOisRates.Add(oisSwapRate);
-                
-                // ratio swaps
-                double c = swapRates[j] / swapOisRates[j];
-                ratioSwaps.Add(c);
-                
-                rateCmsForward.Add(staticSwap.fairRate());
+                // rateCmsForward.Add(staticSwap.fairRate());
[…]

### 2023-08-25 Latex/paper-resum.tex
Changing references
Changing references and thanks

@@
 %\clearpage
-\blfootnote{The authors would like to thank Elisa Al\`os and Josep Vives for helpful discussions.}
+\blfootnote{The authors would like to thank Elisa Al\`os, Dariusz Gatarek, and Josep Vives for helpful discussions.}
 
@@
 
-In order to have a more manageable model, we will follow the ideas of \cite{AndreasenPiterbarg} where the state variables are approximated. So, we can approximate $y(t)$ as
+In order to have a more manageable model, we will follow the ideas of \cite{AndreasenPiterbarg} where the state variables are approximated.
+Although it is possible to use other methodologies, for example \cite{Gatarek2019TowardsAG}.
+So, we can approximate $y(t)$ as
 \begin{equation}\label{approximation_y_t}
